### 2019-03-14 TFM.tex
Empiezo a escribir

\documentclass[oneside, 11pt, letterpaper]{report}

\usepackage[spanish,english] {babel}  % Idioma (és important a l'hora de separar una paraula a final de línia)

%\IfFileExists{myStyle.sty}{\usepackage{myStyle}}{\usepackage{../myStyle}}
\input{myStyle.sty}
\newtheorem{statement}{Statement}
\usepackage[toc,page]{appendix}
\usepackage{todonotes}

\def\@graiments{}
\def\@paraulesclau{}
\def\l@abstractceng{No abstract}

\begin{document}
\tableofcontents

\chapter{preliminaries}

\begin{itemize}
	\item The $\mathcal{G}(n,p)$ model and generalizations to hypergraphs. 
	\item First order language for graphs and hypergraphs.
	\item E.F. Games.
\end{itemize}
\todo[inline]{Escribir todo esto}

\chapter{Almost sure winning conditions for Duplicator}

\begin{itemize}
	\item Classes of j-morphic trees.
	\item Classes of j-morphic Graphs.
	\item Cores and j-agreeability.
	\item Simplicity and richness.
	\item Almost sure winning strategy.

\end{itemize}

\end{document}

### 2019-03-18 TFM.tex
Edge blueprints

@@
 
+\chapter*{Introduction}
+
+\chapter*{Notation}
+
 \chapter{preliminaries}
@@
 \begin{itemize}
+	\item  General hypergraphs.
+	\item First order language for graphs and hypergraphs.
 	\item The $\mathcal{G}(n,p)$ model and generalizations to hypergraphs. 
-	\item First order language for graphs and hypergraphs.
 	\item E.F. Games.
@@
 \todo[inline]{Escribir todo esto}
+
+\section{Generic hypergraphs}
+
+When considering the various definitions of graphs $G$ with no multiple edges,
+one can notice that there are two main properties which set them apart. First, one can set 
+the edges of $G$ to be directed - i.e., the edge $(u,v)$ is different from the edge $(v,u)$-
+or undirected, and second, one can either allow loops - edges of the form $(u,u)$ - or not. 
+The first property is a \textit{commutativity} one, that relates to the 
+\textit{isomorphy} group of our edges: since our edges are of cardinality two, 
+their isomorphy group can either be the trivial one - and they will be directed-, or the whole
+$S_2$ - and they will be undirected -. The second property in turn relates to \textit{anti-reflexivity} constraints.
+While this point of view may seem artificial in the case of graphs, in the framework of hypergraphs
+it becomes more natural. \par
+Given a natural number, $k$, we will call $[k]$ to the set $\{1,\dots, k\}$, and $\Delta_k$ to the
+diagonal $\{ \, (i,i) \,  | \, 1\leq i \leq k \, \} \subset [k]^2$.
+
+\begin{definition} Let $k$ be a natural number. Then a \textbf{k-hyperedge blueprint}, $(\Phi, A)$ 
+consists of 
+\begin{enumerate}
+	\item a subgroup $\Phi$ of the symmetric group $S_k$, and
+	\item a subset $A\subset [k]^2\setminus \Delta_k$ that is $\Phi$-invariant. 
+	This means that if $(i,j)\in A$ and $\sigma \in \Phi$ then $(\sigma(i),\sigma(j))\in A$.
+\end{enumerate} 
+\end{definition}
+
+Given a set $V$, the symmetric group $S_k$ acts in a natural way on $V^k$ in the following way:
+if $\sigma \in S_k$ and $(v_1,\dots , v_k) \in V^k$ then we define $\sigma (v_1,\dots v_k)$ to be
+the $k$-tuple $(w_1, \dots , w_k)$ such that $w_{\sigma(i)}=v_i$ for all $1\leq i \leq k$. 
+In other words, $S_k$ acts on $V^k$ by permuting coordinates of its elements. \par
+Let $S \subseteq V^k$ and $\Phi \leq S_k$. Then $\Phi S$ will denote the set 
+$\{ \, \sigma v \, | \, \sigma \in \Phi, \, v\in S \, \}$. We will say that $S$ is $\Phi$-closed
+if $\Phi S = S$. If $S$ is $\Phi$-closed, we will call $S/ \phi$ to the orbit space of 
+$S$ by $\Phi$.
 

### 2019-06-14 TFM.tex
Escribiendo

--- 2019-03-14 TFM.tex
@@
-\documentclass[oneside, 11pt, letterpaper]{report}
+\documentclass[11pt,notitlepage]{report}
 
-\usepackage[spanish,english] {babel}  % Idioma (és important a l'hora de separar una paraula a final de línia)
+\usepackage[left=4cm,right=4cm,top=3cm,bottom=3cm]{geometry}
+\usepackage{graphicx}
+\usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}
+%\usepackage{color}
+\usepackage{float}
+\usepackage{hyperref}
+\usepackage{enumerate}
+\usepackage{enumitem}
 
-%\IfFileExists{myStyle.sty}{\usepackage{myStyle}}{\usepackage{../myStyle}}
-\input{myStyle.sty}
-\newtheorem{statement}{Statement}
-\usepackage[toc,page]{appendix}
+\newlength{\margen}
+\setlength{\margen}{\paperwidth}
+\addtolength{\margen}{-\textwidth}
+\addtolength{\skip\footins}{0.7 cm}
+\setlength{\margen}{0.5\margen}
+\addtolength{\margen}{-1in}
+\setlength{\oddsidemargin}{\margen}
+\setlength{\evensidemargin}{\margen}
+\setlength{\abovedisplayskip}{3pt}
+\setlength{\belowdisplayskip}{3pt}
+%%%% Small setup %%%%
+\hypersetup{
+	colorlinks=false,
+	pdfborder={1 1 0.0005},
+}
+\setlength{\parskip}{0.2cm}
+%%%%%%%%%%%%%%%
+\usepackage{tikz-cd}
+\usetikzlibrary{cd}
+\usepackage[english]{babel}
 \usepackage{todonotes}
+\usepackage{cleveref}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{bbding}
+\usepackage{tcolorbox}
+\usepackage{natbib}
 
-\def\@graiments{}
-\def\@paraulesclau{}
-\def\l@abstractceng{No abstract}
+\DeclareMathOperator{\incl}{incl}
+
+\newtheorem{proposition}{Proposition}[chapter]
+\newtheorem{fact}{Fact}[chapter]
+\newtheorem{theorem}{Theorem}[chapter]
+\newtheorem{lemma}{Lemma}[chapter]
+\newtheorem{corollary}{Corollary}[chapter]
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[chapter]
+\newtheorem{propdef}{Proposition / Definition}[chapter]
+
+\newtheorem{inneraxiom}{Axiom}
+\newenvironment{axiom}[1]
+{\renewcommand\theinneraxiom{#1}\inneraxiom}
+{\endinneraxiom}
+
+\newcommand{\Z}{\mathbb{Z}}
+\newcommand{\CC}{\mathbb{C}}
+\newcommand{\Q}{\mathbb{Q}}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\N}{\mathbb{N}}
+\newcommand{\Lan}{\mathcal{L}}
+\newcommand{\Ln}{\lim\limits_{n\to \infty}}
+\newcommand{\clist}{c_{i_1}, \cdots, c_{i_m}}
+\newcommand{\morph}[1]{\stackrel{#1}{\simeq}}
 
@@
 
-\chapter{preliminaries}
+\chapter*{Introduction}
 
-\begin{itemize}
-	\item The $\mathcal{G}(n,p)$ model and generalizations to hypergraphs. 
-	\item First order language for graphs and hypergraphs.
-	\item E.F. Games.
-\end{itemize}
-\todo[inline]{Escribir todo esto}
+\chapter*{Notation}
 
-\chapter{Almost sure winning conditions for Duplicator}
+\chapter{Preliminaries}
 
-\begin{itemize}
-	\item Classes of j-morphic trees.
-	\item Classes of j-morphic Graphs.
-	\item Cores and j-agreeability.
-	\item Simplicity and richness.
-	\item Almost sure winning strategy.
+\section{Models of Random Graphs}
 
+\section{First Order Logic}
+
+\section{Ehrenfeucht Fraisse Games and the Logic of Random Graphs}
+
+\chapter{Probabilities of Sentences about Very Sparse Random Graphs}
+
+In this chapter we will review the results obtained
+ in the paper with the same name by James F. Lynch \cite{lynch1992probabilities}.
+In there, limit probabilities of sentences in the first order language of graphs $\mathcal{L}$
+are discussed for the binomial model $G(n,p)$ in the cases $p=\beta/n$ and
+$p=\beta n^{-\alpha}$ with $\alpha=(l+1)/l$ . \par
+
+More precisely, it is proven that in those cases the 
+probability of every sentence converges and it is shown
+that for any of those sentences, its limit probability 
+is among the values taken by some analytic formulas
+with parameter $\beta$. \par
+
+We are interested in the case $p=\frac{\beta}{n}$, which is 
+the one discussed more extensively in \cite{lynch1992probabilities}. 
+According to the author, the relevant theorems for 
+the other case can be proven analogously. From now on we
+will only refer as random graphs to the ones in $G(n,\beta/n)$\par
+
+From now on we will denote by $Poi_\lambda$ the probability
+function of the Poisson distribution with mean $\lambda$.
+That is, the one given by $Poi_\lambda(n)=e^{-\lambda}\lambda^n/n!$ 
+for any $n\in \N$.
+Also, we define $Poi_\lambda(\leq n)$ and $Poi_\lambda(>n)$ as 
+$\sum_{i=0}^n Poi_\lambda(n)$ and $1-Poi_\lambda(\leq n)$
+respectively. Notice that for a fixed $n$, both $Poi_\lambda(\leq n)$ 
+and $Poi_\lambda(>n)$ can be considered real functions of parameter $\lambda$. \par
+
+We define the following sets of functions. Let $\Lambda$ be the smallest 
+set of expressions with parameter $\beta$ such that:
+
+\begin{itemize}[noitemsep, topsep=0pt]
+	\item $1\in \Lambda$,
+	\item For any $\lambda \in \Lambda$ and $i\in \N$, 
+	both $Poi_{\beta\lambda}(n)$ and $Poi_{\beta\lambda}(> n)$ are in
+	$\Lambda$.
+	\item For any $\lambda_1,\lambda_2 \in \Lambda$,
+	$\lambda_1 \lambda_2$ belongs to $\Lambda$ as well.
 \end{itemize}
 
+And let $\Theta$ be the smallest set of functions with parameter $\beta$
+such that:
+\begin{itemize}[noitemsep, topsep=0pt]
+	\item For any $\lambda \in \Lambda$ 
+	and $n,a,i\in \N$, with $i\geq 3$, 
+	both $Poi_{\beta^i\lambda/a}(\leq n)$ and $Poi_{\beta^i\lambda/a}(> n)$
+	are in $\Theta$.
+\end{itemize}
+
+The main result is the following:
+
+\begin{theorem}[Lynch, 1992] \label{thrm:main}
+	Let $\phi$ be a sentence in the first order theory of graphs. Then the limit
+	$\lim\limits_{n\to \infty} P(G(n,\beta/n) \models \phi )$ exists for all positive real numbers
+	$\beta$, and it is a finite sum of expressions in $\Theta$.
+\end{theorem}
+
+We show now an outline of the proof. \par 
+We show that for any quantifier rank $k$ there are some classes of graphs 
+$C^k_1,\dots, C^k_{n_k}$ such that
+\begin{itemize}[noitemsep, topsep=0pt]
+	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
+	\item[(2)] a.a.s. any random graph belongs to some of them, and
+	\item[(3)] the limit probability of random graph belonging to any of them is an expression in $\Theta$. 
+\end{itemize}
+
+After this is archived the theorem follows easily. Indeed, let $\phi$ be a sentence 
+in the first order language $\Lan$ of graphs whose quantifier rank is $k$, and denote by
+$G$ a random graph in $G(n,\beta/n)$. We define the events $E_1,\dots,E_{n_k}$ as
+\[E_i:= (G \models \phi) \wedge (G \in C_i),\]
+and the  event $F$ as
+\[F:= (G \models \phi) \bigwedge_{i=1}^{n_k} (G \notin C_i).\]
+Then, for any $n\in \N$
+\begin{equation} \label{eqn:sumevents}
+P(G\models \phi) = \sum_{i=1}^{n_k} P(E_i)  + P(F),
+\end{equation}
+as the events $E_i$ together with $F$ form a partition of all the cases where $G$ satisfies $\phi$. \par
+
+Fix and index $i\in \{1, \dots, n_k\}$. From the property (1) of the classes $C_1,\dots, C_{n_k}$ 
+it follows that if $G$ and $H$ are random graphs, then
+\[\Ln P((G\models \phi) \wedge \neg(H\models \phi) \, | \, G\in C_i \wedge H\in C_i \, ) = 0.\]
+This is because $G$ and $H$ share a.a.s the same rank $k$ type if they both belong to $C_i$. 
+In consequence the limit
+\[ \Ln P(G\models \phi \, | \, G\in C_i )\] 
+is either zero or one, and 
+\begin{equation}\label{eqn:property1}
+\Ln P(E_i)= \Ln P(G\in C_i)\cdot P(G\models \phi \, | \, G\in C_i)= \text{ either } 0 \text{ or } \Ln P(G\in C_i).
+\end{equation} 
+\par 
+Also, as a consequence of property $(2)$ we obtain
+\[\Ln P(\bigwedge_{i=1}^{n_k} G \notin C_i)=0, \] 
+so
+\begin{equation}\label{eqn:property2}
+\Ln P(F)= \Ln P(\bigwedge_{i=1}^{n_k} G \notin C_i)\cdot P(G\models \phi \, | \, \bigwedge_{i=1}^{n_k} G \notin C_i)=0.  
+\end{equation}
+\par
+Taking limits in equation \ref{eqn:sumevents} and using equations \ref{eqn:property1} and \ref{eqn:property2} 
+we get
+\[ \Ln P(G\models \phi) = \sum\limits_{C_i\in \mathcal{C}} \Ln P(G \in C_i) ,\]
+where $\mathcal{C}$ is a (possibly empty) subset of $\{C_1,\dots, C_{n_k}\}$.
+Finally, because of property (3) for each $i$ the limit $\Ln P(G \in C_i)$ is 
+an expression in $\Theta$. Thus $\Ln P(G\models \phi)$ is a finite sum of expressions in $\Theta$
+and the theorem follows. \par
+
+The objective of next sections will be to define the classes $C_1,\dots, C_{n_k}$ and to show
+that they satisfy properties (1), (2) and (3). Later we will prove a stronger result, so we will
+allow ourselves to just sketch some of the proofs during this chapter.
+
+\section{Agreability Classes}
+
+It is known that $n^{-v/e}$ is the t
+hreshold probability for the appearance 
+of a balanced graph of density $v/e$. 
+In our case $v/e=1$, so in consequence any connected graph $H$
+with $e(H)< v(H)$ a.a.s will not appear 
+as a subgraphs of $G(n,\beta/n)$. It can be easily 
+shown that such graphs $H$ are exactly 
+the ones containing more than one cycle. \par
+
+If $H$ is a connected graph with $v=e$, then $H$ is an uni-cyclic graph.
+In this case, the number $X_H$ of copies of $H$ 
+in $G(n,\beta/n)$ will asymptotically have non-zero bounded expectancy $m$. 
+It does not take much work to prove, using Brun's sieve, 
+that $X_H$ converges in distribution to a Poisson 
+random variable with mean $m$ as $n$ goes to infinity.  \par
+
+Finally, if $H$ is a connected graph 
+with $v>e$ then it must be a tree. Here 
+the expected number of copies of $H$ 
+in $G(n,\beta/n)$ diverges asymptotically. 
+Informally, trees of any kind will occur arbitrarily often. \par
+
+This all means, in a sense, that a.a.s the only 
+difference between large graphs in $G(n,\beta/n)$
+lies in their uni-cyclic subgraphs. More precisely,
+because of the ``locality" of first order logic of quantifier 
+rank $k$ we will only be interested in the 
+``small`` neighborhoods of the ``short" cycles.  
+Thus, our goal will be to classify uni-cyclic graphs
+in a way that respects equivalence under first 
+order logic of quantifier rank $k$. \par
+~\par
+To make our classification suitable for proofs 
+involving E.F. games we need to work graphs to which we ``attach" labels. 
+We define the set of symbols $Const=\{c_i\}_{i\in \N}$ 
+as the set of constants. Also, we will denote by
+$Const_n$ the set $\{c_1,\dots, c_n\}$.
+
+\begin{definition} 
+	A \textbf{co-labeling} of a graph $G=(V,E)$ is a map 
+	$\sigma: D\rightarrow V$, where $D\subset C$ is a 
+	finite set of constant symbols. Given $c_i\in D$, 
+	we will say that the vertex $\sigma(c_i)$ is labeled $c_i$.
+	Equivalently, we can denote a labeling $\sigma$ as a tuple
+	$(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$ where each $c_{i_j}$
+	 is a constant symbol, and $x_j$ is the vertex
+	in $V$ labeled $c_{i_j}$.
+\end{definition}
+
+\begin{definition} 
+	A \textbf{co-labeled graph}\footnote{
+		Compare with \cite{lynch1992probabilities}, where they are called ``rooted graphs". 
+		}
+	$G=(V,E,c_{i_1}[x_1],\dots, c_{i_m}[x_m])$ 
+	is a graph $(V,E)$ together with a labeling 
+	$(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$. 
+\end{definition}
+
+To keep our notation compact we will often drop 
+he $x_i$'s and say $G=(V,$ $E,c_{i_1},\dots, c_{i_m})$. \par
+
+\begin{definition}
+Let $G$ be a co-labeled graph. A co-labeled subgraph $H$ of $G$ is
+a co-labeled graph such that $V(H)\subseteq V(G)$, $E(H)\subseteq E(G)$ and 
+all vertices in $V(H)$ have the same labels in $H$ and $G$. 
+\end{definition}
+
+An important abuse of notation we are going to make
+will be to identify the constants $c_i$ with their labeled
+vertices $\sigma(c_i)$. This way things like $c_i\sim c_j$ 
+will make sense. In this context, notice that the expression
+$c_i=c_j$ is ambiguous because the vertices labeled $c_i$ and $c_j$ 
+may be the same for some $i\neq j$, but 
+the constant symbols $c_i$ and $c_j$ will be equal only if $i=j$. 
+We will make sure to leave no room for ambiguity in this situations. \par
+
+\begin{propdef}
+	Let $G=(V,E,\clist)$ be a connected co-labeled graph. Then it has a unique minimal
+	connected co-labeled subgraph $H$ containing all its constants and cycles.
+	We will call the \textbf{center} of $G$ to such subgraph and denote it by $Center(G)$.
+	If $\bar{G}$ is an arbitrary co-labeled graph, then its center $Center{\bar{G}}$ will
+	be the union of the centers of its connected components. 
+\end{propdef}
+\begin{proof}
+	TO DO
+\end{proof}
+
+For an arbitrary co-labeled graph we define the metric $d(\cdot,\cdot)$ on $V(G)$ 
+as the one such that $d(x,y)$ is the minimum length of a path connecting
+$x$ and $y$ in $G$ or $\infty$ if such path does not exist. 
+For any vertex $x\in V(G)$ and $r\in \N$ we define the co-labeled
+subgraph $N(x;r)$ as the ball of radius $r$ centered at $v$. 
+That is, the induced subgraph with vertex set
+\[ V(N(x;r))= \{\, y\in V \, | \, d(x,y)\leq  r \,	\}.\] 
+In a similar vein, given $X\subseteq V(G)$ we define its neighborhood of radius $r$ as
+the induced co-labeled subgraph $N(X;r)$ whose vertex set is
+\[ V(N(X;r))= \{\, y\in V \, | \, \forall x\in X: \, \,  d(x,y)\leq  r \,	\}.\]  
+\par
+
+Let $G=(V,E)$, and $V^\prime\subseteq V$. Another important abuse 
+of notation we will make is writing $H=(V^\prime, E)$ 
+for a subgraph $H$ to mean that the edge set of $E(H)$ is the one
+induced by $E(G)$ on $V^\prime$.
+
+\begin{definition} 
+	A \textbf{rooted tree} $T=(V,E,x)$ is a tree 
+	$(V,E)$ with distinguished vertex $x\in V$ with we will call 
+	\textbf{root} of the tree.
+\end{definition}
+
+\begin{propdef}
+	Let $G=(V,E,\clist)$ be a connected graph and $x\in V$. 
+	Then define $Tree(x,G)$	as the rooted tree
+	\[Tree(x,G) = (V_x,E,x),\] where
+	\[V_x= \{\, y\in V \, | \,\,d(Center(G),y) = d(Center(G),x) + d(x,y) \}.\]
+
+\end{propdef}
+\begin{proof}
+	TO DO
+\end{proof}
+
+The radius $r(T)$ of a rooted tree $T=(V,E,x)$
+is the maximum distance between its root $x$ and any other of
+its vertices. The branches of $T$ are the rooted trees of the form
+$Tree(y,T)$, where $y\sim x$. We will denote by $Br(T)$ the set of
+branches of $T$. \par
+
+We begin by defining an equivalence relation between rooted 
+trees for each quantifier rank $k$.
+
+\begin{definition} 
+	Let $k\in \N$ with $k\geq 1$. The \textbf{k-morphism} equivalence relation
+	$\morph{k}$ between
+	co-labeled graphs is the one inductively defined as follows:
+	\begin{itemize}
+		\item If $T_1, T_2$ are rooted trees of radius $0$ -i.e., they
+		consist only of their roots- they are $k$-morphic. 
+		\item Let $T_1, T_2$ be rooted trees of radius $r$ whose 
+		rots have the same label. Then $T_1 \morph{k} T_2$ if 
+		for any $k$-morphism class $C$ of trees with
+		radius less than $r$ and root either
+		\begin{center}
+			\vspace{-0.2cm}
+			``$T_1$ and $T_2$ have the same number of branches of type $C$"
+		\end{center}
+		\vspace{-0.3cm}
+		\[ |Br(T_1)\cap C| = |Br(T_2)\cap C|,\]
+		or 
+		\begin{center}
+			\vspace{-0.2cm}
+			``$T_1$ and $T_2$ have both more than $k$ branches of type $C$"
+		\end{center}
+	\vspace{-0.3cm}
+		\[ |Br(T_i)\cap C| \geq k+1 \text{ for } i=1,2. \]
+	\end{itemize} 
+\end{definition}
+
+It follows from the definition that $k$-morphic trees have the same radius. 
+It is also easy to check that the $k$-morphism relation is indeed an equivalence one.
+
+\begin{proposition}
+	For all $k,r\in N$ and with $k\geq 1$, the set of classes of $k$-morphic trees
+	with radius lesser or equal than $r$ is finite.
+\end{proposition}
+\begin{proof}
+TO DO
+\end{proof}
+
+We define now the $k$-morphism relation for arbitrary co-labeled graphs. 
+%If $G^1=(V^1,E^1,\clist)$ and $G^2=(V^2,E^2,\clist)$ are co-labeled graphs with
+%the same constants, to avoid confusion we will denote by $c_{i_j}^1$ and $c_{i_j}^2$
+%the vertices labeled $c_{i_j}$ in $G^1$ and $G^2$ respectively.
+
+\begin{definition}
+	Let $G^1=(V^1,E^1,c_{i_1}[x^1_1],\dots, c_{i_m}[x_m^1])$ and  $G^2=(V^2,E^2,c_{i_1}[x^1_2],$ 
+	$\dots, c_{i_m}[x_m^2])$ be co-labeled graphs with the same constant symbols. 
+	We will say that they are $k$-morphic (denoted by $G^1 \morph{k}G^2$) if there is
+	a bijection $f: V(Center(G^1))\rightarrow V(Center(G^2))$ such that
+	\begin{itemize}
+		\item ``$f$ preserves edges"
+		\[\forall x,y\in V(Center(G^1)): \quad  x\sim y \iff f(x)\sim f(y). \]
+		\item ``$f$ preserves labels"
+		\[\forall j\in \{1,\dots,m\}: \quad f(x^1_j) = x^2_j.\]
+		\item ``$f$ preserves $k$-morphism classes of trees"
+		\[\forall x\in V(Center(G^1)): \quad  Tree(x,G^1)\morph{k} Tree(f(x),G^2).\]
+	\end{itemize}
+	In this case we will say that $G^1 \morph{k} G^2$ via $f$. 	
+\end{definition}
+
+We are going to show that the rank $k$ type of a random graph a.a.s only 
+depends on the neighborhoods of its small cycles. In consequence the following definition
+is motivated:
+
+\begin{definition} 
+	Let $G=(V,E,\clist)$ be a co-labeled graph. Then its core of radius $r$, $Core(G,r)$
+	is the co-labeled subgraph $N(X;r)$, where $X$ is the union of the (vertex sets of the)
+	cycles in $G$ with size at most $2r+1$ and all of the labeled vertices in $G$. 
+\end{definition}
+
+\bibliography{biblio}
+\bibliographystyle{unsrt}
 \end{document}

### 2019-06-16 TFM.tex
Sigo

@@
 \newcommand{\N}{\mathbb{N}}
+\newcommand{\Hc}{\mathcal{H}}
 \newcommand{\Lan}{\mathcal{L}}
@@
 \newcommand{\morph}[1]{\stackrel{#1}{\simeq}}
+\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
+\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
 
@@
 \begin{definition} 
-	A \textbf{co-labeled graph}\footnote{
+	A \textbf{graph with constants}\footnote{
 		Compare with \cite{lynch1992probabilities}, where they are called ``rooted graphs". 
 		}
-	$G=(V,E,c_{i_1}[x_1],\dots, c_{i_m}[x_m])$ 
-	is a graph $(V,E)$ together with a labeling 
+	$G(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$ 
+	is a graph $G$ together with a co-labeling 
 	$(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$. 
@@
 To keep our notation compact we will often drop 
-he $x_i$'s and say $G=(V,$ $E,c_{i_1},\dots, c_{i_m})$. \par
+he $x_i$'s and say $G(c_{i_1},\dots, c_{i_m})$. \par
 
 \begin{definition}
-Let $G$ be a co-labeled graph. A co-labeled subgraph $H$ of $G$ is
-a co-labeled graph such that $V(H)\subseteq V(G)$, $E(H)\subseteq E(G)$ and 
+Let $G$ be a graph with constants. A subgraph $H$ of $G$ is
+a graph with constants such that $V(H)\subseteq V(G)$, $E(H)\subseteq E(G)$ and 
 all vertices in $V(H)$ have the same labels in $H$ and $G$. 
@@
 \begin{propdef}
-	Let $G=(V,E,\clist)$ be a connected co-labeled graph. Then it has a unique minimal
-	connected co-labeled subgraph $H$ containing all its constants and cycles.
+	Let $G=(V,E,\clist)$ be a connected graph with constants. Then it has a unique minimal
+	connected subgraph $H$ containing all its constants and cycles.
 	We will call the \textbf{center} of $G$ to such subgraph and denote it by $Center(G)$.
-	If $\bar{G}$ is an arbitrary co-labeled graph, then its center $Center{\bar{G}}$ will
+	If $\bar{G}$ is an arbitrary graph with constants, then its center $Center{\bar{G}}$ will
 	be the union of the centers of its connected components. 
@@
 
-For an arbitrary co-labeled graph we define the metric $d(\cdot,\cdot)$ on $V(G)$ 
+For an arbitrary graph with constants we define the metric $d(\cdot,\cdot)$ on $V(G)$ 
 as the one such that $d(x,y)$ is the minimum length of a path connecting
@@
 	$\morph{k}$ between
-	co-labeled graphs is the one inductively defined as follows:
+	graph with constantss is the one inductively defined as follows:
 	\begin{itemize}
@@
 
-We define now the $k$-morphism relation for arbitrary co-labeled graphs. 
-%If $G^1=(V^1,E^1,\clist)$ and $G^2=(V^2,E^2,\clist)$ are co-labeled graphs with
+We define now the $k$-morphism relation for arbitrary graph with constantss. 
+%If $G^1=(V^1,E^1,\clist)$ and $G^2=(V^2,E^2,\clist)$ are graph with constantss with
 %the same constants, to avoid confusion we will denote by $c_{i_j}^1$ and $c_{i_j}^2$
@@
 	Let $G^1=(V^1,E^1,c_{i_1}[x^1_1],\dots, c_{i_m}[x_m^1])$ and  $G^2=(V^2,E^2,c_{i_1}[x^1_2],$ 
-	$\dots, c_{i_m}[x_m^2])$ be co-labeled graphs with the same constant symbols. 
+	$\dots, c_{i_m}[x_m^2])$ be graph with constantss with the same constant symbols. 
 	We will say that they are $k$-morphic (denoted by $G^1 \morph{k}G^2$) if there is
@@
 \begin{definition} 
-	Let $G=(V,E,\clist)$ be a co-labeled graph. Then its core of radius $r$, $Core(G,r)$
+	Let $G=(V,E,\clist)$ be a graph with constants. Then its core of radius $r$, $Core(G,r)$
 	is the co-labeled subgraph $N(X;r)$, where $X$ is the union of the (vertex sets of the)
@@
 
+\chapter{First Order Logic of Sparse Random General Hypergraphs}
+
+\section{General Hypergraphs}
+
+$\forall n\in N: \quad [n]:= \{1,\dots, n\}$\par
+$S_n:$ symmetric group on $n$ elements. \par
+Let $X$ be a set, then:
+\begin{itemize}
+	\item $\Delta\subset X^2:$ $\Delta$ is the diagonal subset. $\Delta: \{(a,a)\in X^2 \}$.
+	\item $S_n$ acts on $X^n$ in the obvious way. 
+	\item When the subgroup $\phi$ is understood or (is not relevant) $\langle x_1,\dots,x_n\rangle$
+	denotes the equivalence class of $(\vlst{x}{n})$ in $X^n/\phi$.
+\end{itemize}
+\par
+
+\begin{definition}
+	Let $V$ be a finite set. Given a natural number $a\in \N$, a group $\phi\leq S_a$ and a subset
+	$R\subseteq [a]^2 \setminus \delta$, the total (hiper-)edge set of size $a$, symmetry group $\phi$ and
+	restrictions $R$ is the set:
+	\[ \mathcal{H}_{V,a}^{\phi,R}= V^n/\phi \, \, \setminus \{\,  \langle 
+	x_1, \dots,x_n\rangle
+	 \in V^n/\phi  \, \, | \, \, x_i=x_j \, \text{for some } (i,j)\in R \} \]
+
+\end{definition}
+
+\begin{definition}
+	An hypergraph $(V,H_1,\dots, H_l)$ with edge sizes $a_1,\dots,a_l$, 
+	symmetry groups $\phi_1,dots,\phi_1$ and restrictions $R_1,\dots,R_l$ consists of
+	\begin{itemize}
+		\item A finite vertex set $V$.
+		\item For $i=1,\dots,l$, an edge set $H_i\subseteq \mathcal{H}_{V,a_i}^{\phi_i,R_i}$.
+	\end{itemize}
+\end{definition}
+
+\begin{definition} 
+	Random model $G(n, p_1,\dots, p_l)$ with edge sizes $a_1,\dots,a_l$, 
+	symmetry groups $\phi_1,dots,\phi_1$ and restrictions $R_1,\dots,R_l$:
+	\begin{itemize}
+		\item We obtain a hypergraph $(V,H_1,\dots, H_l)$ with $V=[n]$
+		\item The probability of each edge $e\in \mathcal{H}_{V,a_i}^{\phi_i,R_i}$
+		is $p_i$ independently. 
+	\end{itemize}
+\end{definition}
+
+From now on we fix the edge sizes $a_1,\dots,a_l$, 
+symmetry groups $\phi_1,dots,\phi_1$ and restrictions $R_1,\dots,R_l$. \par
+
+In a graph $G(V,E_1,\dots, E_l)$, the type of an edge $e$ is the index
+$i$ such that $e\in E_i$.
+
+The language is the first order relational 
+language with relations $R_1,..., R_l$ of arities
+$a_1,\dots, a_l$ respectively. The interpretation on 
+$(V,H_1,\dots, H_l)$ is the evident one. \par
+
+\begin{definition}
+	The characteristic $ch(G)$ of an hypergraph $G=(V,E_1,\dots,E_l)$ is
+	\[ \left( \sum_{i=1}^l |E_i|(a_i-1)\right) -	|V|  .\]
+	An hypergraph is c-balanced if it contains no subgraph of
+	greater characteristic than itself. 
+\end{definition}
+
+\begin{proposition}
+	A connected graph cannot have characteristic lesser than $-1$.
+\end{proposition}
+
+\begin{definition}
+	A unicycle is a connected c-balanced graph with characteristic $0$.
+\end{definition}
+
+\begin{definition} A cluster is a minimal c-balanced graph.
+\end{definition}
+
+Remark: Note that clusters have to be connected.
+
+\begin{definition}
+	A cycle is a minimal unicycle, or equivalently a characteristic $0$ cluster.  
+\end{definition}
+
+\begin{proposition}
+	Any unicycle contains exactly one cycle. 
+\end{proposition}
+
+\begin{definition} 
+	A (hiper)forest is a graph with no clusters. A (hiper)tree is a connected forest.
+\end{definition}
+
+\begin{definition} 
+	A path between $x$ and $y$ is a connected graph containing both $x$ and $y$
+	that is minimal among the ones with those properties. 
+\end{definition}
+
+\begin{proposition} There is a unique path between any two vertices of a tree. 
+\end{proposition}
+
+We define the constant set $Const:=\{c_i\}_{i\in \N}$.
+
+\begin{definition} 
+	As before, a (hiper)graph with constants $G(\clist)$ is a hypergraph 
+	$G$ together with a co-labeling. 
+\end{definition}
+
+\begin{definition}
+	The center of a connected graph with constants $G(\clist)$ is its minimal 
+	connected subgraph containing all the constants and clusters. If $G(\clist)$
+	is not connected then its center is the union of the centers of its connected
+	components.   
+\end{definition}
+
+We define a distance over $G(\clist)$.
+\[ d(x,y)= (\text{minimum size of a connected graph containing }x \text{ and } y) - 1 \]
+If such graph does not exist we define $d(x,y)=\infty$.\par
+
+Given $x\in V(G)$ and $X\subseteq V(G)$ we define $N(x;r)$ and $N(X;r)$ as
+\[ N(x;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | dist(x,y)\leq r \, \} \]
+\[ N(X;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | dist(X,y)\leq r \, \}. \]
+
+\begin{definition}
+	 A rooted (hiper)tree is a tree with a distinguished vertex called root.
+	 The radius of the tree is the maximum distance between its root and any
+	 of its vertices.  
+\end{definition}
+
+In a rooted tree $(T,x)$ all the (hiper)edges can be rooted in a canonical way. 
+The root of an edge $e$ is the vertex $y\in e$ such that $dist(x,y)=dist(x,e)$.
+
+\begin{definition}
+	Let $G(\clist)$ be a graph with constants and $x\in V(G)$. Then
+	$Tree(x,G)=(G[V_x],x)$, where
+	\[ V_x= \{\, y\in V \, | \, dist(Center(G),y)= dist(Center(G),x)+ dist(x,y) \,	 \}. \]
+\end{definition}
+
+\begin{definition} 
+	The $k$-morphism equivalence relation $\morph{k}$ between rooted trees,
+	and the $\stackrel{k}{\sim}$ relation for rooted (hyper)edges are defined inductively as follows:
+	\begin{itemize}
+		\item If $T_1$ and $T_2$ are radius $0$ trees then they consist only of
+		their roots and $T_1\morph{k} T_2$. 
+		\item 
+		If $e_1$ and $e_2$ are edges in rooted trees $T_1$,$T_2$ of radii at most $r$,
+		then $e_1\stackrel{k}{\sim} e_2$ if $e_1$ and $e_2$ are edges of the same 
+		type and $e_1=[x_1,\dots, x_m]$, $e_2=[y_1,\dots,y_m]$ in a way that
+		\begin{itemize}
+			\item $x_i$ is the root of $e_1$ if and only if $y_i$ is the root of $e_2$.
+			\item If $x_j$ is not the root of $e_1$, then
+			$Tree(x_j, T_1)\morph{k} Tree(y_j, T_2)$.
+		\end{itemize}
+		\item If $T_1$ and $T_2$ are trees of radii at most $r$ and roots $x$ and $y$,
+		then $T_1\morph{k} T_2$ means that for any $\stackrel{k}{\sim}$ class
+		of edges $C$ either
+		\begin{itemize}
+			\item the number of edges in $T_1$ of type $C$ containing $x$ is the same
+			as the number of edges in $T_2$ of tipe $C$ containing $y$, or
+			\item both $T_1$ and $T_2$ contain no less than $k+1$ edges of type $C$
+			containing $x$ and $y$ respectively. 
+		\end{itemize}
+
+	\end{itemize}
+
+\end{definition}
+
+\begin{definition} 
+	Let $G_1(\clist)$ and $G_2(\clist)$ be graphs with the same constants. Then
+	we say $G_1(\clist)\morph{k}G_2(\clist)$ if there is a bijection 
+	$f:V(Center(G_1))\rightarrow V(Center(G_2))$ such that
+	\begin{itemize}
+		\item $f(c^1_i)=c^2_i$ for all constants, and
+		\item $Tree(x,G_1)\morph{k} Tree(f(x),G_2)$ for all $x\in V(Center(G_1))$.
+	\end{itemize}
+\end{definition}
+
+The diameter of a (hiper)graph is the maximum distance between any two of its vertices.
+
+\begin{definition} 
+	Let $G(\clist)$ be a graph with constants. We define $Core(G,r)$ to be
+	$N(X,r)$ where $X$ is the union of constants and clusters of diameter at most $r$. 
+\end{definition}
+
+\begin{definition} 
+	A (hyper)graph $G$ is $r$-simple if $Core(G,r)$ is a union of unicycles. 
+\end{definition}
+
+\begin{definition}
+	A (hyper)graph $G$ is $i,j,r$-rich for some $i,j,r\in \N$, if for any rooted tree $T$
+	of radius at most $r$ there are $x_1,\dots,x_i\in V(G)$ such that
+	\begin{itemize}
+		\item The $N(x_l;r)$'s are disjoint.
+		\item The $N(x_l;r)$'s do not intersect $Core(G,r)$
+		\item $N(x_l;r)(x_l) \morph{j} T$.		
+	\end{itemize} 
+\end{definition}
+
+\begin{theorem}
+	If $G_1(c_1,\dots,c_m)\morph{k} G_2(c_1,\dots,c_m)$, then for any $x\in V(G_1)$ such 
+	that $d(x,Center(G_1))\neq \infty$ there is a $y\in V(G_2)$ such that
+	$G_1(c_1,\dots,c_m,c_{m+1}[x])\morph{k-1} G_2(c_1,\dots,c_m,c_{m+1}[y])$.
+\end{theorem}
+
+\begin{theorem}
+	If $Core(G_1,r)\morph{k} Core(G_2,r)$ then for any $s<r$, $Core(G_1,s)\morph{k} Core(G_2,s)$.
+\end{theorem}
+
+\begin{definition} 
+	Two graphs with constants $G_1$ and $G_2$ are $k$-agreeable if for each $k$-morphism 
+	equivalence class $C$ they either have the same number of connected components of type
+	$C$ or they both have no less than $k+1$ components of type $C$. 
+\end{definition}
+
+\begin{theorem} 
+	Let $G_1, G_2$ be graphs with constants satisfying:
+	\begin{itemize}
+		\item They are both $(k, k, 3^k)$-rich.
+		\item $Core(G_1,3^k)$ is $k$-agreeable with $Core(G_2,3^k)$.
+	\end{itemize} 
+	Then the $G_1$ and $G_2$ share the same rank $k$ type.
+\end{theorem}
+
+From now on fix $\beta_1,\dots,\beta_l$ positive real numbers.
+
+\begin{theorem} For any $r$,
+	\[\Ln Pr(G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1} ) \text{ is }r \text{-simple})=1 .\]
+\end{theorem}
+
+Define the families of expressions with arguments $\beta_1,\dots, \beta_l$: 
+$\Lambda$, $\mathcal{E}$ and $\Theta$.
+
+\begin{theorem} 
+	Let $\phi(x_1,\dots, x_l)$ be an open formula, and let $k,r,s\in \N$ $s\leq l$. Then
+	\[ \Ln Pr(\bigwedge_{i=i}^s Tree(x_i,G)\morph{k} )   	\]
+
+\end{theorem}
+
 \bibliography{biblio}

### 2019-06-19 TFM.tex
Un poco más

@@
 
+\begin{lemma}
+	Let $H$ be a cluster with $ch(H)>0$, and let $X_n$ be the
+	random variable that counts the number of times that $H$ appears
+	as a subgraph of $G(n,p(n))$. Then
+	\[\Ln Pr(X_n>0)=0. \]
+\end{lemma}
+\begin{proof}
+	Let $v=|V(H)|$ and $e_i=|E_i(H)|$ for $i=1,\dots, l$. 
+	The criticality condition on $H$ means 
+	\[ \langle e, a-1 \rangle - v > 0 .\]
+	Chose a ordering of the vertices in $H$. 
+	For any ordered sequence of vertices $S=(x_1, \dots, x_v)$, 
+	let $X_{n,S}$ be the indicator variable that equals $1$ if $H$
+	is a subgraph of $G[S]$ (in a way that respects the ordering) and
+	$0$ otherwise. Clearly $X_n$ is the sum of all the $X_{n,S}$'s, so
+	\[ E(X_n)= \frac{n(n-1)\cdots (n-v+1)}{b} \prod_{i=1}^{l}
+	\left( \frac{c_i}{n^{a_1-1}}\right) ^{e_i}, \] 
+	where $b$ is the carnality of $H$'s group of isomorphisms. 
+	Then because of the criticality hypothesis
+	\[ \Ln E(X_n)=0, \]
+	and using the first moment method 
+	the result follows. 
+\end{proof}
+
+\begin{lemma}
+	Let $H$ be a critical graph of characteristic $r$.
+	Then $H$ contains a critical subgraph with size no greater than
+	$(a+2)(r+1)+2a$, where $a$ is the largest edge size in $H$. 
+\end{lemma}
+\begin{proof}
+	Choose $x\in V(H)$. Successively remove from $H$ edges $e$
+	such that $dist(x, e)$ is maximum until the resulting graph 
+	$H^\prime$ has characteristic no greater than $0$. We have two cases:
+	\begin{itemize}
+		\item $ch(H^\prime)=1$. Let $e=[x_1, \dots, x_b]$ be
+		the last removed edge and
+		$e\cap H^\prime=\{ x_{i_1}, \dots, x_{i_c}\}$.
+		For any $j=1,\dots, c$ choose 
+		$P_j$ a path of size no greater than $r+1$ joining
+		$x$ and $x_{i_j}$ in $H^\prime$.   
+		Then $P_1\cup \dots P_c \cup e$ is a critical subgraph of $H$
+		of size less than $a(r+1) + a< (a+2)(r+1) + 2a$.
+		\item $ch(H^\prime)=0$. Let $e_1=[x_1, \dots, x_{b_1}]$ be the
+		last removed edge. Continue removing the edges of $H^\prime$ 
+		that are at maximum distance from $x$ until you obtain 
+		$H^{\prime \prime}$ with $ch(H^\prime)=-1$. Let 
+		$e_2=[y_1, \dots, y_{b_1}]$ be the last removed edge.
+		As before, let $e_1\cap H^\prime=\{ x_{i_1}, \dots, x_{i_c}\}$
+		and for $j=1,\dots, c$ let $P_j$ a path of size no greater than $r+1$ 
+		joining	$x$ and $x_{i_j}$ in $H^\prime$
+		Then $e_2 \cup H^{\prime \prime}=\{ y_{i_1}, y_{i_2}  \}$.
+		Let $Q_1, Q_2$ be paths size no greater than $r+1$ from
+		$x$ to $y_{i_1}$ and $y_{i_2}$ in $H^{\prime \prime}$.
+		Then $Q_1 \cup Q_2 \cup e_2$ is a graph of characteristic $0$ 
+		and size less than $2r+2 + a$,
+		and $Q_1\cup Q_2\cup P_1 \cup \dots \cup P_c \cup e_1 \cup e_2$ 
+		is a critical graph	with size less than $(2+a)(r+1) + 2a$	
+	\end{itemize} 
+\end{proof}
+
+\begin{corollary}
+	Let $A_n$ be the event that $G(n,p(n))$ contains critical 
+	subgraph with diameter no greater than $r$. Then
+	\[ \Ln Pr(A_n)=0. \]
+\end{corollary}
+\begin{proof}
+	If a random graph contains $G$ such critical graph, then by the previous
+	lemma it has to contain a critical graph of size less than some constant $M$.
+	The number of critical graphs of such size is finite and the probability 
+	that any one of those appears as a subgraph of $G$ is asymptotically zero.	 
+\end{proof}
+
 \begin{theorem} For any $r$,
@@
 Define the families of expressions with arguments $\beta_1,\dots, \beta_l$: 
-$\Lambda$, $\mathcal{E}$ and $\Theta$.
+$\Lambda$, $\mathcal{E}$ and $\Theta$. \par
+For any sentence $\phi$ we use the notation 
+$Pr_n(\phi):=Pr(G\models \phi)$. \par
+For any F.O. formula $\phi(x_1,\dots,x_l)$ with free variables 
+$x_1, \dots, x_l$, we define $Pr_n(\phi(x_1,\dots,x_l))=
+\sum_{G\models \phi(a_1,\dots,a_l)} Pr_n(G) $, 
+where $a_1, \dots, a_l$ are fixed natural numbers in $[n]$.
 
 \begin{theorem}
-	Let $\phi(x_1,\dots, x_l)$ be an open formula, and let $k,r,s\in \N$ $s\leq l$. Then
-	\[ \Ln Pr(\bigwedge_{i=i}^s Tree(x_i,G)\morph{k} )   	\]
 
+\end{theorem}
+
+\begin{theorem} 
+	Let $\phi(x_1,\dots, x_l)$ be a consistent open formula, and let $k,r,s\in \N$ $s\leq l$. Then for any $k$-morphism classes of trees with radii
+	at most $r$ the limit
+	\[ \Ln Pr(\bigwedge_{i=i}^s Tree_r(x_i,G)\in C_i \, | \, \phi(x_1,\dots, x_l) \,)\]
+	exists and belongs to $\Lambda$.	
 \end{theorem}

### 2019-06-21 TFM.tex
Demo acabada

@@
 \begin{definition}
-	A (hyper)graph $G$ is $i,j,r$-rich for some $i,j,r\in \N$, if for any rooted tree $T$
-	of radius at most $r$ there are $x_1,\dots,x_i\in V(G)$ such that
+	A (hyper)graph $G$ is $j,r$-rich for some $j,r\in \N$, if for any rooted tree $T$
+	of radius at most $r$ there are $x_1,\dots,x_j\in V(G)$ such that
 	\begin{itemize}
@@
 
+\begin{lemma} 
+	Let $(T_1,x)$ and $(T_2,y)$ be rooted trees such that for some $k>0$ 
+	$T_1 \morph{k} T_2$. Then, for any $0\leq j < k$, it is satisfied
+	$T_1 \morph{j} T_2$.
+\end{lemma}
+\begin{proof}
+	Fix $j<k$. The proof is by induction on the radius of $T_1$ and $T_2$.
+	\begin{itemize}
+		\item If they have radius at most $0$ they are $j$-morphic by definition. 
+		\item Suppose now that they have radii at most $r$. Let $e_1$ be an edge with root
+		$x$ in $T_1$ and $e_2$ be an edge of root $y$ in $T_2$ such that $e_1 \morph{k} e_2$.
+		Then $e_1=[x_1,\dots,x_a]$ and $e_2=[y_1,\dots,y_a]$ for some vertices such that for all
+		$i=1,\dots, a$ either 
+		\begin{itemize}
+			\item $Tree(x_i)\morph{k} Tree(y_i)$, and because of the induction hypothesis 
+			$Tree(x_i)\morph{j} Tree(y_i)$. 
+			\item Or $x_i=x$ and $y_i=y$.
+		\end{itemize}
+		In consequence $e_1\morph{j} e_2$. Then, any class $C$ 
+		of $j$-morphic edges in trees of radius at most
+		$r$ is union of classes $D_1,\dots, D_s$ of $k$-morphic edges in 
+		trees of radius at most $r$. Then
+		\[(T_1,C)=\sum_{i=1}^s (T_1, D_i) \text{, and }	(T_2,C)=\sum_{i=1}^s (T_2, D_i).\]	
+	 	Both of the above sums coincide if all the $(T_1, D_i)$'s are not greater than $k$ or
+	 	both are greater than $k$ otherwise. As $j\leq k$ this implies
+	 	\[\text{Either }(T_1,C)=(T_2,C) \text{ or } (T_1,C),(T_2,C)\geq j+1 ,\]
+	 	and $T_1\morph{j}T_2$. 		
+	\end{itemize}
+\end{proof}
+
+\begin{corollary}
+	Let $G_1(c_1,\dots, c_t)$, and $G_2(c_1,\dots,c_t)$ be graphs
+	with constants such that $G_1(c_1,\dots, c_t)\morph{k}G_2(c_1,\dots,c_t)$.
+	Then, for any $j<k$, $G_1(c_1,\dots, c_t)\morph{j}G_2(c_1,\dots,c_t)$.
+\end{corollary}
+
+\begin{lemma}
+	Let $(T_1,x)$ and $(T_2,y)$ be rooted trees such that for some $k>0$ 
+	$T_1 \morph{k} T_2$. Then, for any $r\geq 0$, $N(x;r)\morph{k} N(y;r)$.
+\end{lemma}
+\begin{proof}
+	The proof is by induction on the radius of $T_1$ and $T_2$.
+	\begin{itemize}
+		\item If they have at most radius $0$ the statement is vacuously true. 
+		\item Suppose now that they have radii at most $r$. Let $e_1$ be an edge with root
+		$x$ in $N(x;r)$ and $e_2$ be an edge of root $y$ in $N(y;r)$ such that $e_1 \morph{k} e_2$
+		when both edges are considered in $T_1$ and $T_2$ respectively. We want to prove that
+		$e_1 \morph{k} e_2$ as well when they are considered as edges in $N(x;r)$ and $N(y;r)$.
+		By definition we can write $e_1=[x_1,\dots,x_a]$ and 
+		$e_2=[y_1,\dots,y_a]$ for some vertices such that for all
+		$i=1,\dots, a$ either 
+		\begin{itemize}
+			\item $Tree(x_i)\morph{k} Tree(y_i)$, and because of the induction hypothesis 
+			\[Tree(x_i)\cap N(x_i;r-a) \morph{k} Tree(y_i)\cap N(y_i;r-a).\] 
+			\item Or $x_i=x$ and $y_i=y$.
+		\end{itemize}
+		In consequence $e_1 \morph{k} e_2$ as edges in $N(x;r)$ and $N(y;r)$. 
+		This implies that for any $k$-morphism class of rooted edges $C$ of trees with
+		radii less than $r$ there are $k$-morphism classes $D_1,\dots,D_c$ of rooted edges
+		of trees with radii at most $r$ such that
+		\[ (N(x;r),C) = (T_1, D_1)\cup \dots \cup (T_1,D_a), \]
+		and 
+		\[(N(y;r),C) = (T_2, D_1)\cup \dots \cup (T_2,D_a).\]
+		And we can easily obtain that either
+		$|(N(x;r),C)|=|(N(y;r),C)|$ or $|(N(x;r),C)|,$ $
+		|(N(y;r),C)|\geq k+1$. 	Thus $N(x;r)\morph{k} N(y;r)$.
+	\end{itemize}	
+\end{proof}
+
+\begin{lemma}
+	Let $(T_1,x),(T^\prime_1,x), (T_2, y)$ and $(T^\prime_2,x)$ 
+	be rooted trees satisfying $T_1\morph{k} T_2$.
+	$T_1^\prime\morph{k} T_2^\prime$ for some 
+	$k\geq 0$ and $V(T_1)\cap V(T_1^\prime)=x$, 
+	$V(T_2)\cap V(T_2^\prime)=y$. Then
+	$T_1\cup T_1^\prime \morph{k} T_2\cup T_2^\prime$.
+\end{lemma}
+\begin{proof}
+	Let $C$ be a $k$-morphism class of rooted edges. Then
+	\[|(T_1\cup T_1^\prime,C)|= |(T_1,C)|+ |(T_1^\prime,C)|, \text{and }\]
+	\[|(T_2\cup T_1^\prime,C)|= |(T_2,C)|+ |(T_2^\prime,C)|.\]
+	And it follows easily that either
+	\[|(T_1\cup T_1^\prime,C)|=|(T_2\cup T_2^\prime,C)|,\]
+	or both quantities are greater than $k$. 
+\end{proof}
+
+\begin{lemma} 
+	Let $(T_1,x)$, $(T_2, y)$ be rooted trees and let 
+	$(T^\prime_1,x)$ and $(T^\prime_2,y)$ be sub-trees of 
+	$T_1$ and $T_2$ respectively. Let $k\geq 0$.
+	If there is an isomorphism 
+	$f:T^\prime_1 \rightarrow T^\prime_2$ such that $f(x)=y$ and
+	for all $x_1\in V(T^\prime_1)$
+	\[ Tree(x_1,T^\prime_1)\morph{k} Tree(f(x_1),T^\prime_2),\]
+	then $T_1\morph{k}T_2$. 
+\end{lemma}
+\begin{proof}
+	The proof is, again, by induction on the radius of $T^\prime_1$ and $T^\prime_2$.
+	\begin{itemize}
+		\item If $T^\prime_1$ and $T^\prime_2$ have radius zero, then they consist only of
+		$x$ and $y$ respectively. 
+		\item Suppose that $T^\prime_1$ and $T^\prime_2$ have at most $r$. Let $x_1\neq x$ be
+		a vertex in an edge $e$ rooted at $x$ such that $e\in T^\prime_1$.
+		Then $Tree(x_1, T_1)$ and $Tree(x_1,T^\prime_1)$ satisfy the hypothesis of the lemma,
+		and the radius of $Tree(x_1,T^\prime_1)$ is strictly less than $r$. Then by the induction
+		hypothesis $Tree(x_1, T_1)\morph{k} Tree(f(x_1),T_2)$. In consequence $e\morph{k}f(e)$
+		and using the previous lemma successively we get $T_1\morph{k} T_2$.
+	\end{itemize}
+\end{proof}
+
+\begin{theorem}
+	Let $G_1(c_1,\dots, c_t)$, and $G_2(c_1,\dots,c_t)$ be graphs
+	with constants such that for some $r\in N$
+	\[ Core(G_1(c_1,\dots, c_t);r)\morph{k} Core(G_2(c_1,\dots,c_t);r)\]
+	through $f$. 
+	Then, for any $s<r$
+	\[ Core(G_1(c_1,\dots, c_t);s)\morph{k} Core(G_2(c_1,\dots,c_t);s).\]
+\end{theorem}
+\begin{proof}
+	Fix $s<r$. Let us introduce some notation
+	\[ H_i:= Core(G_i(c_1,\dots, c_t);r) \quad \text{for }i=1,2.\]
+	\[ H^\prime_i:= Core(G_i(c_1,\dots, c_t);s) \quad \text{for }i=1,2.\]
+	One can check $H^\prime_i\subseteq H_i$ for $i=1,2$, and that the isomorphism 
+	$f:Center(H_1)\rightarrow Center(H_2)$ restricts to one between
+	$Center(H^\prime_1)$ and $Center(H^\prime_2)$. Let $v\in Center(H^\prime_1)$.
+	Let $T=Tree(v,H^\prime_1)\cap Center(H_1)$. It is not hard to see that $T$ is connected 
+	and in consequence is a tree. The following identity holds:
+	\[ Tree(v,H^\prime_1)= (Tree(v,H_1)\cap N(v;s)) \cup Tree(T,H^\prime_1) \]
+	Also, for any $w\in V(T)$
+	\[Tree(w,Tree(v,H^\prime_1),T) = Tree(w,H_1)\cap N(w; s-dist(Center(H^\prime_1),w)).\]
+	So, by lemma REF 
+	\[Tree(w,Tree(v,H^\prime_1),T)\morph{k}Tree(f(w),Tree(f(v),H^\prime_2),f(T)).\]
+	In consequence, by lemma REF,
+	\[Tree(T,H^\prime_1)\morph{k} Tree(f(T),H^\prime_2).\]
+	Using that 
+	\[Tree(v,H_1)\cap N(v;s)\morph{k} \morph{k} Tree(v,H_1)\cap N(v;s),\]
+	and lemma REF we obtain
+	\[Tree(v,H^\prime_1)\morph{k} Tree(f(v),H^\prime_2) .\]
+	Hence, $H^\prime_1\morph{k} H^\prime_2$, as desired. 
+\end{proof}
+
+\begin{lemma}
+	Let $(T_1,x)$, $(T_2, y)$ be rooted trees such that for some $k\geq 0$
+	$T_1\morph{k} T_2$. Let $e_1$ and $e_2$ be initial edges of $T_1$ and $T_2$
+	such that $e_1\morph{k} e_2$. Then $T_1\setminus e_1\morph{k-1} T_2\setminus e_2$.
+\end{lemma}
+
+\begin{proof}
+	For any $k$-morphism class $C$ of rooted edges clearly either
+	\[|(T_1\setminus e_1,C)|=|(T_2\setminus e_2,C)|,\]
+	or both quantities are greater than $k-1$.
+	Now, using that any $k-1$ morphism class of rooted edges is union of
+	$k$ morphism classes the result follows. 	
+\end{proof}
+
+\begin{lemma}
+	Let $(T_1,x_1)$, $(T_2,x_2)$ be rooted trees such that for some $k\geq 0$
+	$T_1\morph{k} T_2$. For $i=1,2$, given a vertex $v\in V(T_i)$ let us denote by
+	$P(v)$ the unique path between $v$ and $x_i$.
+	Then for any $v\in V(T_1)$ there is a vertex $w\in V(T_2)$ and an isomorphism
+	$f:P(v)\rightarrow P(w)$ such that
+	\begin{itemize}
+		\item[(1)]  $f(x_1)=x_2$ and $f(v)=w$.
+		\item[(2)] For any edge $e\in E(P(v))$, $e\morph{k} f(e)$.
+		\item[(3)] For any vertex $y\in V(P(v))$, $Tree(y,T_1)\morph{k} Tree(f(y),T_2)$.
+	\end{itemize}
+\end{lemma}
+\begin{proof}
+	The proof is by induction on $d(x_1, v)$.
+	\begin{itemize}
+		\item If $d(x_1,v)=0$ then $x_1=v$ and the statement is true taking $w=x_2$.
+		\item Suppose now that $d(x_1,v)=r$. Then one can write the path $P(v)$ as a
+		succession of edges $e_1,e_2,\dots, e_s$, where $v\in e_s$. Let $v^\prime$ be 
+		the root of $e_s$. Then $d(x_1,v^\prime)=r-a(e_s)+1$. Thus, by the
+		induction hypothesis there exists $w^\prime$ such that there is an isomorphism
+		$f: P(v^\prime)\rightarrow P(w^\prime)$ with the required properties. 
+		In particular, $Tree(v^\prime,T_1)\morph{k}Tree(w^\prime,T_2)$, so there is an
+		edge $e^\prime$ rooted at $w^\prime$ with the same $k$-type as $e_s$. Then one can write
+		\[e_s=[v_1,\dots,v_a], \quad  e^\prime=[w_1,\dots,w_a], \]
+		in a such a way that for some $i$, $v_i=v^\prime$ and $w_i=w^\prime$ and for all $j\neq i$
+		$Tree(v_j,T_1)\morph{k} Tree(w_j,T_2)$. Let $j$ be such that $v=v_j$. Then we can take
+		$w=w_j$, and extend the isomorphism $f$ in the evident way. 
+	\end{itemize}
+\end{proof}
+
+\begin{theorem} 
+	Let $G_1(c_1,\dots, c_t)$, and $G_2(c_1,\dots,c_t)$ be graphs
+	with constants such that 
+	\[ Core(G_1(c_1,\dots, c_t);r)\morph{k} Core(G_2(c_1,\dots,c_t);r)\]
+	by means of $f$. 
+	Then, for any vertex $x\in Core(G_1(c_1,\dots, c_t);r)$ there is a vertex
+	$y\in Core(G_2(c_1,\dots, c_t);r)$ such that 
+	\[Core(G_1(c_1,\dots, c_t,c_{t+1}[v_1]);r)\morph{k-1} Core(G_2(c_1,\dots,c_t,c_{t+1}[v_2]);r)\]
+\end{theorem}
+\begin{proof}
+	Let us introduce some notation:
+	\[H_i:=Core(G_i(c_1,\dots, c_t);r)\quad \text{for }i=1,2. \]
+	\[H^\prime_1:=Core(G_1(c_1,\dots, c_t,c_{t+1}[v_1]);r).\]
+
+	The vertex $v_1$ belongs to $Tree(x_1,H_1)$
+	for a unique $x_1\in Center(H_1)$. By the previous lemma there exist a vertex $v_2$ in 
+	$Tree(f(x_1),H_2)$ such that the path $P(v_1)$, 
+	joining $v_1$ and $x_1$, is isomorphic to the path
+	$P(v_2)$, joining $v_2$ and $f(x_1)$, through an isomorphism $f^\prime: P(v_1)
+	\rightarrow P(v_2)$ satisfying properties (1), (2) and (3). 
+	Let 
+	\[H^\prime_2:=Core(G_1(c_1,\dots, c_t,c_{t+1}[v_2]);r).\]
+	We are going to show that $H^\prime_1\morph{k-1}H^\prime_2$.
+	Clearly $Center(H^\prime_i)=Center(H_i)\cup P(v_1)$ for $i=1,2$ , so we can glue
+	$f$ and $f^\prime$ into an isomorphism $g:Center(H^\prime_1)\rightarrow Center(H^\prime_2)$.
+	Let $w_1\in H^\prime$. Then either
+	\begin{itemize}
+		\item $Tree(w_1,H_1)$ contains no edges in $P(v_1)$. 
+		In this case $Tree(w_1,H^\prime_1)=Tree(w_1,H_1)$.
+		Thus, $Tree(w_1,H^\prime_1)\morph{k} Tree(g(w_1),H^\prime_1)$
+		and $Tree(w_1,H^\prime_1)\morph{k-1} Tree(g(w_1),H^\prime_1)$
+		in consequence by lemma REF.
+		\item $Tree(w_1,H_1)$ contains edges from $P(v_1)$.
+		In this case, $Tree(w_1,H_1)$ contains exactly one initial edge
+		$e_1$ in $P(v_1)$, and $Tree(w_1,H^\prime_1)=Tree(w_1,H_1)\setminus e_1$.
+		One can check that $Tree(g(w_1),H_2)$ contains exactly one edge
+		in $P(v_2)$, namely $g(e_1)$, and 
+		$Tree(g(w_1),H^\prime_2)=Tree(g(w_1),H_2)\setminus g(e_1)$.
+		We had $Tree(w_1,H_1)\morph{k}Tree(g(w_1),H_2)$, so by lemma REF
+		$Tree(w_1,H^\prime_1)\morph{k-1}Tree($ $g(w_1),H^\prime_2)$.	
+	\end{itemize}
+\end{proof}
+
+\begin{definition}
+	Let $G_1,G_2$ be graphs with constants. We say that $G_1$ and $G_2$ are
+	$k$-agreeable if for each $\morph{k}$ class $C$ of connected graphs either
+	\begin{itemize}
+		\item $G_1$ and $G_2$ have the same number of connected components of type $C$, or
+		\item Both $G_1$ and $G_2$ have no less than $k$ connected components of type $C$.
+	\end{itemize} 
+\end{definition}
+
+\begin{theorem} 
+	Let $G_1, G_2$ be $k,3^k$-rich graphs such that $Core(G_1;3^k)$ is $k$-agreeable
+	with $Core(G_2;3^k)$. Then Duplicator has a winning strategy in 
+	the $E.F$ game on $G_1$ and $G_2$. 
+\end{theorem}
+\begin{proof}
+	We will show, by induction on $i$, that Duplicator can play in such a way
+	that in the $i$-th round $Core(G_1(c_1[x_1],\dots,c_i[x_i]);3^{k-i})$
+	is $k-i$-agreeable with  $Core(G_2(c_1[y_1],\dots,c_i[y_i]);3^{k-i})$,
+	where for each $j=1,\dots,i$,0 $x_j,y_j$ are the $j$-th 
+	chosen vertex in the graphs $G_1$ and $G_2$	respectively. After this the theorem
+	follows because
+	$Core(G_1(c_1[x_1],\dots,c_i[x_k]);1)$ being $0$-agreeable with
+	$Core(G_2(c_1[y_1],\dots,c_i[y_k]);1)$ implies that
+	the map given by $x_i\mapsto y_i$ defines a partial isomorphism. \par
+	\begin{itemize}[leftmargin=*]
+		\item For $i=0$ the statement is true by hypothesis. 
+		\item Assume now that $Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$
+		is $k-i+1$-agreeable with $Core(G_2(c_1[y_1],\dots, c_i[y_{i-1}]); 3^{k-i+1})$.
+		Without loss of generality we can suppose that Spoiler chooses a vertex 
+		$x_i$ in $G_1$ in the $i$-th round. We have two cases.
+		\begin{itemize}[leftmargin=*]
+			\item[Case 1.] $N(x_i;3^{k-i})$ is contained in 
+			$Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$.
+			Let $H_1$ be the connected component of $Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$
+			containing $N(x_i;3^{k-i})$. Then there is a connected component $H_2$
+			in $Core(G_2(c_1[y_1],\dots,$ $c_i[y_{i-1}]);3^{k-i+1})$ such that
+			$H_1 \morph{k-i+1} H_2$. Applying theorems REF and REF successively Duplicator can choose
+			$y_i\in V(H_2)$ such that 
+			\[ Core(H_1(c_i[x_i]); 3^{k-1})\morph{k-i} Core(H_2(c_i[y_i]); 3^{k-1}).\]
+			Using Theorem Ref and counting the connected components in each $k-i$-morphism class
+			one can check that now $Core(G_1(c_1[x_1],\dots,c_i[x_i]);3^{k-i})$
+			is $k-i$-agreeable with  $Core(G_2(c_1[y_1],\dots,c_i[y_i]);3^{k-i})$.
+			\item[Case 2.] $N(x_i;3^{k-i})$ is contained in 
+			$Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$. Then
+			$N(x_i;3^{k-i})$ is disjoint from $Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i})$
+			and in particular, $N(x_i;3^{k-i})$ is a tree. As $G_2$ was originally $k,3^k$-rich
+			Duplicator can choose $y_i$ in $G_2$ such that $N(y_i;3^{k-i})$ is disjoint from 
+			$Core(G_2(c_1[y_1],\dots,c_i[y_{i-1}]);3^{k-i})$ and the tree $N(x_i;3^{k-i})$
+			rooted at $x_i$ is $k-i$-morphic to the tree $N(y_i;3^{k-i})$ rooted at $y_i$.
+			Counting connected components of each type we can conclude that
+			$Core(G_1(c_1[x_1],\dots,c_i[x_i]);3^{k-i})$
+			is $k-i$-agreeable with  $Core(G_2(c_1[y_1],\dots,c_i[y_i]);3^{k-i})$.
+		\end{itemize}  		
+	\end{itemize}
+
+\end{proof}
+
 Define the families of expressions with arguments $\beta_1,\dots, \beta_l$: 

### 2019-06-23 TFM.tex
Parte combinatoria acabada

@@
 \usepackage{enumitem}
+\usepackage{chngcntr}
+
+\counterwithout{equation}{section}
+\counterwithout{equation}{chapter}
 
@@
 \newtheorem{propdef}{Proposition / Definition}[chapter]
+\theoremstyle{remark}
+\newtheorem{remark}{Remark}[chapter]
 
@@
 Define the families of expressions with arguments $\beta_1,\dots, \beta_l$: 
-$\Lambda$, $\mathcal{E}$ and $\Theta$. \par
+$\Lambda$, $M$ and $\Theta$. \par
 For any sentence $\phi$ we use the notation 
 $Pr_n(\phi):=Pr(G\models \phi)$. \par
-For any F.O. formula $\phi(x_1,\dots,x_l)$ with free variables 
+For any formula $\phi$ with free variables 
 $x_1, \dots, x_l$, we define $Pr_n(\phi(x_1,\dots,x_l))=
-\sum_{G\models \phi(a_1,\dots,a_l)} Pr_n(G) $, 
-where $a_1, \dots, a_l$ are fixed natural numbers in $[n]$.
+\sum\limits_{G\models \phi(a_1,\dots,a_l)} Pr_n(G) $, 
+where $a_1, \dots, a_l$ are fixed \textbf{different}
+natural numbers in $[n]$. If $\phi$ and $\sigma$ are 
+formulas with possibly some free variables, then we define
+$Pr_n(\phi \, | \sigma)=Pr_n(\phi\wedge \sigma)/Pr_n(\sigma)$. \par
+
+We introduce some notation now. For any numbers $l,r\in \N$ 
+we denote by $\phi_r(x_1,\dots, x_l)$ the formula
+with free variables $x_1,\dots, x_l$
+satisfying $G\models \phi_r(x_1,\dots, x_l)$ 
+if for any $y$ there is a unique
+(minimal) path from $y$ to the set of $x_i$'s.
+
+\begin{lemma}
+	Let $\sigma$ be an open formula (i.e., a formula with no quantifiers)
+	with free variables $x_1, \dots, x_l$. Then, for any $r\in \N$
+	\[ \Ln Pr_n(\phi_r(x_1, \dots x_l) \, | \sigma ) =1 .\]
+\end{lemma}
+\begin{proof}
+	We will se that
+	\[ \Ln Pr_n(\neq \phi_r(x_1, \dots, x_l) \, | \sigma ) =0.\]
+	Fix $n$ and $x_1,\dots, x_l \in [n]$.
+    Notice that without loss of generality we can
+	assume that $\sigma$ Boolean combination of atomic
+	formulas of the form $R_i(y_1,\dots,y_{a_i})$, where the $y_i$'s
+	are among the free variables $x_1,\dots, x_l$.
+	In particular $G\models \sigma(x_1, \dots, x_l)$ and 
+	$G\models \phi_r(x_1,\dots, x_l)$
+	are independent events, because $\phi_r$ depends
+	only on the edges not in $x_1,\dots, x_l$.
+	Thus, $Pr_n(\neg \phi_r \, | \sigma)= Pr_n(\neg \phi_r)$.
+	Consider $G$ a random graph in $G(n,p(n))$. 
+	If $\phi_r$ is not satisfied in $G$ then 
+	there exists a $y$ different from the $x_i$'s
+	and two paths $P_1,P_2$ between $y$ and the set 
+	of $x_i$'s with $V(P_i)\leq r+1$. We have two cases
+	\begin{itemize}[leftmargin=*]
+		\item $P_1$ and $P_2$ contain some vertex $z\neq y$
+		in their intersection. Then, using that
+		$ch(P_1), ch(P_2)\geq -1$ and counting we get that
+		$P_1\cup P_2$ is a critical graph of size no greater
+		than $2r+1$.
+		\item The union $P_1\cup P_2$ is a path
+		between some $x_{i_1}, x_{i_2}$ of size no greater
+		than $2r+1$ that contains vertices different
+		from the $x_j$'s. Let us denote by $A$ the event that
+		such a path exists. One can check that $Pr_n(A)\leq C/n$
+		for some fixed $C$.   	
+	\end{itemize}
+	Thus, if we denote by $B$ the event that $G$ contains some 
+	super-critical subgraph of size no greater than $2r+1$,  by the
+	union bound:
+	\[ Pr_n(\neq \phi_r)\leq  Pr_n(B)+ Pr_n(A) 
+	\stackrel{n\to \infty}{\longrightarrow}	0.\]
+\end{proof}
+
+\begin{theorem}{(Multivatiate Brun's Sieve)}
+	Let $r\in \N$ and for each $i=1,\dots, r$  let
+	$\{X_i(n)\}_{n\in \N}$ be a succession of random variables 
+	such that for each $n\in \N$, $X_i(n)$ 
+	is a sum of random indicator variables (i.e. variables 
+	taking only values $0$ and $1$)
+	$Y_{i,1}(n),\dots, Y_{i,s_n}(n)$. Let $\lambda_1, \dots ,
+	\lambda_r$ be real numbers. If for each 
+	$r$-tuple of natural numbers $a_1,\dots, a_r$
+	is satisfied
+	\[ \Ln E\left[\prod_{i=1}^r \binom{X_i}{a_i} \right] = 
+	\prod_{i=1}^r \frac{\lambda_i^{a_i}}{a_i!}, \]
+	then the random variable$(X_1,\dots ,X_r)$ converges in distribution
+	to a tuple of independent Poisson variables with means $\lambda_1
+	\dots \lambda_r$. That is,	
+	\[ \forall x_1,\dots, x_r\in \N: \quad \Ln Pr(\wedge_{i=1}^r
+	 X_i=x_i)= \prod_{i=1}^r Poi_{\lambda_i}(x_i).\]
+
+\end{theorem}
+
+\begin{remark}
+	Let $X$ be a random variable sum of indicator variables
+	$Y_1, \dots, Y_s$. For each $i\in \N$, let 
+	$X_i$ be the random variable
+	\[X_i= |\{ (j_1,\dots, j_l)\, | \, j_1<\dots<j_i, \, Y_{j_1}=
+	\dots = Y_{j_i}=1 \, \}|.\]
+	That is, $X_i$ counts the unordered $i$-tuples of $Y_j$'s that 
+	take value $1$. Then it is not difficult to check that
+	\[ \binom{X}{i}= X_i, \text{ for all } i\in \N. \] 
+\end{remark}
+
+Let $x_1, \dots, x_l$ be vertices of a random graph $G$.
+For each $y\in V(G)$ we abbreviate by $T_r(y; x,1_,\dots, x_l)$
+the rooted tree 
+\[Tree(y, Core(G(c_1[x_1],\dots, c_l[x_l]);r)).\]
 
 \begin{theorem} 
-
+	Let $\sigma(x_1,\dots, x_l)$ be a consistent open formula, and let $k,r,s\in \N$ $s\leq l$. Then, for any $k$-morphism classes $C_1, 
+	\dots, C_s$ of trees with radii
+	at most $r$ it is satisfied
+	\[ \Ln Pr_n(\bigwedge_{i=1}^s Tree_r(x_i; x_1, \dots, x_l)\in C_i \, | 
+	\, \sigma(x_1,\dots, x_l) \,)= \prod_ {i=1}^s \lambda_{C_i,r}.\]	
 \end{theorem}
+\begin{proof}
+The proof is by induction on $r$.
+
+	\item For $r=0$ there is only one class
+	of $k$-morphic trees and the probability in 
+	the statement is always $1$ for all $n$.
+	\item Fix $r>0$ and assume that the statement
+	is true for all lesser values of $r$. \par
+%	Because of lemma REF
+%	\begin{align*} 
+%	&\Ln Pr_n(\bigwedge_{i=1}^s T_r(x_i; x_1, \dots, x_l)\in C_i \, | 
+%	\,\sigma \,)= \\
+%	&=\Ln Pr_n(\bigwedge_{i=1}^s T_r(x_i; x_1, \dots, x_l)\in C_i \, | 
+%	\, \sigma \wedge \phi_r(x_1,\dots,x_l)\,).
+%	\end{align*}
+	Let $\mathcal{E}$ be the set of $k$-types of edges $E$ of
+	radius at most $r-1$. For each $E\in \mathcal{E}$
+	pick a representative
+	$( C_{E,1}, \dots, C_{E,j-1}, r, C_{E,j}\dots, C_{E,a_E-1})$, 
+	and denote by $j_E$ the index of the root in that representative. 
+	Denote by $a_E$ and $c_E$ the arity and color of $E$, and 
+	denote by $\psi_E$ the subgroup of the symmetry group of $\phi_{c_E}$ 
+	that fixes the index $j_E$.
+	Consider, for each $i=1,\dots, s$ and each the random variables 
+	\[X_{i,E}(n)= \text{number of initial edges of type }E \text{ in } 
+	T_r(x_i;x_1, \dots, x_l). \]
+
+	Given $e=[y_1,\dots,y_{j_E-1},x_i, y_{j_E},\dots ,y_{a_E-1}]\in \mathcal{H}_{c_E}(n)$ we can define the indicator 
+	random variable $X_{i,E,e}$ that takes value $1$ if the following are 
+	all satisfied
+	\begin{itemize}
+		\item $e\in H_{c_E}$,
+		\item $e$ belongs to $T_r(x_i;x_1, \dots, x_l)$, and
+		\item the $k$-type of $e$ is $E$. 	
+	\end{itemize} 
+	One can check that for fixed $i, E$
+	\[X_{i,E}(n)= \sum_{e=[y_1,\dots,y_{j_E-1},x_i,y_{j_E},
+	\dots ,y_{a_E-1}]\in \mathcal{H}_{c_E}(n)} X_{i,E,e}(n).\]
+	Thus we can apply the multivariate Brun's Sieve to the variables 
+	$X_{i, E}$.\par
+
+	Let $(b_{i,E})_{\substack{i=1,\dots, s \\ E\in \mathcal{E}}}$ be 
+	natural numbers. We want to compute
+	\[\Ln E\left[\prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
+	\binom{X_{i,E}(n)}{b_{i,E}} \, \Bigg| \, \sigma \right]. \]
+	Define by $\Omega$ the set
+	\begin{align*}
+		&\Omega:= \{ (i,E,b,j) \, | \, i,b,j \in \N, \, E\in \mathcal{E},\\ 
+		& 1\leq i \leq s, \, b=1\leq b \leq b_{i,E}, \, 1\leq j \leq a_E-1 \,\}. 
+	\end{align*} 
+	And let $\hat{\Omega}$ be the projection of $\Omega$ onto its first
+	three coordinates. That is,
+		\begin{align*}
+	&\widehat{\Omega}:= \{ (i,E,b) \, | \, i,b \in \N, \, E\in \mathcal{E},\\ 
+	& 1\leq i \leq s, \, b=1\leq b \leq b_{i,E}\,\}. 
+	\end{align*}
+
+	Denote by $X$ be the set $\{x_1,\dots,x_l\}$.
+	Choose a function $y: \Omega \rightarrow [n]\setminus X$. 
+	Informally, $y()$ represents a choice of edges in $G$. We
+	say that $y()$ satisfies the property $P$ if for any fixed
+	$1\leq i\leq s$, $E\in \mathcal{E}$ and 
+	$1\leq b_1 < b_2\leq b_{i,E}$, and $t=1,2$, the tuples
+	\[ [y(i,E,b_t,1),\dots, y(i,E,b_t,j_E-1), x_i, y(i,E,b_t,j_E),\dots
+	y(i,E,b_t,a_E-1)] \]
+	represent different elements in $\mathcal{H}_{c_E}(n)$.
+	In other words, $y()$ is a choice of different edges. \par	
+	Define
+	the event $A(y)$ as
+	\[ \bigwedge_{(i,E,b,j)\in \Omega} y(i,E,b,j)\in T_r(x_i;x_1, \dots, x_l) .\]
+	Define also the event $B(y)$ as 
+	\[\bigwedge_{\omega=(i,E,b)\in \widehat{\Omega}} [y(\omega,1), \dots, 
+	y(\omega,j_E-1), \, x_i \, ,y(\omega,j_E),\dots,  y(\omega,a_E-1)]\in H_{c_E} .\]
+	Finally, let $T(y)$ be the event that
+	\[\bigwedge_{(i,E,b,j)\in \Omega} T_{(r-a_E+1)}(y(i,E,b,j);x_1
+	\dots,x_l)\in C_{E,j}.\]
+	That is, 
+	\begin{itemize}[leftmargin=*]
+		\item  $A(y)$ is the event that for any fixed $(i,E,b)$ the vertices $y(i,E,b,j)$ belong to the tree of $x_i$, 
+		\item  $B(y)$ is the event that for any fixed $(i,E,b)$ 
+		the vertices $y(i,E,b,j)$ together with $x_i$ form an edge in 
+		$H_{c_E}$ when ordered in a particular way, and
+		\item $T(y)$ is the event that the tree hanging from
+		each vertex $y(i,E,b,j)$ belongs to the particular $k$-morphism
+		class given by the edge type $E$ and the position $j$. 	 	 
+	\end{itemize}
+	Then it is satisfied
+
+	\begin{align} \nonumber
+		& E\left[\prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
+		\binom{X_{i,E}}{b_{i,E}} \, \bigg|\, \sigma \right]= \\
+		&=\prod_{i=1}^{s}
+		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) \cdot
+		\sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ 
+		y \text{ satisfies } P}} 
+		Pr( T(y) \, \wedge \, A(y) \wedge \, B(y) \, | \, \sigma \, ).		
+	\end{align} 
+	Notice that $A(y)$ implies that $y$ is injective. Indeed, if a vertex
+	$v$ belongs to two edges incident to some $x_i$ then both edges cannot
+	belong to the tree of $x_i$ because they would form a cycle (or a super-critical graph). Also, if $v$ belongs to the edges $e_1, e_2$
+	incident to $x_i$ and $x_j$ respectively then it cannot happen that
+	$e_1$ is in the tree of $x_i$ and $e_2$ is in the tree of $x_j$ at the
+	same time, because $e_1\cup e_2$ would belong to the center of 
+	$Core(G(c_i[x_i],c_j[x_j]);r)$.
+	In consequence we only need to take in consideration injective $y$'s in 
+	last equation. Also, by the symmetry of the random model, the probability
+	written in that equation is equal for all injective $y$'s. 
+	Hence we have
+	\begin{align} \nonumber
+		& \prod_{i=1}^{s}
+		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) \cdot
+		\sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 
+		Pr( T(y) \, \wedge \, A(y) \wedge \, B(y) \, | \, \sigma \, )=\\
+		& \label{eqn:distributed}
+		\prod_{i=1}^{s}
+		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) \cdot
+		Pr( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )
+		\cdot \sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1,
+	\end{align} 
+   	where $z$ is an arbitrary injective map from $\Omega$ to
+   	$[n]\setminus X$. \par
+	We can write
+	\[Pr( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )=
+	Pr( T(z) \, \wedge \, A(z) \, | \, B(z) \wedge \sigma \, )
+	\cdot Pr( \, B(z) \, | \, \sigma \, )\]
+	Notice that $\phi_r(x_1,\dots, x_l)\wedge B(z)$ implies $A(z)\wedge
+	B(z)$,	and in consequence the following chain of inequalities holds
+	\begin{align*} 
+	Pr( T(z)  \, | \, B(z) \wedge \sigma \, ) &
+	\geq Pr( T(z) \wedge A(z)  \, | \, B(z) \wedge \sigma \, ) \geq \\ 
+	& \geq Pr(T(z) \wedge \phi_r(x_1,\dots,x_l) 
+	\, | \, B(z) \wedge \sigma \, ).
+	\end{align*}
+	But using lemma REF we get
+	\[ \Ln  Pr_n(T(z) \wedge \phi_r(x_1,\dots,x_l)
+	\, | \, B(z) \wedge \sigma \, ) = 
+	\Ln Pr_n(T(z)\, | \, B(z) \wedge \sigma \, ), \]
+	so
+	\begin{equation} 
+	\Ln  Pr_n(T(z) \wedge A(z)
+	\, | \, B(z) \wedge \sigma \, ) = 
+	\Ln Pr_n(T(z)\, | \, B(z) \wedge \sigma \, ). 
+	\end{equation}
+ 	Notice that $B(z)$ can be written in terms of a purely relational
+ 	open formula with free variables the $y(i,E,b,j)$'s.
+ 	Thus by the induction hypothesis we have
+ 	\[\Ln Pr_n( T(z)  \, | \, B(z) \wedge \sigma \, )= \Gamma, \]
+ 	where 
+ 	\begin{equation}\label{eqn:gammadef}
+ 	\Gamma:=\prod_{\substack{1\leq i \leq s \\ E\in \mathcal{E}\\
+ 	1\leq j \leq a_E - 1 }} (\lambda_{C_{E,j}})^{b_{i,E}}.
+ 	\end{equation}
+ 	In particular $\Gamma$ is different from $0$.
+ 	Hence, last term in \cref{eqn:distributed} is equal to
+ 	\begin{equation} \label{eqn:distributed2}
+ 	\Ln	\prod_{i=1}^{s}
+ 		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) 
+ 		\cdot \Gamma \cdot
+ 		Pr_m(\, B(z) \, | \, \sigma \, )
+ 		\cdot \sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1.
+ 	\end{equation} 
+ 	Also,
+ 	\[\sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1 =|[n]\setminus X|\cdot (|[n]\setminus X|)\cdots 
+ 	(|[n]\setminus X|-|\Omega|+1), \]
+ 	and using that $X$ and $\Omega$ are constant in size,
+ 	\begin{equation}\label{eqn:sumones}
+ 	\sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1 \simeq n^{|\Omega|},
+ 	\end{equation}
+ 	where $f(n)\simeq g(n)$ means that $\Ln f(n)/g(n)=1$.
+ 	Finally, as $\sigma$ only affects the edges between the $x_i$'s
+ 	, $B(z)$ and $\sigma$ are independent. Hence,
+ 	\[ Pr_n(\, B(z) \, | \, \sigma \, ) = \prod_{i=1}^{s} 
+ 	\prod_{E\in \mathcal{E}} \left(\frac{\beta_{c_E}}{n^{(a_E -1)}}
+ 	\right)^{b_{i,E}},  \]
+ 	and using that
+ 	\[  n^{|\Omega|}= \prod_{i=1}^{s} 
+ 	\prod_{E\in \mathcal{E}} (n^{(a_E-1)})^{b_{i,E}}  \]
+ 	and \cref{eqn:sumones} we obtain 
+ 	\begin{equation} \label{eqn:substitution}
+ 	Pr_n(\, B(z) \, | \, \sigma \, )\cdot \sum_{\substack{y:
+ 	\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1 \simeq 	
+ 	\prod_{E\in \mathcal{E}} \beta_{c_E}^{b_{i,E}}. 
+ 	\end{equation}
+ 	In consequence, using \cref{eqn:substitution} and \cref{eqn:gammadef} in
+ 	\cref{eqn:distributed2} we get
+ 	\[ \Ln E\left[\prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
+ 	\binom{X_{i,E}}{b_{i,E}} \, \Bigg| \, \sigma \right]= \prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
+ 	\left[ 	\left(\frac{\beta_{c_E} \prod_{j=1}^{a_E -1} \lambda_{C_{E,j}} }{|\psi_E|}\right)^{b_{i,E}} \frac{1}{b_{i,E}!} \right]. \]
+ 	And using the multivariate Brun's Sieve we get that for each
+ 	choice of natural numbers $\{b_{i,E}\}_{\substack{1\leq i \leq s\\ 
+ 	E\in \mathcal{E}}}$ it is satisfied
+ 	\[ \Ln Pr_n\left(\bigwedge_{i=0}^{s}\bigwedge_{E\in \mathcal{E}} X_{i,E}=b_{i,E} \, \Bigg| \, \sigma \right) = 
+ 	\prod_{i=0}^{s}\prod_{E\in \mathcal{E}} Poi_{\mu_E}(b_{i,E}),\]
+ 	where
+ 	\[\mu_E=
+ 	\frac{\beta_{c_E} \prod_{j=1}^{a_E -1} \lambda_{C_{(E,j)},(r-a_E+1)} }{|\psi_E|}.\]
+ 	The $k$-morphism class of $T_r(x_j;x_1, \dots, x_l)$ depends exclusively
+ 	on the number, up to $k+1$, of its initial edges of each type.
+ 	More explicitly
+ 	\begin{align*}
+ 	&T_r(x_j;x_1, \dots, x_l)\in C \iff \\
+ 	& \bigwedge_{E\in \mathcal{E}}
+ 	\big(X_{j, E}= (C,E) \text{  if  } (C,E)\leq k \big),
+ 	\text{  or  }  \big(X_{j, E}\geq k+1 \text{ otherwise}\big). 
+ 	\end{align*}
+ 	In consequence 
+ 	\begin{align*}
+ 	&\Ln Pr_n(\bigwedge_{i=1}^s Tree_r(x_i; x_1, \dots, x_l)\in C_i \, | 
+ 	\, \sigma \,)=\\ 
+ 	&=\prod_{i=0}^{s}\left[
+ 	\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)<k+1}} Poi_{\mu_E}((C_i,E))\right)
+ 	\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)\geq k+1}} 
+ 	Poi_{\mu_E}(\geq (k+1))\right)\right]=\\
+ 	&=\prod_{i=0}^{s} \lambda_{C_i,r},
+    \end{align*}
+ 	as we wanted. 
+%n^{\sum_{i=1}^s
+%	\sum_{E\in \mathcal{E}} b_{i,E}\cdot(a_{E}-1)}
+
+ 	%\[	Pr( T(z) \, \wedge \, A(z) \, | \, B(z) \wedge \sigma \, )
+ 	%\cdot Pr( \, B(z) \, | \, \sigma \, )=	Pr( T(z) \, | \, B(z) \wedge %\sigma \, )
+ 	%\cdot Pr( \, B(z) \, | \, \sigma \, )\]
+
+ %  \[ \phi_r(x_1,\dots, x_l)\wedge T(z)\wedge B(z)\implies 
+ % T(z)\wedge A(z) \wedge B(z).\]
+ %  Also, if by lemma REF, for any formula $\alpha$ with possibly 
+ %  some free variables,
+ % \[ Pr_n(\, \alpha \wedge \phi_r \, | \, \sigma \,) \simeq
+ %  Pr_n(\, \alpha \, |\, \phi_r \wedge \sigma \,) .\]
+ %  , where the notation  $ f(n)\simeq \ g(n)$, for maps $\N\rightarrow %\R$ satisfying that $g$ takes non-zero
+ %  values when $n$ is sufficiently large. We will use the notation
+ %   $f\simeq g$ to mean $\Ln f(n)/g(n)=1$. \par
+
+%   \begin{align*}
+%   &\Ln Pr_n ( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )
+%   \simeq \\
+%   &\Ln Pr_n ( T(z) \, \wedge \, B(z) \, | \, \phi_r(x_1, \dots, x_l)\, 
+%   \wedge \, \sigma \, ) = \\
+%   &\Ln Pr_n ( T(z) \, | \, \phi_r \, 
+%   \wedge \, \sigma \, \wedge \, B(z) \, )\cdot
+%   Pr_n(B(z)\, | \, \phi_r \, 
+%   \wedge \, \sigma \,) \simeq \\
+%   &\Ln Pr_n ( T(z) \, | \, \phi_r \, 
+%   \wedge \, \sigma \, \wedge \, B(z) \, )
+%   \prod_{E\in\mathcal{E}}\bigg(\frac{\beta_{c_E}}{n^{a_E-1}}\bigg)^{b_{i,E}}
+%   \end{align*}
+%   
+%   
+%   
+%
+%	Also, by lemma REF, for any formula $\alpha$  
+%	with possibly some free variables,
+%	and any	$r\in \N$, $r>0$, we have
+%	\[\Ln Pr_n(\alpha \, | \, \sigma(x_1,\dots, x_l))
+%	= \Ln Pr_n(\alpha \, | \, \phi_r(x_1,\dots, x_l)\wedge \sigma ).\]
+%
+
+	\end{proof}
 
 \begin{theorem}
-	Let $\phi(x_1,\dots, x_l)$ be a consistent open formula, and let $k,r,s\in \N$ $s\leq l$. Then for any $k$-morphism classes of trees with radii
-	at most $r$ the limit
-	\[ \Ln Pr(\bigwedge_{i=i}^s Tree_r(x_i,G)\in C_i \, | \, \phi(x_1,\dots, x_l) \,)\]
-	exists and belongs to $\Lambda$.	
+	Let $O$ be a simple $k$-agreeability class. Then it is satisfied
+	\[ \Ln Pr_n(Core(G;r)\in O) = \theta, \]
+	for some $\theta\in \Theta$.
 \end{theorem}
+
+\begin{proof}
+	This is an easier version of last theorem. \par
+	Let $\mathcal{U}$ be the set of all $k$-morphism classes of 
+	unicycles with radius at most $r$. 
+	For each class $U\in \mathcal{U}$ choose a representative $rep(U)\in U$, 
+	and let  $cycle(U)$ be the cycle in $rep(U)$, whose number of vertex will be
+	denoted by $n_U$. Choose an ordering $x_{U,1},\dots, x_{U,n_U}$
+	of the vertices in $cycle(U)$ and for each $1\leq i \leq n_{U}$ 
+	denote by $C_{U,i}$ the $k$-morphism class
+	of $Tree(x_i,rep(U))$. One can consider $cycle(U)$ to be a 
+	vertex colored graph where the color assigned to each vertex $x_i$
+    is $C_{U,i}$. Isomorphisms of the colored cycle 
+	$cycle(U)$ induce permutations of $[n_U]$ via this ordering. 
+	Let us denote by $\psi_U$ that group of permutations.\par 
+	For any $U\in \mathcal{U}$ we define the random variable 
+	\[X_{U}(n)=\text{number of connected components of }Core(G;r) 
+	\text{ in } U ,\]
+	and for each element $g\in V(G)^{n_U}/\psi_U$ 
+	we define the indicator variable $X_{U,g}(n)$ that equals $1$ if 
+	\begin{itemize}
+		\item $g=[x_1,\dots, x_{n_U}]$, for some vertices
+		$x_1,\dots, x_{n_U}$ such that the map $f:G[X]\rightarrow cycle(U)$ 
+		,where $X=\{x_1,\dots x_{n_U}\}$, defined by $x_i\mapsto x_{U,i}$ is an
+		isomorphism. 
+		\item $N(X;r)$ is a connected component of $Core(G;r)$.
+		\item $N(X;r)\morph{k} rep(U)$ via $f$. In particular this means
+		that $Tree(x_i, G)$ belongs to $C_{U,i}$.
+	\end{itemize}	
+	In other words, $X_{U,g}$ indicates if there is a graph in the $k$-morphism
+	class $U$ embedded in $G$ in a particular way represented by $g$.
+	One can check that for all $U\in \mathcal{U}$
+	\[ X_U(n)=\sum_{g\in [n]/\psi_U} X_{U,g}(n),  \]
+	so we can apply the multivariate Brun's Sieve to the $X_U$'s.\par
+	Let $(b_U)_{U\in \mathcal{U}}$ be fixed natural numbers. We are interested
+	in obtaining
+	\[\Ln E\left[\prod_{U\in \mathcal{U}}
+	\binom{X_{U}(n)}{b_{U}}\right].\]
+	Let $\Omega$ be the set defined as
+	\[ \Omega:= \{\, (U,b,i) \, | \, U\in \mathcal{U}, 
+	\, b,i\in \N, \, 1\leq b \leq b_U,  \, 1\leq i \leq n_U\,  \}\]
+	and let $\widehat{\Omega}$ be the projection of $\Omega$ onto its
+	two first coordinates. That is, 
+	\[\widehat{\Omega}:=\{\, (U,b) \, | \, U\in \mathcal{U}, 
+	\, b\in \N, \, 1\leq b \leq b_U \, \}. \]
+
+	Let $y: \Omega \rightarrow [n]$ be a map. Informally, $y()$
+	represents a choice of embeddings of graphs in with the appropriate
+	$k$-morphism classes. We will say that $y()$ satisfies the property
+	$P$ if for any fixed $U\in \mathcal{U}$ and $1\leq b_1<b_2\leq b_{U}$
+	the tuples
+	\[ [y(U,b_1,1), \dots, y(U,b_1,n_U)], \text{ and }
+	[y(U,b_2,1), \dots, y(U,b_2,n_U)] \]
+	represent different elements in $[n]^{n_U}/\psi_U$. That is, $y()$ is 
+	a choice of different embeddings.\par
+	Define for any $(U,b)\in \widehat{\Omega}$
+	the set $Y(U,b)=\{ \, y(U,b,i) \, | \, 1\leq i \leq n_U \, \}$.
+
+	We define the following events for a given $y:\Omega\rightarrow [n]$.
+	\begin{itemize}
+		\item Let $A(y)$ be the event that for each $(U,b)\in \widehat{\Omega}$,
+		the map $f_{U,b}:cycle(U)\rightarrow G[Y(U,b)]$ given
+		by $x_{U,i} \rightarrow y(U,b,i)$ is an embedding. 	
+		\item Let $B(y)$ be the event that $Center(N(Y(U,b);r)$ is 
+		the image of $f_{U,b}$,	for each $(U,b)\in \widehat{\Omega}$.
+		\item Let $T(y)$ be the event that 
+		\[\bigwedge_{(U,b,i)\in \Omega} T_r(y(U,b,i); Y)\in C_{U,i}, \]
+		where $Y$ denotes set of vertices in the image of $y$.  
+	\end{itemize}
+	Then,
+	\[ E\left[\prod_{U\in \mathcal{U}}
+	\binom{X_{U}(n)}{b_{U}}\right] = \prod_{U\in \mathcal{U}} 
+	\frac{1}{|\psi_U|^{b_U}b_U!} \cdot
+	\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ satisfies }P}}
+	Pr(A(y)\wedge B(y)\wedge T(y)). \]
+
+	Property $P$,together with events $A(y)$ and $B(y)$ imply that $y$ is
+	injective, so we can consider only such $y$'s in last equation. Again, by 
+	the symmetry of the random model the probability appearing there is the same
+	for all injective $y$'s. Hence,
+	\begin{align}
+	\nonumber
+	&\prod_{U\in \mathcal{U}} 
+	\frac{1}{|\psi_U|^{b_U}b_U!} \cdot
+	\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ satisfies }P}}
+	Pr(A(y)\wedge B(y)\wedge T(y))= \\ 
+	\label{eqn:distributed3}
+	& =\prod_{U\in \mathcal{U}} 
+	\frac{1}{|\psi_U|^{b_U}b_U!} \cdot Pr(A(z)\wedge B(z)\wedge T(z)) \cdot
+	\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ injective }}}1,
+	\end{align}
+	where $z$ is an arbitrary injective map $z:\Omega\rightarrow [n]$.\par
+	We can write 
+	\[Pr(A(z)\wedge B(z)\wedge T(z))=Pr(B(z)\wedge T(z) \, |\, A(z)) \cdot 
+	Pr(A(z)).\]
+	Let $\tau_r$ be the event that $G$ is $r$-simple. One can check that
+	$A(y) \wedge \tau_r$ implies $A(y)\wedge B(y)$. 
+	In consequence the following chain of inequalities holds
+	\[Pr(T(z)\,|\, B(z))\geq Pr(T(z)\wedge A(z) \,| \, B(z)) \geq
+	 Pr(T(z)\wedge \tau_r \,| \, B(z)).\]
+	Notice that $B(z)$ can be expressed as a purely relational open formula
+	with free variables the elements indexed by $z$, because it only depends on
+	the edges between vertices in the image of $z$.
+	Using the previous theorem and LEMMA we obtain
+	\[\Ln Pr_n(T(z)\wedge \tau_r \,| \, B(z))= \Ln Pr_n(T(z)| \,| \, B(z)) = \Gamma, \]
+	where
+	\[ \Gamma:=\prod_{\substack{U\in \mathcal{U}\\ 1 \leq i\leq n_{U}}}
+	(\lambda_{C_{(U,i)}, r})^{b_U}.\]
+
+	Because the probability of each edge is independent, one obtains 
+	\[ Pr_n(B(z))= \prod_{(U,b)\in \widehat{\Omega}} 
+	\frac{\prod_{i=1}^c	\beta_i^{|H_i(cycle(U))|}}{n^{n_U}}.  \]
+	Also,
+	\[\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ injective }}}1
+	\simeq \prod_{(U,b)\in \widehat{\Omega}} n^{n_U}. \]
+	This way substituting REF, REF and REF in EQ we get
+	\[\Ln E\left[\prod_{U\in \mathcal{U}}
+	\binom{X_{U}(n)}{b_{U}}\right]= \prod_{U\in \mathcal{U}}
+	\left(\frac{ \prod_{i=1}^c \beta_i^{|H_i(cycle(U))|} \prod_{i=1}^{n_U} \lambda_{U,i}}{|\psi_U|}\right)^{b_U}\cdot \frac{1}{b_{U}!}. \]
+
+	Applying the multivatiate Brun's Sieve we obtain that for any fixed  
+	natural numbers $(b_U)_{U\in \mathcal{U}}$ 
+	\[\Ln Pr_n\left( \bigwedge_{U\in \mathcal{U}} X_U=b_U  \right)=
+	\prod_{U\in \mathcal{U}}Poi_{\xi_U}(b_i),
+	\]
+	where
+	\[ \xi_U= \frac{ \prod_{i=1}^c \beta_i^{|H_i(cycle(U))|} \prod_{i=1}^{n_U} \lambda_{U,i}}{|\psi_U|}.\]
+
+	The class of $k$-agreeability of a graph depends only on the number
+	of connected components of each $k$-morphism class. More explicitly, 
+	if $O$ is a $k$-agreeability class of radius $r$, 
+	\[Core(G;r)\in O \iff \bigwedge_{U\in \mathcal{U}} (X_U=(O,U) \text{ if }(O,U)\leq k), \text{ or }  (X_U\geq k+1 \text{ otherwise}).\]
+	In consequence,
+	\[ \Ln Pr_n(Core(G;r)\in O) = \left(\prod_{\substack{U\in \mathcal{U}\\(O,U)\leq k}} Poi_{\xi_U}((O,U)) \right) \left(\prod_{\substack{U\in \mathcal{U}\\(O,U)\geq k+1}}
+	Poi_{\xi_U}(\geq (k+1)) \right),\]
+	as we wanted.   
+\end{proof}
 

### 2019-06-25 TFM.tex
Casi fin

@@
 \newtheorem{propdef}{Proposition / Definition}[chapter]
-\theoremstyle{remark}
 \newtheorem{remark}{Remark}[chapter]
@@
 {\endinneraxiom}
-
+\newcommand{\cc}{\mathfrak{c}}
 \newcommand{\Z}{\mathbb{Z}}
@@
 \newcommand{\Ln}{\lim\limits_{n\to \infty}}
-\newcommand{\clist}{c_{i_1}, \cdots, c_{i_m}}
+\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
 \newcommand{\morph}[1]{\stackrel{#1}{\simeq}}
@@
 \begin{document}
+\begin{abstract}
+	The goal is to generalize the results from Lynch (1992) on the convergence law for sparse random graphs to sparse random hypergraphs.
+This requires in particular an understanding of Lynch's techniques, based on Ehrenfeucht-Fraïssé games, an analysis of the structure of sparse random hypergraphs.
+\end{abstract}
 \tableofcontents
@@
 \chapter*{Introduction}
-
-\chapter*{Notation}
 
@@
 in the first order language $\Lan$ of graphs whose quantifier rank is $k$, and denote by
-$G$ a random graph in $G(n,\beta/n)$. We define the events $E_1,\dots,E_{n_k}$ as
-\[E_i:= (G \models \phi) \wedge (G \in C_i),\]
-and the  event $F$ as
-\[F:= (G \models \phi) \bigwedge_{i=1}^{n_k} (G \notin C_i).\]
-Then, for any $n\in \N$
-\begin{equation} \label{eqn:sumevents}
-P(G\models \phi) = \sum_{i=1}^{n_k} P(E_i)  + P(F),
-\end{equation}
-as the events $E_i$ together with $F$ form a partition of all the cases where $G$ satisfies $\phi$. \par
-
-Fix and index $i\in \{1, \dots, n_k\}$. From the property (1) of the classes $C_1,\dots, C_{n_k}$ 
-it follows that if $G$ and $H$ are random graphs, then
-\[\Ln P((G\models \phi) \wedge \neg(H\models \phi) \, | \, G\in C_i \wedge H\in C_i \, ) = 0.\]
-This is because $G$ and $H$ share a.a.s the same rank $k$ type if they both belong to $C_i$. 
-In consequence the limit
-\[ \Ln P(G\models \phi \, | \, G\in C_i )\] 
-is either zero or one, and 
-\begin{equation}\label{eqn:property1}
-\Ln P(E_i)= \Ln P(G\in C_i)\cdot P(G\models \phi \, | \, G\in C_i)= \text{ either } 0 \text{ or } \Ln P(G\in C_i).
-\end{equation} 
-\par 
-Also, as a consequence of property $(2)$ we obtain
-\[\Ln P(\bigwedge_{i=1}^{n_k} G \notin C_i)=0, \] 
-so
-\begin{equation}\label{eqn:property2}
-\Ln P(F)= \Ln P(\bigwedge_{i=1}^{n_k} G \notin C_i)\cdot P(G\models \phi \, | \, \bigwedge_{i=1}^{n_k} G \notin C_i)=0.  
-\end{equation}
-\par
-Taking limits in equation \ref{eqn:sumevents} and using equations \ref{eqn:property1} and \ref{eqn:property2} 
-we get
-\[ \Ln P(G\models \phi) = \sum\limits_{C_i\in \mathcal{C}} \Ln P(G \in C_i) ,\]
-where $\mathcal{C}$ is a (possibly empty) subset of $\{C_1,\dots, C_{n_k}\}$.
-Finally, because of property (3) for each $i$ the limit $\Ln P(G \in C_i)$ is 
-an expression in $\Theta$. Thus $\Ln P(G\models \phi)$ is a finite sum of expressions in $\Theta$
-and the theorem follows. \par
+$G$ a random graph in $G(n,\beta/n)$. \par
 
@@
 
-\section{Agreability Classes}
+\section{Agreeability Classes}
 
@@
 
-\chapter{First Order Logic of Sparse Random General Hypergraphs}
-
-\section{General Hypergraphs}
-
-$\forall n\in N: \quad [n]:= \{1,\dots, n\}$\par
-$S_n:$ symmetric group on $n$ elements. \par
-Let $X$ be a set, then:
-\begin{itemize}
-	\item $\Delta\subset X^2:$ $\Delta$ is the diagonal subset. $\Delta: \{(a,a)\in X^2 \}$.
-	\item $S_n$ acts on $X^n$ in the obvious way. 
-	\item When the subgroup $\phi$ is understood or (is not relevant) $\langle x_1,\dots,x_n\rangle$
-	denotes the equivalence class of $(\vlst{x}{n})$ in $X^n/\phi$.
-\end{itemize}
+\chapter{First Order Logic of Sparse Random Hypergraphs}
+
+\section{Basic definitions and conventions.}
+
+\subsection{General relational structures.}
+
+Given a natural number $n$, we will use the notation
+$[n]:= \{1,\dots, n\}$. We will denote by $S_n$
+the symmetric group on $[n]$, and by $\Delta_n$ the 
+diagonal set $\{(a,a)\in [n]^2 \}$. \par
+Given a set $X$, then $S_n$ acts on $X^n$ in an evident way. That is, 
+given $g\in S_n$ and $(x_1, \dots, x_n)$ one can define
+\[ g \cdot (x_1,\dots,x_n) =(y_1,\dots,y_n), \]
+where $y_{g(i)}=x_i$ for all $1\leq i\leq n$.\par
+Given $\Phi$ a subgroup of $S_n$ we will denote by $X^n/\Phi$
+the orbit set associated to the action of $\Phi$ over $X^n$.\par
+We will use the notation $[x_1,\dots,x_n]$ to refer to the 
+equivalence class of the $n$-tuple $(x_1,\dots, x_n)$ in 
+any sort of quotient $X^n/\Phi$. That is, while the notation
+$(x_1,\dots, x_n)$ will be reserved to ordered $n$-tuples, 
+$[x_1,\dots,x_n]$ will denote an ordered $n$-tuple modulo the
+action of some arbitrary group of permutations. Which group is this 
+will depend solely on the ambient set where $[x_1,\dots,x_n]$ is
+considered.
 \par
@@
 \begin{definition}
-	Let $V$ be a finite set. Given a natural number $a\in \N$, a group $\phi\leq S_a$ and a subset
-	$R\subseteq [a]^2 \setminus \delta$, the total (hiper-)edge set of size $a$, symmetry group $\phi$ and
-	restrictions $R$ is the set:
-	\[ \mathcal{H}_{V,a}^{\phi,R}= V^n/\phi \, \, \setminus \{\,  \langle 
-	x_1, \dots,x_n\rangle
-	 \in V^n/\phi  \, \, | \, \, x_i=x_j \, \text{for some } (i,j)\in R \} \]
-
-\end{definition}
-
-\begin{definition}
-	An hypergraph $(V,H_1,\dots, H_l)$ with edge sizes $a_1,\dots,a_l$, 
-	symmetry groups $\phi_1,dots,\phi_1$ and restrictions $R_1,\dots,R_l$ consists of
-	\begin{itemize}
-		\item A finite vertex set $V$.
-		\item For $i=1,\dots,l$, an edge set $H_i\subseteq \mathcal{H}_{V,a_i}^{\phi_i,R_i}$.
-	\end{itemize}
-\end{definition}
-
-\begin{definition} 
-	Random model $G(n, p_1,\dots, p_l)$ with edge sizes $a_1,\dots,a_l$, 
-	symmetry groups $\phi_1,dots,\phi_1$ and restrictions $R_1,\dots,R_l$:
-	\begin{itemize}
-		\item We obtain a hypergraph $(V,H_1,\dots, H_l)$ with $V=[n]$
-		\item The probability of each edge $e\in \mathcal{H}_{V,a_i}^{\phi_i,R_i}$
-		is $p_i$ independently. 
-	\end{itemize}
-\end{definition}
-
-From now on we fix the edge sizes $a_1,\dots,a_l$, 
-symmetry groups $\phi_1,dots,\phi_1$ and restrictions $R_1,\dots,R_l$. \par
-
-In a graph $G(V,E_1,\dots, E_l)$, the type of an edge $e$ is the index
-$i$ such that $e\in E_i$.
-
-The language is the first order relational 
-language with relations $R_1,..., R_l$ of arities
-$a_1,\dots, a_l$ respectively. The interpretation on 
-$(V,H_1,\dots, H_l)$ is the evident one. \par
-
-\begin{definition}
-	The characteristic $ch(G)$ of an hypergraph $G=(V,E_1,\dots,E_l)$ is
-	\[ \left( \sum_{i=1}^l |E_i|(a_i-1)\right) -	|V|  .\]
-	An hypergraph is c-balanced if it contains no subgraph of
-	greater characteristic than itself. 
-\end{definition}
-
-\begin{proposition}
-	A connected graph cannot have characteristic lesser than $-1$.
+	Let $n,a\in \N$, let $\Phi$ be a subgroup of $S_a$, and let
+	$A$ be a subset 
+	\[ A\subseteq [a]^2 \setminus \delta.\]
+	The total edge set $\mathcal{H}_{(a,\Phi, A)}(n)$ of size $a$, 
+	symmetry group $\Phi$ and
+	restrictions $R$ on $n$ elements is the set:
+	\[  \mathcal{H}_{(a,\Phi, R)}(n)= ([n]^a/\Phi) \, \,
+	\setminus \{\,  [x_1, \dots,x_a] \in [n]^a/\Phi  \, \, 
+	| \, \, x_i=x_j \, \text{for some } (i,j)\in R \} \]
+\end{definition}
+
+\begin{definition}
+	An (hyper)-graph $([n], H_1,\dots, H_c)$ with edge colors 
+	$1,\dots, c$, sizes $a_1,\dots,a_c$, 
+	symmetry groups $\Phi_1,\dots,\Phi_c$ and 
+	restrictions $A_1,\dots,A_c$ consists of 
+	\begin{itemize}
+		\item The set $[n]$ for some natural number $n$.
+		\item For $i=1,\dots,c$, a colored edge set $H_i\subseteq \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ whose elements 
+		have color $i$.
+	\end{itemize}
+\end{definition}
+
+\begin{definition} 
+	Let $p=(p_1,\dots, p_c)$, where all $p_i$'s are real numbers
+	between $0$ and $1$. 
+	The random model $HG(n,p)$ with edge colors $1,\dots,c$,
+	sizes $a_1,\dots,a_c$, 
+	symmetry groups $\Phi_1,dots,\Phi_c$ 
+	and restrictions $A_1,\dots,A_c$, is the one that
+	assigns to each graph $G=([n], H_1,\dots, H_c)$
+	probability
+	\[ Pr(G)=\prod_{i=1}^{c} p_i^{|H_i|}(1-p_i)^{|\mathcal{H}_{(a_i,\Phi_i,A_i)}(n)|-|H_i|}.	
+	\]
+	Equivalently, this is the probability space obtained by 
+	assigning to each colored edge 
+	$e\in \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ probability $p_i$ independently. 
+\end{definition}
+
+For the rest of the work we will consider 
+\begin{itemize}
+	\item the total number of colors $c$,	
+	\item the sizes $a_1,\dots,a_c$,
+	\item the symmetry group $\Phi_1,\dots, \Phi_c$ and,
+	\item the restrictions $A_1,\dots,A_l$
+\end{itemize}
+fixed. When we say ``graph'' from now on what
+we will mean is ``hiper-graph with edge colors 
+$1,\dots, c$, sizes $a_1,\dots,a_c$, 
+symmetry groups $\Phi_1,\dots,\Phi_c$ and 
+restrictions $R_1,\dots,R_c$''. \par
+
+Given a graph $G=([n], H_1,\dots, H_c)$ we will denote by
+$H_i(G)$ the edge set $H_i$, and by $V[G]$ the vertex set
+$[n]$. Also, we will write $H(G)$ to denote the 
+disjoint union of colored sets $\cup_{i=1}^c H_i$.
+This way, an edge $e\in H(G)$ with color $i$ is an element
+$[x_1,\dots,x_{a_i}]\in H_i(G)$, and the $x_i$'s are vertices
+belonging to $V(G)$. \par
+Given a set of vertices, $X\subseteq V(G)$, we will denote
+the by $G[X]$ the induced sub-graph on $X$. \par
+As usual, we will sometimes treat edges as sets of vertices
+rather than ``tuples modulo the action of some permutation group''. 
+This way, expressions like $e_1\cup e_2$ for $e_1, e_2\in H(G)$
+will make sense and mean 
+``the set of vertices that occupy some place in $e_1$ 
+and in $e_2$".\par
+Some other times we will treat edges $e\in H(G)$
+as sub-graphs of $G$ in the evident way. That is, the subgraph
+denoted by $e$ is the one whose vertex set is $e$-i.e., the vertices in $e$-
+and whose only edge is $e$. 
+This way, when we have some edges $e_1,\dots, e_l\in H(G)$ 
+it will make sense to talk
+about the subgraph $\cup_{i=1}^l e_i$, which is the graph
+whose vertex set is the set of vertices belonging to the $e_i$'s, 
+and whose edges are exactly the $e_i$'s. In spite of these
+abuses of notation the ``type'' of any ``term'' involving edges 
+should be derivable from the context. \par
+Another usual abuse of notation we will make is to sometimes
+treat graphs as their underlying vertex sets. Hence,
+expressions defined for sets of vertices will also be defined 
+for graphs.
+
+\subsection{The First Order Language}
+
+From now on when we talk about ``first order formulas" 
+will be referring to formulas in the first order relational 
+language $\mathcal{L}$ with relations $R_1,..., R_c$ of arities
+$a_1,\dots, a_c$ respectively. \par
+
+Graphs are $\mathcal{L}$-structures in an evident way. 
+The universe of a graph $G$ is $V(G)$, and for each 
+$1\leq i \leq c$ and any $x_1,\dots, x_{a_i}$ we say 
+\[R_i(x_1,\dots,x_{a_i}) \text{ if } [x_1,\dots, x_{a_i}]\in H_i(G).\] 
+That is, variables in $L$ are interpreted as vertices in $G$ and
+relations are interpreted as edges. By definition, all graphs $G$ 
+satisfy the formulas
+\begin{itemize}
+	\item Symmetry formulas:
+	\[ S_g: =\big( R_i(x_1\dots,x_{a_i})\iff R_i(x_{j_1}\dots,x_{j_{a_i}})\big) ,\]
+	where the the index $j_k$ is $g(k)$, and $g$ is an element from $\Phi_i$.
+	\item Anti-reflexivity formulas:
+	\[A_{i,(j,l)}:=\big(R_i(x_1\dots,x_{a_i})\implies 
+	\neg(x_j= x_l)\big),\]
+	where $(j,l)\in A_i$.
+\end{itemize}
+
+\section{The Theorem.}
+
+From now on we will adopt the following two conventions:
+\begin{itemize}
+	\item We will always work in the random model $HG(n,p(n))$, where
+	$p(n)=p(n,\beta)$ is defined as the tuple
+	$(\beta_1 n^{1-a_1},\dots, \beta_c n^{1-a_c})$, and
+	$\beta=(\beta_1,\dots, \beta_c)$.
+	The symbols $\beta_1,\dots, \beta_c$
+	denote positive real variables,
+	but for the most part we will 
+	treat them as arbitrary positive real constants.
+	\item The first order language we will always refer to is the one 
+	defined in last section, $\mathcal{L}$. 
+\end{itemize}
+
+We define $\Lambda$ and $M$ as the minimal families
+of expressions with arguments $\beta_1,\dots, \beta_c$ that satisfy the conditions:
+\begin{itemize}
+	\item $1\in \Lambda$
+	\item For any $\mu\in M$ and any $n\in \N$ both
+	$Poi_{\mu}(n)$ and $Poi_\mu(\geq n)$ are in $\Lambda$
+	\item For any $\lambda_1,\lambda_2 \in \Lambda$, the
+	product $\lambda_1\lambda_2$ belongs to $\Lambda$ as well.
+	\item For any $l,a,i\in \N$ with $1\leq i \leq c$,
+	$a > 0$, and $\lambda_1,\dots, \lambda_l\in \Lambda$,
+	the expression $\frac{\beta_i \prod_{j=1}^{l}\lambda_j}{a}$
+	belongs to $M$.		
+\end{itemize}
+We also define another families $\widehat{\Theta}$ and $\Theta$ of expressions with arguments
+$\beta_1,\dots, \beta_c$ as the minimal one satisfying:
+\begin{itemize}
+	\item For any $l,s,a\in \N$ with $a>0$ and any 
+	non-necessarily-different $\lambda_1,\dots, \lambda_l\in \Lambda$,
+	$\alpha_1,\dots,\alpha_s\in \{\beta_1,\dots \beta_c\}$,
+	the expression 
+	\[\frac{\left(\prod_{i=1}^{l} \lambda_i \right)
+		\left( \prod_{i=1}^{s}\alpha_i \right)}{a}\] 
+	lies in $\widehat{\Theta}$.
+	\item For any $g\in \widehat{\Theta}$ and any $n\in \N$ both
+	$Poi_g(n)$ and $Poi_g(\geq n)$ are in $\Theta$.
+	\item For any $\theta_1, \theta_2\in \Theta$ the product
+	$\theta_1\theta_2$ belongs to $\Theta$ as well.
+\end{itemize}
+
+For any first order sentence $\phi$
+we will use the notation 
+$Pr_n(\phi):=Pr(HG(n,p(n))\models \phi)$. \par
+
+The rest of the work will be devoted to prove the following theorem:
+
+\begin{theorem}\label{thm:THEONE} 
+	Let $\beta=(\beta_1,\dots, \beta_c)$, and let $\psi$ be a 
+	F.O sentence in $\mathcal{L}$. Then the function
+	\[
+	\mathfrak{F}(\beta):=\Ln Pr(\, HG(n,p(\beta,n))\, \models \, \psi \,)
+	\]
+	is well defined for all values of $\beta$ and it is a finite sum 
+	of expressions in $\Theta$.
+\end{theorem}
+
+\section{Sub-critical, Critical and Super-critical Graphs.}
+
+We define a distance over arbitrary graphs $G$. For each $x, y\in V(G)$,
+\[ d(x,y)= \min_{\substack{H \text{ subgraph of } G\\ 
+H \text{ connected }\\
+x,y\in V(H)}} |V(H)| - 1 .\]
+That is, the distance between $x$ and $y$ is the minimum size
+of a connected graph $H$ containing both. 
+If such graph does not exist we define $d(x,y)=\infty$.
+This definition extends naturally to subsets $X,Y\subseteq V(G)$:
+\[ d(X,Y)=\min_{\substack{x\in X\\ y\in Y}} d(x,y).\]
+As usual, when $X=\{x\}$ we will omit the brackets and write
+$d(x,Y)$ instead of $d(\{x\},Y)$, for example.  \par
+
+\begin{definition} 
+	A path between $x$ and $y$ is a connected graph containing both 
+	$x$ and $y$	that is minimal among the ones with those properties. 
+\end{definition}
+
+\begin{proposition}\label{prop:pathform}
+	A path $P$ between $x$ and $y$ in a graph $G$ is a union of 
+	edges $e_1,\dots, e_l\in H(G)$ such that
+	\begin{itemize}
+		\item $x$ only belongs to
+		$e_1$ and $y$ only belongs to $e_l$.
+		\item For any $1\leq j < i\leq l$, $e_i$ intersects
+		$e_j$ if and only if $i=j+1$.
+	\end{itemize}  	
 \end{proposition}
-
-\begin{definition}
-	A unicycle is a connected c-balanced graph with characteristic $0$.
-\end{definition}
-
-\begin{definition} A cluster is a minimal c-balanced graph.
-\end{definition}
-
-Remark: Note that clusters have to be connected.
-
-\begin{definition}
-	A cycle is a minimal unicycle, or equivalently a characteristic $0$ cluster.  
-\end{definition}
+\begin{proof}[Sketch of the proof.]
+	Proceed by induction on the number of edges.
+\end{proof}
+
+\begin{definition}
+	The likelihood $L(G)$ of an hypergraph $G=(V,E_1,\dots,E_l)$ is
+	the number
+	\[ \left( |V(G)| - \sum_{i=1}^l |H_i(G)\langle Ta_i-1)\right).\]
+	An hypergraph is $L$-balanced if it contains no subgraph with
+	less likelihood than itself. 
+\end{definition}
+
+Given a graph $G$, and an edge $e\in H(G)$ of color $i$,
+the operation of ``cutting'' the edge $e$ is the one where we remove 
+$e$ from $H_i$ and afterwards we also remove the isolated 
+vertices from the resulting graph.
+
+\begin{proposition} \label{prop:balanced}
+	Any connected graph $G$ is $L$-balanced. 
+\end{proposition}
+\begin{proof}
+	\begin{proof}[Sketch of the proof.]
+		Suppose $G$ is non-empty.
+		The proof is by induction on the number of edges in $G$. 
+		\item If $G$ has zero edges it is an isolated vertex so the statement is true.
+		\item Suppose that $G$ has $m>0$ edges. Choose a vertex $x\in V(G)$ and
+		an edge $e\in H(G)$ such that the distance from the $x$ to $e$ is maximum. 
+		The subgraph $F$ obtained from cutting $e$ must be connected, so by the
+		induction hypothesis $F$ is balanced. 
+		The original graph $G$ was connected, 
+		so $e$ must intersect $F$ in at least one vertex, and
+		\begin{equation}\label{eqn:balanced}
+		L(G)\leq L(F).
+		\end{equation}
+		Suppose that $G$ contains a sub-graph $G_2$ with 
+		$L(G_2)<L(G)$. Then, as $F$ is $L$-balanced and
+		\ref{eqn:balanced} holds, $e\in H(G_2)$. Call $F_2$
+		to the result of cutting $e$ in $G_2$. Then
+		$F_2$ is a subgraph of $F$ and one can check
+		\[ L(F_2) - L_(G_2) \leq L(F)-L(G).\]
+		In consequence, as $L(F)-L(F_2)$ is non-positive, 
+		so is $L(G)-L(G_2)$, arriving at a contradiction.
+	\end{proof}
+\end{proof}
+
+\begin{corollary}
+	A (non-empty) connected graph $G$ cannot have more likelihood than $1$.
+\end{corollary}
+\begin{proof}
+	A because of the previous proposition $G$ is $L$-balanced.
+	If $G$ is non-empty it contains some vertex,
+	and vertices have likelihood $1$.
+\end{proof}
+
+\begin{definition} 
+	We will call sub-critical, critical and super-critical
+	graphs to $L$-balanced graphs with likelihood greater than
+	zero, zero, and less than zero respectively. 
+\end{definition}
+
+\begin{definition}
+	A cluster is a connected graph $G$ with non-positive likelihood such 
+	that all of its subgraphs $T$ have greater likelihood
+	than itself. 
+\end{definition}
+
+We will call unicycles to connected critical graphs, and cycles
+to minimal unicycles. In particular, cycles are clusters.
 
@@
 \end{proposition}
-
-\begin{definition} 
-	A (hiper)forest is a graph with no clusters. A (hiper)tree is a connected forest.
-\end{definition}
-
-\begin{definition} 
-	A path between $x$ and $y$ is a connected graph containing both $x$ and $y$
-	that is minimal among the ones with those properties. 
+\begin{proof}[Sketch of the proof.]
+ 	Suppose the unicycle $G$ contains two different cycles $F_1,F_2$.
+ 	\item If $F_1$ and $F_2$ have nonempty intersection then $F_1\cup F_2$ 
+ 	has negative likelihood.
+ 	\item Otherwise, consider a path $P$ between two vertices $x\in V(F_1)$
+ 	and $y\in V(F_2)$. The union $F_1\cup F_2 \cup P$ has negative likelihood.
+\end{proof}
+
+\begin{proposition}
+	A cycle $G$ is either:
+	\begin{itemize}
+		\item[(1)] An edge $e$ where exactly one vertex appears exactly
+		twice.
+		\item[(2)] A path $P$, with $L(P)=1$
+		between two vertices $x$ and $y$, with
+		$L(P)=1$, together with an edge $e$ that intersects $P$ exactly
+		in $x$ and $y$.
+	\end{itemize}
+\end{proposition} 
+\begin{proof}[Sketch of the proof.]
+	\item If $G$ contains only one edge then (1) holds necessarily.
+
+	\item Otherwise, $G$ cannot contain an edge that intersects the rest of the graph
+	only in one vertex, because cutting it would yield a smaller connected 
+	graph with likelihood $0$.
+
+	This way, by double counting one can obtain that 
+	each edge intersects the rest of $G$ exactly in two vertices.
+	Choose an edge $e\in H(G)$ and call $F$ to the graph obtained by
+	cutting $e$ in $G$. The intersection $e\cup F$ contains exactly two 
+	vertices, $x, y$. The graph $F$ must be 
+	\begin{itemize}
+		\item Connected. Otherwise one of its connected components would have
+		likelihood $0$ or less.
+		\item A path between $x$ and $y$. Otherwise it contains a path $P$ between
+		$x$ and $y$ and $P\cup E$ has likelihood $0$. 
+	\end{itemize} 
+	Thus (2) holds, as we wanted. 
+\end{proof}
+
+Given a graph $G$, its diameter $diam(G)$ will be the maximum distance
+between any two of its vertices:
+\[diam(G)=\max_{\substack{x,y\in V(G)}} d(x,y).\]
+
+\begin{corollary}\label{cor:finitecycles}
+	For any $r\in \N$ there is a finite number of 
+	cycles with diameter at most $r$.
+\end{corollary}
+\begin{proof}[Sketch of the proof]
+	Let $G$ be a cycle with $diam(G)=r$, and let
+	$x,y\in V(G)$ be such that $d(x,y)=r$. Let $e$
+	be an edge containing $y$ and not $x$. If such edge
+	does not exists then $G$ is composed of at most two edges.
+	Otherwise
+	consider $F$ the graph resulting from cutting $e$ in $G$. 
+	One can check that $F$ must be a path of size at most $2r$, 
+	and there are a finite number of those.
+	In consequence we can represent all cycles of diameter $r$
+	either as an edge, as an union of two edges, or as an
+	union of a path with size at most $r$ with an edge. 
+	In particular $|V(G)|\leq 2r+2a$, where $a$ is the
+	maximum of $a_1,\dots, a_c$.
+\end{proof}
+
+\begin{proposition}
+	A cluster is a connected graph $G$ where each edge
+	$e\in H(G)$
+	satisfies at least one of the following:
+	\begin{itemize}
+		\item[(1)] $e$ intersects the union of all the other edges
+		in $H(G)$ in at least two vertices.
+		 \item[(2)] $e$ contains some vertex at least twice.
+	\end{itemize}
+\end{proposition}
+\begin{proof}
+	Suppose that $e\in H(G)$ satisfies neither (1) nor (2). Then
+	the graph $G^\prime$ obtained from cutting $e$ in $G$ is a subgraph
+	of $G$ with
+	\[L(G^\prime)= L(G).\]
+	In consequence $G$ is not a cluster. 
+\end{proof}
+
+\begin{definition} 
+	A tree is a connected graph with likelihood $1$.
 \end{definition}
@@
 \end{proposition}
-
-We define the constant set $Const:=\{c_i\}_{i\in \N}$.
-
-\begin{definition} 
-	As before, a (hiper)graph with constants $G(\clist)$ is a hypergraph 
-	$G$ together with a co-labeling. 
-\end{definition}
+\begin{proof}[Sketch of the proof]
+	Let $T$ be a tree. Suppose there are 
+	two vertices $x, y\in V(T)$
+	with two different paths, $P_1,P_2$, between them. 
+	Then the graph $P_1\cup P_2$ would have non positive
+	likelihood, contradicting \cref{prop:balanced}.
+\end{proof}
+
+\begin{proposition}
+	A tree $T$ is a graph obtained from successively adding edges to a single
+	vertex in such a way that any new edge intersects the current graph
+	in exactly one vertex. 
+\end{proposition}
+\begin{proof}[Sketch of the proof.]
+	Choose a vertex $x\in V(T)$ and an edge $e\in H(T)$ such that 
+	the distance between the two is the maximum one. Call $T_2$
+	to the graph obtained by cutting $e$ in $T$. The graph $T_2$ 
+	is a tree and intersects $e$ in exactly one vertex. 
+	One can continue this process until reaching a single edge.
+	Repeating the process backwards now, adding the removed 
+	edges successively, yields the result.  	
+\end{proof}
+
+\section{Agreeability classes. Winning Strategy For Duplicator}
+
+We define the set of constants symbols as
+$Const:=\{\mathfrak{c}_i\}_{i\in \N, \, i>0}$.
+For any $n\in \N$, $n>0$, let $Const_n$ be the set $\{\mathfrak{c}_1,\dots,\mathfrak{c}_n\}$. 
+A co-labeling of a graph $G$ is a map $\nu:Const_n\rightarrow V(G)$,
+where for some $n>0$. Given $\mathfrak{c}_i\in Const_n$, 
+we will say that the vertex $\nu(\cc_i)$ is labeled $\cc_i$.
+Equivalently, we can denote a labeling $\nu$ as a tuple
+$(\cc_{1}[x_1],\dots, \cc_m[x_m])$ where each 
+$x_j$ in $V(G)$ labeled $\cc_j$.
+
+\begin{definition} 
+	A graph with constants $G(\clist)$ is graph $G$
+	together with a co-labeling $(\cc_{1}[x_1],\dots, \cc_m[x_m])$. 
+\end{definition}
+
+To keep our notation compact we will often drop 
+he $x_i$'s and say $G(\cc_1,\dots, \cc_m)$ and 
+sometimes we will even omit the $(\cc_1,\dots, \cc_m)$ and
+denote by $G$ the graph with constants when the co-labeling is not 
+relevant. \par
+We will often identify constants $\cc_i$ with their labeled vertices
+$\nu(\cc_i)$. This should not lead to confusion. 
+However, note that for two
+different indices $i,j$, $\nu(\cc_i)$ and $\nu(\cc_j)$
+may be the same vertex,
+but the constant symbols $\cc_i$ and $\cc_j$ are different.\par
 
@@
 
-We define a distance over $G(\clist)$.
-\[ d(x,y)= (\text{minimum size of a connected graph containing }x \text{ and } y) - 1 \]
-If such graph does not exist we define $d(x,y)=\infty$.\par
-
-Given $x\in V(G)$ and $X\subseteq V(G)$ we define $N(x;r)$ and $N(X;r)$ as
-\[ N(x;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | dist(x,y)\leq r \, \} \]
-\[ N(X;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | dist(X,y)\leq r \, \}. \]
-
-\begin{definition}
-	 A rooted (hiper)tree is a tree with a distinguished vertex called root.
-	 The radius of the tree is the maximum distance between its root and any
+Given $x\in V(G)$ and $X\subseteq V(G)$ we define the
+neighbourhood graphs $N(x;r)$ and $N(X;r)$ as
+\[ N(x;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | d(x,y)\leq r \, \} \]
+\[ N(X;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | d(X,y)\leq r \, \}, \]
+for each $r\in \N$.
+
+\begin{definition}
+	 A rooted tree $(T,x)$ is a tree $T$ with a distinguished vertex 
+	 $x$ called root.
+	 The radius of the tree is the 
+	 maximum distance between its root and any
 	 of its vertices.  
-\end{definition}
-
-In a rooted tree $(T,x)$ all the (hiper)edges can be rooted in a canonical way. 
-The root of an edge $e$ is the vertex $y\in e$ such that $dist(x,y)=dist(x,e)$.
-
-\begin{definition}
-	Let $G(\clist)$ be a graph with constants and $x\in V(G)$. Then
-	$Tree(x,G)=(G[V_x],x)$, where
-	\[ V_x= \{\, y\in V \, | \, dist(Center(G),y)= dist(Center(G),x)+ dist(x,y) \,	 \}. \]
-\end{definition}
-
-\begin{definition} 
-	The $k$-morphism equivalence relation $\morph{k}$ between rooted trees,
-	and the $\stackrel{k}{\sim}$ relation for rooted (hyper)edges are defined inductively as follows:
-	\begin{itemize}
-		\item If $T_1$ and $T_2$ are radius $0$ trees then they consist only of
-		their roots and $T_1\morph{k} T_2$. 
-		\item 
-		If $e_1$ and $e_2$ are edges in rooted trees $T_1$,$T_2$ of radii at most $r$,
-		then $e_1\stackrel{k}{\sim} e_2$ if $e_1$ and $e_2$ are edges of the same 
-		type and $e_1=[x_1,\dots, x_m]$, $e_2=[y_1,\dots,y_m]$ in a way that
-		\begin{itemize}
-			\item $x_i$ is the root of $e_1$ if and only if $y_i$ is the root of $e_2$.
-			\item If $x_j$ is not the root of $e_1$, then
-			$Tree(x_j, T_1)\morph{k} Tree(y_j, T_2)$.
-		\end{itemize}
-		\item If $T_1$ and $T_2$ are trees of radii at most $r$ and roots $x$ and $y$,
-		then $T_1\morph{k} T_2$ means that for any $\stackrel{k}{\sim}$ class
-		of edges $C$ either
-		\begin{itemize}
-			\item the number of edges in $T_1$ of type $C$ containing $x$ is the same
-			as the number of edges in $T_2$ of tipe $C$ containing $y$, or
-			\item both $T_1$ and $T_2$ contain no less than $k+1$ edges of type $C$
-			containing $x$ and $y$ respectively. 
-		\end{itemize}
-
-	\end{itemize}
-
-\end{definition}
-
-\begin{definition} 
-	Let $G_1(\clist)$ and $G_2(\clist)$ be graphs with the same constants. Then
-	we say $G_1(\clist)\morph{k}G_2(\clist)$ if there is a bijection 
-	$f:V(Center(G_1))\rightarrow V(Center(G_2))$ such that
+	 The initial edges of $(T,x)$ are the edges in $T$ containing
+	 the root.
+\end{definition}
+
+We will often omit the root and denote by $T$ the whole rooted tree $(T,x)$.\par
+
+In a rooted tree $(T,x)$ all the edges can be rooted in a canonical way. 
+The root of an edge $e$ is the vertex $y\in e$ such that $d(x,y)=d(x,e)$.
+
+\begin{definition}
+	Let $G(\clist)$ be a graph with constants and $X,Y\subset V(G)$. Then
+	$Tree(x,G)$ is the rooted tree $(G[V_x],x)$, where
+	\[ V_x= \{\, y\in V \, | \, d(Center(G),y)= d(Center(G),x)+ d(x,y) \,	 \}. \]
+\end{definition}
+
+Informally, $Tree(x,G)$ is the graph composed of all the vertices that
+have to pass through $x$ in order to reach $Center(G)$.
+
+\begin{remark}
+	The graph $Tree(x,G)$ is indeed a tree.
+\end{remark}
+
+When $(T,x)$ is a rooted tree, we will use the notation
+\[ Tree(y, T):= Tree(y,T(\cc_1[x])). \]
+That is, $Tree(y,T)$ is the tree that ``hangs from $y$'' in
+$T$.
+
+When the ``environment graph'' is clear we will write $Tree(x)$
+instead of $Tree(x,G)$.
+
+\begin{definition} 
+	The $k$-morphism equivalence relation $\morph{k}$ between rooted trees
+	of the same radius,
+	and the $k$-type of an edge in a rooted tree,
+	are defined inductively as follows:
+
+	\begin{itemize}
+		\item If $T_1$ and $T_2$ are radius $0$ rooted trees then they consist only of their roots and $T_1\morph{k} T_2$. 
+		\item The radius of a $k$-morphism class of rooted trees $C$
+		is the radius that all trees in $C$ have.
+		\item Let $T$ be a rooted tree of radius $r$. The $k$-type
+		of an edge 
+		\[e=[x_1,\dots, x_{j-1}, x ,x_j, \dots, x_{a_d-1}]\in H(T)\]
+		with color $d$, where $x$ is the root of $e$, is the colored 
+		``tuple modulo the action of $\Phi_d$'' 
+		\[E=[C_1,\dots, C_{j-1}, \mathfrak{r}, C_j,\dots, C_{a_d -1}]
+		,\]
+		with dolor $d$, where
+		\begin{itemize}
+			\item $\mathfrak{r}$ is the ``root symbol''
+			\item $C_i$ is the $k$-morphism class of the tree
+			$Tree(x_i,T)$, for $1\leq i \leq a_d-1$.
+		\end{itemize} 
+		The radius of $E$ is the maximum radius of any of the
+		$C_i$'s.
+
+		\item If $T_1$ and $T_2$ are trees of radius $r>0$ and roots $x$ and $y$, then $T_1\morph{k} T_2$ means that for any $k$-type of edges $E$
+		with radius less than $r$ at least one of the following is satisfied:
+		\begin{itemize}
+			\item The number of initial edges in $T_1$ and $T_2$ of $k$-type $E$ 
+			is the same.
+			\item both $T_1$ and $T_2$ contain no less than $k+1$
+			initial edges of $k$-type $E$. 
+		\end{itemize}
+	\end{itemize}
+\end{definition}
+
+\begin{remark}
+	If $(T,x)$ is a rooted tree with radius 
+	$r$, any initial edge $e\in H(T)$ has ($k$-type
+	of) radius less than $r$.
+\end{remark}
+
+When working with graphs $G_1(\clist)$ and $G_2(\clist)$ with the 
+same constants we will use super-indices to distinguish between the
+constants $\cc_i\in V(G_1)$ and $\cc_i \in V(G_2)$. We will call them
+$\cc_i^1$ and $\cc_i^2$ respectively.
+
+\begin{definition} 
+	Let $G_1(\clist)$ and $G_2(\clist)$ be graphs with the same constants. 
+	Then we
+	will say that they are $k$-morphic, denoted by $G_1(\clist)\morph{k}G_2(\clist)$, if there is an isomorphism
+	$f:Center(G_1)\rightarrow Center(G_2)$ such that
 	\begin{itemize}
@@
 
-The diameter of a (hiper)graph is the maximum distance between any two of its vertices.
-
-\begin{definition} 
-	Let $G(\clist)$ be a graph with constants. We define $Core(G,r)$ to be
-	$N(X,r)$ where $X$ is the union of constants and clusters of diameter at most $r$. 
-\end{definition}
-
-\begin{definition} 
-	A (hyper)graph $G$ is $r$-simple if $Core(G,r)$ is a union of unicycles. 
-\end{definition}
-
-\begin{definition}
-	A (hyper)graph $G$ is $j,r$-rich for some $j,r\in \N$, if for any rooted tree $T$
-	of radius at most $r$ there are $x_1,\dots,x_j\in V(G)$ such that
-	\begin{itemize}
-		\item The $N(x_l;r)$'s are disjoint.
-		\item The $N(x_l;r)$'s do not intersect $Core(G,r)$
-		\item $N(x_l;r)(x_l) \morph{j} T$.		
-	\end{itemize} 
-\end{definition}
-
-\begin{theorem}
-	If $G_1(c_1,\dots,c_m)\morph{k} G_2(c_1,\dots,c_m)$, then for any $x\in V(G_1)$ such 
-	that $d(x,Center(G_1))\neq \infty$ there is a $y\in V(G_2)$ such that
-	$G_1(c_1,\dots,c_m,c_{m+1}[x])\morph{k-1} G_2(c_1,\dots,c_m,c_{m+1}[y])$.
-\end{theorem}
-
-\begin{theorem}
-	If $Core(G_1,r)\morph{k} Core(G_2,r)$ then for any $s<r$, $Core(G_1,s)\morph{k} Core(G_2,s)$.
-\end{theorem}
-
-\begin{definition} 
-	Two graphs with constants $G_1$ and $G_2$ are $k$-agreeable if for each $k$-morphism 
-	equivalence class $C$ they either have the same number of connected components of type
-	$C$ or they both have no less than $k+1$ components of type $C$. 
-\end{definition}
-
-\begin{theorem} 
-	Let $G_1, G_2$ be graphs with constants satisfying:
-	\begin{itemize}
-		\item They are both $(k, k, 3^k)$-rich.
-		\item $Core(G_1,3^k)$ is $k$-agreeable with $Core(G_2,3^k)$.
-	\end{itemize} 
-	Then the $G_1$ and $G_2$ share the same rank $k$ type.
-\end{theorem}
-
-From now on fix $\beta_1,\dots,\beta_l$ positive real numbers.
-
-\begin{lemma}
-	Let $H$ be a cluster with $ch(H)>0$, and let $X_n$ be the
-	random variable that counts the number of times that $H$ appears
-	as a subgraph of $G(n,p(n))$. Then
-	\[\Ln Pr(X_n>0)=0. \]
-\end{lemma}
-\begin{proof}
-	Let $v=|V(H)|$ and $e_i=|E_i(H)|$ for $i=1,\dots, l$. 
-	The criticality condition on $H$ means 
-	\[ \langle e, a-1 \rangle - v > 0 .\]
-	Chose a ordering of the vertices in $H$. 
-	For any ordered sequence of vertices $S=(x_1, \dots, x_v)$, 
-	let $X_{n,S}$ be the indicator variable that equals $1$ if $H$
-	is a subgraph of $G[S]$ (in a way that respects the ordering) and
-	$0$ otherwise. Clearly $X_n$ is the sum of all the $X_{n,S}$'s, so
-	\[ E(X_n)= \frac{n(n-1)\cdots (n-v+1)}{b} \prod_{i=1}^{l}
-	\left( \frac{c_i}{n^{a_1-1}}\right) ^{e_i}, \] 
-	where $b$ is the carnality of $H$'s group of isomorphisms. 
-	Then because of the criticality hypothesis
-	\[ \Ln E(X_n)=0, \]
-	and using the first moment method 
-	the result follows. 
-\end{proof}
-
-\begin{lemma}
-	Let $H$ be a critical graph of characteristic $r$.
-	Then $H$ contains a critical subgraph with size no greater than
-	$(a+2)(r+1)+2a$, where $a$ is the largest edge size in $H$. 
-\end{lemma}
-\begin{proof}
-	Choose $x\in V(H)$. Successively remove from $H$ edges $e$
-	such that $dist(x, e)$ is maximum until the resulting graph 
-	$H^\prime$ has characteristic no greater than $0$. We have two cases:
-	\begin{itemize}
-		\item $ch(H^\prime)=1$. Let $e=[x_1, \dots, x_b]$ be
-		the last removed edge and
-		$e\cap H^\prime=\{ x_{i_1}, \dots, x_{i_c}\}$.
-		For any $j=1,\dots, c$ choose 
-		$P_j$ a path of size no greater than $r+1$ joining
-		$x$ and $x_{i_j}$ in $H^\prime$.   
-		Then $P_1\cup \dots P_c \cup e$ is a critical subgraph of $H$
-		of size less than $a(r+1) + a< (a+2)(r+1) + 2a$.
-		\item $ch(H^\prime)=0$. Let $e_1=[x_1, \dots, x_{b_1}]$ be the
-		last removed edge. Continue removing the edges of $H^\prime$ 
-		that are at maximum distance from $x$ until you obtain 
-		$H^{\prime \prime}$ with $ch(H^\prime)=-1$. Let 
-		$e_2=[y_1, \dots, y_{b_1}]$ be the last removed edge.
-		As before, let $e_1\cap H^\prime=\{ x_{i_1}, \dots, x_{i_c}\}$
-		and for $j=1,\dots, c$ let $P_j$ a path of size no greater than $r+1$ 
-		joining	$x$ and $x_{i_j}$ in $H^\prime$
-		Then $e_2 \cup H^{\prime \prime}=\{ y_{i_1}, y_{i_2}  \}$.
-		Let $Q_1, Q_2$ be paths size no greater than $r+1$ from
-		$x$ to $y_{i_1}$ and $y_{i_2}$ in $H^{\prime \prime}$.
-		Then $Q_1 \cup Q_2 \cup e_2$ is a graph of characteristic $0$ 
-		and size less than $2r+2 + a$,
-		and $Q_1\cup Q_2\cup P_1 \cup \dots \cup P_c \cup e_1 \cup e_2$ 
-		is a critical graph	with size less than $(2+a)(r+1) + 2a$	
-	\end{itemize} 
-\end{proof}
-
-\begin{corollary}
-	Let $A_n$ be the event that $G(n,p(n))$ contains critical 
-	subgraph with diameter no greater than $r$. Then
-	\[ \Ln Pr(A_n)=0. \]
-\end{corollary}
-\begin{proof}
-	If a random graph contains $G$ such critical graph, then by the previous
-	lemma it has to contain a critical graph of size less than some constant $M$.
-	The number of critical graphs of such size is finite and the probability 
-	that any one of those appears as a subgraph of $G$ is asymptotically zero.	 
-\end{proof}
-
-\begin{theorem} For any $r$,
-	\[\Ln Pr(G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1} ) \text{ is }r \text{-simple})=1 .\]
-\end{theorem}
-
-\begin{lemma} 
+Notice that the relation symbol $\morph{k}$ is ``overloaded". 
+It is used to denote
+both the $k$-morphism relation between rooted 
+trees and the $k$-morphism relation
+between graphs with constants. We give now another additional
+meaning to the symbol $\morph{k}$. 
+Let $T_1$ and $T_2$ be rooted trees
+and let $e_1\in H(T_1)$, $e_2\in H(T_2)$ be edges. We will 
+write $e_1\morph{k} e_2$ to denote that $e_1$ and $e_2$ have
+the same $k$-type.
+
+\begin{remark}
+	The $k$-type of an edge $e$ in a rooted tree $T_1$
+	does not only depend on the edge $e$. It also contains some 
+	non-local information about $T_1$. Namely, it contains the 
+	$\morph{k}$ classes of the trees ``hanging'' from $e$.
+	If $T_2$ is a sub-tree of $T_1$ also containing $e$, the $k$-type
+	of $e$ in $T_2$ may differ from the $k$-type of $e$ in $T_1$.
+	However we will usually refer to ``the $k$-type of $e$'' instead of
+	``the $k$-type of $e$ in $T_1$'' when the ``ambient tree'' is clear
+	from context.   
+\end{remark}
+
+Let $T$ be a rooted tree of radius $r$, and let $E$ be a $k$-type of edges with radius less than $r$ for some $k\in \N$. We will denote by $\langle T,E \rangle$
+the number of initial edges in $T$ of $k$-type $E$. \par
+Let $C$ be a $k$-morphism class of rooted trees with radius $r$. 
+Consider
+a representative $T\in C$. We define the number $\langle C, E \rangle$ 
+as the maximum between $\langle T, E\rangle$ and $k+1$. One can check that 
+$\langle C, E\rangle$ does not depend on the choice of $T$.\par
+
+With this new notation, if $C$ is a $k$-morphism class of rooted
+trees with radius $r$ and $T$ is a rooted tree of radius $r$, it
+is satisfied that $T\in C$ if and only if for each $k$-type $E$ of edges 
+with radius less than $r$ either
+\[ \langle C,E \rangle=\langle T,E \rangle, \quad \text{ or } \quad
+\langle C,E \rangle,
+\langle T,E \rangle \geq k+1 .\]
+
+\begin{lemma} \label{lem:lessktree}
 	Let $(T_1,x)$ and $(T_2,y)$ be rooted trees such that for some $k>0$ 
@@
 	Fix $j<k$. The proof is by induction on the radius of $T_1$ and $T_2$.
-	\begin{itemize}
-		\item If they have radius at most $0$ they are $j$-morphic by definition. 
-		\item Suppose now that they have radii at most $r$. Let $e_1$ be an edge with root
-		$x$ in $T_1$ and $e_2$ be an edge of root $y$ in $T_2$ such that $e_1 \morph{k} e_2$.
-		Then $e_1=[x_1,\dots,x_a]$ and $e_2=[y_1,\dots,y_a]$ for some vertices such that for all
-		$i=1,\dots, a$ either 
-		\begin{itemize}
-			\item $Tree(x_i)\morph{k} Tree(y_i)$, and because of the induction hypothesis 
-			$Tree(x_i)\morph{j} Tree(y_i)$. 
-			\item Or $x_i=x$ and $y_i=y$.
-		\end{itemize}
-		In consequence $e_1\morph{j} e_2$. Then, any class $C$ 
-		of $j$-morphic edges in trees of radius at most
-		$r$ is union of classes $D_1,\dots, D_s$ of $k$-morphic edges in 
-		trees of radius at most $r$. Then
-		\[(T_1,C)=\sum_{i=1}^s (T_1, D_i) \text{, and }	(T_2,C)=\sum_{i=1}^s (T_2, D_i).\]	
-	 	Both of the above sums coincide if all the $(T_1, D_i)$'s are not greater than $k$ or
-	 	both are greater than $k$ otherwise. As $j\leq k$ this implies
-	 	\[\text{Either }(T_1,C)=(T_2,C) \text{ or } (T_1,C),(T_2,C)\geq j+1 ,\]
+	\begin{itemize}[leftmargin=*]
+		\item If they have radius $0$ they are $j$-morphic by definition. 
+		\item Suppose now that they have radius $r$. Let $e_1$ be an initial edge 
+		in $T_1$ and $e_2$ be an initial edge in $T_2$ such that $e_1 \morph{k} e_2$.
+		Then, because of the definition of $k$-type,
+		$e_1$ and $e_2$ have the same color $l$ and we can write
+		$e_1=[x_1,\dots,x_{c_l}]$,
+		$e_2=[y_1,\dots,y_{c_l}]$ for some vertices such that for all
+		$i=1,\dots, a_l$ either 
+		\begin{itemize}
+			\item $Tree(x_i)\morph{k} Tree(y_i)$, and because of the induction hypothesis $Tree(x_i)\morph{j} Tree(y_i)$. 
+			\item Or both $x_i=x$ and $y_i=y$ are the roots of $T_1$ and $T_2$.
+		\end{itemize}
+		In consequence $e_1\morph{j} e_2$. Then, the $\morph{k}$ relation
+		implies the $\morph{j}$ relation on edges with radius less than $r$.
+		Thus, for any $j$-type of edges $E$ there are 
+		$k$-types of edges $E_1, \dots, E_m$ such that for all rooted trees $T$
+		\[ \langle T,E\rangle = \sum_{i=1}^{m} \rangle T,E_i \langle .\]
+		In particular
+		\[\langle T_g , E\rangle =\sum_{i=1}^m \langle T_g, E_i \rangle 
+		\quad \text{, for } 	g=1,2.\]	
+	 	Both of the above sums coincide if all the numbers
+	 	$\langle T_1, E_i\rangle$'s are not greater than $k$ or
+	 	both sums are greater than $k$ otherwise. As $j\leq k$ this implies
+	 	\[\text{Either }\langle T_1, E \rangle =\langle T_2,E \rangle \text{ or } \langle T_1,E \rangle ,\langle T_2,C \rangle \geq j+1 ,\]
 	 	and $T_1\morph{j}T_2$. 		
@@
 \begin{corollary}
-	Let $G_1(c_1,\dots, c_t)$, and $G_2(c_1,\dots,c_t)$ be graphs
-	with constants such that $G_1(c_1,\dots, c_t)\morph{k}G_2(c_1,\dots,c_t)$.
-	Then, for any $j<k$, $G_1(c_1,\dots, c_t)\morph{j}G_2(c_1,\dots,c_t)$.
+	Let $G_1(\cc_1,\dots, \cc_t)$, and $G_2(c_1,\dots,c_t)$ be graphs
+	with constants such that $G_1(\cc_1,\dots, \cc_t)\morph{k}G_2(c_1,\dots,c_t)$.
+	Then, for any $j<k$, $G_1(\cc_1,\dots, \cc_t)\morph{j}G_2(c_1,\dots,c_t)$.
 \end{corollary}
 
-\begin{lemma}
+\begin{remark}
+	Given a rooted tree $(T,x)$, the neighborhood $N(x;r)$ for any $r\in \N$
+	together with the root $x$ is a rooted tree.
+\end{remark}
+
+\begin{lemma}\label{lem:radiustree}
 	Let $(T_1,x)$ and $(T_2,y)$ be rooted trees such that for some $k>0$ 
-	$T_1 \morph{k} T_2$. Then, for any $r\geq 0$, $N(x;r)\morph{k} N(y;r)$.
+	$T_1 \morph{k} T_2$. Then, for any $r\geq 0$, 
+	\[(N(x;r),x)\morph{k} (N(y;r),y).\]
 \end{lemma}
@@
 	The proof is by induction on the radius of $T_1$ and $T_2$.
-	\begin{itemize}
+	\begin{itemize}[leftmargin=*]
 		\item If they have at most radius $0$ the statement is vacuously true. 
-		\item Suppose now that they have radii at most $r$. Let $e_1$ be an edge with root
+		\item Suppose now that they have radii at most $s$. Let $e_1$ be an edge with root
 		$x$ in $N(x;r)$ and $e_2$ be an edge of root $y$ in $N(y;r)$ such that $e_1 \morph{k} e_2$
@@
 		In consequence $e_1 \morph{k} e_2$ as edges in $N(x;r)$ and $N(y;r)$. 
-		This implies that for any $k$-morphism class of rooted edges $C$ of trees with
-		radii less than $r$ there are $k$-morphism classes $D_1,\dots,D_c$ of rooted edges
-		of trees with radii at most $r$ such that
-		\[ (N(x;r),C) = (T_1, D_1)\cup \dots \cup (T_1,D_a), \]
-		and 
-		\[(N(y;r),C) = (T_2, D_1)\cup \dots \cup (T_2,D_a).\]
-		And we can easily obtain that either
-		$|(N(x;r),C)|=|(N(y;r),C)|$ or $|(N(x;r),C)|,$ $
-		|(N(y;r),C)|\geq k+1$. 	Thus $N(x;r)\morph{k} N(y;r)$.
-	\end{itemize}	
-\end{proof}
-
-\begin{lemma}
+		This implies that for any $k$-type $E$ edges of trees with
+		radius less than $r$ there are $k$-types of edges classes 
+		$E_1,\dots,E_l$ of rooted edges such
+		of trees with radii at most $s$ such that
+		\[ \langle N(x;r),E \rangle =  \sum_{i=1}^{l}\langle T_1, E_i\rangle ,\]
+		and the same for $N(y;r)$ and $T_2$.\par
+		From this follows that either
+		\[ \langle N(x;r),E \rangle =\langle N(y;r),E \rangle \quad
+		\text{ or } \quad  
+		\langle N(x;r),E \rangle,
+		\langle N(y;r),E \rangle \geq k+1. \]
+		Thus $N(x;r)\morph{k} N(y;r)$.
+	\end{itemize}	
+\end{proof}
+
+\begin{lemma}\label{lem:addtrees}
 	Let $(T_1,x),(T^\prime_1,x), (T_2, y)$ and $(T^\prime_2,x)$ 
@@
 \begin{proof}
-	Let $C$ be a $k$-morphism class of rooted edges. Then
-	\[|(T_1\cup T_1^\prime,C)|= |(T_1,C)|+ |(T_1^\prime,C)|, \text{and }\]
-	\[|(T_2\cup T_1^\prime,C)|= |(T_2,C)|+ |(T_2^\prime,C)|.\]
-	And it follows easily that either
-	\[|(T_1\cup T_1^\prime,C)|=|(T_2\cup T_2^\prime,C)|,\]
+	Let $E$ be a $k$-morphism class of rooted edges. Then
+	\[\langle T_1\cup T_1^\prime,E \rangle = \langle T_1,E \rangle + \langle T_1^\prime,E \rangle , \text{and }\]
+	\[\langle T_2\cup T_1^\prime,E \rangle = \langle T_2,E \rangle + \langle T_2^\prime,E \rangle .\]
+	And it follows that either
+	\[\langle T_1\cup T_1^\prime,E \rangle =\langle T_2\cup T_2^\prime,E \rangle ,\]
 	or both quantities are greater than $k$. 
@@
 
-\begin{lemma} 
+Let $T$ be  tree and $T^\prime$ be a sub-tree of $T$. For any 
+$y\in V(T^\prime)$ we will denote by $Span(y, T^\prime, T)$ the 
+rooted tree $(T[Y],y)$, where
+\[ Y:= \{ \, x\in V(T) \, | \, d(T^\prime,x)=d(x,y) \,  \}	.\]
+That is, $Span(y, T^\prime, T)$ is the tree consisting of the vertices
+in $T$ that ``need to pass through $y$ in order to reach $T^\prime$".
+We also define the graph $Span(T^\prime, T)$ as the union 
+\[ \bigcup_{y\in V(T^\prime)} Span(y,T^\prime, T).  \]
+
+\begin{lemma} \label{lem:isosubtree}
 	Let $(T_1,x)$, $(T_2, y)$ be rooted trees and let 
@@
 	for all $x_1\in V(T^\prime_1)$
-	\[ Tree(x_1,T^\prime_1)\morph{k} Tree(f(x_1),T^\prime_2),\]
+	\[ Span(x_1,T^\prime_1,T_1)\morph{k} Span(f(x_1),T^\prime_2,T_2),\]
 	then $T_1\morph{k}T_2$. 
@@
 	The proof is, again, by induction on the radius of $T^\prime_1$ and $T^\prime_2$.
-	\begin{itemize}
+	\begin{itemize}[leftmargin=*]
 		\item If $T^\prime_1$ and $T^\prime_2$ have radius zero, then they consist only of
@@
 		\item Suppose that $T^\prime_1$ and $T^\prime_2$ have at most $r$. Let $x_1\neq x$ be
-		a vertex in an edge $e$ rooted at $x$ such that $e\in T^\prime_1$.
-		Then $Tree(x_1, T_1)$ and $Tree(x_1,T^\prime_1)$ satisfy the hypothesis of the lemma,
-		and the radius of $Tree(x_1,T^\prime_1)$ is strictly less than $r$. Then by the induction
-		hypothesis $Tree(x_1, T_1)\morph{k} Tree(f(x_1),T_2)$. In consequence $e\morph{k}f(e)$
+		a vertex in an edge $e$ rooted at $x$ such that $e\in H(T^\prime_1)$.
+		Then the four graphs $Tree(x_1, T_g)$ and $Tree(x_1,T^\prime_g)$ 
+		for $g=1,2$ satisfy the hypothesis of the lemma.
+		The radius of $Tree(x_1,T^\prime_1)$ is strictly less than $r$, so 
+		because of the induction
+		hypothesis $Tree(x_1, T_1)\morph{k} Tree(f(x_1),T_2)$. 
+		This happens for any vertex $x_1$ in $e$ different from the root $x$.
+		In consequence $e\morph{k}f(e)$ 
 		and using the previous lemma successively we get $T_1\morph{k} T_2$.
@@
 
-\begin{theorem}
-	Let $G_1(c_1,\dots, c_t)$, and $G_2(c_1,\dots,c_t)$ be graphs
+\begin{definition} 
+	Let $G(\clist)$ be a graph with constants. We define $Core(G,r)$ to be
+	$N(X,r)$ where $X$ is the union of constants and clusters of diameter at most $r$. 
+\end{definition}
+
+\begin{theorem} \label{thm:lessradius}
+	Let $G_1(\cc_1,\dots, \cc_t)$, and $G_2(\cc_1,\dots,\cc_t)$ be graphs
 	with constants such that for some $r\in N$
-	\[ Core(G_1(c_1,\dots, c_t);r)\morph{k} Core(G_2(c_1,\dots,c_t);r)\]
+	\[ Core(G_1(\cc_1,\dots, \cc_t);r)\morph{k} Core(G_2(\cc_1,\dots, \cc_t);r)\]
 	through $f$. 
 	Then, for any $s<r$
-	\[ Core(G_1(c_1,\dots, c_t);s)\morph{k} Core(G_2(c_1,\dots,c_t);s).\]
+	\[ Core(G_1(\cc_1,\dots, \cc_t);s)\morph{k} Core(G_2(\cc_1,\dots, \cc_t);s).\]
 \end{theorem}
@@
 	Fix $s<r$. Let us introduce some notation
-	\[ H_i:= Core(G_i(c_1,\dots, c_t);r) \quad \text{for }i=1,2.\]
-	\[ H^\prime_i:= Core(G_i(c_1,\dots, c_t);s) \quad \text{for }i=1,2.\]
-	One can check $H^\prime_i\subseteq H_i$ for $i=1,2$, and that the isomorphism 
-	$f:Center(H_1)\rightarrow Center(H_2)$ restricts to one between
-	$Center(H^\prime_1)$ and $Center(H^\prime_2)$. Let $v\in Center(H^\prime_1)$.
-	Let $T=Tree(v,H^\prime_1)\cap Center(H_1)$. It is not hard to see that $T$ is connected 
+	\[ F_i:= Core(G_i(\cc_1,\dots, \cc_t);r) \quad \text{for }i=1,2.\]
+	\[ F^\prime_i:= Core(G_i(\cc_1,\dots, \cc_t);s) \quad \text{for }i=1,2.\]
+	One can check $F^\prime_i\subseteq F_i$ for $i=1,2$, and that the isomorphism 
+	$f:Center(F_1)\rightarrow Center(F_2)$ restricts to one between
+	$Center(F^\prime_1)$ and $Center(F^\prime_2)$. Let $v\in Center(F^\prime_1)$.
+	Let $T=Tree(v,F^\prime_1)\cap Center(F_1)$. It is not hard to see that $T$ is connected 
 	and in consequence is a tree. The following identity holds:
-	\[ Tree(v,H^\prime_1)= (Tree(v,H_1)\cap N(v;s)) \cup Tree(T,H^\prime_1) \]
+	\begin{equation} \label{eqn:union}
+	Tree(v,F^\prime_1)= (Tree(v,F_1)\cap N(v;s))
+	\cup Span(T, Tree(v,F^\prime_1)) 
+	\end{equation}
+	And analogously for $f(v), f(T), F_2$ and $F^\prime_2$.\par
 	Also, for any $w\in V(T)$
-	\[Tree(w,Tree(v,H^\prime_1),T) = Tree(w,H_1)\cap N(w; s-dist(Center(H^\prime_1),w)).\]
-	So, by lemma REF 
-	\[Tree(w,Tree(v,H^\prime_1),T)\morph{k}Tree(f(w),Tree(f(v),H^\prime_2),f(T)).\]
-	In consequence, by lemma REF,
-	\[Tree(T,H^\prime_1)\morph{k} Tree(f(T),H^\prime_2).\]
-	Using that 
-	\[Tree(v,H_1)\cap N(v;s)\morph{k} \morph{k} Tree(v,H_1)\cap N(v;s),\]
-	and lemma REF we obtain
-	\[Tree(v,H^\prime_1)\morph{k} Tree(f(v),H^\prime_2) .\]
-	Hence, $H^\prime_1\morph{k} H^\prime_2$, as desired. 
-\end{proof}
-
-\begin{lemma}
+	\[Span(w,T, Tree(v,F^\prime_1)) =
+	Tree(w,F_1)\cap N(w; s-d(Center(F^\prime_1),w)).\]
+	So, by \cref{lem:radiustree}
+	\[Span(w,T,Tree(v,F^\prime_1))\morph{k}
+	Span(f(w),f(T),Tree(f(v),F^\prime_2)).\]
+	In consequence, by \cref{lem:isosubtree},
+	\begin{equation} \label{eqn:span}
+	Span(T,Tree(v,F^\prime_1))\morph{k} Span(f(T),Tree(f(v),F^\prime_2)).
+	\end{equation}
+	Again, by \cref{lem:radiustree} 
+	\begin{equation} \label{eqn:entorno}
+	(Tree(v,F_1)\cap N(v;s))\morph{k}(Tree(f(v),F_1)\cap N(f(v);s)).
+	\end{equation}
+	Finally, using that
+	\[(Tree(v,F_1)\cap N(v;s))\cup Span(T,Tree(v,F^\prime_1))=v\]
+	and
+	\[(Tree(f(v),F_2)\cap N(f(v);s))\cup Span(f(T),Tree(f(v),F^\prime_2))=f(v)\]
+	together with \cref{eqn:union},
+	\cref{eqn:span}, \cref{eqn:entorno} and \cref{lem:addtrees} we get:
+	\[Tree(v,F^\prime_1)\morph{k} Tree(f(v),F^\prime_2) .\]
+	Hence, $F^\prime_1\morph{k} F^\prime_2$, as desired. 
+\end{proof}
+
+Let $(T,x)$ be a rooted tree and let $e\in H(T)$ be an initial edge.
+We will denote by $T\setminus e$ the tree $T[X]$, where
+\[ X= \{\, y\in V(T) \, | \, \forall z\in e, z\neq x: \, y\notin V(Tree(z,T)) \, \}.\]
+In other words, $T\setminus e$ is the result of removing from $T$ the edge $e$ and
+all the trees that ``hang" from $e$.
+
+\begin{lemma} \label{lem:minusedge}
 	Let $(T_1,x)$, $(T_2, y)$ be rooted trees such that for some $k\geq 0$
@@
 \end{lemma}
-
-\begin{proof}
-	For any $k$-morphism class $C$ of rooted edges clearly either
-	\[|(T_1\setminus e_1,C)|=|(T_2\setminus e_2,C)|,\]
+\begin{proof}[Sketch of the proof.]
+	For any $k$-morphism class $E$ of rooted edges clearly either
+	\[\langle T_1\setminus e_1,E \rangle =\langle T_2\setminus e_2,E \rangle ,\]
 	or both quantities are greater than $k-1$.
-	Now, using that any $k-1$ morphism class of rooted edges is union of
-	$k$ morphism classes the result follows. 	
-\end{proof}
-
-\begin{lemma}
+	Now, after an induction process analogous to the one in \cref{lem:lessktree}
+	the result follows. 	
+\end{proof}
+
+\begin{lemma} \label{lem:path}
 	Let $(T_1,x_1)$, $(T_2,x_2)$ be rooted trees such that for some $k\geq 0$
@@
 	The proof is by induction on $d(x_1, v)$.
-	\begin{itemize}
+	\begin{itemize}[leftmargin=*]
 		\item If $d(x_1,v)=0$ then $x_1=v$ and the statement is true taking $w=x_2$.
-		\item Suppose now that $d(x_1,v)=r$. Then one can write the path $P(v)$ as a
-		succession of edges $e_1,e_2,\dots, e_s$, where $v\in e_s$. Let $v^\prime$ be 
-		the root of $e_s$. Then $d(x_1,v^\prime)=r-a(e_s)+1$. Thus, by the
+		\item Suppose now that $d(x_1,v)=r$. Then, by
+		\cref{prop:pathform} one can write the path $P(v)$ as a
+		succession of edges $e_1,e_2,\dots, e_s$, where $v\in e_s$.
+		Let $v^\prime$ be the root of $e_s$, and let $b$ be the color
+		of $e_s$.
+		Then $d(x_1,v^\prime)=r-a_b+1$.
+		Thus, by the
 		induction hypothesis there exists $w^\prime$ such that there is an isomorphism
@@
 		$Tree(v_j,T_1)\morph{k} Tree(w_j,T_2)$. Let $j$ be such that $v=v_j$. Then we can take
-		$w=w_j$, and extend the isomorphism $f$ in the evident way. 
-	\end{itemize}
-\end{proof}
-
-\begin{theorem} 
-	Let $G_1(c_1,\dots, c_t)$, and $G_2(c_1,\dots,c_t)$ be graphs
+		$w=w_j$, and extend the isomorphism $f$ to one between $P(v)$ and
+		$P(w^\prime)\cup e^\prime$
+		in the evident way. 
+	\end{itemize}
+\end{proof}
+
+\begin{theorem} \label{thm:chooseconstant}
+	Let $G_1(\cc_1,\dots, \cc_t)$, and $G_2(c_1,\dots,c_t)$ be graphs
 	with constants such that 
-	\[ Core(G_1(c_1,\dots, c_t);r)\morph{k} Core(G_2(c_1,\dots,c_t);r)\]
+	\[ Core(G_1(\cc_1,\dots, \cc_t);r)\morph{k} Core(G_2(c_1,\dots,c_t);r)\]
 	by means of $f$. 
-	Then, for any vertex $x\in Core(G_1(c_1,\dots, c_t);r)$ there is a vertex
-	$y\in Core(G_2(c_1,\dots, c_t);r)$ such that 
-	\[Core(G_1(c_1,\dots, c_t,c_{t+1}[v_1]);r)\morph{k-1} Core(G_2(c_1,\dots,c_t,c_{t+1}[v_2]);r)\]
+	Then, for any vertex $x\in Core(G_1(\cc_1,\dots, \cc_t);r)$ there is a vertex
+	$y\in Core(G_2(\cc_1,\dots, \cc_t);r)$ such that 
+	\[Core(G_1(\cc_1,\dots, \cc_t,\cc_{t+1}[v_1]);r)\morph{k-1} Core(G_2(c_1,\dots,c_t,\cc_{t+1}[v_2]);r)\]
 \end{theorem}
@@
 	Let us introduce some notation:
-	\[H_i:=Core(G_i(c_1,\dots, c_t);r)\quad \text{for }i=1,2. \]
-	\[H^\prime_1:=Core(G_1(c_1,\dots, c_t,c_{t+1}[v_1]);r).\]
-
-	The vertex $v_1$ belongs to $Tree(x_1,H_1)$
-	for a unique $x_1\in Center(H_1)$. By the previous lemma there exist a vertex $v_2$ in 
-	$Tree(f(x_1),H_2)$ such that the path $P(v_1)$, 
+	\[F_i:=Core(G_i(\cc_1,\dots, \cc_t);r)\quad \text{for }i=1,2. \]
+	\[F^\prime_1:=Core(G_1(\cc_1,\dots, \cc_t,\cc_{t+1}[v_1]);r).\]
+
+	The vertex $v_1$ belongs to $Tree(x_1,F_1)$
+	for a unique $x_1\in Center(F_1)$. By the previous lemma there exist a vertex $v_2$ in 
+	$Tree(f(x_1),F_2)$ such that the path $P(v_1)$, 
 	joining $v_1$ and $x_1$, is isomorphic to the path
@@
 	Let 
-	\[H^\prime_2:=Core(G_1(c_1,\dots, c_t,c_{t+1}[v_2]);r).\]
-	We are going to show that $H^\prime_1\morph{k-1}H^\prime_2$.
-	Clearly $Center(H^\prime_i)=Center(H_i)\cup P(v_1)$ for $i=1,2$ , so we can glue
-	$f$ and $f^\prime$ into an isomorphism $g:Center(H^\prime_1)\rightarrow Center(H^\prime_2)$.
-	Let $w_1\in H^\prime$. Then either
-	\begin{itemize}
-		\item $Tree(w_1,H_1)$ contains no edges in $P(v_1)$. 
-		In this case $Tree(w_1,H^\prime_1)=Tree(w_1,H_1)$.
-		Thus, $Tree(w_1,H^\prime_1)\morph{k} Tree(g(w_1),H^\prime_1)$
-		and $Tree(w_1,H^\prime_1)\morph{k-1} Tree(g(w_1),H^\prime_1)$
-		in consequence by lemma REF.
-		\item $Tree(w_1,H_1)$ contains edges from $P(v_1)$.
-		In this case, $Tree(w_1,H_1)$ contains exactly one initial edge
-		$e_1$ in $P(v_1)$, and $Tree(w_1,H^\prime_1)=Tree(w_1,H_1)\setminus e_1$.
-		One can check that $Tree(g(w_1),H_2)$ contains exactly one edge
+	\[F^\prime_2:=Core(G_1(\cc_1,\dots, \cc_t,\cc_{t+1}[v_2]);r).\]
+	We are going to show that $F^\prime_1\morph{k-1}F^\prime_2$.
+	Clearly $Center(F^\prime_i)=Center(F_i)\cup P(v_1)$ for $i=1,2$ , so we can glue
+	$f$ and $f^\prime$ into an isomorphism $g:Center(F^\prime_1)\rightarrow Center(F^\prime_2)$.
+	Let $w_1\in V(F^\prime_1)$. We have to show that 
+	\[Tree(w_1, F^\prime_1)\morph{k-1} Tree(g(w_1), F^\prime_2)\]
+	and the result will be prove. The following two cases may occur:
+	\begin{itemize}[leftmargin=*]
+		\item $Tree(w_1,F_1)$ contains no edges in $P(v_1)$. 
+		In this case $Tree(w_1,F^\prime_1)=Tree(w_1,F_1)$.
+		Thus, $Tree(w_1,F^\prime_1)\morph{k} Tree(g(w_1),F^\prime_1)$
+		and $Tree(w_1,F^\prime_1)\morph{k-1} Tree(g(w_1),F^\prime_1)$
+		in consequence by \cref{lem:lessktree}.
+		\item $Tree(w_1,F_1)$ contains edges from $P(v_1)$.
+		In this case, $Tree(w_1,F_1)$ contains exactly one initial edge
+		$e_1$ in $P(v_1)$, and 
+		\[Tree(w_1,F^\prime_1)=Tree(w_1,F_1)\setminus e_1. \]
+		One can check that $Tree(g(w_1),F_2)$ contains exactly one edge
 		in $P(v_2)$, namely $g(e_1)$, and 
-		$Tree(g(w_1),H^\prime_2)=Tree(g(w_1),H_2)\setminus g(e_1)$.
-		We had $Tree(w_1,H_1)\morph{k}Tree(g(w_1),H_2)$, so by lemma REF
-		$Tree(w_1,H^\prime_1)\morph{k-1}Tree($ $g(w_1),H^\prime_2)$.	
+		\[Tree(g(w_1),F^\prime_2)=Tree(g(w_1),F_2)\setminus g(e_1).\]
+		We had $Tree(w_1,F_1)\morph{k}Tree(g(w_1),F_2)$, so by
+		\cref{lem:minusedge}
+		\[Tree(w_1,F^\prime_1)\morph{k-1}Tree(g(w_1),F^\prime_2)\].	
 	\end{itemize}
@@
 	Let $G_1,G_2$ be graphs with constants. We say that $G_1$ and $G_2$ are
-	$k$-agreeable if for each $\morph{k}$ class $C$ of connected graphs either
-	\begin{itemize}
-		\item $G_1$ and $G_2$ have the same number of connected components of type $C$, or
-		\item Both $G_1$ and $G_2$ have no less than $k$ connected components of type $C$.
-	\end{itemize} 
-\end{definition}
+	$k$-agreeable if for each $\morph{k}$ class $U$ of connected graphs either
+	\begin{itemize}
+		\item $G_1$ and $G_2$ have the same number of connected components of type $U$, or
+		\item Both $G_1$ and $G_2$ have no less than $k$ connected components of type $U$.
+	\end{itemize} 
+\end{definition}
+
+\begin{definition} 
+	Two graphs with constants $G_1$ and $G_2$ are $k$-agreeable if for each $k$-morphism 
+	equivalence class $C$ they either have the same number of connected components of type
+	$C$ or they both have no less than $k+1$ components of type $C$. 
+\end{definition}
+
+Given a graph with constants $G$ and a $\morph{k}$ class of connected
+graphs $U$, we define the number $\langle G, U \rangle$ as the number
+of connected components of $G$ belonging to $U$. \par
+If $O$ is a $k$-agreeability class and $G\in O$ is a
+representative of it, we define the number $\langle O, U \rangle$ to
+be the maximum between $\langle G,U \rangle$ and $k+1$.
+
+\begin{definition}
+	A (hyper)graph $G$ is $i,k,r$-rich for some $j,k,r\in \N$, if for any rooted tree $T$
+	of radius at most $r$ there are $x_1,\dots,x_i\in V(G)$ such that
+	\begin{itemize}
+		\item The $d(x_l,x_s)\geq 4r$ if $l\neq s$.
+		\item The $N(x_l;r)$'s do not intersect $Core(G,r)$
+		\item $N(x_l;r)(x_l) \morph{k} T$.		
+	\end{itemize} 
+\end{definition}
+
+The following is a corollary of \cref{lem:lessktree} and \cref{lem:radiustree}.
+
+\begin{lemma} \label{lemm:rich}
+	Let $i,k,r\in \N$ be all positive numbers, and let $G(\clist)$
+	be a $(i,k,r)$-rich graph with constants. Then, for any $x\in V(G)$,
+	the graph $G(\clist, \cc_{m+1}(x))$ is $(i-1,j,s)$-rich, 
+	where $j,s$ are arbitrary natural numbers satisfying $j\leq k$,
+	and $s\leq r$.
+\end{lemma}
 
 \begin{theorem} 
-	Let $G_1, G_2$ be $k,3^k$-rich graphs such that $Core(G_1;3^k)$ is $k$-agreeable
-	with $Core(G_2;3^k)$. Then Duplicator has a winning strategy in 
-	the $E.F$ game on $G_1$ and $G_2$. 
+	Let $G_1, G_2$ be $k,k,3^k$-rich graphs such that $Core(G_1;3^k)$ is $k$-agreeable
+	with $Core(G_2;3^k)$. Ten $G_1$ and $G_2$ have the same rank $k$ type.
 \end{theorem}
 \begin{proof}
+	We will prove that Duplicator has a winning strategy in 
+	the $E.F$ game on $G_1$ and $G_2$ with $k$ rounds. 
 	We will show, by induction on $i$, that Duplicator can play in such a way
-	that in the $i$-th round $Core(G_1(c_1[x_1],\dots,c_i[x_i]);3^{k-i})$
-	is $k-i$-agreeable with  $Core(G_2(c_1[y_1],\dots,c_i[y_i]);3^{k-i})$,
-	where for each $j=1,\dots,i$,0 $x_j,y_j$ are the $j$-th 
-	chosen vertex in the graphs $G_1$ and $G_2$	respectively. After this the theorem
+	that in the $i$-th round
+	\[Core(G_1(\cc_1[x_1],\dots,\cc_i[x_i]);3^{k-i}) \]
+	is $k-i$-agreeable with  
+	\[ Core(G_2(\cc_1[y_1],\dots,\cc_i[y_i]);3^{k-i}) \],
+	where for each $1\leq j \leq i$, the vertices
+	$x_j$ and $y_j$ are the ones chosen in the $j$-th 
+	round of the game in the graphs $G_1$ and $G_2$ respectively. 
+	After this the theorem
 	follows because
-	$Core(G_1(c_1[x_1],\dots,c_i[x_k]);1)$ being $0$-agreeable with
-	$Core(G_2(c_1[y_1],\dots,c_i[y_k]);1)$ implies that
+	$Core(G_1(\cc_1[x_1],\dots,c_i[x_k]);1)$ being $0$-agreeable with
+	$Core(G_2(\cc_1[y_1],\dots,c_i[y_k]);1)$ implies that
 	the map given by $x_i\mapsto y_i$ defines a partial isomorphism. \par
@@
 		\item For $i=0$ the statement is true by hypothesis. 
-		\item Assume now that $Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$
-		is $k-i+1$-agreeable with $Core(G_2(c_1[y_1],\dots, c_i[y_{i-1}]); 3^{k-i+1})$.
+		\item Assume now that $Core(G_1(\cc_1[x_1],\dots,\cc_i[x_{i-1}]);3^{k-i+1})$
+		is $(k-i+1)$-agreeable with $Core(G_2(\cc_1[y_1],\dots, \cc_i[y_{i-1}]); 3^{k-i+1})$.
 		Without loss of generality we can suppose that Spoiler chooses a vertex 
-		$x_i$ in $G_1$ in the $i$-th round. We have two cases.
+		$x_i$ in $G_1$ in the $i$-th round. We have two cases: \par
+		\textbf{Case 1.} $N(x_i;3^{k-i})$ is contained in 
+			$Core(G_1(\cc_1[x_1],\dots,\cc_i[x_{i-1}]);3^{k-i+1})$.
+			Let $F_1$ be the connected component of 
+			$Core(G_1(\cc_1[x_1],\dots,\cc_i[x_{i-1}]);3^{k-i+1})$
+			containing $N(x_i;3^{k-i})$. Then there is a connected component $F_2$
+			in \\ 
+			$Core(G_2(\cc_1[y_1],\dots,\cc_i[y_{i-1}]);3^{k-i+1})$ such that
+			$F_1 \morph{k-i+1} F_2$. Applying \cref{thm:chooseconstant} and 
+			\cref{thm:lessradius} successively Duplicator can choose
+			$y_i\in V(F_2)$ such that 
+			\[ Core(F_1(\cc_i[x_i]); 3^{k-1})\morph{k-i} Core(F_2(\cc_i[y_i]); 3^{k-1}).\]
+			Using \cref{thm:lessradius} 
+			and counting the connected components in each $k-i$-morphism class
+			one can check that now $Core(G_1(\cc_1[x_1],\dots,\cc_i[x_i]);3^{k-i})$
+			is $k-i$-agreeable with  $Core(G_2(\cc_1[y_1],\dots,\cc_i[y_i]);3^{k-i})$.
+			\par
+		\textbf{Case 2.} $N(x_i;3^{k-i})$ is contained in 
+			$Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$. Then
+			$N(x_i;3^{k-i})$ is disjoint from $Core(G_1(\cc_1[x_1],\dots,\cc_i[x_{i-1}]);3^{k-i})$
+			and in particular, $N(x_i;3^{k-i})$ is a tree. As $G_2$
+			was originally $k,k,3^k$-rich, using \cref{lemm:rich} we obtain
+			that $G_2(\cc_1[y_1],\dots,\cc_i[y_{i-1}])$ is
+			$(k-i+1,k-i+1,3^{k-i+1})$-rich. Hence,
+			Duplicator can choose $y_i$ in $G_2$ such that $N(y_i;3^{k-i})$ is disjoint from \\
+			$Core(G_2(\cc_1[y_1],\dots,\cc_i[y_{i-1}]);3^{k-i})$ and the tree $N(x_i;3^{k-i})$
+			rooted at $x_i$ is $(k-i)$-morphic to the tree $N(y_i;3^{k-i})$ rooted at $y_i$.
+			Counting connected components of each type we can conclude that
+			$Core(G_1(\cc_1[x_1],\dots,\cc_i[x_i]);3^{k-i})$
+			is $(k-i)$-agreeable with  $Core(G_2(\cc_1[y_1],\dots,\cc_i[y_i]);3^{k-i})$.
+		  	\end{itemize}
+\end{proof}
+
+\section{Probabilistic results}
+
+\subsection{Almost All Graphs are Simple}
+
+\begin{definition} 
+	A graph $G$ is $r$-simple if all connected components of $Core(G;r)$
+	are unicycles. 
+\end{definition}
+
+A $k$-agreeability class $O$ is called simple if all the graphs
+belonging to it are disjoint unions of unicycles.
+
+\begin{proposition}\label{prop:supercritical}
+	Let $F$ be a cluster with $L(F)<0$, and let $X_n$ be the
+	random variable that counts the number of times that $H$ appears
+	as a subgraph of $HG(n,p(n))$. Then
+	\[\Ln Pr(X_n>0)=0. \]
+\end{proposition}
+\begin{proof}
+	Let $v=|V(F)|$ and $h_i=|H_i(F)|$ for $i=1,\dots, l$. 
+	Chose a ordering of the vertices in $H$. 
+	For any ordered sequence of vertices $S=(x_1, \dots, x_v)$, 
+	let $X_{n,S}$ be the indicator variable that equals $1$ if $F$
+	is a subgraph of $G[S]$ (in a way that respects the ordering) and
+	$0$ otherwise. Clearly $X_n$ is the sum of all the $X_{n,S}$'s, so
+	\[ E(X_n)= \frac{n(n-1)\cdots (n-v+1)}{b} \prod_{i=1}^{l}
+	\left( \frac{c_i}{n^{a_1-1}}\right)^{h_i}, \] 
+	where $b$ is the carnality of $F$'s group of isomorphisms. 
+	Then, for some constant $A$,
+	\[ \Ln E(X_n)\leq \Ln A\cdot n^{L(H)}, \]
+	and using that $L(E)<0$, this limit is zero.
+	Using the first moment method the result follows. 
+\end{proof}
+
+\begin{lemma}
+	Let $G$ be a critical graph of radius $r$.
+	Then $G$ contains a critical subgraph with size no greater than
+	$(a+2)(r+1)+2a$, where $a$ is the largest edge size in $G$. 
+\end{lemma}
+\begin{proof}
+	Choose $x\in V(G)$. Successively remove from $G$ edges $e$
+	such that $d(x, e)$ is maximum until the resulting graph 
+	$G^\prime$ has likelihood no less than $0$. We have two cases:
 	\begin{itemize}[leftmargin=*]
-			\item[Case 1.] $N(x_i;3^{k-i})$ is contained in 
-			$Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$.
-			Let $H_1$ be the connected component of $Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$
-			containing $N(x_i;3^{k-i})$. Then there is a connected component $H_2$
-			in $Core(G_2(c_1[y_1],\dots,$ $c_i[y_{i-1}]);3^{k-i+1})$ such that
-			$H_1 \morph{k-i+1} H_2$. Applying theorems REF and REF successively Duplicator can choose
-			$y_i\in V(H_2)$ such that 
-			\[ Core(H_1(c_i[x_i]); 3^{k-1})\morph{k-i} Core(H_2(c_i[y_i]); 3^{k-1}).\]
-			Using Theorem Ref and counting the connected components in each $k-i$-morphism class
-			one can check that now $Core(G_1(c_1[x_1],\dots,c_i[x_i]);3^{k-i})$
-			is $k-i$-agreeable with  $Core(G_2(c_1[y_1],\dots,c_i[y_i]);3^{k-i})$.
-			\item[Case 2.] $N(x_i;3^{k-i})$ is contained in 
-			$Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$. Then
-			$N(x_i;3^{k-i})$ is disjoint from $Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i})$
-			and in particular, $N(x_i;3^{k-i})$ is a tree. As $G_2$ was originally $k,3^k$-rich
-			Duplicator can choose $y_i$ in $G_2$ such that $N(y_i;3^{k-i})$ is disjoint from 
-			$Core(G_2(c_1[y_1],\dots,c_i[y_{i-1}]);3^{k-i})$ and the tree $N(x_i;3^{k-i})$
-			rooted at $x_i$ is $k-i$-morphic to the tree $N(y_i;3^{k-i})$ rooted at $y_i$.
-			Counting connected components of each type we can conclude that
-			$Core(G_1(c_1[x_1],\dots,c_i[x_i]);3^{k-i})$
-			is $k-i$-agreeable with  $Core(G_2(c_1[y_1],\dots,c_i[y_i]);3^{k-i})$.
-		\end{itemize}  		
-	\end{itemize}
-
-\end{proof}
-
-Define the families of expressions with arguments $\beta_1,\dots, \beta_l$: 
-$\Lambda$, $M$ and $\Theta$. \par
-For any sentence $\phi$ we use the notation 
-$Pr_n(\phi):=Pr(G\models \phi)$. \par
+		\item $L(G^\prime)=1$. Let $e=[x_1, \dots, x_b]$ be
+		the last removed edge and
+		$e\cap G^\prime=\{ x_{i_1}, \dots, x_{i_c}\}$.
+		For any $j=1,\dots, c$ choose 
+		$P_j$ a path of size no greater than $r+1$ joining
+		$x$ and $x_{i_j}$ in $G^\prime$.   
+		Then $P_1\cup \dots P_c \cup e$ is a critical subgraph of $G$
+		of size less than $a(r+1) + a< (a+2)(r+1) + 2a$.
+		\item $L(G^\prime)=0$. Let $e_1=[x_1, \dots, x_{b_1}]$ be the
+		last removed edge. Continue removing the edges of $G^\prime$ 
+		that are at maximum distance from $x$ until you obtain 
+		$G^{\prime \prime}$ with $L(G^{\prime\prime})=1$. Let 
+		$e_2=[y_1, \dots, y_{b_1}]$ be the last removed edge.
+		As before, let $e_1\cap G^\prime=\{ x_{i_1}, \dots, x_{i_c}\}$
+		and for $j=1,\dots, c$ let $P_j$ a path of size no greater than $r+1$ 
+		joining	$x$ and $x_{i_j}$ in $G^\prime$
+		Then $e_2 \cup G^{\prime \prime}=\{ y_{i_1}, y_{i_2}  \}$.
+		Let $Q_1, Q_2$ be paths size no greater than $r+1$ from
+		$x$ to $y_{i_1}$ and $y_{i_2}$ in $G^{\prime \prime}$.
+		Then $Q_1 \cup Q_2 \cup e_2$ is a graph of likelihood $0$ 
+		and size less than $2r+2 + a$,
+		and $Q_1\cup Q_2\cup P_1 \cup \dots \cup P_c \cup e_1 \cup e_2$ 
+		is a critical graph	with size less than $(2+a)(r+1) + 2a$	
+	\end{itemize} 
+\end{proof}
+
+\begin{corollary}
+	Let $A_n$ be the event that $HG(n,p(n))$ contains critical 
+	subgraph with diameter no greater than $r$. Then
+	\[ \Ln Pr(A_n)=0. \]
+\end{corollary}
+\begin{proof}
+	If a random graph contains $G$ such critical graph, then by the previous
+	lemma it has to contain a critical graph of size less than some constant $M$.
+	The number of critical graphs of such size is finite and by
+	\cref{prop:supercritical} the probability 
+	that any one of those appears as a subgraph of $G$ is asymptotically zero.	 
+\end{proof}
+
+\begin{corollary} \label{thm:simple} 
+	For any $r$,
+	\[\Ln Pr(G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1} ) \text{ is }r \text{-simple})=1 .\]
+\end{corollary}
+\begin{proof}
+	One can check that if $G$ contains no super-critical subgraphs of
+	diameter at most $4r$ then $G$ is $r$-simple.
+\end{proof}
+
+\subsection{Probabilities of Trees. Almost All Graphs are Rich.}
+
 For any formula $\phi$ with free variables 
@@
 
-\begin{lemma}
+\begin{lemma} \label{lem:faraway}
 	Let $\sigma$ be an open formula (i.e., a formula with no quantifiers)
@@
 		in their intersection. Then, using that
-		$ch(P_1), ch(P_2)\geq -1$ and counting we get that
+		$L(P_1), L(P_2)\leq 1$ and counting we get that
 		$P_1\cup P_2$ is a critical graph of size no greater
@@
 
-\begin{theorem} 
-	Let $\sigma(x_1,\dots, x_l)$ be a consistent open formula, and let $k,r,s\in \N$ $s\leq l$. Then, for any $k$-morphism classes $C_1, 
+\begin{theorem} \label{thm:probtrees}
+	Let $k\in N$. 
+    For all $r\in N$ and any $k$-morphism class of trees with radius
+	at most $r$ there exist expressions $\lambda_{k,C,r}\in \Lambda$ 
+	such that:
+	\item for any consistent open formula $\sigma(x_1,\dots, x_l)$, $r,s\in \N$ $s\leq l$ and any $k$-morphism classes $C_1, 
 	\dots, C_s$ of trees with radii
@@
 	\[ \Ln Pr_n(\bigwedge_{i=1}^s Tree_r(x_i; x_1, \dots, x_l)\in C_i \, | 
-	\, \sigma(x_1,\dots, x_l) \,)= \prod_ {i=1}^s \lambda_{C_i,r}.\]	
+	\, \sigma(x_1,\dots, x_l) \,)= \prod_ {i=1}^s \lambda_{k,C_i,r}.\]	
 \end{theorem}
 \begin{proof}
+Consider $k$ fixed.
 The proof is by induction on $r$.
@@
 	the statement is always $1$ for all $n$.
+	Thus, taking $C$ the $k$-morphism class of the isolated
+	vertex, one can define $\lambda_{k,C,0}=1$. 
 	\item Fix $r>0$ and assume that the statement
@@
 	denote by $\psi_E$ the subgroup of the symmetry group of $\phi_{c_E}$ 
-	that fixes the index $j_E$.
+	that fixes the chosen representative of $E$.
 	Consider, for each $i=1,\dots, s$ and each the random variables 
@@
 	\end{align*}
-	But using lemma REF we get
+	But using \cref{lem:faraway} we get
 	\[ \Ln  Pr_n(T(z) \wedge \phi_r(x_1,\dots,x_l)
@@
  	\Gamma:=\prod_{\substack{1\leq i \leq s \\ E\in \mathcal{E}\\
- 	1\leq j \leq a_E - 1 }} (\lambda_{C_{E,j}})^{b_{i,E}}.
+ 	1\leq j \leq a_E - 1 }} (\lambda_{k,C_{E,j}})^{b_{i,E}}.
  	\end{equation}
@@
  	\binom{X_{i,E}}{b_{i,E}} \, \Bigg| \, \sigma \right]= \prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
- 	\left[ 	\left(\frac{\beta_{c_E} \prod_{j=1}^{a_E -1} \lambda_{C_{E,j}} }{|\psi_E|}\right)^{b_{i,E}} \frac{1}{b_{i,E}!} \right]. \]
+ 	\left[ 	\left(\frac{\beta_{c_E} \prod_{j=1}^{a_E -1} \lambda_{k,C_{E,j}} }{|\psi_E|}\right)^{b_{i,E}} \frac{1}{b_{i,E}!} \right]. \]
  	And using the multivariate Brun's Sieve we get that for each
@@
  	\[ \Ln Pr_n\left(\bigwedge_{i=0}^{s}\bigwedge_{E\in \mathcal{E}} X_{i,E}=b_{i,E} \, \Bigg| \, \sigma \right) = 
- 	\prod_{i=0}^{s}\prod_{E\in \mathcal{E}} Poi_{\mu_E}(b_{i,E}),\]
- 	where
- 	\[\mu_E=
- 	\frac{\beta_{c_E} \prod_{j=1}^{a_E -1} \lambda_{C_{(E,j)},(r-a_E+1)} }{|\psi_E|}.\]
+ 	\prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
+ 	Poi_{\mu_{E,(r-a_E+1)}}(b_{i,E}),\]
+ 	where we define
+ 	\[\mu_{E,(r-a_E+1)}=
+ 	\frac{\beta_{c_E} \prod_{j=1}^{a_E -1} \lambda_{k,C_{(E,j)},(r-a_E+1)} }{|\psi_E|}.\]
+ 	Notice that $\mu_{E,(r-a_E+1)}$ is an expression in $M$.
  	The $k$-morphism class of $T_r(x_j;x_1, \dots, x_l)$ depends exclusively
@@
  	&=\prod_{i=0}^{s}\left[
- 	\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)<k+1}} Poi_{\mu_E}((C_i,E))\right)
+ 	\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)<k+1}} Poi_{\mu_{E,(r-a_E+1)}}((C_i,E))\right)
  	\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)\geq k+1}} 
- 	Poi_{\mu_E}(\geq (k+1))\right)\right]=\\
- 	&=\prod_{i=0}^{s} \lambda_{C_i,r},
+ 	Poi_{\mu_{E,(r-a_E+1)}}(\geq (k+1))\right)\right]=\\
+ 	&=\prod_{i=0}^{s} \lambda_{k,C_i,r},
     \end{align*}
- 	as we wanted. 
-%n^{\sum_{i=1}^s
+    where we define
+    \[
+    \lambda{C_i,r}=\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)<k+1}} Poi_{\mu_{E,(r-a_E+1)}}((C_i,E))\right)
+    \left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)\geq k+1}} 
+    Poi_{\mu_{E,(r-a_E+1)}}(\geq (k+1))\right)
+    .\]
+    Notice that $\lambda{C_i,r}$ belongs to $\Lambda$, and its
+    definition depends only
+    on the previously defined $\lambda$'s for lesser values of $r$, 
+    and on the choice of $C_i, r$, as we wanted.
+
 %	\sum_{E\in \mathcal{E}} b_{i,E}\cdot(a_{E}-1)}
@@
 %	
-
-	\end{proof}
-
-\begin{theorem}
+\end{proof}
+
+\begin{corollary} \label{thm:rich}
+	For any $i,k,r\in \N$
+	\[\Ln Pr_n(\, G \text{ is } i,k,r\text{- rich}\,)=1.\]
+\end{corollary}
+\begin{proof}
+	Fix $i,k,r$, and let $\mathcal{C}$ be the set of all
+	$k$-morphism classes of trees with radius at most $r$.
+	For any $s\in \N$ and $C\in \mathcal{C}$ with $s\geq i$ we define
+	the event $A_{s,C}$ as:
+	\[ \exists x_1, \dots, x_i \in [s]: \quad T_r(x_j;1,dots, s)\in C \quad
+	\forall 1\leq j \leq i.\] 
+	One can check that for all $s$, 
+	\[ \phi_{3r}(1,\dots, s) \bigwedge_{C\in \mathcal{C}} A_{s,C}
+	\implies  G \text{ is } i,k,r\text{- rich}\, .\]
+	This is because  $\phi_{3r}(1,\dots, s)$ means that the
+	vertices $x\in [s]$ are ``far from each other and far from 
+	the cycles of radius $r$''. Thus
+	\begin{equation}\label{eqn:richgeq}
+	\Ln Pr_n\Bigg(\phi_{3r}(1,\dots, s) 
+	\bigwedge_{C\in \mathcal{C}} A_{s,C}\Bigg)
+	\geq \Ln Pr_n(\, G \text{ is } i,k,r\text{- rich}\,).
+	\end{equation}
+	But also, because of lemma LEMM
+	\begin{equation} \label{eqn:richaas}
+	\Ln Pr_n\Bigg(\phi_{3r}(1,\dots, s) 
+	\bigwedge_{C\in \mathcal{C}} A_{s,C}\Bigg)=
+	\Ln Pr_n\Bigg( 
+	\bigwedge_{C\in \mathcal{C}} A_{s,C}\Bigg).
+	\end{equation}
+	Using the intersection bound, we get
+	\[ Pr\Bigg( 
+	\bigwedge_{C\in \mathcal{C}} A_{s,C}\Bigg)\geq
+	1- \sum_{C\in\mathcal{C}} Pr(\neq A_{s,C}).\]
+	Define, for each $s\geq i$, $C\in \mathcal{C}$ the
+	random variable
+	\[ X_{s,C}=|\{ \, y\in [s] \, | \, T_r(y; 1,\dots, s)\in C \,   \}|.\]
+	Because of last theorem $X_{s,C}$ converges in distribution
+	to a binomial variable whose defining probability is $\lambda_{k,C,r}$. 
+	Notice that the event $A_{s,C}$ is precisely the event
+	$X_{s,C}\geq i$. Thus:
+	\begin{align*}
+	 &\Ln Pr_n\Bigg( 
+	\bigwedge_{C\in \mathcal{C}} A_{s,C}\Bigg)\geq
+	\Ln 1- \sum_{C\in\mathcal{C}} Pr_n(\neq A_{s,C})=\\
+	&=\Ln 1- \sum_{C\in\mathcal{C}} Pr_n(X_{s,C}<i)=
+	1- \sum_{j<i} \binom{s}{j}\lambda_{k,C,r}^j(1-\lambda_{k,C,r})^{(s-j)}.
+	\end{align*}
+	This expression goes to $1$ as $s$ goes to infinity because
+	$\lambda_{k,C,r}$ is positive. This means 
+	\[ \lim\limits_{s\to \infty} \Ln Pr_n\Bigg( 
+	\bigwedge_{C\in \mathcal{C}} A_{s,C}\Bigg)=1. \]
+	Finally using \cref{eqn:richgeq} and \cref{eqn:richaas} 
+	we get that 
+	\[\Ln Pr_n(\, G \text{ is } i,k,r\text{- rich}\,)\geq 1\]
+	and the result is proven.
+\end{proof}
+
+\subsection{Probabilities of Unicycles.}
+
+\begin{theorem} \label{thm:probcycles}
+	Let $k\in \N$.
 	Let $O$ be a simple $k$-agreeability class. Then it is satisfied
@@
 \begin{proof}
-	This is an easier version of last theorem. \par
+	This is an easier version of \cref{thm:probtrees}.\par
 	Let $\mathcal{U}$ be the set of all $k$-morphism classes of 
@@
 	the edges between vertices in the image of $z$.
-	Using the previous theorem and LEMMA we obtain
+	Using the previous theorem and \cref{thm:simple} we obtain
 	\[\Ln Pr_n(T(z)\wedge \tau_r \,| \, B(z))= \Ln Pr_n(T(z)| \,| \, B(z)) = \Gamma, \]
@@
 	\[ \Gamma:=\prod_{\substack{U\in \mathcal{U}\\ 1 \leq i\leq n_{U}}}
-	(\lambda_{C_{(U,i)}, r})^{b_U}.\]
+	(\lambda_{k,C_{(U,i)}, r})^{b_U}.\]
 
@@
 	\[ \xi_U= \frac{ \prod_{i=1}^c \beta_i^{|H_i(cycle(U))|} \prod_{i=1}^{n_U} \lambda_{U,i}}{|\psi_U|}.\]
+	Notice that each $\xi_U$ lies in $\widehat{\Theta}$.
 
@@
 	Poi_{\xi_U}(\geq (k+1)) \right),\]
-	as we wanted.   
+	an this last limit belongs to $\Theta$ we wanted.   
+\end{proof}
+
+\subsection{Proof of the Main Theorem.}
+
+We re-estate the main theorem of this section
+
+\begin{theorem} 
+	Let $\beta=(\beta_1,\dots, \beta_c)$, and let $\psi$ be a 
+	F.O sentence in $\mathcal{L}$. Then the function
+	\[
+	\mathfrak{F}(\beta):=\Ln Pr(\, HG(n,p(\beta,n))\, \models \, \psi \,)
+	\]
+	is well defined for all values of $\beta$ and it is a finite sum 
+	of expressions in $\Theta$.
+\end{theorem}
+\begin{proof}
+	Let $k$ be the quantifier rank of $\psi$, and
+	let $O_1,\dots,O_m$ be an enumeration of all $k$-agreeability
+	simple classes of radius at most $3^k$. Because of \cref{thm:simple},
+	\cref{thm:rich} and \cref{thm:probcycles} respectively we have:
+	\begin{itemize}
+		\item[(1)] 
+		\[ \Ln Pr(HG(n,p(n))\in \cup_{i=1}^m O_i)=1,\]
+		\item[(2)] For any $1\leq i \leq m$,
+		\[\Ln Pr_n((G\models \psi) \wedge
+		 (F\models \neg \psi) \, | \, G,F\in O_i\,) = 0, \]
+		 where $G$ and $F$ are independently chosen graphs in $HG(n,p(n,\beta))$.
+		\item[(3)] For any $1\leq i \leq m$,
+		\[ P_i(\beta):= \Ln Pr((HG(n,p(n,\beta)) \in O_i)\]
+		is well defined for all values of $\beta$ and it is an expression
+		in $\Theta$.
+	\end{itemize} 
+ We define the events $E_1,\dots,E_{m}$ as
+\[E_i:= (G \models \psi) \wedge (G \in O_i),\]
+and the  event $F$ as
+\[F:= (G \models \psi) \bigwedge_{i=1}^{m} (G \notin O_i).\]
+Then, for any $n\in \N$
+
+\begin{equation} \label{eqn:sumevents}
+Pr_n(G\models \psi) = \sum_{i=1}^{m} Pr_n(E_i)  + Pr_n(F),
+\end{equation}
+as the events $E_i$ together with $F$ form a partition of all the cases where $G$ satisfies $\psi$. \par
+
+Fix and index $i\in \{1, \dots, m\}$. From (2) follows that 
+the limits 
+\[ \Ln Pr_n(G\models \psi \, | \, G\in O_i )\] 
+are either zero or one, and 
+\begin{align}\label{eqn:property1}
+&\Ln Pr_n(E_i)= \Ln Pr_n(G\in O_i)\cdot Pr_n(G\models \phi \, | \, G\in O_i)=\\ 
+&
+\nonumber
+= \text{ either } 0 \text{ or } \Ln Pr_n(G\in O_i).
+\end{align} 
+\par 
+Also, as a consequence of (1) we obtain
+\[\Ln Pr_n(\bigwedge_{i=1}^{m} G \notin O_i)=0, \] 
+so
+\begin{equation}\label{eqn:property2}
+\Ln Pr_n(F)= \Ln Pr_n(\bigwedge_{i=1}^{m} G \notin O_i)\cdot 
+Pr_n(G\models \phi \, | \, \bigwedge_{i=1}^{m} G \notin O_i)=0.  
+\end{equation}
+\par
+Taking limits in equation \ref{eqn:sumevents} and using equations \ref{eqn:property1} and \ref{eqn:property2} 
+we get
+\[ \Ln Pr_n(G\models \psi) = \sum\limits_{O_i\in \mathcal{O}} \Ln
+Pr_n(G \in O_i) ,\]
+where $\mathcal{O}$ is a (possibly empty) subset of $\{O_1,\dots, O_{m}\}$.
+Finally, because of property (3) for each $i$ the limit $\Ln Pr_n(G \in O_i)$ is 
+an expression in $\Theta$. Thus $\Ln Pr_n(G\models \psi)$ is a finite sum of expressions in $\Theta$ and the theorem follows.
 \end{proof}

### 2019-06-25 BGSM/Motivletter/Motivationletter.tex
BGSM stuff

\documentclass{letter}
\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm]{geometry}

\signature{Lázaro Alberto Larrauri Borroto}

\begin{document}
	\begin{letter}{}
		\opening{To Whom It May Concern:}
		\vspace{1cm}
		I am writing to submit my application for the Maria de Maeztu Master Internships Programme for
		2019. I am currently a student at the Master's degree in Advanced Mathematics and Mathematical
		Engineering offered by the Universitat Politécnica de Catalunya. I graduated from the University of
		Zaragoza in a Degree of Mathematics with various honours marks in subjects related to algebra, 
		discrete mathematics and geometry. I have participated in several math, physics and chemistry competitions 
		since secondary school and got good results in most of them.
		I came to know about the math masters programs offered here, in Barcelona, because of a friend 
		from those competitions, and I became interested. \par
	    My interest in research originated in secondary school, where I developed a strong liking and predisposition for
	    creative and intellectual activities. 
	    Eventually I decided to study math because I believe that it allows oneself to solve interesting, meaningful 
	    problems in creative ways. My main areas of interest are logic, discrete mathematics and algebra, 
	    as well as their applications in other fields, particularly computer science.  
		Recently, I got the opportunity to work on a master's thesis project under the supervision of Marc Noy Serrano,
		involving original research on logic, discrete mathematics and probability. I am very motivated by this project and I think
		it is a great chance for me to get more involved with research and to work hard doing things I enjoy.

		\closing{Yours Faithfully,}

	\end{letter}
\end{document}

### 2019-06-25 BGSM/thesisproposal.tex
BGSM stuff

\documentclass{article}
\usepackage[
  a4paper,
  margin=1in,
  headsep=4pt, % separation between header rule and text
]{geometry}

\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{tgschola}
\usepackage{lastpage}
\usepackage{amsmath}
\pagestyle{fancy}
\fancyhf{}

\newcommand{\soptitle}{First order logic of sparse hypergraphs}

\newcommand{\yourname}{Lázaro Alberto Larrauri Borroto}
\newcommand{\youremail}{email@address.edu}
\newcommand{\yourweb}{https://www.abcd.com/}

\newcommand{\statement}[1]{\par\medskip
  \textcolor{blue}{\textbf{#1:}}\space
}

\usepackage[
  breaklinks,
  pdftitle={\yourname - \soptitle},
  pdfauthor={\yourname},
  unicode
]{hyperref}

\begin{document}

\begin{center}\LARGE\soptitle\\ 
\vspace{0.5cm}
\Large{Master's thesis proposal for Fall-2019} \\
\yourname
\end{center}

\hrule
\vspace{1pt}
\hrule height 1pt

\bigskip

The goal of this project is to generalize, if possible, the results obtained by 
James F. Lynch in \cite{lynch1992probabilities} about the first-order logic of random graphs to 
the framework of uniform random hypergraphs. A motivation for that field of research is the possibility
of studying very large relational structures, as graphs, by means of analyzing their `typical' properties. 
These structures are of interest because they appear in a great variety of places, ranging from social networks to 
biology, but the analysis of very large individual graphs, for example, is a difficult task. 
Instead, the aforementioned approach has proven to be a useful tool. \par

Going into further detail, in \cite{lynch1992probabilities} are studied the limit properties of a certain model
of random graphs under first-order logic. This model $\mathcal{G}(n,p)$ is one where a graph with $n$ vertices is chosen
randomly in such a way that each pair of vertices is joined by an edge with probability $p$ independently. In other 
words, for any given graph $G$ with $n$ vertices and $m$ edges, the probability of obtaining $G$ in $\mathcal{G}(n,p)$
is $p^m(1-p)^{\binom{n}{2} - m}$. To describe these graphs one can use the first order language which is provided with 
only one binary relation. This way, the variables in this language represent vertices of the graph, while the binary relation 
represents the existence or non-existence of an edge between two vertices. A sentence like $\forall x_1, x_2 (\lnot(x_1=x_2)\implies \exists x_3 (\lnot(x_3=x_1) \wedge \lnot(x_3=x_2)\wedge R(x_1,x_3) \wedge R(x_2,x_3))$ can be interpreted as `for any pair of different vertices $x_1, x_2$ there exists third one $x_3$ that is adjacent to $x_1$ and $x_2$ '. Thus, given a sentence  $\phi$ in this language one can talk about the probability of $\phi$ being satisfied in $\mathcal{G}(n,p)$, i.e. $Pr(\mathcal{G}(n,p) \models \phi)$, or even about the limit of this probability when $n$ tends to infinity- which may or may not exist. 
One of the first important results in this area is the Zero-One Law of random graphs, which states that for any constant $p$, and any
first-order sentence $\phi$, the limit $\lim\limits_{n\rightarrow \infty} Pr(\mathcal{G}(n,p) \models \phi)$ always exists
and it is either zero or one. \par
If one wants the graphs in $\mathcal{G}(n,p)$ to typically contain fewer edges one can consider $p$ as a decreasing function
on $n$. For the particular case of $p=\frac{\beta}{n}$, James F. Lynch proved in 1992 \cite{lynch1992probabilities} that the limit $\lim\limits_{n\rightarrow \infty} Pr(\mathcal{G}(n,\frac{\beta}{n}) \models \phi)$ always existed, even though one can no longer assure that it is zero or one. He also showed that this limit has good properties when seen as a function on $\beta$, proving that it is an analytic function, and that its values are elementary functions associated to the parameters of certain Poisson distributions. \par
In this Master's thesis project the aim is to generalize these results to the model of random uniform hypergraphs 
$\mathcal{H}^k(n,p)$. In this model one consider hypergraphs- graph-like structures where each edge can join an arbitrary number 
of vertices- where each edge contains exactly $k$ vertices and the probability of any $k$ of them being joined by some edge is $p$ independently. Analogously to the case of $\mathcal{G}(n,p)$, one can describe these hypergraphs using the first order language provided only with one $k$-ary relation. We will also try to determine the closure of the set of limiting probabilities as in \cite{heinig2018logical} in a related problem.
\par
To reach the goal of this project a good understanding of Lynch's techniques, as well as of the model $\mathcal{H}^k(n,p)$
will be required. Among those techniques there are tools from finite model theory, namely the Ehrenfeucht-Fraissé games 
(see chapter 3, \cite{libkin2013elements}), and involved combinatorial arguments which need to be translated to this model of random hypergraphs.

\bibliography{references}
\bibliographystyle{acm}

\end{document}

### 2019-06-25 TFM.tex
Adiós

@@
-\documentclass[11pt,notitlepage]{report}
-
-\usepackage[left=4cm,right=4cm,top=3cm,bottom=3cm]{geometry}
+\documentclass[11pt,notitlepage,a4paper]{article}
+
+\usepackage[left=3.7cm,right=3.7cm,top=3cm,bottom=3cm]{geometry}
 \usepackage{graphicx}
@@
 \usepackage{chngcntr}
+\usepackage{cleveref}
+\usepackage{pdfpages}
 
 \counterwithout{equation}{section}
-\counterwithout{equation}{chapter}
 
@@
 
-\newtheorem{proposition}{Proposition}[chapter]
-\newtheorem{fact}{Fact}[chapter]
-\newtheorem{theorem}{Theorem}[chapter]
-\newtheorem{lemma}{Lemma}[chapter]
-\newtheorem{corollary}{Corollary}[chapter]
+\newtheorem{proposition}{Proposition}[section]
+\newtheorem{fact}{Fact}[section]
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
+\newtheorem{corollary}{Corollary}[section]
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}[chapter]
-\newtheorem{propdef}{Proposition / Definition}[chapter]
-\newtheorem{remark}{Remark}[chapter]
+\newtheorem{definition}{Definition}[section]
+\newtheorem{propdef}{Proposition / Definition}[section]
+\newtheorem{remark}{Remark}[section]
 
@@
 \begin{document}
+
+	\includepdf{Portada.pdf}
+
 \begin{abstract}
-	The goal is to generalize the results from Lynch (1992) on the convergence law for sparse random graphs to sparse random hypergraphs.
-This requires in particular an understanding of Lynch's techniques, based on Ehrenfeucht-Fraïssé games, an analysis of the structure of sparse random hypergraphs.
+	We give a generalization the results from Lynch in \cite{lynch1992probabilities}
+	on the convergence law for sparse random graphs to sparse random hypergraphs.
 \end{abstract}
+\clearpage
 \tableofcontents
-
-\chapter*{Introduction}
-
-\chapter{Preliminaries}
-
-\section{Models of Random Graphs}
-
-\section{First Order Logic}
-
-\section{Ehrenfeucht Fraisse Games and the Logic of Random Graphs}
-
-\chapter{Probabilities of Sentences about Very Sparse Random Graphs}
-
-In this chapter we will review the results obtained
- in the paper with the same name by James F. Lynch \cite{lynch1992probabilities}.
-In there, limit probabilities of sentences in the first order language of graphs $\mathcal{L}$
-are discussed for the binomial model $G(n,p)$ in the cases $p=\beta/n$ and
-$p=\beta n^{-\alpha}$ with $\alpha=(l+1)/l$ . \par
-
-More precisely, it is proven that in those cases the 
-probability of every sentence converges and it is shown
-that for any of those sentences, its limit probability 
-is among the values taken by some analytic formulas
-with parameter $\beta$. \par
-
-We are interested in the case $p=\frac{\beta}{n}$, which is 
-the one discussed more extensively in \cite{lynch1992probabilities}. 
-According to the author, the relevant theorems for 
-the other case can be proven analogously. From now on we
-will only refer as random graphs to the ones in $G(n,\beta/n)$\par
-
-From now on we will denote by $Poi_\lambda$ the probability
-function of the Poisson distribution with mean $\lambda$.
-That is, the one given by $Poi_\lambda(n)=e^{-\lambda}\lambda^n/n!$ 
-for any $n\in \N$.
-Also, we define $Poi_\lambda(\leq n)$ and $Poi_\lambda(>n)$ as 
-$\sum_{i=0}^n Poi_\lambda(n)$ and $1-Poi_\lambda(\leq n)$
-respectively. Notice that for a fixed $n$, both $Poi_\lambda(\leq n)$ 
-and $Poi_\lambda(>n)$ can be considered real functions of parameter $\lambda$. \par
-
-We define the following sets of functions. Let $\Lambda$ be the smallest 
-set of expressions with parameter $\beta$ such that:
-
-\begin{itemize}[noitemsep, topsep=0pt]
-	\item $1\in \Lambda$,
-	\item For any $\lambda \in \Lambda$ and $i\in \N$, 
-	both $Poi_{\beta\lambda}(n)$ and $Poi_{\beta\lambda}(> n)$ are in
-	$\Lambda$.
-	\item For any $\lambda_1,\lambda_2 \in \Lambda$,
-	$\lambda_1 \lambda_2$ belongs to $\Lambda$ as well.
-\end{itemize}
-
-And let $\Theta$ be the smallest set of functions with parameter $\beta$
-such that:
-\begin{itemize}[noitemsep, topsep=0pt]
-	\item For any $\lambda \in \Lambda$ 
-	and $n,a,i\in \N$, with $i\geq 3$, 
-	both $Poi_{\beta^i\lambda/a}(\leq n)$ and $Poi_{\beta^i\lambda/a}(> n)$
-	are in $\Theta$.
-\end{itemize}
-
-The main result is the following:
-
-\begin{theorem}[Lynch, 1992] \label{thrm:main}
-	Let $\phi$ be a sentence in the first order theory of graphs. Then the limit
-	$\lim\limits_{n\to \infty} P(G(n,\beta/n) \models \phi )$ exists for all positive real numbers
-	$\beta$, and it is a finite sum of expressions in $\Theta$.
-\end{theorem}
-
-We show now an outline of the proof. \par 
-We show that for any quantifier rank $k$ there are some classes of graphs 
-$C^k_1,\dots, C^k_{n_k}$ such that
-\begin{itemize}[noitemsep, topsep=0pt]
-	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
-	\item[(2)] a.a.s. any random graph belongs to some of them, and
-	\item[(3)] the limit probability of random graph belonging to any of them is an expression in $\Theta$. 
-\end{itemize}
-
-After this is archived the theorem follows easily. Indeed, let $\phi$ be a sentence 
-in the first order language $\Lan$ of graphs whose quantifier rank is $k$, and denote by
-$G$ a random graph in $G(n,\beta/n)$. \par
-
-The objective of next sections will be to define the classes $C_1,\dots, C_{n_k}$ and to show
-that they satisfy properties (1), (2) and (3). Later we will prove a stronger result, so we will
-allow ourselves to just sketch some of the proofs during this chapter.
-
-\section{Agreeability Classes}
-
-It is known that $n^{-v/e}$ is the t
-hreshold probability for the appearance 
-of a balanced graph of density $v/e$. 
-In our case $v/e=1$, so in consequence any connected graph $H$
-with $e(H)< v(H)$ a.a.s will not appear 
-as a subgraphs of $G(n,\beta/n)$. It can be easily 
-shown that such graphs $H$ are exactly 
-the ones containing more than one cycle. \par
-
-If $H$ is a connected graph with $v=e$, then $H$ is an uni-cyclic graph.
-In this case, the number $X_H$ of copies of $H$ 
-in $G(n,\beta/n)$ will asymptotically have non-zero bounded expectancy $m$. 
-It does not take much work to prove, using Brun's sieve, 
-that $X_H$ converges in distribution to a Poisson 
-random variable with mean $m$ as $n$ goes to infinity.  \par
-
-Finally, if $H$ is a connected graph 
-with $v>e$ then it must be a tree. Here 
-the expected number of copies of $H$ 
-in $G(n,\beta/n)$ diverges asymptotically. 
-Informally, trees of any kind will occur arbitrarily often. \par
-
-This all means, in a sense, that a.a.s the only 
-difference between large graphs in $G(n,\beta/n)$
-lies in their uni-cyclic subgraphs. More precisely,
-because of the ``locality" of first order logic of quantifier 
-rank $k$ we will only be interested in the 
-``small`` neighborhoods of the ``short" cycles.  
-Thus, our goal will be to classify uni-cyclic graphs
-in a way that respects equivalence under first 
-order logic of quantifier rank $k$. \par
-~\par
-To make our classification suitable for proofs 
-involving E.F. games we need to work graphs to which we ``attach" labels. 
-We define the set of symbols $Const=\{c_i\}_{i\in \N}$ 
-as the set of constants. Also, we will denote by
-$Const_n$ the set $\{c_1,\dots, c_n\}$.
-
-\begin{definition} 
-	A \textbf{co-labeling} of a graph $G=(V,E)$ is a map 
-	$\sigma: D\rightarrow V$, where $D\subset C$ is a 
-	finite set of constant symbols. Given $c_i\in D$, 
-	we will say that the vertex $\sigma(c_i)$ is labeled $c_i$.
-	Equivalently, we can denote a labeling $\sigma$ as a tuple
-	$(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$ where each $c_{i_j}$
-	 is a constant symbol, and $x_j$ is the vertex
-	in $V$ labeled $c_{i_j}$.
-\end{definition}
-
-\begin{definition} 
-	A \textbf{graph with constants}\footnote{
-		Compare with \cite{lynch1992probabilities}, where they are called ``rooted graphs". 
-		}
-	$G(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$ 
-	is a graph $G$ together with a co-labeling 
-	$(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$. 
-\end{definition}
-
-To keep our notation compact we will often drop 
-he $x_i$'s and say $G(c_{i_1},\dots, c_{i_m})$. \par
-
-\begin{definition}
-Let $G$ be a graph with constants. A subgraph $H$ of $G$ is
-a graph with constants such that $V(H)\subseteq V(G)$, $E(H)\subseteq E(G)$ and 
-all vertices in $V(H)$ have the same labels in $H$ and $G$. 
-\end{definition}
-
-An important abuse of notation we are going to make
-will be to identify the constants $c_i$ with their labeled
-vertices $\sigma(c_i)$. This way things like $c_i\sim c_j$ 
-will make sense. In this context, notice that the expression
-$c_i=c_j$ is ambiguous because the vertices labeled $c_i$ and $c_j$ 
-may be the same for some $i\neq j$, but 
-the constant symbols $c_i$ and $c_j$ will be equal only if $i=j$. 
-We will make sure to leave no room for ambiguity in this situations. \par
-
-\begin{propdef}
-	Let $G=(V,E,\clist)$ be a connected graph with constants. Then it has a unique minimal
-	connected subgraph $H$ containing all its constants and cycles.
-	We will call the \textbf{center} of $G$ to such subgraph and denote it by $Center(G)$.
-	If $\bar{G}$ is an arbitrary graph with constants, then its center $Center{\bar{G}}$ will
-	be the union of the centers of its connected components. 
-\end{propdef}
-\begin{proof}
-	TO DO
-\end{proof}
-
-For an arbitrary graph with constants we define the metric $d(\cdot,\cdot)$ on $V(G)$ 
-as the one such that $d(x,y)$ is the minimum length of a path connecting
-$x$ and $y$ in $G$ or $\infty$ if such path does not exist. 
-For any vertex $x\in V(G)$ and $r\in \N$ we define the co-labeled
-subgraph $N(x;r)$ as the ball of radius $r$ centered at $v$. 
-That is, the induced subgraph with vertex set
-\[ V(N(x;r))= \{\, y\in V \, | \, d(x,y)\leq  r \,	\}.\] 
-In a similar vein, given $X\subseteq V(G)$ we define its neighborhood of radius $r$ as
-the induced co-labeled subgraph $N(X;r)$ whose vertex set is
-\[ V(N(X;r))= \{\, y\in V \, | \, \forall x\in X: \, \,  d(x,y)\leq  r \,	\}.\]  
-\par
-
-Let $G=(V,E)$, and $V^\prime\subseteq V$. Another important abuse 
-of notation we will make is writing $H=(V^\prime, E)$ 
-for a subgraph $H$ to mean that the edge set of $E(H)$ is the one
-induced by $E(G)$ on $V^\prime$.
-
-\begin{definition} 
-	A \textbf{rooted tree} $T=(V,E,x)$ is a tree 
-	$(V,E)$ with distinguished vertex $x\in V$ with we will call 
-	\textbf{root} of the tree.
-\end{definition}
-
-\begin{propdef}
-	Let $G=(V,E,\clist)$ be a connected graph and $x\in V$. 
-	Then define $Tree(x,G)$	as the rooted tree
-	\[Tree(x,G) = (V_x,E,x),\] where
-	\[V_x= \{\, y\in V \, | \,\,d(Center(G),y) = d(Center(G),x) + d(x,y) \}.\]
-
-\end{propdef}
-\begin{proof}
-	TO DO
-\end{proof}
-
-The radius $r(T)$ of a rooted tree $T=(V,E,x)$
-is the maximum distance between its root $x$ and any other of
-its vertices. The branches of $T$ are the rooted trees of the form
-$Tree(y,T)$, where $y\sim x$. We will denote by $Br(T)$ the set of
-branches of $T$. \par
-
-We begin by defining an equivalence relation between rooted 
-trees for each quantifier rank $k$.
-
-\begin{definition} 
-	Let $k\in \N$ with $k\geq 1$. The \textbf{k-morphism} equivalence relation
-	$\morph{k}$ between
-	graph with constantss is the one inductively defined as follows:
-	\begin{itemize}
-		\item If $T_1, T_2$ are rooted trees of radius $0$ -i.e., they
-		consist only of their roots- they are $k$-morphic. 
-		\item Let $T_1, T_2$ be rooted trees of radius $r$ whose 
-		rots have the same label. Then $T_1 \morph{k} T_2$ if 
-		for any $k$-morphism class $C$ of trees with
-		radius less than $r$ and root either
-		\begin{center}
-			\vspace{-0.2cm}
-			``$T_1$ and $T_2$ have the same number of branches of type $C$"
-		\end{center}
-		\vspace{-0.3cm}
-		\[ |Br(T_1)\cap C| = |Br(T_2)\cap C|,\]
-		or 
-		\begin{center}
-			\vspace{-0.2cm}
-			``$T_1$ and $T_2$ have both more than $k$ branches of type $C$"
-		\end{center}
-	\vspace{-0.3cm}
-		\[ |Br(T_i)\cap C| \geq k+1 \text{ for } i=1,2. \]
-	\end{itemize} 
-\end{definition}
-
-It follows from the definition that $k$-morphic trees have the same radius. 
-It is also easy to check that the $k$-morphism relation is indeed an equivalence one.
-
-\begin{proposition}
-	For all $k,r\in N$ and with $k\geq 1$, the set of classes of $k$-morphic trees
-	with radius lesser or equal than $r$ is finite.
-\end{proposition}
-\begin{proof}
-TO DO
-\end{proof}
-
-We define now the $k$-morphism relation for arbitrary graph with constantss. 
+\clearpage
+
+\section*{Introduction}
+
+This work is the thesis presented for the Master in Applied Mathematics and 
+Mathematical Engineering of the Universitat Politècnica de Catalunya in 
+June 2019. \par
+
+This text belongs to the study of the asymptotic properties of random structures.
+This is an active area of mathematics that has gained recent popularity due to 
+the increasing need for methods that allow for analysis of large random
+structures. These structures appear in a wide array of 
+``real-life" problems, ranging
+from the study of social networks to biology, and they are
+arguably interesting in their own right.\par
+
+The objective of this work, proposed by Marc Noy and Albert Atserias, was 
+to generalize the results obtained in \cite{lynch1992probabilities} to more
+general random structures. This was motivated by applications to the study
+of the satisfability of random CNF formulas, but those are out of the scope of 
+this work. \par
+
+Going into further detail, in \cite{lynch1992probabilities} the asymptotic 
+behavior under first order logic of the Erdös-Rényi binomial model $\mathcal{G}(n,p)$, where
+$p$ is taken as a decreasing function on $n$ of the form $\beta\cdot n^{-1}$,
+is studied. The first order properties of graphs are the ones expressible in 
+terms of quantification over vertices and Boolean combinations of statements 
+of the form ``$x$ adjacent to $y$'' and  ``$x$ equal to $y$''. The main theorem
+in \cite{lynch1992probabilities} states that the limit probability that a graph
+in $\mathcal{G}(n,\beta/n)$ satisfies any given first-order property exists
+and has good properties with respect to $\beta$. \par
+
+The original goal was to give generalizations for the case of uniform hypergraphs
+but the techniques used for that case also allowed for generalizations to 
+hypergraphs with multiple edge sets of different sizes.
+
+\clearpage
+
+\section{Logic of Sparse Random Graphs}
+
+We give a brief overview of \cite{lynch1992probabilities}.
+The asymptotic behavior of graphs in $G(n,\beta/n)$ is as follows
+	\begin{itemize}
+	\item The number of cycles of 
+	length $3,4\dots, r$
+	are asymptotically distributed like independent Poisson 
+	variables.
+	\item Small cycles are a.a.s (asymptotically almost surely) far away.
+	\item Fixed vertices are a.a.s far away.
+	\item The ball of a given radius centered in fixed
+	vertex is a.a.s a tree. Any tree occurs with a positive 
+	probability.
+\end{itemize}
+
+This way, asymptotically, trees of any kind occur arbitrarily often in a typical
+random graph. Given the locality of first order logic up to a fixed 
+quantifier rank this is tells us that the only thing that the only way 
+to distinguish large random graphs in $G(n,\beta/n)$ 
+(up to a fixed quantifier rank) 
+is by looking at the neighborhoods of their small cycles. \par
+
+It is given a finite and exhaustive classification of the uni-cyclic
+graphs with less than a given radius. After that it is shown that
+if two graphs $G_1$ and $G_2$ contain the same number 
+of uni-cycles of each type or they
+contain a large enough number of those then they are a.a.s equivalent
+under first order logic up to some quantifier rank $k$. This is done by giving
+a winning strategy for duplicator in the E.F. game of $k$ round played on 
+$G_1$ and $G_2$.\par
+
+Finally it is shown that the numbers of uni-cycles of each type contained in
+a random graph are asymptotically distributed like independent Poisson variables 
+whose means are given by some other nested ``Poisson expressions" that correspond 
+to the trees hanging from each uni-cycle.
+
+%In this chapter we will review the results obtained
+% in the paper with the same name by James F. Lynch \cite{lynch1992probabilities}.
+%In there, limit probabilities of sentences in the first order language of graphs $\mathcal{L}$
+%are discussed for the binomial model $G(n,p)$ in the cases $p=\beta/n$ and
+%$p=\beta n^{-\alpha}$ with $\alpha=(l+1)/l$ . \par
+%
+%More precisely, it is proven that in those cases the 
+%probability of every sentence converges and it is shown
+%that for any of those sentences, its limit probability 
+%is among the values taken by some analytic formulas
+%with parameter $\beta$. \par
+%
+%We are interested in the case $p=\frac{\beta}{n}$, which is 
+%the one discussed more extensively in \cite{lynch1992probabilities}. 
+%According to the author, the relevant theorems for 
+%the other case can be proven analogously. From now on we
+%will only refer as random graphs to the ones in $G(n,\beta/n)$\par
+%
+%From now on we will denote by $\mathrm{Poiss}_\lambda$ the probability
+%function of the Poisson distribution with mean $\lambda$.
+%That is, the one given by $\mathrm{Poiss}_\lambda(n)=e^{-\lambda}\lambda^n/n!$ 
+%for any $n\in \N$.
+%Also, we define $\mathrm{Poiss}_\lambda(\leq n)$ and $\mathrm{Poiss}_\lambda(>n)$ as 
+%$\sum_{i=0}^n \mathrm{Poiss}_\lambda(n)$ and $1-\mathrm{Poiss}_\lambda(\leq n)$
+%respectively. Notice that for a fixed $n$, both $\mathrm{Poiss}_\lambda(\leq n)$ 
+%and $\mathrm{Poiss}_\lambda(>n)$ can be considered real functions of parameter $\lambda$. \par
+%
+%We define the following sets of functions. Let $\Lambda$ be the smallest 
+%set of expressions with parameter $\beta$ such that:
+%
+%\begin{itemize}[noitemsep, topsep=0pt]
+%	\item $1\in \Lambda$,
+%	\item For any $\lambda \in \Lambda$ and $i\in \N$, 
+%	both $\mathrm{Poiss}_{\beta\lambda}(n)$ and $\mathrm{Poiss}_{\beta\lambda}(> n)$ are in
+%	$\Lambda$.
+%	\item For any $\lambda_1,\lambda_2 \in \Lambda$,
+%	$\lambda_1 \lambda_2$ belongs to $\Lambda$ as well.
+%\end{itemize}
+%
+%And let $\Theta$ be the smallest set of functions with parameter $\beta$
+%such that:
+%\begin{itemize}[noitemsep, topsep=0pt]
+%	\item For any $\lambda \in \Lambda$ 
+%	and $n,a,i\in \N$, with $i\geq 3$, 
+%	both $\mathrm{Poiss}_{\beta^i\lambda/a}(\leq n)$ and $\mathrm{Poiss}_{\beta^i\lambda/a}(> n)$
+%	are in $\Theta$.
+%\end{itemize} 
+%
+%The main result is the following:
+%
+%\begin{theorem}[Lynch, 1992] \label{thrm:main}
+%	Let $\phi$ be a sentence in the first order theory of graphs. Then the limit
+%	$\lim\limits_{n\to \infty} P(G(n,\beta/n) \models \phi )$ exists for all positive real numbers
+%	$\beta$, and it is a finite sum of expressions in $\Theta$.
+%\end{theorem}
+%
+%We show now an outline of the proof. \par 
+%We show that for any quantifier rank $k$ there are some classes of graphs 
+%$C^k_1,\dots, C^k_{n_k}$ such that
+%\begin{itemize}[noitemsep, topsep=0pt]
+%	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
+%	\item[(2)] a.a.s. any random graph belongs to some of them, and
+%	\item[(3)] the limit probability of random graph belonging to any of them is an expression in $\Theta$. 
+%\end{itemize}
+%
+%After this is archived the theorem follows easily. Indeed, let $\phi$ be a sentence 
+%in the first order language $\Lan$ of graphs whose quantifier rank is $k$, and denote by
+%$G$ a random graph in $G(n,\beta/n)$. \par
+%
+%The objective of next sections will be to define the classes $C_1,\dots, C_{n_k}$ and to show
+%that they satisfy properties (1), (2) and (3). Later we will prove a stronger result, so we will
+%allow ourselves to just sketch some of the proofs during this chapter. 
+%
+%\section{Agreeability Classes}
+%
+%
+%It is known that $n^{-v/e}$ is the t
+%hreshold probability for the appearance 
+%of a balanced graph of density $v/e$. 
+%In our case $v/e=1$, so in consequence any connected graph $H$
+%with $e(H)< v(H)$ a.a.s will not appear 
+%as a subgraphs of $G(n,\beta/n)$. It can be easily 
+%shown that such graphs $H$ are exactly 
+%the ones containing more than one cycle. \par
+%
+%If $H$ is a connected graph with $v=e$, then $H$ is an uni-cyclic graph.
+%In this case, the number $X_H$ of copies of $H$ 
+%in $G(n,\beta/n)$ will asymptotically have non-zero bounded expectancy $m$. 
+%It does not take much work to prove, using Brun's sieve, 
+%that $X_H$ converges in distribution to a Poisson 
+%random variable with mean $m$ as $n$ goes to infinity.  \par
+%
+%Finally, if $H$ is a connected graph 
+%with $v>e$ then it must be a tree. Here 
+%the expected number of copies of $H$ 
+%in $G(n,\beta/n)$ diverges asymptotically. 
+%Informally, trees of any kind will occur arbitrarily often. \par
+%
+%This all means, in a sense, that a.a.s the only 
+%difference between large graphs in $G(n,\beta/n)$
+%lies in their uni-cyclic subgraphs. More precisely,
+%because of the ``locality" of first order logic of quantifier 
+%rank $k$ we will only be interested in the 
+%``small`` neighborhoods of the ``short" cycles.  
+%Thus, our goal will be to classify uni-cyclic graphs
+%in a way that respects equivalence under first 
+%order logic of quantifier rank $k$. \par
+%~\par
+%To make our classification suitable for proofs 
+%involving E.F. games we need to work graphs to which we ``attach" labels. 
+%We define the set of symbols $Const=\{c_i\}_{i\in \N}$ 
+%as the set of constants. Also, we will denote by
+%$Const_n$ the set $\{c_1,\dots, c_n\}$.
+% 
+%\begin{definition} 
+%	A \textbf{co-labeling} of a graph $G=(V,E)$ is a map 
+%	$\sigma: D\rightarrow V$, where $D\subset C$ is a 
+%	finite set of constant symbols. Given $c_i\in D$, 
+%	we will say that the vertex $\sigma(c_i)$ is labeled $c_i$.
+%	Equivalently, we can denote a labeling $\sigma$ as a tuple
+%	$(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$ where each $c_{i_j}$
+%	 is a constant symbol, and $x_j$ is the vertex
+%	in $V$ labeled $c_{i_j}$.
+%\end{definition}
+%
+%\begin{definition} 
+%	A \textbf{graph with constants}\footnote{
+%		Compare with \cite{lynch1992probabilities}, where they are called ``rooted graphs". 
+%		}
+%	$G(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$ 
+%	is a graph $G$ together with a co-labeling 
+%	$(c_{i_1}[x_1],\dots, c_{i_m}[x_m])$. 
+%\end{definition}
+%
+%To keep our notation compact we will often drop 
+%he $x_i$'s and say $G(c_{i_1},\dots, c_{i_m})$. \par
+%
+%\begin{definition}
+%Let $G$ be a graph with constants. A subgraph $H$ of $G$ is
+%a graph with constants such that $V(H)\subseteq V(G)$, $E(H)\subseteq E(G)$ and 
+%all vertices in $V(H)$ have the same labels in $H$ and $G$. 
+%\end{definition}
+%
+%
+%An important abuse of notation we are going to make
+%will be to identify the constants $c_i$ with their labeled
+%vertices $\sigma(c_i)$. This way things like $c_i\sim c_j$ 
+%will make sense. In this context, notice that the expression
+%$c_i=c_j$ is ambiguous because the vertices labeled $c_i$ and $c_j$ 
+%may be the same for some $i\neq j$, but 
+%the constant symbols $c_i$ and $c_j$ will be equal only if $i=j$. 
+%We will make sure to leave no room for ambiguity in this situations. \par
+%
+%
+%\begin{propdef}
+%	Let $G=(V,E,\clist)$ be a connected graph with constants. Then it has a unique minimal
+%	connected subgraph $H$ containing all its constants and cycles.
+%	We will call the \textbf{center} of $G$ to such subgraph and denote it by $Center(G)$.
+%	If $\bar{G}$ is an arbitrary graph with constants, then its center $Center{\bar{G}}$ will
+%	be the union of the centers of its connected components. 
+%\end{propdef}
+%\begin{proof}
+%	TO DO
+%\end{proof}
+%
+%For an arbitrary graph with constants we define the metric $d(\cdot,\cdot)$ on $V(G)$ 
+%as the one such that $d(x,y)$ is the minimum length of a path connecting
+%$x$ and $y$ in $G$ or $\infty$ if such path does not exist. 
+%For any vertex $x\in V(G)$ and $r\in \N$ we define the co-labeled
+%subgraph $N(x;r)$ as the ball of radius $r$ centered at $v$. 
+%That is, the induced subgraph with vertex set
+%\[ V(N(x;r))= \{\, y\in V \, | \, d(x,y)\leq  r \,	\}.\] 
+%In a similar vein, given $X\subseteq V(G)$ we define its neighborhood of radius $r$ as
+%the induced co-labeled subgraph $N(X;r)$ whose vertex set is
+%\[ V(N(X;r))= \{\, y\in V \, | \, \forall x\in X: \, \,  d(x,y)\leq  r \,	\}.\]  
+%\par
+%
+%Let $G=(V,E)$, and $V^\prime\subseteq V$. Another important abuse 
+%of notation we will make is writing $H=(V^\prime, E)$ 
+%for a subgraph $H$ to mean that the edge set of $E(H)$ is the one
+%induced by $E(G)$ on $V^\prime$.
+%
+%\begin{definition} 
+%	A \textbf{rooted tree} $T=(V,E,x)$ is a tree 
+%	$(V,E)$ with distinguished vertex $x\in V$ with we will call 
+%	\textbf{root} of the tree.
+%\end{definition}
+%
+%\begin{propdef}
+%	Let $G=(V,E,\clist)$ be a connected graph and $x\in V$. 
+%	Then define $Tree(x,G)$	as the rooted tree
+%	\[Tree(x,G) = (V_x,E,x),\] where
+%	\[V_x= \{\, y\in V \, | \,\,d(Center(G),y) = d(Center(G),x) + d(x,y) \}.\]
+%
+%\end{propdef}
+%\begin{proof}
+%	TO DO
+%\end{proof}
+%
+%
+%
+%The radius $r(T)$ of a rooted tree $T=(V,E,x)$
+%is the maximum distance between its root $x$ and any other of
+%its vertices. The branches of $T$ are the rooted trees of the form
+%$Tree(y,T)$, where $y\sim x$. We will denote by $Br(T)$ the set of
+%branches of $T$. \par
+%
+%We begin by defining an equivalence relation between rooted 
+%trees for each quantifier rank $k$.
+%
+%\begin{definition} 
+%	Let $k\in \N$ with $k\geq 1$. The \textbf{k-morphism} equivalence relation
+%	$\morph{k}$ between
+%	graph with constantss is the one inductively defined as follows:
+%	\begin{itemize}
+%		\item If $T_1, T_2$ are rooted trees of radius $0$ -i.e., they
+%		consist only of their roots- they are $k$-morphic. 
+%		\item Let $T_1, T_2$ be rooted trees of radius $r$ whose 
+%		rots have the same label. Then $T_1 \morph{k} T_2$ if 
+%		for any $k$-morphism class $C$ of trees with
+%		radius less than $r$ and root either
+%		\begin{center}
+%			\vspace{-0.2cm}
+%			``$T_1$ and $T_2$ have the same number of branches of type $C$"
+%		\end{center}
+%		\vspace{-0.3cm}
+%		\[ |Br(T_1)\cap C| = |Br(T_2)\cap C|,\]
+%		or 
+%		\begin{center}
+%			\vspace{-0.2cm}
+%			``$T_1$ and $T_2$ have both more than $k$ branches of type $C$"
+%		\end{center}
+%	\vspace{-0.3cm}
+%		\[ |Br(T_i)\cap C| \geq k+1 \text{ for } i=1,2. \]
+%	\end{itemize} 
+%\end{definition}
+%
+%It follows from the definition that $k$-morphic trees have the same radius. 
+%It is also easy to check that the $k$-morphism relation is indeed an equivalence one. 
+%
+%\begin{proposition}
+%	For all $k,r\in N$ and with $k\geq 1$, the set of classes of $k$-morphic trees
+%	with radius lesser or equal than $r$ is finite.
+%\end{proposition}
+%\begin{proof}
+%TO DO
+%\end{proof}
+%
+%We define now the $k$-morphism relation for arbitrary graph with constantss. 
 %If $G^1=(V^1,E^1,\clist)$ and $G^2=(V^2,E^2,\clist)$ are graph with constantss with
@@
 %the vertices labeled $c_{i_j}$ in $G^1$ and $G^2$ respectively. 
-
-\begin{definition}
-	Let $G^1=(V^1,E^1,c_{i_1}[x^1_1],\dots, c_{i_m}[x_m^1])$ and  $G^2=(V^2,E^2,c_{i_1}[x^1_2],$ 
-	$\dots, c_{i_m}[x_m^2])$ be graph with constantss with the same constant symbols. 
-	We will say that they are $k$-morphic (denoted by $G^1 \morph{k}G^2$) if there is
-	a bijection $f: V(Center(G^1))\rightarrow V(Center(G^2))$ such that
-	\begin{itemize}
-		\item ``$f$ preserves edges"
-		\[\forall x,y\in V(Center(G^1)): \quad  x\sim y \iff f(x)\sim f(y). \]
-		\item ``$f$ preserves labels"
-		\[\forall j\in \{1,\dots,m\}: \quad f(x^1_j) = x^2_j.\]
-		\item ``$f$ preserves $k$-morphism classes of trees"
-		\[\forall x\in V(Center(G^1)): \quad  Tree(x,G^1)\morph{k} Tree(f(x),G^2).\]
-	\end{itemize}
-	In this case we will say that $G^1 \morph{k} G^2$ via $f$. 	
-\end{definition}
-
-We are going to show that the rank $k$ type of a random graph a.a.s only 
-depends on the neighborhoods of its small cycles. In consequence the following definition
-is motivated:
-
-\begin{definition} 
-	Let $G=(V,E,\clist)$ be a graph with constants. Then its core of radius $r$, $Core(G,r)$
-	is the co-labeled subgraph $N(X;r)$, where $X$ is the union of the (vertex sets of the)
-	cycles in $G$ with size at most $2r+1$ and all of the labeled vertices in $G$. 
-\end{definition}
-
-\chapter{First Order Logic of Sparse Random Hypergraphs}
+%
+%\begin{definition}
+%	Let $G^1=(V^1,E^1,c_{i_1}[x^1_1],\dots, c_{i_m}[x_m^1])$ and  $G^2=(V^2,E^2,c_{i_1}[x^1_2],$ 
+%	$\dots, c_{i_m}[x_m^2])$ be graph with constantss with the same constant symbols. 
+%	We will say that they are $k$-morphic (denoted by $G^1 \morph{k}G^2$) if there is
+%	a bijection $f: V(Center(G^1))\rightarrow V(Center(G^2))$ such that
+%	\begin{itemize}
+%		\item ``$f$ preserves edges"
+%		\[\forall x,y\in V(Center(G^1)): \quad  x\sim y \iff f(x)\sim f(y). \]
+%		\item ``$f$ preserves labels"
+%		\[\forall j\in \{1,\dots,m\}: \quad f(x^1_j) = x^2_j.\]
+%		\item ``$f$ preserves $k$-morphism classes of trees"
+%		\[\forall x\in V(Center(G^1)): \quad  Tree(x,G^1)\morph{k} Tree(f(x),G^2).\]
+%	\end{itemize}
+%	In this case we will say that $G^1 \morph{k} G^2$ via $f$. 	
+%\end{definition}
+%
+%We are going to show that the rank $k$ type of a random graph a.a.s only 
+%depends on the neighborhoods of its small cycles. In consequence the following definition
+%is motivated:
+%
+%\begin{definition} 
+%	Let $G=(V,E,\clist)$ be a graph with constants. Then its core of radius $r$, $Core(G,r)$
+%	is the co-labeled subgraph $N(X;r)$, where $X$ is the union of the (vertex sets of the)
+%	cycles in $G$ with size at most $2r+1$ and all of the labeled vertices in $G$. 
+%\end{definition}
+%
+%
+\section{Random Hyper-graphs}
+
+Work has been done to generalize zero-one laws and limit laws of graphs to the
+setting of random hyper-graphs. The results in \cite{shelah1988zero} from Shelah
+and Spencer have been partially generalized for random $c$-uniform hypergraphs
+in \cite{zeroonehyper}, and a some limit laws, including one for $p(n)=(n^{1-c})$
+have been obtained in \cite{salvadorbrasil} using approaches different
+from the ones appearing here.
 
@@
 	probability
-	\[ Pr(G)=\prod_{i=1}^{c} p_i^{|H_i|}(1-p_i)^{|\mathcal{H}_{(a_i,\Phi_i,A_i)}(n)|-|H_i|}.	
+	\[ \mathrm{Pr}(G)=\prod_{i=1}^{c} p_i^{|H_i|}(1-p_i)^{|\mathcal{H}_{(a_i,\Phi_i,A_i)}(n)|-|H_i|}.	
 	\]
@@
 
-\section{The Theorem.}
+\section{The Theorem}
 
@@
 
+We will denote by $\mathrm{Poiss}_\lambda$ the probability
+function of the Poisson distribution with mean $\lambda$.
+That is, the one given by $\mathrm{Poiss}_\lambda(n)=e^{-\lambda}\lambda^n/n!$ 
+for any $n\in \N$.
+Also, we define $\mathrm{Poiss}_\lambda(\leq n)$ and $\mathrm{Poiss}_\lambda(>n)$ as 
+$\sum_{i=0}^n \mathrm{Poiss}_\lambda(n)$ and $1-\mathrm{Poiss}_\lambda(\leq n)$
+respectively. Notice that for a fixed $n$, both $\mathrm{Poiss}_\lambda(\leq n)$ 
+and $\mathrm{Poiss}_\lambda(>n)$ can be considered real functions of parameter $\lambda$. \par
+
 We define $\Lambda$ and $M$ as the minimal families
@@
 	\item For any $\mu\in M$ and any $n\in \N$ both
-	$Poi_{\mu}(n)$ and $Poi_\mu(\geq n)$ are in $\Lambda$
+	$\mathrm{Poiss}_{\mu}(n)$ and $\mathrm{Poiss}_\mu(\geq n)$ are in $\Lambda$
 	\item For any $\lambda_1,\lambda_2 \in \Lambda$, the
@@
 	\item For any $g\in \widehat{\Theta}$ and any $n\in \N$ both
-	$Poi_g(n)$ and $Poi_g(\geq n)$ are in $\Theta$.
+	$\mathrm{Poiss}_g(n)$ and $\mathrm{Poiss}_g(\geq n)$ are in $\Theta$.
 	\item For any $\theta_1, \theta_2\in \Theta$ the product
@@
 we will use the notation 
-$Pr_n(\phi):=Pr(HG(n,p(n))\models \phi)$. \par
+$\mathrm{Pr}_n(\phi):=\mathrm{Pr}(HG(n,p(n))\models \phi)$. \par
 
@@
 	\[
-	\mathfrak{F}(\beta):=\Ln Pr(\, HG(n,p(\beta,n))\, \models \, \psi \,)
+	\mathfrak{F}(\beta):=\Ln \mathrm{Pr}(\, HG(n,p(\beta,n))\, \models \, \psi \,)
 	\]
@@
 	the number
-	\[ \left( |V(G)| - \sum_{i=1}^l |H_i(G)\langle Ta_i-1)\right).\]
+	\[ \left( |V(G)| - \sum_{i=1}^l |H_i(G)|(a_i-1)\right).\]
 	An hypergraph is $L$-balanced if it contains no subgraph with
@@
 	Choose an edge $e\in H(G)$ and call $F$ to the graph obtained by
-	cutting $e$ in $G$. The intersection $e\cup F$ contains exactly two 
-	vertices, $x, y$. The graph $F$ must be 
+	cutting $e$ in $G$. The intersection $e\cap F$ contains exactly two 
+	vertices, $x, y$. The graph $F$ must be both
 	\begin{itemize}
@@
 
-Given a graph $G$, its diameter $diam(G)$ will be the maximum distance
+Given a graph $G$, its diameter $\mathrm{diam}(G)$ will be the maximum distance
 between any two of its vertices:
-\[diam(G)=\max_{\substack{x,y\in V(G)}} d(x,y).\]
+\[\mathrm{diam}(G)=\max_{\substack{x,y\in V(G)}} d(x,y).\]
 
@@
 \begin{proof}[Sketch of the proof]
-	Let $G$ be a cycle with $diam(G)=r$, and let
+	Let $G$ be a cycle with $\mathrm{diam}(G)=r$, and let
 	$x,y\in V(G)$ be such that $d(x,y)=r$. Let $e$
@@
 	$e\in H(G)$
-	satisfies at least one of the following:
-	\begin{itemize}
-		\item[(1)] $e$ intersects the union of all the other edges
+	satisfies at least one of the following conditions:
+	\begin{itemize}
+		\item[(1)] The edge $e$ intersects the union of all the other edges
 		in $H(G)$ in at least two vertices.
-		 \item[(2)] $e$ contains some vertex at least twice.
+		 \item[(2)] The edge $e$ contains some vertex at least twice.
 	\end{itemize}
@@
 $(\cc_{1}[x_1],\dots, \cc_m[x_m])$ where each 
-$x_j$ in $V(G)$ labeled $\cc_j$.
+$x_j$ in $V(G)$ is labeled $\cc_j$.
 
@@
 neighbourhood graphs $N(x;r)$ and $N(X;r)$ as
-\[ N(x;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | d(x,y)\leq r \, \} \]
+\[ N(x;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | d(x,y)\leq r \, \}, \]
 \[ N(X;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | d(X,y)\leq r \, \}, \]
@@
 
-When the ``environment graph'' is clear we will write $Tree(x)$
+When the ``ambient graph'' is clear we will write $Tree(x)$
 instead of $Tree(x,G)$.
@@
 	\begin{itemize}
-		\item If $T_1$ and $T_2$ are radius $0$ rooted trees then they consist only of their roots and $T_1\morph{k} T_2$. 
+		\item If $T_1$ and $T_2$ are radius $0$ rooted trees, then they consist only of their roots and $T_1\morph{k} T_2$. 
 		\item The radius of a $k$-morphism class of rooted trees $C$
@@
 		,\]
-		with dolor $d$, where
-		\begin{itemize}
-			\item $\mathfrak{r}$ is the ``root symbol''
+		with color $d$, where
+		\begin{itemize}
+			\item $\mathfrak{r}$ is the ``root symbol'',
 			\item $C_i$ is the $k$-morphism class of the tree
@@
 			is the same.
-			\item both $T_1$ and $T_2$ contain no less than $k+1$
+			\item Both $T_1$ and $T_2$ contain no less than $k+1$
 			initial edges of $k$-type $E$. 
@@
 \begin{lemma} \label{lem:lessktree}
-	Let $(T_1,x)$ and $(T_2,y)$ be rooted trees such that for some $k>0$ 
+	Let $(T_1,x)$ and $(T_2,y)$ be rooted trees such that for some $k>0$, 
 	$T_1 \morph{k} T_2$. Then, for any $0\leq j < k$, it is satisfied
@@
 		$e_2=[y_1,\dots,y_{c_l}]$ for some vertices such that for all
-		$i=1,\dots, a_l$ either 
+		$i=1,\dots, a_l$, either 
 		\begin{itemize}
@@
 		$k$-types of edges $E_1, \dots, E_m$ such that for all rooted trees $T$
-		\[ \langle T,E\rangle = \sum_{i=1}^{m} \rangle T,E_i \langle .\]
+		\[ \langle T,E\rangle = \sum_{i=1}^{m} \langle T,E_i \rangle .\]
 		In particular
@@
 	with constants such that $G_1(\cc_1,\dots, \cc_t)\morph{k}G_2(c_1,\dots,c_t)$.
+	\\
 	Then, for any $j<k$, $G_1(\cc_1,\dots, \cc_t)\morph{j}G_2(c_1,\dots,c_t)$.
@@
 	Let $(T_1,x),(T^\prime_1,x), (T_2, y)$ and $(T^\prime_2,x)$ 
-	be rooted trees satisfying $T_1\morph{k} T_2$.
+	be rooted trees satisfying $T_1\morph{k} T_2$, and 
 	$T_1^\prime\morph{k} T_2^\prime$ for some 
@@
 
-Let $T$ be  tree and $T^\prime$ be a sub-tree of $T$. For any 
+Let $T$ be a tree and $T^\prime$ be a sub-tree of $T$. For any 
 $y\in V(T^\prime)$ we will denote by $Span(y, T^\prime, T)$ the 
@@
 	\[Tree(w_1, F^\prime_1)\morph{k-1} Tree(g(w_1), F^\prime_2)\]
-	and the result will be prove. The following two cases may occur:
+	and the result will be proven. The following two cases may occur:
 	\begin{itemize}[leftmargin=*]
@@
 \begin{definition}
-	A (hyper)graph $G$ is $i,k,r$-rich for some $j,k,r\in \N$, if for any rooted tree $T$
+	A graph $G$ is $(i,k,r)$-rich for some $i,k,r\in \N$, if for any rooted tree $T$
 	of radius at most $r$ there are $x_1,\dots,x_i\in V(G)$ such that
@@
 	be a $(i,k,r)$-rich graph with constants. Then, for any $x\in V(G)$,
-	the graph $G(\clist, \cc_{m+1}(x))$ is $(i-1,j,s)$-rich, 
+	the graph \\$G(\clist, \cc_{m+1}(x))$ is $(i-1,j,s)$-rich, 
 	where $j,s$ are arbitrary natural numbers satisfying $j\leq k$,
@@
 
+For reference about E.F. games see \cite{finitemodeltheory1} and \cite{finitemodeltheory2}.
+
 \begin{theorem} 
-	Let $G_1, G_2$ be $k,k,3^k$-rich graphs such that $Core(G_1;3^k)$ is $k$-agreeable
+	Let $G_1, G_2$ be $(k,k,3^k)$-rich graphs such that $Core(G_1;3^k)$ is $k$-agreeable
 	with $Core(G_2;3^k)$. Ten $G_1$ and $G_2$ have the same rank $k$ type.
@@
 	is $k-i$-agreeable with  
-	\[ Core(G_2(\cc_1[y_1],\dots,\cc_i[y_i]);3^{k-i}) \],
+	\[ Core(G_2(\cc_1[y_1],\dots,\cc_i[y_i]);3^{k-i}), \]
 	where for each $1\leq j \leq i$, the vertices
@@
 	as a subgraph of $HG(n,p(n))$. Then
-	\[\Ln Pr(X_n>0)=0. \]
+	\[\Ln \mathrm{Pr}(X_n>0)=0. \]
 \end{proposition}
@@
 	\left( \frac{c_i}{n^{a_1-1}}\right)^{h_i}, \] 
-	where $b$ is the carnality of $F$'s group of isomorphisms. 
+	where $b$ is the cardinality of $F$'s group of isomorphisms. 
 	Then, for some constant $A$,
@@
 	subgraph with diameter no greater than $r$. Then
-	\[ \Ln Pr(A_n)=0. \]
+	\[ \Ln \mathrm{Pr}(A_n)=0. \]
 \end{corollary}
@@
 	For any $r$,
-	\[\Ln Pr(G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1} ) \text{ is }r \text{-simple})=1 .\]
+	\[\Ln \mathrm{Pr}(G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1} ) \text{ is }r \text{-simple})=1 .\]
 \end{corollary}
@@
 For any formula $\phi$ with free variables 
-$x_1, \dots, x_l$, we define $Pr_n(\phi(x_1,\dots,x_l))=
-\sum\limits_{G\models \phi(a_1,\dots,a_l)} Pr_n(G) $, 
+$x_1, \dots, x_l$, we define $\mathrm{Pr}_n(\phi(x_1,\dots,x_l))=
+\sum\limits_{G\models \phi(a_1,\dots,a_l)} \mathrm{Pr}_n(G) $, 
 where $a_1, \dots, a_l$ are fixed \textbf{different}
@@
 formulas with possibly some free variables, then we define
-$Pr_n(\phi \, | \sigma)=Pr_n(\phi\wedge \sigma)/Pr_n(\sigma)$. \par
+$\mathrm{Pr}_n(\phi \, | \sigma)=\mathrm{Pr}_n(\phi\wedge \sigma)/\mathrm{Pr}_n(\sigma)$. \par
 
@@
 	with free variables $x_1, \dots, x_l$. Then, for any $r\in \N$
-	\[ \Ln Pr_n(\phi_r(x_1, \dots x_l) \, | \sigma ) =1 .\]
+	\[ \Ln \mathrm{Pr}_n(\phi_r(x_1, \dots x_l) \, | \sigma ) =1 .\]
 \end{lemma}
 \begin{proof}
-	We will se that
-	\[ \Ln Pr_n(\neq \phi_r(x_1, \dots, x_l) \, | \sigma ) =0.\]
+	We will see that
+	\[ \Ln \mathrm{Pr}_n(\neq \phi_r(x_1, \dots, x_l) \, | \sigma ) =0.\]
 	Fix $n$ and $x_1,\dots, x_l \in [n]$.
     Notice that without loss of generality we can
-	assume that $\sigma$ Boolean combination of atomic
+	assume that $\sigma$ is Boolean combination of atomic
 	formulas of the form $R_i(y_1,\dots,y_{a_i})$, where the $y_i$'s
@@
 	only on the edges not in $x_1,\dots, x_l$.
-	Thus, $Pr_n(\neg \phi_r \, | \sigma)= Pr_n(\neg \phi_r)$.
+	Thus, $\mathrm{Pr}_n(\neg \phi_r \, | \sigma)= \mathrm{Pr}_n(\neg \phi_r)$.
 	Consider $G$ a random graph in $G(n,p(n))$. 
@@
 		from the $x_j$'s. Let us denote by $A$ the event that
-		such a path exists. One can check that $Pr_n(A)\leq C/n$
+		such a path exists. One can check that $\mathrm{Pr}_n(A)\leq C/n$
 		for some fixed $C$.   	
@@
 	union bound:
-	\[ Pr_n(\neq \phi_r)\leq  Pr_n(B)+ Pr_n(A) 
+	\[ \mathrm{Pr}_n(\neq \phi_r)\leq  \mathrm{Pr}_n(B)+ \mathrm{Pr}_n(A) 
 	\stackrel{n\to \infty}{\longrightarrow}	0.\]
 \end{proof}
+
+We give without proof (see Chapter 8, \cite{lecturenotes}) the following theorem,
+which will be our main technical tool for the rest of the work.
 
@@
 	\dots \lambda_r$. That is,	
-	\[ \forall x_1,\dots, x_r\in \N: \quad \Ln Pr(\wedge_{i=1}^r
-	 X_i=x_i)= \prod_{i=1}^r Poi_{\lambda_i}(x_i).\]
+	\[ \forall x_1,\dots, x_r\in \N: \quad \Ln \mathrm{Pr}(\wedge_{i=1}^r
+	 X_i=x_i)= \prod_{i=1}^r \mathrm{Poiss}_{\lambda_i}(x_i).\]
 
@@
 	at most $r$ it is satisfied
-	\[ \Ln Pr_n(\bigwedge_{i=1}^s Tree_r(x_i; x_1, \dots, x_l)\in C_i \, | 
+	\[ \Ln \mathrm{Pr}_n(\bigwedge_{i=1}^s Tree_r(x_i; x_1, \dots, x_l)\in C_i \, | 
 	\, \sigma(x_1,\dots, x_l) \,)= \prod_ {i=1}^s \lambda_{k,C_i,r}.\]	
@@
 %	\begin{align*} 
-%	&\Ln Pr_n(\bigwedge_{i=1}^s T_r(x_i; x_1, \dots, x_l)\in C_i \, | 
+%	&\Ln \mathrm{Pr}_n(\bigwedge_{i=1}^s T_r(x_i; x_1, \dots, x_l)\in C_i \, | 
 %	\,\sigma \,)= \\
-%	&=\Ln Pr_n(\bigwedge_{i=1}^s T_r(x_i; x_1, \dots, x_l)\in C_i \, | 
-%	\, \sigma \wedge \phi_r(x_1,\dots,x_l)\,).
+%	&=\Ln \mathrm{Pr}_n(\bigwedge_{i=1}^s T_r(x_i; x_1, \dots, x_l)\in C_i \, | 
+%	\, \textbf{\sigma }\wedge \phi_r(x_1,\dots,x_l)\,).
 %	\end{align*}
@@
 		y \text{ satisfies } P}} 
-		Pr( T(y) \, \wedge \, A(y) \wedge \, B(y) \, | \, \sigma \, ).		
+		\mathrm{Pr}( T(y) \, \wedge \, A(y) \wedge \, B(y) \, | \, \sigma \, ).		
 	\end{align} 
@@
 		\sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 
-		Pr( T(y) \, \wedge \, A(y) \wedge \, B(y) \, | \, \sigma \, )=\\
+		\mathrm{Pr}( T(y) \, \wedge \, A(y) \wedge \, B(y) \, | \, \sigma \, )=\\
 		& \label{eqn:distributed}
@@
 		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) \cdot
-		Pr( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )
+		\mathrm{Pr}( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )
 		\cdot \sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1,
@@
 	We can write
-	\[Pr( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )=
-	Pr( T(z) \, \wedge \, A(z) \, | \, B(z) \wedge \sigma \, )
-	\cdot Pr( \, B(z) \, | \, \sigma \, )\]
+	\[\mathrm{Pr}( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )=
+	\mathrm{Pr}( T(z) \, \wedge \, A(z) \, | \, B(z) \wedge \sigma \, )
+	\cdot \mathrm{Pr}( \, B(z) \, | \, \sigma \, )\]
 	Notice that $\phi_r(x_1,\dots, x_l)\wedge B(z)$ implies $A(z)\wedge
@@
 	\begin{align*} 
-	Pr( T(z)  \, | \, B(z) \wedge \sigma \, ) &
-	\geq Pr( T(z) \wedge A(z)  \, | \, B(z) \wedge \sigma \, ) \geq \\ 
-	& \geq Pr(T(z) \wedge \phi_r(x_1,\dots,x_l) 
+	\mathrm{Pr}( T(z)  \, | \, B(z) \wedge \sigma \, ) &
+	\geq \mathrm{Pr}( T(z) \wedge A(z)  \, | \, B(z) \wedge \sigma \, ) \geq \\ 
+	& \geq \mathrm{Pr}(T(z) \wedge \phi_r(x_1,\dots,x_l) 
 	\, | \, B(z) \wedge \sigma \, ).
@@
 	But using \cref{lem:faraway} we get
-	\[ \Ln  Pr_n(T(z) \wedge \phi_r(x_1,\dots,x_l)
+	\[ \Ln  \mathrm{Pr}_n(T(z) \wedge \phi_r(x_1,\dots,x_l)
 	\, | \, B(z) \wedge \sigma \, ) = 
-	\Ln Pr_n(T(z)\, | \, B(z) \wedge \sigma \, ), \]
+	\Ln \mathrm{Pr}_n(T(z)\, | \, B(z) \wedge \sigma \, ), \]
 	so
 	\begin{equation} 
-	\Ln  Pr_n(T(z) \wedge A(z)
+	\Ln  \mathrm{Pr}_n(T(z) \wedge A(z)
 	\, | \, B(z) \wedge \sigma \, ) = 
-	\Ln Pr_n(T(z)\, | \, B(z) \wedge \sigma \, ). 
+	\Ln \mathrm{Pr}_n(T(z)\, | \, B(z) \wedge \sigma \, ). 
 	\end{equation}
@@
  	Thus by the induction hypothesis we have
- 	\[\Ln Pr_n( T(z)  \, | \, B(z) \wedge \sigma \, )= \Gamma, \]
+ 	\[\Ln \mathrm{Pr}_n( T(z)  \, | \, B(z) \wedge \sigma \, )= \Gamma, \]
  	where 
@@
  		\cdot \Gamma \cdot
- 		Pr_m(\, B(z) \, | \, \sigma \, )
+ 		\mathrm{Pr}_m(\, B(z) \, | \, \sigma \, )
  		\cdot \sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1.
@@
  	, $B(z)$ and $\sigma$ are independent. Hence,
- 	\[ Pr_n(\, B(z) \, | \, \sigma \, ) = \prod_{i=1}^{s} 
+ 	\[ \mathrm{Pr}_n(\, B(z) \, | \, \sigma \, ) = \prod_{i=1}^{s} 
  	\prod_{E\in \mathcal{E}} \left(\frac{\beta_{c_E}}{n^{(a_E -1)}}
@@
  	\begin{equation} \label{eqn:substitution}
- 	Pr_n(\, B(z) \, | \, \sigma \, )\cdot \sum_{\substack{y:
+ 	\mathrm{Pr}_n(\, B(z) \, | \, \sigma \, )\cdot \sum_{\substack{y:
  	\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1 \simeq 	
@@
  	E\in \mathcal{E}}}$ it is satisfied
- 	\[ \Ln Pr_n\left(\bigwedge_{i=0}^{s}\bigwedge_{E\in \mathcal{E}} X_{i,E}=b_{i,E} \, \Bigg| \, \sigma \right) = 
+ 	\[ \Ln \mathrm{Pr}_n\left(\bigwedge_{i=0}^{s}\bigwedge_{E\in \mathcal{E}} X_{i,E}=b_{i,E} \, \Bigg| \, \sigma \right) = 
  	\prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
- 	Poi_{\mu_{E,(r-a_E+1)}}(b_{i,E}),\]
+ 	\mathrm{Poiss}_{\mu_{E,(r-a_E+1)}}(b_{i,E}),\]
  	where we define
@@
  	Notice that $\mu_{E,(r-a_E+1)}$ is an expression in $M$.
- 	The $k$-morphism class of $T_r(x_j;x_1, \dots, x_l)$ depends exclusively
+ 	The $k$-morphism class of $\\T_r(x_j;x_1, \dots, x_l)$ depends exclusively
  	on the number, up to $k+1$, of its initial edges of each type.
@@
  	\begin{align*}
- 	&\Ln Pr_n(\bigwedge_{i=1}^s Tree_r(x_i; x_1, \dots, x_l)\in C_i \, | 
+ 	&\Ln \mathrm{Pr}_n(\bigwedge_{i=1}^s Tree_r(x_i; x_1, \dots, x_l)\in C_i \, | 
  	\, \sigma \,)=\\ 
  	&=\prod_{i=0}^{s}\left[
- 	\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)<k+1}} Poi_{\mu_{E,(r-a_E+1)}}((C_i,E))\right)
+ 	\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)<k+1}} \mathrm{Poiss}_{\mu_{E,(r-a_E+1)}}((C_i,E))\right)
  	\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)\geq k+1}} 
- 	Poi_{\mu_{E,(r-a_E+1)}}(\geq (k+1))\right)\right]=\\
+ 	\mathrm{Poiss}_{\mu_{E,(r-a_E+1)}}(\geq (k+1))\right)\right]=\\
  	&=\prod_{i=0}^{s} \lambda_{k,C_i,r},
@@
     \[
-    \lambda{C_i,r}=\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)<k+1}} Poi_{\mu_{E,(r-a_E+1)}}((C_i,E))\right)
+    \lambda{C_i,r}=\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)<k+1}} \mathrm{Poiss}_{\mu_{E,(r-a_E+1)}}((C_i,E))\right)
     \left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)\geq k+1}} 
-    Poi_{\mu_{E,(r-a_E+1)}}(\geq (k+1))\right)
+    \mathrm{Poiss}_{\mu_{E,(r-a_E+1)}}(\geq (k+1))\right)
     .\]
@@
 
- 	%\[	Pr( T(z) \, \wedge \, A(z) \, | \, B(z) \wedge \sigma \, )
- 	%\cdot Pr( \, B(z) \, | \, \sigma \, )=	Pr( T(z) \, | \, B(z) \wedge %\sigma \, )
- 	%\cdot Pr( \, B(z) \, | \, \sigma \, )\]
+ 	%\[	\mathrm{Pr}( T(z) \, \wedge \, A(z) \, | \, B(z) \wedge \sigma \, )
+ 	%\cdot \mathrm{Pr}( \, B(z) \, | \, \sigma \, )=	\mathrm{Pr}( T(z) \, | \, B(z) \wedge %\sigma \, )
+ 	%\cdot \mathrm{Pr}( \, B(z) \, | \, \sigma \, )\]
 
@@
  %  some free variables,
- % \[ Pr_n(\, \alpha \wedge \phi_r \, | \, \sigma \,) \simeq
- %  Pr_n(\, \alpha \, |\, \phi_r \wedge \sigma \,) .\]
+ % \[ \mathrm{Pr}_n(\, \alpha \wedge \phi_r \, | \, \sigma \,) \simeq
+ %  \mathrm{Pr}_n(\, \alpha \, |\, \phi_r \wedge \sigma \,) .\]
  %  , where the notation  $ f(n)\simeq \ g(n)$, for maps $\N\rightarrow %\R$ satisfying that $g$ takes non-zero
@@
 %   \begin{align*}
-%   &\Ln Pr_n ( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )
+%   &\Ln \mathrm{Pr}_n ( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )
 %   \simeq \\
-%   &\Ln Pr_n ( T(z) \, \wedge \, B(z) \, | \, \phi_r(x_1, \dots, x_l)\, 
+%   &\Ln \mathrm{Pr}_n ( T(z) \, \wedge \, B(z) \, | \, \phi_r(x_1, \dots, x_l)\, 
 %   \wedge \, \sigma \, ) = \\
-%   &\Ln Pr_n ( T(z) \, | \, \phi_r \, 
+%   &\Ln \mathrm{Pr}_n ( T(z) \, | \, \phi_r \, 
 %   \wedge \, \sigma \, \wedge \, B(z) \, )\cdot
-%   Pr_n(B(z)\, | \, \phi_r \, 
+%   \mathrm{Pr}_n(B(z)\, | \, \phi_r \, 
 %   \wedge \, \sigma \,) \simeq \\
-%   &\Ln Pr_n ( T(z) \, | \, \phi_r \, 
+%   &\Ln \mathrm{Pr}_n ( T(z) \, | \, \phi_r \, 
 %   \wedge \, \sigma \, \wedge \, B(z) \, )
@@
 %	and any	$r\in \N$, $r>0$, we have
-%	\[\Ln Pr_n(\alpha \, | \, \sigma(x_1,\dots, x_l))
-%	= \Ln Pr_n(\alpha \, | \, \phi_r(x_1,\dots, x_l)\wedge \sigma ).\]
+%	\[\Ln \mathrm{Pr}_n(\alpha \, | \, \sigma(x_1,\dots, x_l))
+%	= \Ln \mathrm{Pr}_n(\alpha \, | \, \phi_r(x_1,\dots, x_l)\wedge \sigma ).\]
 %	
@@
 	For any $i,k,r\in \N$
-	\[\Ln Pr_n(\, G \text{ is } i,k,r\text{- rich}\,)=1.\]
+	\[\Ln \mathrm{Pr}_n(\, G \text{ is } i,k,r\text{- rich}\,)=1.\]
 \end{corollary}
@@
 	\begin{equation}\label{eqn:richgeq}
-	\Ln Pr_n\Bigg(\phi_{3r}(1,\dots, s) 
+	\Ln \mathrm{Pr}_n\Bigg(\phi_{3r}(1,\dots, s) 
 	\bigwedge_{C\in \mathcal{C}} A_{s,C}\Bigg)
-	\geq \Ln Pr_n(\, G \text{ is } i,k,r\text{- rich}\,).
+	\geq \Ln \mathrm{Pr}_n(\, G \text{ is } i,k,r\text{- rich}\,).
 	\end{equation}
@@
 	\begin{equation} \label{eqn:richaas}
-	\Ln Pr_n\Bigg(\phi_{3r}(1,\dots, s) 
+	\Ln \mathrm{Pr}_n\Bigg(\phi_{3r}(1,\dots, s) 
 	\bigwedge_{C\in \mathcal{C}} A_{s,C}\Bigg)=
-	\Ln Pr_n\Bigg( 
+	\Ln \mathrm{Pr}_n\Bigg( 
 	\bigwedge_{C\in \mathcal{C}} A_{s,C}\Bigg).
@@
 	\bigwedge_{C\in \mathcal{C}} A_{s,C}\Bigg)\geq
-	1- \sum_{C\in\mathcal{C}} Pr(\neq A_{s,C}).\]
+	1- \sum_{C\in\mathcal{C}} \mathrm{Pr}(\neq A_{s,C}).\]
 	Define, for each $s\geq i$, $C\in \mathcal{C}$ the
@@
 	\begin{align*}
-	 &\Ln Pr_n\Bigg( 
+	 &\Ln \mathrm{Pr}_n\Bigg( 
 	\bigwedge_{C\in \mathcal{C}} A_{s,C}\Bigg)\geq
-	\Ln 1- \sum_{C\in\mathcal{C}} Pr_n(\neq A_{s,C})=\\
-	&=\Ln 1- \sum_{C\in\mathcal{C}} Pr_n(X_{s,C}<i)=
+	\Ln 1- \sum_{C\in\mathcal{C}} \mathrm{Pr}_n(\neq A_{s,C})=\\
+	&=\Ln 1- \sum_{C\in\mathcal{C}} \mathrm{Pr}_n(X_{s,C}<i)=
 	1- \sum_{j<i} \binom{s}{j}\lambda_{k,C,r}^j(1-\lambda_{k,C,r})^{(s-j)}.
@@
 	$\lambda_{k,C,r}$ is positive. This means 
-	\[ \lim\limits_{s\to \infty} \Ln Pr_n\Bigg( 
+	\[ \lim\limits_{s\to \infty} \Ln \mathrm{Pr}_n\Bigg( 
 	\bigwedge_{C\in \mathcal{C}} A_{s,C}\Bigg)=1. \]
@@
 	we get that 
-	\[\Ln Pr_n(\, G \text{ is } i,k,r\text{- rich}\,)\geq 1\]
+	\[\Ln \mathrm{Pr}_n(\, G \text{ is } i,k,r\text{- rich}\,)\geq 1\]
 	and the result is proven.
@@
 	Let $O$ be a simple $k$-agreeability class. Then it is satisfied
-	\[ \Ln Pr_n(Core(G;r)\in O) = \theta, \]
+	\[ \Ln \mathrm{Pr}_n(Core(G;r)\in O) = \theta, \]
 	for some $\theta\in \Theta$.
@@
 	\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ satisfies }P}}
-	Pr(A(y)\wedge B(y)\wedge T(y)). \]
+	\mathrm{Pr}(A(y)\wedge B(y)\wedge T(y)). \]
 
@@
 	\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ satisfies }P}}
-	Pr(A(y)\wedge B(y)\wedge T(y))= \\ 
+	\mathrm{Pr}(A(y)\wedge B(y)\wedge T(y))= \\ 
 	\label{eqn:distributed3}
 	& =\prod_{U\in \mathcal{U}} 
-	\frac{1}{|\psi_U|^{b_U}b_U!} \cdot Pr(A(z)\wedge B(z)\wedge T(z)) \cdot
+	\frac{1}{|\psi_U|^{b_U}b_U!} \cdot \mathrm{Pr}(A(z)\wedge B(z)\wedge T(z)) \cdot
 	\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ injective }}}1,
@@
 	We can write 
-	\[Pr(A(z)\wedge B(z)\wedge T(z))=Pr(B(z)\wedge T(z) \, |\, A(z)) \cdot 
-	Pr(A(z)).\]
+	\[\mathrm{Pr}(A(z)\wedge B(z)\wedge T(z))=\mathrm{Pr}(B(z)\wedge T(z) \, |\, A(z)) \cdot 
+	\mathrm{Pr}(A(z)).\]
 	Let $\tau_r$ be the event that $G$ is $r$-simple. One can check that
@@
 	In consequence the following chain of inequalities holds
-	\[Pr(T(z)\,|\, B(z))\geq Pr(T(z)\wedge A(z) \,| \, B(z)) \geq
-	 Pr(T(z)\wedge \tau_r \,| \, B(z)).\]
+	\[\mathrm{Pr}(T(z)\,|\, B(z))\geq \mathrm{Pr}(T(z)\wedge A(z) \,| \, B(z)) \geq
+	 \mathrm{Pr}(T(z)\wedge \tau_r \,| \, B(z)).\]
 	Notice that $B(z)$ can be expressed as a purely relational open formula
@@
 	Using the previous theorem and \cref{thm:simple} we obtain
-	\[\Ln Pr_n(T(z)\wedge \tau_r \,| \, B(z))= \Ln Pr_n(T(z)| \,| \, B(z)) = \Gamma, \]
+	\[\Ln \mathrm{Pr}_n(T(z)\wedge \tau_r \,| \, B(z))= \Ln \mathrm{Pr}_n(T(z)| \,| \, B(z)) = \Gamma, \]
 	where
@@
 	Because the probability of each edge is independent, one obtains 
-	\[ Pr_n(B(z))= \prod_{(U,b)\in \widehat{\Omega}} 
+	\[ \mathrm{Pr}_n(B(z))= \prod_{(U,b)\in \widehat{\Omega}} 
 	\frac{\prod_{i=1}^c	\beta_i^{|H_i(cycle(U))|}}{n^{n_U}}.  \]
@@
 	natural numbers $(b_U)_{U\in \mathcal{U}}$ 
-	\[\Ln Pr_n\left( \bigwedge_{U\in \mathcal{U}} X_U=b_U  \right)=
-	\prod_{U\in \mathcal{U}}Poi_{\xi_U}(b_i),
+	\[\Ln \mathrm{Pr}_n\left( \bigwedge_{U\in \mathcal{U}} X_U=b_U  \right)=
+	\prod_{U\in \mathcal{U}}\mathrm{Poiss}_{\xi_U}(b_i),
 	\]
@@
 	In consequence,
-	\[ \Ln Pr_n(Core(G;r)\in O) = \left(\prod_{\substack{U\in \mathcal{U}\\(O,U)\leq k}} Poi_{\xi_U}((O,U)) \right) \left(\prod_{\substack{U\in \mathcal{U}\\(O,U)\geq k+1}}
-	Poi_{\xi_U}(\geq (k+1)) \right),\]
+	\[ \Ln \mathrm{Pr}_n(Core(G;r)\in O) = \left(\prod_{\substack{U\in \mathcal{U}\\(O,U)\leq k}} \mathrm{Poiss}_{\xi_U}((O,U)) \right) \left(\prod_{\substack{U\in \mathcal{U}\\(O,U)\geq k+1}}
+	\mathrm{Poiss}_{\xi_U}(\geq (k+1)) \right),\]
 	an this last limit belongs to $\Theta$ we wanted.   
@@
 		\item[(1)] 
-		\[ \Ln Pr(HG(n,p(n))\in \cup_{i=1}^m O_i)=1,\]
+		\[ \Ln \mathrm{Pr}(HG(n,p(n))\in \cup_{i=1}^m O_i)=1,\]
 		\item[(2)] For any $1\leq i \leq m$,
-		\[\Ln Pr_n((G\models \psi) \wedge
+		\[\Ln \mathrm{Pr}_n((G\models \psi) \wedge
 		 (F\models \neg \psi) \, | \, G,F\in O_i\,) = 0, \]
@@
 		\item[(3)] For any $1\leq i \leq m$,
-		\[ P_i(\beta):= \Ln Pr((HG(n,p(n,\beta)) \in O_i)\]
+		\[ P_i(\beta):= \Ln \mathrm{Pr}((HG(n,p(n,\beta)) \in O_i)\]
 		is well defined for all values of $\beta$ and it is an expression
@@
 \begin{equation} \label{eqn:sumevents}
-Pr_n(G\models \psi) = \sum_{i=1}^{m} Pr_n(E_i)  + Pr_n(F),
+\mathrm{Pr}_n(G\models \psi) = \sum_{i=1}^{m} \mathrm{Pr}_n(E_i)  + \mathrm{Pr}_n(F),
 \end{equation}
@@
 the limits 
-\[ \Ln Pr_n(G\models \psi \, | \, G\in O_i )\] 
+\[ \Ln \mathrm{Pr}_n(G\models \psi \, | \, G\in O_i )\] 
 are either zero or one, and 
 \begin{align}\label{eqn:property1}
-&\Ln Pr_n(E_i)= \Ln Pr_n(G\in O_i)\cdot Pr_n(G\models \phi \, | \, G\in O_i)=\\ 
+&\Ln \mathrm{Pr}_n(E_i)= \Ln \mathrm{Pr}_n(G\in O_i)\cdot \mathrm{Pr}_n(G\models \phi \, | \, G\in O_i)=\\ 
 &
 \nonumber
-= \text{ either } 0 \text{ or } \Ln Pr_n(G\in O_i).
+= \text{ either } 0 \text{ or } \Ln \mathrm{Pr}_n(G\in O_i).
 \end{align} 
@@
 Also, as a consequence of (1) we obtain
-\[\Ln Pr_n(\bigwedge_{i=1}^{m} G \notin O_i)=0, \] 
+\[\Ln \mathrm{Pr}_n(\bigwedge_{i=1}^{m} G \notin O_i)=0, \] 
 so
 \begin{equation}\label{eqn:property2}
-\Ln Pr_n(F)= \Ln Pr_n(\bigwedge_{i=1}^{m} G \notin O_i)\cdot 
-Pr_n(G\models \phi \, | \, \bigwedge_{i=1}^{m} G \notin O_i)=0.  
+\Ln \mathrm{Pr}_n(F)= \Ln \mathrm{Pr}_n(\bigwedge_{i=1}^{m} G \notin O_i)\cdot 
+\mathrm{Pr}_n(G\models \phi \, | \, \bigwedge_{i=1}^{m} G \notin O_i)=0.  
 \end{equation}
@@
 we get
-\[ \Ln Pr_n(G\models \psi) = \sum\limits_{O_i\in \mathcal{O}} \Ln
-Pr_n(G \in O_i) ,\]
+\[ \Ln \mathrm{Pr}_n(G\models \psi) = \sum\limits_{O_i\in \mathcal{O}} \Ln
+\mathrm{Pr}_n(G \in O_i) ,\]
 where $\mathcal{O}$ is a (possibly empty) subset of $\{O_1,\dots, O_{m}\}$.
-Finally, because of property (3) for each $i$ the limit $\Ln Pr_n(G \in O_i)$ is 
-an expression in $\Theta$. Thus $\Ln Pr_n(G\models \psi)$ is a finite sum of expressions in $\Theta$ and the theorem follows.
+Finally, because of property (3) for each $i$ the limit $\Ln \mathrm{Pr}_n(G \in O_i)$ is 
+an expression in $\Theta$. Thus $\Ln \mathrm{Pr}_n(G\models \psi)$ is a finite sum of expressions in $\Theta$ and the theorem follows.
 \end{proof}

### 2019-07-06 Presentacion Sparse Graphs/EssayPresentation.tex
Ha presentar

\documentclass[handout, 11pt]{beamer}

\usepackage[english] {babel}                 % Idioma (és important a l'hora de separar una paraula a final de línia)
\input{myStyle.sty}

\usetheme{CambridgeUS}
\usepackage{color}
\usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}

\setbeamertemplate{itemize items}[square]
\newtheorem{inneraxiom}{Axiom}
\newenvironment{axiom}[1]
{\renewcommand\theinneraxiom{#1}\inneraxiom}
{\endinneraxiom}
\definecolor{MyBackground}{RGB}{0.149    0.218   0.443}

\title[An Introduction to Synthetic Differential Geometry]{An Introduction to Synthetic Differential Geometry}

\author[Differential Geometry]{Lázaro Alberto Larrauri Borroto}
\date\today

\begin{document}
	\frame{\titlepage}
	\frame{\tableofcontents}

\section{Introduction}
\begin{frame}{What is Synthetic Differential Geometry?}
		\begin{columns}
			\begin{column}{0.55\textwidth}
				\begin{itemize}
					\item Given two different points there exists only one line incident to both
					of them.
					\\ ~\\
					\item Through a point not in a line, only one parallel line to the given one can be drawn.

				\end{itemize}
			\end{column}
			\begin{column}{0.45\textwidth}  %%<--- here
				\begin{center}
					\includegraphics[width=0.45\textwidth]{Euklid.jpg}
				\end{center}
			\end{column}
		\end{columns}
		\begin{center}
			But what are points and lines?
		\end{center}	
\end{frame}

\begin{frame}{What is Synthetic Differential Geometry?}
	\begin{columns}
		\begin{column}{0.55\textwidth}
			\begin{itemize}
				\item It is an axiomatic theory that deals with space forms in terms of their structure.
				\\~\\
				\item It allows for rigorous reasoning with nilpotent infinitesimals.
			\end{itemize}
		\end{column}
		\begin{column}{0.45\textwidth}
			\begin{center}				
				\includegraphics[width=0.45\textwidth]{Lie.jpg}
			\end{center}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Where does it take place?}
	We work in an ambient category $\mathcal{E}$ composed of ``smooth spaces and morphisms". \\~\\
	Synthetic differential geometry has no models in the category of sets. It has to be interpreted
	over a \textbf{topos}.
	\begin{itemize}
		\item Cartesian closed category with sub-object classifier. \\
		$A\times B$, $A^B$, $A\cup B$, $A\cap B$, $P(A)$ \dots

	\end{itemize}
\end{frame}

\section{Basic structure of the geometric line. The Kock-Lawvere axiom.}
\begin{frame}{Basic structure of the geometric line.}
	The geometric line $R$ satisfies:  \\~\\
	\begin{axiom}{0} $R$ is a non-trivial $\mathbb{Q}$-algebra.
	\end{axiom}
	\begin{center}
		\includegraphics[width=0.6\textwidth]{Compass.png}
	\end{center}
\end{frame}

\begin{frame}{The Kock-Lawvere axiom.}
\[ f(x) \simeq f(0) + f^\prime(0)x \]
\\~\\
\begin{itemize}
	\item Is there any $x$ such that we can substitute $\simeq$ with $=$ for all $f$'s? 
	\\~\\
	\pause
	\item No, we would need $x$ ``so small" that $x^2=0$.

\end{itemize}
\end{frame}

\begin{frame}{The Kock-Lawvere axiom.}
Let 
\[
D:=\{ \, d\in R  \, | \, d^2=0 \,\}\] \\~\\

\begin{axiom}{1}[Kock-Lawvere axiom]
	For any $f:D\rightarrow R$ there exists a unique $b\in R$ such that
	\[\forall d\in D: \quad f(d)= f(0) + db. \]
\end{axiom}
\end{frame}

\begin{frame}{Wait, are we safe?}
Intuitionistically speaking, yes. \\~\\
Under classical assumptions, not so much. 
\end{frame}

\begin{frame}{Wait, are we safe?}
The Kock-Lawvere axiom is not consistent with the Principle of the Excluded Middle: \\~\\
\[ P\vee \neg P \]
\\~\\
We must use ``intuitionistic" logic. 
\end{frame}

\begin{frame}{Derivatives and Taylor series.}
	Derivatives are defined in a natural way. \\~\\~\\
	\begin{definition} 
		Let $f\in R^R$. The derivative of $f$ at the point $x\in R$ is the unique 
		constant $f^\prime(x)\in R$ such that
		\[\forall d\in D: \quad f(x+d)= f(x)+ f^\prime(x)d.\]
	\end{definition}
	And functions ``locally" coincide with their linear approximations. 
\end{frame}

\begin{frame}{Derivatives and Taylor series.} 
	D is not an ideal.\\ ~ \\
	What can we say  about
	\[ D_2:= \{ \, d\in R \, | \, d^3=0 \,  \}?\]
\end{frame}

\begin{frame}{Derivatives and Taylor series.} 
	Not much. 
	We need an additional axiom:
	\\~\\
	\begin{axiom}{$1_2$} For any $f\in R^{D_2}$ there exist unique $c_1,c_2\in R$ such that
		\[ \forall d\in D_2: \quad f(d) = f(0) + c_1d + c_2d^2  \]
	\end{axiom}  
\end{frame}

\begin{frame}{Derivatives and Taylor series.} 
	This way we have:
	\\~\\ 
	\begin{theorem} For any $f\in R^R$
		\[ \forall d \in D_2, \forall x\in R : \quad f(x + d)=f(0) + f^\prime(x)d + \frac{f^{\prime \prime}(x)}{2}
		d^2. \]
	\end{theorem}
\end{frame}

\begin{frame}{Derivatives and Taylor series.} 
	Similarly, we would need an additional axiom for any of
	\[ D_k := \{ \, d\in R \, | d^{k+1}=0 \, \} \text{ for } k=1,2,\dots  	\]
	\\~\\
	We can state them all together: \\~\\

	\begin{axiom}{$1^\prime$} Let $f\in R^{D_k}$ for some $k\in \N$. Then there exists 
		a unique $k$-tuple of constants $c_1,\dots, c_k\in R$ such that
		\[ \forall d\in D_k: \quad f(d)= f(0) + \sum_{i=1}^{k}c_k d^k \]
	\end{axiom}

\end{frame}

\begin{frame}{Derivatives and Taylor series.} 
	If we define $D_\infty=\bigcup_{i=0}^\infty D_i$ it follows\\~\\~\\
	\begin{theorem}[Taylor series] 
		For all $f\in R^R$ and $x\in R$ there exists a unique formal power series $\Phi(X)$
		such that
		\[ \forall d\in D_\infty:  \quad f(x+d) = \Phi(d).\]
		Namely, 
		\[ \Phi(X) = \sum_{i=0}^\infty \frac{f^{(k)}}{k!} X^k.	\]

	\end{theorem}
\end{frame}

\begin{frame}{Don't let the axiom-party stop.} 
	There are still families of infinitesimals we cannot deal with.
	\[ D(2):=\{\, (d_1,d_2)\in D^2 \, | \, d_1d_2=0 \, \} \]
	\\~\\ 
	Our current axioms state that
	\[ W_k:=R[X]/\langle X^{k+1} \simeq R^{D_k}, \text{ where } ``D_k=Spec_R(W_k)" \]

\end{frame}

\begin{frame}{Don't let the axiom-party stop.} 	
	In general, if $W=R[X_1,\dots,X_n]$ satisfies some technical condition (it is a \textbf{Weil algebra}) 
	we can state:
	\begin{axiom}{w}~
	\[W\simeq R^{Spec_R(W)} \]
	\end{axiom}
\end{frame}

\section{Vector fields}
\begin{frame}{Tangent Vectors}

	\begin{definition}
		A \textbf{tangent vector} to $M$ at the point $p\in M$ is a map 
		$t\in M^D$ such that $t(0)=p$.
	\end{definition}
	Thus, $M^D$ is the \text{tangent bundle} of $M$. 
	\\~\\ To give $(M^D)_p$ a tangent space structure we need $M$ to be ``infinitesimally linear".

\end{frame}

\begin{frame}{Tangent Vectors}
	\begin{definition} \label{def:inflinear}
		An object $M$ is said to be \textbf{infinitesimally linear} if for any $p\in M$ and 
		any	$n$-tuple of maps $t_1,\dots, t_n \in (M^D)_p$ there is a unique map $l\in M^{D(n)}$ satisfying 
		$l\circ incl_i=t_i$ for all $i=1,\dots,n$. 
	\end{definition} 
\end{frame}

\begin{frame}{Differentials}

	\begin{theorem} \label{prof:difflinear}
		Let $M$ and $N$ be infinitesimally linear, and $f\in N^M$. Then, for
		any $p\in M$ the map $f^D(t)=f\circ t$ restricts to a linear map from $(M^D)_p$
		to $(N^D)_{f(p)}$.

	\end{theorem}

\end{frame}
\begin{frame}{Vector Fields}
\begin{definition} 
	A vector field $X$ over $M$ is any of the following: 
	\begin{itemize}
		\item A ``section of the tangent bundle",  $\hat{X}:M\rightarrow M^D$.
		\item An ``infinitesimal flow
		of the aditive group $R$" $X: M\times D \rightarrow M$
		\item An ``infinitesimal
		deformation of the identity map" $\check{X}:D\rightarrow M^M$.
	\end{itemize}
\end{definition}
\end{frame}

\begin{frame}{Directional Derivatives}
	\begin{definition} 
		The directional derivative of $f$ in the direction of $X$
		is the unique map $X(f)\in M^R$ such that, for any $p\in M$
		\[\forall d\in D: \quad f(X(p,d))= f(p) + dX(f)(p) .\]			
	\end{definition}
\end{frame}

\begin{frame}
Under some additional hypotheses on $M$ we can define:
\\~\\

\begin{definition}
	Let $X,Y\in Vect(M)$. The \textbf{Lie bracket} $[X,Y]$ is the unique vector 
	field such that
	\[\forall d_1, d_2 \in D: \quad[X,Y]^\vee (d_1d_2)= 
	\check{Y}(-d_2)\circ \check{X}(-d_1)\circ
	\check{Y}(d_2)\circ \check{X}(d_1) \]
\end{definition}
~\\
And it is satisfied 
\[ [X,Y](f)= X(f) - Y(f) \]
\end{frame}

\begin{frame}

\begin{center}
	\Large{Questions?}\\~\\~\\~\\~\\
	\tiny{Let them be easy please}
\end{center}

\end{frame}

\end{document}

### 2019-07-06 Presentacion Sparse Graphs/presentacio.tex
Ha presentar

\documentclass[handout, 11pt]{beamer}

\usepackage[english] {babel}                 % Idioma (és important a l'hora de separar una paraula a final de línia)
%\input{myStyle.sty}

\usetheme{CambridgeUS}
\usepackage{color}
\usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\setbeamertemplate{itemize items}[circle]

\title[First Order Logic of Sparse Random Graphs]{First Order
Logic of Sparse Random Graphs}

\begin{document}
	\frame{\titlepage}

\begin{frame}{Preliminaries}
\begin{center}
	\large{First order language of graphs}
\end{center}
\begin{columns}
	\begin{column}{0.55\textwidth}
		\begin{itemize}
			\item Variables $x_1, \dots, x_n, \dots$
			\item Connectives $\wedge, \vee$, equality symbol $=$,
			and negation symbol $\neg$.
			\item Quantifiers $\forall, \exists$.
			\item A binary relation symbol $R$
		\end{itemize}
	\end{column}
		\begin{column}{0.45\textwidth}
		\begin{itemize}
			\item Vertices.
			\item ``And", ``or", ``equals", ``not".
			\item ``For all", ``there exists".
			\item Edges $x\sim y$. 
		\end{itemize}
	\end{column}
\end{columns}
~\\
\[ \forall x_1,x_2 \, R(x_1,x_2) \implies \exists x_3 \,
 \neg(x_3=x_1)\wedge \neg(x_3=x_1) \wedge R(x_1, x_3)\]
\end{frame}

\begin{frame}{Preliminaries}
	\Large{Binomial model of random graphs $G(n,p)$.} \\
	\large
	~\\
	Start with vertex set $[n]=\{1,\dots, n\}$ and
	each edge is added with probability $p$ independently. 
	\\~\\
	If $G=([n], E)$:
	\[ Pr(G)= p^{|E|}\cdot (1-p)^{\binom{n}{2}- |E|}. \]

\end{frame}

\begin{frame}{The problem}
For any F.O. sentence $\phi$ we can talk about
\[ Pr(G(n,p)\models \phi ), \]
And if $p=p(n)$ it also makes sense
\[ \Ln Pr(G(n,p(n))\models \phi) .\]

What do we know about these limits?

\end{frame}

\begin{frame}{The problem}	
For $p(n)=n^{-\alpha}$ and $\alpha\in [0,1]$ we have a nearly complete answer.
\begin{theorem}{(Fagin 19776)} If $0\leq p \leq 1$ is constant a Zero-One Law is satisfied
\end{theorem}
\begin{theorem}{(Spencer, Shelah 1988)} 
	\begin{itemize}
		\item If $\alpha \in (0,1)\setminus \mathbb{Q}$ then
		a Zero-One law holds.
		\item If $\alpha \in (0,1)\cup \mathbb{Q}$ then a Zero-One
		lay does not hold. Even more, there is a F.O. sentence
		$\phi$ such that
		\[ \Ln Pr(G(n,p(n))\models \phi) \]   
		does not exist.
	\end{itemize}
\end{theorem}

\end{frame}

\begin{frame}{The problem}
\begin{theorem}{(Lynch, 1992).} 
	If $p(n)=c/n$ for some positive real $c$
	the limit
	\[ \Ln Pr(G(n,p(n))\models \phi)\]
	always exists and is analytic in $c$.  
\end{theorem}
\end{frame}

\begin{frame}{The landscape of $G(n,c/n)$}
	We are interested in last theorem.\\~\\
	\begin{itemize}
		\item The number of cycles of 
		length $3,4\dots, r$
		are asymptotically distributed like independent Poisson 
		variables.
		\item Small cycles are a.a.s far away.
		\item Fixed vertices are a.a.s far away.
		\item The ball of a given radius centered in fixed
		vertex is a.a.s a tree. Any tree occurs with a positive 
		probability.
	\end{itemize}
\end{frame}

\begin{frame}{Outline of the proof}
	For any quantifier rank $k$ we show (constructively) that there exist
	some classes of graphs $C_1,.., C_m$ such that \\~\\
	\begin{itemize}
		\item[(1)] A.a.s any two random graphs in the same class
		have the same rank $k$ type.
		\item[(2)] A.a.s. a random graph belongs to some $C_i$.
		\item[(3)] $\Ln Pr(G\in C_i)$ exists for any $i$ and is
		analytic in $c$.
	\end{itemize}

\end{frame}
\begin{frame}{Outline of the proof}
	After this, for any F.O. sentence $\phi$ we obtain
	\\
	\begin{align*}
	 \Ln Pr(\phi) &= \sum_{i=1}^{m} \Ln Pr(\, \phi \wedge G\in C_i \,) + 
	  \Ln Pr(\, \phi \wedge G\notin C_1\cup \dots \cup C_l \,) \\
	 & \stackrel{(2)}{=} \sum_{i=1}^{m} \Ln Pr(\, \phi \, |\, G\in C_i \,)Pr( \, G\in C_i \,) \\
	 & \stackrel{(1)}{=} \sum_{j=1}^{l} \Ln Pr(\,G \in C_{i_j} \,)
	\end{align*}
	\\~\\
	And finally because of (3) this limit exists and is analytic in $c$.	
\end{frame}

\begin{frame}{Outline of the proof}

The classes $C_1,\dots, C_m$ are obtained as the equivalence classes
of a relation on graphs that \textbf{only} depends on the ``small" neighborhoods
of the small cycles. \\
\[ x \in  Core(G,r) \iff d(x,c)\leq r , \text{ for some cycle }c \text{ of length 
} \leq 2r+1 \]
~\\

\end{frame}

\begin{frame}{Outline of the proof}
\Large
	\begin{itemize}
		\item The probability of any given ``class" of core is given by
		a nested sequence of products of ``Poisson expressions¨, analytic on $c$.
		\\~\\
		\item To show that graphs with ``equivalent¨ cores share the same 
		rank $k$ type E.F games are used. 
	\end{itemize}

\end{frame}

\begin{frame}
	 \Large
	Can this be generalized to regular hypergraphs with edge size $a$ y
	edge probability $c/n^{a-1}$?\\~\\

	Yes it seems so. You can even consider arbitrary symmetry groups on the edges and
	multiple edge sets with different sizes.  
\end{frame}

\end{document}

### 2019-07-06 Presentacion/Presentación.tex
Ha presentar

--- 2019-07-06 Presentacion Sparse Graphs/presentacio.tex
@@
 
-\usepackage[english] {babel}                 % Idioma (és important a l'hora de separar una paraula a final de línia)
+\usepackage[english] {babel}                 % Idioma (és important a l'hora de separar una paraula a final de línia)t
 %\input{myStyle.sty}
@@
 \usepackage{color}
+\usepackage{graphicx}
 \usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}
@@
 	\frame{\titlepage}
-
-\begin{frame}{Preliminaries}
-\begin{center}
-	\large{First order language of graphs}
-\end{center}
-\begin{columns}
-	\begin{column}{0.55\textwidth}
-		\begin{itemize}
-			\item Variables $x_1, \dots, x_n, \dots$
-			\item Connectives $\wedge, \vee$, equality symbol $=$,
-			and negation symbol $\neg$.
-			\item Quantifiers $\forall, \exists$.
-			\item A binary relation symbol $R$
-		\end{itemize}
-	\end{column}
-		\begin{column}{0.45\textwidth}
-		\begin{itemize}
-			\item Vertices.
-			\item ``And", ``or", ``equals", ``not".
-			\item ``For all", ``there exists".
-			\item Edges $x\sim y$. 
-		\end{itemize}
-	\end{column}
-\end{columns}
-~\\
-\[ \forall x_1,x_2 \, R(x_1,x_2) \implies \exists x_3 \,
- \neg(x_3=x_1)\wedge \neg(x_3=x_1) \wedge R(x_1, x_3)\]
-\end{frame}
-
-\begin{frame}{Preliminaries}
-	\Large{Binomial model of random graphs $G(n,p)$.} \\
-	\large
-	~\\
-	Start with vertex set $[n]=\{1,\dots, n\}$ and
-	each edge is added with probability $p$ independently. 
-	\\~\\
-	If $G=([n], E)$:
-	\[ Pr(G)= p^{|E|}\cdot (1-p)^{\binom{n}{2}- |E|}. \]
-
-\end{frame}
-
-\begin{frame}{The problem}
-For any F.O. sentence $\phi$ we can talk about
-\[ Pr(G(n,p)\models \phi ), \]
-And if $p=p(n)$ it also makes sense
-\[ \Ln Pr(G(n,p(n))\models \phi) .\]
-
-What do we know about these limits?
-
-\end{frame}
-
-\begin{frame}{The problem}	
-For $p(n)=n^{-\alpha}$ and $\alpha\in [0,1]$ we have a nearly complete answer.
-\begin{theorem}{(Fagin 19776)} If $0\leq p \leq 1$ is constant a Zero-One Law is satisfied
-\end{theorem}
-\begin{theorem}{(Spencer, Shelah 1988)} 
-	\begin{itemize}
-		\item If $\alpha \in (0,1)\setminus \mathbb{Q}$ then
-		a Zero-One law holds.
-		\item If $\alpha \in (0,1)\cup \mathbb{Q}$ then a Zero-One
-		lay does not hold. Even more, there is a F.O. sentence
-		$\phi$ such that
-		\[ \Ln Pr(G(n,p(n))\models \phi) \]   
-		does not exist.
-	\end{itemize}
-\end{theorem}
-
-\end{frame}
-
-\begin{frame}{The problem}
-\begin{theorem}{(Lynch, 1992).} 
-	If $p(n)=c/n$ for some positive real $c$
-	the limit
-	\[ \Ln Pr(G(n,p(n))\models \phi)\]
-	always exists and is analytic in $c$.  
-\end{theorem}
-\end{frame}
-
-\begin{frame}{The landscape of $G(n,c/n)$}
-	We are interested in last theorem.\\~\\
-	\begin{itemize}
-		\item The number of cycles of 
-		length $3,4\dots, r$
-		are asymptotically distributed like independent Poisson 
-		variables.
-		\item Small cycles are a.a.s far away.
-		\item Fixed vertices are a.a.s far away.
-		\item The ball of a given radius centered in fixed
-		vertex is a.a.s a tree. Any tree occurs with a positive 
-		probability.
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Outline of the proof}
-	For any quantifier rank $k$ we show (constructively) that there exist
-	some classes of graphs $C_1,.., C_m$ such that \\~\\
-	\begin{itemize}
-		\item[(1)] A.a.s any two random graphs in the same class
-		have the same rank $k$ type.
-		\item[(2)] A.a.s. a random graph belongs to some $C_i$.
-		\item[(3)] $\Ln Pr(G\in C_i)$ exists for any $i$ and is
-		analytic in $c$.
-	\end{itemize}
-
-\end{frame}
-\begin{frame}{Outline of the proof}
-	After this, for any F.O. sentence $\phi$ we obtain
-	\\
-	\begin{align*}
-	 \Ln Pr(\phi) &= \sum_{i=1}^{m} \Ln Pr(\, \phi \wedge G\in C_i \,) + 
-	  \Ln Pr(\, \phi \wedge G\notin C_1\cup \dots \cup C_l \,) \\
-	 & \stackrel{(2)}{=} \sum_{i=1}^{m} \Ln Pr(\, \phi \, |\, G\in C_i \,)Pr( \, G\in C_i \,) \\
-	 & \stackrel{(1)}{=} \sum_{j=1}^{l} \Ln Pr(\,G \in C_{i_j} \,)
-	\end{align*}
-	\\~\\
-	And finally because of (3) this limit exists and is analytic in $c$.	
-\end{frame}
-
-\begin{frame}{Outline of the proof}
-
-The classes $C_1,\dots, C_m$ are obtained as the equivalence classes
-of a relation on graphs that \textbf{only} depends on the ``small" neighborhoods
-of the small cycles. \\
-\[ x \in  Core(G,r) \iff d(x,c)\leq r , \text{ for some cycle }c \text{ of length 
-} \leq 2r+1 \]
-~\\
-
-\end{frame}
-
-\begin{frame}{Outline of the proof}
-\Large
-	\begin{itemize}
-		\item The probability of any given ``class" of core is given by
-		a nested sequence of products of ``Poisson expressions¨, analytic on $c$.
-		\\~\\
-		\item To show that graphs with ``equivalent¨ cores share the same 
-		rank $k$ type E.F games are used. 
-	\end{itemize}
-
-\end{frame}
-
 \begin{frame}
-	 \Large
-	Can this be generalized to regular hypergraphs with edge size $a$ y
-	edge probability $c/n^{a-1}$?\\~\\
-
-	Yes it seems so. You can even consider arbitrary symmetry groups on the edges and
-	multiple edge sets with different sizes.  
+	\includegraphics[scale=0.5]{kmorphictrees}
 \end{frame}

### 2019-07-06 Presentacion/Presentación.tex
Haciendo presentaciooon

@@
 
-\usepackage[english] {babel}                 % Idioma (és important a l'hora de separar una paraula a final de línia)t
+\usepackage[english] {babel}                 % Idioma (és important a l'hora de separar una paraula a final de línia)
 %\input{myStyle.sty}
@@
 \usepackage{color}
+\usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}
 \usepackage{graphicx}
-\usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}
-\newcommand{\Ln}{\lim\limits_{n\to \infty}}
+\usepackage{float}
+%\usepackage{hyperref}
+%\usepackage{enumerate}
+%\usepackage{enumitem}
+\usepackage{chngcntr}
+%\usepackage{cleveref}
+\usepackage{pdfpages}
 \setbeamertemplate{itemize items}[circle]
 
-\title[First Order Logic of Sparse Random Graphs]{First Order
-Logic of Sparse Random Graphs}
+\newcommand{\cc}{\mathfrak{c}}
+\newcommand{\Z}{\mathbb{Z}}
+\newcommand{\CC}{\mathbb{C}}
+\newcommand{\Q}{\mathbb{Q}}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\N}{\mathbb{N}}
+\newcommand{\Hc}{\mathcal{H}}
+\newcommand{\Lan}{\mathcal{L}}
+\newcommand{\Ln}{\lim\limits_{n\to \infty}}
+\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
+\newcommand{\morph}[1]{\stackrel{#1}{\simeq}}
+\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
+\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
+
+\setbeamertemplate{itemize items}[circle]
+
+\AtBeginSection[]
+{
+	\begin{frame}{Contents}
+	\tableofcontents[currentsection]
+	\end{frame}
+}
+
+\title[First Order Logic of Sparse Random Hyper-Graphs]{First Order
+	Logic of Sparse Random Hyper-Graphs}
+
+\author{L\'azaro Alberto Larrauri Borroto \\ 
+	Supervisor: Marc Noy Serrano}
+
+\date\today
 
@@
 	\frame{\titlepage}
-\begin{frame}
-	\includegraphics[scale=0.5]{kmorphictrees}
+	\frame{\tableofcontents}
+
+	\section{First Order Logic of Sparse Graphs}
+	\begin{frame}{The first order language of graphs.}
+		\begin{columns}
+			\begin{column}{0.55\textwidth}
+				\begin{itemize}
+					\item Variables $x_1, \dots, x_n, \dots$
+					\item Connectives $\wedge, \vee$, equality symbol $=$,
+					and negation symbol $\neg$.
+					\item Quantifiers $\forall, \exists$.
+					\item A binary relation symbol $R$
+				\end{itemize}
+			\end{column}
+			\begin{column}{0.45\textwidth}
+				\begin{itemize}
+					\item Vertices.
+					\item ``And", ``or", ``equals", ``not".
+					\item ``For all", ``there exists".
+					\item Edges $x\sim y$. 
+				\end{itemize}
+			\end{column}
+		\end{columns}
+		~\\
+		\[ \forall x_1,x_2 \, R(x_1,x_2) \implies \exists x_3 (\,
+		\neg(x_3=x_1)\wedge \neg(x_3=x_2) \wedge R(x_1, x_3))\]
 	\end{frame}
 
+	\begin{frame}{The binomial model}
+	The binomial model of random graphs $G(n,p)$ is a discrete probability space where 
+	we assign to each graph $G=([n],E)$ the probability
+	\[\mathrm{Pr}(G)= p^{|E|}\cdot (1-p)^{\binom{n}{2}- |E| }. \]
+	\end{frame}
+
+	\begin{frame}{Lynch's theorem}
+	\begin{theorem}[Lynch, 1992]
+		Let $\varphi$ be a sentence in the F.O. language of graphs. 
+		Then the map $\mathrm{F}_\varphi: [0,\infty) \rightarrow \R$ given by 
+		\[\mathrm{F}_\varphi(\beta)=\Ln \mathrm{Pr}(\, G(n,\beta/n)\models \varphi \,) \]
+		is well defined and admits an analytic extension to $\CC$.
+	\end{theorem}
+	\end{frame}
+
+	\begin{frame}{Overview of the proof}
+	Some properties of $G(n,\beta/n)$:
+	\\~\\
+	\begin{itemize}
+		\item The number of cycles of 
+		length $3,4\dots, r$
+		are asymptotically distributed like independent Poisson 
+		variables.
+		\item Small cycles are a.a.s far away.
+		\item Fixed vertices are a.a.s far away.
+		\item The ball of a given radius centered in fixed
+		vertex is a.a.s a tree. Any tree occurs with a positive 
+		probability.
+	\end{itemize}
+
+	\end{frame}
+
+	\begin{frame}{Overview of the proof}
+	For each fixed quantifier rank $k$:
+	\\~\\
+		\begin{itemize}
+			\item[(1)]	It is given a finite classification of "small" uni-cycles.
+			\item[(2)]  It is shown that the rank $k$ type of random graph $G$
+			 in $G(n,\beta/n)$ a.a.s depends exclusively on the number of "small" uni-cycles
+			 belonging to each class. 
+			\item[(3)] The asymptotic distribution of those quantities is obtained. 
+		\end{itemize}
+
+	\end{frame}
+	\section{General relational structures}
+	\begin{frame}{Edge sets}
+		\begin{definition} Fix
+			\begin{itemize}
+				\item natural numbers $n,a\in \N$, with $a\geq 2$
+				\item a subgroup of the symmetric group $\Phi \leq S_a$
+				\item and a subset of pairs $A\subset ([a]\times [a]) \setminus \Delta_a$.
+			\end{itemize}
+		The \textbf{total edge set} $\mathcal{H}_{(a,\Phi, A)}(n)$ of size $a$, 
+		symmetry group $\Phi$ and
+		restrictions $A$, on $n$ elements is the set
+		\[ \mathcal{H}_{(a,\Phi, A)}(n)= ([n]^a/\Phi) \, \,
+		\setminus R, \]
+		where
+		\[ R = \{\,  [x_1, \dots,x_a] \in [n]^a/\Phi  \, \, 
+		| \, \, x_i=x_j \, \text{for some } (i,j)\in A \} \] 
+		\end{definition}
+	\end{frame}
+	\begin{frame}{Graphs}
+		\begin{definition}
+			An (hyper)-graph $([n], H_1,\dots, H_c)$ with edge colors 
+			$1,\dots, c$, sizes $a_1,\dots,a_c$, 
+			symmetry groups $\Phi_1,\dots,\Phi_c$ and 
+			restrictions $A_1,\dots,A_c$ consists of 
+			\begin{itemize}
+				\item The vertex set $[n]$ for some natural number $n$.
+				\item For $i=1,\dots,c$, a ``colored" edge set $H_i\subseteq \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ whose elements 
+				have color $i$.
+			\end{itemize}
+		\end{definition}
+	\end{frame}
+
+	\begin{frame}{The first order language}
+	Consider the first order purely relational language $\mathcal{L}$ whose signature consists of the relation symbols
+	$R_1,\dots, R_c$ with arities $a_1,\dots,a_c$. \\~ \par
+
+	A graph $G=([n],H_1,\dots, H_c)$ is a $\mathcal{L}$-structure in the following way:
+	\begin{itemize}
+		\item The universe of $G$ is its vertex set, $[n]$.
+		\item For each $1\leq i \leq c$, 
+		\[(x_1,\dots,x_{a_i})\in R_i^G \iff [x_1,\dots, x_{a_i}]\in H_i. \] 
+	\end{itemize}
+%		\begin{columns}
+%			\begin{column}{0.55\textwidth}
+%				\begin{itemize}
+%					\item Variables $x_1, \dots, x_n, \dots$
+%					\item Connectives $\wedge, \vee$, equality symbol $=$,
+%					and negation symbol $\neg$.
+%					\item Quantifiers $\forall, \exists$.
+%					\item For each $1\leq i \leq c$ a relation symbol $R_i$ with arity $a_i$.
+%				\end{itemize}
+%			\end{column}
+%			\begin{column}{0.45\textwidth}
+%				\begin{itemize}
+%					\item Vertices.
+%					\item ``And", ``or", ``equals", ``not".
+%					\item ``For all", ``there exists".
+%					\item $i$-colored edges \\
+%					$[x_1,\dots,x_{a_i}]$. 
+%				\end{itemize}
+%			\end{column}
+%		\end{columns}
+	\end{frame}
+
+	\begin{frame}{The first order language}
+		By definition, a graph $G=([n],H_1,\dots, H_n)$ satisfies, for each $1\leq i \leq c$:
+		\vspace{0.5 em}
+		\begin{itemize}
+			\item Symmetry formulas:
+			\[ S_g: =\big( R_i(x_1\dots,x_{a_i})\iff R_i(x_{g(1)}\dots,x_{g(a_i)})\big) ,\]
+			where $g$ is an element from $\Phi_i$.
+			\item Anti-reflexivity formulas:
+			\[A_{i,(j,l)}:=\big(R_i(x_1\dots,x_{a_i})\implies 
+			\neg(x_j= x_l)\big),\]
+			where $(j,l)\in A_i$.
+		\end{itemize}
+
+	\end{frame}
+
+	\begin{frame}{The random model}
+
+	The random model $HG(n,p_1,\dots, p_c)$ is a discrete probability space where for each graph 
+	$G=([n],H_1,\dots,H_c)$,
+	\[ \mathrm{Pr}(G)=\prod_{i=1}^{c} p_i^{|H_i|}\cdot (1-p_i)^{|\mathcal{H}_{(a_i,\Phi_i,A_i)}(n)|-|H_i|} . \]
+	We consider the case where for each $1\leq i \leq c$,  $p_i(n)=\beta_i/n^{a_i-1}$.
+	\\~\\ 
+	Let $\beta=(\beta_1,\dots, \beta_c)\in [0,\infty)^c$. We abbreviate
+	\[HG(n,p(n,\beta)):= HG(n,\beta_1/n^{a_1-1},\dots, \beta_c/n^{a_c-1}). \]
+
+	\end{frame}
+
+	\begin{frame}{The theorem}
+		For each $1\leq i \leq c$ let $p_i(n,\beta_i)=\beta_i/n^{a_i-1}$. Let $\beta=(\beta_1,\dots,\beta_c)$ and 
+		$p(n,\beta)=(p_1(n,\beta_i),\dots,p_c(n,\beta_c)$.
+
+		\end{frame}
 \end{document}

### 2019-07-07 Presentacion/Presentación.tex
cambio tonto
Pictures

@@
 	\begin{frame}{The theorem}
-		For each $1\leq i \leq c$ let $p_i(n,\beta_i)=\beta_i/n^{a_i-1}$. Let $\beta=(\beta_1,\dots,\beta_c)$ and 
-		$p(n,\beta)=(p_1(n,\beta_i),\dots,p_c(n,\beta_c)$.
+		We want to prove the following
+
+		\begin{theorem} Let $\varphi$ be a first order sentence in $\mathcal{L}$.
+			Then the map $\mathrm{F}:[0,\infty)^c\rightarrow \R$ given by
+			\[ \mathrm{F}(\beta_1,\dots, \beta_c)= \Ln 
+			\mathrm{Pr}(HG(n,p(n,\beta))\models \varphi )
+			\]
+			is well defined and admits an analytic extension to $\CC^c$. 
+		\end{theorem}
 
 	\end{frame}
+
+	\begin{frame}{Distance and paths}
+		Given any graph $G$, we define the following distance over its vertex-set:
+
+			\begin{equation*}d(x,y)= \min_{\substack{H \leq G\\ 
+					H \text{ connected }\\
+					x,y\in V(H)}} \big(|V(H)| - 1 \big), \, \, \text{ or } \infty \text{ if }
+				x,y \text{ are not connected.}
+			\end{equation*}
+
+		\begin{definition} 
+			A path between two vertices $x,y$ in a graph $G$ is
+			a connected subgraph $H\leq G$ containing both $x,y$ whose
+			number of vertices is minimum. 
+		\end{definition}
+
+	\end{frame}
+	\begin{frame}{Likelihood, trees, cycles and clusters} 
+		\begin{definition}
+			The likelihood $L(G)$ of a graph $G=(V,H_1,\dots,H_c)$ is
+			the number
+			\[ |V(G)| - \sum_{i=1}^c |H_i|(a_i-1).\]
+		\end{definition}
+	~\\
+	\end{frame}
+
+	\begin{frame}{Likelihood, trees, cycles and clusters} 
+	\begin{itemize}
+		\item A tree is a connected graph with likelihood $1$.
+		\vspace*{0.5 em}
+	\end{itemize}
+
+	\begin{center}
+		\includegraphics[width=0.7\linewidth]{Tree.pdf}
+	\end{center}
+	\end{frame}
+
+	\begin{frame}{Likelihood, trees, cycles and clusters} 
+		\begin{itemize}
+			\item An unicycle is a connected graph with likelihood $0$.
+			A cycle is a minimal unicycle.
+		\end{itemize}
+		\begin{center}
+			\includegraphics[width=0.9\linewidth]{Cycles.pdf}
+		\end{center}
+	\end{frame}
+
+	\begin{frame}{Likelihood, trees, cycles and clusters}
+		\begin{itemize}
+			\item A cluster is a graph $G$ with $L(G)\leq 0$ such 
+			that $L(H)>L(G)$\\ for any subgraph $H\leq G$.
+		\end{itemize}
+	\begin{center}
+		\includegraphics[width=0.4\linewidth]{Cluster.pdf}
+	\end{center}
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation over trees.}
+		A rooted $(T,x)$ is a tree $T$ together with a distinguished vertex
+		$x\in V(T)$.\par
+		\[Tree(y, T) = (T[X], y),\]
+		\[\text{where } \, X=\{ z\in V(T) \, | \, d(x,z)=d(x,y)+d(y,z)\}.\]~\\
+		The root of an edge $e\in H(T)$ in a rooted tree 
+		$(T,x)$ is the vertex $y\in e$ such that $d(x,y)=d(x,e)$.\\~\\
+		The radius of an edge $e\in H(T)$ is 
+		\[\max_{\substack{y\in e \\ y \text{ not the root of } e}} r(Tree(y,T)). \]
+
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation over trees.}
+		Fix $k\in \N$.\\
+		We define the $k$-morphism relation over rooted trees of the same radius
+		inductively as follows:
+
+		\begin{itemize}
+			\item If $r(T_1)=r(T_2)=0$ then $T_1\morph{k} T_2$.
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation over trees.}
+		For $r>0$:
+			\begin{itemize}
+				\item  First we
+				define the type of a en edge with radius less than $r$:
+
+			\end{itemize}
+		\begin{center}
+			\includegraphics[width=0.8\linewidth]{Edgetype.pdf}
+		\end{center}
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation over trees.}
+		\begin{itemize}
+		\item If $r(T_1)=r(T_2)=r$ we say that $T_1\morph{K}T_2$ if
+		for any edge $k$-type $E$ of radius less than $r$ either:
+		\begin{itemize}
+			\vspace{0.2 em}
+			\item the number of initial edges in $T_1$ and $T_2$ of $k$-type $E$ 
+			is the same, or
+			\vspace{0.2 em}
+			\item both $T_1$ and $T_2$ contain no less than $k+1$
+			initial edges of $k$-type $E$. 
+		\end{itemize}
+		\begin{center}
+			\includegraphics[width=0.7\linewidth]{Try.pdf}
+		\end{center}
+
+		\end{itemize}
+
+	\end{frame}
+
 \end{document}

### 2019-07-08 Presentacion/Presentación.tex
Mas dibus

@@
-\documentclass[handout, 11pt]{beamer}
+\documentclass[11pt]{beamer}
 
@@
 
-\author{L\'azaro Alberto Larrauri Borroto \\ 
-	Supervisor: Marc Noy Serrano}
+\author{L\'azaro Alberto Larrauri Borroto}
 
@@
 \begin{document}
-	\frame{\titlepage}
+\begin{frame}[plain]
+	\maketitle
+	\small
+	\begin{center}
+	Supervisor: Marc Noy Serrano
+	\end{center}
+
+\end{frame}
 	\frame{\tableofcontents}
@@
 
+	\begin{frame}{The $k$-morphism relation for graphs}
+		To make the definitions suitable for proofs using E.F. games we need to work with "graphs
+		with constants". 
+		\begin{definition}
+			The center of a connected graph $G(\clist)$ is its minimal 
+			connected subgraph containing all the constants and clusters.\\
+			\vspace{0.2 em} If $G(\clist)$
+			is not connected its center is the union of the centers of its connected
+			components.   
+		\end{definition}
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation for graphs}
+	A sketch of a center:
+	\begin{center}
+		\includegraphics[width=0.5\linewidth]{Center.pdf}
+	\end{center}
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation for graphs}
+	\begin{definition} 
+		We say that$G_1(\clist)\morph{k}G_2(\clist)$, if there is an isomorphism
+		$f:Center(G_1)\rightarrow Center(G_2)$ s.t.
+		\begin{itemize}
+			\item $f(c^1_i)=c^2_i$ for all constants, and
+			\item $Tree(x,G_1)\morph{k} Tree(f(x),G_2)$ for all $x\in V(Center(G_1))$.
+		\end{itemize}
+	\end{definition}
+
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation for graphs}
+	\begin{center}
+		\includegraphics[width=\linewidth]{kmorphiccenter1.pdf}
+	\end{center}
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation for graphs}
+	\begin{center}
+		\vspace{0.58 em}
+		\includegraphics[width=\linewidth]{kmorphiccenter2.pdf}
+	\end{center}
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation for graphs}
+	\begin{center}
+	\vspace{1.6em}
+	\includegraphics[width=\linewidth]{kmorphiccenter3.pdf}
+	\end{center}
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation for graphs}
+		Connected $k$-morphic graphs $G,H$ with $L(G),L(H)\leq 0$ have the same
+		first order rank $k$-type.	\\~\\
+
+		The tool for proving this are Ehrenfeucht Fraisse games.
+		\\~\\
+
+		The $k$-morphism relation gives, for any $r$, a finite classification of the cycles of diameter
+		at most $r$ with trees of radii at most $r$ hanging from their vertices.
+
+	\end{frame}
+
 \end{document}

### 2019-07-09 TFM.tex
Pictures
Terminamos

@@
 \usepackage{graphicx}
+%%BeginIpePreamble
 \usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}
+%%EndIpePreamble
 %\usepackage{color}
@@
 
-The original goal was to give generalizations for the case of uniform hypergraphs
-but the techniques used for that case also allowed for generalizations to 
+The original goal was to give a generalization for the case of uniform hypergraphs
+but the techniques used for that case also allowed for a generalization for 
 hypergraphs with multiple edge sets of different sizes.
@@
 random graph. Given the locality of first order logic up to a fixed 
-quantifier rank this is tells us that the only thing that the only way 
-to distinguish large random graphs in $G(n,\beta/n)$ 
+quantifier rank this is tells us that the only way 
+to distinguish large random graphs in $G(n,\beta/n)$ under first order logic
 (up to a fixed quantifier rank) 
@@
 under first order logic up to some quantifier rank $k$. This is done by giving
-a winning strategy for duplicator in the E.F. game of $k$ round played on 
+a winning strategy for duplicator in the Ehrenfeucht Fraisse game of $k$ rounds played on 
 $G_1$ and $G_2$.\par
 
-Finally it is shown that the numbers of uni-cycles of each type contained in
-a random graph are asymptotically distributed like independent Poisson variables 
+Finally it is shown that the quantities of uni-cycles of each type in a random graph
+are asymptotically distributed like independent Poisson variables 
 whose means are given by some other nested ``Poisson expressions" that correspond 
@@
 diagonal set $\{(a,a)\in [n]^2 \}$. \par
-Given a set $X$, then $S_n$ acts on $X^n$ in an evident way. That is, 
+Given a set $X$, then $S_n$ acts on $X^n$ in a natural way. That is, 
 given $g\in S_n$ and $(x_1, \dots, x_n)$ one can define
@@
 \begin{definition}
-	Let $n,a\in \N$, let $\Phi$ be a subgroup of $S_a$, and let
+	Let $n,a\in \N$, with $a\geq 2$, let $\Phi$ be a subgroup of $S_a$, and let
 	$A$ be a subset 
-	\[ A\subseteq [a]^2 \setminus \delta.\]
+	\[ A\subseteq [a]^2 \setminus \Delta_a.\]
 	The total edge set $\mathcal{H}_{(a,\Phi, A)}(n)$ of size $a$, 
 	symmetry group $\Phi$ and
-	restrictions $R$ on $n$ elements is the set:
-	\[  \mathcal{H}_{(a,\Phi, R)}(n)= ([n]^a/\Phi) \, \,
+	restrictions $A$ on $n$ elements is the set:
+	\[  \mathcal{H}_{(a,\Phi, A)}(n)= ([n]^a/\Phi) \, \,
 	\setminus \{\,  [x_1, \dots,x_a] \in [n]^a/\Phi  \, \, 
-	| \, \, x_i=x_j \, \text{for some } (i,j)\in R \} \]
+	| \, \, x_i=x_j \, \text{for some } (i,j)\in A \} \]
 \end{definition}
@@
 	sizes $a_1,\dots,a_c$, 
-	symmetry groups $\Phi_1,dots,\Phi_c$ 
+	symmetry groups $\Phi_1,\dots,\Phi_c$ 
 	and restrictions $A_1,\dots,A_c$, is the one that
@@
 
-For the rest of the work we will consider 
+For the rest of the work we will consider  fixed
 \begin{itemize}
@@
 	\item the symmetry group $\Phi_1,\dots, \Phi_c$ and,
-	\item the restrictions $A_1,\dots,A_l$
-\end{itemize}
-fixed. When we say ``graph'' from now on what
+	\item the restrictions $A_1,\dots,A_c$.
+\end{itemize}
+When we say ``graph'' from now on what
 we will mean is ``hiper-graph with edge colors 
@@
 symmetry groups $\Phi_1,\dots,\Phi_c$ and 
-restrictions $R_1,\dots,R_c$''. \par
+restrictions $A_1,\dots,A_c$''. \par
 
 Given a graph $G=([n], H_1,\dots, H_c)$ we will denote by
-$H_i(G)$ the edge set $H_i$, and by $V[G]$ the vertex set
+$H_i(G)$ the edge set $H_i$, and by $V(G)$ the vertex set
 $[n]$. Also, we will write $H(G)$ to denote the 
@@
 rather than ``tuples modulo the action of some permutation group''. 
-This way, expressions like $e_1\cup e_2$ for $e_1, e_2\in H(G)$
+This way, expressions like $e_1\cap e_2$ for $e_1, e_2\in H(G)$
 will make sense and mean 
@@
 Some other times we will treat edges $e\in H(G)$
-as sub-graphs of $G$ in the evident way. That is, the subgraph
+as sub-graphs of $G$ in the natural way. That is, the subgraph
 denoted by $e$ is the one whose vertex set is $e$-i.e., the vertices in $e$-
@@
 about the subgraph $\cup_{i=1}^l e_i$, which is the graph
-whose vertex set is the set of vertices belonging to the $e_i$'s, 
+whose vertex set is the set of vertices belonging to any of the $e_i$'s, 
 and whose edges are exactly the $e_i$'s. In spite of these
@@
 	\item Symmetry formulas:
-	\[ S_g: =\big( R_i(x_1\dots,x_{a_i})\iff R_i(x_{j_1}\dots,x_{j_{a_i}})\big) ,\]
-	where the the index $j_k$ is $g(k)$, and $g$ is an element from $\Phi_i$.
+	\[ S_g: =\big( R_i(x_1\dots,x_{a_i})\iff R_i(x_{g(1)}\dots,x_{g(a_i)})\big) ,\]
+	where $g$ is an element from $\Phi_i$.
 	\item Anti-reflexivity formulas:
-	\[A_{i,(j,l)}:=\big(R_i(x_1\dots,x_{a_i})\implies 
+	\[AR_{i,(j,l)}:=\big(R_i(x_1\dots,x_{a_i})\implies 
 	\neg(x_j= x_l)\big),\]
@@
 	The symbols $\beta_1,\dots, \beta_c$
-	denote positive real variables,
+	denote non-negative real variables,
 	but for the most part we will 
-	treat them as arbitrary positive real constants.
+	treat them as non-negative positive real constants.
 	\item The first order language we will always refer to is the one 
@@
 	product $\lambda_1\lambda_2$ belongs to $\Lambda$ as well.
-	\item For any $l,a,i\in \N$ with $1\leq i \leq c$,
-	$a > 0$, and $\lambda_1,\dots, \lambda_l\in \Lambda$,
-	the expression $\frac{\beta_i \prod_{j=1}^{l}\lambda_j}{a}$
+	\item For any $b,i\in \N$ with $1\leq i \leq c$,
+	$b > 0$, and $\lambda_1,\dots, \lambda_{a_i-1}\in \Lambda$,
+	the expression $\frac{\beta_i \prod_{j=1}^{a_i-1}\lambda_j}{b}$
 	belongs to $M$.		
@@
 We also define another families $\widehat{\Theta}$ and $\Theta$ of expressions with arguments
-$\beta_1,\dots, \beta_c$ as the minimal one satisfying:
-\begin{itemize}
-	\item For any $l,s,a\in \N$ with $a>0$ and any 
+$\beta_1,\dots, \beta_c$ as the minimal ones satisfying:
+\begin{itemize}
+	\item For any $l,s,b\in \N$ with $b>0$ and any 
 	non-necessarily-different $\lambda_1,\dots, \lambda_l\in \Lambda$,
@@
 	\[\frac{\left(\prod_{i=1}^{l} \lambda_i \right)
-		\left( \prod_{i=1}^{s}\alpha_i \right)}{a}\] 
+		\left( \prod_{i=1}^{s}\alpha_i \right)}{b}\] 
 	lies in $\widehat{\Theta}$.
-	\item For any $g\in \widehat{\Theta}$ and any $n\in \N$ both
-	$\mathrm{Poiss}_g(n)$ and $\mathrm{Poiss}_g(\geq n)$ are in $\Theta$.
+	\item For any $u\in \widehat{\Theta}$ and any $n\in \N$ both
+	$\mathrm{Poiss}_u(n)$ and $\mathrm{Poiss}_u(\geq n)$ are in $\Theta$.
 	\item For any $\theta_1, \theta_2\in \Theta$ the product
@@
 \end{itemize}
-
-For any first order sentence $\phi$
+\vspace{1 em}
+
+For any first order sentence $\varphi$
 we will use the notation 
-$\mathrm{Pr}_n(\phi):=\mathrm{Pr}(HG(n,p(n))\models \phi)$. \par
+\[\mathrm{Pr}_n(\varphi):=\mathrm{Pr}(HG(n,p(n))\models \varphi).\]
+\par
 
@@
 \begin{theorem}\label{thm:THEONE} 
-	Let $\beta=(\beta_1,\dots, \beta_c)$, and let $\psi$ be a 
+	Let $\beta=(\beta_1,\dots, \beta_c)$, and let $\varphi$ be a 
 	F.O sentence in $\mathcal{L}$. Then the function
 	\[
-	\mathfrak{F}(\beta):=\Ln \mathrm{Pr}(\, HG(n,p(\beta,n))\, \models \, \psi \,)
+	\mathfrak{F}(\beta):=\Ln \mathrm{Pr}(\, HG(n,p(\beta,n))\, \models \, \varphi \,)
 	\]
@@
 x,y\in V(H)}} |V(H)| - 1 .\]
-That is, the distance between $x$ and $y$ is the minimum size
-of a connected graph $H$ containing both. 
+That is, the distance between $x$ and $y$ is the minimum
+of a connected graph $H$ containing both, minus one. 
 If such graph does not exist we define $d(x,y)=\infty$.
@@
 \begin{definition} 
-	A path between $x$ and $y$ is a connected graph containing both 
-	$x$ and $y$	that is minimal among the ones with those properties. 
+	A path between $x$ and $y$ is minimal graph among the connected graphs
+	containing both $x$ and $y$. 
 \end{definition}
@@
 \begin{proof}[Sketch of the proof.]
-	Proceed by induction on the number of edges.
+	Order the edges of the path in a way that (1) $x$ belongs to the first and $y$ to the last, and
+	(2) each edge intersects the previous one and the next one. Such ordering exists because a path is connected.
+	If an edge intersects any other edge than its previous one or next one then we can remove some edge of the path,
+	contradicting the minimality condition.
 \end{proof}
@@
 \begin{definition}
-	The likelihood $L(G)$ of an hypergraph $G=(V,E_1,\dots,E_l)$ is
+	The likelihood $L(G)$ of an hypergraph $G=(V,H_1,\dots,H_c)$ is
 	the number
-	\[ \left( |V(G)| - \sum_{i=1}^l |H_i(G)|(a_i-1)\right).\]
+	\[ \left( |V(G)| - \sum_{i=1}^c |H_i|(a_i-1)\right).\]
 	An hypergraph is $L$-balanced if it contains no subgraph with
@@
 	\begin{proof}
-	\begin{proof}[Sketch of the proof.]
 		Suppose $G$ is non-empty.
@@
 		The subgraph $F$ obtained from cutting $e$ must be connected, so by the
-		induction hypothesis $F$ is balanced. 
+		induction hypothesis $F$ is L-balanced. 
 		The original graph $G$ was connected, 
@@
 		$F_2$ is a subgraph of $F$ and one can check
-		\[ L(F_2) - L_(G_2) \leq L(F)-L(G).\]
+		\[ L(F_2) - L(G_2) \leq L(F)-L(G).\]
 		In consequence, as $L(F)-L(F_2)$ is non-positive, 
 		so is $L(G)-L(G_2)$, arriving at a contradiction.
-	\end{proof}
 	\end{proof}
@@
 		\item[(2)] A path $P$, with $L(P)=1$
-		between two vertices $x$ and $y$, with
-		$L(P)=1$, together with an edge $e$ that intersects $P$ exactly
+		between two vertices $x$ and $y$, 
+		together with an edge $e$ that intersects $P$ exactly
 		in $x$ and $y$.
@@
 	``the $k$-type of $e$ in $T_1$'' when the ``ambient tree'' is clear
-	from context.   
+	from the context.   
 \end{remark}
 
-Let $T$ be a rooted tree of radius $r$, and let $E$ be a $k$-type of edges with radius less than $r$ for some $k\in \N$. We will denote by $\langle T,E \rangle$
+Let $T$ be a rooted tree of radius $r$, and let $E$ be a $k$-type 
+of edges with radius less than $r$ for some $k\in \N$. We will denote by $\langle T,E \rangle$
 the number of initial edges in $T$ of $k$-type $E$. \par
@@
 		$e_1$ and $e_2$ have the same color $l$ and we can write
-		$e_1=[x_1,\dots,x_{c_l}]$,
-		$e_2=[y_1,\dots,y_{c_l}]$ for some vertices such that for all
+		$e_1=[x_1,\dots,x_{a_l}]$,
+		$e_2=[y_1,\dots,y_{a_l}]$ for some vertices such that for all
 		$i=1,\dots, a_l$, either 
@@
 		Thus, for any $j$-type of edges $E$ there are 
-		$k$-types of edges $E_1, \dots, E_m$ such that for all rooted trees $T$
+		$k$-types of edges $E_1, \dots, E_m$ such that for all rooted trees $T$ of radius $r$
 		\[ \langle T,E\rangle = \sum_{i=1}^{m} \langle T,E_i \rangle .\]
@@
 		\item If they have at most radius $0$ the statement is vacuously true. 
-		\item Suppose now that they have radii at most $s$. Let $e_1$ be an edge with root
+		\item Suppose now that they have radius $s$. Let $e_1$ be an edge with root
 		$x$ in $N(x;r)$ and $e_2$ be an edge of root $y$ in $N(y;r)$ such that $e_1 \morph{k} e_2$
@@
 		radius less than $r$ there are $k$-types of edges classes 
-		$E_1,\dots,E_l$ of rooted edges such
-		of trees with radii at most $s$ such that
+		$E_1,\dots,E_l$ of rooted edges such that for all trees $(T_1,x)$,$(T_2,y)$ 
+		with radius $s$:
 		\[ \langle N(x;r),E \rangle =  \sum_{i=1}^{l}\langle T_1, E_i\rangle ,\]
@@
 		$P(w^\prime)\cup e^\prime$
-		in the evident way. 
+		in the natural way. 
 	\end{itemize}
@@
 		\cref{lem:minusedge}
-		\[Tree(w_1,F^\prime_1)\morph{k-1}Tree(g(w_1),F^\prime_2)\].	
+		\[Tree(w_1,F^\prime_1)\morph{k-1}Tree(g(w_1),F^\prime_2).\]
 	\end{itemize}
@@
 	\end{itemize} 
-\end{definition}
-
-\begin{definition} 
-	Two graphs with constants $G_1$ and $G_2$ are $k$-agreeable if for each $k$-morphism 
-	equivalence class $C$ they either have the same number of connected components of type
-	$C$ or they both have no less than $k+1$ components of type $C$. 
 \end{definition}
@@
 		\item The $N(x_l;r)$'s do not intersect $Core(G,r)$
-		\item $N(x_l;r)(x_l) \morph{k} T$.		
+		\item $(N(x_l;r),x_l) \morph{k} T$.		
 	\end{itemize} 
@@
 
-For reference about E.F. games see \cite{finitemodeltheory1} and \cite{finitemodeltheory2}.
+For reference about Ehrenfeucht Fraisse games see \cite{finitemodeltheory1} and \cite{finitemodeltheory2}.
 
@@
 	Let $G_1, G_2$ be $(k,k,3^k)$-rich graphs such that $Core(G_1;3^k)$ is $k$-agreeable
-	with $Core(G_2;3^k)$. Ten $G_1$ and $G_2$ have the same rank $k$ type.
+	with $Core(G_2;3^k)$. Then $G_1$ and $G_2$ have the same rank $k$ type.
 \end{theorem}
@@
 	\[Core(G_1(\cc_1[x_1],\dots,\cc_i[x_i]);3^{k-i}) \]
-	is $k-i$-agreeable with  
+	is $(k-i)$-agreeable with  
 	\[ Core(G_2(\cc_1[y_1],\dots,\cc_i[y_i]);3^{k-i}), \]
@@
 	follows because
-	$Core(G_1(\cc_1[x_1],\dots,c_i[x_k]);1)$ being $0$-agreeable with
+	$Core(G_1(\cc_1[x_1],\dots,c_i[x_k]);1)$ being $0$-agreeable with\\
 	$Core(G_2(\cc_1[y_1],\dots,c_i[y_k]);1)$ implies that
@@
 			one can check that now $Core(G_1(\cc_1[x_1],\dots,\cc_i[x_i]);3^{k-i})$
-			is $k-i$-agreeable with  $Core(G_2(\cc_1[y_1],\dots,\cc_i[y_i]);3^{k-i})$.
+			is $(k-i)$-agreeable with  $Core(G_2(\cc_1[y_1],\dots,\cc_i[y_i]);3^{k-i})$.
 			\par
@@
 		the last removed edge and
-		$e\cap G^\prime=\{ x_{i_1}, \dots, x_{i_c}\}$.
-		For any $j=1,\dots, c$ choose 
+		$e\cap G^\prime=\{ x_{i_1}, \dots, x_{i_d}\}$.
+		For any $j=1,\dots, d$ choose 
 		$P_j$ a path of size no greater than $r+1$ joining
 		$x$ and $x_{i_j}$ in $G^\prime$.   
-		Then $P_1\cup \dots P_c \cup e$ is a critical subgraph of $G$
+		Then $P_1\cup \dots P_d \cup e$ is a critical subgraph of $G$
 		of size less than $a(r+1) + a< (a+2)(r+1) + 2a$.
@@
 		$e_2=[y_1, \dots, y_{b_1}]$ be the last removed edge.
-		As before, let $e_1\cap G^\prime=\{ x_{i_1}, \dots, x_{i_c}\}$
-		and for $j=1,\dots, c$ let $P_j$ a path of size no greater than $r+1$ 
+		As before, let $e_1\cap G^\prime=\{ x_{i_1}, \dots, x_{i_d}\}$
+		and for $j=1,\dots, d$ let $P_j$ a path of size no greater than $r+1$ 
 		joining	$x$ and $x_{i_j}$ in $G^\prime$
@@
 		and size less than $2r+2 + a$,
-		and $Q_1\cup Q_2\cup P_1 \cup \dots \cup P_c \cup e_1 \cup e_2$ 
+		and $Q_1\cup Q_2\cup P_1 \cup \dots \cup P_d \cup e_1 \cup e_2$ 
 		is a critical graph	with size less than $(2+a)(r+1) + 2a$	
@@
 with free variables $x_1,\dots, x_l$
-satisfying $G\models \phi_r(x_1,\dots, x_l)$ 
+that is satisfied
 if for any $y$ there is a unique
@@
 \begin{lemma} \label{lem:faraway}
-	Let $\sigma$ be an open formula (i.e., a formula with no quantifiers)
+	Let $\sigma$ be a consistent open formula (i.e., a formula with no quantifiers)
 	with free variables $x_1, \dots, x_l$. Then, for any $r\in \N$
@@
 	union bound:
-	\[ \mathrm{Pr}_n(\neq \phi_r)\leq  \mathrm{Pr}_n(B)+ \mathrm{Pr}_n(A) 
+	\[ \mathrm{Pr}_n(\neg \phi_r)\leq  \mathrm{Pr}_n(B)+ \mathrm{Pr}_n(A) 
 	\stackrel{n\to \infty}{\longrightarrow}	0.\]
@@
 	is a sum of random indicator variables (i.e. variables 
-	taking only values $0$ and $1$)
-	$Y_{i,1}(n),\dots, Y_{i,s_n}(n)$. Let $\lambda_1, \dots ,
+	taking only values $0$ and $1$).\\Let $\lambda_1, \dots ,
 	\lambda_r$ be real numbers. If for each 
-	$r$-tuple of natural numbers $a_1,\dots, a_r$
+	$r$-tuple of natural numbers $b_1,\dots, b_r$
 	is satisfied
-	\[ \Ln E\left[\prod_{i=1}^r \binom{X_i}{a_i} \right] = 
-	\prod_{i=1}^r \frac{\lambda_i^{a_i}}{a_i!}, \]
+	\[ \Ln E\left[\prod_{i=1}^r \binom{X_i}{b_i} \right] = 
+	\prod_{i=1}^r \frac{\lambda_i^{b_i}}{b_i!}, \]
 	then the random variable$(X_1,\dots ,X_r)$ converges in distribution
@@
 Let $x_1, \dots, x_l$ be vertices of a random graph $G$.
-For each $y\in V(G)$ we abbreviate by $T_r(y; x,1_,\dots, x_l)$
+For each $y\in V(G)$ we abbreviate by $T_r(y; x_1,\dots, x_l)$
 the rooted tree 
@@
     For all $r\in N$ and any $k$-morphism class of trees with radius
-	at most $r$ there exist expressions $\lambda_{k,C,r}\in \Lambda$ 
+	at most $r$ there exist expressions $\lambda(k,C,r)\in \Lambda$ 
 	such that:
@@
 	\[ \Ln \mathrm{Pr}_n(\bigwedge_{i=1}^s Tree_r(x_i; x_1, \dots, x_l)\in C_i \, | 
-	\, \sigma(x_1,\dots, x_l) \,)= \prod_ {i=1}^s \lambda_{k,C_i,r}.\]	
+	\, \sigma(x_1,\dots, x_l) \,)= \prod_ {i=1}^s \lambda(k,C_i,r).\]	
 \end{theorem}
@@
 	Thus, taking $C$ the $k$-morphism class of the isolated
-	vertex, one can define $\lambda_{k,C,0}=1$. 
+	vertex, one can define $\lambda(k,C,0)=1$. 
 	\item Fix $r>0$ and assume that the statement
@@
 	pick a representative
-	$( C_{E,1}, \dots, C_{E,j-1}, r, C_{E,j}\dots, C_{E,a_E-1})$, 
+	$( C_{E,1}, \dots, C_{E,j-1}, r, C_{(E,j)}\dots, C_{E,a_E-1})$, 
 	and denote by $j_E$ the index of the root in that representative. 
@@
 
-	Let $(b_{i,E})_{\substack{i=1,\dots, s \\ E\in \mathcal{E}}}$ be 
+	Let $(b_{(i,E})_{\substack{i=1,\dots, s \\ E\in \mathcal{E}}}$ be 
 	natural numbers. We want to compute
 	\[\Ln E\left[\prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
-	\binom{X_{i,E}(n)}{b_{i,E}} \, \Bigg| \, \sigma \right]. \]
+	\binom{X_{i,E}(n)}{b_{(i,E}} \, \Bigg| \, \sigma \right]. \]
 	Define by $\Omega$ the set
@@
 		&\Omega:= \{ (i,E,b,j) \, | \, i,b,j \in \N, \, E\in \mathcal{E},\\ 
-		& 1\leq i \leq s, \, b=1\leq b \leq b_{i,E}, \, 1\leq j \leq a_E-1 \,\}. 
+		& 1\leq i \leq s, \, b=1\leq b \leq b_{(i,E}, \, 1\leq j \leq a_E-1 \,\}. 
 	\end{align*} 
@@
 	&\widehat{\Omega}:= \{ (i,E,b) \, | \, i,b \in \N, \, E\in \mathcal{E},\\ 
-	& 1\leq i \leq s, \, b=1\leq b \leq b_{i,E}\,\}. 
+	& 1\leq i \leq s, \, b=1\leq b \leq b_{(i,E}\,\}. 
 	\end{align*}
@@
 	$1\leq i\leq s$, $E\in \mathcal{E}$ and 
-	$1\leq b_1 < b_2\leq b_{i,E}$, and $t=1,2$, the tuples
+	$1\leq b_1 < b_2\leq b_{(i,E}$, and $t=1,2$, the tuples
 	\[ [y(i,E,b_t,1),\dots, y(i,E,b_t,j_E-1), x_i, y(i,E,b_t,j_E),\dots
@@
 	\[\bigwedge_{(i,E,b,j)\in \Omega} T_{(r-a_E+1)}(y(i,E,b,j);x_1
-	\dots,x_l)\in C_{E,j}.\]
+	\dots,x_l)\in C_{(E,j)}.\]
 	That is, 
@@
 		& E\left[\prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
-		\binom{X_{i,E}}{b_{i,E}} \, \bigg|\, \sigma \right]= \\
+		\binom{X_{i,E}}{b_{(i,E}} \, \bigg|\, \sigma \right]= \\
 		&=\prod_{i=1}^{s}
-		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) \cdot
+		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{(i,E}} \cdot b_{(i,E})}\right) \cdot
 		\sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ 
@@
 		& \prod_{i=1}^{s}
-		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) \cdot
+		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{(i,E}} \cdot b_{(i,E)}}\right) \cdot
 		\sum_{\substack{y:\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 
@@
 		\prod_{i=1}^{s}
-		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) \cdot
+		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{(i,E}} \cdot b_{(i,E)}}\right) \cdot
 		\mathrm{Pr}( T(z) \, \wedge \, A(z) \wedge \, B(z) \, | \, \sigma \, )
@@
  	\Gamma:=\prod_{\substack{1\leq i \leq s \\ E\in \mathcal{E}\\
- 	1\leq j \leq a_E - 1 }} (\lambda_{k,C_{E,j}})^{b_{i,E}}.
+ 	1\leq j \leq a_E - 1 }} (\lambda(k,C_{(E,j)},r-a(E)+1))^{b_{(i,E)}},
  	\end{equation}
+ 	where $a(E)$ is the size of $E$.
  	In particular $\Gamma$ is different from $0$.
@@
  	\Ln	\prod_{i=1}^{s}
- 		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{i,E}} \cdot b_{i,E}!}\right) 
+ 		\prod_{E\in \mathcal{E}} \left(\frac{1}{|\psi_E|^{b_{(i,E}} \cdot b_{(i,E)}}\right) 
  		\cdot \Gamma \cdot
@@
  	\prod_{E\in \mathcal{E}} \left(\frac{\beta_{c_E}}{n^{(a_E -1)}}
- 	\right)^{b_{i,E}},  \]
+ 	\right)^{b_{(i,E}},  \]
  	and using that
  	\[  n^{|\Omega|}= \prod_{i=1}^{s} 
- 	\prod_{E\in \mathcal{E}} (n^{(a_E-1)})^{b_{i,E}}  \]
+ 	\prod_{E\in \mathcal{E}} (n^{(a_E-1)})^{b_{(i,E)}}  \]
  	and \cref{eqn:sumones} we obtain 
@@
  	\Omega \rightarrow [n]\setminus X\\ y \text{ injective}}} 1 \simeq 	
- 	\prod_{E\in \mathcal{E}} \beta_{c_E}^{b_{i,E}}. 
+ 	\prod_{E\in \mathcal{E}} \beta_{c_E}^{b_{(i,E}}. 
  	\end{equation}
@@
  	\[ \Ln E\left[\prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
- 	\binom{X_{i,E}}{b_{i,E}} \, \Bigg| \, \sigma \right]= \prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
- 	\left[ 	\left(\frac{\beta_{c_E} \prod_{j=1}^{a_E -1} \lambda_{k,C_{E,j}} }{|\psi_E|}\right)^{b_{i,E}} \frac{1}{b_{i,E}!} \right]. \]
+ 	\binom{X_{i,E}}{b_{(i,E}} \, \Bigg| \, \sigma \right]= \prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
+ 	\left[ 	\left(\frac{\beta_{c_E} \prod_{j=1}^{a_E -1} \lambda(k,C_{(E,j)},r-a(E)+1)}{|\psi_E|}\right)^{b_{(i,E}} \frac{1}{b_{(i,E})} \right]. \]
  	And using the multivariate Brun's Sieve we get that for each
- 	choice of natural numbers $\{b_{i,E}\}_{\substack{1\leq i \leq s\\ 
+ 	choice of natural numbers $\{b_{(i,E}\}_{\substack{1\leq i \leq s\\ 
  	E\in \mathcal{E}}}$ it is satisfied
- 	\[ \Ln \mathrm{Pr}_n\left(\bigwedge_{i=0}^{s}\bigwedge_{E\in \mathcal{E}} X_{i,E}=b_{i,E} \, \Bigg| \, \sigma \right) = 
+ 	\[ \Ln \mathrm{Pr}_n\left(\bigwedge_{i=0}^{s}\bigwedge_{E\in \mathcal{E}} X_{i,E}=b_{(i,E)} \, \Bigg| \, \sigma \right) = 
  	\prod_{i=0}^{s}\prod_{E\in \mathcal{E}}
- 	\mathrm{Poiss}_{\mu_{E,(r-a_E+1)}}(b_{i,E}),\]
+ 	\mathrm{Poiss}_{\mu(k,E,r-a_E+1)}(b_{(i,E}),\]
  	where we define
- 	\[\mu_{E,(r-a_E+1)}=
- 	\frac{\beta_{c_E} \prod_{j=1}^{a_E -1} \lambda_{k,C_{(E,j)},(r-a_E+1)} }{|\psi_E|}.\]
- 	Notice that $\mu_{E,(r-a_E+1)}$ is an expression in $M$.
+ 	\[\mu(k,E,r-a_E+1)=
+ 	\frac{\beta_{c_E} \prod_{j=1}^{a_E -1} \lambda(k,C_{(E,j)},r-a(E)+1) }{|\psi_E|}.\]
+ 	Notice that $\mu(k,E,r-a_E+1)$ is an expression in $M$.
  	The $k$-morphism class of $\\T_r(x_j;x_1, \dots, x_l)$ depends exclusively
@@
  	& \bigwedge_{E\in \mathcal{E}}
- 	\big(X_{j, E}= (C,E) \text{  if  } (C,E)\leq k \big),
+ 	\big(X_{j, E}= \langle C, E \rangle \text{  if  } \langle C, E \rangle\leq k \big),
  	\text{  or  }  \big(X_{j, E}\geq k+1 \text{ otherwise}\big). 
@@
  	&=\prod_{i=0}^{s}\left[
- 	\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)<k+1}} \mathrm{Poiss}_{\mu_{E,(r-a_E+1)}}((C_i,E))\right)
- 	\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)\geq k+1}} 
- 	\mathrm{Poiss}_{\mu_{E,(r-a_E+1)}}(\geq (k+1))\right)\right]=\\
- 	&=\prod_{i=0}^{s} \lambda_{k,C_i,r},
+ 	\left(\prod_{\substack{E\in \mathcal{E}\\ \langle C_i, E \rangle <k+1}} \mathrm{Poiss}_{\mu(k,E,r-a_E+1)}(\langle C_i, E \rangle )\right)
+ 	\left(\prod_{\substack{E\in \mathcal{E}\\ \langle C_i, E \rangle \geq k+1}} 
+ 	\mathrm{Poiss}_{\mu(k,E,r-a_E+1)}(\geq (k+1))\right)\right]=\\
+ 	&=\prod_{i=0}^{s} \lambda(k,C_i,r),
     \end{align*}
@@
     \[
-    \lambda{C_i,r}=\left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)<k+1}} \mathrm{Poiss}_{\mu_{E,(r-a_E+1)}}((C_i,E))\right)
-    \left(\prod_{\substack{E\in \mathcal{E}\\ (C_i,E)\geq k+1}} 
-    \mathrm{Poiss}_{\mu_{E,(r-a_E+1)}}(\geq (k+1))\right)
+    \lambda(k,C_i,r)=\left(\prod_{\substack{E\in \mathcal{E}\\ \langle C_i, E \rangle <k+1}} \mathrm{Poiss}_{\mu(k,E,r-a_E+1)}(\langle C_i, E \rangle )\right)
+    \left(\prod_{\substack{E\in \mathcal{E}\\ \langle C_i, E \rangle \geq k+1}} 
+    \mathrm{Poiss}_{\mu(k,E,r-a_E+1)}(\geq (k+1))\right)
     .\]
-    Notice that $\lambda{C_i,r}$ belongs to $\Lambda$, and its
+    Notice that $\lambda(k,C_i,r)$ belongs to $\Lambda$, and its
     definition depends only
@@
 
-%	\sum_{E\in \mathcal{E}} b_{i,E}\cdot(a_{E}-1)}
+%	\sum_{E\in \mathcal{E}} b_{(i,E}\cdot(a_{E}-1)}
 
@@
 %   \wedge \, \sigma \, \wedge \, B(z) \, )
-%   \prod_{E\in\mathcal{E}}\bigg(\frac{\beta_{c_E}}{n^{a_E-1}}\bigg)^{b_{i,E}}
+%   \prod_{E\in\mathcal{E}}\bigg(\frac{\beta_{c_E}}{n^{a_E-1}}\bigg)^{b_{(i,E}}
 %   \end{align*}
@@
 	\end{equation}
-	But also, because of lemma LEMM
+	But also, because of \cref{lem:faraway}
 	\begin{equation} \label{eqn:richaas}
@@
 	Because of last theorem $X_{s,C}$ converges in distribution
-	to a binomial variable whose defining probability is $\lambda_{k,C,r}$. 
+	to a binomial variable whose defining probability is $\lambda(k,C,r)$. 
 	Notice that the event $A_{s,C}$ is precisely the event
@@
 	&=\Ln 1- \sum_{C\in\mathcal{C}} \mathrm{Pr}_n(X_{s,C}<i)=
-	1- \sum_{j<i} \binom{s}{j}\lambda_{k,C,r}^j(1-\lambda_{k,C,r})^{(s-j)}.
+	1- \sum_{j<i} \binom{s}{j}\lambda(k,C,r)^j(1-\lambda(k,C,r))^{(s-j)}.
 	\end{align*}
 	This expression goes to $1$ as $s$ goes to infinity because
-	$\lambda_{k,C,r}$ is positive. This means 
+	$\lambda(k,C,r)$ is positive. This means 
 	\[ \lim\limits_{s\to \infty} \Ln \mathrm{Pr}_n\Bigg( 
@@
 	and let  $cycle(U)$ be the cycle in $rep(U)$, whose number of vertex will be
-	denoted by $n_U$. Choose an ordering $x_{U,1},\dots, x_{U,n_U}$
+	denoted by $n_U$. Choose an ordering $x_{(U,1)},\dots, x_{(U,n_U)}$
 	of the vertices in $cycle(U)$ and for each $1\leq i \leq n_{U}$ 
-	denote by $C_{U,i}$ the $k$-morphism class
+	denote by $C_{(U,i)}$ the $k$-morphism class
 	of $Tree(x_i,rep(U))$. One can consider $cycle(U)$ to be a 
 	vertex colored graph where the color assigned to each vertex $x_i$
-    is $C_{U,i}$. Isomorphisms of the colored cycle 
+    is $C_{(U,i)}$. Isomorphisms of the colored cycle 
 	$cycle(U)$ induce permutations of $[n_U]$ via this ordering. 
@@
 		$x_1,\dots, x_{n_U}$ such that the map $f:G[X]\rightarrow cycle(U)$ 
-		,where $X=\{x_1,\dots x_{n_U}\}$, defined by $x_i\mapsto x_{U,i}$ is an
+		,where $X=\{x_1,\dots x_{n_U}\}$, defined by $x_i\mapsto x_{(U,i)}$ is an
 		isomorphism. 
@@
 		\item $N(X;r)\morph{k} rep(U)$ via $f$. In particular this means
-		that $Tree(x_i, G)$ belongs to $C_{U,i}$.
+		that $Tree(x_i, G)$ belongs to $C_{(U,i)}$.
 	\end{itemize}	
@@
 		the map $f_{U,b}:cycle(U)\rightarrow G[Y(U,b)]$ given
-		by $x_{U,i} \rightarrow y(U,b,i)$ is an embedding. 	
+		by $x_{(U,i)} \rightarrow y(U,b,i)$ is an embedding. 	
 		\item Let $B(y)$ be the event that $Center(N(Y(U,b);r)$ is 
@@
 		\item Let $T(y)$ be the event that 
-		\[\bigwedge_{(U,b,i)\in \Omega} T_r(y(U,b,i); Y)\in C_{U,i}, \]
+		\[\bigwedge_{(U,b,i)\in \Omega} T_r(y(U,b,i); Y)\in C_{(U,i)}, \]
 		where $Y$ denotes set of vertices in the image of $y$.  
@@
 	In consequence the following chain of inequalities holds
-	\[\mathrm{Pr}(T(z)\,|\, B(z))\geq \mathrm{Pr}(T(z)\wedge A(z) \,| \, B(z)) \geq
-	 \mathrm{Pr}(T(z)\wedge \tau_r \,| \, B(z)).\]
-	Notice that $B(z)$ can be expressed as a purely relational open formula
+	\[\mathrm{Pr}(T(z)\,|\, A(z))\geq \mathrm{Pr}(T(z)\wedge B(z) \,| \, A(z)) \geq
+	 \mathrm{Pr}(T(z)\wedge \tau_r \,| \, A(z)).\]
+	Notice that $A(z)$ can be expressed as a purely relational open formula
 	with free variables the elements indexed by $z$, because it only depends on
 	the edges between vertices in the image of $z$.
-	Using the previous theorem and \cref{thm:simple} we obtain
-	\[\Ln \mathrm{Pr}_n(T(z)\wedge \tau_r \,| \, B(z))= \Ln \mathrm{Pr}_n(T(z)| \,| \, B(z)) = \Gamma, \]
+	Using \cref{thm:probtrees} and \cref{thm:simple} we obtain
+	\begin{equation}\label{eq:ref1}
+		\Ln \mathrm{Pr}_n(T(z)\wedge \tau_r \,| \, A(z))= \Ln \mathrm{Pr}_n(T(z) \,| \, A(z)) = \Gamma, 
+	\end{equation}
 	where
 	\[ \Gamma:=\prod_{\substack{U\in \mathcal{U}\\ 1 \leq i\leq n_{U}}}
-	(\lambda_{k,C_{(U,i)}, r})^{b_U}.\]
+	(\lambda(k,C_{(U,i)}, r))^{b_U}.\]
 
 	Because the probability of each edge is independent, one obtains 
-	\[ \mathrm{Pr}_n(B(z))= \prod_{(U,b)\in \widehat{\Omega}} 
-	\frac{\prod_{i=1}^c	\beta_i^{|H_i(cycle(U))|}}{n^{n_U}}.  \]
+	\begin{equation}\label{eq:ref2}
+	 \mathrm{Pr}_n(A(z))= \prod_{(U,b)\in \widehat{\Omega}} 
+	\frac{\prod_{i=1}^c	\beta_i^{|H_i(cycle(U))|}}{n^{n_U}}.  
+	\end{equation}
 	Also,
-	\[\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ injective }}}1
-	\simeq \prod_{(U,b)\in \widehat{\Omega}} n^{n_U}. \]
-	This way substituting REF, REF and REF in EQ we get
+	\begin{equation}\label{eq:ref3}
+	\sum_{\substack{y:\Omega \rightarrow [n]\\y \text{ injective }}}1
+	\simeq \prod_{(U,b)\in \widehat{\Omega}} n^{n_U}. 
+	\end{equation}
+	This way substituting \cref{eq:ref1}, \cref{eq:ref2} and \cref{eq:ref3} in \cref{eqn:distributed3} we get
 	\[\Ln E\left[\prod_{U\in \mathcal{U}}
@@
 	if $O$ is a $k$-agreeability class of radius $r$, 
-	\[Core(G;r)\in O \iff \bigwedge_{U\in \mathcal{U}} (X_U=(O,U) \text{ if }(O,U)\leq k), \text{ or }  (X_U\geq k+1 \text{ otherwise}).\]
+	\[Core(G;r)\in O \iff \bigwedge_{U\in \mathcal{U}} (X_U=\langle O,U \rangle \text{ if }\langle O,U \rangle\leq k), \text{ or }  (X_U\geq k+1 \text{ otherwise}).\]
 	In consequence,
-	\[ \Ln \mathrm{Pr}_n(Core(G;r)\in O) = \left(\prod_{\substack{U\in \mathcal{U}\\(O,U)\leq k}} \mathrm{Poiss}_{\xi_U}((O,U)) \right) \left(\prod_{\substack{U\in \mathcal{U}\\(O,U)\geq k+1}}
+	\[ \Ln \mathrm{Pr}_n(Core(G;r)\in O) = \left(\prod_{\substack{U\in \mathcal{U}\\\langle O,U \rangle\leq k}} \mathrm{Poiss}_{\xi_U}(\langle O,U \rangle) \right) \left(\prod_{\substack{U\in \mathcal{U}\\\langle O,U \rangle\geq k+1}}
 	\mathrm{Poiss}_{\xi_U}(\geq (k+1)) \right),\]
@@
 	let $O_1,\dots,O_m$ be an enumeration of all $k$-agreeability
-	simple classes of radius at most $3^k$. Because of \cref{thm:simple},
+	simple classes whose components are cycles of diameter at most $3^k$ with trees of radii at most $3^k$ hanging from them.
+	Because of \cref{thm:simple},
 	\cref{thm:rich} and \cref{thm:probcycles} respectively we have:
@@
 \end{proof}
-
+\pagebreak
 \bibliography{biblio}

### 2019-10-10 Article.tex
Empiezo Articulo

\documentclass[11pt,notitlepage,a4paper]{article}

\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry}
\usepackage{graphicx}
\usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}
%\usepackage{color}
\usepackage{float}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{chngcntr}
\usepackage{cleveref}
\usepackage{pdfpages}

\counterwithout{equation}{section}

\newlength{\margen}
\setlength{\margen}{\paperwidth}
\addtolength{\margen}{-\textwidth}
\addtolength{\skip\footins}{0.7 cm}
\setlength{\margen}{0.5\margen}
\addtolength{\margen}{-1in}
\setlength{\oddsidemargin}{\margen}
\setlength{\evensidemargin}{\margen}
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{3pt}
%%%% Small setup %%%%
\hypersetup{
	colorlinks=false,
	pdfborder={1 1 0.0005},
}
\setlength{\parskip}{0.2cm}
%%%%%%%%%%%%%%%
\usepackage{tikz-cd}
\usetikzlibrary{cd}
\usepackage[english]{babel}
\usepackage{todonotes}
\usepackage{cleveref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{bbding}
\usepackage{tcolorbox}
\usepackage{natbib}

\newtheorem{proposition}{Proposition}[section]
\newtheorem{fact}{Fact}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{propdef}{Proposition / Definition}[section]
\newtheorem{remark}{Remark}[section]

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\stackrel{#1}{\simeq}}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}

\begin{document}
\begin{abstract}
	We consider a finite relational vocabulary $\sigma$ with
    a first order theory $T$ written in $\sigma$ 
    composed of symmetry and 
    anti-reflexivity axioms. We define a binomial random model of finite 
    $\sigma$-structures that satisfy $T$ and show that first order properties have well defined asymptotic probabilities in the sparse 
    case. It is also shown that those limit probabilities are well-behaved with
    respect to some parameters that represent edge densities. 
    An application of these results to the problem of random Boolean 
    satisfability is presented afterwards. 
    We show that there is no first order property of $k$-CNF formulas
    that implies unsatisfability and holds for almost all typical 
    unsatisfable formulas when the number of clauses is linear.

\end{abstract}
\clearpage

\section*{Introduction}
.
.
.
.

\setcounter{section}{-1}

\section{Preliminaries}

A (relational) vocabulary $\sigma$ is a collection of
relation symbols $(R_1,\dots, R_m,\dots)$
where each relation symbol has associated a natural number called its arity.
.\par

A ($\sigma$-)structure $\mathfrak{A}$ is composed of (1)
a set $A$, called the universe of $\mathfrak{A}$, and sets of tuples 
$R_i^{\mathfrak{A}}\subseteq A^{a_i}$ for all relation symbols 
$R_i$ in $\sigma$, where $a_i$ is the arity of $R_i$.  
A structure is called finite if its universe is a finite set.

The first order language with signature $\sigma$ deals with strings
of symbols taken from the alphabet consisting of
 variable symbols $x_1,\dots,x_m,\dots$, the symbols in $\sigma$,
the logical connectives $\neg, \wedge, \vee$,
the universal $\forall$ and existential $\exists$ quantifiers,
the equality symbol, and the parentheses $),($.
A first order formula is a string obtained after applying the
following set of rules a finite number of times: 
\begin{enumerate}[label=(\Roman*),itemsep=0pt, topsep=0pt]
	\item If $x_1,x_2$ are variables then $x_1=x_2$ is a formula.
	\item If $R_i$ is a relation symbol in $\sigma$ with arity $a_i$,
	and $t_1,\dots, t_{a_i}$ are terms then 
	$R_i(t_1,\dots,t_{a_i})$ is a formula.
	\item If $\varphi$ and $\psi$ are formulas, then both
	$(\varphi \wedge \psi)$ and $(\varphi \vee \psi)$ are formulas.
	\item If $\varphi$ is a formula then $\neq \varphi$ is also 
	a formula.
	\item If $\varphi$ is a formula and $x$ is a variable then both
	$\forall x \varphi$ and $\exists x\varphi$ are formulas. 
\end{enumerate}

Let $\varphi$ be a first order formula. An occurrence of a variable 
in $\varphi$ is called bounded if it is within the scope of
a quantifier binding it, and is called free otherwise. We
will assume that the occurrences of any given variable in a first
order sentence are either all free or all bounded. 
We will use the notation $\varphi(x_1,\dots, x_n)$ to indicate
that $x_1, \dots, x_n$ are distinct and they are the free variables
(i.e. the variables whose occurrences are all free) 
in $\varphi$. A formula with no free variables is called a sentence,
and a formula whose variables are all free is called open.

Let $\mathfrak{A}$ be a $\sigma$-structure and $\varphi(x_1,\dots,x_n)$ 
be a first order sentence. Given a map $\alpha$ from the set
of free variables $\{x_1,\dots,x_n\}$ to the universe $A$ 
of $\mathfrak{A}$ we define the relation 
$\mathfrak{A} \models \varphi[\alpha]$, "$\alpha$ satisfies $\phi$ in $\mathfrak{A}$",
in the following way:
\begin{enumerate}[label=(\Roman*),itemsep=0pt, topsep=0pt]
	\item 
	\item If $R_i$ is a relation symbol in $\sigma$ with arity $a_i$,
	and $t_1,\dots, t_{a_i}$ are terms then 
	$R_i(t_1,\dots,t_{a_i})$ is a formula.
	\item If $\varphi$ and $\psi$ are formulas, then both
	$(\varphi \wedge \psi)$ and $(\varphi \vee \psi)$ are formulas.
	\item If $\varphi$ is a formula then $\neq \varphi$ is also 
	a formula.
	\item If $\varphi$ is a formula and $x$ is a variable then both
	$\forall x \varphi$ and $\exists x\varphi$ are formulas. 
\end{enumerate}

%
%\section{Random relational structures}
%
%Given a natural number $n$, we will use the notation
%$[n]:= \{1,\dots, n\}$. We will denote by $S_n$
%the symmetric group on $[n]$, and by $\Delta_n$ the 
%diagonal set $\{(a,a)\in [n]^2 \}$. \par
%Given a set $X$, then $S_n$ acts on $X^n$ in an evident way. That is, 
%given $g\in S_n$ and $(x_1, \dots, x_n)$ one can define
%\[ g \cdot (x_1,\dots,x_n) =(y_1,\dots,y_n), \]
%where $y_{g(i)}=x_i$ for all $1\leq i\leq n$.\par
%Given $\Phi$ a subgroup of $S_n$ we will denote by $X^n/\Phi$
%the orbit set associated to the action of $\Phi$ over $X^n$.\par
%We will use the notation $[x_1,\dots,x_n]$ to refer to the 
%equivalence class of the $n$-tuple $(x_1,\dots, x_n)$ in 
%any sort of quotient $X^n/\Phi$. That is, while the notation
%$(x_1,\dots, x_n)$ will be reserved to ordered $n$-tuples, 
%$[x_1,\dots,x_n]$ will denote an ordered $n$-tuple modulo the
%action of some arbitrary group of permutations. Which group is this 
%will depend solely on the ambient set where $[x_1,\dots,x_n]$ is
%considered.
%\par
%
%
%\begin{definition}
%	Let $n,a \in \N$, let $\Phi$ be a subgroup of $S_a$, and let
%	$A$ be a subset 
%	\[ A\subseteq [a]^2 \setminus \delta.\]
%	The total edge set $\mathcal{H}_{(a,\Phi, A)}(n)$ of size $a$, 
%	symmetry group $\Phi$ and
%	restrictions $R$ on $n$ elements is the set:
%	\[  \mathcal{H}_{(a,\Phi, R)}(n)= ([n]^a/\Phi) \, \,
%	\setminus \{\,  [x_1, \dots,x_a] \in [n]^a/\Phi  \, \, 
%	| \, \, x_i=x_j \, \text{for some } (i,j)\in R \} \]
%\end{definition}
%
%\begin{definition}
%	An (hyper)-graph $([n], H_1,\dots, H_c)$ with edge colors 
%	$1,\dots, c$, sizes $a_1,\dots,a_c$, 
%	symmetry groups $\Phi_1,\dots,\Phi_c$ and 
%	restrictions $A_1,\dots,A_c$ consists of 
%	\begin{itemize}
%		\item The set $[n]$ for some natural number $n$.
%		\item For $i=1,\dots,c$, a colored edge set $H_i\subseteq \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ whose elements 
%		have color $i$.
%	\end{itemize}
%\end{definition}
%
%\begin{definition} 
%	Let $p=(p_1,\dots, p_c)$, where all $p_i$'s are real numbers
%	between $0$ and $1$. 
%	The random model $HG(n,p)$ with edge colors $1,\dots,c$,
%	sizes $a_1,\dots,a_c$, 
%	symmetry groups $\Phi_1,dots,\Phi_c$ 
%	and restrictions $A_1,\dots,A_c$, is the one that
%	assigns to each graph $G=([n], H_1,\dots, H_c)$
%	probability
%	\[ \mathrm{Pr}(G)=\prod_{i=1}^{c} p_i^{|H_i|}(1-p_i)^{|\mathcal{H}_{(a_i,\Phi_i,A_i)}(n)|-|H_i|}.	
%	\]
%	Equivalently, this is the probability space obtained by 
%	assigning to each colored edge 
%	$e\in \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ probability $p_i$ independently. 
%\end{definition}
%
%For the rest of the work we will consider 
%\begin{itemize}
%	\item the total number of colors $c$,	
%	\item the sizes $a_1,\dots,a_c$,
%	\item the symmetry group $\Phi_1,\dots, \Phi_c$ and,
%	\item the restrictions $A_1,\dots,A_l$
%\end{itemize}
%fixed. When we say ``graph'' from now on what
%we will mean is ``hiper-graph with edge colors 
%$1,\dots, c$, sizes $a_1,\dots,a_c$, 
%symmetry groups $\Phi_1,\dots,\Phi_c$ and 
%restrictions $R_1,\dots,R_c$''. \par
%
%Given a graph $G=([n], H_1,\dots, H_c)$ we will denote by
%$H_i(G)$ the edge set $H_i$, and by $V[G]$ the vertex set
%$[n]$. Also, we will write $H(G)$ to denote the 
%disjoint union of colored sets $\cup_{i=1}^c H_i$.
%This way, an edge $e\in H(G)$ with color $i$ is an element
%$[x_1,\dots,x_{a_i}]\in H_i(G)$, and the $x_i$'s are vertices
%belonging to $V(G)$. \par
%Given a set of vertices, $X\subseteq V(G)$, we will denote
%the by $G[X]$ the induced sub-graph on $X$. \par
%As usual, we will sometimes treat edges as sets of vertices
%rather than ``tuples modulo the action of some permutation group''. 
%This way, expressions like $e_1\cup e_2$ for $e_1, e_2\in H(G)$
%will make sense and mean 
%``the set of vertices that occupy some place in $e_1$ 
%and in $e_2$".\par
%Some other times we will treat edges $e\in H(G)$
%as sub-graphs of $G$ in the evident way. That is, the subgraph
%denoted by $e$ is the one whose vertex set is $e$-i.e., the vertices in $e$-
%and whose only edge is $e$. 
%This way, when we have some edges $e_1,\dots, e_l\in H(G)$ 
%it will make sense to talk
%about the subgraph $\cup_{i=1}^l e_i$, which is the graph
%whose vertex set is the set of vertices belonging to the $e_i$'s, 
%and whose edges are exactly the $e_i$'s. In spite of these
%abuses of notation the ``type'' of any ``term'' involving edges 
%should be derivable from the context. \par
%Another usual abuse of notation we will make is to sometimes
%treat graphs as their underlying vertex sets. Hence,
%expressions defined for sets of vertices will also be defined 
%for graphs. 
%

\end{document}

### 2019-10-24 Article.tex

@@
 \begin{abstract}
-	We consider a finite relational vocabulary $\sigma$ with
-    a first order theory $T$ written in $\sigma$ 
+	We consider a finite relational vocabulary $\sigma$
+	and a first order theory $T$ for $\sigma$ 
     composed of symmetry and 
     anti-reflexivity axioms. We define a binomial random model of finite 
-    $\sigma$-structures that satisfy $T$ and show that first order properties have well defined asymptotic probabilities in the sparse 
+    $\sigma$-structures that satisfy $T$ and show that first order properties have 
+    well defined asymptotic probabilities in the sparse 
     case. It is also shown that those limit probabilities are well-behaved with
@@
 relation symbols $(R_1,\dots, R_m,\dots)$
-where each relation symbol has associated a natural number called its arity.
+where each relation symbol $R_i$ has associated a natural $a_i$
+number called its arity.
 .\par
 
-A ($\sigma$-)structure $\mathfrak{A}$ is composed of (1)
-a set $A$, called the universe of $\mathfrak{A}$, and sets of tuples 
-$R_i^{\mathfrak{A}}\subseteq A^{a_i}$ for all relation symbols 
-$R_i$ in $\sigma$, where $a_i$ is the arity of $R_i$.  
-A structure is called finite if its universe is a finite set.
+A ($\sigma$-)structure $\mathfrak{A}$ is composed of
+a set $A$, called the universe of $\mathfrak{A}$, equipped with
+relations $R_1^{\mathfrak{A}}\subseteq A^{a_1},
+\dots, R_m^{\mathfrak{A}}\subseteq A^{a_m}$. When $\sigma$
+is understood we may refer to $\sigma$-structures as relational
+structures or simply as structures.
+A structure is called finite if its universe is a finite set. \par
+
+It is specially relevant the case where $\sigma$ contains a unique
+relation $R$ symbol with arity two. In this case two important classes
+of relational structures are the class of posets- i.e. those structures
+where the relation is anti-symmetric, transitive and anti-reflexive- and 
+partially graphs- i.e. those where the relation is symmetric and
+anti-reflexive. Unlike posets, one can easily enumerate graphs with a 
+given universe size - in other words, number of vertices.
+
+%One can also consider graphs where 'loops' are allowed or directed graphs. 
+%Unlike the class of posets, these other classes of graph-like structures share 
+%the property that one can easily enumerate their elements up to a given universe 
+%size.
 

### 2019-10-24 Presentacion/Presentación.tex

--- 2019-07-07 Presentacion/Presentación.tex
@@
 
-\AtBeginSection[]
-{
-	\begin{frame}{Contents}
-	\tableofcontents[currentsection]
-	\end{frame}
-}
+%\AtBeginSection[]
+%{
+%	\begin{frame}{Contents}
+%	\tableofcontents[currentsection]
+%	\end{frame}
+%}
 
@@
 \begin{document}
-	\frame{\titlepage}
-	\frame{\tableofcontents}
+ \begin{frame}[plain]
+	\maketitle
+	\small
+	\begin{center}
+	Supervisor: Marc Noy Serrano
+	\end{center}
+ \end{frame}
+%	\frame{\tableofcontents}
 
-	\section{First Order Logic of Sparse Graphs}
+%	\section{First Order Logic of Sparse Graphs}
 	\begin{frame}{The first order language of graphs.}
@@
 		\[\mathrm{F}_\varphi(\beta)=\Ln \mathrm{Pr}(\, G(n,\beta/n)\models \varphi \,) \]
-		is well defined and admits an analytic extension to $\CC$.
+		is well defined and is analytic with respect to $\beta$.
 	\end{theorem}
@@
 		variables.
-		\item Small cycles are a.a.s far away.
-		\item Fixed vertices are a.a.s far away.
+		\vspace{0.5em}
+		\item Small cycles are a.a.s. far away.
+		\vspace{0.5em}
+		\item Fixed vertices are a.a.s. far away.
+		\vspace{0.5em}
 		\item The ball of a given radius centered in fixed
-		vertex is a.a.s a tree. Any tree occurs with a positive 
+		vertex is a.a.s. a tree. Any tree occurs with a positive 
 		probability.
@@
 			\item[(1)]	It is given a finite classification of "small" uni-cycles.
+			\vspace{0.5em}
 			\item[(2)]  It is shown that the rank $k$ type of random graph $G$
-			 in $G(n,\beta/n)$ a.a.s depends exclusively on the number of "small" uni-cycles
+			 in $G(n,\beta/n)$ a.a.s. depends exclusively on the number of "small" uni-cycles
 			 belonging to each class. 
+			\vspace{0.5em}
 			\item[(3)] The asymptotic distribution of those quantities is obtained. 
 		\end{itemize}
+	\end{frame}
 
-	\end{frame}
-	\section{General relational structures}
+%	\section{General relational structures}
 	\begin{frame}{Edge sets}
-		\begin{definition} Fix
-			\begin{itemize}
-				\item natural numbers $n,a\in \N$, with $a\geq 2$
-				\item a subgroup of the symmetric group $\Phi \leq S_a$
-				\item and a subset of pairs $A\subset ([a]\times [a]) \setminus \Delta_a$.
-			\end{itemize}
-		The \textbf{total edge set} $\mathcal{H}_{(a,\Phi, A)}(n)$ of size $a$, 
-		symmetry group $\Phi$ and
-		restrictions $A$, on $n$ elements is the set
+		\begin{definition}
+		The \textbf{total edge set} $\mathcal{H}_{(a,\Phi, A)}(n)$ of \textbf{size} $a$, 
+		\textbf{symmetry group} $\Phi$ and
+		\textbf{restrictions $A$}, on $n$ \textbf{elements} is the set
 		\[ \mathcal{H}_{(a,\Phi, A)}(n)= ([n]^a/\Phi) \, \,
@@
 		\begin{definition}
-			An (hyper)-graph $([n], H_1,\dots, H_c)$ with edge colors 
+			An \textbf{(hyper)-graph} $([n], H_1,\dots, H_c)$ with edge colors 
 			$1,\dots, c$, sizes $a_1,\dots,a_c$, 
@@
 			\begin{itemize}
-				\item The vertex set $[n]$ for some natural number $n$.
-				\item For $i=1,\dots,c$, a ``colored" edge set $H_i\subseteq \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ whose elements 
+				\vspace{1em}
+				\item The \textbf{vertex set} $[n]$ for some natural number $n$.
+				\vspace{1em}
+				\item For $i=1,\dots,c$, a ``colored" \textbf{edge set} $H_i\subseteq \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ whose elements 
 				have color $i$.
@@
 	\begin{frame}{The first order language}
-	Consider the first order purely relational language $\mathcal{L}$ whose signature consists of the relation symbols
+	Consider the first order purely relational language $\mathcal{L}$ with relation symbols
 	$R_1,\dots, R_c$ with arities $a_1,\dots,a_c$. \\~ \par
@@
 	\begin{frame}{The first order language}
-		By definition, a graph $G=([n],H_1,\dots, H_n)$ satisfies, for each $1\leq i \leq c$:
+		A graph $G=([n],H_1,\dots, H_n)$ satisfies, for each $1\leq i \leq c$:
 		\vspace{0.5 em}
 		\begin{itemize}
-			\item Symmetry formulas:
+			\item \textbf{Symmetry formulas}:
 			\[ S_g: =\big( R_i(x_1\dots,x_{a_i})\iff R_i(x_{g(1)}\dots,x_{g(a_i)})\big) ,\]
 			where $g$ is an element from $\Phi_i$.
-			\item Anti-reflexivity formulas:
-			\[A_{i,(j,l)}:=\big(R_i(x_1\dots,x_{a_i})\implies 
+			\item \textbf{Anti-reflexivity formulas}:
+			\[AR_{i,(j,l)}:=\big(R_i(x_1\dots,x_{a_i})\implies 
 			\neg(x_j= x_l)\big),\]
@@
 	$G=([n],H_1,\dots,H_c)$,
+	\\~\\
 	\[ \mathrm{Pr}(G)=\prod_{i=1}^{c} p_i^{|H_i|}\cdot (1-p_i)^{|\mathcal{H}_{(a_i,\Phi_i,A_i)}(n)|-|H_i|} . \]
-	We consider the case where for each $1\leq i \leq c$,  $p_i(n)=\beta_i/n^{a_i-1}$.
-	\\~\\ 
-	Let $\beta=(\beta_1,\dots, \beta_c)\in [0,\infty)^c$. We abbreviate
-	\[HG(n,p(n,\beta)):= HG(n,\beta_1/n^{a_1-1},\dots, \beta_c/n^{a_c-1}). \]
+	~\\~\\
+	We consider the \textbf{sparse} case where for each $1\leq i \leq c$,  $p_i(n)=\beta_i/n^{a_i-1}$.
 
@@
 			\[ \mathrm{F}(\beta_1,\dots, \beta_c)= \Ln 
-			\mathrm{Pr}(HG(n,p(n,\beta))\models \varphi )
+			\mathrm{Pr}(HG(n,p(n,\beta))\models \varphi ),
 			\]
-			is well defined and admits an analytic extension to $\CC^c$. 
+			where 	
+			\[p(n,\beta):= (\beta_1/n^{a_1-1},\dots, \beta_c/n^{a_c-1}) \]
+			is well defined and is analytic with respect to $\beta=(\beta_1,\dots,\beta_c)$. 
 		\end{theorem}
@@
 
-			\begin{equation*}d(x,y)= \min_{\substack{H \leq G\\ 
-					H \text{ connected }\\
-					x,y\in V(H)}} \big(|V(H)| - 1 \big), \, \, \text{ or } \infty \text{ if }
+			\begin{equation*}d(x,y)= \min_{\substack{H \leq G, x,y\in V(H)\\ 
+					H \text{ connected}}}
+					 \big(|V(H)| - 1 \big), \, \, \text{ or } \infty \text{ if }
 				x,y \text{ are not connected.}
 			\end{equation*}
-
+			\vspace{-0.3em}
 		\begin{definition} 
 			A path between two vertices $x,y$ in a graph $G$ is
-			a connected subgraph $H\leq G$ containing both $x,y$ whose
-			number of vertices is minimum. 
+			a minimal graph among the 
+			connected subgraphs $H\leq G$ containing both $x,y$.
 		\end{definition}
-
+			\begin{center}
+			\includegraphics[width=0.8\linewidth]{Path.pdf}
+		\end{center}
 	\end{frame}
@@
 		\end{definition}
-	~\\
+
 	\end{frame}
@@
 
-	\begin{frame}{The $k$-morphism relation over trees.}
-		A rooted $(T,x)$ is a tree $T$ together with a distinguished vertex
-		$x\in V(T)$.\par
-		\[Tree(y, T) = (T[X], y),\]
-		\[\text{where } \, X=\{ z\in V(T) \, | \, d(x,z)=d(x,y)+d(y,z)\}.\]~\\
-		The root of an edge $e\in H(T)$ in a rooted tree 
-		$(T,x)$ is the vertex $y\in e$ such that $d(x,y)=d(x,e)$.\\~\\
-		The radius of an edge $e\in H(T)$ is 
-		\[\max_{\substack{y\in e \\ y \text{ not the root of } e}} r(Tree(y,T)). \]
-
-	\end{frame}
+%	\begin{frame}{The $k$-morphism relation over trees.}
+%		A rooted $(T,x)$ is a tree $T$ together with a distinguished vertex
+%		$x\in V(T)$.\par
+%		\[Tree(y, T) = (T[X], y),\]
+%		\[\text{where } \, X=\{ z\in V(T) \, | \, d(x,z)=d(x,y)+d(y,z)\}.\]~\\
+%		The root of an edge $e\in H(T)$ in a rooted tree 
+%		$(T,x)$ is the vertex $y\in e$ such that $d(x,y)=d(x,e)$.\\~\\
+%		The radius of an edge $e\in H(T)$ is 
+%		\[\max_{\substack{y\in e \\ y \text{ not the root of } e}} r(Tree(y,T)). \]
+%		
+%	\end{frame}
 
@@
 		inductively as follows:
-
+		\\~\\~\\
 		\begin{itemize}
@@
 	\begin{frame}{The $k$-morphism relation over trees.}
-		For $r>0$:
+		If $r(T_1)=r(T_2)>0$:
 			\begin{itemize}
 				\item  First we
-				define the type of a en edge with radius less than $r$:
+				define the $k$-type of a an initial edge:
 
@@
 		\begin{itemize}
-		\item If $r(T_1)=r(T_2)=r$ we say that $T_1\morph{K}T_2$ if
-		for any edge $k$-type $E$ of radius less than $r$ either:
+		\item We say that $T_1\morph{k}T_2$ if
+		for any defined edge $k$-type $E$ either:
 		\begin{itemize}
@@
 		\end{itemize}
+	\end{frame}
+%
+%	\begin{frame}{The $k$-morphism relation for graphs}
+%		To make the definitions suitable for proofs using E.F. games we need to work with "graphs
+%		with constants". 
+%		\begin{definition}
+%			The center of a connected graph $G(\clist)$ is its minimal 
+%			connected subgraph containing all the constants and clusters.\\
+%			\vspace{0.2 em} If $G(\clist)$
+%			is not connected its center is the union of the centers of its connected
+%			components.   
+%		\end{definition}
+%	\end{frame}
+%
+%		
+%	\begin{frame}{The $k$-morphism relation for graphs}
+%	A sketch of a center:
+%	\begin{center}
+%		\includegraphics[width=0.5\linewidth]{Center.pdf}
+%	\end{center}
+%	\end{frame}
+%
+%	\begin{frame}{The $k$-morphism relation for graphs}
+%	\begin{definition} 
+%		We say that $G_1(\clist)\morph{k}G_2(\clist)$, if there is an isomorphism
+%		$f:Center(G_1)\rightarrow Center(G_2)$ s.t.
+%		\begin{itemize}
+%			\item $f(c^1_i)=c^2_i$ for all constants, and
+%			\item $Tree(x,G_1)\morph{k} Tree(f(x),G_2)$ for all $x\in V(Center(G_1))$.
+%		\end{itemize}
+%	\end{definition}
+
+	\begin{frame}{The $k$-morphism relation for uni-cycles}
+	\begin{definition} 
+		Let $G_1,G_2$ be uni-cycles. Let $O_1, O_2$ be their cycles respectively.\\
+		 $G_1\morph{k}G_2$, if  for some $f$: \\~\\
+		\begin{itemize}
+
+			\item $O_1 \morph{f} O_2$, and \\~\\
+
+			\item $Tree(x,G_1)\morph{k} Tree(f(x),G_2)$ for all $x\in V(O_1)$.
+		\end{itemize}
+	\end{definition}
+	\end{frame}
+%	
+%	\end{frame}
+%	
+	\begin{frame}{The $k$-morphism relation for uni-cycles}
+	\begin{center}
+		\includegraphics[width=0.95\linewidth]{KmorphicCycles1.pdf}
+	\end{center}
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation for uni-cycles}
+	\begin{center}
+		\vspace{0.48 em}
+		\includegraphics[width=0.95\linewidth]{KmorphicCycles2.pdf}
+	\end{center}
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation for uni-cycles}
+	\begin{center}
+	\vspace{2.3em}
+	\includegraphics[width=\linewidth]{KmorphicCycles3.pdf}
+	\end{center}
+	\end{frame}
+
+	\begin{frame}{The $k$-morphism relation for cycles}
+
+		Uni-cyclic $k$-morphic graphs have the same
+		first order rank $k$-type.	\\~\\
+
+		The tool for proving this are \textbf{Ehrenfeucht Fraisse games}.
+		\\~\\
+
+		The $k$-morphism relation gives, for any $r$, a \textbf{finite classification} of the cycles of diameter
+		at most $r$ with trees of radii at most $r$ hanging from their vertices.
 
@@
 
+	\begin{frame}{The landscape of $HG(n,p(n,\beta))$}
+		\begin{itemize}
+		\item Clusters with diameter at most $d$, for any fixed $d$, a.a.s. will not appear.
+		In particular, small cycles are a.a.s. far away.
+	\end{itemize}
+	\begin{center}
+			\includegraphics[width=0.8\linewidth]{FarCycles.pdf}
+	\end{center}
+
+	\end{frame}
+
+	\begin{frame}{The landscape of $HG(n,p(n,\beta))$}
+	\begin{itemize}
+		\item Given any fixed cycles $O_1, \dots, O_l$, their quantities converge
+		in distribution to independent Poisson 
+		variables.
+		\vspace{1em}
+		\item Fixed vertices are a.a.s. far away.
+		\vspace{1em}
+		\item The ball of a given radius centered in fixed
+		vertex is a.a.s. a tree. Any tree occurs with a positive 
+		probability.
+	\end{itemize}
+	~\\
+	In consequence, F.O. properties of a fixed quantifier rank $k$ only depend on the small neighbourhoods of the small cycles in
+	a graph.  
+	\end{frame}
+
+	\begin{frame}{Probabilities of uni-cycles}
+
+	The main tool for computing probabilities is the following:
+
+		\begin{theorem}{(Multivatiate Brun's Sieve)}
+			For $1\leq i \leq l$ let $\{X_i(n)\}_{n\in \N}$,  be successions of 
+			random variables s.t the $X_i(n)$'s are sums of random indicator variables.
+			If for any natural numbers $a_1,\dots, a_l$
+			\[ \Ln E\left[\prod_{i=1}^l \binom{X_i}{a_i} \right] = 
+			\prod_{i=1}^l \frac{\lambda_i^{a_i}}{a_i!}, \]
+			then
+			\[ \forall x_1,\dots, x_l\in \N: \quad \Ln \mathrm{Pr}(\wedge_{i=1}^l
+			X_i=x_i)= \prod_{i=1}^l \mathrm{Poiss}_{\lambda_i}(x_i).\]
+
+		\end{theorem}
+
+	\end{frame}
+
+	\begin{frame}{Ending summary}
+		\begin{itemize}
+			\item $HG(n,p(\beta,n))$ is very similar to $G(n,\beta/n)$. The ideas behind Lynch's proof
+			can be used here after finding suitable definitions. 
+			\\~\\
+			\item The main increase in complexity is due to the fact that trees are more complicated in $HG(n,p(\beta,n))$:
+			the types of the edges have to be considered now. 
+			\\~\\
+			\item Using Brun's Sieve simplifies the harder combinatorial proofs.  
+		\end{itemize}
+	\vfill
+	\pause
+	{\hfill \Large Thank you for attention!}
+ 	\end{frame}
+
 \end{document}

### 2020-01-08 Article.tex
Ordenador barcelona

@@
-\documentclass[11pt,notitlepage,a4paper]{article}
+\documentclass[12pt,notitlepage,a4paper]{article}
 
-\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry}
+\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}
 \usepackage{graphicx}
@@
 \usepackage{pdfpages}
+
+\usepackage{mathptmx}
 
@@
 \newtheorem{theorem}{Theorem}[section]
+\newtheorem{obs}{Observation}[section]
 \newtheorem{lemma}{Lemma}[section]
@@
 \newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
+\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
+\newcommand{\ehr}{\textsc{Ehr}}
 
@@
     An application of these results to the problem of random Boolean 
-    satisfability is presented afterwards. 
+    satisfiability is presented afterwards. 
     We show that there is no first order property of $k$-CNF formulas
-    that implies unsatisfability and holds for almost all typical 
-    unsatisfable formulas when the number of clauses is linear.
+    that implies unsatisfiability and holds for almost all typical 
+    unsatisfiable formulas when the number of clauses is linear.
 
@@
 \section*{Introduction}
-.
-.
-.
-.
 
-\setcounter{section}{-1}
+Since the work of Erd\"os and R\`enyi on the evolution of random graphs
+\cite{erdHos1960evolution} the study of the asymptotic properties of random
+structures has played a relevant role in combinatorics and computer science.
+A central theme in this topic is, given a succession $(G_n)_n$ of random
+structures of some sort and a property $P$, to determine the limit probability
+that $G_n$ satisfies $P$ or to determine whether that limit exists. \par
+One approach that has proven to be useful is to classify the properties $P$
+according to the logical languages they can be defined in. We say that the 
+succession $(G_n)_n$ obeys a convergence law with respect to some logical language
+$\mathcal{L}$ if for any given property $P$ expressible in $\mathcal{L}$ the 
+probability that $G_n$ satisfies $P$ tends to some limit as $n$ grows to infinity.
+We say that $(G_n)_n$ obeys a zero-one law with respect to $\mathcal{L}$ if
+that limit is always either zero or one. 
+The seminal theorem on this topic, due to Fagin \cite{fagin1976probabilities}
+and Glebskii et al. 
+\cite{glebskii1969range} independently, states that if $G_n$ denotes a labeled
+graph with $n$ vertices picked uniformly at random among all $2^{\binom{n}{2}}$ 
+possible then $(G_n)_n$ satisfies a zero-one law with respect to the first order
+(FO) language of graphs. \par
+Originally this result was proven in the broader context of relational
+structures but it was in the theory of random graphs were the study of 
+other zero-one and convergence laws became more prominent. In particular,
+the asymptotic behavior of FO logic in the binomial model of random graphs 
+$G(n,p)$ has been extensively studied. In this model, introduced by Gilbert 
+\cite{gilbert1959random}, a random graph is obtained from $n$ labeled vertices
+by adding each possible edge with probability $p$ independently. When $p=1/2$
+this distribution of random graphs coincides with the uniform one, mentioned 
+above. In general, for the case where $p$ is a constant probability a slight 
+generalization of the proofs in \cite{fagin1976probabilities} and 
+\cite{glebskii1969range} works and $G(n,p)$ satisfies a zero-one law 
+for FO logic. If we consider $p(n)$ a decreasing function of the form
+$n^{-\alpha}$ we can ask the question of what are the values of $\alpha$
+for which $G(n,p(n))$ obeys a zero-one or a convergence law for FO logic. 
+In \cite{shelah1988zero} Shelah and Spencer gave a complete answer 
+for the range $\alpha\in (0,1)$. Among other results, they proved that
+if $\alpha$ is an irrational number in this interval then
+$G(n,p(n))$ obeys a zero-one law for FO logic, while if $\alpha$
+is a rational number in the same range then $G(n,p(n))$ does not
+even satisfy a convergence law for FO logic. The case $\alpha=1$
+was later solved by Lynch in \cite{lynch1992probabilities}. A weaker
+form of the main theorem in that article states the following:
+\begin{theorem} 
+	For any FO sentence $\phi$, the function
+	$F_\phi: (0,\infty)\rightarrow [0,1]$ given by 
+	\[ F_\phi(\beta) = \Ln \mathrm{Pr}\big( \mathrm{G}(n,\beta/n)
+	\text{ satisfies } \phi   \big) \]
+	is well defined and analytic. In particular, for any
+	$\beta \geq 0$ the model $\mathrm{G}(n,\beta/n)$
+	obeys a convergence law for FO logic. 
+\end{theorem}
+
+The analyticity of these asymptotic probabilities with respect to 
+the parameter $\beta$ imply that FO properties cannot "capture" sudden
+changes that occur in the random graph $\mathrm{G}(n,\beta/n)$
+as $\beta$ changes. Given $p(n)$ a probability, $P$ a property of graphs,
+and $Q$ a sufficient condition for $P$ - i.e., a property that 
+implies $P$ -, we say that $Q$ explains $P$ if $\mathrm{G}(n,p(n))$ satisfies 
+the converse implication $P \implies Q$ asymptotically almost surely
+(a.a.s.). A notable example of this phenomenon happens in the range 
+$p(n)= \log(n)/n + \beta/n$ with $\beta$ constant. Erd\"os and R\`enyi
+\cite{erdHos1960evolution} 
+showed that for probabilities of this form $\mathrm{G}(n,p(n))$ 
+a.a.s. is disconnected only if it contains an isolated vertex. 
+An observation by Albert Atserias is the following:
+
+\begin{theorem}
+Let $c$ be a real constant such that 
+$\Ln \mathrm{Pr}\big( G(n, c/n) 
+\text{ is not }	3\text{-colorable }\big)> 0$.  
+Then there is no FO graph property that explains 
+non-$3$-colorability for $G(n, c/n)$.
+\end{theorem}
+
+The short proof of this theorem is as follows: 
+It is a known fact that there are positive constants
+$c_0\leq c_1$ such that $G(n, c/n)$ is a.a.s $3$-colorable
+if $c<c_0$ and it is a.a.s non $3$-colorable if $c>c_1$ 
+REFERENCES NEEDED.
+Suppose that $P$ is a FO graph property that implies
+non-$3$-colorability. Then, because of this implication,
+for all values of $c$
+\[\Ln \mathrm{Pr}\big( G(n, c/n) 
+\text{ satisfies } P \big) \leq \Ln \mathrm{Pr}\big( G(n, c/n) 
+\text{ is not }	3\text{-colorable}\big).\]
+In consequence the asymptotic probability that $G(n,c/n)$ 
+satisfies $P$ is zero when $c<c_0$. By Lynch's theorem, if 
+$P$ is definable in FO logic then this asymptotic probability
+varies analytically with $c$. Using the fact that any analytic 
+function that takes value zero in a non-empty interval must 
+equal zero everywhere, we obtain that $G(n,c/n)$ a.a.s does 
+not satisfy $P$ for any value of $c$. 
+As a consequence the theorem follows.  \par
+
+The aim of this work is to extend Lynch's result to arbitrary 
+relational structures were the relations are subject to some
+predetermined symmetry and anti-reflexivity axioms. This was 
+originally motivated by an application to the study of random
+$k$-CNF formulas. Since \cite{chvatal1992mick} it is known that 
+for each $k$ there are constants $c_0,c_1$ such that a random 
+$k$-CNF formula with $cn$ clauses over $n$ variables
+
+%Besides this 
+% 
+%This question was originally posed in \cite{atserias2005definability}
+%by Albert Atserias where the answer was given for various probability
+
+\setcounter{section}{0}
 
@@
 
-A (relational) vocabulary $\sigma$ is a collection of
+\subsection{General notation}
+
+Given a positive natural number $n$, we will write
+$[n]$ to denote the set ${1,2,\dots,n}$.\par
+Given a set $S$ and a natural number $k\in \N$
+we will use $\binom{S}{k}$ to denote the set of 
+subsets of $S$ whose size is $k$. \par
+Let $S$ be a set, $a$ a positive natural number, 
+and $\Phi$ a group of permutations over 
+$[a]$. Then $\Phi$ acts naturally over
+$S^a$ in the following way: Given $g\in \Phi$ and
+$(x_1,\dots,x_a)$ we define $g(x_1,\dots,x_a)=
+(x_{g(1)},\dots,x_{g(a)})$.
+We will denote by $S^a/\Phi$ to the quotient
+of the set $S^a$ by this action. Given an element
+$(x_1,\dots, x_a)\in S^a$ we will denote its equivalence
+class in $S^a/\Phi$ by $[x_1,\dots,x_a]$. Thus, for any
+$g\in \Phi$, by definition $[x_1,\dots,x_a]=[x_{g(1)}
+,\dots,x_{g(a)}]$. The notation $(x_1,\dots, x_a)$ 
+will be reserved 
+to ordered tuples while 
+$[x_1,\dots,x_a]$ will denote an ordered tuple modulo the
+action of some arbitrary group of permutations. Which group is
+this will depend on the ambient set where $[x_1,\dots,x_a]$ belongs
+and it should either be clear from context or not be relevant.\par
+We will denote ordered lists of elements by $\overbar{x}:=x_1,\dots,x_a$. 
+This way, expressions like $(\overbar{x})$ or $[\overbar{x}]$ would mean 
+$(x_1,\dots,x_a)$ and $[x_1,\dots,x_a]$ respectively.
+Sometimes we will directly write $\overbar{x}$ without specifying the list
+it names nor its length when it is understood or not relevant.
+\par
+Given two real functions over the natural numbers 
+$f,g:\N \rightarrow \R$ we will write $f=O(g)$ to 
+mean that there exists some constant $C\in \R$
+such that $f(n)\leq Cg(n)$ for $n$ sufficiently large, 
+as usual.
+If $g(n)\neq 0$ for sufficiently large values of $n$ then
+we will write $f\simeq g$ if $\Ln \frac{f(n)}{g(n)}=1$.\par
+
+\subsection{Logical preliminaries}
+We will assume a certain degree of familiarity with the 
+concepts. For a more complete exposition of the topics 
+presented here one can consult \cite{ebbinghaus2013mathematical}.
+
+A relational vocabulary $\sigma$ is a collection of
 relation symbols $(R_1,\dots, R_m,\dots)$
@@
 number called its arity.
-.\par
-
-A ($\sigma$-)structure $\mathfrak{A}$ is composed of
+A $\sigma$-structure $\mathfrak{A}$ is composed of
 a set $A$, called the universe of $\mathfrak{A}$, equipped with
@@
 
-It is specially relevant the case where $\sigma$ contains a unique
-relation $R$ symbol with arity two. In this case two important classes
-of relational structures are the class of posets- i.e. those structures
-where the relation is anti-symmetric, transitive and anti-reflexive- and 
-partially graphs- i.e. those where the relation is symmetric and
-anti-reflexive. Unlike posets, one can easily enumerate graphs with a 
-given universe size - in other words, number of vertices.
+In the first order language $FO[\sigma]$ with signature $\sigma$ 
+formulas are formed by variables $x_1,\dots, x_i,\dots$,
+the relation symbols in $\sigma$, the equal symbol $=$,
+the usual Boolean connectives $\neg, \wedge, \vee, \dots$, 
+the existential and universal quantifiers $\exists, \forall$, and
+the parentheses $),($. Then formulas in $FO[\sigma]$ are defined as 
+follows.
+\vspace*{-0.2em}
+\begin{itemize}[topsep=1pt, itemsep=1pt]
+	\item The expression $R(y_1,\dots,y_a)$, where the $y_i$'s are variables and $R$
+	is a relation symbol in $\sigma$ with arity $a$, belongs to $FO[\sigma]$.
+	\item The expression $y_1=y_2$, where $y_1, y_2$ are variables, 
+	belongs to $FO[\sigma]$.
+	\item Given formulas $\phi, \psi \in FO[\sigma]$, any Boolean combination of them
+	$\neg(\phi), (\phi \wedge \psi), (\phi \vee \psi), \dots$ belongs to $FO[\sigma]$ as well.
+	\item Given a formula $\phi \in FO[\sigma]$ and $x$ a variable that 
+	does not appear bounded
+	by a quantifier in $\phi$, the expressions $\forall x (\phi)$ and 
+	$\exists x (\phi)$ belong both to $FO[\sigma]$. 
+\end{itemize}  
+We will write $\forall y_1, y_2,\dots, y_m$ or simply $\forall \overbar{y}$
+instead of  
+$\forall y_1, \forall y_2,\dots, \forall y_m$ and likewise for
+the quantifier $\exists$.
+
+We define the set of free variables of a formula as usual. 
+We will use the notation $\phi(\overbar{y})$ to refer to a 
+formula $\phi\in FO[\sigma]$
+to denote that its free variables are the ones in $\overbar{y}$.
+Formulas with no free variables are called sentences. \par
+The quantifier rank of a formula $\phi$, denoted by $qr(\phi)$, 
+is defined as the maximum number of nested quantifiers in $\phi$. \par
+Sentences in $FO[\sigma]$ are interpreted over $\sigma$-structures
+in the natural way. Given an structure $\mathcal{A}$, and a sentence
+$\phi\in FO[\sigma]$ we write $\mathcal{A} \models \phi$ to denote 
+that $\mathcal{A}$ satisfies $\phi$. If $\psi(\overbar{y})$ is a
+formula, $\overbar{a}$ are elements in the universe of 
+$\mathcal{A}$, and $\overbar{y}$ and $\overbar{a}$ are lists of the same size,
+then we write $\mathcal{A} \models 
+\psi(\overbar{a})$
+to mean that $\mathcal{A}$ satisfies $\psi$ when the free variables in
+$\overbar{y}$ are interpreted as the elements in $\overbar{a}$.
+
+\subsection{Structures as multi-hypergraphs}
+
+For the rest of the article consider fixed:
+\begin{itemize}
+	\item Positive natural numbers $t$, $\overbar{a}=a_1,\dots, a_t$.\
+
+	\item A relational vocabulary $\sigma=\{\overbar{R}\}$, with
+	$\overbar{R}=R_1,\dots, R_t$ such that $a_i$ is the arity of
+	$R_i$.
+
+	\item 
+	Groups $\overbar{\Phi}=\Phi_1,\dots,\Phi_t$
+	such that each $\Phi_i$ is consists of 
+	permutations on $[a_i]$ with the usual 
+	composition as its operation.
+
+	\item 
+	Sets $\overbar{P}=P_1, \dots, P_t$ satisfying 
+	$P_i\subseteq \binom{[a_i]}{2}$
+
+\end{itemize}
+
+We define the class $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$ as the 
+class of $\sigma$-structures that
+satisfy the 
+following axioms: 
+\begin{itemize}
+	\item \textit{Symmetry axioms}: For each $1\leq s \leq t$ and
+	each $g\in \Phi_s$:
+	\[ \forall x_1,\dots, x_{a_s} \big(  R_s(x_1,\dots, x_{a_s})
+	\iff R_s(x_{g(1)},\dots,x_{g(a_s)}) \big)    \]
+	\item \textit{Anti-reflexivity axioms}: For each 
+	$1\leq s \leq t$ and $\{i,j\}\in P_s$
+	\[ \forall x_1,\dots, x_{a_s} 
+	\big( (x_i=x_j) \implies \neg R_s(x_1,\dots, x_{a_s})
+	\big)\]
+	\end{itemize}
+
+We can think of structures in  $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$
+as "multi-hypergraphs" with
+$t$ edge sets whose edges are of sizes $\overbar{a}$ respectively
+, are invariant under permutations in $\overbar{\Phi}$ resp., 
+and do 
+not contain repetitions of vertices in the positions given by
+$\overbar{P}$ resp. We make this observation formal in the 
+following definitions:
+
+\begin{definition} 
+	Let $V$ be a set, $a$ be a positive natural number,
+	$\Phi$ be a group of permutations over $[a]$ and
+	$P\subseteq \binom{[a]}{2}$. 
+	We define the \textbf{total
+	edge set over $V$ with edge size $a$, symmetry group $\Phi$ and 
+	anti-reflexivity restrictions $P$} as the set
+	\[ E^{V}_{a,\Phi,P}= (V^a/\Phi) \setminus \{ [x_1,\dots,x_a]  
+	\,| \,
+	x_1,\dots,x_a\in V \, \wedge \, x_i=x_j \text{ for some } \{i,j\}\in P \}. \]
+\end{definition}
+
+That is, $E^{V}_{a,\Phi,P}$ contains all the ``tuples modulo the permutations
+in $\phi$" excluding those that contain some repetition of vertices in
+the positions given by $P$.
+
+\begin{definition} 
+Let $V$ be a set. A \textbf{ multi-hypergraph with
+vertex set $V$, $t$ edge sets, with edge sizes given by $\overbar{a}$,
+symmetry groups $\overbar{\Phi}$, and anti-reflexivity restrictions $\overbar{P}$}
+is a pair $G=(V,\overbar{E})$, where $\overbar{E}=E_1,\dots, E_t$ and
+for each $i$, $E_i \subseteq E^{V}_{a_i,\Phi_i,P_i}$.
+\end{definition}
+
+For the sake of word economy the expression ``multi-hypergraph with
+vertex set $V$, $t$ edge sets, with edge sizes given by $\overbar{a}$,
+symmetry groups $\overbar{\Phi}$, and anti-reflexivity restrictions $\overbar{P}$" 
+will be replaced simply by ``hypergraph". The word ``hypergraph" will not hold
+any other meaning than this for the rest of this writing except for the places
+where it is explicitly stated.  \par
+
+Hypergraphs, as we have defined them, can be naturally interpreted as
+structures from $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$ in the following way: 
+given $G=(V,\overbar{E})$,
+we consider $V$ to be the universe of $G$, and for any $i$ we define
+$R_i^G\subseteq V^{a_i}$ as the set such that
+$(\overbar{x})\in V^{a_i}$, $(\overbar{x})\in R_i^G$ if and only if 
+$[\overbar{x}]\in E_i$. Under this interpretation hypergraphs, by definition,
+satisfy the symmetry and anti-reflexivity axioms given above. It is also easy to
+see that this interpretation induces a one-to-one identification between 
+structures in $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$ and hypergraphs. \par
+
+Before moving on we need to introduce some additional notation. NOTACION
+
+Given an hypergraph $G$ we define the following metric, $d$, over $V(G)$:
+\[ d^G(v,u)= \min_{\substack{H \text{ subgraph of } G\\ 
+		H \text{ connected }\\
+		v,u\in V(H)}} |V(H)| - 1 .\]
+That is, the distance between $v$ and $u$ is the minimum size
+of a connected graph $H$ containing both vertices, minus one. 
+If such graph does not exist we define $d^G(u,v)=\infty$.
+This definition extends naturally to subsets $X,Y\subseteq V(G)$:
+\[ d^G(X,Y)=\min_{\substack{x\in X\\ y\in Y}} d^G(x,y).\]
+As usual, when $X=\{x\}$ we will omit the brackets and write
+$d^G(x,Y)$ instead of $d^G(\{x\},Y)$, for example. When $G$ 
+is understood or not relevant we will usually simply denote the 
+distance by $d$ instead of $d^G$. \par
+
+Given set of vertices vertex, $X\subseteq V(G)$, 
+we denote by $N^G(X;r)$ the $r$-neighborhood of $X$ in 
+$G$. That is,  $N^G(X;r)= G[Y]$, where $Y\subseteq V(G)$ is 
+the set:
+\[ Y:= \{ u \in V(G) \ | \ d(X,u)\leq r   \}. \]
+In particular, when $X$ is a singleton $\{v\}$, we
+will write $N^G(v;r)$ instead of $N^G(\{v\};r)$.
+As before, we will usually drop the ``$G$'' from our 
+notation when $G$ is understood or not relevant.
+
+\subsection{The random model}
+
+Let $\overbar{p}:=p_1\dots,p_t$.
+The random model $G^{\mathcal{C}}(n,\overbar{p})$ 
+is the discrete probability space that
+assigns to each hypergraph $G$ whose vertex
+set $V(G)$ is $[n]$ the following probability:
+
+\[ \mathrm{Pr}(G)=\prod_{i=1}^{t} p_i^{|E_i(G)|}
+(1-p_i)^{ |E^{[n]}_{a_i,\Phi_i,P_i}|-|E_i(G)|}.	
+\]
+Equivalently, this is the probability space obtained by 
+assigning to each edge with color $i$,  
+$e\in  E^{[n]}_{a_i,\Phi_i,P_i}$ probability $p_i$ independently.
+
+\subsection{Ehrenfeucht-Fraisse Games}
+
+Let $G_1$ and $G_2$ be hypergraphs. We define the $k$ round 
+Ehrenfeucht-Fraisse game on $G_1$ and $G_2$, denoted by
+$\ehr_k(G_1,G_2)$, as follows:
+The game is played between two players, Spoiler and Duplicator, and
+the number of rounds, $k$, is known for both from the start.
+At the beginning of each round Spoiler chooses a vertex from either
+$V(G_1)$ or $V(G_2)$ and Duplicator responds by choosing a vertex
+from the other set.
+Let us denote by 
+$v_i$, resp. $u_i$ the vertex from $G_1$, resp. from $G_2$, 
+chosen in the $i$-th round,
+for $i\in [k]$. At the end of the $k$-th round 
+Duplicator wins if the following holds:
+\begin{itemize}
+	\item For any $i,j\in [k]$, $v_i=v_j \iff u_i=u_j$.
+	\item Given indices $i_1,\dots, i_a \in [k]$, and a color 
+	$c\in [t]$,  
+	$[v_{i_1},\dots,v_{i_a}] \in E_c(G_1) \iff [u_{i_1},\dots,u_{i_a}]
+	\in E_c(G_2)$.
+
+\end{itemize}
+
+We define the equivalence relation $=_k$ between hypergraphs as follows:
+We say that $G_1=_k G_2$ if for any sentence $\phi\in 
+FO[\sigma]$ with $qr(\phi)\leq k$ then $G_1\models\phi$ if and 
+only if $G_2\models\phi$. 
+\par
+
+The following is satisfied:
+
+\begin{theorem}
+	[Ehrenfeut, \citealp{ehrenfeucht1961application}] Let
+	$G_1$ and $G_2$ be hypergraphs.
+	Then Duplicator wins $\ehr_k(G_1,G_2)$
+	if and only if $G_1=_k G_2$.	
+\end{theorem}
+
+Now consider $\overbar{v}$, and $\overbar{u}$ lists of vertices of the same length, $l$,
+from $G_1$ and $G_2$ respectively. We define the $k$ round 
+Ehrenfeucht-Fraisse game on $G_1$ and $G_2$ with initial position given
+by $\overbar{v}$ and $\overbar{u}$, denoted by $\ehr_k(G_1,\overbar{v},G_2,\overbar{u})$,
+the same way as $\ehr_k(G_1,G_2)$, but in this case the game has $l$ extra 
+rounds at the beginning where the vertices in $\overbar{v}$ and $\overbar{u}$ are 
+played successively. After this, $k$ more rounds are played normally. \par
+
+We also define the $k$-round distance Ehrenfeucht-Fraisse game on 
+$G_1$ and $G_2$, denoted by $d\ehr_k(G_1,G_2)$, the same way as
+$\ehr_k(G_1,G_2)$, but now, in order for Duplicator to win the
+game, the following additional condition has to be satisfied 
+at the end of the $k$-th round:
+\begin{itemize}
+	\item For any $i,j\in [k]$, $d^{G_1}(v_i,v_j)=d^{G_2}(u_i,u_j)$.
+\end{itemize}
+
+Given $\overbar{v}$, and $\overbar{u}$ lists of vertices of the same length,
+from $G_1$ and $G_2$ respectively we define the game 
+$d\ehr_k(G_1,\overbar{v},G_2,\overbar{u})$ analogously to 
+$\ehr_k(G_1,\overbar{v},G_2,\overbar{u})$.
+
+\subsection{Some winning strategies for Duplicator}
+
+The aim of this section is to show the winning strategy
+for Duplicator that is going to be used in our proofs. \par
+
+Let $G_1$ and $G_2$ be hypergraphs, and let $\overbar{v} \subseteq V(G_1), 
+\overbar{u} \subseteq V(G_2)$ be lists of vertices of the same size.
+We say that $N(\overbar{v};r)$ and $N(\overbar{u};r)$ are
+$k$-similar, or that $\overbar{v}$ and $\overbar{u}$
+have $k$-similar $r$-neighborhoods, if Duplicator wins
+$d\ehr_k(N(\overbar{v};r),\overbar{v},N(\overbar{u};r),\overbar{u})$.\par
+If $X\subseteq V(G_1)$ and $Y\subseteq V(G_2)$
+are sets of vertices we say that $X$ and $Y$ have $k$-similar
+$r$-neighborhoods if we can order their vertices to form
+lists $\overbar{v}$, resp. $\overbar{u}$ such that $N(\overbar{v};r)$ and
+$N(\overbar{u};r)$ are $k$-similar.
+\par
+Now suppose that $X\subseteq V(G_1)$ and $Y\subseteq V(G_2)$ can
+be partitioned into lists $X=\overbar{v_1}\cup \dots \cup \overbar{v_a}$
+and $Y=\overbar{u_1}\cup \dots \cup \overbar{u_b}$ 
+such that $N(\overbar{v_i};r)$'s, and the
+$N(\overbar{u_i};r)$'s, are connected and disjoint. 
+We say that $N(X;r)$ and
+$N(Y;r)$ are $k$-agreeable,
+or that they have $k$-agreeable neighborhoods, 
+if any $\overbar{w}$ among the $\overbar{v_i}$'s or
+among the $\overbar{u_i}$'s satisfies:
+\begin{itemize}
+	\item The number of $\overbar{v_i}$'s and 
+	the number of $\overbar{u_i}$'s satisfying that ``$\overbar{v_i}$ 
+	(resp. $\overbar{u_i}$) and $\overbar{w}$ have $k$-similar 
+	$r$-neighborhoods" are the
+	same or are both greater or equal than $k$.
+\end{itemize}
+
+The main theorem of this section,which
+is a slight strengthening of Theorem 
+2.6.7 from \cite{spencer2013strange}, is the following:
+
+\begin{theorem}\label{ThmDuplicator}
+	 Set $r=(3^k-1)/2$.
+Let $G_1,G_2$ be hypergraphs, and suppose there exist
+sets $X\subseteq V(G_1)$, $Y\subseteq V(G_2)$ with the 
+following properties:
+\begin{enumerate}
+	\item[(1)] $N(X;r)$ and $N(Y;r)$ are $k$-agreeable.
+	\item[(2)] Let $r^\prime\leq r$. Let $v\in V(G_1)$ 
+	such that $d(v,X)>2r^\prime+1$, and let
+	$u_1,\dots,u_{k-1}\in V(G_2)$. Then there exists a vertex
+	$u\in V(G_2)$ with $u,v$ having $k$-similar $r^\prime$-neighborhoods 
+	and satisfying $d(u,u_i)>2r^\prime+1$ for all $u_i$'s as well as
+	$d(u,Y)>2r^\prime +1$.
+	\item[(3)] Let $r^\prime\leq r$. Let $u\in V(G_2)$ 
+	such that $d(u,Y)>2r^\prime+1$, and let
+	$v_1,\dots,v_{k-1}\in V(G_1)$. Then there exists a vertex
+	$v\in V(G_1)$ with $v,u$ having $k$-similar $r^\prime$-neighborhoods 
+	and satisfying $d(v,v_i)>2r^\prime+1$ for all $v_i$'s as well as
+	$d(v,X)>2r^\prime +1$.
+\end{enumerate}
+Then Duplicator wins $\ehr_k(G_1,G_2)$.
+\end{theorem}
+
+In order to prove this theorem we need to make two observations
+and prove a previous lemma.
+
+\begin{obs} \label{obs1}
+Let $H_1$, $H_2$ be hypergraphs and 
+$\overbar{v}$, $\overbar{u}$, be lists of vertices
+from $V(H_1)$ and $V(H_2)$ respectively. Suppose that
+Duplicator wins $d\ehr_k(H_1,\overbar{v},H_2,\overbar{u})$.
+Then, for any $r$ Duplicator also wins
+$d\ehr_k(N(\overbar{v};r),\overbar{v},N(\overbar{u};r),\overbar{u})$. 
+In particular, given hypergraphs $G_1, G_2$ and sets
+$X\subseteq V(G_1)$, $Y\subseteq V(G_2)$ such that
+$N(X;r)$ and $N(Y;r)$ are $k$-similar, then for any 
+$r^\prime \leq r$ the graphs
+$N(X;r^\prime)$ and $N(Y;r^\prime)$ are $k$-similar
+as well. 
+\end{obs}
+
+\begin{obs} \label{obs2}
+Let $H_1$, $H_2$ be hypergraphs and 
+$\overbar{v}$, $\overbar{u}$, be lists of vertices
+from $V(H_1)$ and $V(H_2)$ respectively. Suppose 
+Duplicator wins $d\ehr_k(H_1,\overbar{v},H_2,\overbar{u})$. 
+Let $v^\prime\in V(H_1),u^\prime\in V(H_2)$ be vertices
+played in the first round of an instance of the game 
+where Duplicator is following a winning strategy. Then 
+Duplicator also wins $d\ehr_{k-1}(H_1,\overbar{v_2},
+H_2,\overbar{u_2})$, where $\overbar{v_2}:=\overbar{v},v^\prime$
+and $\overbar{u_2}:=\overbar{u},u^\prime$.
+\end{obs}
+
+\begin{lemma} \label{lemm:Duplicator}
+Let $G_1$, $G_2$ be hypergraphs and 
+$\overbar{v}$, $\overbar{u}$, be lists of vertices
+from $V(G_1)$ and $V(G_2)$ respectively. Let
+$r$ be greater than zero. Suppose that
+$N(\overbar{v};3r+1)$ and $N(\overbar{u};3r+1)$ are 
+$k$-similar. Let $v^\prime\in V(G_1),u^\prime\in V(G_2)$
+be vertices played in the first round of an instance of 
+$d\ehr_k(N(\overbar{v};3r+1),\overbar{v},N(\overbar{u};3r+1),\overbar{u})$ 
+where Duplicator is following a winning strategy. Further suppose
+that $d(\overbar{v},v_2)\leq 2r+1$ (and in consequence
+$d(\overbar{u},u_2)\leq 2r+1$ as well). 
+Let $\overbar{v_2}:=\overbar{v},v^\prime$
+and $\overbar{u_2}:=\overbar{u},u^\prime$.
+Then $N(\overbar{v_2};r)$ and $N(\overbar{u_2};r)$ are 
+$(k-1)$-similar
+\end{lemma}
+
+\begin{proof}
+Using \cref{obs2} we get that Duplicator wins 
+\[d\ehr_k(N^{G_1}(\overbar{v};3r+1),\overbar{v_2},N^{G_2}(\overbar{u};3r+1)
+,\overbar{u_2})\]
+as well. Call $H_1=N^{G_1}(\overbar{v};3r+1)$,
+$H_2=N^{G_2}(\overbar{u};3r+1)$. Then by \cref{obs2}
+Duplicator wins
+\[
+d\ehr_k(N^{H_1}(\overbar{v_2};r),\overbar{v_2},N^{H_2}(\overbar{u_2};r),\overbar{u_2}).
+\]
+Because of this if we prove $N^{G_1}(\overbar{v_2};r)
+=N^{H_1}(\overbar{v_2};r)$ and $N^{G_2}(\overbar{u_2};r)
+=N^{H_2}(\overbar{u_2};r)$, then we are finished. 
+Let $z\in N^{G_1}(v^\prime;r)$. Then
+$d(z,\overbar{v})\leq d(z,v^\prime)+d(v^\prime,\overbar{v})=3r+1$.
+In consequence, $N^{G_1}(v;r)\subset H_1$. Thus,
+$N^{G_1}(\overbar{v_2};r)\subseteq H_1$, and $N^{G_1}(\overbar{v_2};r)
+=N^{H_1}(\overbar{v_2};r)$. Analogously we obtain 
+$N^{G_2}(\overbar{u_2};r)=N^{H_2}(\overbar{u_2};r)$, as we wanted. 
+\end{proof}
+
+Now we are in conditions to prove \cref{ThmDuplicator}.
+
+\begin{proof}[Proof of \cref{ThmDuplicator}]
+Define $r_0=0$ and $r_i=3r_{i-1}+1$ for $i>0$.
+Let us denote by $w_i$ and $z_i$ the vertices played
+in $G_1$ and $G_2$ respectively during the $i$-th
+round of $\ehr_k(G_1,G_2)$. 
+%Set 
+%$\overbar{v}[i]:=v_1,\dots,v_i$ and
+%$\overbar{u}[i]:=u_1,\dots,u_i$
+%We say that Duplicator can play following the strategy $S$
+%if they can play in a way that
+%at the end of the $s$-th round, $\overbar{w}[s]$ and
+%$\overbar{z}[s]$ have $(k-s)$-similar $r_{k-s}$-neighborhoods.
+%In particular this means that at the end of the $k$-th
+%round Duplicator will have won $\ehr_k(G_1,G_2)$.
+\par
+
+Let $\overbar{v_1},\dots,\overbar{v_a}$ and 
+$\overbar{u_1},\dots,\overbar{u_b}$ be lists
+forming partitions of 
+$X$ and $Y$ respectively, and assume they
+are as in the definition of $k$-agreeability.
+Set 
+\[\mathcal{X}[0]=\{\overbar{v_1},\dots,\overbar{v_a}\},
+\quad \mathcal{Y}[0]=\{\overbar{u_1},\dots,\overbar{u_b}\}.\]
+That is, $\mathcal{X}[0]$ and $\mathcal{Y}[0]$ are the whose elements
+are the $\overbar{v_i}$'s and $\overbar{u_i}$'s respectively. 
+At the end of the $s$-th round $\mathcal{X}[s-1]$,
+resp. $\mathcal{Y}[s-1]$, will be updated into 
+$\mathcal{X}[s]$,
+resp. $\mathcal{Y}[s]$, by performing on it
+some of the following operations: adding a new list
+to it, appending one vertex to an existing list, and 
+marking a list with the index $s$. Duplicator will
+keep track of the sets $\mathcal{X}[s]$ and $\mathcal{Y}[s]$.\par
+
+We show first an strategy for Duplicator and will prove its
+correctness afterwards. The strategy is as follows: At the 
+beginning of the $s$-th round suppose Spoiler plays $w_s$ in
+$G_1$. The case where they play $z_s$ in $G_2$ is symmetric.
+Call $r=r_{k-s}$. There are three possibilities. 
+\begin{itemize}
+	\item[Case 1:] The vertex $w_s$ satisfies
+	$d(w_s,\overbar{v})>2r+1$ for all 
+	$\overbar{v}\in \mathcal{X}[s-1]$. Then Duplicator 
+	can find a vertex $z_s$ in $G_2$ such that
+	$d(z_s,\overbar{u})>2r+1$ for all 
+	$\overbar{u}\in \mathcal{Y}[s-1]$ satisfying 
+	that $w_s$ and $z_s$ have $(k-s)$-similar
+	$r$-neighborhoods. To form $ \mathcal{X}[s]$
+	and $ \mathcal{Y}[s]$, add to $\mathcal{X}[s-1]$
+	and $ \mathcal{Y}[s-1]$ the lists consisting
+	of only $w_s$ and only $z_s$ respectively, and mark
+	them with the number $s$.
+
+	\item[Case 2:] The vertex $w_s$ satisfies
+	$d(w_s,\overbar{v})\leq 2r+1$ for a unique 
+	$\overbar{v}\in \mathcal{X}[s-1]$,and
+	$\overbar{v}$ is marked. In this case,
+	find the list $\overbar{u}\in \mathcal{Y}[s-1]$
+	with the same mark. Duplicator 
+	then can chose $z_s\in N(\overbar{u},2r+1)$
+	in response to $w_s$ according to a winning strategy
+	for
+	\[
+	d\ehr_{k-s}(N(\overbar{v},3r+1),\overbar{v},
+	N(\overbar{u},3r+1),\overbar{u}).
+	\]
+	To form $ \mathcal{X}[s]$
+	and $ \mathcal{Y}[s]$, append $w_s$ and $z_s$
+	to $\overbar{v}$ and $\overbar{u}$ respectively.
+
+	\item[Case 3:] The vertex $w_s$ satisfies
+	$d(w_s,\overbar{v})\leq 2r+1$ for a unique 
+	$\overbar{v}\in \mathcal{X}[s-1]$,and
+	$\overbar{v}$ is not marked. In this case we 
+	can	find a non-marked 
+	list $\overbar{u}\in \mathcal{Y}[s-1]$
+	such that $\overbar{v}$ and $\overbar{u}$ 
+	have $(k-s)$-similar $(3r+1)$-neighborhoods. 
+	Duplicator then can chose $z_s\in N(\overbar{u},2r+1)$
+	in response to $w_s$ according to a winning strategy
+	for
+	\[
+	d\ehr_{k-s}(N(\overbar{v},3r+1),\overbar{v},
+	N(\overbar{u},3r+1),\overbar{u}).
+	\]
+	To form $ \mathcal{X}[s]$
+	and $ \mathcal{Y}[s]$, append $w_s$ and $z_s$
+	to $\overbar{v}$ and $\overbar{u}$ respectively,
+	and mark those lists with the number $s$. 
+\end{itemize}
+
+All that is left now is to prove the correctness of the
+strategy. We show that at the end the $s$-th round, if 
+two lists $\overbar{v} \in \mathcal{X}[s]$ and 
+$\overbar{u} \in \mathcal{Z}[s]$ have the same mark then
+$\overbar{v}$ and $\overbar{u}$ have $(k-s)$-similar
+$r_{k-s}$-neighborhoods. This happens trivially at
+the end of the zeroth round -i.e., the beginning 
+of the game- as there are no marked lists. Assume the
+statement holds up to the end of the $(s-1)$-th round, 
+where $s>0$.
+
+\begin{itemize}
+	\item[Case 1:] Notice that the lists
+	in $\mathcal{Y}[s-1]$ only contain the
+	vertices previously played in $G_2$ and 
+	the ones from $Y$. Thus, assumption $(3)$ 
+	of the theorem, (or assumption $(2)$ in the 
+	symmetric
+	case where Spoiler plays in $G_2$) assures us
+	that Duplicator can always find such $z_s$ 
+	sufficiently far away from all the other lists. 
+	In this case, the only new marked lists in $\mathcal{X}[s]$
+	and $\mathcal{Y}[s]$ are the ones
+	consisting of $w_s$ and $z_s$ respectively. By assumption
+	$w_s$ and $z_s$ have $(k-s)$-similar $r_{k-s}$-neighborhoods.
+
+	\item[Case 2:] Notice that by the induction hypothesis 
+	$\overbar{v}$ and $\overbar{u}$ have $(k-s+1)$-similar
+	$r_{s-k+1}$-neighborhoods, and in consequence a winning strategy
+	for Duplicator exists. Using \cref{lemm:Duplicator} we obtain 
+	that the extended lists $\overbar{v},w_s$ and $\overbar{u},z_s$
+	have $(k-s)$-similar $r_{s-k}$-neighborhoods.
+
+	\item[Case 3:] This case is analogous to the previous one.
+	The definition of $k$-agreeability implies that there is 
+	such an unmarked list $\overbar{u}$ available. Using \cref{lemm:Duplicator} 
+	we obtain 
+	that the extended lists $\overbar{v},w_s$ and $\overbar{u},z_s$
+	have $(k-s)$-similar $r_{s-k}$-neighborhoods.	
+\end{itemize}
+
+In the three cases, if $\overbar{v}$ and $\overbar{v}$
+are lists in $\mathcal{X}[s-1]$ and $\mathcal{Y}[s-1]$
+respectively that share the same mark and remain unmodified
+in $\mathcal{X}[s]$ and $\mathcal{Y}[s]$, then by the 
+induction hypothesis $\overbar{v}$ and $\overbar{v}$
+have $(k-s+1)$-similar $r_{k-s+1}$-neighborhoods. This
+easily implies that they also have
+$(k-s)$-similar $r_{k-s}$-neighborhoods.\par
+At the end of the game, if $\overbar{v}\in \mathcal{X}[k]$ and 
+$\overbar{u}\in \mathcal{Y}[k]$ are lists with the same mark
+then the natural mapping between $\overbar{v}$ and $\overbar{u}$
+defines an isomorphism between $G_1[\overbar{v}]$ and $G_2[\overbar{u}]$.
+
+\subsection{Outline of the proof}
+
+We show now an outline of the proof. \par 
+We show that for any quantifier rank $k$ there are some classes of graphs 
+$C^k_1,\dots, C^k_{n_k}$ such that
+\begin{itemize}[noitemsep, topsep=0pt]
+	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
+	\item[(2)] a.a.s. any random graph belongs to some of them, and
+	\item[(3)] the limit probability of random graph belonging to any of them is an expression in $\Theta$. 
+\end{itemize}
+
+After this is archived the theorem follows easily. Indeed, let $\phi$ be a sentence 
+in the first order language $\Lan$ of graphs whose quantifier rank is $k$, and denote by
+$G$ a random graph in $G(n,\beta/n)$. \par
+
+The objective of next sections will be to define the classes $C_1,\dots, C_{n_k}$ and to show
+that they satisfy properties (1), (2) and (3). Later we will prove a stronger result, so we will
+allow ourselves to just sketch some of the proofs during this chapter.
+
+%Let $\overbar{v[s]}$, resp. $\overbar{u[s]}$,
+%be the list obtained by joining the marked lists
+%in $\mathcal{X}[s]$, resp. $\mathcal{Y}[s]$, according
+%to the order of their marks. We show that during
+%this strategy, at the end of the $s$-th round
+% $\overbar{v[s]}$ and $\overbar{u[s]}$ have $(k-s)$-similar
+% $r_{k-s}$-neighborhoods. For $s=0$ this is trivially
+%the case, as at the beginning of the game no lists have
+%been marked and both $\overbar{v[s]},\overbar{u[s]}$ are empty.
+%Suppose
+
+\end{proof}
+
+%variables
+%
+%and , 
+%an instance of $x$ in $\phi$ is called bounded if it occurs within the 
+%scope of a quantifier bounding it (i.e. it occurs in a sub-formula of
+%$\phi$ of the form $\forall x(\psi)$ or $\exists x (\psi)$). 
+%free if $\phi$ contains an instance of $x$ that is 
+%It is specially relevant the case where $\sigma$ contains a unique
+%relation $R$ symbol with arity two. In this case two important classes
+%of relational structures are the class of posets- i.e. those structures
+%where the relation is anti-symmetric, transitive and anti-reflexive- and 
+%graphs- i.e. those where the relation is symmetric and
+%anti-reflexive. Elements of a graph's universe are called vertices
+%and pairs of related vertices are called edges. \par
+%
+%The relatively simpler structure of the binary relation in the 
+%family of graphs allows to easily enumerate (labeled) graph with
+%a given number of vertices and count how many among them have some
+%fixed number of edges. In effect, in a graph each pair of (different)
+%vertices can either form an edge or not with total independence. Thus,
+%there can be $2^{\binom{n}{2}}$ graphs with $n$ vertices and 
+%$\binom{\binom{n}{2}}{m}$ of those have exactly $m$ edges. \par
+%
+%These kind of considerations make probability spaces over graphs
+%easier to define and to deal with compared with other relational
+%structures such as posets. Among the first of such constructions 
+%to be studied are the random models of graphs $\mathrm{G}(n,m)$ 
+%and $\mathrm{G}(n,p)$ introduced by Erd\H{o}s and R\'enyi and 
+%by Gilbert respectively. \par
+%
+%Given a natural number $n$, we denote by $[n]$ the set $\{1,\dots,n\}$.
+%The model $\mathrm{G}(n,m)$, with $n$ and $m$ natural numbers,
+% is the discrete probability space
+%over the set of all graphs with $m$ edges and $[n]$ as their vertex
+%set in where the uniform probability distribution is chosen. 
+%The model $\mathrm{G}(n,p)$, with $n$ a natural number and 
+%$0\leq p \leq 1$ in the real numbers, is the discrete probability space over
+%the set of all graphs whose vertex set is $[n]$ in where each graph 
+%with $m$ edges has probability $p^m(1-p)^{\binom{n}{2}-m}$.\par
+%
+%Although early on random models of graphs were used as tools to solve 
+%other problems such as constructing graphs with large girth and large
+%chromatic number or providing lower bounds for Ramsey numbers, later 
+%they began to be studied as objects interesting in their own right.
+%A problem in this field is to determine whether the asymptotic probability
+%of a property exists or not in a given model of random graphs. For example,
+%in the model $\mathrm{G}(n,p)$, if we take $p=p(n)$ a fixed function on $n$, 
+%we want to know for which graph properties $P$ the limit of 
+%\( \mathrm{Pr}\big( \mathrm{G}(n,p(n)) \text{ satisfies } P \big) \) exists as
+%$n$ tends to infinity. \par
+%
+%A way to study this problem that has proven to be fruitful is to classify
+%graph properties according to the logical languages they can be defined 
+%in. We say that a sequence of random graphs $(G_n)_n$ obeys a
+%\textit{convergence law}
+%with respect to some logical language $\mathcal{L}$ if for any sentence
+%$\phi$ in $\mathcal{L}$ the probability that $G_n$ satisfies $\phi$ tends
+%to some limit as $n$ tends to infinity. We say that $(G_n)_n$ obeys a 
+%\textit{zero-one law} with respect to $\mathcal{L}$ if that limit is always
+%either zero or one.  \par
+%
+%The usual example of logical language is the \textit{first order (FO) language 
+%of graphs}. Here formulas are composed of variables $x,y,z, \dots$ ranging over
+%vertices, the adjacency relation symbol $R$, Boolean connectives 
+%$\wedge, \vee, \neg, \implies, \dots$, the universal $\forall$ and 
+%existential $\exists$ quantifiers and the parentheses $)$, $($. 
+%Other examples
+%of logical languages for graphs include higher order logics such as the 
+%\textit{second order (SO) language of graphs} or fragments of those such as
+%the \textit{monadic second order (MSO) language of graphs} or 
+%the \textit{existential second order (ESO) language of graphs}. \par
+%
+%Convergence laws for FO logic in the binomial model $\mathrm{G}(n,p)$
+%have been extensively studied. A classical result in this area is due to 
+%Fagin (REF) and states that $\mathrm{G}(n,p)$ obeys a zero-one law with
+%respect to FO logic when $0\leq p \leq 1$ is a fixed constant. By then
+%it was speculated that for all ``sufficiently nice" functions $p(n)$
+%tending to zero as $n$ tends to infinity the model $\mathrm{G}(n,p(n))$
+%would obey at least a convergence law with respect to FO logic. However,
+%this intuition was proven wrong in a remarkable article by Shelah and 
+%Spencer REF. Among other results, there was proven that for 
+%$\alpha\in (0,1)$ the model $\mathrm{G}(n,n^{-\alpha})$ satisfies a 
+%zero-one law with respect to FO logic if and only if $\alpha$ is irrational.
+%Furthermore, if $\alpha\in (0,1)$ is rational then 
+%$\mathrm{G}(n,n^{-\alpha})$ does not even obey a convergence law for FO
+%logic. \par
+%This strange behavior of the rational powers of $n$ is suddenly
+%interrupted at $n^{-1}$. In REF Lynch proved the following result 
+%
+%This is in fact a weaker version of theorem 2.1 in the mentioned
+%article. In there is given a characterization of the family functions
+%of the form $F_\phi$. The analyticity of the $F_\phi$'s is 
+%a consequence of this characterization. \par
+%In $\mathrm{G}(n,p)$ the regime where $p(n)=\beta n^{-1}$ is called
+%sparse. In there the number of edges in a random graph is approximately
+%$\frac{beta}{2}n$. Many interesting phenomena occur in this regime, being
+%the most notable one the sudden appearance of a unique giant connected 
+%component when $\beta$ is greater than one REF.  
+%The goal of this article is to generalize this result from Lynch to
+%other families of relational structures different form the family of 
+%graphs that still share the desirable properties that allow for a 
+%natural definition of binomial random model. \par
+%
+%A particular case of those are the families of $k$-uniform
+%(labeled) hyper-graphs for $k$ a natural number. These are formed
+%by a set of vertices and a set of edges where each edge is a set of 
+%exactly $k$ vertices. A random hyper-graph in the binomial model of 
+%random $k$-uniform hyper-graphs $\mathrm{G}_k(n,p)$ has vertex set $[n]$ 
+%and contains each possible edge with probability $p$ independently, 
+%analogously to the model $\mathrm{G}(n,p)$. In particular
+%$\mathrm{G}_2(n,p)$ is the same model as $\mathrm{G}(n,p)$. \par
+%A number of results about the binomial random model for graphs have 
+%been generalized to $\mathrm{G}_k(n,p)$. Some analogous for convergence
+%and zero-one laws for the FO language of $k$-uniform hyper-graphs have
+%been obtained REFS. The sparse regime in this model occurs when 
+%$p$ is of the form $p(n)=\beta n^{-k+1}$. This way the expected total 
+%number of edges in a random hyper-graph grows linearly with $n$, and the
+%model shares many similarities with $\mathrm{G}(n,cn^{-1})$. 
+%In REF, among other results, it is proven that
+%$\mathrm{G}_k(n,p)$ obeys a convergence law for FO logic when
+%$p=\beta n^{k-1}$.
+%
 
@@
 
-The first order language with signature $\sigma$ deals with strings
-of symbols taken from the alphabet consisting of
- variable symbols $x_1,\dots,x_m,\dots$, the symbols in $\sigma$,
-the logical connectives $\neg, \wedge, \vee$,
-the universal $\forall$ and existential $\exists$ quantifiers,
-the equality symbol, and the parentheses $),($.
-A first order formula is a string obtained after applying the
-following set of rules a finite number of times: 
-\begin{enumerate}[label=(\Roman*),itemsep=0pt, topsep=0pt]
-	\item If $x_1,x_2$ are variables then $x_1=x_2$ is a formula.
-	\item If $R_i$ is a relation symbol in $\sigma$ with arity $a_i$,
-	and $t_1,\dots, t_{a_i}$ are terms then 
-	$R_i(t_1,\dots,t_{a_i})$ is a formula.
-	\item If $\varphi$ and $\psi$ are formulas, then both
-	$(\varphi \wedge \psi)$ and $(\varphi \vee \psi)$ are formulas.
-	\item If $\varphi$ is a formula then $\neq \varphi$ is also 
-	a formula.
-	\item If $\varphi$ is a formula and $x$ is a variable then both
-	$\forall x \varphi$ and $\exists x\varphi$ are formulas. 
-\end{enumerate}
-
-Let $\varphi$ be a first order formula. An occurrence of a variable 
-in $\varphi$ is called bounded if it is within the scope of
-a quantifier binding it, and is called free otherwise. We
-will assume that the occurrences of any given variable in a first
-order sentence are either all free or all bounded. 
-We will use the notation $\varphi(x_1,\dots, x_n)$ to indicate
-that $x_1, \dots, x_n$ are distinct and they are the free variables
-(i.e. the variables whose occurrences are all free) 
-in $\varphi$. A formula with no free variables is called a sentence,
-and a formula whose variables are all free is called open.
-
-Let $\mathfrak{A}$ be a $\sigma$-structure and $\varphi(x_1,\dots,x_n)$ 
-be a first order sentence. Given a map $\alpha$ from the set
-of free variables $\{x_1,\dots,x_n\}$ to the universe $A$ 
-of $\mathfrak{A}$ we define the relation 
-$\mathfrak{A} \models \varphi[\alpha]$, "$\alpha$ satisfies $\phi$ in $\mathfrak{A}$",
-in the following way:
-\begin{enumerate}[label=(\Roman*),itemsep=0pt, topsep=0pt]
-	\item 
-	\item If $R_i$ is a relation symbol in $\sigma$ with arity $a_i$,
-	and $t_1,\dots, t_{a_i}$ are terms then 
-	$R_i(t_1,\dots,t_{a_i})$ is a formula.
-	\item If $\varphi$ and $\psi$ are formulas, then both
-	$(\varphi \wedge \psi)$ and $(\varphi \vee \psi)$ are formulas.
-	\item If $\varphi$ is a formula then $\neq \varphi$ is also 
-	a formula.
-	\item If $\varphi$ is a formula and $x$ is a variable then both
-	$\forall x \varphi$ and $\exists x\varphi$ are formulas. 
-\end{enumerate}
+%The first order language with signature $\sigma$ deals with strings
+%of symbols taken from the alphabet consisting of
+% variable symbols $x_1,\dots,x_m,\dots$, the symbols in $\sigma$,
+%the logical connectives $\neg, \wedge, \vee$,
+%the universal $\forall$ and existential $\exists$ quantifiers,
+%the equality symbol, and the parentheses $),($.
+%A first order formula is a string obtained after applying the
+%following set of rules a finite number of times: 
+%\begin{enumerate}[label=(\Roman*),itemsep=0pt, topsep=0pt]
+%	\item If $x_1,x_2$ are variables then $x_1=x_2$ is a formula.
+%	\item If $R_i$ is a relation symbol in $\sigma$ with arity $a_i$,
+%	and $t_1,\dots, t_{a_i}$ are terms then 
+%	$R_i(t_1,\dots,t_{a_i})$ is a formula.
+%	\item If $\varphi$ and $\psi$ are formulas, then both
+%	$(\varphi \wedge \psi)$ and $(\varphi \vee \psi)$ are formulas.
+%	\item If $\varphi$ is a formula then $\neq \varphi$ is also 
+%	a formula.
+%	\item If $\varphi$ is a formula and $x$ is a variable then both
+%	$\forall x \varphi$ and $\exists x\varphi$ are formulas. 
+%\end{enumerate} 
+%
+%Let $\varphi$ be a first order formula. An occurrence of a variable 
+%in $\varphi$ is called bounded if it is within the scope of
+%a quantifier binding it, and is called free otherwise. We
+%will assume that the occurrences of any given variable in a first
+%order sentence are either all free or all bounded. 
+%We will use the notation $\varphi(x_1,\dots, x_n)$ to indicate
+%that $x_1, \dots, x_n$ are distinct and they are the free variables
+%(i.e. the variables whose occurrences are all free) 
+%in $\varphi$. A formula with no free variables is called a sentence,
+%and a formula whose variables are all free is called open.
+%
+%Let $\mathfrak{A}$ be a $\sigma$-structure and $\varphi(x_1,\dots,x_n)$ 
+%be a first order sentence. Given a map $\alpha$ from the set
+%of free variables $\{x_1,\dots,x_n\}$ to the universe $A$ 
+%of $\mathfrak{A}$ we define the relation 
+%$\mathfrak{A} \models \varphi[\alpha]$, "$\alpha$ satisfies $\phi$ in $\mathfrak{A}$",
+%in the following way:
+%\begin{enumerate}[label=(\Roman*),itemsep=0pt, topsep=0pt]
+%	\item 
+%	\item If $R_i$ is a relation symbol in $\sigma$ with arity $a_i$,
+%	and $t_1,\dots, t_{a_i}$ are terms then 
+%	$R_i(t_1,\dots,t_{a_i})$ is a formula.
+%	\item If $\varphi$ and $\psi$ are formulas, then both
+%	$(\varphi \wedge \psi)$ and $(\varphi \vee \psi)$ are formulas.
+%	\item If $\varphi$ is a formula then $\neq \varphi$ is also 
+%	a formula.
+%	\item If $\varphi$ is a formula and $x$ is a variable then both
+%	$\forall x \varphi$ and $\exists x\varphi$ are formulas. 
+%\end{enumerate} 
+%
+%
 
@@
 
+\pagebreak
+\bibliography{biblio}
+\bibliographystyle{unsrt}	
 \end{document}

### 2020-01-08 Article.tex

@@
 \newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
-\newcommand{\morph}[1]{\stackrel{#1}{\simeq}}
+\newcommand{\morph}[1]{\simeq_#1}
 \newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
@@
 $\overbar{y}$ are interpreted as the elements in $\overbar{a}$.
+\todo[inline]{Deber\'a al menos mencionar un par de trabajos que estudien random k-SAT y propiedades a.a.s suficientes para no-satisfacibilidad}
 
@@
 \begin{itemize}
-	\item Positive natural numbers $t$, $\overbar{a}=a_1,\dots, a_t$.\
+	\item Positive natural numbers $t$, $\overbar{a}=a_1,\dots, a_t$, with 
+	all the $a_i$'s greater than $1$.\
 
@@
 
-We define the class $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$ as the 
+We will only consider relational structures where the relations
+are of arity at least two. This restriction is not necessary, but 
+it makes notation easier. 
+\todo[inline]{Quiz\'as deber\'ia a\~nadir un anexo dando alguna indicaci\'on sobre c\'omo tratar las relaciones unarias?}
+
+%We will denote by $t_u$ the, possibly zero,
+%amount of unary
+%relation symbols in $\sigma$. 
+%For the sake of convenience we may assume that $R_i$'s are
+%ordered in such a way that the unary relation symbols, if any, 
+%are the first ones $R_1,\dots, R_{t_u}$. This will
+%become relevant later. \par
+
+We define the class $\mathcal{C}$ as the 
 class of $\sigma$-structures that
@@
 \begin{definition} 
-Let $V$ be a set. A \textbf{ multi-hypergraph with
-vertex set $V$, $t$ edge sets, with edge sizes given by $\overbar{a}$,
-symmetry groups $\overbar{\Phi}$, and anti-reflexivity restrictions $\overbar{P}$}
-is a pair $G=(V,\overbar{E})$, where $\overbar{E}=E_1,\dots, E_t$ and
-for each $i$, $E_i \subseteq E^{V}_{a_i,\Phi_i,P_i}$.
+A \textbf{ multi-hypergraph with
+with $t$ edge sets, edge sizes given by
+$\overbar{a}$,
+symmetry groups $\overbar{\Phi}$, 
+and anti-reflexivity restrictions $\overbar{P}$}
+is a pair $G=(V(G),\overbar{E(G)})$,
+where $\overbar{E(G)}=E_1(G),\dots, E_t(G)$ and
+for each $i$, $E_i(G) \subseteq E^{V}_{a_i,\Phi_i,P_i}$.
 \end{definition}
 
-For the sake of word economy the expression ``multi-hypergraph with
-vertex set $V$, $t$ edge sets, with edge sizes given by $\overbar{a}$,
-symmetry groups $\overbar{\Phi}$, and anti-reflexivity restrictions $\overbar{P}$" 
-will be replaced simply by ``hypergraph". The word ``hypergraph" will not hold
-any other meaning than this for the rest of this writing except for the places
+For the sake of word economy the expression 
+``multi-hypergraph with
+$t$ edge sets, with edge sizes given by $\overbar{a}$,
+symmetry groups $\overbar{\Phi}$, and anti-reflexivity 
+restrictions $\overbar{P}$" 
+will be replaced simply by ``hypergraph ". The word 
+``hypergraph" will not hold
+any other meaning than this for the rest 
+of this writing except for the places
 where it is explicitly stated.  \par
 
-Hypergraphs, as we have defined them, can be naturally interpreted as
-structures from $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$ in the following way: 
+Hypergraphs, as we have defined them, 
+can be naturally interpreted as
+structures from $\mathcal{C}^
+{\sigma}_{\overbar{\Phi},\overbar{P}}$ 
+in the following way: 
 given $G=(V,\overbar{E})$,
-we consider $V$ to be the universe of $G$, and for any $i$ we define
+we consider $V$ to be the universe of
+ $G$, and for any $i$ we define
 $R_i^G\subseteq V^{a_i}$ as the set such that
-$(\overbar{x})\in V^{a_i}$, $(\overbar{x})\in R_i^G$ if and only if 
-$[\overbar{x}]\in E_i$. Under this interpretation hypergraphs, by definition,
-satisfy the symmetry and anti-reflexivity axioms given above. It is also easy to
-see that this interpretation induces a one-to-one identification between 
-structures in $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$ and hypergraphs. \par
+$(\overbar{x})\in V^{a_i}$, 
+$(\overbar{x})\in R_i^G$ if and only if 
+$[\overbar{x}]\in E_i$. Under 
+this interpretation hypergraphs, by definition,
+satisfy the symmetry and anti-reflexivity
+axioms given above. It is also easy to
+see that this interpretation induces
+a one-to-one identification between 
+structures in $\mathcal{C}^{\sigma}_{\overbar{\Phi}
+,\overbar{P}}$ and hypergraphs. \par
+
+We will use standard nomenclature and notation
+from graph theory. This way, we will call vertex set
+to $V(G)$ and vertices to its elements. Likewise, each of 
+the $E_i(G)$'s will be called an edge set and its elements, 
+edges. Given an edge set $E_i(G)$, the index $i$ will
+be called its color, and the number
+$a_i$ its size. Thus, we will say that
+an edge $e\in E_i(G)$ has color $i$ and size
+$a_i$.
+
+Given a set of vertices $U\subseteq V(G)$, 
+we will denote by $G[U]$ the hypergraph induced
+by $G$ on $U$. That is, $G[U]$ is an hypergraph
+$H=(V(H),\overbar{E(H)})$ such that $V(H)=U$ and
+for any list $\overbar{v}$ of vertices in $U$,
+$[\overbar{v}]\in E_i(H)$ if and only if 
+$[\overbar{v}]\in E_i(G)$.
+\par
+
+An homomorphism between two hypergraphs $G$ and $H$ 
+a map $f:V(G)\rightarrow V(H)$ that sends edges 
+from $G$ to edges in $H$ of the same color. That is,
+if vertices $v_1,\dots, v_{a_i}$ form an edge 
+$[v_1,\dots,v_{a_i}]\in E_i(G)$, then
+$[f(v_1),\dots,f(v_{a_i})]\in E_i(H)$.
+If $f$ is injective then it is called a monomorphism. 
+If $f$ is bijective and its inverse is also an homomorphism 
+between $H$ and $G$ then $f$ is called an isomorphism.\par
+
+The group of automorphisms $Aut(G)$ of an hypergraph $G$ is the group
+of isomorphisms between $G$ and itself. 
+\par
+
+Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is
+
+The excess $ex(G)$ of an hypergraph $G$ is the number
+\[
+ex(G)= \big(\sum_{i=1}^{t} (a_i-1)|E_i(G)|\big) - |V(G)|.  
+\] 
+That is, the excess of $G$ is its "weighted number of edges"
+minus its number of vertices. Here the "weighted number of edges"
+in $G$ the sum of the weight of all its edges, where the
+weight of an edge is its size minus one.
 
@@
 
-Let $\overbar{p}:=p_1\dots,p_t$.
+Let $p_1\dots,p_t$ real numbers between zero and one,
+and let $\overbar{p}=p_1,\dots,p_t$.
 The random model $G^{\mathcal{C}}(n,\overbar{p})$ 
@@
 assigning to each edge with color $i$,  
-$e\in  E^{[n]}_{a_i,\Phi_i,P_i}$ probability $p_i$ independently.
+$e\in  E^{[n]}_{a_i,\Phi_i,P_i}$ probability 
+$p_i$ independently. \par
+
+%Let $G_n$ denote a random hypergraph in 
+%$G^\mathcal{C}(n,\overbar{p})$, where 
+%$\bar{p}:=p_1,\dots,p_t$, and 
+%we allow each $p_i$ to depend on $n$. 
+As in the case of Lynch's theorem, we are interested in the
+"sparse regime" of $G^\mathcal{C}(n,\overbar{p})$, were the 
+expected number of edges each color is linear. 
+%In other words, we want that
+%$\mathrm{E}[m_i(G_n)]=\Theta(n)$ for all $i$'s.
+This is achieved when each of the $p_i$'s are 
+of the form $\beta_i/n^{a_i-1}$ for some 
+non-negative real numbers $\beta_1,\dots,\beta_t$.
+Let $\overbar{\beta}:=\beta_1,\dots,\beta_t$.
+We will write $\overbar{p}(n,\overbar{\beta})$ to denote 
+the list $\beta_1/n^{a_1-1},\dots, \beta_t/n^{a_t-1}$.
+We will treat
+the parameters $\beta_1,\dots, \beta_t$ as fixed
+real constants for the most part and will abbreviate 
+$\overbar{p}(n,\overbar{\beta})$ as $\overbar{p}(n)$.\par
+
+Our goal is to prove the following theorem:
+%is to prove that for any sentence $\phi\in FO[\sigma]$,
+%the limit 
+%\[\Ln \mathrm{Pr}(G^\mathcal{C}(n,\overbar{p}
+%(n,\overbar{\beta})) \models \phi)\] 
+%is well defined and varies 
+%analytically with $\overbar{\beta}$.
+% Some care is needed
+%in order to formulate this precisely, as there are some values
+%of $\overbar{\beta}$ for which $\overbar{p}
+%(n,\overbar{\beta})$ asymptotically does not 
+%define a list of 
+%proper probabilities. 
+%Indeed, suppose that some relation
+%symbol $R_i$ in $\sigma$ is unary. 
+%Then, by definition $a_i=1$ and
+%the expression $\beta_i/n^{a_i-1}$ 
+%equals $\beta_i$. 
+%In consequence, if we assign 
+%values to $\overbar{\beta}$ and let
+%$\beta_i>1$ then the random 
+%model $G^\mathcal{C}(n,\overbar{p}
+%(n,\overbar{\beta})$ will not be well defined. 
+%To avoid this we need to impose $\beta_i\in [0,1]$ 
+%for all the $i$'s such that $a_i=1$. \par
+%For the sake of convenience we will adopt the convention
+%that the unary relation symbols among $R_1,\dots,R_t$ 
+%are the first ones, and we will denote by $t_u$ the 
+%(possibly zero) number of such relations. 
+%Thus $a_1= a_2 =\dots= a_{t_0}=1$, and $a_i>1$ 
+%for $i>t_0$. Now we are in conditions of stating our main 
+%theorem:
+
+\begin{theorem} \label{thm:main}
+	Let $\phi$ be a sentence in $FO[\sigma]$. Then
+	the function
+	%$F_\phi: [0,1]^{t_u}\times [0,\infty)^{t-t_u}
+	$F_\phi: [0,\infty)^{t}
+	\rightarrow \R$ given by 
+	\[
+	\overbar{\beta} \mapsto \Ln Pr\big( G^\mathcal{C}(n,\overbar{p}
+	(n,\overbar{\beta})) \models \phi\big)
+	\]
+	is well defined and analytic. 
+\end{theorem}
 
@@
 $\ehr_k(G_1,\overbar{v},G_2,\overbar{u})$.
+
+\subsection{Outline of the proof}
+
+We show now an outline of the proof. \par 
+We show that for any quantifier rank $k$ there are some classes of
+hypergraphs 
+$C^k_1,\dots, C^k_{n_k}$ such that
+\begin{itemize}[noitemsep, topsep=0pt]
+	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
+	\item[(2)] a.a.s. any random graph belongs to some of them, and
+	\item[(3)] the limit probability of random graph belonging to any of them is an analytic expression on the parameters $\overbar{\beta}$. 
+\end{itemize}
+
+After this is archived the theorem follows easily.
+
+The objective of next sections will be to define the classes $C_1,\dots, C_{n_k}$ and to show that they satisfy properties (1), (2) and (3).
+
+\todo[inline]{Explicar esto mejor}
 
@@
 	defines an isomorphism between $G_1[\overbar{v}]$ and $G_2[\overbar{u}]$.
-
-\subsection{Outline of the proof}
-
-We show now an outline of the proof. \par 
-We show that for any quantifier rank $k$ there are some classes of graphs 
-$C^k_1,\dots, C^k_{n_k}$ such that
-\begin{itemize}[noitemsep, topsep=0pt]
-	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
-	\item[(2)] a.a.s. any random graph belongs to some of them, and
-	\item[(3)] the limit probability of random graph belonging to any of them is an expression in $\Theta$. 
+\end{proof}
+
+\todo[inline]{Quiz\'as reordenando esta demostraci\'on se puede acortar o se entiende mejor.}
+
+\subsection{Types of trees}
+
+We define tree $T$ as a connected hypergraph such that
+$ex(T)=-1$. We define a vertex-rooted tree $(T,v)$ 
+as a tree $T$ with a 
+distinguished vertex $v\in V(T)$ called its root. We will
+usually omit the root when it is not relevant and 
+write just $T$ instead of $(T,v)$. We define the set
+of initial edges of a vertex-rooted tree $(T,v)$ as the
+set of edges in $T$ that contain $v$. \par
+%
+%Similarly, we define an edge-rooted tree $(T,e,v)$
+%as a tree $T$ with a distinguished edge $e\in E(T)$ and
+%a distinguished vertex $v\in e$. \par
+Given a rooted tree $(T, v)$, and a vertex $u\in V(T)$, 
+we define $Tree_{(T,v)}(u)$ as the tree $T[X]$ induced on the
+set $X:=\{ \, w\in V(T) \, | \, d(v,w)=d(v,u)+ d(u,w) \,  \}
+$, to which we assign $u$ as the root.
+That is, $Tree_{(T,v)}(u)$ is the tree consisting of those vertices
+whose only path to $v$ contains $u$.
+\par
+We define the radius of a vertex-rooted, or edge-rooted,
+tree as the maximum distance between its marked
+vertex and any other one. \par
+
+Fix a natural number $k$. We will define 
+two equivalence relations, one between 
+rooted trees and another between pairs
+$(T,e)$ of rooted trees $T$ and initial edges
+$e\in E(T)$. We will name both relations
+$k$-equivalence relations and
+denote them by $\morph{k}$. 
+They are defined recursively as follows:
+
+\begin{itemize}
+	\item Any two trees with radius zero are $k$-equivalent 
+	.Notice that those trees
+	consist only of one vertex, their respective roots.
+	\item Suppose that the $k$-equivalence relation has been
+	defined for rooted trees with radius at most $r$.
+	\begin{itemize}
+		\item Let $T_1$ and $T_2$ be rooted trees with radius
+		at most $r+1$, and let $e_1, e_2$
+		be initial edges of $T_1$ and $T_2$ respectively.
+		Then $(T_1,e_1)\simeq_k (T_2,e_2)$ if
+		$e_1$ and $e_2$ have the same color and there is a bijection 
+		$f: e_1\rightarrow e_2$ between the vertices in $e_1$ and
+		$e_2$ such that:
+		\begin{itemize}
+			\item If $e_1=[u_1,\dots, u_a]$ then $e_2=[f(u_1),\dots,f(u_a)]$.
+			\item If $v_1$ and $v_2$ are the roots of
+			$T_1$ and $T_2$ respectively, then $v_2=f(v_1)$.
+			\item For any vertex different from the root $u\in e_1$, it is satisfied that
+			\[Tree_{(T_1,v_1)}(u)\morph{k} Tree_{(T_2,v_2)}(f(u)).\]
 		\end{itemize}
-
-After this is archived the theorem follows easily. Indeed, let $\phi$ be a sentence 
-in the first order language $\Lan$ of graphs whose quantifier rank is $k$, and denote by
-$G$ a random graph in $G(n,\beta/n)$. \par
-
-The objective of next sections will be to define the classes $C_1,\dots, C_{n_k}$ and to show
-that they satisfy properties (1), (2) and (3). Later we will prove a stronger result, so we will
-allow ourselves to just sketch some of the proofs during this chapter.
+		\item Let $T_1$ and $T_2$ be rooted trees with
+		radius at most $r+1$. Then $T_1\morph{k} T_2$ if
+		for any chosen $T=T_1$ or $T=T_2$ and any initial edge
+		$e\in E(T)$, the "quantity 
+		of initial edges $e_1$ from $T_1$ that satisfy
+		$(T_1,e_1)\simeq_k (T, e)$" and the "quantity 
+		of initial edges $e_2$ from $T_2$ that satisfy
+		$(T_2,e_2)\simeq_k (T, e)$" are the same or 
+		are both greater than $k-1$.
+
+	\end{itemize}
+\end{itemize}
+
+We want prove the following
+\begin{theorem} \label{thm:equivalenttrees} 
+	Let $(T_1,v_1)$ and $(T_2,v_2)$ be rooted trees.
+	Then, if they are $k$-equivalent Duplicator wins
+	$d\ehr_{k}(T_1,v_1,T_2,v_2)$.
+\end{theorem}
+
+Before proceeding with the proof that we need an auxiliary
+result. Let $(T,v)$ be a rooted tree and $e$ an 
+initial edge of $T$. We define $Tree_{(T_v)}(e)$ as
+the induced tree $T[X]$ on the set
+$X:=\{v\} \cup \{\, u\in V(T) \, | \, d(v,u) = |e| + d(e,v) \,\}$,
+to which we assign $v$ as the root. In other words, 
+$Tree_{(T_v)}(e)$ is the tree formed of $v$ and all the vertices
+in $T$ whose only path to $v$ contain $e$. 
+Now we can check the following:
+
+\begin{lemma} \label{lem:equivalentedges}
+	Fix $r>0$. Suppose that theorem \ref{thm:equivalenttrees}
+	holds for rooted trees with radii at most $r$.
+	Let $(T_1,v_1)$ and $(T_2,v_2)$ be rooted trees with radii
+	at most $r+1$. Let $e_1$ and $e_2$ be initial edges 
+	of $T_1$ and $T_2$ respectively satisfying 
+	$(T_1,e_1)\simeq_k (T_2,e_2)$. Name 
+	$T^\prime_1=Tree_{(T_1,v_1)}(e_1)$ and 
+	$T^\prime_2=Tree_{(T_2,v_2)}(e_2)$. Then
+	Duplicator wins $d\ehr{k}(T^\prime_1, v_1, T^\prime_2,v_2)$.
+\end{lemma}
+\begin{proof}
+	We show a winning strategy for Duplicator. 
+	Suppose that in the $i$-th round of the game Spoiler
+	plays on $T^\prime_1$. The other case is symmetric. Let
+	$f:e_1\rightarrow e_2$ be a bijection as in the definition
+	of $(T_1,e_1)\simeq_k (T_2,e_2)$. There are two possibilities:
+	\begin{itemize}
+		\item If Spoiler plays a vertex $v$ on $e_1$ 
+		then Duplicator can play $f(v)$ on $e_2$. 
+		\item Otherwise, Spoiler plays a vertex $v$ that belongs
+		to some $Tree_{(T^\prime_1,v_1)}(u)$ for a unique $u\in e_1$
+		different from the root $v_1$.
+		By the definition of $(T_1,e_1)\simeq_k (T_2,e_2)$,
+		$Tree_{(T^\prime_1,v_1)}(u)\simeq_k 
+		Tree_{(T^\prime_2,v_2)}(f(u))$. As both these trees
+		have radii at most $r$, by assumption Duplicator has a winning 
+		strategy between them and they can follow it.		
+	\end{itemize}
+\end{proof}
+
+Now we can prove the main theorem of this section:
+
+\begin{proof}[Proof of \cref{thm:equivalenttrees}]~ \par
+	Notice that, as $T_1\morph{k} T_2$, both $T_1$ and
+	$T_2$ have the same radius $r$.
+	We prove the result by induction on $r$.
+	If $r=0$ then both $T_1$ and $T_2$ consist
+	of only one vertex and we are done. \par
+	Now let $r>0$ and assume that the 
+	statement is true for all lesser values of $r$.
+	We will show that there is a winning strategy 
+	for Duplicator in
+	$d\ehr_k(T_1,v_1,T_2,v_2)$.
+	At the start of the game, set all the initial edges
+	in $T_1$ and $T_2$ as non-marked. 
+	Suppose that in the $i$-th round Spoiler plays in 
+	$T_1$. The other case is symmetric. 
+	\begin{itemize}
+		\item If Spoiler plays $v_1$ then Duplicator plays $v_2$.
+		\item Otherwise, the vertex played by Spoiler belongs to
+		$Tree_{(T_1,v_1)}(e_1)$
+		for a unique initial edge $e_1$ of $T_1$. 
+		There are two possibilities:
+		\begin{itemize}
+			\item If $e_1$ is not marked yet, mark it with
+			the index $i$. In this case, there is a 
+			non-marked initial
+			edge $e_2$ in $T_2$ satisfying 
+			$(T_1,e_1)\simeq_k (T_2,e_2)$.
+			Mark $e_2$ with the index $i$ as well. 
+			Because of
+			\cref{lem:equivalentedges}, Duplicator
+			has a winning strategy in
+			\[d\ehr{k}(Tree_{T_1}(e_1), v_1, 
+			Tree_{T_1}(e_2),v_2)\] and can play according to it.
+			\item If $e_1$ is already marked then there is
+			a unique initial edge $e_2$ in $T_2$ marked with 
+			the same mark as $e_1$ and 	
+			$(T_1,e_1)\simeq_k (T_2,e_2)$. Again, 
+			Because of
+			\cref{lem:equivalentedges}, Duplicator
+			has a winning strategy in
+			\[d\ehr{k}(Tree_{T_1}(e_1), v_1, 
+			Tree_{T_1}(e_2),v_2)\] and can
+			continue playing 
+			according to it.
+
+		\end{itemize}
+		Then Duplicator can find an initial 
+		edge $e_2$ of $T_2$ such that
+		$(T_1,e_1)\simeq_k (T_2,e_2)$.
+		Because of
+		\cref{lem:equivalentedges}, Duplicator
+		has a winning strategy in
+		$d\ehr{k}(Tree_{T_1}(e_1), v_1, 
+		Tree_{T_1}(e_2),v_2) $ and can play according to it.
+	\end{itemize}
+
+\end{proof}
+\todo[inline]{probablemente con alg\'un dibujo sencillo esta demostraci\'on se entienda mejor}
+
+\subsection{Probabilistic results}
+
+Given a natural numbers $n$ and $l$ we will use 
+$(n)_l$ to denote 
+$n(n-1)\cdots (n-l+1)$ or $1$ if $l=0$.
+
+Our main tool for computing probabilities will be
+the following multivariate version of Brun's Sieve 
+CITA REQUERIDA
+
+\begin{theorem}
+	Fix $k\in \N$. For each 
+	$n\in \N$, let $X_{1,n},\dots, X_{k,n}$ be non-negative
+	random integer variables over the same
+	probability space. Let $\lambda_1,\dots,\lambda_l$ 
+	be real numbers. Suppose that for any $r_1,\dots,r_l \in \N$
+	\[ 
+	\Ln \mathrm{E}\big[
+	\prod_{i=1}^{k} (X_{i,n})_{r_i} \big]
+	= \prod_{i=1}^{k} \frac{\lambda_i}{r_i !}.	
+	\]
+	Then the $X_{1,n},\dots,X_{k,n}$ converge in distribution to
+	independent Poisson variables with means $\lambda_1,\dots,\lambda_k$ 
+	respectively. 
+\end{theorem}
+
+\subsection{Almost all hypergraphs are simple}
+
+We say that a connected hypergraph $G$ is \textbf{dense} if
+$ex(G)>0$.
+We want to show that a.a.s any sub-hypergraph 
+of $\mathrm{G}^\mathcal{C}(n,\overbar{p})$ whose
+diameter is small (i.e. bounded by some constant)
+is not dense. \par
+It takes a direct computation to show that given
+an hypergraph $H$, the number of different (not necessarily
+induced) sub-hypergraphs of $\mathrm{G}^\mathcal{C}(n,\overbar{p})$
+isomorphic to $H$ belongs to $\Theta(n^{-ex(H)})$.
+Indeed, let $N:=|V(H)|$ and let $\phi$ be the automorphism
+group of $H$. Then, each sequence $v_1,\dots,v_N$ of $N$
+different vertices in $[n]$ can either define a copy of $H$
+in $\mathrm{G}^\mathcal{C}(n,\overbar{p})$ or not. Also, each
+sequence
+
+\subsection{Probabilities of trees}
+
+In this section we want to show that, given various classes of
+$k$-equivalence over rooted trees of radii at most $r$,
+$\mathcal{T}_1,\dots,\mathcal{T}_l$, and for 
+any fixed vertices $v_1,\dots,v_l \in \N$,
+the limit probabilities that each $N(v_i;r)$ is a tree which
+belongs to $\mathcal{T}_i$ class when rooted at $v_i$ are
+independent and they vary analitically with $\overbar{\beta}$.\par
+
+%
+%expressions analytic in $\overbar{\beta}$
+%
+%\begin{lemma}
+%	Let $v_1,\dots,v_l \in [n]$	
+%	
+%\end{lemma}
 
@@
 %Suppose
-
-\end{proof}
 

### 2020-01-08 BGSM/PersonalStatement.tex

\documentclass{article}
\usepackage[
  a4paper,
  margin=1in,
  headsep=4pt, % separation between header rule and text
]{geometry}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{tgschola}
\usepackage{lastpage}
\usepackage{amsmath}

\newcommand{\soptitle}{First order logic of sparse hypergraphs}

\newcommand{\yourname}{Lázaro Alberto Larrauri Borroto}
\newcommand{\youremail}{email@address.edu}
\newcommand{\yourweb}{https://www.abcd.com/}

\newcommand{\statement}[1]{\par\medskip
  \textcolor{blue}{\textbf{#1:}}\space
}

\usepackage[
  breaklinks,
  pdftitle={\yourname - \soptitle},
  pdfauthor={\yourname},
  unicode
]{hyperref}

\begin{document}

\begin{large}
\underline{\textbf{Personal statement}}
\end{large}

\bigskip

From a very young age the aspect of studying that 
I enjoyed the most was solving problems. Because 
of my high motivation and the support from my parents
and teachers, I was able to finish elementary school a 
year earlier than usual. Since I was thirteen
I have been participating in math and science competitions with
various degrees of success. At the time I finished my 
secondary studies, it was said that 
studying math would lead to fewer career possibilities
than other sciences or engineering. In spite of that,
I chose to pursue a math degree because it was what 
interested me the most. \par

Currently I am mostly interested in the connection between
logic, discrete mathematics and complexity theory, but my 
first interests were in the foundations of mathematics. 
Shortly after my math studies in university began, I discovered
the fact that some important theorems require the Axiom 
of Choice to be proven while this same axiom allows for counter-
intuitive results like the Banach-Tarski paradox. This was puzzling 
to me. You even need weak forms of this axiom if you want to show
that various different -and seemingly reasonable- definitions of 
finiteness are equivalent to each other. From there on I started 
studying mathematical logic and stumbled upon computability 
theory. These topics, as well as others that also interested me 
to a lesser extent, like non standard analysis or categorical logic, 
were not taught to me during my Bachelor's degree, so what I learnt 
about them was mostly through self-studying. \par
It was not until my master's thesis when I could do research related
to logic. My supervisor, Marc Noy, introduced me to the field of finite
model theory, which is of a fairly different nature from that of the logic 
I had studied up until that point but was equally interesting to me. 
The goal of my thesis was to extend a theorem that showed a certain 
convergence law

% Also, there were people 
%that rejected this axiom and others that are usually taken 
%for granted, like the Principle of the Excluded Middle, and 
%did mathematics in a different way. It was a shocking discovery 
%to me that mathematical truths were

%\bibliography{references}
%\bibliographystyle{acm}

\end{document}

### 2020-01-09 Article.tex
Pequeño update

@@
 
+We can think of structures in  $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$
+as "multi-hypergraphs" with
+$t$ edge sets whose edges are of sizes $\overbar{a}$ respectively
+, are invariant under permutations in $\overbar{\Phi}$ resp., 
+and do 
+not contain repetitions of vertices in the positions given by
+$\overbar{P}$ resp. We make this observation formal in the 
+following definitions:
+
 %We will denote by $t_u$ the, possibly zero,
@@
 Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is
+a sub-hypergraph $H_2\subseteq G$ isomorphic to $H$. A labeled copy
+of $H$ in $G$ is a sub-hypergraph $H_2\subseteq G$ together with
+an isomorphism $f$ from $H$ to $H_2$. Clearly, the number
+of labeled copies of $H$ in $G$ is $|Aut(H)|$ times the number
+of copies of $H$ in $G$.
 

### 2020-01-13 Article.tex
Mas pequeño

--- 2020-01-08 Article.tex
@@
 Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is
+a sub-hypergraph $H_2\subseteq G$ isomorphic to $H$. The copy
+is called induced if $H_2$ is an induced sub-hypergraph.
+We will call a labeled copy
+of $H$ in $G$ to a monomorphism $f:H\rightarrow G$. 
+It is satisfied that the number
+of labeled copies of $H$ in $G$ is $|Aut(H)|$ times the number
+of copies of $H$ in $G$.
 
@@
 	\item[(2)] a.a.s. any random graph belongs to some of them, and
-	\item[(3)] the limit probability of random graph belonging to any of them is an analytic expression on the parameters $\overbar{\beta}$. 
+	\item[(3)] the limit probability of random graph belonging to 
+	any of them is an analytic expression on the parameters $\overbar{\beta}$. 
 \end{itemize}
@@
 
-The objective of next sections will be to define the classes $C_1,\dots, C_{n_k}$ and to show that they satisfy properties (1), (2) and (3).
+The objective of next sections will be to define the classes 
+$C_1,\dots, C_{n_k}$ and to show that they satisfy properties (1), (2) and (3).
 
@@
 We say that a connected hypergraph $G$ is \textbf{dense} if
-$ex(G)>0$.
-We want to show that a.a.s any sub-hypergraph 
-of $\mathrm{G}^\mathcal{C}(n,\overbar{p})$ whose
-diameter is small (i.e. bounded by some constant)
-is not dense. \par
-It takes a direct computation to show that given
-an hypergraph $H$, the number of different (not necessarily
-induced) sub-hypergraphs of $\mathrm{G}^\mathcal{C}(n,\overbar{p})$
-isomorphic to $H$ belongs to $\Theta(n^{-ex(H)})$.
-Indeed, let $N:=|V(H)|$ and let $\phi$ be the automorphism
-group of $H$. Then, each sequence $v_1,\dots,v_N$ of $N$
-different vertices in $[n]$ can either define a copy of $H$
-in $\mathrm{G}^\mathcal{C}(n,\overbar{p})$ or not. Also, each
-sequence
+$ex(G)>0$. Given $r\in \N$, we say that $G$ is \textbf{$r$-simple}
+if $G$ does not contain any dense subgraph $H$ such that 
+$diam(H)\leq r$. The goal of this section is to show that, for any
+fixed $r$, a.a.s $G_n$ is $r$-simple.\par
+
+\begin{lemma}
+	Let $H$ be an hypergraph. Then 
+	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
+	\Theta(n^{-ex(H)})$ as $n$ tends to infinity.  
+\end{lemma}
+\begin{proof}
+
+Indeed, let $n\in \N$ and let $G_n$ be a random hypergraph sampled from
+$\mathrm{G}^\mathcal{C}(n,\overbar{p})$. Let
+$\overbar{h}$ be an ordering of the vertices
+in $V(H)$. For any list 
+$\overbar{v}\in [n]_{|V(H)|}$ (recall that $[n]=V(G)$), 
+let $X_{\overbar{v}}$ be the random indicator variable
+that takes value $1$ if the natural map 
+$f:\overbar{h}\rightarrow \overbar{v}$ defines an homomorphism 
+between $H$ and $G$. That is, $X_{\overbar{v}}$ takes value $1$
+with probability
+$ \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|},
+$
+and zero otherwise. The sum of all $X_{\overbar{v}}$'s for 
+all $\overbar{v}\in [n]_{|V(H)|}$ counts how many labelled 
+copies of $H$ are in $G_n$. Thus, 
+\[ \mathrm{E}\big[\# \text{labelled copies of }H \text{ in } G_n\big] 
+= \sum_{\overbar{v}\in [n]_{|V(G)|}} 
+\prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
+= (n)_{|V(H)|} \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}.
+\]
+The expected number of copies of $H$ in $G_n$ is then this last
+expectation divided by the number of automorphisms of $H$, $|Aut(H)|$.
+In consequence,
+\begin{align*}
+&\Ln \mathrm{E}\big[\# \text{copies of }H \text{ in } G_n\big] 
+=\Ln \frac{(n)_{|V(H)|}}{|Aut(H)|} \prod_{i=1}^{t} 
+\big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
+=\\ &\Ln \Big[(n)_{|V(H)|}\prod_{i=1}^{t}n^{(1-a_i)|E_i(H)|}\Big]
+\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|} \simeq \Ln
+n^{-ex(H)}\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|},
+\end{align*}
+and last expression belongs to $\theta(n^{-ex(H)})$, as desired.\par
+\end{proof}
+
+As a corollary of last result we get the following:  
+\begin{lemma} 
+	Let $H$ be an hypergraph such that $ex(H)>0$. Then
+	a.a.s there are no copies of $H$ in $G_n$. 
+\end{lemma}  
+\begin{proof}
+	Because of the previous fact, 
+	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big] 
+	\xrightarrow[]{n\to \infty} 0$. Then an application of the first moment
+	method yields the desired result. 
+\end{proof}
+
+The main theorem of this section is the following
+
+\begin{lemma}
+	Let $H$ be a dense hypergraph of radius $r$.
+	Then $H$ contains a dense sub-hypergraph $H^\prime$ 
+	with size no greater than
+	$(a+2)(r+1)+2a$, where $a$ is the largest edge size in $H$. 
+\end{lemma}
+\begin{proof}
+	Choose $x\in V(H)$. Successively remove from $G$ edges $e$
+	such that $d(x, e)$ is maximum until the resulting graph 
+	$H^\prime$ has excess no greater than $0$. We have two cases:
+	\begin{itemize}[leftmargin=*]
+		\item $ex(H^\prime)=-1$. Let $e=[x_1, \dots, x_b]$ be
+		the last removed edge and
+		$e\cap H^\prime=\{ x_{i_1}, \dots, x_{i_d}\}$.
+		For any $j=1,\dots, d$ choose 
+		$P_j$ a path of size no greater than $r+1$ joining
+		$x$ and $x_{i_j}$ in $H^\prime$.   
+		Then $P_1\cup \dots P_d \cup e$ is a dense sub-hypergraph of $H$
+		of size less than $a(r+1) + a< (a+2)(r+1) + 2a$.
+		\item $ex(H^\prime)=0$. Let $e_1=[x_1, \dots, x_{b_1}]$ be the
+		last removed edge. Continue removing the edges of $G^\prime$ 
+		that are at maximum distance from $x$ until you obtain 
+		$H^{\prime \prime}$ with $ex(H^{\prime\prime})=-1$. Let 
+		$e_2=[y_1, \dots, y_{b_2}]$ be the last removed edge this time.
+		As before, let $e_1\cap H^\prime=\{ x_{i_1}, \dots, x_{i_d}\}$
+		and for $j=1,\dots, d$ let $P_j$ a path of size no greater than $r+1$ 
+		joining	$x$ and $x_{i_j}$ in $H^\prime$
+		Then $e_2 \cup H^{\prime \prime}=\{ y_{i_1}, y_{i_2}  \}$.
+		Let $Q_1, Q_2$ be paths size no greater than $r+1$ from
+		$x$ to $y_{i_1}$ and $y_{i_2}$ in $H^{\prime \prime}$.
+		Then $Q_1 \cup Q_2 \cup e_2$ is a graph of likelihood $0$ 
+		and size less than $2r+2 + a$,
+		and $Q_1\cup Q_2\cup P_1 \cup \dots \cup P_d \cup e_1 \cup e_2$ 
+		is a critical graph	with size less than $(2+a)(r+1) + 2a$	
+	\end{itemize} 
+\end{proof}
+
+\begin{theorem}
+	Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple. 
+\end{theorem}
+\begin{proof}
+	The first moment method alone is not sufficient
+	to prove our claim because the amount of dense 
+	hypergraphs	$H$ such that $diam(H)\leq r$ is not finite
+	in general. Thus, we need to prove that it suffices to
+	prohibit a finite amount of dense sub-hypergraphs in order
+	to guarantee that $G_n$ is $r$-simple.
+\end{proof}
 

### 2020-01-15 Article.tex
Merge

@@
 
+During this section we want to study
+the asymptotic probability that the 
+$r$-neighborhood of a given vertex $v\in \N$
+in $G_n$ 
+is a tree that belongs to a given $k$-equivalence
+class of trees $\mathcal{T}$ with radius at most
+$r$. That is, we want to know
+\[\Ln \mathrm{Pr}\big( 
+T:=N^{G_n}(v;r) \text{ is a tree, and } (T,v)\in \mathcal{T} \big). 
+\]
+Denote this limit by $\mathrm{Pr}[\mathcal{T}]$. Notice that the definition of  $\mathrm{Pr}[\mathcal{T}]$ does not depend by the
+choice of $v$.\\
+
+An easy observation is that if we are given a finite
+set of vertices $X \subset \N$ and some
+
+vertex $v\in \N$ and a $k$-equivalence class
+of trees $\mathcal{T}$ with radius at most $r$,
+
 In this section we want to show that, given various classes of
@@
 independent and they vary analitically with $\overbar{\beta}$.\par
+
+%During this section we will consider
+%inside of $G_n$ a set of distinguished vertices
+%$\overbar{v}\in \N*$ cho
 

### 2020-01-16 Article.tex
Maxo acaba ya

@@
 \]
-Denote this limit by $\mathrm{Pr}[\mathcal{T}]$. Notice that the definition of  $\mathrm{Pr}[\mathcal{T}]$ does not depend by the
-choice of $v$.\\
-
-An easy observation is that if we are given a finite
-set of vertices $X \subset \N$ and some
-
-vertex $v\in \N$ and a $k$-equivalence class
-of trees $\mathcal{T}$ with radius at most $r$,
-
-In this section we want to show that, given various classes of
-$k$-equivalence over rooted trees of radii at most $r$,
-$\mathcal{T}_1,\dots,\mathcal{T}_l$, and for 
-any fixed vertices $v_1,\dots,v_l \in \N$,
-the limit probabilities that each $N(v_i;r)$ is a tree which
-belongs to $\mathcal{T}_i$ class when rooted at $v_i$ are
-independent and they vary analitically with $\overbar{\beta}$.\par
-
+Denote this limit by $\mathrm{Pr}[r,\mathcal{T}]$. Notice that the 
+definition of  $\mathrm{Pr}[r,\mathcal{T}]$ does not depend by the
+choice of $v$.\par
+
+We define $\Lambda$ and $M$ as the minimal families
+of expressions with arguments $\overbar{\beta}$ that satisfy
+ the conditions: \textbf{(1)} $1\in \Lambda$, \textbf{(2)} 
+for any $b,i\in \N$ with $1\leq i \leq c$,
+$b > 0$, and $\lambda_1,\dots, \lambda_{a_i-1}\in \Lambda$,
+the expression $(\beta_i/b) \prod_{j=1}^{a_i-1}\lambda_j$
+belongs to $M$,  \textbf{(3)}
+for any $\mu\in M$ and any $n\in \N$ both
+$\mathrm{Poiss}_{\mu}(n)$ and $\mathrm{Poiss}_\mu(\geq n)$ are in $\Lambda$, 
+and  \textbf{(4)} for any $\lambda_1,\lambda_2 \in \Lambda$, the
+product $\lambda_1\lambda_2$ belongs to $\Lambda$ as well.
+\par
+The goal of this section is to show  want to 
+show that $\mathrm{Pr}[r,\mathcal{T}]$,
+as an expression with parameters
+$\overbar{\beta}$, belongs to $\Lambda$ for any choice of 
+$r$ and $\mathcal{T}$. The argument is as follows:
+let $T:=N^{G_n}(v;r)$. \par
+
+\begin{lemma}
+	Let $X\subset \N$ be a finite set of fixed vertices, and let 
+	$r\in \N$. Define $G_n^\prime=G_n \setminus E(X)$.
+	Then (1) a.a.s $G^\prime_n$ does not contain a path of size
+	$r+1$ between any two vertices $u,v\in X$, and (2)
+	a.a.s $G^\prime_n$ does not contain a cycle containing
+	any vertex $u\in X$.
+\end{lemma}
+\begin{proof}
+	To prove the first part of the statement it suffices
+	to show that the expected number of such paths
+	tends to zero as $n$ tends to infinity. 
+	Let $P$ be a path of size $r+1$ between two vertices $w,z$,
+	and let $u,v$ be two vertices from $X$. 
+	Given $f$ 	
+\end{proof}
+
+Let $\overbar{v}\in \N*$ a list of vertices. For each $n,r\in \N$ and 
+$v_i\in \overbar{v}$ we define the random hypergraph
+$T_n(v_i,\overbar{v};r)$ in the following way: Let $G^\prime_n:=G_n \setminus
+E(G_n[\overbar{v}])$. Then $T_n(v_i,\overbar{v};r):= N^{G^\prime_n}(v;r)$.
+That is, $T_n(v_i,\overbar{v};r)$ is the $r$-neighborhood of $v_i$ in ``$G_n$
+minus the edges induced on $\overbar{v}$".
+
+\begin{theorem} 
+	The following are satisfied:
+	\begin{itemize}
+		\item[(1)] Let $r\in \N$ and let $\mathcal{T}$ be a
+		$k$-equivalence class for trees with radii at most $r$.
+		Then $\mathrm{Pr}[r,\mathcal{T}]$ exists and is an expression
+		in $\Lambda$.
+		\item[(2)] Let $\overbar{w}\in \N*$ be a list of different fixed 
+		vertices, and let $\overbar{v}\in \N*$ be another list of 
+		 Let $r_1,\dots r_k\in \N$ and let
+		$\mathcal{T}_1,\dots \mathcal{T}_k$ be 
+		$k$-equivalence classes for trees such that
+		each $\mathcal{T}_i$ has radii bounded by $r_i$. Let
+		$\overbar{v}$ denote a list of fixed vertices 
+		$v_1,\dots,v_k,\dots, v_l\in \N$, and let 
+		$\phi(\overbar{x})$ be an open sentence on $l$ variables.
+		Let $G_n^\prime=G_n\setminus E[\overbar{v}]$ 
+	\end{itemize}
+
+Let $\overbar{\mathcal{T}}$ be a  $\overbar{u}\in N$
+
+\end{theorem}
 %During this section we will consider

### 2020-01-16 Seminar.tex
Maxo acaba ya

\documentclass{article}
\usepackage[
a4paper,
margin=1in,
headsep=4pt, % separation between header rule and text
]{geometry}
\usepackage{amssymb,mathtools, amsmath, amsfonts, amsthm}
\begin{document}

Title: On the evolution of the set of limiting probabilities of first order properties for sparse random graphs. \par

Abstract: This is joint work with Marc Noy and Tobias M\"uller. It is known that for any first order property of graphs P,
the limit probability that the random graph $G(n,c/n)$ satisfies $P$ as $n$ tends to infinity exists and varies in a smooth 
way with $c$. An immediate consequence of this is that first order properties cannot individually ``capture'' the phase
transition that occurs in $G(n,c/n)$ when c=1. \par
We consider the set of limiting probabilities
\[L_c:= \{ \lim\limits_{n->\infty} \mathrm{Pr}(G(n,c/n) \text{ satisfies } P \, |
\, P \text{ first order property } \}.\]
We ask the question of whether we can ``detect" the phase transition in $G(n,c/n)$ through the changes in $L_c$. We 
arrive at a negative answer and show that there is a constant $c_0\simeq 0.93...$ such that the closure $\overline{L_c}$ 
of $L_c$ is the whole interval $[0,1]$ when $c\geq c_0$ and $\overline{L_c}$ is a finite union of disjoint intervals when 
$c< c_0$. Moreover, the number of intervals forming  $\overline{L_c}$ tends to infinity as $c$ tends to zero. The same
question can be asked in the setting of random uniform hypergraphs and similar results are obtained. 
\end{document}

### 2020-01-21 Article.tex
Seminario

@@
 		\item[(2)] Let $\overbar{w}\in \N*$ be a list of different fixed 
-		vertices, and let $\overbar{v}\in \N*$ be another list of 
-		 Let $r_1,\dots r_k\in \N$ and let
-		$\mathcal{T}_1,\dots \mathcal{T}_k$ be 
-		$k$-equivalence classes for trees such that
-		each $\mathcal{T}_i$ has radii bounded by $r_i$. Let
-		$\overbar{v}$ denote a list of fixed vertices 
-		$v_1,\dots,v_k,\dots, v_l\in \N$, and let 
-		$\phi(\overbar{x})$ be an open sentence on $l$ variables.
-		Let $G_n^\prime=G_n\setminus E[\overbar{v}]$ 
+		vertices, and let $\phi[\overbar{x}]\in FO[\sigma]$ be an open sentence
+		(i.e. with no bounded variables) such that $\overbar{x}$ and $\overbar{w}$
+		have the same size. Let $=v_1,\dots,v_k \in \N$ be another 
+		list of different vertices that are contained in $\overbar{w}$.
+		Let $r_1,\dots,r_k \in \N$ and let $\mathcal{T}_1,\dots \mathcal{T}_k$
+		be $k$-equivalence classes for trees such that
+		each $\mathcal{T}_i$ has radii bounded by $r_i$. Then
+		\[
+		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
+		T_{n,i}=T_n(v_i,\overbar{w};r_i) \text{ is a tree and } 
+		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
+		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]. \]		
 	\end{itemize}
+	\begin{proof}
+		Let $R$ be an upper bound of the radius of $r$ and the 
+		$r_i$'s	in the statement. 
+		We will prove (1) and (2) together by induction on $R$. \par
+		Assume $R=0$. We start by showing that (1) holds. Recall that
+		all trees with radius zero are $k$-equivalent. Thus, if
+		$\mathcal{T}$ is the unique $k$-equivalence class of trees
+		with radius zero
+		and $v\in \N$ is a fixed vertex, then
+		 \[
+		 \mathrm{Pr}[0;\mathcal{T}] = \Ln \mathrm{Pr}\big( 
+		 T:=N^{G_n}(v;0) \text{ is a tree, and } (T,v)\in \mathcal{T} \big)
+		 =1, 
+		 \]
+		Indeed, $N^{G_n}(v;0)$ consists of a single vertex for all $n\geq v$,
+		and the above equation follows. The expression $1$ belongs to 
+		$\Lambda$, so (1) holds. \par
+		The case of (2) is analogous. As $R=0$, then $\mathcal{T}_1=\dots=
+		\mathcal{T}_k$ are the unique $k$-equivalence class of trees with
+		radius zero. Then, given $\sigma, \overbar{w}, v_1,\dots, v_k$ as
+		in the statement,
+		\[\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
+		T_{n,i}=T_n(v_i,\overbar{w};0) \text{ is a tree and } 
+		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
+		\big)=1. \]	
+		Because of (1), $\mathrm{Pr}[0,\mathcal{T}_i]=1$ for all $i$'s, 
+		and (2) holds. \par
+		Now let $R>0$ and assume that both (1) and (2) hold for all 
+		lesser values of $R$.
+
+	\end{proof}
 

### 2020-01-21 Presentacion Sparse Graphs/seminario.tex
Seminario

--- 2019-07-06 Presentacion Sparse Graphs/presentacio.tex
@@
 
-\begin{frame}{Preliminaries}
-\begin{center}
-	\large{First order language of graphs}
-\end{center}
-\begin{columns}
-	\begin{column}{0.55\textwidth}
+\begin{frame}{Preliminaries: The first order logic (FO) of graphs}
+	Variables $x_1, \dots, x_n, \dots$ $\rightarrow$ Vertices\\
+	Boolean connectives $\wedge, \vee, \neg$ and equality symbol $=$.\\
+	Quantifiers $\forall, \exists$.\\
+	A binary relation symbol $E$.\\~\\
+	It can express properties like:
 	\begin{itemize}
-			\item Variables $x_1, \dots, x_n, \dots$
-			\item Connectives $\wedge, \vee$, equality symbol $=$,
-			and negation symbol $\neg$.
-			\item Quantifiers $\forall, \exists$.
-			\item A binary relation symbol $R$
+		\item The existence of a given subgraph
+		\item The existence of a covering set of size $k$
 	\end{itemize}
-	\end{column}
-		\begin{column}{0.45\textwidth}
-		\begin{itemize}
-			\item Vertices.
-			\item ``And", ``or", ``equals", ``not".
-			\item ``For all", ``there exists".
-			\item Edges $x\sim y$. 
-		\end{itemize}
-	\end{column}
-\end{columns}
-~\\
-\[ \forall x_1,x_2 \, R(x_1,x_2) \implies \exists x_3 \,
- \neg(x_3=x_1)\wedge \neg(x_3=x_1) \wedge R(x_1, x_3)\]
+	It cannot express connectivity, $k$-colorability, existence of a Hamiltonian
+	path \dots
 \end{frame}
 
-\begin{frame}{Preliminaries}
-	\Large{Binomial model of random graphs $G(n,p)$.} \\
-	\large
-	~\\
+\begin{frame}{Preliminaries: The binomial model of random graphs $G(n,p)$}
+
 	Start with vertex set $[n]=\{1,\dots, n\}$ and
@@
 For $p(n)=n^{-\alpha}$ and $\alpha\in [0,1]$ we have a nearly complete answer.
-\begin{theorem}{(Fagin 19776)} If $0\leq p \leq 1$ is constant a Zero-One Law is satisfied
+\begin{theorem}{(Fagin 1976)} If $0\leq p \leq 1$ is constant a Zero-One Law is satisfied
 \end{theorem}

### 2020-01-30 Article.tex
A zgz

@@
 The analyticity of these asymptotic probabilities with respect to 
-the parameter $\beta$ imply that FO properties cannot "capture" sudden
+the parameter $\beta$ implies that FO properties cannot "capture" sudden
 changes that occur in the random graph $\mathrm{G}(n,\beta/n)$
@@
 The main theorem of this section is the following
+\begin{theorem} \label{thm:simple}
+	Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple. 
+\end{theorem}
+
+	The first moment method alone is not sufficient
+	to prove our claim because the amount of dense 
+	hypergraphs	$H$ such that $diam(H)\leq r$ is not finite
+	in general. Thus, we need to prove that it suffices to
+	prohibit a finite amount of dense sub-hypergraphs in order
+	to guarantee that $G_n$ is $r$-simple.
 
@@
 
-\begin{theorem}
-	Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple. 
-\end{theorem}
-\begin{proof}
-	The first moment method alone is not sufficient
-	to prove our claim because the amount of dense 
-	hypergraphs	$H$ such that $diam(H)\leq r$ is not finite
-	in general. Thus, we need to prove that it suffices to
-	prohibit a finite amount of dense sub-hypergraphs in order
-	to guarantee that $G_n$ is $r$-simple.
-\end{proof}
+Now we are in conditions to prove \cref{thm:simple}.
 
@@
 
+\begin{definition}
+
+\end{definition}
+
 \begin{lemma}
@@
 	Then (1) a.a.s $G^\prime_n$ does not contain a path of size
-	$r+1$ between any two vertices $u,v\in X$, and (2)
-	a.a.s $G^\prime_n$ does not contain a cycle containing
-	any vertex $u\in X$.
+	at most	$r+1$ between any two vertices $u,v\in X$, and (2)
+	a.a.s $G^\prime_n$ does not contain a cycle of size $r+1$ 
+	that contains a vertex $u\in X$.
 \end{lemma}
@@
 	tends to zero as $n$ tends to infinity. 
-	Let $P$ be a path of size $r+1$ between two vertices $w,z$,
-	and let $u,v$ be two vertices from $X$. 
+	Let $u,v$ be two vertices lying in $X$. 
 	Given $f$ 	

### 2020-02-17 Article.tex
Pequeño update

@@
 That is, the excess of $G$ is its "weighted number of edges"
-minus its number of vertices. Here the "weighted number of edges"
-in $G$ the sum of the weight of all its edges, where the
-weight of an edge is its size minus one.
+minus its number of vertices. \par
 
@@
 Our main tool for computing probabilities will be
-the following multivariate version of Brun's Sieve 
-CITA REQUERIDA
+the following multivariate version of Brun's Sieve (
+Theorem 1.23, \cite{bollobas2001random}).
 
@@
 	Fix $k\in \N$. For each 
-	$n\in \N$, let $X_{1,n},\dots, X_{k,n}$ be non-negative
+	$n\in \N$, let $X_{n,1},\dots, X_{n,k}$ be non-negative
 	random integer variables over the same
@@
 	\Ln \mathrm{E}\big[
-	\prod_{i=1}^{k} (X_{i,n})_{r_i} \big]
+	\prod_{i=1}^{k} (X_{n,i})_{r_i} \big]
 	= \prod_{i=1}^{k} \frac{\lambda_i}{r_i !}.	
 	\]
-	Then the $X_{1,n},\dots,X_{k,n}$ converge in distribution to
+	Then the $X_{n,1},\dots,X_{n,k}$ converge in distribution to
 	independent Poisson variables with means $\lambda_1,\dots,\lambda_k$ 
@@
 		Now let $R>0$ and assume that both (1) and (2) hold for all 
-		lesser values of $R$.
+		lesser values of $R$.  \par
 

### 2020-02-17 Article.tex
Venga Alberto esta semana ya

@@
 to denote that its free variables are the ones in $\overbar{y}$.
-Formulas with no free variables are called sentences. \par
+Formulas with no free variables are called sentences and 
+formulas with no quantifiers are called open formulas. \par
 The quantifier rank of a formula $\phi$, denoted by $qr(\phi)$, 
@@
 \begin{itemize}
-	\item Any two trees with radius zero are $k$-equivalent 
-	.Notice that those trees
-	consist only of one vertex, their respective roots.
+	\item Any two trees with radius zero are $k$-equivalent.
+	Notice that those trees
+	consist only of one vertex: their respective roots.
 	\item Suppose that the $k$-equivalence relation has been
@@
 \begin{proof}
-
-Indeed, let $n\in \N$ and let $G_n$ be a random hypergraph sampled from
-$\mathrm{G}^\mathcal{C}(n,\overbar{p})$. Let
-$\overbar{h}$ be an ordering of the vertices
-in $V(H)$. For any list 
-$\overbar{v}\in [n]_{|V(H)|}$ (recall that $[n]=V(G)$), 
-let $X_{\overbar{v}}$ be the random indicator variable
-that takes value $1$ if the natural map 
-$f:\overbar{h}\rightarrow \overbar{v}$ defines an homomorphism 
-between $H$ and $G$. That is, $X_{\overbar{v}}$ takes value $1$
-with probability
-$ \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|},
-$
-and zero otherwise. The sum of all $X_{\overbar{v}}$'s for 
-all $\overbar{v}\in [n]_{|V(H)|}$ counts how many labelled 
-copies of $H$ are in $G_n$. Thus, 
-\[ \mathrm{E}\big[\# \text{labelled copies of }H \text{ in } G_n\big] 
-= \sum_{\overbar{v}\in [n]_{|V(G)|}} 
-\prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
-= (n)_{|V(H)|} \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}.
+Given any one-to-one map $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be 
+the indicator variable
+that takes value one when $f$ defines an monomorphism 
+between $H$ and $G_n$ and zero otherwise. 
+The probability that $X^H_{n,f}=1$ is exactly
+$\prod_{i=1}^t \left(\frac{\beta_i}{n^{a_i-1}}\right)^{e_i(H)}$ which can
+be written as $C\cdot n^{-ex(H)-v(H)}$ for some constant
+$C$ that does not depend on $f$ nor $n$. Define 
+$X^H_n=\sum_{f\in [n]_{V(H)}} X^H_{n,f}$. Then, by definition, the number of 
+copies of $H$ in $G_n$ is exactly $X^H_n/|Aut(H)|$.
+Taking into account that 
+\[
+\mathrm{E}[X^H_n]=(n)_{v(H)} \cdot C\cdot n^{-\sum_{i=1}^t (a_i-1)\cdot e_i(H)}= \Theta(n^{-ex(H)}),
 \]
-The expected number of copies of $H$ in $G_n$ is then this last
-expectation divided by the number of automorphisms of $H$, $|Aut(H)|$.
-In consequence,
-\begin{align*}
-&\Ln \mathrm{E}\big[\# \text{copies of }H \text{ in } G_n\big] 
-=\Ln \frac{(n)_{|V(H)|}}{|Aut(H)|} \prod_{i=1}^{t} 
-\big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
-=\\ &\Ln \Big[(n)_{|V(H)|}\prod_{i=1}^{t}n^{(1-a_i)|E_i(H)|}\Big]
-\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|} \simeq \Ln
-n^{-ex(H)}\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|},
-\end{align*}
-and last expression belongs to $\theta(n^{-ex(H)})$, as desired.\par
+the result follows. 
+%Indeed, let $n\in \N$ and let $G_n$ be a random hypergraph sampled from
+% $\mathrm{G}^\mathcal{C}(n,\overbar{p})$. Let
+% $\overbar{h}$ be an ordering of the vertices
+%in $V(H)$. For any list 
+% $\overbar{v}\in [n]_{|V(H)|}$ (recall that $[n]=V(G)$), 
+%let $X_{\overbar{v}}$ be the random indicator variable
+%that takes value $1$ if the natural map 
+% $f:\overbar{h}\rightarrow \overbar{v}$ defines an homomorphism 
+%between $H$ and $G$. That is, $X_{\overbar{v}}$ takes value $1$
+%with probability
+% $ \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|},
+% $
+%and zero otherwise. The sum of all $X_{\overbar{v}}$'s for 
+%all $\overbar{v}\in [n]_{|V(H)|}$ counts how many labelled 
+%copies of $H$ are in $G_n$. Thus, 
+%\[ \mathrm{E}\big[\# \text{labelled copies of }H \text{ in } G_n\big] 
+%= \sum_{\overbar{v}\in [n]_{|V(G)|}} 
+%\prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
+%= (n)_{|V(H)|} \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}.
+%\]
+%The expected number of copies of $H$ in $G_n$ is then this last
+%expectation divided by the number of automorphisms of $H$, $|Aut(H)|$.
+%In consequence,
+%\begin{align*}
+% &\Ln \mathrm{E}\big[\# \text{copies of }H \text{ in } G_n\big] 
+%=\Ln \frac{(n)_{|V(H)|}}{|Aut(H)|} \prod_{i=1}^{t} 
+%\big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
+%=\\ &\Ln \Big[(n)_{|V(H)|}\prod_{i=1}^{t}n^{(1-a_i)|E_i(H)|}\Big]
+%\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|} \simeq \Ln
+%n^{-ex(H)}\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|},
+%\end{align*}
+%and last expression belongs to $\theta(n^{-ex(H)})$, as desired.\par
 \end{proof}
@@
 As a corollary of last result we get the following:  
-\begin{lemma} 
+\begin{lemma} \label{lem:nocopiesdense}
 	Let $H$ be an hypergraph such that $ex(H)>0$. Then
@@
 	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big] 
-	\xrightarrow[]{n\to \infty} 0$. Then an application of the first moment
+	\xrightarrow[]{n\to \infty} 0$. An application of the first moment
 	method yields the desired result. 
+\end{proof}
+
+A similar result that will be useful later is the following:
+
+\begin{lemma}\label{lem:nocopiesfixed}
+	Let $\overline{v}:=(v_1,\dots,v_j)\in \N*$.
+	Let $H$ be an hypergraph such that $ex(H)>-j$. 
+	Then a.a.s there is no copy of $H$ in $G_n$ that
+	contains all $v_1,\dots,v_j$. 
+\end{lemma} 
+\begin{proof}
+It is sufficient to show that
+\begin{equation}\label{eqn:aux}
+\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
+\overline{v} \big]\xrightarrow[]{n\to \infty} 0.
+\end{equation}
+Then, because of a first moment argument the result follows.\par
+Suppose that $v(H)\geq j$. Otherwise the statement is trivial. 
+As before, given any $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be the random
+variable that takes value one if $f$ is a monomorphism from $H$ to $G_n$
+and zero otherwise. The probability that $X^H_{n,f}$ takes value one is
+$C\cdot n^{-ex(H)-v(H)}$ for some constant $C$ independent from $f$ and $n$. 
+Let 
+\[ Y^H_{n,\overline{x}}= \sum_{\substack{f\in [n]_{V(H)}\\ 
+\overline{x}\subset Im(f)}} X^H_{n,f}.\]
+The number of functions $f\in [n]_{V(H)}$ such that $v_1,\dots,v_j\in Im(f)$
+is $\Theta(n^{v(H)-j})$. In consequence 
+$
+\mathrm{E}\big[Y^H_{n,\overline{v}}\big]=\Theta(n^{-ex(H)-j})
+$, and 
+\[\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
+\overline{v} \big]=\Theta(n^{-ex(H)-j}).
+\]
+This, together with $ex(H)>-j$, proves \cref{eqn:aux}. 
 \end{proof}
@@
 \end{theorem}
-
 	The first moment method alone is not sufficient
@@
 	to guarantee that $G_n$ is $r$-simple.
-
 \begin{lemma}
@@
 
+\begin{proof}
+	Because of last lemma there is a constant $R$ such that 
+	``$G$ does not contain dense hypergraphs of size bounded by $R$" implies
+	that ``$G$ is $r$-simple". Thus,
+	\[ \Ln \mathrm{Pr}\big( G_n \text{ is } r \text{-simple}  \big)
+	\geq \Ln \mathrm{Pr} \big( G_n \text{ does not contain dense 
+	hypergraphs of size bounded by } R\big).\] 
+	Because of	\cref{lem:nocopiesdense}, given any individual dense hypergraph,
+	the probability that there are no copies
+	of it in $G_n$ tends to $1$ as $n$ goes to infinity. Using that
+	there are a finite number of dense hypergraphs of size bounded by
+	$R$ we deduce that the RHS of last inequality tends to $1$. 
+\end{proof}
+
 \subsection{Probabilities of trees}
@@
 \par
-The goal of this section is to show  want to 
-show that $\mathrm{Pr}[r,\mathcal{T}]$,
+The goal of this section is to show 
+that $\mathrm{Pr}[r,\mathcal{T}]$,
 as an expression with parameters
 $\overbar{\beta}$, belongs to $\Lambda$ for any choice of 
-$r$ and $\mathcal{T}$. The argument is as follows:
-let $T:=N^{G_n}(v;r)$. \par
-
-\begin{definition}
-
-\end{definition}
+$r$ and $\mathcal{T}$. \par
 
 \begin{lemma}
-	Let $X\subset \N$ be a finite set of fixed vertices, and let 
-	$r\in \N$. Define $G_n^\prime=G_n \setminus E(X)$.
-	Then (1) a.a.s $G^\prime_n$ does not contain a path of size
-	at most	$r+1$ between any two vertices $u,v\in X$, and (2)
-	a.a.s $G^\prime_n$ does not contain a cycle of size $r+1$ 
-	that contains a vertex $u\in X$.
+	Let $\overline{v} \subset \N*$ be a finite set of fixed vertices and let 
+	$\sigma(\overline{x})$ be an open formula with no equality such that
+	$length(\overline{x})=length(\overline{v})$. 
+	Define $G_n^\prime=G_n \setminus E(\overline{v})$. Fix $R\in \N$. 
+	\begin{itemize}
+		\item Let $A_n$ be the event that $G^\prime_n$ contains a path of size
+		at most	$R+1$ between any two vertices $u,w\in \overline{v}$.
+		\item Let $B_n$ be the event
+		that $G^\prime_n$ contains a cycle of size at most $R+1$ 
+		that contains a vertex $u\in \overline{v}$.
+	\end{itemize}
+	Then $\Ln \mathrm{Pr}(A_n \, | \, \sigma(\overline{v}))=0$, and 
+	$\Ln \mathrm{Pr}(B_n \, | \, \sigma(\overline{v})=0$. 
 \end{lemma}
 \begin{proof}
-	To prove the first part of the statement it suffices
-	to show that the expected number of such paths
-	tends to zero as $n$ tends to infinity. 
-	Let $u,v$ be two vertices lying in $X$. 
-	Given $f$ 	
+	Notice that the events $A_n$ and $B_n$ do not concern the possible edges
+	induced over $\overline{v}$. In consequence, because edges are independent
+	in our random model, 
+	$\mathrm{Pr}(A_n \, | \, \sigma(\overline{v}))
+	=\mathrm{Pr}(A_n)$ and 
+	$\mathrm{Pr}(B_n \, | \, \sigma(\overline{v}))
+	=\mathrm{Pr}(B_n)$.\par
+	The facts that $\Ln \mathrm{Pr}(A_n)=0$ and 
+	$\Ln \mathrm{Pr}(B_n)=0$ follow
+	from \cref{lem:nocopiesfixed} using that 
+	(1) the excess of any path is greater or equal than $-1$,
+	(2) the amount of paths of size at most $R+1$ is finite,
+	(3) the excess of any cycle is zero, and (4) the
+	amount of cycles of size at most $R+1$ is finite. 
 \end{proof}
@@
 		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]. \]	
+		\item[(3)] 	
 	\end{itemize}

### 2020-02-18 Article.tex
Trees

@@
 \]
+
 Denote this limit by $\mathrm{Pr}[r,\mathcal{T}]$. Notice that the 
@@
 \end{proof}
+
+\begin{definition}
+	We call an hypergraph $G$ \textbf{saturated} if any proper 
+	sub-hypergraph $G^\prime \subset H$ satisfies $ex(G^\prime)<ex(G)$. \par
+	The \textbf{center} of a connected hypergraph $G$ is the maximal saturated
+	sub-hypergraph and it is denoted by $Center(G)$. In the general case 
+	the center of an hypergraph is the union of the
+	centers of its connected components. 
+\end{definition}
+
+\begin{definition}
+	Let $G$ be a connected hypergraph and let $\overline{v}\in V(G)^*$.
+	Then we call $Center(G, \overline{v})$ to the minimal connected hypergraph
+	that contains $Center(G)$ and the vertices $\overline{v}$. In general, if 
+	$G$ is an arbitrary hypergraph with connected components $G_1, \dots, G_k$,
+	and $\overline{v}$ are vertices $V(G)$, then we call 
+	$Center(G, \overline{v})$ to the union of $Center(G_i, V(G_i)\cap
+	\overline{v})$ for all the connected components $G_i$.
+\end{definition}
+
+\begin{definition}
+	Let $G$ be an hypergraph $G$, let $\overline{u}\in V(G)^*$
+	and let $v\in V(G)$.
+	Consider the graph $G^\prime= G\setminus 
+	E\big(Center(G,\overline{u})\big)$. Then the connected components of
+	$G^\prime$ are all trees. We call the \textbf{tree of $v$ in
+	$G(\overline{u})$}, denoted by $Tree(G\big(\overline{u}),v\big)$,
+	to the connected component of $G^\prime$ to which $v$ belongs
+	with $v$ as its root. \par   
+\end{definition}
 

### 2020-02-20 Article.tex
colorings

@@
 Given a rooted tree $(T, v)$, and a vertex $u\in V(T)$, 
-we define $Tree_{(T,v)}(u)$ as the tree $T[X]$ induced on the
+we define $\tau_{(T,v)}(u)$ as the tree $T[X]$ induced on the
 set $X:=\{ \, w\in V(T) \, | \, d(v,w)=d(v,u)+ d(u,w) \,  \}
 $, to which we assign $u$ as the root.
-That is, $Tree_{(T,v)}(u)$ is the tree consisting of those vertices
+That is, $\tau_{(T,v)}(u)$ is the tree consisting of those vertices
 whose only path to $v$ contains $u$.
@@
 			\item For any vertex different from the root $u\in e_1$, it is satisfied that
-			\[Tree_{(T_1,v_1)}(u)\morph{k} Tree_{(T_2,v_2)}(f(u)).\]
+			\[\tau_{(T_1,v_1)}(u)\morph{k} \tau_{(T_2,v_2)}(f(u)).\]
 		\end{itemize}
@@
 
-\begin{theorem}
+\begin{theorem} \label{thm:BrunSieve}
 	Fix $k\in \N$. For each 
@@
 	sub-hypergraph $G^\prime \subset H$ satisfies $ex(G^\prime)<ex(G)$. \par
-	The \textbf{center} of a connected hypergraph $G$ is the maximal saturated
+	The \textbf{center} of a connected hypergraph $G$ is its maximal saturated
 	sub-hypergraph and it is denoted by $Center(G)$. In the general case 
@@
 	Let $G$ be an hypergraph $G$, let $\overline{u}\in V(G)^*$
-	and let $v\in V(G)$.
+	and let $v\in \overline{u}$.
 	Consider the graph $G^\prime= G\setminus 
@@
 	$G^\prime$ are all trees. We call the \textbf{tree of $v$ in
-	$G(\overline{u})$}, denoted by $Tree(G\big(\overline{u}),v\big)$,
+	$G(\overline{u})$}, denoted by $Tr\big(G(\overline{u}),v\big)$,
 	to the connected component of $G^\prime$ to which $v$ belongs
 	with $v$ as its root. \par   
+	In this same situation, let $r\in \N$ and $H:=N^G(\overline{u};r)$.
+	We call the \textbf{$r$-tree of $v$ in $G(\overline{u})$}, 
+	denoted by $Tr\big(G(\overline{u}),v;r\big)$ to 
+	$Tr\big(H(\overline{u}),v\big)$.
 \end{definition}
 
-Let $\overbar{v}\in \N*$ a list of vertices. For each $n,r\in \N$ and 
-$v_i\in \overbar{v}$ we define the random hypergraph
-$T_n(v_i,\overbar{v};r)$ in the following way: Let $G^\prime_n:=G_n \setminus
-E(G_n[\overbar{v}])$. Then $T_n(v_i,\overbar{v};r):= N^{G^\prime_n}(v;r)$.
-That is, $T_n(v_i,\overbar{v};r)$ is the $r$-neighborhood of $v_i$ in ``$G_n$
-minus the edges induced on $\overbar{v}$".
+\newpage
+
+\begin{definition} 
+	Given a set $\Sigma$ and an hypergraph $G$, a $\Sigma$-coloring 
+	of $G$ is a partial function $\chi$ from $V(G)$ to $\Sigma$. 
+	A $\Sigma$-hypergraph $(G,\chi)$ is an hypergraph $G$ equipped
+	with a $\Sigma$-coloring of $G$, $\chi$. When $\chi$ is understood
+	or is not relevant we may omit it and write just $G$ instead of $(G,\chi)$.\par
+	Given two $\Sigma$-hypergraphs $(G_1,\chi_1)$ and $(G_2,\chi_2)$,
+	a $\Sigma$-isomorphism between them is an hypergraph isomorphism 
+	$f:V(G_1)\rightarrow V(G_2)$ satisfying that
+	that for any $v\in V(G_1)$ 
+	either (1) $\chi_1(v)=\chi_2(f(v))$, or (2) both $\chi_1(v)$ and $\chi_2(f(v))$ 
+	are undefined.	A $\Sigma$ automorphism of a $\Sigma$-hypergraph $G$ is a 
+	$\Sigma$-isomorphism from $G$ to itself.
+	 \par
+	Let $(H,\chi_1), (G,\chi_2)$ be two $\Sigma$-hypergraphs. Then a copy of $H$ in $G$ is
+	a sub-hypergraph $G_2\subset G$ such that 
+	$(H,\chi_1) \simeq_\Sigma (G_2,\chi_2|_{_{G_2}})$.	
+\end{definition}
+
+\begin{theorem} 
+	Let $v_1,\dots, v_k\in \N$ be different vertices and let 
+	$\Sigma_1,\dots,\Sigma_k$ be finite sets. For each 
+	$i\in [k]$ let $\mathcal{T}_i$ be a finite set of non-superimposable
+	rooted $\Sigma_i$-trees. 
+	For each $n\in N$ and $i\in [k]$ let $\chi_{n,i}$ be a random 
+	$\Sigma_i$ coloring over $G_n$ such that for any $w\in \N$ and any $S \in \Sigma_i$
+	the limit
+	\[
+	\Ln \mathrm{Pr}\big( \chi_n(w)=S\big)
+	\]
+	exists and does not depend on the chosen $w$. For each 
+	$S \in \Sigma_i$, let $\mu_{i,S}$ denote last limit. 
+	Given a tree $T\in \mathcal{T}_i$ let
+	\[
+	\lambda_{i,T}=\frac{1}{|Aut(T)|}\prod_{S\in \Sigma_i} \mu_{i,S}^{v(S,T)} 
+	\]	
+\end{theorem}
 
@@
 		in $\Lambda$.
-		\item[(2)] Let $\overbar{w}\in \N*$ be a list of different fixed 
-		vertices, and let $\phi[\overbar{x}]\in FO[\sigma]$ be an open sentence
-		(i.e. with no bounded variables) such that $\overbar{x}$ and $\overbar{w}$
-		have the same size. Let $=v_1,\dots,v_k \in \N$ be another 
-		list of different vertices that are contained in $\overbar{w}$.
+		\item[(2)] Let $\overline{u}\in \N*$ be a list of different fixed 
+		vertices, and let $\phi[\overbar{x}]\in FO[\sigma]$ be a consistent
+		open sentence (i.e. with no bounded variables) such that 
+		$length(\overbar{x})=length(\overbar{w})$.
+		Let $=v_1,\dots,v_k \in \N$ be different vertices
+		contained in $\overline{u}$.
 		Let $r_1,\dots,r_k \in \N$ and let $\mathcal{T}_1,\dots \mathcal{T}_k$
 		be $k$-equivalence classes for trees such that
-		each $\mathcal{T}_i$ has radii bounded by $r_i$. Then
+		each $\mathcal{T}_i$ has radii bounded by the correspondent
+		$r_i$. Then
 		\[
 		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
-		T_{n,i}=T_n(v_i,\overbar{w};r_i) \text{ is a tree and } 
-		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
+		Tr\big(G_n(\overbar{u}),v_i;r\big)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
 		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]. \]	 	
-		\item[(3)] 	
 	\end{itemize}
@@
 		with radius zero
-		and $v\in \N$ is a fixed vertex, then
+		and $v\in \N$ is a fixed vertex then
 		 \[
@@
 		\mathcal{T}_k$ are the unique $k$-equivalence class of trees with
-		radius zero. Then, given $\sigma, \overbar{w}, v_1,\dots, v_k$ as
+		radius zero. Then, given $\sigma, \overbar{u}, v_1,\dots, v_k$ as
 		in the statement,
 		\[\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
-		T_{n,i}=T_n(v_i,\overbar{w};0) \text{ is a tree and } 
-		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
-		\big)=1. \]	
+		Tr\big(G_n(\overbar{u}),v_i;r\big)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
+		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]=1. \]	 	
 		Because of (1), $\mathrm{Pr}[0,\mathcal{T}_i]=1$ for all $i$'s, 
@@
 		lesser values of $R$.  \par
-
+		Let $T_{n,i}=Tr\big(G_n(\overbar{u}),v_i;r\big)$. 
+		Let $i\in [k]$ and let $\mathcal{E}$ be any $k$-equivalence class
+		of initial edges of radius at most $r_i$. Then we define $X_{n,i,\mathcal{E}}$
+		as the random variable that counts the number of initial edges $e$ such that
+		$(T_{n,i},e)\in \mathcal{E}$.\par
+		We are going to show that the variables $X_{n,i,\mathcal{E}}$ converge, as
+		$n$ tends to infinity, to independent Poisson variables 
+		$\mathrm{Poiss}(\mu_{r_i,\mathcal{E}})$ whose means $\mu_{r_i,\mathcal{E}}$ 
+		are expressions in the family $M$. That is,
+		\begin{equation} \label{eqn:PoissonEdges}
+		\Ln \mathrm{Pr}\big(
+		\bigwedge_{i=1}^k \bigwedge_{\mathcal{E} \in EDGE_{r_i}} X_{n,i,\mathcal{E}}=a_{i,\mathcal{E}}
+		\, | \, \sigma(\overline{w})\big) =
+		\prod_{i=1}^k \prod_{\mathcal{E} \in EDGE_{r_i}} e^{-\mu_{r_i,\mathcal{E}}}
+		\frac{\mu_{r_i,\mathcal{E}}^{a_{i,\mathcal{E}}}}{a_{i,\mathcal{E}}!}
+		\end{equation}
+		Furthermore, for each $i$ and $\mathcal{E}$ we will prove that the mean 
+		$\mu_{r_i,\mathcal{E}}$ does only depend on $r_i$ and $\mathcal{E}$.
+		This proves both (1), and (2).\par
+
+		We will prove \cref{eqn:PoissonEdges} using \cref{thm:BrunSieve}.
+		For each $i\in [k]$ and $\mathcal{E}\in EDGE_{r_i}$ we define $\mu[r_i,\mathcal{E}]$
+		in the following way. Let $(T,e)$ be a representative of the equivalence class
+		$\mathcal{E}$. Let $p$ be the root of $T$ and let $j$ be the color of $e$. 
+		Let $b$ be the number of bijections $f:e\rightarrow e$ satisfying that (1)
+		$f(p)=p$, and (2) for any $q\in e$ different from $p$
+		$\tau_{(T)}(q) \simeq_k \tau_{(T)}(f(q))$. For any $q\in e$ 
+		different from $p$, let $\mathcal{T}_q$ be the $k$-equivalence class
+		of the tree $\tau_{(T)}(q)$. Then
+		\[
+		\mu_[r_i,\mathcal{E}]=\frac{\beta_j}{b} \prod_{\substack{q\in e \\ q\neq p}} 
+		\mathrm{Pr}[r_i-a_j+1,\mathcal{T}_q].
+		\]
+
+		Now we have to prove that for any non-negative numbers, 
+		$(d_{i,\mathcal{E}})_{\substack{i\in [k]}\\
+		\mathcal{E}\in EDGE_{r_i}}$, it is satisfied
+		\[\Ln
+		\mathrm{E}\left[
+		\prod_{\substack{\substack{i\in [k]}\\
+				\mathcal{E}\in EDGE_{r_i}}} \binom{X_n[i,\mathcal{E}]}{d[i,\mathcal{E}]}
+		\right] = \prod_{\substack{\substack{i\in [k]}\\
+				\mathcal{E}\in EDGE_{r_i}}} \frac{\mu[r_i,\mathcal{E}]^{d[i,\mathcal{E}]}}
+			{d[i,\mathcal{E}]!}.\]
 	\end{proof}
-
-Let $\overbar{\mathcal{T}}$ be a  $\overbar{u}\in N$
 
@@
 %an instance of $x$ in $\phi$ is called bounded if it occurs within the 
-%scope of a quantifier bounding it (i.e. it occurs in a sub-formula of
-%$\phi$ of the form $\forall x(\psi)$ or $\exists x (\psi)$). 
+% scope of a quantifier bounding it (i.e. it occurs in a sub-formula of
+% $\phi$ of the form $\forall x(\psi)$ or $\exists x (\psi)$). 
 %free if $\phi$ contains an instance of $x$ that is 
@@
 %there can be $2^{\binom{n}{2}}$ graphs with $n$ vertices and 
-%$\binom{\binom{n}{2}}{m}$ of those have exactly $m$ edges. \par
+% $\binom{\binom{n}{2}}{m}$ of those have exactly $m$ edges. \par
 %
@@
 %The model $\mathrm{G}(n,p)$, with $n$ a natural number and 
-%$0\leq p \leq 1$ in the real numbers, is the discrete probability space over
+% $0\leq p \leq 1$ in the real numbers, is the discrete probability space over
 %the set of all graphs whose vertex set is $[n]$ in where each graph 
@@
 %\( \mathrm{Pr}\big( \mathrm{G}(n,p(n)) \text{ satisfies } P \big) \) exists as
-%$n$ tends to infinity. \par
+% $n$ tends to infinity. \par
 %
@@
 %with respect to some logical language $\mathcal{L}$ if for any sentence
-%$\phi$ in $\mathcal{L}$ the probability that $G_n$ satisfies $\phi$ tends
+% $\phi$ in $\mathcal{L}$ the probability that $G_n$ satisfies $\phi$ tends
 %to some limit as $n$ tends to infinity. We say that $(G_n)_n$ obeys a 
@@
 %vertices, the adjacency relation symbol $R$, Boolean connectives 
-%$\wedge, \vee, \neg, \implies, \dots$, the universal $\forall$ and 
+% $\wedge, \vee, \neg, \implies, \dots$, the universal $\forall$ and 
 %existential $\exists$ quantifiers and the parentheses $)$, $($. 
@@
 %Spencer REF. Among other results, there was proven that for 
-%$\alpha\in (0,1)$ the model $\mathrm{G}(n,n^{-\alpha})$ satisfies a 
+% $\alpha\in (0,1)$ the model $\mathrm{G}(n,n^{-\alpha})$ satisfies a 
 %zero-one law with respect to FO logic if and only if $\alpha$ is irrational.
 %Furthermore, if $\alpha\in (0,1)$ is rational then 
-%$\mathrm{G}(n,n^{-\alpha})$ does not even obey a convergence law for FO
+% $\mathrm{G}(n,n^{-\alpha})$ does not even obey a convergence law for FO
 %logic. \par
@@
 %sparse. In there the number of edges in a random graph is approximately
-%$\frac{beta}{2}n$. Many interesting phenomena occur in this regime, being
+% $\frac{beta}{2}n$. Many interesting phenomena occur in this regime, being
 %the most notable one the sudden appearance of a unique giant connected 
@@
 %analogously to the model $\mathrm{G}(n,p)$. In particular
-%$\mathrm{G}_2(n,p)$ is the same model as $\mathrm{G}(n,p)$. \par
+% $\mathrm{G}_2(n,p)$ is the same model as $\mathrm{G}(n,p)$. \par
 %A number of results about the binomial random model for graphs have 
@@
 %been obtained REFS. The sparse regime in this model occurs when 
-%$p$ is of the form $p(n)=\beta n^{-k+1}$. This way the expected total 
+% $p$ is of the form $p(n)=\beta n^{-k+1}$. This way the expected total 
 %number of edges in a random hyper-graph grows linearly with $n$, and the
@@
 %In REF, among other results, it is proven that
-%$\mathrm{G}_k(n,p)$ obeys a convergence law for FO logic when
-%$p=\beta n^{k-1}$.
+% $\mathrm{G}_k(n,p)$ obeys a convergence law for FO logic when
+% $p=\beta n^{k-1}$.
 %
@@
 %of $\mathfrak{A}$ we define the relation 
-%$\mathfrak{A} \models \varphi[\alpha]$, "$\alpha$ satisfies $\phi$ in $\mathfrak{A}$",
+% $\mathfrak{A} \models \varphi[\alpha]$, "$\alpha$ satisfies $\phi$ in $\mathfrak{A}$",
 %in the following way:
@@
 %Given a natural number $n$, we will use the notation
-%$[n]:= \{1,\dots, n\}$. We will denote by $S_n$
+% $[n]:= \{1,\dots, n\}$. We will denote by $S_n$
 %the symmetric group on $[n]$, and by $\Delta_n$ the 
@@
 %any sort of quotient $X^n/\Phi$. That is, while the notation
-%$(x_1,\dots, x_n)$ will be reserved to ordered $n$-tuples, 
-%$[x_1,\dots,x_n]$ will denote an ordered $n$-tuple modulo the
+% $(x_1,\dots, x_n)$ will be reserved to ordered $n$-tuples, 
+% $[x_1,\dots,x_n]$ will denote an ordered $n$-tuple modulo the
 %action of some arbitrary group of permutations. Which group is this 
@@
 %we will mean is ``hiper-graph with edge colors 
-%$1,\dots, c$, sizes $a_1,\dots,a_c$, 
+% $1,\dots, c$, sizes $a_1,\dots,a_c$, 
 %symmetry groups $\Phi_1,\dots,\Phi_c$ and 
@@
 %Given a graph $G=([n], H_1,\dots, H_c)$ we will denote by
-%$H_i(G)$ the edge set $H_i$, and by $V[G]$ the vertex set
-%$[n]$. Also, we will write $H(G)$ to denote the 
+% $H_i(G)$ the edge set $H_i$, and by $V[G]$ the vertex set
+% $[n]$. Also, we will write $H(G)$ to denote the 
 %disjoint union of colored sets $\cup_{i=1}^c H_i$.

### 2020-02-20 Article.tex
colorings

@@
 	a sub-hypergraph $G_2\subset G$ such that 
-	$(H,\chi_1) \simeq_\Sigma (G_2,\chi_2|_{_{G_2}})$.	
+	$(H,\chi_1) \simeq_\Sigma (G_2,\chi_2|_{_{G_2}})$.	\par
+
+	Notation: $Copies([n],(G, \chi))$
+	Notation: $H\subset_{\Sigma}G$.
+
+\end{definition}
+\begin{definition}
+	Given a set $\Sigma$, a random $\Sigma$-coloring on $G_n$ is a random 
+	partial function $\chi : [n]\rightarrow \Sigma$. \par
+	Let $\overline{u}\in [n]^*$, and let $\chi$ be a random coloring on 
+	$G_n$. We say that $\chi$ is $\overline{u}$-symmetric if for every 
+	$s\in \Sigma$ the probability $\mathrm{Pr}\big(	\chi(v)=s\big)$ is the
+	same for all $v\in [n]\setminus\overline{u}$.
+
+\end{definition}
+
+Remark: A random coloring $\chi$ of $G_n$ does not have to be independent from
+$G_n$. In fact, in the cases we are going to consider $\chi$ will be determined
+by $G_n$.
+
+\begin{definition}
+	Let $\Sigma$ be a set, let $\mathcal{F}:=\{H_1, \dots, H_l\}$
+	be a finite family of hypergraphs, and
+	for each $n\in \N$ let $\chi_n$ be a random coloring of $G_n$. We say that 
+	$\chi_n$ is asymptotically $\mathcal{F}$-invariant if for any 
+	\begin{itemize}
+		\item fixed finite number of copies of hypergraphs from 
+		$\mathcal{F}$ in $\N$,
+		$G^1,\dots, G^k \in Copies(\N,H_1)\cup \dots \cup Copies(\N,H_l)$.
+		\item fixed vertices $\overbrace{v}\in G^1,\dots,G^k$.
+		\item fixed labels $\overbar{s}\in \Sigma$
+	\end{itemize}  
 \end{definition}

### 2020-02-20 Article.tex
FindeZgZ

@@
 $G_n$. In fact, in the cases we are going to consider $\chi$ will be determined
-by $G_n$.
+by $G_n$. \par
+
+For each $n\in \N$ let $\chi_n$ be a random $\Sigma$-coloring of $G_n$. 
+We say that the sequence $\chi_n$ is regular if:
+\begin{itemize}
+	\item[(1)] For each $n\in \N$ and $s\in \Sigma$ the probability 
+	$\mathrm{Pr}\big(\chi_n(v)=s\big)$ is the same for all vertices
+	$v\in [n]$. 
+	\item[(2)] For any vertex $v\in \N$ and any $s\in \Sigma$, the limit 
+	$\Ln \mathrm{Pr}\big(\chi_n(v)=s\big)$ exists. Notice that condition (1) implies
+	that this limit does not depend on $v$.
+\end{itemize}
+If the $\chi_n$'s form a regular sequence of colorings we will write
+$\mathrm{Pr}[\chi,s]$ to denote the limit $\Ln \mathrm{Pr}\big(\chi_n(v)=s\big)$
+in (2).
 
 \begin{definition}
-	Let $\Sigma$ be a set, let $\mathcal{F}:=\{H_1, \dots, H_l\}$
-	be a finite family of hypergraphs, and
-	for each $n\in \N$ let $\chi_n$ be a random coloring of $G_n$. We say that 
-	$\chi_n$ is asymptotically $\mathcal{F}$-invariant if for any 
+	Let $\mathcal{F}$
+	be a family of hypergraphs, and for each $i\in [l]$
+	let $(\chi_{n,i})_{n\in \N}$ be a sequence of regular 
+	random	$\Sigma_i$-colorings of $G_n$. We say that the sequences 
+	$(\chi_{n,i})$ are asymptotically stable with respect to $\mathcal{F}$
+	if for any 
 	\begin{itemize}
@@
 		$\mathcal{F}$ in $\N$,
-		$G^1,\dots, G^k \in Copies(\N,H_1)\cup \dots \cup Copies(\N,H_l)$.
-		\item fixed vertices $\overbrace{v}\in G^1,\dots,G^k$.
-		\item fixed labels $\overbar{s}\in \Sigma$
-	\end{itemize}  
+		$G^1,\dots, G^k \in \bigcup_{H\in \mathcal{F}} Copies(\N,H)$,
+		\item fixed different vertices $v_1, \dots, v_a \in V(G^1)\cup\dots \cup V(G^k)$,
+		indices $i_1,\dots, i_a \in [l]$ and labels $s_1 \in \Sigma_{i_1},\dots, s_a\in
+		\Sigma_{i_a}$,
+	\end{itemize}  
+	it is satisfied that
+	\[
+	\Ln \mathrm{Pr}\big(
+	\bigwedge_{c=1}^l \chi_{n,i_c}(v_c)= s_c  \, \big| \, \bigwedge_{j=1}^k G^j \subset G_n 
+	\big)= \prod_{c=1}^{l} \mathrm{Pr}[\chi_{i,c},s_c].	
+	\]
 \end{definition}
@@
 \begin{theorem}
-	Let $v_1,\dots, v_k\in \N$ be different vertices and let 
-	$\Sigma_1,\dots,\Sigma_k$ be finite sets. For each 
-	$i\in [k]$ let $\mathcal{T}_i$ be a finite set of non-superimposable
-	rooted $\Sigma_i$-trees. 
-	For each $n\in N$ and $i\in [k]$ let $\chi_{n,i}$ be a random 
-	$\Sigma_i$ coloring over $G_n$ such that for any $w\in \N$ and any $S \in \Sigma_i$
-	the limit
+	Let $l\in \N$. For any $i\in [l]$ 
+	\begin{itemize}
+	\item Let $\Sigma_i$ be a set of colors. 
+	\item Let $H_i$ be a unicycle and let $\eta_i$
+	be a $\Sigma_i$-coloring of
+	$H_i$.
+	\item Let $(\chi_{n,i})_{n\in \N}$ be a regular
+	sequence of random $\Sigma_i$-colorings
+	of $(G_n)_{n\in \N}$.
+	\item Let $X_{n,i}$ be the random variable that
+	counts the copies of $(H_i, \eta_i)$ in $(G_n,
+	\chi_{n,i})$.
+	\end{itemize}
+	Let $\mathcal{F}=\{H_1,\dots,H_l\}$. Suppose the
+	sequences $(\chi_{n,i})$ are asymptotically stable
+	with respect to $\mathcal{F}$. Then the random variables
+	$X_{n,i}$ are asymptotically distributed like independent Poisson 
+	variables with means 
+	\[\lambda_i:= \frac{\left(\prod_{i=1}^t \beta_i^{e_i(H_i)}\right) \left(
+	\prod_{s\in \Sigma_i} \mathrm{Pr}[\chi_i,s]^{|\eta^{-1}(s)|}	\right) }
+	{|Aut(H_i,\eta_i)|}. 
+  	\]
+  	That is, given any $b_1,\dots,b_l \in \N$,
   	\[
-	\Ln \mathrm{Pr}\big( \chi_n(w)=S\big)
-	\]
-	exists and does not depend on the chosen $w$. For each 
-	$S \in \Sigma_i$, let $\mu_{i,S}$ denote last limit. 
-	Given a tree $T\in \mathcal{T}_i$ let
-	\[
-	\lambda_{i,T}=\frac{1}{|Aut(T)|}\prod_{S\in \Sigma_i} \mu_{i,S}^{v(S,T)} 
+  	\Ln \mathrm{Pr}\big( 
+  	\bigwedge_{i=1}^l X_{n,i}=b_i
+  	\big) = \prod_{i=1}^l e^{-\lambda_i}\frac{\lambda_i^{b_i}}{b_i!}.
   	\] 
 \end{theorem}	
+\begin{proof}
+	We have to show that for any $c_1, \dots, c_l\in \N$
+	\begin{equation}\label{eqn:aux2}
+	\Ln  \mathrm{E}\big[
+	\prod_{i=1}^l (X_{n,i})_{c_i}
+	\big] = \prod_{i=1}^l \lambda_i^{c_i}.
+	\end{equation}
+	Then using \cref{thm:BrunSieve} the theorem follows.\par
+	For any $i\in [l]$, the random variable $(X_{n,i})_{c_i}$
+	counts the number of ordered tuples 
+	$(H_i^1,\eta_i^1),\dots,$ $(H_i^{c_i},\eta_i^{c_i})$ such that
+	for each $j\in [c_i]$, $(H_i^j,\eta_i^j)\subset
+	(G_n,\chi_{n,i})$. Let 
+	$\Omega=\prod_{i=1}^{l}[Copy((H_i,\eta_i),[n])]_{c_i}$ 
+	\[
+	\mathrm{E}\big[
+	\prod_{i=1}^l (X_{n,i})_{c_i}
+	\big]\]
+
+\end{proof}
 

### 2020-02-25 Article.tex

--- 2020-02-20 Article.tex
@@
 
+\subsection{Counting colored sub-hypergraphs}
+
+\begin{definition} 
+	Given a set $\Sigma$ and an hypergraph $G$, a $\Sigma$-coloring 
+	of $G$ is a function $\chi: V(G)\rightarrow \Sigma$. 
+	A $\Sigma$-hypergraph $(G,\chi)$ is an hypergraph $G$ equipped
+	with a $\Sigma$-coloring of $G$, $\chi$. When $\chi$ is understood
+	or is not relevant we may omit it and write just $G$ instead of $(G,\chi)$.\par
+	Given two $\Sigma$-hypergraphs $(G_1,\chi_1)$ and $(G_2,\chi_2)$,
+	a $\Sigma$-isomorphism between them is an hypergraph isomorphism 
+	$f:V(G_1)\rightarrow V(G_2)$ satisfying that
+	that for any $v\in V(G_1)$, $\chi_1(v)=\chi_2(f(v))$.
+	A $\Sigma$ automorphism of a $\Sigma$-hypergraph $G$ is a 
+	$\Sigma$-isomorphism from $G$ to itself.
+	\par
+	Let $(H,\chi_1), (G,\chi_2)$ be two $\Sigma$-hypergraphs. 
+	Then a copy of $H$ in $G$ is
+	a sub-hypergraph $G_2\subset G$ such that 
+	$(H,\chi_1) \simeq_\Sigma (G_2,\chi_2|_{_{G_2}})$.	\par
+
+	Notation: $Copies([n],(G, \chi))$
+	Notation: $H\subset_{\Sigma}G$.
+
+\end{definition}
+
+\begin{definition}
+	Given a set $\Sigma$, a random $\Sigma$-coloring of $G_n$ is 
+	a random function $\chi_n: [n]\rightarrow \Sigma$. We say that	
+	$\chi_n$ is symmetric if for any $s\in \Sigma$ the probability
+	$\mathrm{Pr}\big( \chi_n(v)=s \big)$ is the same for any vertex
+	$v\in [n]$. Notation $\mathrm{Pr}\big[\chi_n=s\big]$. \par
+	For each $n\in \N$ let $\chi_n$ be a random $\Sigma$-coloring of $G_n$.
+	We say that the succession $(\chi_n)_{n\in \N}$ is regular if
+	the $\chi_n$'s are symmetric and for any $s\in \Sigma$ the limit
+	$\Ln \mathrm{Pr}\big[ \chi_n = s \big]$ exists. 
+\end{definition}
+
+Remark: A random coloring $\chi$ of $G_n$ does not have to be independent from
+$G_n$. In fact, in the cases we are going to consider $\chi$ will be determined
+by $G_n$.
+
+\begin{definition}
+	Let $\Sigma_1,\dots,\Sigma_k$ be a sets. For each $i\in [k]$
+	let $(\chi_{n,i})_{n \in \N}$ be a random regular sequence of
+	$\Sigma_i$-colorings.
+	Let $\mathcal{F}$ be a family of hypergraphs.
+	We say that the successions $(\chi_{n,1})_{n \in \N},\dots,
+	(\chi_{n,k})_{n \in \N}$ are $\mathcal{F}$-independent if
+	for any given
+	\begin{itemize}
+		\item fixed finite number of copies of hypergraphs from 
+		$\mathcal{F}$ in $\N$,
+		\[
+		S \subset \bigcup_{H\in \mathcal{F}} Copies(H,\N).
+		\]		
+		\item fixed disjoint sets of vertices 
+		$V_1, \dots, V_k \subset \bigcup_{H\in S} V(H).$
+		\item for each $i\in [k]$ and each $v\in V_i$, 
+		a fixed label $s(v)\in \Sigma_i$
+	\end{itemize}
+	it is satisfied
+	\[
+	\Ln \mathrm{Pr}\big(
+	\bigwedge_{i=1}^k \bigwedge_{v\in V_i} \chi_{n,i}(v)=s(v)
+	\, \big| \, \bigwedge_{H\in S} H\subset G_n \,
+	\big) = \prod_{i=1}^k \prod_{v\in V_i} \mathrm{Pr}\big[\chi_i=s(v)
+	\big]		
+	\]  
+\end{definition}
+
+\begin{definition}
+	Let $H_1,\dots, H_k$ be hypergraphs. Let $n,b_1,\dots,b_k\in \N$
+	A $b_1,\dots,b_k$-configuration of $H_1,\dots, H_k$ over $[n]$
+	is an ordered tuple $(O_1,\dots,O_k)$ where for each $i\in [k]$
+	$O_i$ is an ordered $b_i$-tuple of different $H_i$-hypergraphs 
+	over $[n]$. In other words, each $O_i$ is an element of
+	$\big( Copies(H,[n])\big)_{b_i}$, and the set of 
+	$b_1,\dots,b_k$-configurations of $H_1,\dots, H_k$ over $[n]$
+	is precisely $\prod_{i=1}^{k}\big( Copies(H,[n])\big)_{b_i}$.
+\end{definition}
+
+\begin{definition}
+ 	The underlying set of a configuration $\omega
+ 	=  (O_1, \dots, O_k)$ is the defined as
+ 	$S_{\omega}:=\{ H\in O_i \, | \, i\in [k]\}$.
+ 	A configuration $\omega$ is called disjoint
+	if all the hypergraphs belonging to its underlying set
+	$S_\omega$ have disjoint sets of vertices. 
+\end{definition}
+
+\begin{theorem}
+	Let $k\in \N$. For each $i\in [k]$ 
+	\begin{itemize}
+		\item Let $\Sigma_i$ be a set, let $H_i$ be a unicycle and 
+		let $\rho^i$ be a $\Sigma_i$-coloring of $H_i$.
+		\item Let $(\chi^i_n)_{n\in\N}$ be a succession of
+		random $\Sigma_i$-colorings of $(G_n)_{n\in \N}$
+		\item Let $X_{i,n}$ be the random variable that counts
+		the number of copies of $(H_i, \rho^i)$ in
+		$(G_n,\chi^i_n)$.				
+	\end{itemize}
+	Let $\mathcal{F}=\{H_1,\dots, H_n\}$. Suppose that the
+	successions $(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
+	are $\mathcal{F}$-independent. Then, for each $a_1,\dots,a_k\in \N$
+	\[
+	\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k X_{n,i}=a_i  \big)=
+	\prod_{i=1}^{k}e^{-\lambda_i}\frac{\lambda_i^{a_i}}{a_i!},
+	\]
+	where for each $i\in [k]$,
+	\[
+	\lambda_i:= \frac{\prod_{j\in \sigma} \beta_j^{e_j(H_i)}}{|Aut(H_i,\rho^i)|} 
+	\prod_{v\in V(H_i)} \mathrm{Pr}\big[\chi^i=\rho^i(v)\big].
+	\]
+\end{theorem}
+\begin{proof}
+	Because of \cref{thm:BrunSieve} we only need to show that for any 
+	fixed $b_1,\dots, b_k\in \N$ it is satisfied
+	\[
+	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
+	\prod_{i=1}^{k} \lambda_i^{b_i}.		
+	\]
+	For each $n\in \N$ let $\Omega_n$ be the set
+	of $b_1, \dots, b_k$-configurations of $(H_1,\rho^1)
+	,\dots, (H_k, \rho^k)$ over $[n]$. Then
+	\[
+	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
+	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
+	\mathrm{Pr}
+	\big(
+	(O_1,\dots, O_k) \subset G_n
+	\big).	
+	\]
+	Let $\Omega^{\times}_n\subset \Omega_n$ be the set of 
+	disjoint configurations in $\Omega_n$. Because of REF,
+	\[
+	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
+	\mathrm{Pr}
+	\big(
+	(O_1,\dots, O_k) \subset G_n
+	\big)=
+	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
+	\mathrm{Pr}\big(
+	(O_1,\dots, O_k) \subset G_n
+	\big).
+	\]
+	Because of the symmetry of the random hypergraph $G_n$ and
+	the colorings $\chi^1_n, \dots, \chi^k_n$ the probability
+	$\mathrm{Pr}\big(
+	(O_1,\dots, O_k) \subset G_n
+	\big)$ is the same for all $(U_1,\dots, U_k)\in 
+	\Omega^\times_n$. Thus, if we fix
+	$(O_1, \dots, O_k)$ a 
+	disjoint $b_1,\dots,b_k$-configuration of
+	 $(H_1,\rho^1)
+	,\dots, (H_k, \rho^k)$ over $\N$, 
+	\[
+	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
+	\mathrm{Pr}\big(
+	(O_1,\dots, O_k) \subset G_n
+	\big) =
+	\Ln |\Omega^{\times}_n|	\mathrm{Pr}\big(
+	(U_1,\dots, U_k) \subset G_n
+	\big).
+	\]
+
+\end{proof}
+
 \subsection{Probabilities of trees}
@@
 \newpage
-
-\begin{definition} 
-	Given a set $\Sigma$ and an hypergraph $G$, a $\Sigma$-coloring 
-	of $G$ is a partial function $\chi$ from $V(G)$ to $\Sigma$. 
-	A $\Sigma$-hypergraph $(G,\chi)$ is an hypergraph $G$ equipped
-	with a $\Sigma$-coloring of $G$, $\chi$. When $\chi$ is understood
-	or is not relevant we may omit it and write just $G$ instead of $(G,\chi)$.\par
-	Given two $\Sigma$-hypergraphs $(G_1,\chi_1)$ and $(G_2,\chi_2)$,
-	a $\Sigma$-isomorphism between them is an hypergraph isomorphism 
-	$f:V(G_1)\rightarrow V(G_2)$ satisfying that
-	that for any $v\in V(G_1)$ 
-	either (1) $\chi_1(v)=\chi_2(f(v))$, or (2) both $\chi_1(v)$ and $\chi_2(f(v))$ 
-	are undefined.	A $\Sigma$ automorphism of a $\Sigma$-hypergraph $G$ is a 
-	$\Sigma$-isomorphism from $G$ to itself.
-	 \par
-	Let $(H,\chi_1), (G,\chi_2)$ be two $\Sigma$-hypergraphs. Then a copy of $H$ in $G$ is
-	a sub-hypergraph $G_2\subset G$ such that 
-	$(H,\chi_1) \simeq_\Sigma (G_2,\chi_2|_{_{G_2}})$.	
-\end{definition}
-
-\begin{theorem} 
-	Let $v_1,\dots, v_k\in \N$ be different vertices and let 
-	$\Sigma_1,\dots,\Sigma_k$ be finite sets. For each 
-	$i\in [k]$ let $\mathcal{T}_i$ be a finite set of non-superimposable
-	rooted $\Sigma_i$-trees. 
-	For each $n\in N$ and $i\in [k]$ let $\chi_{n,i}$ be a random 
-	$\Sigma_i$ coloring over $G_n$ such that for any $w\in \N$ and any $S \in \Sigma_i$
-	the limit
-	\[
-	\Ln \mathrm{Pr}\big( \chi_n(w)=S\big)
-	\]
-	exists and does not depend on the chosen $w$. For each 
-	$S \in \Sigma_i$, let $\mu_{i,S}$ denote last limit. 
-	Given a tree $T\in \mathcal{T}_i$ let
-	\[
-	\lambda_{i,T}=\frac{1}{|Aut(T)|}\prod_{S\in \Sigma_i} \mu_{i,S}^{v(S,T)} 
-	\]	
-\end{theorem}
 

### 2020-02-27 Article.tex
Clase Albert

@@
 \newcommand{\ehr}{\textsc{Ehr}}
+\newcommand{\PR}[1]{\mathrm{Pr}\big(#1\big)}
 
@@
 \begin{definition} 
-	Given a set $\Sigma$ and an hypergraph $G$, a $\Sigma$-coloring 
-	of $G$ is a function $\chi: V(G)\rightarrow \Sigma$. 
-	A $\Sigma$-hypergraph $(G,\chi)$ is an hypergraph $G$ equipped
-	with a $\Sigma$-coloring of $G$, $\chi$. When $\chi$ is understood
-	or is not relevant we may omit it and write just $G$ instead of $(G,\chi)$.\par
-	Given two $\Sigma$-hypergraphs $(G_1,\chi_1)$ and $(G_2,\chi_2)$,
-	a $\Sigma$-isomorphism between them is an hypergraph isomorphism 
-	$f:V(G_1)\rightarrow V(G_2)$ satisfying that
-	that for any $v\in V(G_1)$, $\chi_1(v)=\chi_2(f(v))$.
-	A $\Sigma$ automorphism of a $\Sigma$-hypergraph $G$ is a 
-	$\Sigma$-isomorphism from $G$ to itself.
+	Given a set $\Sigma$, a $\Sigma$-hypergraph is a pair
+	$(G,\chi)$ consisting of an hypergraph $G$ and a map 
+	$\chi: V(G) \rightarrow \Sigma$.  
+	Given two $\Sigma$-hypergraphs $(H,\rho)$ and $(G,\chi)$,
+	an isomorphism between them is an hypergraph isomorphism 
+	$f:V(H)\rightarrow V(G)$ satisfying $\rho(v)=\chi(f(v))$
+	for any $v\in V(H)$. 
+	An automorphism of a $\Sigma$-hypergraph $(G,\chi)$ is an
+	isomorphism from $(G,\chi)$ to itself. As with the case of
+	hypergraphs we write $Aut(G,\chi)$ to denote the group of 
+	automorphisms of $(G,\chi)$.
 	\par
-	Let $(H,\chi_1), (G,\chi_2)$ be two $\Sigma$-hypergraphs. 
+	Let $(H,\rho), (G,\chi)$ be two $\Sigma$-hypergraphs. 
 	Then a copy of $H$ in $G$ is
-	a sub-hypergraph $G_2\subset G$ such that 
-	$(H,\chi_1) \simeq_\Sigma (G_2,\chi_2|_{_{G_2}})$.	\par
-
-	Notation: $Copies([n],(G, \chi))$
+	a sub-hypergraph $H^\prime\subset G$ such that 
+	$(H,\rho)$ is isomorphic to 
+	$(H^\prime,\chi|_{_{H^\prime}})$.\par
+	Given a $\Sigma$-hypergraph $(G,\chi)$ and a set $V$ we
+	define the set $Copies(S,(G, \chi))$ as the one that contains all 
+	possible $\Sigma$-hypergraphs $(H,\rho)$ isomorphic to $(G,\chi)$ 
+	such that $V(H)\subset S$.
 	Notation: $H\subset_{\Sigma}G$.
@@
 	\big) =
-	\Ln |\Omega^{\times}_n|	\mathrm{Pr}\big(
+	\Ln |\Omega^{\times}_n|\cdot \mathrm{Pr}\big(
 	(U_1,\dots, U_k) \subset G_n
@@
 	\]
-
+	Let $S$ be the underlying set of the configuration $(U_1,\dots,U_k)$.
+	Let $l= \sum_{H\in S} v(S)$. Then it is satisfied 
+	\[
+	|\Omega^{\times}_n|= \frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}.
+	\]
+	Using the definition of $(U_1,\dots, U_k) \subset G_n$ and
+	substituting $|\Omega^{\times}_n|$ we get
+	\[
+	\Ln |\Omega^{\times}_n|\cdot \mathrm{Pr}\big(
+	(U_1,\dots, U_k) \subset G_n
+	\big) = \Ln
+	\frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot
+	\PR{\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
+	(H,\rho)\subset (G_n, \chi_n^i)}.
+	\]
+	But the event $(H,\rho)\subset (G_n, \chi_n^i)$ is equivalent to $H\subset G_n$ and
+	$\chi_n^i(v)=\rho(v)$ for all $v\in V(H)$. Thus the LHS of last equation equals
+	\[
+	\Ln
+	\frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot
+	\Pr\Big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
+	\big(H\subset G_n \bigwedge_{v\in V(H)} \chi_n^i(v)=\rho(v) \big) \Big).
+	\]
+	For each $n\in \N$ let $A_n$ the event
+	\[
+	A_n:=\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
+	H\subset G_n.
+	\]	
+	Then,
+	\begin{align*}
+	&\Pr\Big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
+	\big(H\subset G_n \bigwedge_{v\in V(H)} \chi_n^i(v)=\rho(v) \big) \Big)=\\
+	&\Pr\big(A_n\big)\cdot \Pr\big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
+	\bigwedge_{v\in V(H)} \chi^i_n(v)=\rho(v) \, \big| \, A \big).
+	\end{align*}
+	It holds that
+	\[
+	\PR{A_n}=\frac{1}{n^l} \prod_{i=1}^{k}\prod_{R\in \sigma} \beta_R^{e_R(H_i)\cdot b_i},
+	\]
+	and in consequence 
+	\[
+	\Ln \frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot \PR{A_n}
+	= \frac{\prod_{i=1}^{k}\prod_{R\in \sigma} \beta_R^{e_R(H_i)\cdot b_i}}
+	{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}.
+	\]
+	Finally, using the hypothesis that 
+	$(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
+	are $\mathcal{F}$-independent we obtain
+	\[
+	\Ln \Pr\big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
+	\bigwedge_{v\in V(H)} \chi^i_n(v)=\rho(v) \, \big| \, A \big)
+	= \prod_{i=1}^{k} \prod_{v\in V(H_i)} \Pr\big[ \chi^i=\rho^i(v)\big]^{b_i}.
+	\]
+	The result follows from joining equations. 
 \end{proof}
+
+\begin{definition}
+	Let $\Sigma$ be a set containing the empty label $\emptyset$.
+	Let $V\subset [n]$. We say that a random $\Sigma$-coloring $\chi$
+	of $G_n$ is $V$-symmetric if $\chi(v)=\emptyset$ if and only if $v\in V$ and
+	for any $s\in \Sigma$ the probability $\Pr(\chi(v)=s)$ is the same for all 
+	$v\in [n]\setminus V$. \par
+	Let $V\subset \N$ be a finite set of vertices and let $(\chi^n)_{n\in \N}$
+	be a succession such that each $\chi^n$ is a random coloring of $G_n$. We
+	call the succession $(\chi^n)_{n\in \N}$ $V$-regular if each $\chi^n$ is
+	$V$-symmetric and for all $s\in \Sigma$ and $v\in \N \setminus \N$ the limit 
+	$\Ln \PR{\chi^n(v)=s}$ exists. 
+\end{definition}
+
+\begin{definition}
+	Let $\Sigma$ be a set containing the empty label $\emptyset$. A rooted $\Sigma$-edge
+	is a $\Sigma$-hypergraph $(e,\chi)$ where $e$ is an edge 
+	(i.e., an hypergraph consisting of only one edge), $v\in V(e)$ is a vertex called the root 
+	of $e$, and $\chi: V(e)\rightarrow \Sigma$ such that $\chi(u)=\emptyset$ if and only if 
+	$u=v$.\par
+	Given a rooted $\Sigma$-edge $(e,v,\chi)$, a set $V$ and a 
+\end{definition}
+
+\begin{definition}
+
+\end{definition}
 

### 2020-02-27 Article.tex
atendiendo a albert

@@
 	$u=v$.\par
-	Given a rooted $\Sigma$-edge $(e,v,\chi)$, a set $V$ and a 
+	Given a rooted $\Sigma$-edge $(e,\chi)$, a set of vertices $V$ and a vertex $v\in \N$
+	we define the set $Copies((e,\chi),(V,v))$ as the set of copies 
+	$(e^\prime, \chi^\prime) \in  Copies((e,\chi),V)$ such that $v$ is
+	 the root of $(e^\prime,\chi^\prime)$.
 \end{definition}
@@
 \begin{definition} 
+	Let $V$ be a finite set of vertices
 

### 2020-02-27 Article.tex
Auto stash before merge of "master" and "origin/master"

--- 2020-02-27 Article.tex
@@
 	is a $\Sigma$-hypergraph $(e,\chi)$ where $e$ is an edge 
+	(i.e., an hypergraph consisting of only one edge), and there is a unique vertex
+	$v\in V(e)$ such that $\chi(v)=\emptyset$.
+	Given a rooted $\Sigma$-edge $(e,v,\chi)$, a set $V$ and a 
 	(i.e., an hypergraph consisting of only one edge), $v\in V(e)$ is a vertex called the root 

### 2020-03-09 Article.tex
Demos hechas

--- 2020-02-27 Article.tex
@@
 \newcommand{\PR}[1]{\mathrm{Pr}\big(#1\big)}
+\newcommand{\Tr}{\mathrm{Tr}}
 
@@
 	\item Suppose that the $k$-equivalence relation has been
-	defined for rooted trees with radius at most $r$.
-	\begin{itemize}
-		\item Let $T_1$ and $T_2$ be rooted trees with radius
-		at most $r+1$, and let $e_1, e_2$
-		be initial edges of $T_1$ and $T_2$ respectively.
-		Then $(T_1,e_1)\simeq_k (T_2,e_2)$ if
-		$e_1$ and $e_2$ have the same color and there is a bijection 
-		$f: e_1\rightarrow e_2$ between the vertices in $e_1$ and
-		$e_2$ such that:
-		\begin{itemize}
-			\item If $e_1=[u_1,\dots, u_a]$ then $e_2=[f(u_1),\dots,f(u_a)]$.
-			\item If $v_1$ and $v_2$ are the roots of
-			$T_1$ and $T_2$ respectively, then $v_2=f(v_1)$.
-			\item For any vertex different from the root $u\in e_1$, it is satisfied that
-			\[\tau_{(T_1,v_1)}(u)\morph{k} \tau_{(T_2,v_2)}(f(u)).\]
-		\end{itemize}
-		\item Let $T_1$ and $T_2$ be rooted trees with
-		radius at most $r+1$. Then $T_1\morph{k} T_2$ if
-		for any chosen $T=T_1$ or $T=T_2$ and any initial edge
-		$e\in E(T)$, the "quantity 
-		of initial edges $e_1$ from $T_1$ that satisfy
-		$(T_1,e_1)\simeq_k (T, e)$" and the "quantity 
-		of initial edges $e_2$ from $T_2$ that satisfy
-		$(T_2,e_2)\simeq_k (T, e)$" are the same or 
+	defined for rooted trees with radius at most $r$. Let $\Sigma_r$
+	be the set consisting of the root symbol $\tau$ and
+	the $k$-equivalence classes of trees with radius lesser than $r$.
+	Given a rooted tree $(T,v)$ with whose radius is lesser than $r$
+	we define its canonical $\Sigma_r$-coloring as the map 
+	$\chi_{(T,v)}: V(T)\rightarrow \Sigma_r$ satisfying that
+	$\chi_{(T,v)}(u)$ is the $k$-equivalence class of $\mathrm{Tr}(u,T;v)$
+	for any $u\neq v$ and $\chi_{(T,v)}(v)=\tau$. \par
+	Let $T_1$ and $T_2$ be rooted trees with radius
+	at most $r+1$. We say that $(T_1,v_1)\simeq_k (T_2,v_2)$ 
+	if given any $\Sigma_r$-pattern $(e,\chi)$ the 
+	"quantity of initial edges $e_1\prime\in E(T_1)$ such that
+	$(e,\chi)\simeq (e_1,\chi_{(T_1,v_1)})$" and the
+	"quantity of initial edges $e_2\prime\in E(T_2)$ such that
+	$(e,\chi)\simeq (e_2,\chi_{(T_2,v_2)})$" are the same or
 	are both greater than $k-1$.
-
-	\end{itemize}
 \end{itemize}
@@
 
-\subsection{Probabilistic results}
+\section{Probabilistic results}
+\subsection{Convergence to Poisson variables}
 
@@
 	\Ln \mathrm{E}\big[
-	\prod_{i=1}^{k} (X_{n,i})_{r_i} \big]
+	\prod_{i=1}^{k} \binom{X_{n,i}}{r_i} \big]
 	= \prod_{i=1}^{k} \frac{\lambda_i}{r_i !}.	
@@
 \begin{proof}
-Given any one-to-one map $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be 
-the indicator variable
-that takes value one when $f$ defines an monomorphism 
-between $H$ and $G_n$ and zero otherwise. 
-The probability that $X^H_{n,f}=1$ is exactly
-$\prod_{i=1}^t \left(\frac{\beta_i}{n^{a_i-1}}\right)^{e_i(H)}$ which can
-be written as $C\cdot n^{-ex(H)-v(H)}$ for some constant
-$C$ that does not depend on $f$ nor $n$. Define 
-$X^H_n=\sum_{f\in [n]_{V(H)}} X^H_{n,f}$. Then, by definition, the number of 
-copies of $H$ in $G_n$ is exactly $X^H_n/|Aut(H)|$.
-Taking into account that 
-\[
-\mathrm{E}[X^H_n]=(n)_{v(H)} \cdot C\cdot n^{-\sum_{i=1}^t (a_i-1)\cdot e_i(H)}= \Theta(n^{-ex(H)}),
-\]
-the result follows. 
+It holds
+\[
+ \mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
+ \sum_{H^\prime \in Copies(H,[n])} \PR{H^\prime \subset G_n}.
+\]	
+We have that $|Copies(H,[n])|=\frac{(n)_{v(H)}}{|Aut(H)|}$. Also, 
+for any $H^\prime \in Copies(H,[n])$ it is satisfied
+\[
+\PR{H^\prime \subset G_n}= \prod_{R\in \sigma} \left(\frac{\beta_R}{n^{ar(R)-1}} 
+\right)^{e_R(H)}.
+\]
+Substituting in the first equation we get
+\[
+\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
+\frac{(n)_{v(H)}}{|Aut(H)|}\cdot
+\prod_{R\in \sigma} \left(\frac{\beta_R}{n^{ar(R)-1}}\right)^{e_R(H)}
+\underset{n \to \infty}{\sim}
+n^{-ex(H)} \cdot \frac{\prod_{R\in \sigma} \beta_R^{
+e_R{H} }}{|Aut(H)|}.
+\]
+
+%Given any one-to-one map $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be 
+%the indicator variable
+%that takes value one when $f$ defines an monomorphism 
+%between $H$ and $G_n$ and zero otherwise. 
+%The probability that $X^H_{n,f}=1$ is exactly
+%$\prod_{i=1}^t \left(\frac{\beta_i}{n^{a_i-1}}\right)^{e_i(H)}$ which can
+%be written as $C\cdot n^{-ex(H)-v(H)}$ for some constant
+%$C$ that does not depend on $f$ nor $n$. Define 
+%$X^H_n=\sum_{f\in [n]_{V(H)}} X^H_{n,f}$. Then, by definition, the number of 
+%copies of $H$ in $G_n$ is exactly $X^H_n/|Aut(H)|$.
+%Taking into account that 
+%\[
+%\mathrm{E}[X^H_n]=(n)_{v(H)} \cdot C\cdot n^{-\sum_{i=1}^t (a_i-1)\cdot e_i(H)}= \Theta(n^{-ex(H)}),
+%\]
+%the result follows. 
 %Indeed, let $n\in \N$ and let $G_n$ be a random hypergraph sampled from
@@
 	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big] 
-	\xrightarrow[]{n\to \infty} 0$. An application of the first moment
+	\xrightarrow[]{n\to \infty} 0$ . An application of the first moment
 	method yields the desired result. 
@@
 
+\subsubsection{Rooted hypergraphs}
+
+A rooted hypergraph $(G,\overline{u})$ is an hypergraph $H$ together with 
+an ordered sequence of distinguished vertices $\overline{u}\in (V(H))_*$.
+An isomorphism between two rooted hypergraphs $(G,\overline{u})$ and
+$(H,\overline{v})$ is a map $f: V(G)\rightarrow V(H)$ such that $f$
+is an isomorphism between $G$ and $H$ that satisfies the additional condition
+$f(\overline{u})=\overline{v}$. An automorphism of $(G,\overline{u})$  is 
+an isomorphism from $(G,\overline{u})$  to itself. 
+We write $Aut(G,\overline{u})$ to denote the group
+of automorphisms of $(G,\overline{u})$. \par
+
+Given a rooted hypergraph $(G,\overline{u})$, a set of vertices
+$V$ and a list $\overline{v}\in (V)_*$ such that $len(\overline{u})
+= len(\overline{v})$ we define the set $Copies((G,\overline{u}),
+(V,\overline{v}))$ as the set of rooted hypergraphs 
+$(H,\overline{v})$ isomorphic to $(G,\overline{u})$ such that
+$V(H)\subset V$. \par
+
 \begin{lemma}\label{lem:nocopiesfixed}
-	Let $\overline{v}:=(v_1,\dots,v_j)\in \N*$.
-	Let $H$ be an hypergraph such that $ex(H)>-j$. 
-	Then a.a.s there is no copy of $H$ in $G_n$ that
-	contains all $v_1,\dots,v_j$. 
+	Let $(H,\overline{u})$ be a rooted hypergraph. Let
+	$\overline{v}\in (\N)_*$ be a list of vertices satisfying
+	$len(\overline{u})=len(\overline{v})$. For each $n\in \N$ 
+	let $X_n$ be the random variable that
+	counts the copies $(H^\prime,\overline{v})\in
+	Copies((H,\overline{u}),
+	([n],\overline{v}))$ that are contained in $G_n$. Then
+	$\mathrm{E}\big[ X_n \big]=\Theta(n^{-ex(H)-len(\overline{u})})$.	
 \end{lemma}
 \begin{proof}
-It is sufficient to show that
-\begin{equation}\label{eqn:aux}
-\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
-\overline{v} \big]\xrightarrow[]{n\to \infty} 0.
-\end{equation}
-Then, because of a first moment argument the result follows.\par
-Suppose that $v(H)\geq j$. Otherwise the statement is trivial. 
-As before, given any $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be the random
-variable that takes value one if $f$ is a monomorphism from $H$ to $G_n$
-and zero otherwise. The probability that $X^H_{n,f}$ takes value one is
-$C\cdot n^{-ex(H)-v(H)}$ for some constant $C$ independent from $f$ and $n$. 
-Let 
-\[ Y^H_{n,\overline{x}}= \sum_{\substack{f\in [n]_{V(H)}\\ 
-\overline{x}\subset Im(f)}} X^H_{n,f}.\]
-The number of functions $f\in [n]_{V(H)}$ such that $v_1,\dots,v_j\in Im(f)$
-is $\Theta(n^{v(H)-j})$. In consequence 
-$
-\mathrm{E}\big[Y^H_{n,\overline{v}}\big]=\Theta(n^{-ex(H)-j})
-$, and 
-\[\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
-\overline{v} \big]=\Theta(n^{-ex(H)-j}).
-\]
-This, together with $ex(H)>-j$, proves \cref{eqn:aux}. 
+	It holds
+	\[
+	\mathrm{E}\big[ X_n \big]=\sum_{H^\prime\in (H^\prime,\overline{v})\in
+		Copies((H,\overline{u})} \PR{H^\prime \subset G_n}
+	= \frac{(n)_{(v(H)-len(\overline{u}))}}{|Aut(H,\overline{u})|} 
+	\cdot\prod_{R\in\tau} \left( \frac{\beta_R}{n^{ar(R)-1}}\right)^{e_R(H)}
+	\]
 \end{proof}
+
+%
+%\begin{lemma}
+%	Let $\overline{v}:=(v_1,\dots,v_j)\in \N*$.
+%	Let $H$ be an hypergraph such that $ex(H)>-j$. 
+%	Then a.a.s there is no copy of $H$ in $G_n$ that
+%	contains all $v_1,\dots,v_j$. 
+%\end{lemma} 
+%\begin{proof}
+%It is sufficient to show that
+%\begin{equation}\label{eqn:aux}
+%\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
+%\overline{v} \big]\xrightarrow[]{n\to \infty} 0.
+%\end{equation}
+%Then, because of a first moment argument the result follows.\par
+%Suppose that $v(H)\geq j$. Otherwise the statement is trivial. 
+%As before, given any $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be the random
+%variable that takes value one if $f$ is a monomorphism from $H$ to $G_n$
+%and zero otherwise. The probability that $X^H_{n,f}$ takes value one is
+%$C\cdot n^{-ex(H)-v(H)}$ for some constant $C$ independent from $f$ and $n$. 
+%Let 
+%\[ Y^H_{n,\overline{x}}= \sum_{\substack{f\in [n]_{V(H)}\\ 
+%\overline{x}\subset Im(f)}} X^H_{n,f}.\]
+%The number of functions $f\in [n]_{V(H)}$ such that $v_1,\dots,v_j\in Im(f)$
+%is $\Theta(n^{v(H)-j})$. In consequence 
+%$
+%\mathrm{E}\big[Y^H_{n,\overline{v}}\big]=\Theta(n^{-ex(H)-j})
+%$, and 
+%\[\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
+%\overline{v} \big]=\Theta(n^{-ex(H)-j}).
+%\]
+%This, together with $ex(H)>-j$, proves \cref{eqn:aux}. 
+%\end{proof}
 
@@
 	such that $V(H)\subset S$.	
-	Notation: $H\subset_{\Sigma}G$.
-
 \end{definition}
@@
 	is a $\Sigma$-hypergraph $(e,\chi)$ where $e$ is an edge 
-	(i.e., an hypergraph consisting of only one edge), $v\in V(e)$ is a vertex called the root 
-	of $e$, and $\chi: V(e)\rightarrow \Sigma$ such that $\chi(u)=\emptyset$ if and only if 
-	$u=v$.\par
-	Given a rooted $\Sigma$-edge $(e,v,\chi)$, a set $V$ and a 
+	(i.e., an hypergraph consisting of only one edge), and there is a unique vertex
+	$v\in V(e)$ such that $\chi(v)=\emptyset$.
+	Given a rooted $\Sigma$-edge $(e,\chi)$, a set of vertices $V$ and a vertex $v\in \N$
+	we define the set $Copies((e,\chi),(V,v))$ as the set of copies 
+	$(e^\prime, \chi^\prime) \in  Copies((e,\chi),V)$ such that $v$ is
+	the root of $(e^\prime,\chi^\prime)$.
 \end{definition}
@@
 \begin{definition} 
-
+	Let $V\subset \N$ be a finite set of vertices. 
+	Let $\Sigma_1,\dots, \Sigma_k$ be sets containing the empty label 
+	$\emptyset$. For each $i\in [k]$ and each $n\in \N$
+	let $\chi_i^n$ be a random $\Sigma_i$-coloring
+	of $G_n$ satisfying that the succession $(\chi_i^n)_{n\in \N}$ is
+	$V$-regular. We say that the sequences $(\chi_1^n)_{n\in \N},
+	\dots, (\chi_k^n)_{n\in \N}$ are asymptotically independent
+	with respect to edges intersecting $V$ if for any given
+	\begin{itemize}
+		\item fixed finite set of edges $S\subset E(\N)$ such that any edge $e\in S$ 
+		contains some vertex in $V$,
+		\item fixed disjoint sets of vertices $V_1,\dots, V_k \subset \bigcup_{e\in S}e$ 
+		satisfying $V\cup V_i=\emptyset$ for all $i\in [k]$, and
+		\item for each $i\in [k]$ and $v\in V_i$ a fixed label $s(v)\in \Sigma_i$
+		different from the empty label,
+	\end{itemize}
+	it is satisfied 
+	\[
+	\Ln \mathrm{Pr}\big(
+	\bigwedge_{i=1}^k \bigwedge_{v\in V_i} \chi_{n,i}(v)=s(v)
+	\, \big| \, \bigwedge_{e\in S} e\subset G_n \,
+	\big) = \prod_{i=1}^k \prod_{v\in V_i} \mathrm{Pr}\big[\chi_i=s(v)
+	\big]		
+	\]
 \end{definition}
+
+\begin{theorem}
+	\begin{theorem}
+		Let $k\in \N$.	For each $i\in [k]$ 
+		\begin{itemize}
+			\item Let $v_i\in \N$ be a vertex. Define $V:=\{v_1,\dots,v_k\}$.
+			\item Let $\Sigma_i$ be a set containing the empty label, and let $S_i$ be a set
+			of non-isomorphic rooted $\Sigma_i$-edges. 
+			\item For each $n\in \N$ let $\chi^i_n$ be random $\Sigma_i$-coloring
+			$G_n$ satisfying that the succession $(\chi^i_n)_{n\in \N}$ is $V$-regular. 
+			\item For each $(e,\rho)\in S_i$, let $X^{(e,\rho)}_{n,i}$ be the random 
+			variable that counts the number of copies in $Copies((e,\rho),([n],v_i))$
+			that appear in $(G_n,\chi^i_n)$.				
+		\end{itemize}
+		Suppose that the
+		successions $(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
+		are independent with respect to edges intersecting $V$.
+		Then, for any fixed natural numbers 
+		$(a^{(e,\rho)}_{i})_{i\in [k], (e,\rho)\in S_i}$ it holds
+		\[
+		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k \bigwedge_{(e,\rho)\in S_i}
+		 X_{n,i}=a^{(e,\rho)}_i  \big)=
+		\prod_{i=1}^{k}e^{-\lambda_i}\frac{\lambda_{(e,\rho)}^{a^{(e,\rho)}_i}}{{a^{(e,\rho)}_i}!},
+		\]
+		where for each $i\in [k]$,
+		\[
+		\lambda_{(e,\rho)}:= \frac{1}{|Aut(e,\rho)|} 
+		\prod_{v\in V(e), \rho(v)\neq \emptyset}
+		\mathrm{Pr}\big[\chi^i=\rho^i(v)\big].
+		\]
+	\end{theorem}
+\end{theorem}
 
@@
 
-\begin{theorem} 
-	The following are satisfied:
+\begin{theorem} \label{thm:BigTrees}
+	Fix $r\in \N$. The following are satisfied:
 	\begin{itemize}
-		\item[(1)] Let $r\in \N$ and let $\mathcal{T}$ be a
+		\item[(1)] Let $\mathcal{T}$ be a
 		$k$-equivalence class for trees with radii at most $r$.
@@
 		in $\Lambda$.
-		\item[(2)] Let $\overline{u}\in \N*$ be a list of different fixed 
+		\item[(2)] Let $\overline{u}\in (\N)_*$ be a list of different fixed 
 		vertices, and let $\phi[\overbar{x}]\in FO[\sigma]$ be a consistent
-		open sentence (i.e. with no bounded variables) such that 
-		$length(\overbar{x})=length(\overbar{w})$.
-		Let $=v_1,\dots,v_k \in \N$ be different vertices
-		contained in $\overline{u}$.
-		Let $r_1,\dots,r_k \in \N$ and let $\mathcal{T}_1,\dots \mathcal{T}_k$
-		be $k$-equivalence classes for trees such that
-		each $\mathcal{T}_i$ has radii bounded by the correspondent
-		$r_i$. Then
-		\[
-		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
-		Tr\big(G_n(\overbar{u}),v_i;r\big)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
-		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]. \]	 	
+		edge sentence such that 
+		$len(\overbar{x})=len(\overbar{u})$.
+		Let $\overline{v}\in (\N)_*$ be vertices contained
+		in $\overline{u}$. For each $v\in \overline{v}$
+		let $\mathcal{T}_v$ be a $k$-equivalence class
+		of trees with radii	at most $r$. Then
+		\[
+		\Ln \mathrm{Pr}\big( \bigwedge_{v\in \overline{v}} 
+		Tr\big(G_n, \overbar{u},v;r\big)\in \mathcal{T}_v 
+		\, | \, \sigma(\overbar{w})
+		\big)= \prod_{v\in \overline{v}} \mathrm{Pr}[r,\mathcal{T}_v]. \]	 	
 	\end{itemize}
+\end{theorem}
 	\begin{proof}
-		Let $R$ be an upper bound of the radius of $r$ and the 
-		$r_i$'s	in the statement. 
-		We will prove (1) and (2) together by induction on $R$. \par
-		Assume $R=0$. We start by showing that (1) holds. Recall that
+		We will prove (1) and (2) together by induction on $r$. \par
+		Assume $r=0$. We start by showing that (1) holds. Recall that
 		all trees with radius zero are $k$-equivalent. Thus, if
@@
 		$\Lambda$, so (1) holds. \par
-		The case of (2) is analogous. As $R=0$, then $\mathcal{T}_1=\dots=
+		The case of (2) is analogous. As $r=0$, then $\mathcal{T}_1=\dots=
 		\mathcal{T}_k$ are the unique $k$-equivalence class of trees with
@@
 		in the statement,
-		\[\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
-		Tr\big(G_n(\overbar{u}),v_i;r\big)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
-		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]=1. \]	 	
+		\[\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^l
+		Tr\big(G_n, \overbar{u},v_i;0\big)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
+		\big)= \prod_{i=1}^l \mathrm{Pr}[0,\mathcal{T}_i]=1. \]	 	
 		Because of (1), $\mathrm{Pr}[0,\mathcal{T}_i]=1$ for all $i$'s, 
 		and (2) holds. \par
-		Now let $R>0$ and assume that both (1) and (2) hold for all 
-		lesser values of $R$.  \par
-		Let $T_{n,i}=Tr\big(G_n(\overbar{u}),v_i;r\big)$. 
-		Let $i\in [k]$ and let $\mathcal{E}$ be any $k$-equivalence class
-		of initial edges of radius at most $r_i$. Then we define $X_{n,i,\mathcal{E}}$
-		as the random variable that counts the number of initial edges $e$ such that
-		$(T_{n,i},e)\in \mathcal{E}$.\par
-		We are going to show that the variables $X_{n,i,\mathcal{E}}$ converge, as
+		Now let $r>0$ and assume that both (1) and (2) hold for all
+
+		Via similar computations we can show that for any fixed
+		$v\in \overline{v}$.
+
+		We are going to show that the variables $X_{n,i,\epsilon}$ converge, as
 		$n$ tends to infinity, to independent Poisson variables 
-		$\mathrm{Poiss}(\mu_{r_i,\mathcal{E}})$ whose means $\mu_{r_i,\mathcal{E}}$ 
-		are expressions in the family $M$. That is,
+		$\mathrm{Poiss}(\mu_{r_i,\epsilon})$ whose means $\mu_{r_i,\epsilon}$ 
+		are expressions in the family $M$. Let $[\Sigma_{r_i}]$ be the set of
+		$\Sigma_{r_i}$-patterns. We want to prove: 
 		\begin{equation} \label{eqn:PoissonEdges}
-		\Ln \mathrm{Pr}\big(
-		\bigwedge_{i=1}^k \bigwedge_{\mathcal{E} \in EDGE_{r_i}} X_{n,i,\mathcal{E}}=a_{i,\mathcal{E}}
-		\, | \, \sigma(\overline{w})\big) =
-		\prod_{i=1}^k \prod_{\mathcal{E} \in EDGE_{r_i}} e^{-\mu_{r_i,\mathcal{E}}}
-		\frac{\mu_{r_i,\mathcal{E}}^{a_{i,\mathcal{E}}}}{a_{i,\mathcal{E}}!}
+		\Ln \mathrm{Pr}\Big(
+		\bigwedge_{i=1}^k \bigwedge_{\epsilon \in [\Sigma_{r_i}]} X_{n,i,\epsilon}=a_{i,\epsilon}
+		\, | \, \sigma(\overline{w})\Big) =
+		\prod_{i=1}^k \prod_{\epsilon \in [\Sigma_{r_i}]} e^{-\mu_{r_i,\epsilon}}
+		\frac{(\mu_{r_i,\epsilon})^{a_{i,\epsilon}}}{a_{i,\epsilon}!}
 		\end{equation}
-		Furthermore, for each $i$ and $\mathcal{E}$ we will prove that the mean 
-		$\mu_{r_i,\mathcal{E}}$ does only depend on $r_i$ and $\mathcal{E}$.
+		Furthermore, for each $i$ and $\epsilon$ we will prove that the mean 
+		$\mu_{r_i,\epsilon}$ does only depend on $r_i$ and $\epsilon$.
 		This proves both (1), and (2).\par
-
-		We will prove \cref{eqn:PoissonEdges} using \cref{thm:BrunSieve}.
-		For each $i\in [k]$ and $\mathcal{E}\in EDGE_{r_i}$ we define $\mu[r_i,\mathcal{E}]$
-		in the following way. Let $(T,e)$ be a representative of the equivalence class
-		$\mathcal{E}$. Let $p$ be the root of $T$ and let $j$ be the color of $e$. 
-		Let $b$ be the number of bijections $f:e\rightarrow e$ satisfying that (1)
-		$f(p)=p$, and (2) for any $q\in e$ different from $p$
-		$\tau_{(T)}(q) \simeq_k \tau_{(T)}(f(q))$. For any $q\in e$ 
-		different from $p$, let $\mathcal{T}_q$ be the $k$-equivalence class
-		of the tree $\tau_{(T)}(q)$. Then
-		\[
-		\mu_[r_i,\mathcal{E}]=\frac{\beta_j}{b} \prod_{\substack{q\in e \\ q\neq p}} 
-		\mathrm{Pr}[r_i-a_j+1,\mathcal{T}_q].
-		\]
-
-		Now we have to prove that for any non-negative numbers, 
-		$(d_{i,\mathcal{E}})_{\substack{i\in [k]}\\
-		\mathcal{E}\in EDGE_{r_i}}$, it is satisfied
-		\[\Ln
+		Given an $\Sigma_{r_i}$-pattern $\epsilon$ and any 
+		$(e,\chi)\in Copies(\epsilon,[n])$ we say that $(e,\chi)\in T_{n,i}$
+		if the following are satisfied: (1)	$e$ is an initial edge of $T_{n,i}$,
+		and	(2) that for any $v\in e$ such that $v\neq v_i$, it holds that
+		$\chi(v)$ is the $\simeq_k$ class of $Tr(T_{n,i},v)$.\par 
+		Given $r\in \N$ and $\epsilon\in \Sigma_{r}$
+		we define
+		$\mu_{r,\epsilon}$ as follows. Let $(e,\chi)$ be any representative of
+		$\epsilon$. Then
+		\[\mu_{r,\epsilon}=  \frac{\beta_{R(e)}}{|Aut(e,\chi)|}
+		\prod_{\substack{v\in e\\ \chi(v)\neq \tau }} \Pr[r,\chi(v)]. \]
+		For each $i\in [l]$ and $\epsilon\in [\Sigma_{r_i}]$ let 		
+		$b_{i,\epsilon}\in \N$ be fixed.
+
+		We want to prove
+		\[
+		\Ln \mathrm{E}\left[\prod_{\substack{i\in [l]\\ \epsilon \in [\Sigma_{r_i}]}} \binom{X_{n,i,\epsilon}}{b_{i,\epsilon}}
+		\right]= \prod_{\substack{i\in [l]\\ \epsilon \in [\Sigma_{r_i}]}}
+		\frac{(\mu_{r_i,\epsilon})^{b_{i,\epsilon}}}{b_{i,\epsilon}!}.
+		\]
+		Because \cref{thm:BrunSieve} this is sufficient to prove \cref{eqn:PoissonEdges}. \par
+		For each $n\in \N$ define
+		\begin{align*}
+		\Omega_n=&\Bigg\{
+		(E_{v,\epsilon})_{\substack{v\in \overline{v}\\ \epsilon
+		\in [\Sigma_{r(v)}]}} \quad \Big|\\ 
+		&  \forall v\in \overline{v},
+		\forall \epsilon \in [\Sigma_{r(v)}]\, \quad  E_{v,\epsilon}\subset
+		Copies(\epsilon,[n],\overline{w};v)\quad  \wedge \quad |E_{v,\epsilon}|=b_{v,\epsilon}\Bigg\}.
+		\end{align*}
+		Informally, the elements $(E_{v,\epsilon})_{v,\epsilon}$
+		of $\Omega_n$ are represent all choices of
+		possible initial edges for the $T_{n,v}$'s: For each $v\in \overline{v}$
+		and each $\epsilon\in [\Sigma_{r(v)}]$, $E_{n,v,\epsilon}$ selects
+		$b_{v,\epsilon}$ possible initial edges of $T_{n,v}$
+		with pattern $\epsilon$.\par
+%	 	Given an element $O\in \Omega_n$, with
+%	 	$O=\big(O_{i,\epsilon}\big)_{i\in [l], \epsilon \in [\Sigma_{r_i}]}$,
+%	 	we write $O\in G_n$ if
+		Using observation REF we obtain that
+		\[
+		\mathrm{E}\Big[\prod_{\substack{i\in [l]\\ \epsilon \in [\Sigma_{r_i}]}} \binom{X_{n,i,\epsilon}}{b_{i,\epsilon}}
+		\Big]= \sum_{(E_{v,\epsilon})_{v,\epsilon} \in \Omega_n
+		}		
+		\Pr \left( \bigwedge_{\substack{v\in \overline{v} \\ \epsilon \in
+		[\Sigma_{r(v)}]\\ (e,\chi) \in E_{v,\epsilon} }} \left( e\in E(T_{n,i}) 
+		\bigwedge_{u\in V(e), u\neq v} Tr(T_{n,v};u)\in \chi(u)
+		\right)  \right)
+		\]
+		Let $(E_{v,\epsilon})_{v,\epsilon}\in \Omega_n$. 
+		In order for $e\in E(T_{n,v})$ to be possible for all
+		$v\in \overline{v}$, $\epsilon\in [\Sigma_{r(v)}]$, 
+		$e\in E_{v,\epsilon}$ it is needed that each vertex 
+		in $[n]\setminus \overline{w}$ belongs at most to one
+		edge $(e,\chi)\in \cup_{v,\epsilon} \, E_{v,\epsilon}$.
+		This is because if for some 
+		\[
+		\bigwedge_{\substack{i\in [l]\\ \epsilon \in
+		[\Sigma_{r_i}]\\ (e,\chi) \in O_{i,\epsilon} }} \left( e\in E(T_{n,i}) 
+		\bigwedge_{v\in e, v\neq v_i} Tr(T_{n,i},v)\in \chi(v)
+		\right) 
+		\] 
+		to be possible it is needed that each $v\in $
+	\end{proof}
+
+	\newpage
+	\begin{lemma}
+	Let $r\in \N$, $r>0$. Let $\mathcal{T}$ be a 
+	$\simeq_k$ class of trees with radii at most $r$.
+	Suppose that \cref{thm:BigTrees} holds
+	for $r-1$. Then $\Pr\big[r, \mathcal{T}\big]$ 
+	exists and is and expression in $\Lambda$.   
+	\end{lemma}
+	\begin{proof}
+		Fix a vertex $v\in \N$. For each $n$ let
+		$T_n:=Tr(G_n,v;r)$. We are going to show that
+		$\Ln \PR{T_n\in \mathcal{T}}$ exists and it is an 
+		expression in $\Lambda$. \par
+		For any $(k,r)$-pattern  $\epsilon$  let 
+		$X_{n,\epsilon}$ be the random variable that counts
+		the initial edges in $T_n$ whose $k$-pattern
+		is $\epsilon$. In other words, $X_{n,\epsilon}$ counts
+		the colored edges $(e,\tau)\in Copies(\epsilon,[n],v)$ 
+		such that $e$ is an initial edge in $T_n$ satisfying that
+		for any $u\in V(e)$ with $u\neq v$, it holds
+		$Tr(T_n(v),u)\in \tau(u)$. Thus,
+		\[
+		\mathrm{E}\big[ X_{n,\epsilon} \big]
+		= \sum_{(e,\tau)\in Copies(\epsilon,[n];v)} \Pr
+		\left(e\in E(T_n)
+		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_{n}, v; u)\in 
+		\tau(u) \right).
+		\]
+		Because of the symmetry of our random model the probability 
+		in the RHS of last equation is the same for all 
+		$(e,\tau)\in Copies(\epsilon,[n],;v)$. Let
+		$(e,\tau)\in Copies(\epsilon,\N;v)$ be fixed. 
+		Using that 
+		$|Copies(\epsilon,[n],v)|=\frac{(n)_{|e|-1}}
+		{|Aut(\epsilon)|}$ we obtain
+		\[
+		\mathrm{E}\big[ X_{n,\epsilon} \big]
+		=
+		\frac{(n)_{|e|-1}}{|
+			Aut(\epsilon)|} \Pr
+		\left(e\in E(T_{n})
+		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_n, v; u)\in \tau(u) \right).
+		\]
+		Also, it is satisfied
+		\begin{align*}
+		&\Pr
+		\left( e\in E(T_{n})
+		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_n, v; u)\in 
+		\tau(u) \right)=\\
+		&\PR{ e\in E(G_n)} \cdot
+		\Pr
+		\left( e\in E(T_{n})
+		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_{n}, v; u)\in \tau(u) \, \Bigg| \,  e\in E(G_n) \right)
+		\end{align*}
+		Using REF and $\PR{e\in E(G_n)}=\frac{\beta_{R(e)}}{n^{|e|-1}}$, 
+		the RHS of last equation is asymptotically equivalent
+		to
+		\[
+		\frac{\beta_{R(e)}}{n^{|e|-1}} \cdot
+		\Pr	\left(
+		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_{n}, v; u)\in \tau(u) \, \Bigg| \,  e\in E(G_n) \right)
+		\]
+		Fix $\overbar{u}\in (\N)_*$ a list that contains exactly the vertices
+		in $e$. Then it holds that
+		$Tr(T_{n}, v, u)=Tr(G_n(\overline{u}),u;r-1)$. 
+		Thus,
+		\[
+		\Pr	\left(
+		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_{n}, v; u)\in \tau(u) 
+		\, \Bigg| \,  e\in E(G_n) \right)
+		=
+		\Pr \left(
+		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(G_n(\overline{u}), u;
+		r-1)\in \tau(u) \, \Bigg| \,  e\in E(G_n) \right)
+		\]		
+		The event $e\in E(G_n)$ can be written as an edge sentence
+		whose variables are interpreted as vertices in $\overline{u}$.
+		Thus, by hypothesis, the RHS of last equality
+		is asymptotically equivalent to
+		$\prod_{\substack{u\in V(e)\\ u\neq v} } \Pr\big[
+		r-1, \tau(u)\big]$.
+		Finally, joining everything we obtain
+		\[
+		\Ln
+		\mathrm{E}\big[ X_{n,\epsilon} \big]
+		= \Ln \frac{(n)_{|e|-1}}{|Aut(\epsilon)|}
+		\cdot  \frac{\beta_{R(e)}}{n^{|e|-1}}
+		\prod_{\substack{u\in V(e)\\ u\neq v} }
+		\Pr\big[
+		r-1, \tau(u)\big] =
+		\frac{\beta_{R(e)}}{|Aut(\epsilon)|} 
+		\prod_{\substack{u\in V(e)\\ u\neq v} } \Pr\big[
+		r-1, \tau(u)\big].
+		\]
+		For each $\epsilon\in [(k,r)]$ we define $\mu_{r,\epsilon}$ 
+		as follows: let $(e,\tau)$ be a representative of $\epsilon$
+		whose root is $v$. Then
+		\[
+		\mu_{r,\epsilon}=\frac{\beta_{R(e)}}{|Aut(\epsilon)|} 
+		\prod_{\substack{u\in V(e)\\ u\neq v} } \Pr\big[
+		r-1, \tau(u)\big].
+		\]
+		Notice that $\mu_{r,\epsilon}$ depends only on $r$ and $\epsilon$
+		and it is an expression belonging to $M$. \par
+		We are going to prove that the variables $X_{n,\epsilon}$
+		converge in distribution to independent Poisson variables 
+		with mean values $\mu_{r,\epsilon}$ respectively. For
+		each $\epsilon\in [(k,r)]$ let $b_\epsilon\in \N$. We want 
+		to show that
+		\begin{equation} \label{eqn:binomexpedges}
+		\Ln
+		\mathrm{E}
+		\left[
+		\prod_{\epsilon\in [(k,r)]} \binom{X_{n,\epsilon}}{b_\epsilon}	
+		\right]
+		= \prod_{\epsilon\in [(k,r)]} \frac{(\mu_{r,\epsilon})^
+		{b_\epsilon}}{b_\epsilon!}.	
+		\end{equation}
+		For each $n\in \N$ define
+		\[
+		\Omega_n:=\left\{
+		(E_\epsilon)_{\epsilon\in [(k,r)]} \quad 
+		\Big | \quad \forall \epsilon\in [(k,r)] \quad
+		E_\epsilon\subset Copies(\epsilon,[n],v), 
+		\quad |E_\epsilon|=b_\epsilon	
+		\right\}		
+		\]
+		Informally, elements of $\Omega_n$ represent choices of 
+		$b_\epsilon$ possible initial edges of $T_n$ whose $k$-
+		pattern is $\epsilon$ for all $(k,r)$-patterns $\epsilon$. 	
+		Using observation REF we obtain
+		\[
+		\mathrm{E}
+		\left[
+		\prod_{\epsilon\in [(k,r)]} \binom{X_{n,\epsilon}}{b_\epsilon}	
+		\right]
+		= 
+		\sum_{
+		(E_\epsilon)_{\epsilon\in [(k,r)]}
+		\in \Omega_n}
+		\Pr\left(
+		\bigwedge_{\substack{
+		\epsilon\in [(k,r)]\\
+		(e, \tau)\in E_{\epsilon}
+		}} \left(
+		e\in E(T_n) \bigwedge_{\substack{
+		u\in V(e)\\
+		u\neq v}} Tr(T_n,v,u)\in \tau(u)		
+		\right)
+		\right). 		
+		\]
+		We say that an element $(E_\epsilon)_{\epsilon\in [(k,r)]}$
+		of $\Omega_n$ is \textbf{disjoint} each vertex 
+		$w\in [n]\setminus\{v\}$ belongs to at most one edge 
+		$(e,\tau)\in\bigcup_{\epsilon\in [(k,r)]} E_\epsilon$
+		Notice that if we want the probability in the last sum to be greater 
+		than $0$ for a particular $(E_\epsilon)_{\epsilon\in [(k,r)]}
+		\in \Omega_n$ then necessarily $(E_\epsilon)_{\epsilon\in [(k,r)]}$
+		is disjoint. 
+		Indeed, suppose that a vertex $w\in [n]\setminus \{v\}$ belongs to two different 
+		edges $(e_1, \tau_1),$ $(e_2,\tau_2)\in \bigcup_{\epsilon\in [(k,r)]} E_\epsilon$. 
+		In consequence $e_1$ and $e_2$ form a cycle, as they 
+		both contain $v$ and $w$. This implies that $e_1, e_2 \notin E(T_n)$.
+		\par
+		For each $n\in \N$ let $\Omega_n^\prime\subset \Omega_n$ be the set
+		of disjoint elements in $\Omega_n$. Then
+		\[
+		\mathrm{E}
+		\left[
+		\prod_{\epsilon\in [(k,r)]} \binom{X_{n,\epsilon}}{b_\epsilon}	
+		\right]
+		= 
+		\sum_{
+			(E_\epsilon)_{\epsilon\in [(k,r)]}
+			\in \Omega_n^\prime}
+		\Pr\left(
+		\bigwedge_{\substack{
+				\epsilon\in [(k,r)]\\
+				(e, \tau)\in E_{\epsilon}
+		}} \left(
+		e\in E(T_n) \bigwedge_{\substack{
+				u\in V(e)\\
+				u\neq v}} Tr(T_n,v,u)\in \tau(u)		
+		\right)
+		\right). 		
+		\] 
+		Also, because of the symmetry of the random model, 
+		for all disjoint elements 
+		$(E_\epsilon)_{\epsilon\in [(k,r)]}$ the probability 
+		in last sum is the same. In consequence, if we fix
+		$(E_\epsilon)_{\epsilon\in [(k,r)]}\in \Omega^\prime_\N$
+		we obtain
+		\[
+		\mathrm{E}
+		\left[
+		\prod_{\epsilon\in [(k,r)]} \binom{X_{n,\epsilon}}{b_\epsilon}	
+		\right]
+		= 
+		|\Omega_n^\prime|\cdot
+		\Pr\left(
+		\bigwedge_{\substack{
+				\epsilon\in [(k,r)]\\
+				(e, \tau)\in E_{\epsilon}
+		}} \left(
+		e\in E(T_n) \bigwedge_{\substack{
+				u\in V(e)\\
+				u\neq v}} Tr(T_n,v,u)\in \tau(u)		
+		\right)
+		\right). 		
+		\] 
+		Let $\overbar{w}\in (\N)_*$ be a list containing exactly
+		the vertices $u\in V(e)$ for all $e\in 
+		\bigcup_{\epsilon\in [(k,r)]} E_\epsilon$. Then, 
+		for any $e\in 
+		\bigcup_{\epsilon\in [(k,r)]} E_\epsilon$ and any
+		any $V(e)$ with $u\neq v$ it holds that
+		if $e\in E(T_n)$ then 
+		$Tr(T_n,v,u)=Tr(G_n,\overline{w},u;r-1)$. Then
+		\[
+		\mathrm{E}
+		\left[
+		\prod_{\epsilon\in [(k,r)]} \binom{X_{n,\epsilon}}{b_\epsilon}	
+		\right]
+		= 
+		|\Omega_n^\prime|\cdot
+		\Pr\left(
+		\bigwedge_{\substack{
+				\epsilon\in [(k,r)]\\
+				(e, \tau)\in E_{\epsilon}
+		}} \left(
+		e\in E(T_n) \bigwedge_{\substack{
+				u\in V(e)\\
+				u\neq v}} Tr(G_n,\overline{w},u;r-1)\in \tau(u)		
+		\right)
+		\right). 		
+		\] 
+		Counting vertices and automorphisms we get that
+		\[
+		|\Omega_n^\prime|= (n)_{\sum_{\epsilon\in [(k,r)]} 
+			(|\epsilon|-1)\cdot b_\epsilon}
+		\prod_{\epsilon\in [(k,r)]}
+		\frac{1}{b_\epsilon!} \cdot
+		\left( \frac{1}{|Aut(\epsilon)|} \right)^
+		{b_\epsilon} .
+		\]
+		Also, using REF
+		\begin{align*}
+		&\Pr\left(
+		\bigwedge_{\substack{
+				\epsilon\in [(k,r)]\\
+				(e, \tau)\in E_{\epsilon}
+		}} \left(
+		e\in E(T_n) \bigwedge_{\substack{
+				u\in V(e)\\
+				u\neq v}} Tr(G_n,\overline{w},u;r-1)
+			\in \tau(u)		
+		\right)
+		\right)\sim\\
+		&\Pr\left(
+		\bigwedge_{\substack{
+				\epsilon\in [(k,r)]\\
+				(e, \tau)\in E_{\epsilon}
+		}} e\in E(G_n)
+		\right)\cdot 		
+		\Pr\left(
+		\bigwedge_{\substack{
+				\epsilon\in [(k,r)]\\
+				(e, \tau)\in E_{\epsilon}\\
+				u\in V(e)\\
+				u\neq v
+		}}Tr(G_n,\overline{w},u;r-1)\in \tau(u)	
+		\, \Bigg| \, 
+		\bigwedge_{\substack{
+		\epsilon\in [(k,r)]\\
+		(e, \tau)\in E_{\epsilon}
+		}} e\in E(G_n)
+		\right).
+		\end{align*}
+		The event 
+		$ \bigwedge_{\substack{
+				\epsilon\in [(k,r)]\\
+				(e, \tau)\in E_{\epsilon}
+		}} e\in E(G_n)$ clearly can be described via an edge sentence
+	whose variables are interpreted as vertices in $\overline{w}$. Thus,
+	by hypothesis last product of probabilities is asymptotically equivalent
+	to
+	\[
+	\prod_{\epsilon\in [(k,r)]}
+	\left(\frac{\beta_{R(\epsilon)}}
+	{n^{|\epsilon|-1}}\right)^{b_\epsilon} \cdot
+	\prod_{\epsilon\in [(k,r)]} (\lambda_{r,\epsilon})^{b_\epsilon}.
+	\]
+	Joining everything we obtain 
+	\begin{align*} 
+	\Ln
+	\mathrm{E}
+	\left[
+	\prod_{\epsilon\in [(k,r)]} \binom{X_{n,\epsilon}}{b_\epsilon}	
+	\right]
+	= \Ln  
+	\frac{(n)_{\sum_{\epsilon\in [(k,r)]}(|\epsilon|-1)\cdot b_\epsilon}}
+	{n^{\sum_{\epsilon\in [(k,r)]}(|\epsilon|-1)\cdot b_\epsilon}}
+	\cdot
+	\prod_{\epsilon\in [(k,r)]}
+	\frac{1}{b_\epsilon!} \cdot
+	\left( \frac{\beta_{R(\epsilon)}}{|Aut(\epsilon)|} \right)^
+	{b_\epsilon} \cdot 
+	(\lambda_{r,\epsilon})^{b_\epsilon}&\\
+	= \prod_{\epsilon\in [(k,r)]}
+	\frac{\left( \mu_{r,\epsilon} \right)^
+	{b_\epsilon}}{b_\epsilon!}
+	,&
+	\end{align*}
+	as we wanted. In consequence, by \cref{thm:BrunSieve},
+	given $a_{\epsilon}\in \N$ for all $\epsilon\in [(k,r)]$
+	it holds
+	\[
+	\Ln
+	\Pr\left( 
+	\bigwedge_{\epsilon \in [(k,r)]} X_{n,\epsilon}=a_\epsilon
+	\right)=
+	\prod_{\epsilon\in [(k,r)]} e^{-\mu_{r,\epsilon}}
+	\frac{(\mu_{r,\epsilon})^{a_\epsilon}}{a_\epsilon!}.
+	\]
+	Notice that, because of the definition of $\simeq_k$, 
+	the event $T_n\in \mathcal{T}$ is equivalent to 
+	\[
+	\left(\bigwedge_{\epsilon \in E^1_\mathcal{T}}
+	X_{n,\epsilon}\geq k 
+	\right) \wedge \left(\bigwedge_{\epsilon \in E^2_\mathcal{T}}
+	X_{n,\epsilon}=a_\epsilon\right),
+	\]
+	for some partition $E^1_\mathcal{T}, E^2_\mathcal{T}$
+	of $[(k,r)]$ that only depends on $\mathcal{T}$ and some
+	natural numbers $a_\epsilon < k$ for each $\epsilon\in
+	E^2_\mathcal{T}$ that only depend on $\mathcal{T}$ as well. 
+	In consequence 
+	\[
+	\Ln \PR{T_n\in \mathcal{T}}= 
+	\left(
+	\prod_{\epsilon\in E^1_\mathcal{T}} \left( 1-\sum_{i=0}^{k-1}
+	e^{-\mu_{r,\epsilon}}
+	\frac{(\mu_{r,\epsilon})^i}{i!} \right)
+	\right)\cdot
+	\left(
+	\prod_{\epsilon\in E^2_\mathcal{T}}
+	e^{-\mu_{r,\epsilon}}
+	\frac{(\mu_{r,\epsilon})^{a_{\epsilon}}}{a_\epsilon!} 
+	\right)
+	\]
+	And last expression belongs to $\Lambda$ as we wanted to prove. 
+ 	\end{proof}
+
+	\section{Probabilities of cycles}
+
+\begin{theorem}
+	Let $\mathcal{O}$ be a $k$-agreeability class
+	of hypergraphs. Then 
+	$\Ln \PR{G_n\in \mathcal{O}}$ exists and is an expression
+	in $\Theta$. 
+\end{theorem}
+\begin{proof}
+	Define $r:=3^k$. 
+	For each $O\in C(k,r)$ let $X_{n,O}$ be the random variable
+	that counts the number of cycles in $Core(G_n;r)$ 
+	whose $k$-type is $O$. Fix $O\in C(k,r)$. It holds
+	\[
+	\mathrm{E}\big[ X_{n,O}\big]
+	=\sum_{(H,\tau)\in Copies(0,[n])} \Pr\left(
+	H\subset G_n \bigwedge_{v\in V(H)} 
+	Tree(G_n, v;r)\in \tau(v)
+	\right)	
+	\]
+	Because of the symmetry of the random model last probability is the 
+	same for all $(H,\tau)\in Copies(O,[n])$. Fix $(H,\tau)\in
+	Copies(O,\N )$. Then
+	\begin{align*}
+	\mathrm{E}\big[ X_{n,O}\big]
+	&=\frac{(n)_{|V(H)|}}{|Aut(H,\tau)|} 
+	\cdot \Pr\left(
+	H\subset G_n \bigwedge_{v\in V(H)} 
+	Tree(G_n, v;r)\in \tau(v)
+	\right)	\\
+	&=\frac{(n)_{|V(H)|}}{|Aut(H,\tau)|}\cdot
+	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}{n^{|V(H)|}}\cdot
+	\Pr\left(\bigwedge_{v\in V(H)} 
+	Tr(G_n, v;r)\in \tau(v)
+	\quad  \Big| \quad H\subset G_n
+	\right)\\
+	&\sim 
+	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
+	{|Aut(H,\tau)|}\cdot
+	\Pr\left(\bigwedge_{v\in V(H)} 
+	Tr(G_n, v;r)\in \tau(v)
+	\quad  \Big| \quad H\subset G_n
+	\right)
+	\end{align*}
+	Let $\overline{v}\in (\N)_*$ be a list containing 
+	exactly the vertices in $V(H)$. If $H\subset G_n$
+	then $Tr(G_n, v;r)=Tr(G_n,\overline{v},v;r)$. Also,
+	the event $H\subset G_n$ clearly can be described via
+	an edge sentence concerning the vertices in $\overline{v}$.
+	In consequence, using \cref{thm:BigTrees}, last expression
+	is asymptotically equivalent to
+	\[
+	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
+	{|Aut(H,\tau)|}\cdot
+	\prod_{v\in V(H)}
+	\Pr \big[ r, \tau(v) \big].
+	\]
+	For any $O\in C(k,r)$ we define $\lambda_O$ and 
+	$\omega_O$ in the following way. Let $(H,\tau)$ be
+	a representative of $O$. Then
+	\[ 
+	\lambda_O:
+	=\prod_{v\in V(H)}
+	\Pr \big[ r, \tau(v) \big],
+	\]
+	and
+	\[
+	\omega_O:=
+	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
+	{|Aut(H,\tau)|}\cdot\lambda_O.
+	\]
+	We are going to prove that the variables $X_{n,O}$ converge
+	in distribution as $n$ tends to infinity to 
+	independent Poisson variables whose respective means are
+	the $\omega_O$. For that we are going to use again the factorial 
+	moments method. For each $O\in C(k,r)$ fix a number $b_{O}\in\N$.
+	We want to prove 
+	\[
+	\Ln 
 	\mathrm{E}\left[
-		\prod_{\substack{\substack{i\in [k]}\\
-				\mathcal{E}\in EDGE_{r_i}}} \binom{X_n[i,\mathcal{E}]}{d[i,\mathcal{E}]}
-		\right] = \prod_{\substack{\substack{i\in [k]}\\
-				\mathcal{E}\in EDGE_{r_i}}} \frac{\mu[r_i,\mathcal{E}]^{d[i,\mathcal{E}]}}
-			{d[i,\mathcal{E}]!}.\]
+	\prod_{O\in C(k,r)}
+	\binom{X_{n,O}}{b_O}
+	\right]= \prod_{O\in C(k,r)} 
+	\frac{(\omega_O)^{b_O}}{b_O!}.
+	\]
+	For each $n\in \N$ we define
+	\[
+	\Omega_n:=\left\{
+	(F_O)_{O\in C(k,r)} \quad \Big|
+	\quad \forall O\in C(k,r) \quad
+	F_O\subset Copies(O,[n]), \quad
+	|F_O|=b_O	
+	\right\}.
+	\]
+	We also define $\Omega_\N$ by substituting $[n]$ for $\N$ in
+	the definition of $\Omega_n$. Informally, an element of $\Omega_n$ 
+	represents a choice of an unordered $b_O$-tuple
+	of possible cycles over $[n]$ whose $(k,r)$-type is $O$, for each
+	$(k,r)$ type $O$. Using observation REF we obtain
+	\[
+	\mathrm{E}\left[
+	\prod_{O\in C(k,r)}
+	\binom{X_{n,O}}{b_O}
+	\right]=
+	\sum_{(F_O)_{O\in C(k,r)}\in \Omega_n}
+	\Pr\left(
+	\bigwedge_{
+	\substack{
+	O\in C(k,r)\\
+	(H,\tau)\in F_O
+	}}
+	\left(
+	H\subset G_n
+	\bigwedge_{v\in V(H)}
+	Tr(G_n,v;r)\in \tau(v)
+	\right)
+	\right).
+	\]
+	Consider the subset $\Omega_n^\prime\subset \Omega_n$ that contains
+	the elements $(F_O)_{O\in C(k,r)}\in \Omega_n$ such that there exists
+	some vertex $v\in [n]$ contained in two graphs
+	$(H_1,\tau_1),(H_2,\tau_2)\in \bigcup_{O\in C(k,r)} F_O$. We want to argue 
+	that
+	\begin{equation}\label{eqn:denseconfigurations}
+	\Ln
+	\sum_{(F_O)_{O\in C(k,r)}\in \Omega_n^\prime}
+	\Pr\left(
+	\bigwedge_{
+		\substack{
+			O\in C(k,r)\\
+			(H,\tau)\in F_O
+	}}
+	\left(
+	H\subset G_n
+	\bigwedge_{v\in V(H)}
+	Tr(G_n,v;r)\in \tau(v)
+	\right)
+	\right)=0.
+	\end{equation}
+	Given an element $(F_O)_{O\in C(k,r)}\in \Omega_n$ we 
+	define the hypergraph $G\Big((F_O)_{O\in C(k,r)}\Big)$ as
+	follows:
+	\[
+	G\Big((F_O)_{O\in C(k,r)}\Big):=
+	\bigcup_{H\in F} H, 
+	\]
+	where
+	\[
+	F:=\left\{
+	H \quad \Big| \quad 
+	(H,\tau)\in \bigcup_{O\in C(k,r)} F_O	
+	\right\}.
+	\]
+	That is, $G\Big((F_O)_{O\in C(k,r)}\Big)$
+	is the union of all hypergraphs chosen in 
+	$(F_O)_{O\in C(k,r)}$. Then, for all 
+	$(F_O)_{O\in C(k,r)}\in \Omega_n$ it is 
+	satisfied
+	\begin{align*}
+	&\Pr\left(
+	\bigwedge_{
+		\substack{
+			O\in C(k,r)\\
+			(H,\tau)\in F_O
+	}}
+	\left(
+	H\subset G_n
+	\bigwedge_{v\in V(H)}
+	Tr(G_n,v;r)\in \tau(v)
+	\right)
+	\right)
+	\leq 
+	\Pr\left(
+	\bigwedge_{
+		\substack{
+			O\in C(k,r)\\
+			(H,\tau)\in F_O
+	}}
+	H\subset G_n
+	\right) =
+	\\&
+	\Pr \left(
+	G\Big((F_O)_{O\in C(k,r)}\Big) \subset G_n
+	\right).
+	\end{align*}
+	Let 
+	\[
+	t = \sum_{O\in C(k,r)} |V(O)|\cdot b_O.
+	\]
+	Then $V\Big(
+	G\Big((F_O)_{O\in C(k,r)}\Big)
+	\Big) \leq t$
+	for any $(F_O)_{O\in C(k,r)}\in \Omega_n$.\par
+	Consider the following facts
+	\begin{itemize}
+		\item[(1)] If $(F_O)_{O\in C(k,r)}\in \Omega_n^\prime$ then
+		$G\big((F_O)_{O\in C(k,r)}\big)$ is dense.
+
+		\item[(2)] Given an hypergraph $H$ with $V(H)\subset \N$,
+		the number of elements  $(F_O)_{O\in C(k,r)}\in \Omega_\N^\prime$
+		such that $H=G\big((F_O)_{O\in C(k,r)}\big)$ is finite and it is 
+		the same for all $H^\prime \simeq H$ with $V(H^\prime) \subset \N$.
+
+		\item[(3)] There is a finite amount of unlabeled dense
+		hypergraphs with size bounded by $t$.
+	\end{itemize}
+	Then it follows that
+	\begin{align*}
+	\sum_{(F_O)_{O\in C(k,r)}\in \Omega^\prime_n}
+	\Pr \Big(
+	G\Big(&(F_O)_{O\in C(k,r)}\Big) \subset G_n
+	 \Big) \\
+	& = 
+	\mathrm{O} \left(
+	\mathrm{E}\left[
+	\# \text{ of dense subgraphs in $G_n$ with size bounded by
+	 $t$}\right] \right).	
+	\end{align*}
+	And this, together with \cref{lem:nocopiesdense} proves
+	\cref{eqn:denseconfigurations}.\par
+	For all $n$ define $\Omega_n^{\prime\prime}=
+	\Omega_n\setminus \Omega_n^\prime$. That is, 
+	$\Omega_n^{\prime\prime}$ contains the elements
+	$(F_O)_{O\in C(k,r)}$ in $\Omega_n$ such that all vertices
+	$v\in [n]$ belong to at most one hypergraph
+	$(H,\tau)\in \bigcup_{O\in C(k,r)} F_O$. We also
+	define $\Omega_\N^{\prime\prime}$. Because of 
+	\cref{eqn:denseconfigurations} we have
+	\[
+	\mathrm{E}\left[
+	\prod_{O\in C(k,r)}
+	\binom{X_{n,O}}{b_O}
+	\right]=
+	\sum_{(F_O)_{O\in C(k,r)}\in \Omega_n^{\prime\prime}}
+	\Pr\left(
+	\bigwedge_{
+	\substack{
+		O\in C(k,r)\\
+		(H,\tau)\in F_O
+	}}
+	\left(
+	H\subset G_n
+	\bigwedge_{v\in V(H)}
+	Tr(G_n,v;r)\in \tau(v)
+	\right)
+	\right)+o(1).
+	\]
+
+	Because of the symmetry of the model the probability inside of last sum 
+	is the same for all elements $(F_O)_{O\in C(k,r)}\in \Omega_n^{\prime\prime}$.
+	Also, counting all different vertices and automorphisms we obtain that
+	\[
+	|\Omega_n^{\prime\prime}|=
+	\frac{(n)_{\sum_{O\in C(k,r)} |V(O)|\cdot b_O}}
+	{\prod_{O\in C(k,r)} b_O!\cdot |Aut(O)|^{b_O}}.
+	\]
+	Fix $(F_O)_{O\in C(k,r)}\in \Omega_\N^{\prime\prime}$. Then 
+	\begin{align*}
+	&\Ln \mathrm{E}\left[
+	\prod_{O\in C(k,r)}
+	\binom{X_{n,O}}{b_O}
+	\right]=\\
+	&
+	\Ln
+	\frac{(n)_{\sum_{O\in C(k,r)} |V(O)|\cdot b_O}}
+	{\prod_{O\in C(k,r)} b_O!\cdot |Aut(O)|^{b_O}} \cdot
+	\Pr\left(
+	\bigwedge_{
+		\substack{
+			O\in C(k,r)\\
+			(H,\tau)\in F_O
+	}}
+	\left(
+	H\subset G_n
+	\bigwedge_{v\in V(H)}
+	Tr(G_n,v;r)\in \tau(v)
+	\right)
+	\right).
+	\end{align*}
+	It holds that the probability in last expression equals
+	\[
+	\prod_{O\in C(k,r)}
+	\left( 
+	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(O)|}}{n^{|V(O)|}}
+	\right)^{b_O} \cdot
+	\Pr\left(
+	\bigwedge_{
+		\substack{
+			O\in C(k,r)\\
+			(H,\tau)\in F_O\\
+			v\in V(H)
+	}}
+	Tr(G_n,v;r)\in \tau(v) \,
+	\Bigg|  \,
+	\bigwedge_{
+		\substack{
+			O\in C(k,r)\\
+			(H,\tau)\in F_O\\
+		}}
+	H\subset G_n
+	\right).
+	\]
+	Let $\overbar{v}\in (\N)_*$ be 
+	a list that contains exactly the vertices in $G\big(
+	(F_O)_{O\in C(k,r)}	\big)$. Then the event
+	\[
+	A_n:=
+		\bigwedge_{
+		\substack{
+			O\in C(k,r)\\
+			(H,\tau)\in F_O\\
+	}}
+	H\subset G_n
+	\]
+	can be written as an edge sentence concerning the vertices in $\overline{w}$.
+	Also, if $A_n$ holds then all vertices in $\overline{w}$ belong to 
+	$Core(G_n;r)$. Thus, for all $v\in \overline{v}$,
+	$Tr(G_n,v;r)=Tr(G_n,\overline{w};r)$ and using \cref{thm:BigTrees}
+	we obtain
+	\[
+	\Pr\left(
+	\bigwedge_{
+		\substack{
+			O\in C(k,r)\\
+			(H,\tau)\in F_O\\
+			v\in V(H)
+	}}
+	Tr(G_n,v;r)\in \tau(v) \,
+	\Bigg|  \,
+	\bigwedge_{
+		\substack{
+			O\in C(k,r)\\
+			(H,\tau)\in F_O\\
+	}}
+	H\subset G_n
+	\right) \sim
+	\prod_{O\in C(k,r)} (\lambda_O)^{b_O}.	
+	\]
+	Joining everything together we obtain
+	\begin{align*}
+&\Ln \mathrm{E}\left[
+\prod_{O\in C(k,r)}
+\binom{X_{n,O}}{b_O}
+\right]=\\
+&
+\Ln
+\frac{(n)_{\sum_{O\in C(k,r)} |V(O)|\cdot b_O}}
+{\prod_{O\in C(k,r)} b_O!\cdot |Aut(O)|^{b_O}} \cdot
+\prod_{O\in C(k,r)}
+\left( 
+\frac{\lambda_O \cdot \prod_{R\in \sigma} \beta_R^{|E_R(O)|}}{n^{|V(O)|}}
+\right)^{b_O} = \\
+&\prod_{O\in C(k,r)} \frac{1}{b_O!}\left(\frac{\lambda_O  
+\cdot \prod_{R\in \sigma} \beta_R^{|E_R(O)|} }{|Aut(O)|}
+\right)^{b_O}= \prod_{O\in C(k,r)} 
+\frac{(\omega_O)^{b_O}}{b_O!},
+\end{align*}
+as we wanted. With this, because of \cref{thm:BrunSieve}, it 
+is proven that when $n$ tends to infinity
+the $X_{n,O}$'s are asymptotically distributed 
+like independent
+Poisson variables with the $\omega_O$'s as their respective means.\par
+Given a simple $k$-agreeability class for hypergraphs $\mathcal{O}$ there 
+is a partition $C_1, C_2\subset C(k,r)$, $C_1\cup C_2=C(k,r)$ 
+and there are natural numbers $a_O\leq k-1$ for any $O\in C_2$ such that
+$C_1, C_2, (a_O)_{O\in C_2}$ depend only on $\mathcal{O}$ and
+the event $G_n\in \mathcal{O}$ is equivalent to
+\[
+G_n \text{ is $r$-simple } \wedge
+\left(
+ \bigwedge_{O\in C_1}
+ X_{n,O}\geq k
+\right)
+\wedge
+\left(
+\bigwedge_{O\in C_1}
+X_{n,O}=a_O.
+\right).
+\]
+In consequence
+\begin{align*}
+ & \Ln
+ \PR{G_n \in \mathcal{O}}=\\
+ &\Ln
+ \Pr \left(
+ G_n \text{ is $r$-simple } \wedge
+ \left(
+ \bigwedge_{O\in C_1}
+ X_{n,O}\geq k
+ \right)
+ \wedge
+ \left(
+ \bigwedge_{O\in C_1}
+ X_{n,O}=a_O.
+ \right)
+ \right).
+\end{align*}
+Because of \cref{thm:simple}, last limit equals
+\begin{align*}
+&\Ln
+\Pr \left(
+\left(
+\bigwedge_{O\in C_1}
+X_{n,O}\geq k
+\right)
+\wedge
+\left(
+\bigwedge_{O\in C_1}
+X_{n,O}=a_O.
+\right)
+\right)
+=\\
+&
+\left(
+\prod_{O\in C_1}
+1-\sum_{i=0}^{k-1} e^{-\omega_O}\frac{(\omega_O)^i}{i!}
+\right)
+\cdot
+\left(
+\prod_{O\in C_2}
+e^{-\omega_O}\frac{(\omega_O)^{a_O}}{a_O!}
+\right)
+.
+\end{align*}
+This last expression belongs to $\Omega$, so the theorem is proven. 
 \end{proof}
 
-\end{theorem}
+\section{Proof of the main theorem}
+
+\section{Application to random SAT}
+
 %During this section we will consider
@@
 %This way, an edge $e\in H(G)$ with color $i$ is an element
-%$[x_1,\dots,x_{a_i}]\in H_i(G)$, and the $x_i$'s are vertices
+% $[x_1,\dots,x_{a_i}]\in H_i(G)$, and the $x_i$'s are vertices
 %belonging to $V(G)$. \par

### 2020-03-12 Article.tex
Coronavirus

@@
 \newcommand{\Tr}{\mathrm{Tr}}
+\newcommand{\InR}[1]{\left\{ #1_R \right\}_{R\in \sigma}}
 
@@
 
-\subsection{General notation}
+\subsection{General notation}\label{subsect:notation}
 
@@
 subsets of $S$ whose size is $k$. \par
+Given numbers, $n,m\in \N$ with $m\leq n$ we define
+$(n)_m:=n\cdot (n-1)\cdots (n-m+1)$. Given a set
+$S$ and a number $n\in \N$ with $n\leq |S|$ we define
+$(S)_n$ as the subset of $S^n$ consisting of the $n$-tuples
+whose coordinates are all different. 
+We also define $S^*:=\bigcup_{n=0}^\infty S^n$ and
+$(S)_*=\bigcup_{n\leq |S|} (S)_n$. Given a tuple 
+$\overline{x}\in S^*$ and an element $x\in S$ the expression
+$x\in \overline{x}$ will mean that $x$ appears as some coordinate
+in $\overline{x}$. We will at times make an abuse of notation and
+treat the tuple $\overline{x}$
+as the set of elements $x\in \overline{x}$. \par
+We will use the convention that over-lined variables
+, like $\overline{x}$, denote ordered tuples of arbitrary length. 
+For example, given a set $S$, if we write $\overline{x}\in S^*$
+then $\overline{x}=(x_1,\dots, x_a)$ for some $a\in \N$ and 
+some $x_1,\dots, x_a\in S$. Given an ordered tuple $\overline{x}$
+we define the number $len(\overline{x})$ as its length. 
+Given a map $f:X\rightarrow Y$ between two sets $X, Y$ and 
+an ordered tuple $\overline{x}:=(x_1,\dots,x_a)\in X^*$ 
+we define $f(\overline{x})\in Y^*$ as the tuple 
+$(f(x_1),\dots,f(x_a))$.
+\par
+
 Let $S$ be a set, $a$ a positive natural number, 
@@
 $S^a$ in the following way: Given $g\in \Phi$ and
-$(x_1,\dots,x_a)$ we define $g(x_1,\dots,x_a)=
-(x_{g(1)},\dots,x_{g(a)})$.
+$\overline{x}=(x_1,\dots,x_a)\in S^a$ we define 
+$g\cdot(x_1,\dots,x_a)$ and $g\cdot \overline{x}$ 
+as the tuple $(x_{g(1)},\dots,x_{g(a)})$. 
 We will denote by $S^a/\Phi$ to the quotient
 of the set $S^a$ by this action. Given an element
-$(x_1,\dots, x_a)\in S^a$ we will denote its equivalence
-class in $S^a/\Phi$ by $[x_1,\dots,x_a]$. Thus, for any
+$\overline{x}:=(x_1,\dots, x_a)\in S^a$ we will denote its equivalence
+class in $S^a/\Phi$ by $[x_1,\dots,x_a]$ or $[\overline{x}]$.
+Thus, for any
 $g\in \Phi$, by definition $[x_1,\dots,x_a]=[x_{g(1)}
-,\dots,x_{g(a)}]$. The notation $(x_1,\dots, x_a)$ 
+,\dots,x_{g(a)}]$. The notations $\overline{x}$ and
+$(x_1,\dots, x_a)$ 
 will be reserved 
 to ordered tuples while 
-$[x_1,\dots,x_a]$ will denote an ordered tuple modulo the
+$[\overline{x}]$ and
+$[x_1,\dots,x_a]$ will denote ordered tuples modulo the
 action of some arbitrary group of permutations. Which group is
@@
 and it should either be clear from context or not be relevant.\par
-We will denote ordered lists of elements by $\overbar{x}:=x_1,\dots,x_a$. 
-This way, expressions like $(\overbar{x})$ or $[\overbar{x}]$ would mean 
-$(x_1,\dots,x_a)$ and $[x_1,\dots,x_a]$ respectively.
-Sometimes we will directly write $\overbar{x}$ without specifying the list
-it names nor its length when it is understood or not relevant.
 \par
@@
 as usual.
-If $g(n)\neq 0$ for sufficiently large values of $n$ then
-we will write $f\simeq g$ if $\Ln \frac{f(n)}{g(n)}=1$.\par
+If $g(n)\neq 0$ for $n$ large enough then
+we will write $f\sim g$ when $\Ln \frac{f(n)}{g(n)}=1$.\par
 
@@
 A relational vocabulary $\sigma$ is a collection of
-relation symbols $(R_1,\dots, R_m,\dots)$
-where each relation symbol $R_i$ has associated a natural $a_i$
-number called its arity.
+relation symbols $\{R_1,\dots, R_m,\dots\}$
+where each relation symbol $R_i$ has associated a natural
+number $ar(R_i)$ called its arity.
 A $\sigma$-structure $\mathfrak{A}$ is composed of
@@
 In the first order language $FO[\sigma]$ with signature $\sigma$ 
-formulas are formed by variables $x_1,\dots, x_i,\dots$,
+formulas are formed by variables $x_1,\dots,$ $x_i,\dots$,
 the relation symbols in $\sigma$, the equal symbol $=$,
@@
 	\item The expression $R(y_1,\dots,y_a)$, where the $y_i$'s are variables and $R$
-	is a relation symbol in $\sigma$ with arity $a$, belongs to $FO[\sigma]$.
+	is a relation symbol in $\sigma$ such that $ar(R)=a$,
+	belongs to $FO[\sigma]$.
 	\item The expression $y_1=y_2$, where $y_1, y_2$ are variables, 
@@
 \end{itemize}  
-We will write $\forall y_1, y_2,\dots, y_m$ or simply $\forall \overbar{y}$
+We will write $\forall y_1, y_2,\dots, y_m$ or simply $\forall \overline{y}$
 instead of  
 $\forall y_1, \forall y_2,\dots, \forall y_m$ and likewise for
-the quantifier $\exists$.
-
+the quantifier $\exists$. Also, if $\overline{y}:=(y_1,\dots,y_a)$ is a
+tuple of variables we may write simply $R(\overline{y})$ instead
+of $R(y_1\dots,y_a)$.\par
+For the remaining of this article we will reserve the names $x,y,z$
+for the variables in our first order formulas.\par
 We define the set of free variables of a formula as usual. 
-We will use the notation $\phi(\overbar{y})$ to refer to a 
-formula $\phi\in FO[\sigma]$
-to denote that its free variables are the ones in $\overbar{y}$.
+Given a formula $\phi\in FO[\sigma]$ we will use the notation $\phi(\overline{y})$ 
+to denote that $\overline{y}$ is a tuple of 
+(different) variables that contains all free variables in $\phi$ and
+none of its bounded variables, although it may contain variables
+which not appear in $\phi$. \par
 Formulas with no free variables are called sentences and 
@@
 $\phi\in FO[\sigma]$ we write $\mathcal{A} \models \phi$ to denote 
-that $\mathcal{A}$ satisfies $\phi$. If $\psi(\overbar{y})$ is a
-formula, $\overbar{a}$ are elements in the universe of 
-$\mathcal{A}$, and $\overbar{y}$ and $\overbar{a}$ are lists of the same size,
+that $\mathcal{A}$ satisfies $\phi$. If $\psi(\overline{y})$ is a
+formula, $\overline{a}$ are elements in the universe of 
+$\mathcal{A}$, and $\overline{y}$ and $\overline{a}$ are lists of the same size,
 then we write $\mathcal{A} \models 
-\psi(\overbar{a})$
+\psi(\overline{a})$
 to mean that $\mathcal{A}$ satisfies $\psi$ when the free variables in
-$\overbar{y}$ are interpreted as the elements in $\overbar{a}$.
+$\overline{y}$ are interpreted as the elements in $\overline{a}$ (i.e., 
+the $i$-th element of $\overline{y}$ is interpreted as the $i$-th
+element of $\overline{a}$).
 \todo[inline]{Deber\'a al menos mencionar un par de trabajos que estudien random k-SAT y propiedades a.a.s suficientes para no-satisfacibilidad}
@@
 \begin{itemize}
-	\item Positive natural numbers $t$, $\overbar{a}=a_1,\dots, a_t$, with 
-	all the $a_i$'s greater than $1$.\
-
-	\item A relational vocabulary $\sigma=\{\overbar{R}\}$, with
-	$\overbar{R}=R_1,\dots, R_t$ such that $a_i$ is the arity of
-	$R_i$.
-
+	\item A relational vocabulary $\sigma$ such that all the relations $R\in\sigma$ satisfy $ar(R)\geq 2$. 
 	\item 
-	Groups $\overbar{\Phi}=\Phi_1,\dots,\Phi_t$
-	such that each $\Phi_i$ is consists of 
-	permutations on $[a_i]$ with the usual 
+	Groups $\overline{\Phi}=\{ \Phi_R \}_{R\in \sigma}$
+	such that each $\Phi_R$ is consists of 
+	permutations on $[ar(R)]$ with the usual 
 	composition as its operation.	
-
 	\item 
-	Sets $\overbar{P}=P_1, \dots, P_t$ satisfying 
-	$P_i\subseteq \binom{[a_i]}{2}$
+	Sets $\{P_R\}_{R\in \sigma}$ satisfying that for 
+	all $R\in \sigma$, 
+	$P_R\subseteq \binom{[ar(R)]}{2}$
 
@@
 \todo[inline]{Quiz\'as deber\'ia a\~nadir un anexo dando alguna indicaci\'on sobre c\'omo tratar las relaciones unarias?}
-
-We can think of structures in  $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$
-as "multi-hypergraphs" with
-$t$ edge sets whose edges are of sizes $\overbar{a}$ respectively
-, are invariant under permutations in $\overbar{\Phi}$ resp., 
-and do 
-not contain repetitions of vertices in the positions given by
-$\overbar{P}$ resp. We make this observation formal in the 
-following definitions:
 
@@
 \begin{itemize}
-	\item \textit{Symmetry axioms}: For each $1\leq s \leq t$ and
-	each $g\in \Phi_s$:
-	\[ \forall x_1,\dots, x_{a_s} \big(  R_s(x_1,\dots, x_{a_s})
-	\iff R_s(x_{g(1)},\dots,x_{g(a_s)}) \big)    \]
+	\item \textit{Symmetry axioms}: For each $R\in \sigma$ and
+	each $g\in \Phi_R$:
+	\[ \forall \overline{x}:=x_1,\dots, x_{ar(R)} \big(  R(\overline{x})
+	\iff R(g\cdot\overline{x}) \big)    \]
 	\item \textit{Anti-reflexivity axioms}: For each 
-	$1\leq s \leq t$ and $\{i,j\}\in P_s$
-	\[ \forall x_1,\dots, x_{a_s} 
-	\big( (x_i=x_j) \implies \neg R_s(x_1,\dots, x_{a_s})
+	$R\in \sigma$ and $\{i,j\}\in P_R$
+	\[ \forall x_1,\dots, x_{ar(R)} 
+	\big( (x_i=x_j) \implies \neg R(x_1,\dots, x_{a_s})
 	\big)\]
@@
 
-We can think of structures in  $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$
-as "multi-hypergraphs" with
-$t$ edge sets whose edges are of sizes $\overbar{a}$ respectively
-, are invariant under permutations in $\overbar{\Phi}$ resp., 
-and do 
-not contain repetitions of vertices in the positions given by
-$\overbar{P}$ resp. We make this observation formal in the 
-following definitions:
+We can think any structure $G$ in $\mathcal{C}$
+as a "multi-hypergraph" whose vertices are the elements
+of the universe of $G$. Each relation $R\in \sigma$, can be 
+represented over $G$ as an "edge set" formed by tuples vertices
+of size $ar(R)$ modulo the action of $\Phi_R$. Furthermore, 
+repetitions of vertices in the positions given by
+$P_R$ are not allowed in these tuples.\par
+The following definitions make this ideas formal. They 
+depend on our choices of $\sigma$, $\{\phi_R\}_{R\in \sigma}$
+and $\{P_R\}_{R\in \sigma}$ but as those are fixed we can
+allow ourselves to omit those dependencies for the sake of readability.
 
 \begin{definition} 
-	Let $V$ be a set, $a$ be a positive natural number,
-	$\Phi$ be a group of permutations over $[a]$ and
-	$P\subseteq \binom{[a]}{2}$. 
-	We define the \textbf{total
-	edge set over $V$ with edge size $a$, symmetry group $\Phi$ and 
-	anti-reflexivity restrictions $P$} as the set
-	\[ E^{V}_{a,\Phi,P}= (V^a/\Phi) \setminus \{ [x_1,\dots,x_a]  
-	\,| \,
-	x_1,\dots,x_a\in V \, \wedge \, x_i=x_j \text{ for some } \{i,j\}\in P \}. \]
+	Let $V$ be a set, and let $R\in \sigma$.
+	We define the \textbf{total edge set over $V$
+	given by $R$} as
+	\[ E_R[V]= (V^{ar(R)}/\Phi_R) \quad \setminus 
+	\quad X, \]
+	where
+	\[
+	X=
+	\Big\{ [x_1,\dots,x_{ar(R)}]  
+	\quad \Big| \quad
+	x_1,\dots,x_{ar(R)}\in V, \,
+	\text{ and } 
+	 \, x_i=x_j \text{ for some } 
+	\{i,j\}\in P_R \Big\}.
+	\]
+	Also, we will say that the \textbf{sort} of the elements $e\in E_R[V]$
+	is $R$. 
 \end{definition}
 
-That is, $E^{V}_{a,\Phi,P}$ contains all the ``tuples modulo the permutations
-in $\phi$" excluding those that contain some repetition of vertices in
-the positions given by $P$.
+That is, $E_R[V]$ contains all the ``$ar(R)$-tuples of elements
+in $V$ modulo the permutations
+in $\phi_R$" 
+excluding those that contain some repetition of elements in
+the positions given by $P_R$.\par
+The fact that the elements $e\in E_R(V)$ are of sort $R$ 
+is a technical detail
+introduced so that for any different relation symbols $R_1$ and
+$R_2$ it holds $E_{R_1}(V)\cap E_{R_2}(V)=\emptyset$ even in the case
+that $ar(R_1)=ar(R_2)$, $\Phi_{R_1}=\Phi_{R_2}$ and $P_{R_1}=P_{R_2}$.\par
+
+In the case where $V=[n]$ we will write simply $E_R[n]$ instead
+of $E_R[[n]]$.
 
 \begin{definition} 
-A \textbf{ multi-hypergraph with
-with $t$ edge sets, edge sizes given by
-$\overbar{a}$,
-symmetry groups $\overbar{\Phi}$, 
-and anti-reflexivity restrictions $\overbar{P}$}
-is a pair $G=(V(G),\overbar{E(G)})$,
-where $\overbar{E(G)}=E_1(G),\dots, E_t(G)$ and
-for each $i$, $E_i(G) \subseteq E^{V}_{a_i,\Phi_i,P_i}$.
+We call $\mathcal{C}$-\textbf{hypergraph}, or simply hypergraph, 
+to a pair $G=\Big(V(G),\{E_R(G)\}_{R\in\sigma}\Big)$,
+where for each $R$, $E_R(G) \subseteq E_R[V]$.
 \end{definition}
-
-For the sake of word economy the expression 
-``multi-hypergraph with
-$t$ edge sets, with edge sizes given by $\overbar{a}$,
-symmetry groups $\overbar{\Phi}$, and anti-reflexivity 
-restrictions $\overbar{P}$" 
-will be replaced simply by ``hypergraph ". The word 
-``hypergraph" will not hold
-any other meaning than this for the rest 
-of this writing except for the places
-where it is explicitly stated.  \par
 
@@
 can be naturally interpreted as
-structures from $\mathcal{C}^
-{\sigma}_{\overbar{\Phi},\overbar{P}}$ 
+structures from $\mathcal{C}$ 
 in the following way: 
-given $G=(V,\overbar{E})$,
+given $G=(V,\{E_R\}_{R\in \sigma})$,
 we consider $V$ to be the universe of
- $G$, and for any $i$ we define
-$R_i^G\subseteq V^{a_i}$ as the set such that
-$(\overbar{x})\in V^{a_i}$, 
-$(\overbar{x})\in R_i^G$ if and only if 
-$[\overbar{x}]\in E_i$. Under 
-this interpretation hypergraphs, by definition,
-satisfy the symmetry and anti-reflexivity
-axioms given above. It is also easy to
+ $G$, and for any $R\in \sigma$ we define
+$R^G\subseteq V^{ar(R)}$ as the set of tuples
+$\overline{x}\in V^{ar(R)}$ such that
+$[\overline{x}]\in E_R$. Under 
+this interpretation hypergraphs
+satisfy by definition the 
+symmetry and anti-reflexivity
+axioms given at the beginning of this section. It is also easy to
 see that this interpretation induces
 a one-to-one identification between 
-structures in $\mathcal{C}^{\sigma}_{\overbar{\Phi}
-,\overbar{P}}$ and hypergraphs. \par
+structures in $\mathcal{C}$ and hypergraphs. \par
+
+\subsection{Hypergraph notation and nomenclature}
 
 We will use standard nomenclature and notation
-from graph theory. This way, we will call vertex set
-to $V(G)$ and vertices to its elements. Likewise, each of 
-the $E_i(G)$'s will be called an edge set and its elements, 
-edges. Given an edge set $E_i(G)$, the index $i$ will
-be called its color, and the number
-$a_i$ its size. Thus, we will say that
-an edge $e\in E_i(G)$ has color $i$ and size
-$a_i$.
+from graph theory with some additions. Given an 
+hypergraph $G$ we will call its \textbf{vertex set} to $V(G)$ 
+and \textbf{vertices} 
+to the elements $v\in V(G)$. Likewise, each of 
+the $E_R(G)$'s will be called an \textbf{edge set} and its elements, 
+\textbf{edges}. Given an edge set $E_R(G)$, 
+the index $R$ will be called its \textbf{relation}.
+
+\par
+Given an hypergraph $G$ we define the set $E(G)$ as the
+union $\cup_{R\in \sigma}E_R(G)$. Notice that this union 
+is disjoint because elements from different $E_R(G)$'s 
+are of different sorts. Thus, $|E(G)|=\sum_{R\in \sigma} 
+|E_R(G)|$. Analogously, given a set $V$, we define
+$E[V]:=\cup_{R\in \sigma} E_R[V]$.
+Given an edge $e\in E[V]$ we define $R(e)$
+as the sort of $e$, i.e.,
+the unique relation symbol $R(e)\in \sigma$
+such that $e\in E_{R(e)}[V]$.
+
+Given two hypergraphs $H$ and $G$ we say that $H$
+is a \textbf{sub-hypergraph} of $G$, which we write as $H\subset G$,
+if $V(H)\subset V(G)$ and $E(H)\subset E(G)$ (notice 
+that this is equivalent to $E_R(H)\subset E_R(G)$ for all
+$R\in \sigma$, since the edges are sorted).\par
 
 Given a set of vertices $U\subseteq V(G)$, 
-we will denote by $G[U]$ the hypergraph induced
-by $G$ on $U$. That is, $G[U]$ is an hypergraph
-$H=(V(H),\overbar{E(H)})$ such that $V(H)=U$ and
-for any list $\overbar{v}$ of vertices in $U$,
-$[\overbar{v}]\in E_i(H)$ if and only if 
-$[\overbar{v}]\in E_i(G)$.
+we will denote by $G[U]$ the \textbf{hypergraph induced
+by $G$ on $U$}. That is, $G[U]$ is an hypergraph
+$H=(V(H),\{E(H)_R\}_{R\in \sigma})$ such that 
+$V(H)=U$ and for any $R\in \sigma$ 
+each edge $e\in E_R(G)$ belongs 
+to $E_R(H)$ as well if and only if the vertices
+involved in $e$ are in $U$ (i.e. $e\in E_R[U]$).
 \par
-
-An homomorphism between two hypergraphs $G$ and $H$ 
-a map $f:V(G)\rightarrow V(H)$ that sends edges 
-from $G$ to edges in $H$ of the same color. That is,
-if vertices $v_1,\dots, v_{a_i}$ form an edge 
-$[v_1,\dots,v_{a_i}]\in E_i(G)$, then
-$[f(v_1),\dots,f(v_{a_i})]\in E_i(H)$.
-If $f$ is injective then it is called a monomorphism. 
-If $f$ is bijective and its inverse is also an homomorphism 
-between $H$ and $G$ then $f$ is called an isomorphism.\par
-
-The group of automorphisms $Aut(G)$ of an hypergraph $G$ is the group
-of isomorphisms between $G$ and itself. 
-\par
-
-Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is
-a sub-hypergraph $H_2\subseteq G$ isomorphic to $H$. The copy
-is called induced if $H_2$ is an induced sub-hypergraph.
-We will call a labeled copy
-of $H$ in $G$ to a monomorphism $f:H\rightarrow G$. 
-It is satisfied that the number
-of labeled copies of $H$ in $G$ is $|Aut(H)|$ times the number
-of copies of $H$ in $G$.
-
-The excess $ex(G)$ of an hypergraph $G$ is the number
-\[
-ex(G)= \big(\sum_{i=1}^{t} (a_i-1)|E_i(G)|\big) - |V(G)|.  
+%
+%An homomorphism between two hypergraphs $G$ and $H$ 
+%a map $f:V(G)\rightarrow V(H)$ that sends edges 
+%from $G$ to edges in $H$ of the same color. That is,
+%if vertices $v_1,\dots, v_{a_i}$ form an edge 
+%$[v_1,\dots,v_{a_i}]\in E_i(G)$, then
+%$[f(v_1),\dots,f(v_{a_i})]\in E_i(H)$.
+%If $f$ is injective then it is called a monomorphism. 
+%If $f$ is bijective and its inverse is also an homomorphism 
+%between $H$ and $G$ then $f$ is called an isomorphism.\par
+%
+%The group of automorphisms $Aut(G)$ of an hypergraph $G$ is the group
+%of isomorphisms between $G$ and itself.
+
+%
+%Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is
+%a sub-hypergraph $H_2\subseteq G$ isomorphic to $H$. The copy
+%is called induced if $H_2$ is an induced sub-hypergraph.
+%We will call a labeled copy
+%of $H$ in $G$ to a monomorphism $f:H\rightarrow G$. 
+%It is satisfied that the number
+%of labeled copies of $H$ in $G$ is $|Aut(H)|$ times the number
+%of copies of $H$ in $G$.
+
+We define the \textbf{excess} $ex(G)$ of an hypergraph $G$ as the number
+\[
+ex(G):= \big(\sum_{R\in \sigma} (ar(R)-1)|E_R(G)|\big) - |V(G)|.  
 \] 
@@
 
-Before moving on we need to introduce some additional notation. NOTACION
-
 Given an hypergraph $G$ we define the following metric, $d$, over $V(G)$:
-\[ d^G(v,u)= \min_{\substack{H \text{ subgraph of } G\\ 
+\[ d^G(u,v)= \min_{\substack{H \subset G\\ 
 		H \text{ connected }\\
-		v,u\in V(H)}} |V(H)| - 1 .\]
-That is, the distance between $v$ and $u$ is the minimum size
-of a connected graph $H$ containing both vertices, minus one. 
-If such graph does not exist we define $d^G(u,v)=\infty$.
-This definition extends naturally to subsets $X,Y\subseteq V(G)$:
-\[ d^G(X,Y)=\min_{\substack{x\in X\\ y\in Y}} d^G(x,y).\]
-As usual, when $X=\{x\}$ we will omit the brackets and write
-$d^G(x,Y)$ instead of $d^G(\{x\},Y)$, for example. When $G$ 
+		u,v\in V(H)}} |E(H)| .\]
+That is, the distance between $v$ and $u$ is the minimum number of
+edges necessary to connect $v$ and $u$. 
+If such number does not exist we define $d^G(u,v)=\infty$. \par
+As usual, define $d^{G}(X,Y)$ for sets $X,Y\subset V(G)$ as the minimum
+distance $d(u,v)$ where $u\in X$ and $v\in Y$. 
+When $X=\{x\}$ we will omit the brackets and write
+$d^G(x,Y)$ instead of $d^G(\{x\},Y)$, for example.
+When $G$ 
 is understood or not relevant we will usually simply denote the 
@@
 Given set of vertices vertex, $X\subseteq V(G)$, 
-we denote by $N^G(X;r)$ the $r$-neighborhood of $X$ in 
+we denote by $N^G(X;r)$ the $r$-\textbf{neighborhood} of $X$ in 
 $G$. That is,  $N^G(X;r)= G[Y]$, where $Y\subseteq V(G)$ is 
@@
 As before, we will usually drop the ``$G$'' from our 
-notation when $G$ is understood or not relevant.
+notation when $G$ is understood or not relevant.  \par
+
+We will often write tuples of vertices instead of sets
+inside of $d(\cdot\, , \cdot)$ and $N(\cdot\, ;r)$. In those cases
+we are treating those tuples as sets as specified in
+\cref{subsect:notation}.
 
@@
 
-Let $p_1\dots,p_t$ real numbers between zero and one,
-and let $\overbar{p}=p_1,\dots,p_t$.
-The random model $G^{\mathcal{C}}(n,\overbar{p})$ 
+For each $R\in \sigma$ let
+$p_R$ be a real number between zero and one.
+Let $\overline{p}:=\InR{p}$.
+The random model $G^{\mathcal{C}}(n,\overline{p})$ 
 is the discrete probability space that
@@
 
-\[ \mathrm{Pr}(G)=\prod_{i=1}^{t} p_i^{|E_i(G)|}
-(1-p_i)^{ |E^{[n]}_{a_i,\Phi_i,P_i}|-|E_i(G)|}.	
+\[ \mathrm{Pr}(G)=\prod_{R\in \sigma} p_R^{|E_R(G)|}
+(1-p_R)^{ \big|E_R[n]\big|-\big|E_R(G)\big|}.	
 \]
 Equivalently, this is the probability space obtained by 
-assigning to each edge with color $i$,  
-$e\in  E^{[n]}_{a_i,\Phi_i,P_i}$ probability 
-$p_i$ independently. \par
+assigning to each edge $e\in E_R[n]$ probability 
+$p_R$ independently. \par
 
 %Let $G_n$ denote a random hypergraph in 
-%$G^\mathcal{C}(n,\overbar{p})$, where 
+%$G^\mathcal{C}(n,\overline{p})$, where 
 %$\bar{p}:=p_1,\dots,p_t$, and 
@@
 As in the case of Lynch's theorem, we are interested in the
-"sparse regime" of $G^\mathcal{C}(n,\overbar{p})$, were the 
+"sparse regime" of $G^\mathcal{C}(n,\overline{p})$, were the 
 expected number of edges each color is linear. 
@@
 %$\mathrm{E}[m_i(G_n)]=\Theta(n)$ for all $i$'s.
-This is achieved when each of the $p_i$'s are 
-of the form $\beta_i/n^{a_i-1}$ for some 
-non-negative real numbers $\beta_1,\dots,\beta_t$.
-Let $\overbar{\beta}:=\beta_1,\dots,\beta_t$.
-We will write $\overbar{p}(n,\overbar{\beta})$ to denote 
-the list $\beta_1/n^{a_1-1},\dots, \beta_t/n^{a_t-1}$.
-We will treat
-the parameters $\beta_1,\dots, \beta_t$ as fixed
-real constants for the most part and will abbreviate 
-$\overbar{p}(n,\overbar{\beta})$ as $\overbar{p}(n)$.\par
+This is achieved when each of the $p_R$'s are 
+of the form $\beta_R/n^{ar(R)-1}$ for some 
+non-negative real numbers $\InR{\beta}$.
+From now on we will write $G_n\left(\InR{\beta}\right)$
+to denote a random sample of 
+$G^\mathcal{C}\left(n,\left\{ \frac{
+\beta_R}{n^{ar(R)-1}}\right\}_{R\in\sigma}\right)$.
+When the choice of $\InR{\beta}$ is not relevant
+we will write $G_n$ instead of 
+$G_n\left(\InR{\beta}\right)$.\par
 
@@
 %the limit 
-%\[\Ln \mathrm{Pr}(G^\mathcal{C}(n,\overbar{p}
-%(n,\overbar{\beta})) \models \phi)\] 
+%\[\Ln \mathrm{Pr}(G^\mathcal{C}(n,\overline{p}
+%(n,\overline{\beta})) \models \phi)\] 
 %is well defined and varies 
-%analytically with $\overbar{\beta}$.
+%analytically with $\overline{\beta}$.
 % Some care is needed
 %in order to formulate this precisely, as there are some values
-%of $\overbar{\beta}$ for which $\overbar{p}
-%(n,\overbar{\beta})$ asymptotically does not 
+%of $\overline{\beta}$ for which $\overline{p}
+%(n,\overline{\beta})$ asymptotically does not 
 %define a list of 
@@
 %In consequence, if we assign 
-%values to $\overbar{\beta}$ and let
+%values to $\overline{\beta}$ and let
 %$\beta_i>1$ then the random 
-%model $G^\mathcal{C}(n,\overbar{p}
-%(n,\overbar{\beta})$ will not be well defined. 
+%model $G^\mathcal{C}(n,\overline{p}
+%(n,\overline{\beta})$ will not be well defined. 
 %To avoid this we need to impose $\beta_i\in [0,1]$ 
@@
 	%$F_\phi: [0,1]^{t_u}\times [0,\infty)^{t-t_u}
-	$F_\phi: [0,\infty)^{t}
+	$F_\phi: [0,\infty)^{|\sigma|}
 	\rightarrow \R$ given by 
 	\[
-	\overbar{\beta} \mapsto \Ln Pr\big( G^\mathcal{C}(n,\overbar{p}
-	(n,\overbar{\beta})) \models \phi\big)
+	\InR{\beta} \mapsto \Ln Pr\big( G_n\left(
+	\InR{\beta}\right) \models \phi\big)
 	\]
@@
 
-Let $G_1$ and $G_2$ be hypergraphs. We define the $k$ round 
-Ehrenfeucht-Fraisse game on $G_1$ and $G_2$, denoted by
-$\ehr_k(G_1,G_2)$, as follows:
+Let $G^1$ and $G^2$ be hypergraphs. We define the $k$ round 
+Ehrenfeucht-Fraisse game on $G^1$ and $G^2$, denoted by
+$\ehr_k(G^1;G^2)$, as follows:
 The game is played between two players, Spoiler and Duplicator, and
@@
 At the beginning of each round Spoiler chooses a vertex from either
-$V(G_1)$ or $V(G_2)$ and Duplicator responds by choosing a vertex
+$V(G^1)$ or $V(G^2)$ and Duplicator responds by choosing a vertex
 from the other set.
 Let us denote by 
-$v_i$, resp. $u_i$ the vertex from $G_1$, resp. from $G_2$, 
+$v_i$, resp. $u_i$ the vertex from $G^1$, resp. from $G^2$, 
 chosen in the $i$-th round,
@@
 	\item For any $i,j\in [k]$, $v_i=v_j \iff u_i=u_j$.
-	\item Given indices $i_1,\dots, i_a \in [k]$, and a color 
-	$c\in [t]$,  
-	$[v_{i_1},\dots,v_{i_a}] \in E_c(G_1) \iff [u_{i_1},\dots,u_{i_a}]
-	\in E_c(G_2)$.
+	\item Given a relation symbol $R\in \sigma$ 
+	and indices $i_1,\dots, i_{ar(R)} \in [k]$, 
+	$[v_{i_1},\dots,v_{i_{ar(R)}}] \in E_R(G^1) \iff 
+	[u_{i_1},\dots,u_{i_{ar(R)}}]
+	\in E_R(G^2)$.
 
@@
 We define the equivalence relation $=_k$ between hypergraphs as follows:
-We say that $G_1=_k G_2$ if for any sentence $\phi\in 
-FO[\sigma]$ with $qr(\phi)\leq k$ then $G_1\models\phi$ if and 
-only if $G_2\models\phi$. 
+We say that $G^1=_k G^2$ if for any sentence $\phi\in 
+FO[\sigma]$ with $qr(\phi)\leq k$ then ``$G^1\models\phi$ if and 
+only if $G^2\models\phi$". 
 \par
@@
 	[Ehrenfeut, \citealp{ehrenfeucht1961application}] Let
-	$G_1$ and $G_2$ be hypergraphs.
-	Then Duplicator wins $\ehr_k(G_1,G_2)$
-	if and only if $G_1=_k G_2$.	
+	$G^1$ and $G^2$ be hypergraphs.
+	Then Duplicator wins $\ehr_k(G^1;G^2)$
+	if and only if $G^1=_k G^2$.	
 \end{theorem}
 
-Now consider $\overbar{v}$, and $\overbar{u}$ lists of vertices of the same length, $l$,
-from $G_1$ and $G_2$ respectively. We define the $k$ round 
-Ehrenfeucht-Fraisse game on $G_1$ and $G_2$ with initial position given
-by $\overbar{v}$ and $\overbar{u}$, denoted by $\ehr_k(G_1,\overbar{v},G_2,\overbar{u})$,
-the same way as $\ehr_k(G_1,G_2)$, but in this case the game has $l$ extra 
-rounds at the beginning where the vertices in $\overbar{v}$ and $\overbar{u}$ are 
+Let $\overline{v}\in V(G^1)^*$, and 
+$\overline{u}\in V(G^2)^*$ be lists of vertices of the same length, 
+$l=len(\overline{v})=len(\overline{u})$. We define the $k$ round 
+Ehrenfeucht-Fraisse game on $G^1$ and $G^2$ with initial position given
+by $\overline{v}$ and $\overline{u}$, denoted by $\ehr_k(G^1,\overline{v};G^2,\overline{u})$,
+the same way as $\ehr_k(G^1;G^2)$, but in this case the game has $l$ extra 
+rounds at the beginning where the vertices in $\overline{v}$ and $\overline{u}$ are 
 played successively. After this, $k$ more rounds are played normally. \par
@@
 We also define the $k$-round distance Ehrenfeucht-Fraisse game on 
-$G_1$ and $G_2$, denoted by $d\ehr_k(G_1,G_2)$, the same way as
-$\ehr_k(G_1,G_2)$, but now, in order for Duplicator to win the
+$G^1$ and $G^2$, denoted by $d\ehr_k(G^1;G^2)$, the same way as
+$\ehr_k(G^1;G^2)$, but now, in order for Duplicator to win the
 game, the following additional condition has to be satisfied 
-at the end of the $k$-th round:
+at the end of the game:
 \begin{itemize}
-	\item For any $i,j\in [k]$, $d^{G_1}(v_i,v_j)=d^{G_2}(u_i,u_j)$.
+	\item For any $i,j\in [k]$, $d^{G^1}(v_i,v_j)=d^{G^2}(u_i,u_j)$.
 \end{itemize}
 
-Given $\overbar{v}$, and $\overbar{u}$ lists of vertices of the same length,
-from $G_1$ and $G_2$ respectively we define the game 
-$d\ehr_k(G_1,\overbar{v},G_2,\overbar{u})$ analogously to 
-$\ehr_k(G_1,\overbar{v},G_2,\overbar{u})$.
+Given $\overline{v}\in V(G^1)^*$, and $\overline{u}\in V(G^2)^*$
+lists of vertices of the same length,
+we define the game 
+$d\ehr_k(G^1,\overline{v};G^2,\overline{u})$ analogously to 
+$\ehr_k(G^1,\overline{v};G^2,\overline{u})$.
 
@@
 	\item[(3)] the limit probability of random graph belonging to 
-	any of them is an analytic expression on the parameters $\overbar{\beta}$. 
+	any of them is an analytic expression on the parameters $\overline{\beta}$. 
 \end{itemize}
@@
 
-\subsection{Some winning strategies for Duplicator}
+\section{Some winning strategies for Duplicator}
 
@@
 
-Let $G_1$ and $G_2$ be hypergraphs, and let $\overbar{v} \subseteq V(G_1), 
-\overbar{u} \subseteq V(G_2)$ be lists of vertices of the same size.
-We say that $N(\overbar{v};r)$ and $N(\overbar{u};r)$ are
-$k$-similar, or that $\overbar{v}$ and $\overbar{u}$
-have $k$-similar $r$-neighborhoods, if Duplicator wins
-$d\ehr_k(N(\overbar{v};r),\overbar{v},N(\overbar{u};r),\overbar{u})$.\par
-If $X\subseteq V(G_1)$ and $Y\subseteq V(G_2)$
-are sets of vertices we say that $X$ and $Y$ have $k$-similar
-$r$-neighborhoods if we can order their vertices to form
-lists $\overbar{v}$, resp. $\overbar{u}$ such that $N(\overbar{v};r)$ and
-$N(\overbar{u};r)$ are $k$-similar.
+Let $G^1$ and $G^2$ be hypergraphs, and let
+$V_1:=V(G^1), V_2:=V(G^2)$.
+Let $\overline{v} \in V_1^*, 
+\overline{u} \in V_2^*$ be tuples of the same length.
+We say that $\overline{v}$ and $\overline{u}$ have
+$k$-\textbf{similar} $r$-neighborhoods, written as
+$(G^1,\overline{v})\simeq_{k,r}(G^2 \overline{u})$, if Duplicator wins
+$d\ehr_k\big(N(\overline{v};r),
+\overline{v};\, N(\overline{u};r),\overline{u}\big)$.\par
+Given sets of vertices $X\subseteq V_1$ and $Y\subseteq V_2$
+we say that $X$ and $Y$ have $k$-\textbf{similar}
+$r$-neighborhoods, written as
+$X\simeq_{k,r} Y$, if we can order their elements to form
+lists $\overline{v}$, resp. $\overline{u}$ such that 
+$(G^1,\overline{v})\simeq_{k,r}(G^2,\overline{u})$.
 \par
-Now suppose that $X\subseteq V(G_1)$ and $Y\subseteq V(G_2)$ can
-be partitioned into lists $X=\overbar{v_1}\cup \dots \cup \overbar{v_a}$
-and $Y=\overbar{u_1}\cup \dots \cup \overbar{u_b}$ 
-such that $N(\overbar{v_i};r)$'s, and the
-$N(\overbar{u_i};r)$'s, are connected and disjoint. 
-We say that $N(X;r)$ and
-$N(Y;r)$ are $k$-agreeable,
-or that they have $k$-agreeable neighborhoods, 
-if any $\overbar{w}$ among the $\overbar{v_i}$'s or
-among the $\overbar{u_i}$'s satisfies:
-\begin{itemize}
-	\item The number of $\overbar{v_i}$'s and 
-	the number of $\overbar{u_i}$'s satisfying that ``$\overbar{v_i}$ 
-	(resp. $\overbar{u_i}$) and $\overbar{w}$ have $k$-similar 
-	$r$-neighborhoods" are the
-	same or are both greater or equal than $k$.
-\end{itemize}
+Fix $r\in \N$. Suppose that $X\subseteq V_1$ and 
+$Y\subseteq V_2$ can
+be partitioned into sets $X=X_1\cup \dots \cup X_a$
+and $Y=Y_1\cup \dots \cup Y_b$ 
+such that $N(X_i;r)$'s, and the
+$N(Y_i;r)$'s, are connected and disjoint. 
+We say that $X$ and
+$Y$ have $k$-\textbf{agreeable} $r$-neighborhoods,
+written as $(G^1,X)\cong_{k,r} (G^2,Y)$, 
+if for any set $Z\subset V_\delta$, with $\delta\in \{1,2\}$,
+among the $X_i$'s or the $Y_i$'s
+it is satisfied that ``the number of $X_i$'s  
+such that $(G^\delta, Z) \simeq_{k,r} (G^1,X_i)$ 
+and the number of $Y_i$'s such that
+$(G^\delta,Z)\simeq_{k,r} (G^2,Y_i)$
+are both equal or are both greater 
+or equal than $k$" .
 
@@
 	Set $r=(3^k-1)/2$.
-	Let $G_1,G_2$ be hypergraphs, and suppose there exist
-	sets $X\subseteq V(G_1)$, $Y\subseteq V(G_2)$ with the 
+	Let $G^1,G^2$ be hypergraphs and let $V_1:=V(G^1)$, $V_2:=
+	V(G^2)$.
+	Suppose there exist
+	sets $X\subseteq V_1$, $Y\subseteq V_2$ with the 
 	following properties:
 	\begin{enumerate}
-		\item[(1)] $N(X;r)$ and $N(Y;r)$ are $k$-agreeable.
-		\item[(2)] Let $r^\prime\leq r$. Let $v\in V(G_1)$ 
-		such that $d(v,X)>2r^\prime+1$, and let
-		$u_1,\dots,u_{k-1}\in V(G_2)$. Then there exists a vertex
-		$u\in V(G_2)$ with $u,v$ having $k$-similar $r^\prime$-neighborhoods 
-		and satisfying $d(u,u_i)>2r^\prime+1$ for all $u_i$'s as well as
-		$d(u,Y)>2r^\prime +1$.
-		\item[(3)] Let $r^\prime\leq r$. Let $u\in V(G_2)$ 
-		such that $d(u,Y)>2r^\prime+1$, and let
-		$v_1,\dots,v_{k-1}\in V(G_1)$. Then there exists a vertex
-		$v\in V(G_1)$ with $v,u$ having $k$-similar $r^\prime$-neighborhoods 
-		and satisfying $d(v,v_i)>2r^\prime+1$ for all $v_i$'s as well as
-		$d(v,X)>2r^\prime +1$.
+		\item[(1)] $(G^1,X)\cong_{k,r} (G^2,Y)$.
+		\item[(2)] Let $r^\prime\leq r$. Let $v\in V_1$ be
+		a vertex such that $d(X,v)> 2r^\prime + 1$. Let 
+		$\overline{u}\in (V_2)^{k-1}$ be a tuple of vertices. 
+		Then there exists $u\in V_2$ such that 
+		$d(u,\overline{u})>2r^\prime+1$,
+		$d(Y,u)>2r^\prime +1$ and
+		$(G^1,v)\simeq_{k,r^\prime} (G^2,u)$.	
+		\item[(3)] Let $r^\prime\leq r$. Let $u\in V_2$ be
+		a vertex such that $d(Y,u)> 2r^\prime + 1$. Let 
+		$\overline{v}\in (V_1)^{k-1}$ be a tuple of vertices. 
+		Then there exists $v\in V_1$ such that 
+		$d(v,\overline{v})>2r^\prime+1$,
+		$d(X,v)>2r^\prime +1$ and
+		$(G^1,v)\simeq_{k,r^\prime} (G^2,u)$
 	\end{enumerate}
-	Then Duplicator wins $\ehr_k(G_1,G_2)$.
+	Then Duplicator wins $\ehr_k\big(G^1;G^2\big)$.
 \end{theorem}
@@
 \begin{obs} \label{obs1}
-	Let $H_1$, $H_2$ be hypergraphs and 
-	$\overbar{v}$, $\overbar{u}$, be lists of vertices
-	from $V(H_1)$ and $V(H_2)$ respectively. Suppose that
-	Duplicator wins $d\ehr_k(H_1,\overbar{v},H_2,\overbar{u})$.
-	Then, for any $r$ Duplicator also wins
-	$d\ehr_k(N(\overbar{v};r),\overbar{v},N(\overbar{u};r),\overbar{u})$. 
-	In particular, given hypergraphs $G_1, G_2$ and sets
-	$X\subseteq V(G_1)$, $Y\subseteq V(G_2)$ such that
-	$N(X;r)$ and $N(Y;r)$ are $k$-similar, then for any 
-	$r^\prime \leq r$ the graphs
-	$N(X;r^\prime)$ and $N(Y;r^\prime)$ are $k$-similar
-	as well. 
+	Let $H^1$, $H^2$ be hypergraphs and 
+	$\overline{v}\in V(H^1)^*$, $\overline{u}\in V(H^2)^*$,
+	be lists of vertices. Suppose that
+	Duplicator wins $d\ehr_k(H^1,\overline{v}; \, H^2,\overline{u})$.
+	Then, for any $r\in \N$, $(H^1, \overline{v})\simeq_{k,r} 
+	(H^2,\overline{u})$. A direct consequence of this fact 
+	is that 
+	given hypergraphs $G^1, G^2$ and sets
+	$X\subseteq V(G^1)$, $Y\subseteq V(G^2)$ such that
+	$(G^1,X)\simeq_{k,r} (G^2,Y)$ for some $r\in \N$, 
+	then for any $r^\prime \leq r$ it also holds 
+	$(G^1,X)\simeq_{k,r^\prime} (G^2,Y)$
 \end{obs}
+
+Given a set $S$ and tuples $\overline{s},\overline{t}\in S^*$
+we write $\overline{s}^\frown \overline{t}$ to denote their 
+concatenation.
 
@@
 	Let $H_1$, $H_2$ be hypergraphs and 
-	$\overbar{v}$, $\overbar{u}$, be lists of vertices
+	$\overline{v}$, $\overline{u}$, be lists of vertices
 	from $V(H_1)$ and $V(H_2)$ respectively. Suppose 
-	Duplicator wins $d\ehr_k(H_1,\overbar{v},H_2,\overbar{u})$. 
-	Let $v^\prime\in V(H_1),u^\prime\in V(H_2)$ be vertices
+	Duplicator wins $d\ehr_k(H_1,\overline{v};\,H_2,\overline{u})$. 
+	Let $v\in V(H_1),u\in V(H_2)$ be vertices
 	played in the first round of an instance of the game 
 	where Duplicator is following a winning strategy. Then 
-	Duplicator also wins $d\ehr_{k-1}(H_1,\overbar{v_2},
-	H_2,\overbar{u_2})$, where $\overbar{v_2}:=\overbar{v},v^\prime$
-	and $\overbar{u_2}:=\overbar{u},u^\prime$.
+	Duplicator also wins $d\ehr_{k-1}(H_1,\overline{v_2}; \,
+	H_2,\overline{u_2})$, where $\overline{v_2}:=\overline{v}^\frown v$
+	and $\overline{u_2}:=\overline{u}^\frown u$.
 \end{obs}
@@
 \begin{lemma} \label{lemm:Duplicator}
-	Let $G_1$, $G_2$ be hypergraphs and 
-	$\overbar{v}$, $\overbar{u}$, be lists of vertices
-	from $V(G_1)$ and $V(G_2)$ respectively. Let
-	$r$ be greater than zero. Suppose that
-	$N(\overbar{v};3r+1)$ and $N(\overbar{u};3r+1)$ are 
-	$k$-similar. Let $v^\prime\in V(G_1),u^\prime\in V(G_2)$
+	Let $G^1$, $G^2$ be hypergraphs and let $V_1:=V(G^1),
+	V_2:=V(G^2)$. Let $\overline{v}\in V_1^*$ and
+	$\overline{u} \in V_2^*$ be lists of vertices. Let
+	$r\in \N$ be greater than zero. Suppose that
+	$(G^1,\overline{v})\simeq_{k,3r+1} (G^2,\overline{u})$.
+	Let $v \in V_1$ and $u\in V_2$
 	be vertices played in the first round of an instance of 
-	$d\ehr_k(N(\overbar{v};3r+1),\overbar{v},N(\overbar{u};3r+1),\overbar{u})$ 
+	\[
+	d\ehr_k\big(\, N(\overline{v};3r+1),
+	\overline{v}; \quad N(\overline{u};3r+1),\overline{u}\, \big)
+	\]
 	where Duplicator is following a winning strategy. Further suppose
-	that $d(\overbar{v},v_2)\leq 2r+1$ (and in consequence
-	$d(\overbar{u},u_2)\leq 2r+1$ as well). 
-	Let $\overbar{v_2}:=\overbar{v},v^\prime$
-	and $\overbar{u_2}:=\overbar{u},u^\prime$.
-	Then $N(\overbar{v_2};r)$ and $N(\overbar{u_2};r)$ are 
-	$(k-1)$-similar
+	that $d(\overline{v},v)\leq 2r+1$ (and in consequence
+	$d(\overline{u},u)\leq 2r+1$ as well). 
+	Let $\overline{v_2}:=\overline{v}^\frown v$
+	and $\overline{u_2}:=\overline{u}\frown u$.
+	Then $(G^1,\overline{v_2})\simeq_{k-1,r}
+	(G^2,\overline{u_2})$.
 \end{lemma}
@@
 	Using \cref{obs2} we get that Duplicator wins 
-	\[d\ehr_k(N^{G_1}(\overbar{v};3r+1),\overbar{v_2},N^{G_2}(\overbar{u};3r+1)
-	,\overbar{u_2})\]
-	as well. Call $H_1=N^{G_1}(\overbar{v};3r+1)$,
-	$H_2=N^{G_2}(\overbar{u};3r+1)$. Then by \cref{obs2}
+	\[
+	d\ehr_{k-1}\big(\, N(\overline{v};3r+1),
+	\overline{v_2}; \quad N(\overline{u};3r+1)
+	,\overline{u_2} \, \big)\]
+	as well. Call $H_1=N(\overline{v};3r+1)$,
+	$H_2=N(\overline{u};3r+1)$. Then by \cref{obs2}
 	Duplicator wins
 	\[
-	d\ehr_k(N^{H_1}(\overbar{v_2};r),\overbar{v_2},N^{H_2}(\overbar{u_2};r),\overbar{u_2}).
-	\]
-	Because of this if we prove $N^{G_1}(\overbar{v_2};r)
-	=N^{H_1}(\overbar{v_2};r)$ and $N^{G_2}(\overbar{u_2};r)
-	=N^{H_2}(\overbar{u_2};r)$, then we are finished. 
-	Let $z\in N^{G_1}(v^\prime;r)$. Then
-	$d(z,\overbar{v})\leq d(z,v^\prime)+d(v^\prime,\overbar{v})=3r+1$.
-	In consequence, $N^{G_1}(v;r)\subset H_1$. Thus,
-	$N^{G_1}(\overbar{v_2};r)\subseteq H_1$, and $N^{G_1}(\overbar{v_2};r)
-	=N^{H_1}(\overbar{v_2};r)$. Analogously we obtain 
-	$N^{G_2}(\overbar{u_2};r)=N^{H_2}(\overbar{u_2};r)$, as we wanted. 
+	d\ehr_{k-1}\big(\, N^{H_1}(
+	\overline{v_2};r),\overline{v_2};\quad
+	N^{H_2}(\overline{u_2};r),\overline{u_2}\, \big).
+	\]
+	Because of this if we prove $N^{G^1}(\overline{v_2};r)
+	=N^{H_1}(\overline{v_2};r)$ and $N^{G^2}(\overline{u_2};r)
+	=N^{H_2}(\overline{u_2};r)$, then we are finished. 
+	Let $z\in N^{G^1}(v^\prime;r)$. Then
+	$d(z,\overline{v})\leq d(z,v^\prime)+d(v^\prime,\overline{v})=3r+1$.
+	In consequence, $N^{G^1}(v;r)\subset H_1$. Thus,
+	$N^{G^1}(\overline{v_2};r)\subseteq H_1$, and $N^{G^1}(\overline{v_2};r)
+	=N^{H_1}(\overline{v_2};r)$. Analogously we obtain 
+	$N^{G^2}(\overline{u_2};r)=N^{H_2}(\overline{u_2};r)$, as we wanted. 
 \end{proof}
+\noindent\rule{2cm}{0.4pt}\par
 
@@
 	Let us denote by $w_i$ and $z_i$ the vertices played
-	in $G_1$ and $G_2$ respectively during the $i$-th
-	round of $\ehr_k(G_1,G_2)$. 
+	in $G^1$ and $G^2$ respectively during the $i$-th
+	round of $\ehr_k(G^1,G^2)$. 
 	%Set 
-	%$\overbar{v}[i]:=v_1,\dots,v_i$ and
-	%$\overbar{u}[i]:=u_1,\dots,u_i$
+	%$\overline{v}[i]:=v_1,\dots,v_i$ and
+	%$\overline{u}[i]:=u_1,\dots,u_i$
 	%We say that Duplicator can play following the strategy $S$
 	%if they can play in a way that
-	%at the end of the $s$-th round, $\overbar{w}[s]$ and
-	%$\overbar{z}[s]$ have $(k-s)$-similar $r_{k-s}$-neighborhoods.
+	%at the end of the $s$-th round, $\overline{w}[s]$ and
+	%$\overline{z}[s]$ have $(k-s)$-similar $r_{k-s}$-neighborhoods.
 	%In particular this means that at the end of the $k$-th
-	%round Duplicator will have won $\ehr_k(G_1,G_2)$.
+	%round Duplicator will have won $\ehr_k(G^1,G^2)$.
 	\par
 
-	Let $\overbar{v_1},\dots,\overbar{v_a}$ and 
-	$\overbar{u_1},\dots,\overbar{u_b}$ be lists
-	forming partitions of 
-	$X$ and $Y$ respectively, and assume they
-	are as in the definition of $k$-agreeability.
-	Set 
-	\[\mathcal{X}[0]=\{\overbar{v_1},\dots,\overbar{v_a}\},
-	\quad \mathcal{Y}[0]=\{\overbar{u_1},\dots,\overbar{u_b}\}.\]
-	That is, $\mathcal{X}[0]$ and $\mathcal{Y}[0]$ are the whose elements
-	are the $\overbar{v_i}$'s and $\overbar{u_i}$'s respectively. 
-	At the end of the $s$-th round $\mathcal{X}[s-1]$,
-	resp. $\mathcal{Y}[s-1]$, will be updated into 
-	$\mathcal{X}[s]$,
-	resp. $\mathcal{Y}[s]$, by performing on it
-	some of the following operations: adding a new list
-	to it, appending one vertex to an existing list, and 
-	marking a list with the index $s$. Duplicator will
-	keep track of the sets $\mathcal{X}[s]$ and $\mathcal{Y}[s]$.\par
-
-	We show first an strategy for Duplicator and will prove its
-	correctness afterwards. The strategy is as follows: At the 
-	beginning of the $s$-th round suppose Spoiler plays $w_s$ in
-	$G_1$. The case where they play $z_s$ in $G_2$ is symmetric.
-	Call $r=r_{k-s}$. There are three possibilities. 
-	\begin{itemize}
-		\item[Case 1:] The vertex $w_s$ satisfies
-		$d(w_s,\overbar{v})>2r+1$ for all 
-		$\overbar{v}\in \mathcal{X}[s-1]$. Then Duplicator 
-		can find a vertex $z_s$ in $G_2$ such that
-		$d(z_s,\overbar{u})>2r+1$ for all 
-		$\overbar{u}\in \mathcal{Y}[s-1]$ satisfying 
-		that $w_s$ and $z_s$ have $(k-s)$-similar
-		$r$-neighborhoods. To form $ \mathcal{X}[s]$
-		and $ \mathcal{Y}[s]$, add to $\mathcal{X}[s-1]$
-		and $ \mathcal{Y}[s-1]$ the lists consisting
-		of only $w_s$ and only $z_s$ respectively, and mark
-		them with the number $s$.
-
-		\item[Case 2:] The vertex $w_s$ satisfies
-		$d(w_s,\overbar{v})\leq 2r+1$ for a unique 
-		$\overbar{v}\in \mathcal{X}[s-1]$,and
-		$\overbar{v}$ is marked. In this case,
-		find the list $\overbar{u}\in \mathcal{Y}[s-1]$
-		with the same mark. Duplicator 
-		then can chose $z_s\in N(\overbar{u},2r+1)$
-		in response to $w_s$ according to a winning strategy
-		for
-		\[
-		d\ehr_{k-s}(N(\overbar{v},3r+1),\overbar{v},
-		N(\overbar{u},3r+1),\overbar{u}).
-		\]
-		To form $ \mathcal{X}[s]$
-		and $ \mathcal{Y}[s]$, append $w_s$ and $z_s$
-		to $\overbar{v}$ and $\overbar{u}$ respectively.
-
-		\item[Case 3:] The vertex $w_s$ satisfies
-		$d(w_s,\overbar{v})\leq 2r+1$ for a unique 
-		$\overbar{v}\in \mathcal{X}[s-1]$,and
-		$\overbar{v}$ is not marked. In this case we 
-		can	find a non-marked 
-		list $\overbar{u}\in \mathcal{Y}[s-1]$
-		such that $\overbar{v}$ and $\overbar{u}$ 
-		have $(k-s)$-similar $(3r+1)$-neighborhoods. 
-		Duplicator then can chose $z_s\in N(\overbar{u},2r+1)$
-		in response to $w_s$ according to a winning strategy
-		for
-		\[
-		d\ehr_{k-s}(N(\overbar{v},3r+1),\overbar{v},
-		N(\overbar{u},3r+1),\overbar{u}).
-		\]
-		To form $ \mathcal{X}[s]$
-		and $ \mathcal{Y}[s]$, append $w_s$ and $z_s$
-		to $\overbar{v}$ and $\overbar{u}$ respectively,
-		and mark those lists with the number $s$. 
-	\end{itemize}
-
-	All that is left now is to prove the correctness of the
-	strategy. We show that at the end the $s$-th round, if 
-	two lists $\overbar{v} \in \mathcal{X}[s]$ and 
-	$\overbar{u} \in \mathcal{Z}[s]$ have the same mark then
-	$\overbar{v}$ and $\overbar{u}$ have $(k-s)$-similar
-	$r_{k-s}$-neighborhoods. This happens trivially at
-	the end of the zeroth round -i.e., the beginning 
-	of the game- as there are no marked lists. Assume the
-	statement holds up to the end of the $(s-1)$-th round, 
-	where $s>0$.
-
-	\begin{itemize}
-		\item[Case 1:] Notice that the lists
-		in $\mathcal{Y}[s-1]$ only contain the
-		vertices previously played in $G_2$ and 
-		the ones from $Y$. Thus, assumption $(3)$ 
-		of the theorem, (or assumption $(2)$ in the 
-		symmetric
-		case where Spoiler plays in $G_2$) assures us
-		that Duplicator can always find such $z_s$ 
-		sufficiently far away from all the other lists. 
-		In this case, the only new marked lists in $\mathcal{X}[s]$
-		and $\mathcal{Y}[s]$ are the ones
-		consisting of $w_s$ and $z_s$ respectively. By assumption
-		$w_s$ and $z_s$ have $(k-s)$-similar $r_{k-s}$-neighborhoods.
-
-		\item[Case 2:] Notice that by the induction hypothesis 
-		$\overbar{v}$ and $\overbar{u}$ have $(k-s+1)$-similar
-		$r_{s-k+1}$-neighborhoods, and in consequence a winning strategy
-		for Duplicator exists. Using \cref{lemm:Duplicator} we obtain 
-		that the extended lists $\overbar{v},w_s$ and $\overbar{u},z_s$
-		have $(k-s)$-similar $r_{s-k}$-neighborhoods.
-
-		\item[Case 3:] This case is analogous to the previous one.
-		The definition of $k$-agreeability implies that there is 
-		such an unmarked list $\overbar{u}$ available. Using \cref{lemm:Duplicator} 
-		we obtain 
-		that the extended lists $\overbar{v},w_s$ and $\overbar{u},z_s$
-		have $(k-s)$-similar $r_{s-k}$-neighborhoods.	
-	\end{itemize}
-
-	In the three cases, if $\overbar{v}$ and $\overbar{v}$
-	are lists in $\mathcal{X}[s-1]$ and $\mathcal{Y}[s-1]$
-	respectively that share the same mark and remain unmodified
-	in $\mathcal{X}[s]$ and $\mathcal{Y}[s]$, then by the 
-	induction hypothesis $\overbar{v}$ and $\overbar{v}$
-	have $(k-s+1)$-similar $r_{k-s+1}$-neighborhoods. This
-	easily implies that they also have
-	$(k-s)$-similar $r_{k-s}$-neighborhoods.\par
-	At the end of the game, if $\overbar{v}\in \mathcal{X}[k]$ and 
-	$\overbar{u}\in \mathcal{Y}[k]$ are lists with the same mark
-	then the natural mapping between $\overbar{v}$ and $\overbar{u}$
-	defines an isomorphism between $G_1[\overbar{v}]$ and $G_2[\overbar{u}]$.
+	Let $X_1,\dots,X_a$ and 
+	$Y_1,\dots,Y_b$ be partitions of 
+	$X$ and $Y$ respectively
+	as in the definition of $k$-agreeability.
+	We will show a winning strategy for Duplicator
+	in $d\ehr_{k}\big(G^1;\, G^2\big)$.	
+	Let $r_k=1$ and for each $i\in [k-1]$ 
+	let $r_i=3r_{i+1}+1$. In particular, 
+	$r_1=r=(3^k-1)/2$.
+
+% During the game
+%	Duplicator will track of sets of lists $L^1[i]$'s
+%	and $L^2[i]$'s. At the end of the $i$-th round
+%	Duplicator will obtain $L^1[i]$, resp $L^2[i]$
+%	performing one of the following operations on 
+%	$L^1[i-1]$, resp $L^2[i-1]$:
+%	\begin{itemize}
+%		\item Adding a list $\overline{v}\in (V_1)^*$
+%		to $L^1[i-1]$ and marking it with the index $i$. 
+%		\item Appending a new vertex $v\in V_1$ to an 
+%		existing list $\overline{v}\in L^1[i-1]$.
+%	\end{itemize}	
+%	Let $r_k=1$ and for each $i\in [k-1]$ 
+%	let $r_i=3r_{i+1}+1$.
+%	We are going to show that Duplicator can 
+%	play in a way such that
+%	at the end of the $i$-th 
+%	round the following conditions
+%	are satisfied:
+%	\begin{itemize}
+%		\item[(1)] 
+%		
+%		
+%		
+%	\end{itemize}
+%	
+%	
+%	\[\mathcal{X}[0]=\emptyset,
+%	\quad \mathcal{Y}[0]=\emptyset.\]
+%	At the end of the $s$-th round $\mathcal{X}[s-1]$,
+%	resp. $\mathcal{Y}[s-1]$, will be updated into 
+%	$\mathcal{X}[s]$,
+%	resp. $\mathcal{Y}[s]$, by performing on it
+%	some of the following operations: adding a new list
+%	to it, appending one vertex to an existing list, and 
+%	marking a list with the index $s$. Duplicator will
+%	keep track of the sets $\mathcal{X}[s]$ and $\mathcal{Y}[s]$.\par
+%	
+%	We show first an strategy for Duplicator and will prove its
+%	correctness afterwards. The strategy is as follows: At the 
+%	beginning of the $s$-th round suppose Spoiler plays $w_s$ in
+%	$G^1$. The case where they play $z_s$ in $G^2$ is symmetric.
+%	Call $r=r_{k-s}$. There are three possibilities. 
+%	\begin{itemize}
+%		\item[Case 1:] The vertex $w_s$ satisfies
+%		$d(w_s,\overline{v})>2r+1$ for all 
+%		$\overline{v}\in \mathcal{X}[s-1]$. Then Duplicator 
+%		can find a vertex $z_s$ in $G^2$ such that
+%		$d(z_s,\overline{u})>2r+1$ for all 
+%		$\overline{u}\in \mathcal{Y}[s-1]$ satisfying 
+%		that $w_s$ and $z_s$ have $(k-s)$-similar
+%		$r$-neighborhoods. To form $ \mathcal{X}[s]$
+%		and $ \mathcal{Y}[s]$, add to $\mathcal{X}[s-1]$
+%		and $ \mathcal{Y}[s-1]$ the lists consisting
+%		of only $w_s$ and only $z_s$ respectively, and mark
+%		them with the number $s$.
+%		
+%		\item[Case 2:] The vertex $w_s$ satisfies
+%		$d(w_s,\overline{v})\leq 2r+1$ for a unique 
+%		$\overline{v}\in \mathcal{X}[s-1]$,and
+%		$\overline{v}$ is marked. In this case,
+%		find the list $\overline{u}\in \mathcal{Y}[s-1]$
+%		with the same mark. Duplicator 
+%		then can chose $z_s\in N(\overline{u},2r+1)$
+%		in response to $w_s$ according to a winning strategy
+%		for
+%		\[
+%		d\ehr_{k-s}(N(\overline{v},3r+1),\overline{v},
+%		N(\overline{u},3r+1),\overline{u}).
+%		\]
+%		To form $ \mathcal{X}[s]$
+%		and $ \mathcal{Y}[s]$, append $w_s$ and $z_s$
+%		to $\overline{v}$ and $\overline{u}$ respectively.
+%		
+%		\item[Case 3:] The vertex $w_s$ satisfies
+%		$d(w_s,\overline{v})\leq 2r+1$ for a unique 
+%		$\overline{v}\in \mathcal{X}[s-1]$,and
+%		$\overline{v}$ is not marked. In this case we 
+%		can	find a non-marked 
+%		list $\overline{u}\in \mathcal{Y}[s-1]$
+%		such that $\overline{v}$ and $\overline{u}$ 
+%		have $(k-s)$-similar $(3r+1)$-neighborhoods. 
+%		Duplicator then can chose $z_s\in N(\overline{u},2r+1)$
+%		in response to $w_s$ according to a winning strategy
+%		for
+%		\[
+%		d\ehr_{k-s}(N(\overline{v},3r+1),\overline{v},
+%		N(\overline{u},3r+1),\overline{u}).
+%		\]
+%		To form $ \mathcal{X}[s]$
+%		and $ \mathcal{Y}[s]$, append $w_s$ and $z_s$
+%		to $\overline{v}$ and $\overline{u}$ respectively,
+%		and mark those lists with the number $s$. 
+%	\end{itemize}
+%	
+%	All that is left now is to prove the correctness of the
+%	strategy. We show that at the end the $s$-th round, if 
+%	two lists $\overline{v} \in \mathcal{X}[s]$ and 
+%	$\overline{u} \in \mathcal{Z}[s]$ have the same mark then
+%	$\overline{v}$ and $\overline{u}$ have $(k-s)$-similar
+%	$r_{k-s}$-neighborhoods. This happens trivially at
+%	the end of the zeroth round -i.e., the beginning 
+%	of the game- as there are no marked lists. Assume the
+%	statement holds up to the end of the $(s-1)$-th round, 
+%	where $s>0$. 
+%	
+%	\begin{itemize}
+%		\item[Case 1:] Notice that the lists
+%		in $\mathcal{Y}[s-1]$ only contain the
+%		vertices previously played in $G^2$ and 
+%		the ones from $Y$. Thus, assumption $(3)$ 
+%		of the theorem, (or assumption $(2)$ in the 
+%		symmetric
+%		case where Spoiler plays in $G^2$) assures us
+%		that Duplicator can always find such $z_s$ 
+%		sufficiently far away from all the other lists. 
+%		In this case, the only new marked lists in $\mathcal{X}[s]$
+%		and $\mathcal{Y}[s]$ are the ones
+%		consisting of $w_s$ and $z_s$ respectively. By assumption
+%		$w_s$ and $z_s$ have $(k-s)$-similar $r_{k-s}$-neighborhoods.
+%		
+%		\item[Case 2:] Notice that by the induction hypothesis 
+%		$\overline{v}$ and $\overline{u}$ have $(k-s+1)$-similar
+%		$r_{s-k+1}$-neighborhoods, and in consequence a winning strategy
+%		for Duplicator exists. Using \cref{lemm:Duplicator} we obtain 
+%		that the extended lists $\overline{v},w_s$ and $\overline{u},z_s$
+%		have $(k-s)$-similar $r_{s-k}$-neighborhoods. 	
+%		
+%		\item[Case 3:] This case is analogous to the previous one.
+%		The definition of $k$-agreeability implies that there is 
+%		such an unmarked list $\overline{u}$ available. Using \cref{lemm:Duplicator} 
+%		we obtain 
+%		that the extended lists $\overline{v},w_s$ and $\overline{u},z_s$
+%		have $(k-s)$-similar $r_{s-k}$-neighborhoods.	
+%	\end{itemize} 
+%	
+%	In the three cases, if $\overline{v}$ and $\overline{v}$
+%	are lists in $\mathcal{X}[s-1]$ and $\mathcal{Y}[s-1]$
+%	respectively that share the same mark and remain unmodified
+%	in $\mathcal{X}[s]$ and $\mathcal{Y}[s]$, then by the 
+%	induction hypothesis $\overline{v}$ and $\overline{v}$
+%	have $(k-s+1)$-similar $r_{k-s+1}$-neighborhoods. This
+%	easily implies that they also have
+%	$(k-s)$-similar $r_{k-s}$-neighborhoods.\par
+%	At the end of the game, if $\overline{v}\in \mathcal{X}[k]$ and 
+%	$\overline{u}\in \mathcal{Y}[k]$ are lists with the same mark
+%	then the natural mapping between $\overline{v}$ and $\overline{u}$
+%	defines an isomorphism between $G^1[\overline{v}]$ and $G^2[\overline{u}]$.
 \end{proof}
@@
 %Indeed, let $n\in \N$ and let $G_n$ be a random hypergraph sampled from
-% $\mathrm{G}^\mathcal{C}(n,\overbar{p})$. Let
-% $\overbar{h}$ be an ordering of the vertices
+% $\mathrm{G}^\mathcal{C}(n,\overline{p})$. Let
+% $\overline{h}$ be an ordering of the vertices
 %in $V(H)$. For any list 
-% $\overbar{v}\in [n]_{|V(H)|}$ (recall that $[n]=V(G)$), 
-%let $X_{\overbar{v}}$ be the random indicator variable
+% $\overline{v}\in [n]_{|V(H)|}$ (recall that $[n]=V(G)$), 
+%let $X_{\overline{v}}$ be the random indicator variable
 %that takes value $1$ if the natural map 
-% $f:\overbar{h}\rightarrow \overbar{v}$ defines an homomorphism 
-%between $H$ and $G$. That is, $X_{\overbar{v}}$ takes value $1$
+% $f:\overline{h}\rightarrow \overline{v}$ defines an homomorphism 
+%between $H$ and $G$. That is, $X_{\overline{v}}$ takes value $1$
 %with probability
@@
 % $
-%and zero otherwise. The sum of all $X_{\overbar{v}}$'s for 
-%all $\overbar{v}\in [n]_{|V(H)|}$ counts how many labelled 
+%and zero otherwise. The sum of all $X_{\overline{v}}$'s for 
+%all $\overline{v}\in [n]_{|V(H)|}$ counts how many labelled 
 %copies of $H$ are in $G_n$. Thus, 
 %\[ \mathrm{E}\big[\# \text{labelled copies of }H \text{ in } G_n\big] 
-%= \sum_{\overbar{v}\in [n]_{|V(G)|}} 
+%= \sum_{\overline{v}\in [n]_{|V(G)|}} 
 %\prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
@@
 
-\subsection{Counting colored sub-hypergraphs}
-
-\begin{definition} 
-	Given a set $\Sigma$, a $\Sigma$-hypergraph is a pair
-	$(G,\chi)$ consisting of an hypergraph $G$ and a map 
-	$\chi: V(G) \rightarrow \Sigma$.  
-	Given two $\Sigma$-hypergraphs $(H,\rho)$ and $(G,\chi)$,
-	an isomorphism between them is an hypergraph isomorphism 
-	$f:V(H)\rightarrow V(G)$ satisfying $\rho(v)=\chi(f(v))$
-	for any $v\in V(H)$. 
-	An automorphism of a $\Sigma$-hypergraph $(G,\chi)$ is an
-	isomorphism from $(G,\chi)$ to itself. As with the case of
-	hypergraphs we write $Aut(G,\chi)$ to denote the group of 
-	automorphisms of $(G,\chi)$.
-	\par
-	Let $(H,\rho), (G,\chi)$ be two $\Sigma$-hypergraphs. 
-	Then a copy of $H$ in $G$ is
-	a sub-hypergraph $H^\prime\subset G$ such that 
-	$(H,\rho)$ is isomorphic to 
-	$(H^\prime,\chi|_{_{H^\prime}})$.\par
-	Given a $\Sigma$-hypergraph $(G,\chi)$ and a set $V$ we
-	define the set $Copies(S,(G, \chi))$ as the one that contains all 
-	possible $\Sigma$-hypergraphs $(H,\rho)$ isomorphic to $(G,\chi)$ 
-	such that $V(H)\subset S$.	
-\end{definition}
-
-\begin{definition}
-	Given a set $\Sigma$, a random $\Sigma$-coloring of $G_n$ is 
-	a random function $\chi_n: [n]\rightarrow \Sigma$. We say that	
-	$\chi_n$ is symmetric if for any $s\in \Sigma$ the probability
-	$\mathrm{Pr}\big( \chi_n(v)=s \big)$ is the same for any vertex
-	$v\in [n]$. Notation $\mathrm{Pr}\big[\chi_n=s\big]$. \par
-	For each $n\in \N$ let $\chi_n$ be a random $\Sigma$-coloring of $G_n$.
-	We say that the succession $(\chi_n)_{n\in \N}$ is regular if
-	the $\chi_n$'s are symmetric and for any $s\in \Sigma$ the limit
-	$\Ln \mathrm{Pr}\big[ \chi_n = s \big]$ exists. 
-\end{definition}
-
-Remark: A random coloring $\chi$ of $G_n$ does not have to be independent from
-$G_n$. In fact, in the cases we are going to consider $\chi$ will be determined
-by $G_n$.
-
-\begin{definition}
-	Let $\Sigma_1,\dots,\Sigma_k$ be a sets. For each $i\in [k]$
-	let $(\chi_{n,i})_{n \in \N}$ be a random regular sequence of
-	$\Sigma_i$-colorings.
-	Let $\mathcal{F}$ be a family of hypergraphs.
-	We say that the successions $(\chi_{n,1})_{n \in \N},\dots,
-	(\chi_{n,k})_{n \in \N}$ are $\mathcal{F}$-independent if
-	for any given
-	\begin{itemize}
-		\item fixed finite number of copies of hypergraphs from 
-		$\mathcal{F}$ in $\N$,
-		\[
-		S \subset \bigcup_{H\in \mathcal{F}} Copies(H,\N).
-		\]		
-		\item fixed disjoint sets of vertices 
-		$V_1, \dots, V_k \subset \bigcup_{H\in S} V(H).$
-		\item for each $i\in [k]$ and each $v\in V_i$, 
-		a fixed label $s(v)\in \Sigma_i$
-	\end{itemize}
-	it is satisfied
-	\[
-	\Ln \mathrm{Pr}\big(
-	\bigwedge_{i=1}^k \bigwedge_{v\in V_i} \chi_{n,i}(v)=s(v)
-	\, \big| \, \bigwedge_{H\in S} H\subset G_n \,
-	\big) = \prod_{i=1}^k \prod_{v\in V_i} \mathrm{Pr}\big[\chi_i=s(v)
-	\big]		
-	\]  
-\end{definition}
-
-\begin{definition}
-	Let $H_1,\dots, H_k$ be hypergraphs. Let $n,b_1,\dots,b_k\in \N$
-	A $b_1,\dots,b_k$-configuration of $H_1,\dots, H_k$ over $[n]$
-	is an ordered tuple $(O_1,\dots,O_k)$ where for each $i\in [k]$
-	$O_i$ is an ordered $b_i$-tuple of different $H_i$-hypergraphs 
-	over $[n]$. In other words, each $O_i$ is an element of
-	$\big( Copies(H,[n])\big)_{b_i}$, and the set of 
-	$b_1,\dots,b_k$-configurations of $H_1,\dots, H_k$ over $[n]$
-	is precisely $\prod_{i=1}^{k}\big( Copies(H,[n])\big)_{b_i}$.
-\end{definition}
-
-\begin{definition}
- 	The underlying set of a configuration $\omega
- 	=  (O_1, \dots, O_k)$ is the defined as
- 	$S_{\omega}:=\{ H\in O_i \, | \, i\in [k]\}$.
- 	A configuration $\omega$ is called disjoint
-	if all the hypergraphs belonging to its underlying set
-	$S_\omega$ have disjoint sets of vertices. 
-\end{definition}
-
-\begin{theorem}
-	Let $k\in \N$. For each $i\in [k]$ 
-	\begin{itemize}
-		\item Let $\Sigma_i$ be a set, let $H_i$ be a unicycle and 
-		let $\rho^i$ be a $\Sigma_i$-coloring of $H_i$.
-		\item Let $(\chi^i_n)_{n\in\N}$ be a succession of
-		random $\Sigma_i$-colorings of $(G_n)_{n\in \N}$
-		\item Let $X_{i,n}$ be the random variable that counts
-		the number of copies of $(H_i, \rho^i)$ in
-		$(G_n,\chi^i_n)$.				
-	\end{itemize}
-	Let $\mathcal{F}=\{H_1,\dots, H_n\}$. Suppose that the
-	successions $(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
-	are $\mathcal{F}$-independent. Then, for each $a_1,\dots,a_k\in \N$
-	\[
-	\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k X_{n,i}=a_i  \big)=
-	\prod_{i=1}^{k}e^{-\lambda_i}\frac{\lambda_i^{a_i}}{a_i!},
-	\]
-	where for each $i\in [k]$,
-	\[
-	\lambda_i:= \frac{\prod_{j\in \sigma} \beta_j^{e_j(H_i)}}{|Aut(H_i,\rho^i)|} 
-	\prod_{v\in V(H_i)} \mathrm{Pr}\big[\chi^i=\rho^i(v)\big].
-	\]
-\end{theorem}
-\begin{proof}
-	Because of \cref{thm:BrunSieve} we only need to show that for any 
-	fixed $b_1,\dots, b_k\in \N$ it is satisfied
-	\[
-	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
-	\prod_{i=1}^{k} \lambda_i^{b_i}.		
-	\]
-	For each $n\in \N$ let $\Omega_n$ be the set
-	of $b_1, \dots, b_k$-configurations of $(H_1,\rho^1)
-	,\dots, (H_k, \rho^k)$ over $[n]$. Then
-	\[
-	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
-	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
-	\mathrm{Pr}
-	\big(
-	(O_1,\dots, O_k) \subset G_n
-	\big).	
-	\]
-	Let $\Omega^{\times}_n\subset \Omega_n$ be the set of 
-	disjoint configurations in $\Omega_n$. Because of REF,
-	\[
-	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
-	\mathrm{Pr}
-	\big(
-	(O_1,\dots, O_k) \subset G_n
-	\big)=
-	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
-	\mathrm{Pr}\big(
-	(O_1,\dots, O_k) \subset G_n
-	\big).
-	\]
-	Because of the symmetry of the random hypergraph $G_n$ and
-	the colorings $\chi^1_n, \dots, \chi^k_n$ the probability
-	$\mathrm{Pr}\big(
-	(O_1,\dots, O_k) \subset G_n
-	\big)$ is the same for all $(U_1,\dots, U_k)\in 
-	\Omega^\times_n$. Thus, if we fix
-	$(O_1, \dots, O_k)$ a 
-	disjoint $b_1,\dots,b_k$-configuration of
-	 $(H_1,\rho^1)
-	,\dots, (H_k, \rho^k)$ over $\N$, 
-	\[
-	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
-	\mathrm{Pr}\big(
-	(O_1,\dots, O_k) \subset G_n
-	\big) =
-	\Ln |\Omega^{\times}_n|\cdot \mathrm{Pr}\big(
-	(U_1,\dots, U_k) \subset G_n
-	\big).
-	\]
-	Let $S$ be the underlying set of the configuration $(U_1,\dots,U_k)$.
-	Let $l= \sum_{H\in S} v(S)$. Then it is satisfied 
-	\[
-	|\Omega^{\times}_n|= \frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}.
-	\]
-	Using the definition of $(U_1,\dots, U_k) \subset G_n$ and
-	substituting $|\Omega^{\times}_n|$ we get
-	\[
-	\Ln |\Omega^{\times}_n|\cdot \mathrm{Pr}\big(
-	(U_1,\dots, U_k) \subset G_n
-	\big) = \Ln
-	\frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot
-	\PR{\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
-	(H,\rho)\subset (G_n, \chi_n^i)}.
-	\]
-	But the event $(H,\rho)\subset (G_n, \chi_n^i)$ is equivalent to $H\subset G_n$ and
-	$\chi_n^i(v)=\rho(v)$ for all $v\in V(H)$. Thus the LHS of last equation equals
-	\[
-	\Ln
-	\frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot
-	\Pr\Big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
-	\big(H\subset G_n \bigwedge_{v\in V(H)} \chi_n^i(v)=\rho(v) \big) \Big).
-	\]
-	For each $n\in \N$ let $A_n$ the event
-	\[
-	A_n:=\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
-	H\subset G_n.
-	\]	
-	Then,
-	\begin{align*}
-	&\Pr\Big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
-	\big(H\subset G_n \bigwedge_{v\in V(H)} \chi_n^i(v)=\rho(v) \big) \Big)=\\
-	&\Pr\big(A_n\big)\cdot \Pr\big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
-	\bigwedge_{v\in V(H)} \chi^i_n(v)=\rho(v) \, \big| \, A \big).
-	\end{align*}
-	It holds that
-	\[
-	\PR{A_n}=\frac{1}{n^l} \prod_{i=1}^{k}\prod_{R\in \sigma} \beta_R^{e_R(H_i)\cdot b_i},
-	\]
-	and in consequence 
-	\[
-	\Ln \frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot \PR{A_n}
-	= \frac{\prod_{i=1}^{k}\prod_{R\in \sigma} \beta_R^{e_R(H_i)\cdot b_i}}
-	{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}.
-	\]
-	Finally, using the hypothesis that 
-	$(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
-	are $\mathcal{F}$-independent we obtain
-	\[
-	\Ln \Pr\big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
-	\bigwedge_{v\in V(H)} \chi^i_n(v)=\rho(v) \, \big| \, A \big)
-	= \prod_{i=1}^{k} \prod_{v\in V(H_i)} \Pr\big[ \chi^i=\rho^i(v)\big]^{b_i}.
-	\]
-	The result follows from joining equations. 
-\end{proof}
-
-\begin{definition}
-	Let $\Sigma$ be a set containing the empty label $\emptyset$.
-	Let $V\subset [n]$. We say that a random $\Sigma$-coloring $\chi$
-	of $G_n$ is $V$-symmetric if $\chi(v)=\emptyset$ if and only if $v\in V$ and
-	for any $s\in \Sigma$ the probability $\Pr(\chi(v)=s)$ is the same for all 
-	$v\in [n]\setminus V$. \par
-	Let $V\subset \N$ be a finite set of vertices and let $(\chi^n)_{n\in \N}$
-	be a succession such that each $\chi^n$ is a random coloring of $G_n$. We
-	call the succession $(\chi^n)_{n\in \N}$ $V$-regular if each $\chi^n$ is
-	$V$-symmetric and for all $s\in \Sigma$ and $v\in \N \setminus \N$ the limit 
-	$\Ln \PR{\chi^n(v)=s}$ exists. 
-\end{definition}
-
-\begin{definition}
-	Let $\Sigma$ be a set containing the empty label $\emptyset$. A rooted $\Sigma$-edge
-	is a $\Sigma$-hypergraph $(e,\chi)$ where $e$ is an edge 
-	(i.e., an hypergraph consisting of only one edge), and there is a unique vertex
-	$v\in V(e)$ such that $\chi(v)=\emptyset$.
-	Given a rooted $\Sigma$-edge $(e,\chi)$, a set of vertices $V$ and a vertex $v\in \N$
-	we define the set $Copies((e,\chi),(V,v))$ as the set of copies 
-	$(e^\prime, \chi^\prime) \in  Copies((e,\chi),V)$ such that $v$ is
-	the root of $(e^\prime,\chi^\prime)$.
-\end{definition}
-
-\begin{definition} 
-	Let $V\subset \N$ be a finite set of vertices. 
-	Let $\Sigma_1,\dots, \Sigma_k$ be sets containing the empty label 
-	$\emptyset$. For each $i\in [k]$ and each $n\in \N$
-	let $\chi_i^n$ be a random $\Sigma_i$-coloring
-	of $G_n$ satisfying that the succession $(\chi_i^n)_{n\in \N}$ is
-	$V$-regular. We say that the sequences $(\chi_1^n)_{n\in \N},
-	\dots, (\chi_k^n)_{n\in \N}$ are asymptotically independent
-	with respect to edges intersecting $V$ if for any given
-	\begin{itemize}
-		\item fixed finite set of edges $S\subset E(\N)$ such that any edge $e\in S$ 
-		contains some vertex in $V$,
-		\item fixed disjoint sets of vertices $V_1,\dots, V_k \subset \bigcup_{e\in S}e$ 
-		satisfying $V\cup V_i=\emptyset$ for all $i\in [k]$, and
-		\item for each $i\in [k]$ and $v\in V_i$ a fixed label $s(v)\in \Sigma_i$
-		different from the empty label,
-	\end{itemize}
-	it is satisfied 
-	\[
-	\Ln \mathrm{Pr}\big(
-	\bigwedge_{i=1}^k \bigwedge_{v\in V_i} \chi_{n,i}(v)=s(v)
-	\, \big| \, \bigwedge_{e\in S} e\subset G_n \,
-	\big) = \prod_{i=1}^k \prod_{v\in V_i} \mathrm{Pr}\big[\chi_i=s(v)
-	\big]		
-	\]
-\end{definition}
-
-\begin{theorem}
-	\begin{theorem}
-		Let $k\in \N$.	For each $i\in [k]$ 
-		\begin{itemize}
-			\item Let $v_i\in \N$ be a vertex. Define $V:=\{v_1,\dots,v_k\}$.
-			\item Let $\Sigma_i$ be a set containing the empty label, and let $S_i$ be a set
-			of non-isomorphic rooted $\Sigma_i$-edges. 
-			\item For each $n\in \N$ let $\chi^i_n$ be random $\Sigma_i$-coloring
-			$G_n$ satisfying that the succession $(\chi^i_n)_{n\in \N}$ is $V$-regular. 
-			\item For each $(e,\rho)\in S_i$, let $X^{(e,\rho)}_{n,i}$ be the random 
-			variable that counts the number of copies in $Copies((e,\rho),([n],v_i))$
-			that appear in $(G_n,\chi^i_n)$.				
-		\end{itemize}
-		Suppose that the
-		successions $(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
-		are independent with respect to edges intersecting $V$.
-		Then, for any fixed natural numbers 
-		$(a^{(e,\rho)}_{i})_{i\in [k], (e,\rho)\in S_i}$ it holds
-		\[
-		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k \bigwedge_{(e,\rho)\in S_i}
-		 X_{n,i}=a^{(e,\rho)}_i  \big)=
-		\prod_{i=1}^{k}e^{-\lambda_i}\frac{\lambda_{(e,\rho)}^{a^{(e,\rho)}_i}}{{a^{(e,\rho)}_i}!},
-		\]
-		where for each $i\in [k]$,
-		\[
-		\lambda_{(e,\rho)}:= \frac{1}{|Aut(e,\rho)|} 
-		\prod_{v\in V(e), \rho(v)\neq \emptyset}
-		\mathrm{Pr}\big[\chi^i=\rho^i(v)\big].
-		\]
-	\end{theorem}
-\end{theorem}
+%\subsection{Counting colored sub-hypergraphs}
+%
+%
+%\begin{definition} 
+%	Given a set $\Sigma$, a $\Sigma$-hypergraph is a pair
+%	$(G,\chi)$ consisting of an hypergraph $G$ and a map 
+%	$\chi: V(G) \rightarrow \Sigma$.  
+%	Given two $\Sigma$-hypergraphs $(H,\rho)$ and $(G,\chi)$,
+%	an isomorphism between them is an hypergraph isomorphism 
+%	$f:V(H)\rightarrow V(G)$ satisfying $\rho(v)=\chi(f(v))$
+%	for any $v\in V(H)$. 
+%	An automorphism of a $\Sigma$-hypergraph $(G,\chi)$ is an
+%	isomorphism from $(G,\chi)$ to itself. As with the case of
+%	hypergraphs we write $Aut(G,\chi)$ to denote the group of 
+%	automorphisms of $(G,\chi)$.
+%	\par
+%	Let $(H,\rho), (G,\chi)$ be two $\Sigma$-hypergraphs. 
+%	Then a copy of $H$ in $G$ is
+%	a sub-hypergraph $H^\prime\subset G$ such that 
+%	$(H,\rho)$ is isomorphic to 
+%	$(H^\prime,\chi|_{_{H^\prime}})$.\par
+%	Given a $\Sigma$-hypergraph $(G,\chi)$ and a set $V$ we
+%	define the set $Copies(S,(G, \chi))$ as the one that contains all 
+%	possible $\Sigma$-hypergraphs $(H,\rho)$ isomorphic to $(G,\chi)$ 
+%	such that $V(H)\subset S$.	
+%\end{definition}
+%
+%\begin{definition}
+%	Given a set $\Sigma$, a random $\Sigma$-coloring of $G_n$ is 
+%	a random function $\chi_n: [n]\rightarrow \Sigma$. We say that	
+%	$\chi_n$ is symmetric if for any $s\in \Sigma$ the probability
+%	$\mathrm{Pr}\big( \chi_n(v)=s \big)$ is the same for any vertex
+%	$v\in [n]$. Notation $\mathrm{Pr}\big[\chi_n=s\big]$. \par
+%	For each $n\in \N$ let $\chi_n$ be a random $\Sigma$-coloring of $G_n$.
+%	We say that the succession $(\chi_n)_{n\in \N}$ is regular if
+%	the $\chi_n$'s are symmetric and for any $s\in \Sigma$ the limit
+%	$\Ln \mathrm{Pr}\big[ \chi_n = s \big]$ exists. 
+%\end{definition}
+%
+%
+%Remark: A random coloring $\chi$ of $G_n$ does not have to be independent from
+%$G_n$. In fact, in the cases we are going to consider $\chi$ will be determined
+%by $G_n$. 
+%
+%\begin{definition}
+%	Let $\Sigma_1,\dots,\Sigma_k$ be a sets. For each $i\in [k]$
+%	let $(\chi_{n,i})_{n \in \N}$ be a random regular sequence of
+%	$\Sigma_i$-colorings.
+%	Let $\mathcal{F}$ be a family of hypergraphs.
+%	We say that the successions $(\chi_{n,1})_{n \in \N},\dots,
+%	(\chi_{n,k})_{n \in \N}$ are $\mathcal{F}$-independent if
+%	for any given
+%	\begin{itemize}
+%		\item fixed finite number of copies of hypergraphs from 
+%		$\mathcal{F}$ in $\N$,
+%		\[
+%		S \subset \bigcup_{H\in \mathcal{F}} Copies(H,\N).
+%		\]		
+%		\item fixed disjoint sets of vertices 
+%		$V_1, \dots, V_k \subset \bigcup_{H\in S} V(H).$
+%		\item for each $i\in [k]$ and each $v\in V_i$, 
+%		a fixed label $s(v)\in \Sigma_i$
+%	\end{itemize}
+%	it is satisfied
+%	\[
+%	\Ln \mathrm{Pr}\big(
+%	\bigwedge_{i=1}^k \bigwedge_{v\in V_i} \chi_{n,i}(v)=s(v)
+%	\, \big| \, \bigwedge_{H\in S} H\subset G_n \,
+%	\big) = \prod_{i=1}^k \prod_{v\in V_i} \mathrm{Pr}\big[\chi_i=s(v)
+%	\big]		
+%	\]  
+%\end{definition}
+%
+%\begin{definition}
+%	Let $H_1,\dots, H_k$ be hypergraphs. Let $n,b_1,\dots,b_k\in \N$
+%	A $b_1,\dots,b_k$-configuration of $H_1,\dots, H_k$ over $[n]$
+%	is an ordered tuple $(O_1,\dots,O_k)$ where for each $i\in [k]$
+%	$O_i$ is an ordered $b_i$-tuple of different $H_i$-hypergraphs 
+%	over $[n]$. In other words, each $O_i$ is an element of
+%	$\big( Copies(H,[n])\big)_{b_i}$, and the set of 
+%	$b_1,\dots,b_k$-configurations of $H_1,\dots, H_k$ over $[n]$
+%	is precisely $\prod_{i=1}^{k}\big( Copies(H,[n])\big)_{b_i}$.
+%\end{definition}
+%
+%\begin{definition}
+% 	The underlying set of a configuration $\omega
+% 	=  (O_1, \dots, O_k)$ is the defined as
+% 	$S_{\omega}:=\{ H\in O_i \, | \, i\in [k]\}$.
+% 	A configuration $\omega$ is called disjoint
+%	if all the hypergraphs belonging to its underlying set
+%	$S_\omega$ have disjoint sets of vertices. 
+%\end{definition}
+%
+%\begin{theorem}
+%	Let $k\in \N$. For each $i\in [k]$ 
+%	\begin{itemize}
+%		\item Let $\Sigma_i$ be a set, let $H_i$ be a unicycle and 
+%		let $\rho^i$ be a $\Sigma_i$-coloring of $H_i$.
+%		\item Let $(\chi^i_n)_{n\in\N}$ be a succession of
+%		random $\Sigma_i$-colorings of $(G_n)_{n\in \N}$
+%		\item Let $X_{i,n}$ be the random variable that counts
+%		the number of copies of $(H_i, \rho^i)$ in
+%		$(G_n,\chi^i_n)$.				
+%	\end{itemize}
+%	Let $\mathcal{F}=\{H_1,\dots, H_n\}$. Suppose that the
+%	successions $(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
+%	are $\mathcal{F}$-independent. Then, for each $a_1,\dots,a_k\in \N$
+%	\[
+%	\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k X_{n,i}=a_i  \big)=
+%	\prod_{i=1}^{k}e^{-\lambda_i}\frac{\lambda_i^{a_i}}{a_i!},
+%	\]
+%	where for each $i\in [k]$,
+%	\[
+%	\lambda_i:= \frac{\prod_{j\in \sigma} \beta_j^{e_j(H_i)}}{|Aut(H_i,\rho^i)|} 
+%	\prod_{v\in V(H_i)} \mathrm{Pr}\big[\chi^i=\rho^i(v)\big].
+%	\]
+%\end{theorem}
+%\begin{proof}
+%	Because of \cref{thm:BrunSieve} we only need to show that for any 
+%	fixed $b_1,\dots, b_k\in \N$ it is satisfied
+%	\[
+%	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
+%	\prod_{i=1}^{k} \lambda_i^{b_i}.		
+%	\]
+%	For each $n\in \N$ let $\Omega_n$ be the set
+%	of $b_1, \dots, b_k$-configurations of $(H_1,\rho^1)
+%	,\dots, (H_k, \rho^k)$ over $[n]$. Then
+%	\[
+%	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
+%	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
+%	\mathrm{Pr}
+%	\big(
+%	(O_1,\dots, O_k) \subset G_n
+%	\big).	
+%	\]
+%	Let $\Omega^{\times}_n\subset \Omega_n$ be the set of 
+%	disjoint configurations in $\Omega_n$. Because of REF,
+%	\[
+%	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
+%	\mathrm{Pr}
+%	\big(
+%	(O_1,\dots, O_k) \subset G_n
+%	\big)=
+%	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
+%	\mathrm{Pr}\big(
+%	(O_1,\dots, O_k) \subset G_n
+%	\big).
+%	\]
+%	Because of the symmetry of the random hypergraph $G_n$ and
+%	the colorings $\chi^1_n, \dots, \chi^k_n$ the probability
+%	$\mathrm{Pr}\big(
+%	(O_1,\dots, O_k) \subset G_n
+%	\big)$ is the same for all $(U_1,\dots, U_k)\in 
+%	\Omega^\times_n$. Thus, if we fix
+%	$(O_1, \dots, O_k)$ a 
+%	disjoint $b_1,\dots,b_k$-configuration of
+%	 $(H_1,\rho^1)
+%	,\dots, (H_k, \rho^k)$ over $\N$, 
+%	\[
+%	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
+%	\mathrm{Pr}\big(
+%	(O_1,\dots, O_k) \subset G_n
+%	\big) =
+%	\Ln |\Omega^{\times}_n|\cdot \mathrm{Pr}\big(
+%	(U_1,\dots, U_k) \subset G_n
+%	\big).
+%	\]
+%	Let $S$ be the underlying set of the configuration $(U_1,\dots,U_k)$.
+%	Let $l= \sum_{H\in S} v(S)$. Then it is satisfied 
+%	\[
+%	|\Omega^{\times}_n|= \frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}.
+%	\]
+%	Using the definition of $(U_1,\dots, U_k) \subset G_n$ and
+%	substituting $|\Omega^{\times}_n|$ we get
+%	\[
+%	\Ln |\Omega^{\times}_n|\cdot \mathrm{Pr}\big(
+%	(U_1,\dots, U_k) \subset G_n
+%	\big) = \Ln
+%	\frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot
+%	\PR{\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
+%	(H,\rho)\subset (G_n, \chi_n^i)}.
+%	\]
+%	But the event $(H,\rho)\subset (G_n, \chi_n^i)$ is equivalent to $H\subset G_n$ and
+%	$\chi_n^i(v)=\rho(v)$ for all $v\in V(H)$. Thus the LHS of last equation equals
+%	\[
+%	\Ln
+%	\frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot
+%	\Pr\Big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
+%	\big(H\subset G_n \bigwedge_{v\in V(H)} \chi_n^i(v)=\rho(v) \big) \Big).
+%	\]
+%	For each $n\in \N$ let $A_n$ the event
+%	\[
+%	A_n:=\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
+%	H\subset G_n.
+%	\]	
+%	Then,
+%	\begin{align*}
+%	&\Pr\Big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
+%	\big(H\subset G_n \bigwedge_{v\in V(H)} \chi_n^i(v)=\rho(v) \big) \Big)=\\
+%	&\Pr\big(A_n\big)\cdot \Pr\big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
+%	\bigwedge_{v\in V(H)} \chi^i_n(v)=\rho(v) \, \big| \, A \big).
+%	\end{align*}
+%	It holds that
+%	\[
+%	\PR{A_n}=\frac{1}{n^l} \prod_{i=1}^{k}\prod_{R\in \sigma} \beta_R^{e_R(H_i)\cdot b_i},
+%	\]
+%	and in consequence 
+%	\[
+%	\Ln \frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot \PR{A_n}
+%	= \frac{\prod_{i=1}^{k}\prod_{R\in \sigma} \beta_R^{e_R(H_i)\cdot b_i}}
+%	{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}.
+%	\]
+%	Finally, using the hypothesis that 
+%	$(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
+%	are $\mathcal{F}$-independent we obtain
+%	\[
+%	\Ln \Pr\big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
+%	\bigwedge_{v\in V(H)} \chi^i_n(v)=\rho(v) \, \big| \, A \big)
+%	= \prod_{i=1}^{k} \prod_{v\in V(H_i)} \Pr\big[ \chi^i=\rho^i(v)\big]^{b_i}.
+%	\]
+%	The result follows from joining equations. 
+%\end{proof}
+%
+%\begin{definition}
+%	Let $\Sigma$ be a set containing the empty label $\emptyset$.
+%	Let $V\subset [n]$. We say that a random $\Sigma$-coloring $\chi$
+%	of $G_n$ is $V$-symmetric if $\chi(v)=\emptyset$ if and only if $v\in V$ and
+%	for any $s\in \Sigma$ the probability $\Pr(\chi(v)=s)$ is the same for all 
+%	$v\in [n]\setminus V$. \par
+%	Let $V\subset \N$ be a finite set of vertices and let $(\chi^n)_{n\in \N}$
+%	be a succession such that each $\chi^n$ is a random coloring of $G_n$. We
+%	call the succession $(\chi^n)_{n\in \N}$ $V$-regular if each $\chi^n$ is
+%	$V$-symmetric and for all $s\in \Sigma$ and $v\in \N \setminus \N$ the limit 
+%	$\Ln \PR{\chi^n(v)=s}$ exists. 
+%\end{definition}
+%
+%\begin{definition}
+%	Let $\Sigma$ be a set containing the empty label $\emptyset$. A rooted $\Sigma$-edge
+%	is a $\Sigma$-hypergraph $(e,\chi)$ where $e$ is an edge 
+%	(i.e., an hypergraph consisting of only one edge), and there is a unique vertex
+%	$v\in V(e)$ such that $\chi(v)=\emptyset$.
+%	Given a rooted $\Sigma$-edge $(e,\chi)$, a set of vertices $V$ and a vertex $v\in \N$
+%	we define the set $Copies((e,\chi),(V,v))$ as the set of copies 
+%	$(e^\prime, \chi^\prime) \in  Copies((e,\chi),V)$ such that $v$ is
+%	the root of $(e^\prime,\chi^\prime)$.
+%\end{definition}
+%
+%\begin{definition} 
+%	Let $V\subset \N$ be a finite set of vertices. 
+%	Let $\Sigma_1,\dots, \Sigma_k$ be sets containing the empty label 
+%	$\emptyset$. For each $i\in [k]$ and each $n\in \N$
+%	let $\chi_i^n$ be a random $\Sigma_i$-coloring
+%	of $G_n$ satisfying that the succession $(\chi_i^n)_{n\in \N}$ is
+%	$V$-regular. We say that the sequences $(\chi_1^n)_{n\in \N},
+%	\dots, (\chi_k^n)_{n\in \N}$ are asymptotically independent
+%	with respect to edges intersecting $V$ if for any given
+%	\begin{itemize}
+%		\item fixed finite set of edges $S\subset E(\N)$ such that any edge $e\in S$ 
+%		contains some vertex in $V$,
+%		\item fixed disjoint sets of vertices $V_1,\dots, V_k \subset \bigcup_{e\in S}e$ 
+%		satisfying $V\cup V_i=\emptyset$ for all $i\in [k]$, and
+%		\item for each $i\in [k]$ and $v\in V_i$ a fixed label $s(v)\in \Sigma_i$
+%		different from the empty label,
+%	\end{itemize}
+%	it is satisfied 
+%	\[
+%	\Ln \mathrm{Pr}\big(
+%	\bigwedge_{i=1}^k \bigwedge_{v\in V_i} \chi_{n,i}(v)=s(v)
+%	\, \big| \, \bigwedge_{e\in S} e\subset G_n \,
+%	\big) = \prod_{i=1}^k \prod_{v\in V_i} \mathrm{Pr}\big[\chi_i=s(v)
+%	\big]		
+%	\]
+%\end{definition}
+%
+%
+%\begin{theorem}
+%	\begin{theorem}
+%		Let $k\in \N$.	For each $i\in [k]$ 
+%		\begin{itemize}
+%			\item Let $v_i\in \N$ be a vertex. Define $V:=\{v_1,\dots,v_k\}$.
+%			\item Let $\Sigma_i$ be a set containing the empty label, and let $S_i$ be a set
+%			of non-isomorphic rooted $\Sigma_i$-edges. 
+%			\item For each $n\in \N$ let $\chi^i_n$ be random $\Sigma_i$-coloring
+%			$G_n$ satisfying that the succession $(\chi^i_n)_{n\in \N}$ is $V$-regular. 
+%			\item For each $(e,\rho)\in S_i$, let $X^{(e,\rho)}_{n,i}$ be the random 
+%			variable that counts the number of copies in $Copies((e,\rho),([n],v_i))$
+%			that appear in $(G_n,\chi^i_n)$.				
+%		\end{itemize}
+%		Suppose that the
+%		successions $(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
+%		are independent with respect to edges intersecting $V$.
+%		Then, for any fixed natural numbers 
+%		$(a^{(e,\rho)}_{i})_{i\in [k], (e,\rho)\in S_i}$ it holds
+%		\[
+%		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k \bigwedge_{(e,\rho)\in S_i}
+%		 X_{n,i}=a^{(e,\rho)}_i  \big)=
+%		\prod_{i=1}^{k}e^{-\lambda_i}\frac{\lambda_{(e,\rho)}^{a^{(e,\rho)}_i}}{{a^{(e,\rho)}_i}!},
+%		\]
+%		where for each $i\in [k]$,
+%		\[
+%		\lambda_{(e,\rho)}:= \frac{1}{|Aut(e,\rho)|} 
+%		\prod_{v\in V(e), \rho(v)\neq \emptyset}
+%		\mathrm{Pr}\big[\chi^i=\rho^i(v)\big].
+%		\]
+%	\end{theorem}
+%\end{theorem}
+%
 
@@
 We define $\Lambda$ and $M$ as the minimal families
-of expressions with arguments $\overbar{\beta}$ that satisfy
+of expressions with arguments $\overline{\beta}$ that satisfy
  the conditions: \textbf{(1)} $1\in \Lambda$, \textbf{(2)} 
@@
 as an expression with parameters
-$\overbar{\beta}$, belongs to $\Lambda$ for any choice of 
+$\overline{\beta}$, belongs to $\Lambda$ for any choice of 
 $r$ and $\mathcal{T}$. \par
@@
 	that contains $Center(G)$ and the vertices $\overline{v}$. In general, if 
-	$G$ is an arbitrary hypergraph with connected components $G_1, \dots, G_k$,
+	$G$ is an arbitrary hypergraph with connected components $G^1, \dots, G_k$,
 	and $\overline{v}$ are vertices $V(G)$, then we call 
@@
 		\item[(2)] Let $\overline{u}\in (\N)_*$ be a list of different fixed 
-		vertices, and let $\phi[\overbar{x}]\in FO[\sigma]$ be a consistent
+		vertices, and let $\phi[\overline{x}]\in FO[\sigma]$ be a consistent
 		edge sentence such that 
-		$len(\overbar{x})=len(\overbar{u})$.
+		$len(\overline{x})=len(\overline{u})$.
 		Let $\overline{v}\in (\N)_*$ be vertices contained
@@
 		\Ln \mathrm{Pr}\big( \bigwedge_{v\in \overline{v}} 
-		Tr\big(G_n, \overbar{u},v;r\big)\in \mathcal{T}_v 
-		\, | \, \sigma(\overbar{w})
+		Tr\big(G_n, \overline{u},v;r\big)\in \mathcal{T}_v 
+		\, | \, \sigma(\overline{w})
 		\big)= \prod_{v\in \overline{v}} \mathrm{Pr}[r,\mathcal{T}_v]. \]	 	
@@
 		\mathcal{T}_k$ are the unique $k$-equivalence class of trees with
-		radius zero. Then, given $\sigma, \overbar{u}, v_1,\dots, v_k$ as
+		radius zero. Then, given $\sigma, \overline{u}, v_1,\dots, v_k$ as
 		in the statement,
 		\[\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^l
-		Tr\big(G_n, \overbar{u},v_i;0\big)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
+		Tr\big(G_n, \overline{u},v_i;0\big)\in \mathcal{T}_i \, | \, \sigma(\overline{w})
 		\big)= \prod_{i=1}^l \mathrm{Pr}[0,\mathcal{T}_i]=1. \]	 	
@@
 		\]
-		Fix $\overbar{u}\in (\N)_*$ a list that contains exactly the vertices
+		Fix $\overline{u}\in (\N)_*$ a list that contains exactly the vertices
 		in $e$. Then it holds that
@@
 		\] 
-		Let $\overbar{w}\in (\N)_*$ be a list containing exactly
+		Let $\overline{w}\in (\N)_*$ be a list containing exactly
 		the vertices $u\in V(e)$ for all $e\in 
@@
 
-\begin{theorem}
-	Let $\mathcal{O}$ be a $k$-agreeability class
+\begin{theorem}\label{thm:agreeabilityprobabilities}
+	Let $\mathcal{O}$ be a simple $k$-agreeability class
 	of hypergraphs. Then 
@@
 	\]
-	Let $\overbar{v}\in (\N)_*$ be 
+	Let $\overline{v}\in (\N)_*$ be 
 	a list that contains exactly the vertices in $G\big(
@@
 
+\begin{theorem}
+	Let $\phi\in FO[\sigma]$. Then the function 
+	$F_\phi: [O,\infty)^{|\sigma|}\rightarrow [0,1]$
+	given by
+	\[
+	\overline{\beta}:=(\beta_R)_{R\in \sigma} \mapsto
+	\Ln \Pr \left(
+	G_n(\overline{\beta}) \models \phi
+	\right)
+	\]
+	is well defined and it is given by a finite sum of expressions
+	in $\Theta$.
+\end{theorem}
+\begin{proof}
+	Let $k$ be the quantifier rank of $\phi$ and
+	let $r=3^k$. Using \cref{thm:simple} we obtain
+	\[
+	\Ln \Pr \left(
+	G_n(\overline{\beta}) \models \phi
+	\right)=
+	\Ln \Pr \left(
+	G_n(\overline{\beta}) \models \phi
+	\, \Big|
+	\, G_n(\overline{\beta})
+	\text{ is $r$-simple}
+	\right).
+	\]
+	Let $S$ be the set of simple $k$-agreeability classes. 
+	Then the LHS of last equation equals
+	\[
+	\Ln
+	\sum_{\mathcal{O}\in S} \Pr\left(
+	G_n(\overline{\beta})\in \mathcal{O}
+	\right) \cdot 
+	\Pr\left(
+	G_n(\overline{\beta})\models \phi \,
+	\Big| \,
+	G_n(\overline{\beta})\in \mathcal{O}
+	\right).
+	\]
+	Notice that, because the set $S$ is finite, 
+	this is the limit of a finite sum. Also, 
+	using REF, we obtain that for any $\mathcal{O}\in S$
+	it holds
+	\[
+	\Ln \Pr\left(
+	G_n(\overline{\beta})\models \phi \,
+	\Big| \,
+	G_n(\overline{\beta})\in \mathcal{O}
+	\right) = 0 \textrm{ or } 1.
+	\]
+	Let $S^\prime\subset S$ be the set of classes 
+	$\mathcal{O}$ for which last limit equals $1$. Then
+	\[
+	\Ln \Pr \left(
+	G_n(\overline{\beta}) \models \phi
+	\right)=
+	\sum_{\mathcal{O}\in S^\prime}
+	\Ln \Pr\left(
+	G_n(\overline{\beta})\in \mathcal{O}
+	\right).		
+	\]
+	Because of \cref{thm:agreeabilityprobabilities} we know that
+	each of the limits inside last sum exists and is given by
+	an expression that belongs to $\Theta$. As a consequence the
+	theorem follows. 	
+\end{proof}
+
 \section{Application to random SAT}
@@
 %inside of $G_n$ a set of distinguished vertices
-%$\overbar{v}\in \N*$ cho
-
-%
-%expressions analytic in $\overbar{\beta}$
+%$\overline{v}\in \N*$ cho
+
+%
+%expressions analytic in $\overline{\beta}$
 %
@@
 
-%Let $\overbar{v[s]}$, resp. $\overbar{u[s]}$,
+%Let $\overline{v[s]}$, resp. $\overline{u[s]}$,
 %be the list obtained by joining the marked lists
@@
 %this strategy, at the end of the $s$-th round
-% $\overbar{v[s]}$ and $\overbar{u[s]}$ have $(k-s)$-similar
+% $\overline{v[s]}$ and $\overline{u[s]}$ have $(k-s)$-similar
 % $r_{k-s}$-neighborhoods. For $s=0$ this is trivially
 %the case, as at the beginning of the game no lists have
-%been marked and both $\overbar{v[s]},\overbar{u[s]}$ are empty.
+%been marked and both $\overline{v[s]},\overline{u[s]}$ are empty.
 %Suppose

### 2020-03-16 Article.tex
Cuarentena1

@@
 
+\subsection{Colored Hypergraphs and Copies.}
+
+\begin{definition}
+	Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
+	is a pair $(G, \chi)$ where $G$ is an hypergraph
+	and $\chi: V(G)\rightarrow \Sigma$ is a map 
+	called \textbf{$\Sigma$-coloring} of $G$. \par
+	Given two $\Sigma$-hypergraphs $(G^1,\chi_1)$
+	and $(G^2,\chi_2)$, and \textbf{isomorphism} between them is
+	a bijection $f:V(G^1)\rightarrow V(G^2)$ satisfying
+	that $f$ is an hypergraph isomorphism between $G^1$ and
+	$G^2$ as well as
+	$\chi_2(f(v))=\chi_1(v)$ for all $v\in V(G^1)$.\par	 
+	Given a $\Sigma$-hypergraph $(G,\chi)$, an \textbf{automorphism}
+	of $(G,\chi)$ is an isomorphism from it into itself. We will denote
+	by $Aut(G,\chi)$ the group of such automorphisms. 
+\end{definition}
+
 \subsection{The random model}
@@
 $d\ehr_k\big(N(\overline{v};r),
-\overline{v};\, N(\overline{u};r),\overline{u}\big)$.\par
+\overline{v};\, N(\overline{u};r),\overline{u}\big)$.
 Given sets of vertices $X\subseteq V_1$ and $Y\subseteq V_2$
-we say that $X$ and $Y$ have $k$-\textbf{similar}
+we say that $X$ and $Y$ have $k$-similar
 $r$-neighborhoods, written as
@@
 $(G^1,\overline{v})\simeq_{k,r}(G^2,\overline{u})$. 
-\par
+Given sets of vertices $X\in V_1$, $Y\in V_2$ and 
+tuples of the same length $\overline{v}\in V_1^*$ and
+$\overline{u}\in V_2^*$ we will say that $(X,\overline{v})$ 
+and $(Y,\overline{u})$ have $k$-similar $r$-neighborhoods,
+written as $\big(G_1, (X,\overline{v})  \big)
+\simeq_{k,r} \big(G_2, (Y,\overline{u})  \big)$, if
+the elements of $X$ and $Y$ can be ordered in lists
+$\overline{w}$, $\overline{z}$ such that
+$(G_1,\overline{w}^\smallfrown \overline{v})
+\simeq_{k,r} (G_2,\overline{z}^\smallfrown \overline{u})$. \par
 Fix $r\in \N$. Suppose that $X\subseteq V_1$ and 
@@
 		\item[(1)] $(G^1,X)\cong_{k,r} (G^2,Y)$.
-		\item[(2)] Let $r^\prime\leq r$. Let $v\in V_1$ be
+		\item[(2)]
+		\begin{itemize}
+			\item Let $r^\prime\leq r$. Let $v\in V_1$ be
 			a vertex such that $d(X,v)> 2r^\prime + 1$. Let 
@@
 			$(G^1,v)\simeq_{k,r^\prime} (G^2,u)$.	
-		\item[(3)] Let $r^\prime\leq r$. Let $u\in V_2$ be
+			\item Let $r^\prime\leq r$. Let $u\in V_2$ be
 			a vertex such that $d(Y,u)> 2r^\prime + 1$. Let 
@@
 			$(G^1,v)\simeq_{k,r^\prime} (G^2,u)$
+		\end{itemize}
 	\end{enumerate}
@@
 \begin{proof}[Proof of \cref{ThmDuplicator}]
-	Define $r_0=0$ and $r_i=3r_{i-1}+1$ for $i>0$.
-	Let us denote by $w_i$ and $z_i$ the vertices played
-	in $G^1$ and $G^2$ respectively during the $i$-th
-	round of $\ehr_k(G^1,G^2)$. 
 	%Set 
@@
 	%round Duplicator will have won $\ehr_k(G^1,G^2)$.	
-	\par
-
 	Let $X_1,\dots,X_a$ and 
@@
 	as in the definition of $k$-agreeability.
+	Define $r_0=(3^k-1)/2$ and $r_i=(r_{i-1}-1)/3$ for each
+	$1\leq i \leq k$. 
+	Let us denote by $v^1_i$ and $v^2_i$ the vertices played
+	in $G^1$ and $G^2$ respectively during the $i$-th
+	round of $\ehr_k(G^1,G^2)$. 
 	We will show a winning strategy for Duplicator
-	in $d\ehr_{k}\big(G^1;\, G^2\big)$.	
-	Let $r_k=1$ and for each $i\in [k-1]$ 
-	let $r_i=3r_{i+1}+1$. In particular, 
-	$r_1=r=(3^k-1)/2$.
+	in $d\ehr_{k}\big(G^1;\, G^2\big)$. For each $0\leq i \leq k$,
+	Duplicator will	keep track of some marked sets 
+	of vertices $T\subset V_1$, $S\subset V_2$. 
+	For $\delta=1,2$ each marked set
+	$T\subset V_\delta$ will have associated a tuple
+	of vertices $\overline{v}(T)\in V_\delta^*$ consisting
+	of the vertices played in $G_2$ so far, ordered according
+	to the rounds they where played, that were 
+	"appropriately close" to $T$ when chosen.
+	The game will start with no sets of vertices marked and 
+	at the end of the $i$-th
+	round Duplicator will perform one of the two
+	following operations:
+	\begin{itemize}
+	\item Mark two sets $S\subset V_1$ and $T\subset V_2$ and
+	define $\overline{v}(S)=v^1_i$ and $\overline{v}(T)=v^2_i$.
+	\item Given two sets $S\subset V_1$, $T\subset V_2$ that were 
+	previously marked during the same round, append $v^1_i$
+	and $v^2_i$ to $\overline{v}(S)$ and $\overline{v}(T)$ 
+	respectively. 
+	\end{itemize}
+	In particular this means that at the 
+	end of the $i$-th round the marked sets $S\subset V_1$
+	, $T\subset V_2$ and their respective lists $\overline{v}(S)$,
+	$\overline{v}(T)$ satisfy
+	\begin{itemize}
+		\item[(i)] For $\delta=1,2$, each vertex played
+		so far $v^\delta_j\in V_\delta$ belongs to 
+		$\overline{v}(S)$ for a	 unique marked set 
+		$S\subset V_\delta$.
+		\item[(ii)] Let $S\subset V_1$ and $T\subset V_2$ be sets
+		marked during the same round. Then any previously played
+		vertex $v^1_j$ occupies a position in $\overline{v}(S)$
+		if and only if $v^2_j$ occupies the same position 
+		in $\overline{v}(T)$.
+	\end{itemize}
+	The following conditions will also be satisfied at the 
+	end of the $i$-th round
+	\begin{itemize}
+		\item[(iii)] 
+			\begin{itemize}
+			\item  Let $S\subset V_1$ be a marked set. Then 
+			for any different marked $S^\prime \subset V_1$ 
+			of any different $S^\prime$ among $X_1,\dots,X_a$
+			it holds $d(S,S^\prime)>2r_i + 1$. 
+			\item Let $T\subset V_2$ be a marked set. Then
+			for any different marked $T^\prime \subset V_2$
+			or any different $T^\prime$ among
+			$Y_1,\dots, Y_b$  it holds $d(T,T^\prime)>2r_i +1$.
+			\end{itemize}
+		\item[(iv)] Let $S\subset V_1, T\subset V_2$ be sets
+		marked during the same round. Then
+		\[
+		\big(G^1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
+		\big(G^2, (T,\overline{v}(T))\big).	\]
+
+	\end{itemize}
+	In particular, if conditions (i) to (iv) are satisfied this means
+	that if $\overline{v}^1=(v^1_1,\dots,v^1_i)$ and
+	$\overline{v}^2=(v^2_1,\dots, v^2_i)$ are the vertices played so far
+	then Duplicator wins
+	\[
+	d\ehr_{k-i}\big(\,
+	N(\overline{v}^1;\, r_i), \overline{v}^1; \quad
+	N(\overline{v}^2;\, r_i),\overline{v}^2 \,
+	\big),	
+	\]
+	And at the end of the $k$-th round Duplicator will have won
+	$\ehr(G^1;\, G^2)$. \par
+	The game $d\ehr_k(G_1; \, G_2)$ proceeds as follows. Suppose 
+	that during the $i$-th round Spoiler chooses $v^1_i\in V_1$ 
+	(the case where they play in $V_2$ is symmetric). There are 
+	three possible cases:
+	\begin{itemize}
+		\item For some unique previously marked set $S\subset V_1$ 
+		it holds that $d(S\cup \overline{v},\quad v^1_i)\leq 2r_i +1$. 
+		In this case let $T\subset V_2$ be the set in $G_2$ marked in the 
+		same round as $T$. By hypothesis 
+		\[ \big(G^1,(S,\overline{v}(S))\big)
+		\simeq_{k-i+1,3r_i+1}
+		\big(G^2,(T,\overline{v}(T))\big). 		
+		\]
+		Then, by definition,
+		for some orderings $\overline{w}$, $\overline{z}$
+		of the vertices in $S$ and $T$ respectively it holds that
+		Duplicator wins
+		\[
+		d\ehr_{k-i+1}\big(\,
+		N(\overline{w}^\smallfrown \overline{v}(S); \, 3r_i	+ 1)
+		, \overline{w}^\smallfrown \overline{v}(S); \quad
+		N(\overline{z}^\smallfrown \overline{v}(T); \, 3r_i	+ 1)
+		, \overline{z}^\smallfrown \overline{v}(T)\,	
+		\big).		
+		\]
+		Thus Duplicator can choose $v^2_i\in V_2$ according to the 
+		winning strategy in that game. After this Duplicator sets 
+		$\overline{v}(S):= \overline{v}(S)^\smallfrown v^1_i$, and
+		$\overline{v}(T):= \overline{v}(T)^\smallfrown v^2_i$. Notice
+		that because of \cref{lemm:Duplicator} now
+		\[
+		\big(G^1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
+		\big(G^2, (T,\overline{v}(T))\big).
+		\]
+		\item For all marked sets $S\subset V_1$ it holds
+		$d(S\cup \overline{v}(S), \quad v^1_i)>2r_i +1$, but there is
+		a unique $S$ among $X_1,\dots, X_a$ such that
+		$d(S,v^1_i)\leq 2r_i+1$. In this case from condition (1)
+		of the statement follows that there is some non-marked
+		set $T$ among $Y_1,\dots, Y_b$ such that
+		\[
+		(G^1,S)\simeq_{k-i+1,3r_i+1} (G^2,T).\] 
+		Thus, by definition, for some orderings $\overline{w}$, 
+		$\overline{z}$ of the vertices in $S$ and $T$ respectively
+		it holds that Duplicator wins
+		\[
+		d\ehr_{k-i+1}\big( \,
+		N(\overline{w};3r_i+1), \overline{w};
+		\quad
+		N(\overline{z};3r_i+1), \overline{z}
+		\, \big).		
+		\]
+		Then Duplicator can choose $v^2_i\in V_2$ according 
+		to a winning strategy for this game. After this Duplicator
+		marks both $S$ and $T$ and sets 
+		$\overline{v}(S):=v^1_i$, and 
+		$\overline{v}(T):=v^2_i$. Notice
+		that because of \cref{lemm:Duplicator} now
+		\[
+		\big(G^1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
+		\big(G^2, (T,\overline{v}(T))\big).
+		\]
+		\item For all marked sets $S\subset V_1$ it holds
+		$d(S\cup \overline{v}(S), \quad v^1_i)>2r_i +1$, and
+		for all sets $S$ among $X_1,\dots, X_a$ it also holds
+		$d(S,v^1_i)> 2r_i+1$. In this case
+		from condition (2) of the statement follows that
+		Duplicator can choose
+		$v^2_i\in V_2$ such that
+		(A)
+		$d(T\cup \overline{v}(T),\quad v^2_i)>2r_i+1$ for all
+		marked sets $T\subset V_2$, (B)
+		$d(T, v^2_i)> 2r_i+1$ for all sets $T$ among
+		$Y_1,\dots, Y_b$, and (C) 
+		$(G^1,v^1_i)\simeq_{k-i,r_i} (G^2, v^2_i)$.
+		After this Duplicator marks both $S=\{
+		v^1_i\}$ and $T=\{v^2_i\}$ and sets
+		$\overline{v}(S):=v^1_i$, and
+		$\overline{v}(T):=v^2_i$. 		
+	\end{itemize}	 
+	The fact that conditions
+	(i) to (iv) still hold at the end of the round
+	follows from comparing $r_{i-1}$ and $r_{i}$ as well 
+	as applying \cref{obs1} and \cref{obs2}.
 
@@
 \end{proof}
-
-\todo[inline]{Quiz\'as reordenando esta demostraci\'on se puede acortar o se entiende mejor.}
 

### 2020-04-29 Articlebackup.tex
Corregir

--- 2020-03-16 Article.tex
@@
 \newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
-\newcommand{\morph}[1]{\simeq_#1}
+\newcommand{\morph}[1]{\sim_#1}
 \newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
@@
 we will write $f\sim g$ when $\Ln \frac{f(n)}{g(n)}=1$.\par
+
+\todo[inline]{Añadir referencias y trabajo relacionado con random SAT}
 
@@
 element of $\overline{a}$).
-\todo[inline]{Deber\'a al menos mencionar un par de trabajos que estudien random k-SAT y propiedades a.a.s suficientes para no-satisfacibilidad}
 
@@
 	\item 
-	Groups $\overline{\Phi}=\{ \Phi_R \}_{R\in \sigma}$
+	Groups $\{ \Phi_R \}_{R\in \sigma}$
 	such that each $\Phi_R$ is consists of 
@@
 
-\subsection{Colored Hypergraphs and Copies.}
+\subsection{Copies of Hypergraphs}
+
+Given two hypergraphs $H_1, H_2$ an \textbf{isomorphism} 
+$f$ between them is a bijection $f: V(H_1)\rightarrow V(H_2)$
+such that for any $R\in \sigma$, a tuple $\overline{v}\in V(H_1)^*$
+forms an edge $[\overline{v}]\in E_\sigma(H_1)$ if and only
+if $[f(\overline{v})]\in E_\sigma(H_2)$. We say that $H_1$ and
+$H_2$ are isomorphic, written as $H_1\simeq H_2$, if there exists
+some isomorphism between them.\par
+
+Let $H$ be an hypergraph. An \textbf{automorphism} of $H$
+is an isomorphism from $H$ to itself. We will denote by
+$Aut(H)$ the group of such automorphisms. \par
+
+Let $H^\simeq$ be an isomorphism class of hypergraphs. Let
+$H\in H^\simeq$ be a representative of the class. 
+Then we define $ex(H^\simeq)$ as $ex(H)$. Clearly this definition
+does not depend on the choice of $H$. The expressions
+$|Aut(H^\simeq)|$,
+$|V(H^\simeq)|$, $|E(H^\simeq)|$ or
+$|E_R(H^\simeq)|$ for $R\in \sigma$ are defined 
+in an analogous way.\par
+
+Let $H$ be an hypergraph and let $V$ be a set. We define the
+set $Copies(H,V)$ as the set of hypergraphs $H^\prime$ such that
+$V(H^\prime)\subset V$ and $H\simeq H^\prime$. Analogously, if
+$H^\simeq$ is an isomorphism class of hypergraphs we define
+$Copies(H^\simeq,V)$ as the set of hypergraphs $H^\prime$ 
+that satisfy
+$V(H^\prime)\subset V$ as well as $H^\prime \in H^\simeq$.   \par
+
+In our proofs it will be useful to consider colorings over 
+hypergraphs as a way to assign extra information to their 
+vertices.
 
@@
 	Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
-	is a pair $(G, \chi)$ where $G$ is an hypergraph
-	and $\chi: V(G)\rightarrow \Sigma$ is a map 
-	called \textbf{$\Sigma$-coloring} of $G$. \par
-	Given two $\Sigma$-hypergraphs $(G^1,\chi_1)$
-	and $(G^2,\chi_2)$, and \textbf{isomorphism} between them is
-	a bijection $f:V(G^1)\rightarrow V(G^2)$ satisfying
-	that $f$ is an hypergraph isomorphism between $G^1$ and
-	$G^2$ as well as
-	$\chi_2(f(v))=\chi_1(v)$ for all $v\in V(G^1)$.\par	 
-	Given a $\Sigma$-hypergraph $(G,\chi)$, an \textbf{automorphism}
-	of $(G,\chi)$ is an isomorphism from it into itself. We will denote
-	by $Aut(G,\chi)$ the group of such automorphisms. 
+	is a pair $(H, \chi)$ where $H$ is an hypergraph
+	and $\chi: V(H)\rightarrow \Sigma$ is a map 
+	called \textbf{$\Sigma$-coloring} of $H$.
 \end{definition}
+
+	Given two $\Sigma$-hypergraphs $(H_1,\chi_1)$
+	and $(H_2,\chi_2)$, an \textbf{isomorphism} between them is
+	a bijection $f:V(H_1)\rightarrow V(H_2)$ satisfying
+	that $f$ is an hypergraph isomorphism between $H_1$ and
+	$H_2$ as well as $\chi_2(f(v))=\chi_1(v)$ for all $v\in V(H_1)$.
+	We say that $(H_1,\chi_1)$ is isomorphic to $(H_2,\chi_2)$,
+	written as $(H_1, chi_1)\simeq (H_2,\chi_2)$, if there exists an
+	isomorphism between them.
+	\par	 
+	Let $(H,\chi)$ be a $\Sigma$-hypergraph, an 
+	\textbf{automorphism} of $(H,\chi)$ is an 
+	isomorphism from it into itself. We will denote
+	by $Aut(H,\chi)$ the group of such automorphisms. 
+	\par
+	As with the case of hypergraphs, if $H^\simeq$ is 
+	an isomorphism class of $\Sigma$-hypergraphs
+	then the expressions $|Aut(H^\simeq)|$ and
+	$|V(H^\simeq)|$ are defined via representatives. \par
+	Let $(H,\chi)$ be a $\Sigma$-hypergraph and let $V$ be a set.
+	We define the set $Copies\big(
+	(H,\chi),\, \, V\big)$ as the set of $\Sigma$-hypergraphs
+	$(H^\prime,\chi^\prime)$ satisfying $V(H^\prime)\subset V$ and
+	$(H,\chi)\simeq (H^\prime,\chi^\prime)$. Let $H^\simeq$ be 
+	an isomorphism class of $\Sigma$-hypergraphs. Then the set
+	$Copies(H^\simeq, V)$ is defined$\Sigma$-hypergraphs
+	$(H^\prime,\chi^\prime)$ such that 
+	$V(H^\prime)\subset V$ and
+	$(H^\prime,\chi^\prime)\in H^\simeq$. 
+	Let $v\in V$ and $s\in \Sigma$. We define the
+	set $Copies\big(H^\simeq, V;\,\, (v,s)\big)$ 
+	as the set of $\Sigma$-hypergraphs
+	$(H^\prime,\chi^\prime)\in Copies(H^\simeq, V)$
+	that satisfy $v\in V(H^\prime)$ as well as
+	$\chi^\prime(v)=s$.
 
@@
 We say that $X$ and
-$Y$ have $k$-\textbf{agreeable} $r$-neighborhoods,
+$Y$ have $k$-\textbf{analogous} $r$-neighborhoods,
 written as $(G^1,X)\cong_{k,r} (G^2,Y)$, 
@@
 	$X$ and $Y$ respectively
-	as in the definition of $k$-agreeability.
+	as in the definition of $\cong_{k,r}$.
 	Define $r_0=(3^k-1)/2$ and $r_i=(r_{i-1}-1)/3$ for each
@@
 
-\subsection{Types of trees}
-
-We define tree $T$ as a connected hypergraph such that
-$ex(T)=-1$. We define a vertex-rooted tree $(T,v)$ 
-as a tree $T$ with a 
-distinguished vertex $v\in V(T)$ called its root. We will
-usually omit the root when it is not relevant and 
-write just $T$ instead of $(T,v)$. We define the set
-of initial edges of a vertex-rooted tree $(T,v)$ as the
-set of edges in $T$ that contain $v$. \par
+\subsection{k-Equivalence relation}
+
+To prove \cref{thm:main} we are going to exploit the facts that
+(1) for any fixed $r\in N$, $r$-neighborhoods in $G_n$ a.a.s 
+are either trees of unicycles, and
+(2) we can identify $k$-equivalent trees
+and unicycles sufficiently often in a simple way.
+
+\subsubsection{k-Equivalent trees}
+
+\begin{definition}
+	We define a \textbf{tree} $T$ as a connected hypergraph such that
+	$ex(T)=-1$. A \textbf{rooted tree} $(T,v)$ is a tree $T$ with a 
+	distinguished vertex $v\in V(T)$ called its \textbf{root}.
+\end{definition}
+We will usually omit the root when it is not relevant and 
+write just $T$ instead of $(T,v)$. The
+\textbf{initial edges} of a rooted tree $(T,v)$ are 
+the edges in $T$ that contain $v$. \par
+
 %
@@
 Given a rooted tree $(T, v)$, and a vertex $u\in V(T)$, 
-we define $\tau_{(T,v)}(u)$ as the tree $T[X]$ induced on the
+we define $\mathrm{Tr}(T,v;\,\, u)$ as the tree $T[X]$ induced on the
 set $X:=\{ \, w\in V(T) \, | \, d(v,w)=d(v,u)+ d(u,w) \,  \}
 $, to which we assign $u$ as the root.
-That is, $\tau_{(T,v)}(u)$ is the tree consisting of those vertices
+That is, $\mathrm{Tr}(T,v;\,\, u)$ is the tree consisting of those vertices
 whose only path to $v$ contains $u$.
 \par
-We define the radius of a vertex-rooted, or edge-rooted,
-tree as the maximum distance between its marked
-vertex and any other one. \par
-
-Fix a natural number $k$. We will define 
-two equivalence relations, one between 
-rooted trees and another between pairs
-$(T,e)$ of rooted trees $T$ and initial edges
-$e\in E(T)$. We will name both relations
-$k$-equivalence relations and
-denote them by $\morph{k}$. 
-They are defined recursively as follows:
+We define the radius of a rooted tree
+as the maximum distance between its root
+and any other vertex. \par
+
+\begin{definition}
+
+Fix a natural number $k$. We will define the
+\textbf{$k$-equivalence} relation, written as 
+$\sim_k$,  over rooted trees
+inductively over their radii as follows:
 
@@
 	consist only of one vertex: their respective roots.
+
 	\item Suppose that the $k$-equivalence relation has been
 	defined for rooted trees with radius at most $r$. Let $\Sigma_r$
-	be the set consisting of the root symbol $\tau$ and
-	the $k$-equivalence classes of trees with radius lesser than $r$.
-	Given a rooted tree $(T,v)$ with whose radius is lesser than $r$
+	be the set consisting of the root symbol $\rho$ and
+	the $k$-equivalence classes of trees with radius at most $r$.
+	Given a rooted tree $(T,v)$ with whose radius is $r+1$
 	we define its canonical $\Sigma_r$-coloring as the map 
-	$\chi_{(T,v)}: V(T)\rightarrow \Sigma_r$ satisfying that
-	$\chi_{(T,v)}(u)$ is the $k$-equivalence class of $\mathrm{Tr}(u,T;v)$
-	for any $u\neq v$ and $\chi_{(T,v)}(v)=\tau$. \par
-	Let $T_1$ and $T_2$ be rooted trees with radius
-	at most $r+1$. We say that $(T_1,v_1)\simeq_k (T_2,v_2)$ 
-	if given any $\Sigma_r$-pattern $(e,\chi)$ the 
-	"quantity of initial edges $e_1\prime\in E(T_1)$ such that
-	$(e,\chi)\simeq (e_1,\chi_{(T_1,v_1)})$" and the
-	"quantity of initial edges $e_2\prime\in E(T_2)$ such that
-	$(e,\chi)\simeq (e_2,\chi_{(T_2,v_2)})$" are the same or
+	$\tau_{(T,v)}: V(T)\rightarrow \Sigma_r$ satisfying that
+	for any $u\neq v$ $\tau_{(T,v)}(u)$ is the $k$-equivalence class 
+	of $\mathrm{Tr}(T,u;\, \,v)$ and that $\tau_{(T,v)}(v)=\tau$. \par
+	Let $T_1$ and $T_2$ be rooted trees with radius $r+1$. 
+	We say that $(T_1,v_1)\sim_k (T_2,v_2)$ 
+	if for $\delta=1,2$, given any initial edge $e$ from $(T_\delta,v_\delta)$
+	the
+	``quantity of initial edges $e_1\in E(T_1)$ such that
+	\[
+	\big(e,\tau_{(T_\delta,v_\delta)}\big)
+	\simeq \big(e_1,\tau_{(T_1,v_1)}\big)" 
+	\] and the
+	``quantity of initial edges $e_2\in E(T_2)$ such that
+	\[
+	\big(e,\tau_{(T_\delta,v_\delta)}\big)
+	\simeq \big(e_2,\tau_{(T_2,v_2)}\big)"\] are equal or
 	are both greater than $k-1$.
@@
 
+\begin{definition}
+	Let $\Sigma_{(k,r-1)}$ be the set of $\sim_k$ classes
+	of rooted trees with radii at most $r-1$. Then
+	we call a $(k,r)$-\textbf{pattern} to an isomorphism class
+	of $(\Sigma_{(k,r-1)}\cup \{\rho \})$-hypergraphs 
+	$(e,\tau)$ consisting of only one edge that satisfy 
+	$\tau(v)=\rho$ for exactly one vertex $v\in V(e)$. We will
+	denote by $P(k,r)$ the set of $(k,r)$-patterns.
+\end{definition}
+
+The following is a way of characterizing $\sim_k$ classes
+of rooted trees with radii at most $r$ that will be useful later.
+
+\begin{obs}\label{obs:equivalenttrees}
+Let $\mathcal{T}$ be a $\sim_k$ class of rooted trees with
+radii at most $r$. Then there is a partition $E^1_\mathcal{T},
+E^2_\mathcal{T}$ of $P(k,r)$ and natural numbers $a_\epsilon<k$
+for each $\epsilon\in E^2_\mathcal{T}$ that only depend on 
+$\mathcal{T}$ such that any rooted tree $(T,v)$ belongs to
+$\mathcal{T}$ if and only if it holds that
+\begin{itemize}
+	\item[(1)] For any $\epsilon\in E^1_\mathcal{T}$ there are at least
+	$k$ initial edges $e\in E(T)$ such that
+	$(e,\tau_{(T,v)})\in \epsilon$.
+	\item[(2)] For any $\epsilon\in E^2_\mathcal{T}$ there are exactly
+	$a_\epsilon$ initial edges $e\in E(T)$ such that
+	$(e,\tau_{(T,v)})\in \epsilon$.	
+\end{itemize}
+\end{obs}
+
+\end{definition}
 We want prove the following
@@
 	Then, if they are $k$-equivalent Duplicator wins
-	$d\ehr_{k}(T_1,v_1,T_2,v_2)$.
+	$d\ehr_{k}(T_1,v_1;\, \, T_2,v_2)$.
 \end{theorem}
@@
 result. Let $(T,v)$ be a rooted tree and $e$ an 
-initial edge of $T$. We define $Tree_{(T_v)}(e)$ as
+initial edge of $T$. We define $\mathrm{Tr}(T,v;\, e)$ as
 the induced tree $T[X]$ on the set
-$X:=\{v\} \cup \{\, u\in V(T) \, | \, d(v,u) = |e| + d(e,v) \,\}$,
+$X:=\{v\} \cup \{\, u\in V(T) \, | \, d(v,u) = 1 + d(e,u) \,\}$,
 to which we assign $v$ as the root. In other words, 
-$Tree_{(T_v)}(e)$ is the tree formed of $v$ and all the vertices
+$\mathrm{Tr}\big(T,v;\, e\big)$ is the tree formed of 
+$v$ and all the vertices
 in $T$ whose only path to $v$ contain $e$. 
@@
 	holds for rooted trees with radii at most $r$.
-	Let $(T_1,v_1)$ and $(T_2,v_2)$ be rooted trees with radii
-	at most $r+1$. Let $e_1$ and $e_2$ be initial edges 
+	Let $(T_1,v_1)$ and $(T_2,v_2)$ be rooted trees with radius
+	$r+1$. Let $\tau_{(T_1,v_1)}$ and $\tau_{(T_2,v_2)}$
+	be colorings over $T_1$ and $T_2$ as in the
+	definition of $k$-equivalence. 
+	Let $e_1$ and $e_2$ be initial edges 
 	of $T_1$ and $T_2$ respectively satisfying 
-	$(T_1,e_1)\simeq_k (T_2,e_2)$. Name 
-	$T^\prime_1=Tree_{(T_1,v_1)}(e_1)$ and 
-	$T^\prime_2=Tree_{(T_2,v_2)}(e_2)$. Then
-	Duplicator wins $d\ehr{k}(T^\prime_1, v_1, T^\prime_2,v_2)$.
+	$(e_1,\tau_{(T_1,v_1)})\simeq (e_2,\tau_{(T_2,v_2)})$. Name 
+	$T^\prime_1:=\mathrm{Tr}(T_1,v_1; \,\,e_1)$ and 
+	$T^\prime_2:=\mathrm{Tr}(T_2,v_2;\,\,e_2)$. Then
+	Duplicator wins 
+	$d\ehr{k}(T^\prime_1, v_1; \, \, T^\prime_2,v_2)$.
 \end{lemma}
@@
 	We show a winning strategy for Duplicator.
+	At the beginning of the game fix 
+	$f:V(e_1)\rightarrow V(e_2)$ an isomorphism between 
+	$(e_1,\tau_{(T_1,v_1)})$
+	and $(e_2,\tau_{(T_2,v_2)})$.
 	Suppose that in the $i$-th round of the game Spoiler
-	plays on $T^\prime_1$. The other case is symmetric. Let
-	$f:e_1\rightarrow e_2$ be a bijection as in the definition
-	of $(T_1,e_1)\simeq_k (T_2,e_2)$. There are two possibilities:
+	plays on $T^\prime_1$. The other case is symmetric. 
+	There are two possibilities:
 	\begin{itemize}
-		\item If Spoiler plays a vertex $v$ on $e_1$ 
-		then Duplicator can play $f(v)$ on $e_2$. 
+		\item If Spoiler plays $v_1$ 
+		then Duplicator chooses $v_2$. 
 		\item Otherwise, Spoiler plays a vertex $v$ that belongs
-		to some $Tree_{(T^\prime_1,v_1)}(u)$ for a unique $u\in e_1$
+		to some $\mathrm{Tr}(T^\prime_1,v_1;\,\, u)$ for a unique $u\in V(e_1)$
 		different from the root $v_1$. 
-		By the definition of $(T_1,e_1)\simeq_k (T_2,e_2)$,
-		$Tree_{(T^\prime_1,v_1)}(u)\simeq_k 
-		Tree_{(T^\prime_2,v_2)}(f(u))$. As both these trees
-		have radii at most $r$, by assumption Duplicator has a winning 
-		strategy between them and they can follow it.		
+		Set $T^{\prime\prime}_1:=
+		\mathrm{Tr}\big(T^\prime_1,v_1;\,\, u\big)$
+		and
+		$T^{\prime\prime}_2:=\mathrm{Tr}\big(T^\prime_2,v_2;\,\, f(u)\big)$
+		Then, as $\tau_{(T_1,v_1)}\big(u\big)=\tau_{(T_2,v_2)}\big(f(u)\big)$,
+		we obtain
+		$\big(T^{\prime\prime}_1,u\big) \sim_k 
+		\big(T^{\prime \prime}_2,f(u)\big)$.
+		As both these trees have radii at most $r$, 
+		by assumption Duplicator has a winning 
+		strategy in \[
+		d\ehr_{k}\big(\,T^{\prime\prime}_1, u;
+		\quad T^{\prime \prime}_2, f(u)\,  \big)
+		\]
+		and they can follow it considering the previous plays in
+		$T^{\prime\prime}_1$ and $T^{\prime\prime}_2$.	
 	\end{itemize}
 \end{proof}
+\noindent\rule{2cm}{0.4pt}
 
@@
 \begin{proof}[Proof of \cref{thm:equivalenttrees}]~ \par
-	Notice that, as $T_1\morph{k} T_2$, both $T_1$ and
+	Notice that, as $(T_1,v_1)\morph{k} (T_2,v_2)$, both $T_1$ and
 	$T_2$ have the same radius $r$.
@@
 	statement is true for all lesser values of $r$.
+	Let $\tau_{(T_1,v_1)}$ and $\tau_{(T_2,v_2)}$ 
+	be the colorings over $T_1$ and $T_2$ defined as in 
+	the definition of $\sim_k$. 
 	We will show that there is a winning strategy 
 	for Duplicator in
-	$d\ehr_k(T_1,v_1,T_2,v_2)$.
+	$d\ehr_k(T_1,v_1;\,\, T_2,v_2)$.
 	At the start of the game, set all the initial edges
@@
 		\item Otherwise, the vertex played by Spoiler belongs to
-		$Tree_{(T_1,v_1)}(e_1)$
+		$\mathrm{Tr}(T_1,v_1;\,\,e_1)$
 		for a unique initial edge $e_1$ of $T_1$. 
@@
 		\begin{itemize}
-			\item If $e_1$ is not marked yet, mark it with
-			the index $i$. In this case, there is a 
+			\item If $e_1$ is not marked yet, mark it. 
+			In this case, there is a 
 			non-marked initial
 			edge $e_2$ in $T_2$ satisfying 
-			$(T_1,e_1)\simeq_k (T_2,e_2)$.
-			Mark $e_2$ with the index $i$ as well. 
+			\[
+			\big(e_1,\tau_{(T_1,v_1)}\big)\simeq
+			\big(e_2,\tau_{(T_2,v_2)}  \big).\]
+			Mark $e_2$ as well. 
+			Set $T^\prime_1:=\mathrm{Tr}(T_1,v_1;\,\,e_1)$
+			and
+			$T^\prime_2:=\mathrm{Tr}(T_2,v_2;\,\,e_2)$
 			Because of
@@
 			has a winning strategy in
-			\[d\ehr{k}(Tree_{T_1}(e_1), v_1, 
-			Tree_{T_1}(e_2),v_2)\] and can play according to it.
+			$ d\ehr{k}(T^\prime_1, v_1; \,\, T^\prime_2,v_2)$
+			and can play according to it.
 			\item If $e_1$ is already marked then there is
-			a unique initial edge $e_2$ in $T_2$ marked with 
-			the same mark as $e_1$ and 	
-			$(T_1,e_1)\simeq_k (T_2,e_2)$. Again, 
+			a unique initial edge $e_2$ in $T_2$ that was 
+			marked during the same round as $e_1$ and it satisfies 
+			\[
+			\big(e_1,\tau_{(T_1,v_1)}\big)\simeq
+			\big(e_2,\tau_{(T_2,v_2)}  \big).\]	
+			Again, 
 			Because of
@@
 			has a winning strategy in
-			\[d\ehr{k}(Tree_{T_1}(e_1), v_1, 
-			Tree_{T_1}(e_2),v_2)\] and can
-			continue playing 
-			according to it.
-
+			$d\ehr{k}(T^\prime_1, v_1; \,\, T^\prime_2,v_2)$
+			and can continue playing according to it taking
+			into account the plays made previously in 
+			$T^\prime_1$ and $T^\prime_2$.	
 		\end{itemize}
-		Then Duplicator can find an initial 
-		edge $e_2$ of $T_2$ such that
-		$(T_1,e_1)\simeq_k (T_2,e_2)$.
-		Because of
-		\cref{lem:equivalentedges}, Duplicator
-		has a winning strategy in
-		$d\ehr{k}(Tree_{T_1}(e_1), v_1, 
-		Tree_{T_1}(e_2),v_2) $ and can play according to it.
 	\end{itemize}
-
 \end{proof}
-\todo[inline]{probablemente con alg\'un dibujo sencillo esta demostraci\'on se entienda mejor}
+
+\subsubsection{k-Equivalent hypergraphs}
+
+\begin{definition}
+	We call a connected hypergraph $H$ \textbf{saturated} if any proper 
+	sub-hypergraph $H^\prime \subset H$ satisfies $ex(H^\prime)<ex(H)$. 
+	Notice that if $H$ is saturated, in particular $ex(H)\geq 0$ because
+	the empty hypergraph has excess zero. \par
+
+	The \textbf{center} of a connected hypergraph $H$, written as
+	$Center(H)$,  
+	is its maximal saturated
+	sub-hypergraph in the case that $H$ is not a tree and 
+	is the empty hypergraph otherwise.  
+	If $H$ is an arbitrary hypergraph
+	then the center of $H$ is the union of the
+	centers of its connected components. \par
+	Let $H$ be an hypergraph and let $\overline{v}\in V(H)*$. If $H$
+	is connected then we define the graph $Center(H,\overline{v})$ 
+	as the minimal connected sub-hypergaph of $H$ that contains
+	both $Center(H)$ and the vertices in $\overline{v}$. Otherwise,
+	if $H$ is a general hypergraph we define $Center(H,\overline{v})$ 
+	as the union for all connected components $H^\prime$ of $H$
+	of the minimal connected sub-hypergraph of $H^\prime$ that
+	contains both $Center(H^\prime)$ and the vertices in $\overline{v}$
+	that belong to $V(H^\prime)$.
+\end{definition}
+
+\begin{definition}
+	Let $H$ be an hypergraph, let $\overline{v}\in V(H)^*$
+	and let $v\in H$. We define $\mathrm{Tr}\big(
+	H,\overline{v};\,\, v\big)$ in the following way:
+	\begin{itemize}
+		\item If $d\big(\, Center(H, \overline{v})
+		, \, \, v \big)=\infty$ then $v$ belongs to a connected
+		component $T$ of $H$ which is a tree and does not contain
+		any vertex in $\overline{v}$. In this case
+		$\mathrm{Tr}\big(
+		H,\overline{v};\,\, v\big)$ is the tree $T$ rooted at $v$.
+		\item Otherwise $\mathrm{Tr}\big(
+		H,\overline{v};\,\, v\big)$ is the tree $H[X]$ 
+		induced on the set 
+		\[
+		X:=\big\{\, u\in V(H) \,\, \big| \, 
+		d\big(\, Center(H, \overline{v})
+		, \, \, u \big)= d\big(\, Center(H, \overline{v})
+		, \, \, v \big) + d(v,u)
+		\big\},
+		\]
+		to which we assign $v$ as a root. That is,
+		$\mathrm{Tr}\big(
+		H,\overline{v};\,\, v\big)$ is the tree formed of all 
+		vertices whose only path to $Center(H,\overline{v})$ 
+		contains $v$. 		
+	\end{itemize}
+	In the case that $\overline{v}$ is the empty list we will write
+	simply $\mathrm{Tr}(H;\,\, v)$ instead of 
+	$\mathrm{Tr}(H,\, \, ;\,\, v)$. Notice that in the case that
+	$(T,u)$ is a rooted tree then the definition of 
+	$\mathrm{Tr}(T,u;\, \, v)$ given before coincides with this one,
+	so no confusion should arise. 	
+\end{definition}
+
+\begin{definition}
+	Let $H_1$ and $H_2$ be connected hypergraphs which are not trees.
+	Set $H^\prime_1:= Center(H_1)$ and $H^\prime_2:= Center(H_2)$.
+	We say that $H_1$ and $H_2$ are $k$-equivalent,
+	written as $H_1\sim_k H_2$, if there is an hypergraph isomorphism
+	$f:V(H^\prime_1)\rightarrow V(H^\prime_2)$ such that for all vertices
+	$v\in V(H^\prime_1)$ it holds that
+	\[
+	\mathrm{Tr}\big(H_1;\,\, v\big)\sim_k 
+	\mathrm{Tr}\big(H_2;\,\, f(v)\big).
+	\] 
+\end{definition}
+	Let $H$ be a non-tree connected hypergraph. We define
+	the canonical coloring $\tau_{H}$ over $Center(H)$
+	as the one that assigns to each vertex $v\in V\big(
+	Center(H)\big)$ the $\sim_k$ class of the tree
+	$\mathrm{Tr}(H,v)$.\par
+	An equivalent definition of $\sim_k$ for non tree connected
+	hypergraphs is the following: 
+	Let $H_1$ and $H_2$ be connected hypergraphs which are not trees.
+	Set $H^\prime_1:= Center(H_1)$ and $H^\prime_2:= Center(H_2)$.
+	Then we say that $H_1\sim_k H_2$ if
+	$\big( H^\prime_1,\tau_{H_1}\big) \simeq 
+	\big(H^\prime_2,\tau_{H_2}\big)$.\par
+	The main theorem of this section is the following
+
+	\begin{theorem}
+		Let $H_1$ and $H_2$ be non-tree 
+		connected hypergraphs satisfying
+		$H_1\sim_k H_2$. 
+		Set $H^\prime_1:= Center(H_1)$ and 
+		$H^\prime_2:= Center(H_2)$. Let $f$ be an isomorphism
+		between $\big( H^\prime_1,\tau_{H_1}\big)$ and 
+		$\big(H^\prime_2,\tau_{H_2}\big)$. Let $\overline{v_1}$ 
+		be an ordering of the vertices of $H^\prime_1$ and let
+		$\overline{v_2}:=f(\overline{v_1})$ be the corresponding
+		ordering of the vertices of $H^\prime_2$. Then
+		Duplicator wins 
+		\[	d\ehr_{k}\big(\,
+		H^\prime_1,\overline{v_1};\quad
+		H^\prime_2,\overline{v_2}\,
+		\big).
+		\]
+	\end{theorem}
+	\begin{proof}
+		The winning strategy for Duplicator is as follows. 
+		Suppose that at the beginning of the $i$-th round
+		Spoiler plays in $H_1$ (the case where they play in
+		$H_2$ is symmetric). Then Spoiler has chosen a vertex 
+		that belongs to $\mathrm{Tr}(H_1;\,\,u)$ for a unique
+		$u\in H^\prime_1$. 
+		Set $T_1:=\mathrm{Tr}\big(H_1;\,\,u\big)$ and
+		$T_2:=\mathrm{Tr}\big(H_2;\,\,f(u)\big)$.
+		By hypothesis
+		$(T_1,u)\sim_k (T_2,f(u))$. 
+		Then because of \cref{thm:equivalenttrees} we have that
+		Duplicator has a winning strategy in
+		\[
+		d\ehr_{k}\big(\,
+		T_1,u; \quad T_2, f(u)\,\big),
+		\]
+		and they can follow it taking into account the previous
+		plays made in $T_1$ and $T_2$. In particular, 
+		if Spoiler has chosen
+		$u$ then Duplicator will necessarily choose $f(u)$.\par
+		One can easily check that distances are preserved
+		following this strategy. 
+	\end{proof}
+
+\subsection{$r$-Cores}
+
+\begin{definition}
+	Let $H$ be an hypergraph. We define its \textbf{$r$-core}, 
+	written as $Core(H;r)$ as $N(X;r)$,
+	where $X$ is the set of vertices $v\in V(H)$
+	that participate in any saturated sub-hypergraph 
+	$H^\prime\subset H$ whose diameter is at most $2r+1$.\par
+	Let $H_1$ and $H_2$ be hypergraphs and let $r\in \N$.
+	Let $H^\prime_1:=Core(H_1;r)$ and $H^\prime_2:=Core(H_2;r)$. 
+	Suppose that any connected component $F$ from either 
+	$H^\prime_1$ or $H^\prime_2$ satisfies that
+	``the number of connected components $H^{\prime\prime}_1$
+	from $H^\prime_1$ such that $ H^{\prime\prime}_1 \sim_k F\, \, \,$'' 
+	and ``the number of
+	connected components $H^{\prime \prime}_2$ of $H^\prime_2$
+	such that
+	$ H^{\prime\prime}_2\sim_k F\, \, \,$" 
+	are both equal or are both greater 
+	or equal than $k$. Then we say that $H_1$ and $H_2$
+	are $(k,r)$-\textbf{agreeable}, written as $H_1\approx_{k,r} H_2$. \par
+	We say that an hypergraph $H$ is $r$-simple all connected components
+	of $Core(H;r)$ are unicycles.   
+\end{definition}
+
+\begin{definition}
+	Let $\Sigma_{(k,r-1)}$ be the set of $\sim_k$ classes
+	of rooted trees with radii at most $r-1$. Then
+	we call a $(k,r)$-\textbf{cycle} to an isomorphism class
+	of $\Sigma_{(k,r-1)}$-hypergraphs 
+	$(H,\tau)$ that are cycles of diameter at most $2r+1$.
+	We will denote by $C(k,r)$ the set of $(k,r)$-cycles.
+\end{definition}
+
+The following is a way of characterizing $\approx_{k,r}$ classes
+of $r$-simple hypergraphs.
+
+\begin{obs}\label{obs:agreeablecores}
+	Let $\mathcal{O}$ be a $\approx_{k,r}$ class
+	of $r$-simple hypergraphs. 
+	Then there is a partition $U^1_\mathcal{O},
+	U^2_\mathcal{O}$ of $C(k,r)$ and natural numbers $a_\omega<k$
+	for each $\omega\in U^2_\mathcal{O}$ that only depend on 
+	$\mathcal{O}$ such that any $r$-simple hypergraph $G$ belongs to
+	$\mathcal{O}$ if and only if it holds that
+	\begin{itemize}
+		\item[(1)] For any $\omega\in U^1_\mathcal{O}$ there are at least
+		$k$ connected components $H \subset Core(H;r)$ whose cycle 		
+		$H^\prime=Center(H)$ satisfies that
+		$(H^{\prime},\tau_{H})\in \omega$.
+		\item[(2)]For any $\omega\in U^2_\mathcal{O}$ there are exactly 
+		$a_\omega$ connected components $H \subset Core(H;r)$ whose cycle 		
+		$H^\prime=Center(H)$ satisfies that
+		$(H^{\prime},\tau_{H})\in \omega$.	
+	\end{itemize}
+\end{obs}
+
+\begin{lemma}
+	Let $r\in \N$ and let $H_1, H_2$ be hypergraphs such that 
+	$H_1\approx_{k,r} H_2$. Let $X$ and $Y$ be the
+	sets of vertices in $H_1$, resp. $H_2$, that
+	belong to any saturated sub-hypergraph of diameter 
+	at most $2r+1$. Then $(H_1,X)\cong_{k,r} (H_2,Y)$.	
+\end{lemma}
+\begin{proof}
+	Let $X_1,\dots, X_a$ and $Y_1,\dots, Y_b$ be partitions of
+	$X$ and $Y$ such that each $N(X_i;r)$ and $N(Y_i;r)$ is 
+	a connected component of $Core(H_1;r)$, resp. $Core(H_2;r)$.
+	Using the definition of $H_1\approx_{k,r}H_2$ as well 
+	as the fact that $N(X_i;r)\sim_k N(Y_j;r)$ implies 
+	$(H_1,X_i)\simeq_{k,r} (H_2,Y_j)$ the result follows.	
+\end{proof}
+
+\begin{definition}
+	Let $H$ be an hypergraph and let $r\in\N$. Let
+	$X\subset V(H)$ be the set of vertices in $H$
+	belonging to some saturated sub-hypergraph of diameter
+	at most $2r+1$.	We say that $H$ is $(k,r)$-\textbf{rich}
+	if for any $r^\prime\leq r$, any vertices $v_1,\dots, v_k$ 
+	and any $\sim_k$ class $\mathcal{T}$ of trees with radius
+	at most $r^\prime$ it holds that there exists a vertex $v\in V(H)$
+	such that $d(v,X)> 2r^\prime+1$, $d(v,v_i)>2r^\prime+1$ for all
+	$v_i$'s and that $T:=N(v;r^\prime)$ is a tree such that
+	$(T,v)\in \mathcal{T}$ (notice that $T$ is a tree necessarily. 
+	Otherwise $T$ contains a saturated sub-hypergraph with diameter 
+	lesser or equal than $2r^\prime+1$).	
+\end{definition}
+
+\begin{theorem}\label{thm:Duplicatorwins}
+	Let $H_1$, $H_2$ be hypergraphs. Let $r:=(3^k-1)/2$. Suppose
+	that both $H_1$ and $H_2$ are $(k,r)$-rich and
+	$H_1\approx_{k,r} H_2$. Then Duplicator wins $\ehr_{k}(H_1,H_2)$.
+\end{theorem}
+	\begin{proof}
+		We can apply \cref{ThmDuplicator} with $X\subset V(H_1)$ 
+		and	$Y\subset V(H_2)$ the sets of vertices that belong
+		to some saturated sub-hypergraph of $H_1$ or $H_2$ respectively
+		with diameter at most $2r+1$.
+	\end{proof}
 
 \section{Probabilistic results}
-\subsection{Convergence to Poisson variables}
-
-Given a natural numbers $n$ and $l$ we will use 
-$(n)_l$ to denote 
-$n(n-1)\cdots (n-l+1)$ or $1$ if $l=0$.
-
-Our main tool for computing probabilities will be
-the following multivariate version of Brun's Sieve (
-Theorem 1.23, \cite{bollobas2001random}).
-
-\begin{theorem} \label{thm:BrunSieve}
-	Fix $k\in \N$. For each 
-	$n\in \N$, let $X_{n,1},\dots, X_{n,k}$ be non-negative
-	random integer variables over the same
-	probability space. Let $\lambda_1,\dots,\lambda_l$ 
-	be real numbers. Suppose that for any $r_1,\dots,r_l \in \N$
-	\[ 
-	\Ln \mathrm{E}\big[
-	\prod_{i=1}^{k} \binom{X_{n,i}}{r_i} \big]
-	= \prod_{i=1}^{k} \frac{\lambda_i}{r_i !}.	
-	\]
-	Then the $X_{n,1},\dots,X_{n,k}$ converge in distribution to
-	independent Poisson variables with means $\lambda_1,\dots,\lambda_k$ 
-	respectively. 
-\end{theorem}
 
@@
 We say that a connected hypergraph $G$ is \textbf{dense} if
-$ex(G)>0$. Given $r\in \N$, we say that $G$ is \textbf{$r$-simple}
+$ex(G)>0$. Given $r\in \N$, we say that $G$ is \textbf{$r$-sparse}
 if $G$ does not contain any dense subgraph $H$ such that 
 $diam(H)\leq r$. The goal of this section is to show that, for any
-fixed $r$, a.a.s $G_n$ is $r$-simple.\par
+fixed $r$, a.a.s $G_n$ is $r$-sparse.\par
 
@@
 \PR{H^\prime \subset G_n}= \prod_{R\in \sigma} \left(\frac{\beta_R}{n^{ar(R)-1}} 
-\right)^{e_R(H)}.
+\right)^{|E_R(H)|}.
 \]
@@
 \frac{(n)_{v(H)}}{|Aut(H)|}\cdot
-\prod_{R\in \sigma} \left(\frac{\beta_R}{n^{ar(R)-1}}\right)^{e_R(H)}
-\underset{n \to \infty}{\sim}
+\prod_{R\in \sigma} \left(\frac{\beta_R}{n^{ar(R)-1}}\right)^{|E_R(H)|}
+\sim
 n^{-ex(H)} \cdot \frac{\prod_{R\in \sigma} \beta_R^{
-e_R{H} }}{|Aut(H)|}.
+|E_R{H}| }}{|Aut(H)|}.
 \]
@@
 
-\subsubsection{Rooted hypergraphs}
-
-A rooted hypergraph $(G,\overline{u})$ is an hypergraph $H$ together with 
-an ordered sequence of distinguished vertices $\overline{u}\in (V(H))_*$.
-An isomorphism between two rooted hypergraphs $(G,\overline{u})$ and
-$(H,\overline{v})$ is a map $f: V(G)\rightarrow V(H)$ such that $f$
-is an isomorphism between $G$ and $H$ that satisfies the additional condition
-$f(\overline{u})=\overline{v}$. An automorphism of $(G,\overline{u})$  is 
-an isomorphism from $(G,\overline{u})$  to itself. 
-We write $Aut(G,\overline{u})$ to denote the group
-of automorphisms of $(G,\overline{u})$. \par
-
-Given a rooted hypergraph $(G,\overline{u})$, a set of vertices
-$V$ and a list $\overline{v}\in (V)_*$ such that $len(\overline{u})
-= len(\overline{v})$ we define the set $Copies((G,\overline{u}),
-(V,\overline{v}))$ as the set of rooted hypergraphs 
-$(H,\overline{v})$ isomorphic to $(G,\overline{u})$ such that
-$V(H)\subset V$. \par
+%\subsubsection{Rooted hypergraphs}
+%
+%A rooted hypergraph $(G,\overline{u})$ is an hypergraph $H$ together with 
+%an ordered sequence of distinguished vertices $\overline{u}\in (V(H))_*$.
+%An isomorphism between two rooted hypergraphs $(G,\overline{u})$ and
+%$(H,\overline{v})$ is a map $f: V(G)\rightarrow V(H)$ such that $f$
+%is an isomorphism between $G$ and $H$ that satisfies the additional condition
+%$f(\overline{u})=\overline{v}$. An automorphism of $(G,\overline{u})$  is 
+%an isomorphism from $(G,\overline{u})$  to itself. 
+%We write $Aut(G,\overline{u})$ to denote the group
+%of automorphisms of $(G,\overline{u})$. \par
+%
+%Given a rooted hypergraph $(G,\overline{u})$, a set of vertices
+%$V$ and a list $\overline{v}\in (V)_*$ such that $len(\overline{u})
+%= len(\overline{v})$ we define the set $Copies((G,\overline{u}),
+%(V,\overline{v}))$ as the set of rooted hypergraphs 
+%$(H,\overline{v})$ isomorphic to $(G,\overline{u})$ such that
+%$V(H)\subset V$. \par
 
 \begin{lemma}\label{lem:nocopiesfixed}
-	Let $(H,\overline{u})$ be a rooted hypergraph. Let
-	$\overline{v}\in (\N)_*$ be a list of vertices satisfying
-	$len(\overline{u})=len(\overline{v})$. For each $n\in \N$ 
+	Let $H$ be an hypergraph. Let
+	$\overline{v}\in (\N)_*$ be a list of vertices
+	with $len(\overline{v})\leq |V(H)|$.
+	For each $n\in \N$ 
 	let $X_n$ be the random variable that
-	counts the copies $(H^\prime,\overline{v})\in
-	Copies((H,\overline{u}),
-	([n],\overline{v}))$ that are contained in $G_n$. Then
-	$\mathrm{E}\big[ X_n \big]=\Theta(n^{-ex(H)-len(\overline{u})})$.	
+	counts the copies of $H$ in $G_n$ that contain the vertices
+	in $\overline{v}$. Then
+	$\mathrm{E}\big[ X_n \big]=\Theta(n^{-ex(H)-len(\overline{v})})$.	
 \end{lemma}
 \begin{proof}
-	It holds
-	\[
-	\mathrm{E}\big[ X_n \big]=\sum_{H^\prime\in (H^\prime,\overline{v})\in
-		Copies((H,\overline{u})} \PR{H^\prime \subset G_n}
-	= \frac{(n)_{(v(H)-len(\overline{u}))}}{|Aut(H,\overline{u})|} 
-	\cdot\prod_{R\in\tau} \left( \frac{\beta_R}{n^{ar(R)-1}}\right)^{e_R(H)}
+	It holds that the number of hypergraphs $H^\prime \in Copies(H,[n])$
+	that contain all vertices in $\overline{v}$ is
+	 $\Theta\big(n^{|V(H)|-len(\overline{v})}\big)$. Then for
+	 some constant $C$,
+	\[
+	\mathrm{E}\big[ X_n \big]\sim 
+	C n^{|V(H)|-len(\overline{v})}
+	\cdot\prod_{R\in\tau} \left( \frac{\beta_R}{n^{ar(R)-1}}\right)^{e_R(H)}=
+	n^{-ex(H)-len(\overline{v})}\cdot C \cdot
+	\prod_{R\in\tau} \left( \beta_R \right)^{e_R(H)}.
 	\]
@@
 The main theorem of this section is the following
-\begin{theorem} \label{thm:simple}
-	Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple. 
+\begin{theorem} \label{thm:sparse}
+	Let $r\in \N$. Then a.a.s $G_n$ is $r$-sparse. 
 \end{theorem}
+
 	The first moment method alone is not sufficient
@@
 	prohibit a finite amount of dense sub-hypergraphs in order
-	to guarantee that $G_n$ is $r$-simple.
+	to guarantee that $G_n$ is $r$-sparse.\par
+	Given an hypergraph $H$ and an edge $e\in E(H)$ we
+	define the operation of \textbf{cutting} the edge 
+	$e$ as removing $e$ from $H$ and then removing any isolated
+	vertices from the resulting hypergraph. \par
+
 \begin{lemma}
-	Let $H$ be a dense hypergraph of radius $r$.
-	Then $H$ contains a dense sub-hypergraph $H^\prime$ 
-	with size no greater than
-	$(a+2)(r+1)+2a$, where $a$ is the largest edge size in $H$. 
+	Let $G$ be a
+	dense hypergraph with diameter at most $r$.
+	And let $H\subset G$ be a connected 
+	sub-hypergraph with $ex(H)<ex(G)$. Then
+	there is a connected
+	sub-hypergraph $H^\prime \subset G$
+	satisfying $H\subset H^\prime$,
+	$ex(H)<ex(H^\prime)$ and that 
+	$|E(H^\prime)|\leq |E(H)|+2\cdot(r) + 1$, 
 \end{lemma}
 \begin{proof}
-	Choose $x\in V(H)$. Successively remove from $G$ edges $e$
-	such that $d(x, e)$ is maximum until the resulting graph 
-	$H^\prime$ has excess no greater than $0$. We have two cases:
-	\begin{itemize}[leftmargin=*]
-		\item $ex(H^\prime)=-1$. Let $e=[x_1, \dots, x_b]$ be
-		the last removed edge and
-		$e\cap H^\prime=\{ x_{i_1}, \dots, x_{i_d}\}$.
-		For any $j=1,\dots, d$ choose 
-		$P_j$ a path of size no greater than $r+1$ joining
-		$x$ and $x_{i_j}$ in $H^\prime$.   
-		Then $P_1\cup \dots P_d \cup e$ is a dense sub-hypergraph of $H$
-		of size less than $a(r+1) + a< (a+2)(r+1) + 2a$.
-		\item $ex(H^\prime)=0$. Let $e_1=[x_1, \dots, x_{b_1}]$ be the
-		last removed edge. Continue removing the edges of $G^\prime$ 
-		that are at maximum distance from $x$ until you obtain 
-		$H^{\prime \prime}$ with $ex(H^{\prime\prime})=-1$. Let 
-		$e_2=[y_1, \dots, y_{b_2}]$ be the last removed edge this time.
-		As before, let $e_1\cap H^\prime=\{ x_{i_1}, \dots, x_{i_d}\}$
-		and for $j=1,\dots, d$ let $P_j$ a path of size no greater than $r+1$ 
-		joining	$x$ and $x_{i_j}$ in $H^\prime$
-		Then $e_2 \cup H^{\prime \prime}=\{ y_{i_1}, y_{i_2}  \}$.
-		Let $Q_1, Q_2$ be paths size no greater than $r+1$ from
-		$x$ to $y_{i_1}$ and $y_{i_2}$ in $H^{\prime \prime}$.
-		Then $Q_1 \cup Q_2 \cup e_2$ is a graph of likelihood $0$ 
-		and size less than $2r+2 + a$,
-		and $Q_1\cup Q_2\cup P_1 \cup \dots \cup P_d \cup e_1 \cup e_2$ 
-		is a critical graph	with size less than $(2+a)(r+1) + 2a$	
-	\end{itemize} 
+	Suppose that there is some edge $e\in E(G)\setminus E(H)$ with
+	and $ex(e)\geq 0$. Let $P$ be a path
+	of length at most $r$ joining $H$ and $e$ in $G$. 
+	Then $H^\prime:=H\cup P \cup e$ satisfies the conditions of 
+	the statement. \par
+	Otherwise, all edges $e\in E(G)\setminus E(H)$ 
+	satisfy $ex(e)=-1$. In this case we successively cut
+	edges $e$ from $G$ such that $d(e, H)$ is the maximum possible
+	(notice that this always yields a connected hypergraph)
+	until we obtain an hypergraph $G^\prime$ with $ex(G^\prime)<ex(G)$.
+	Let $e$ be the edge that was cut last. Then $V(G^\prime)\cap V(e)=
+	ex(G)-ex(G^\prime)+1 \geq 2$. Let $v_1, v_2\in V(G^\prime)\cap V(e)$,
+	and let $P_1$, $P_2$ be paths of length at most $r$ that join $H$
+	with $v_1$ and $v_2$ respectively in $G^\prime$. Then the hypergraph
+	$H^\prime:=H\cup e \cup P^1 \cup P^2$ satisfies the conditions 
+	in the statement. 
 \end{proof}
 
-Now we are in conditions to prove \cref{thm:simple}.
+\begin{lemma}
+	Let $G$ be a
+	dense hypergraph of diameter at most 
+	$r$. Then $G$ contains a connected 
+	dense sub-hypergraph $H$ 
+	with $|E(H)|\leq 4r+2$. 
+\end{lemma}
+\begin{proof}
+	Apply the previous lemma twice in a row starting with $G$ and taking
+	as $H$ a sub-hypergraph of $G$ consisting of a single vertex and 
+	no edges. 
+\end{proof}
+
+In particular, if we define $l:=\max\limits_{R\in \sigma} \,\, ar(R)$
+then last lemma implies that if $G$ is a dense hypergraph whose
+diameter is at most $r$ then $G$ contains a dense sub-hypergraph
+$H$ with $|V(H)|\leq l\cdot (4r+2)$.\par
+
+Now we are in conditions to prove \cref{thm:sparse}.
 
@@
 	``$G$ does not contain dense hypergraphs of size bounded by $R$" implies
-	that ``$G$ is $r$-simple". Thus,
-	\[ \Ln \mathrm{Pr}\big( G_n \text{ is } r \text{-simple}  \big)
+	that ``$G$ is $r$-sparse". Thus,
+	\[ \Ln \mathrm{Pr}\big( G_n \text{ is } r \text{-sparse}  \big)
 	\geq \Ln \mathrm{Pr} \big( G_n \text{ does not contain dense 
@@
 \end{proof}
+
+\begin{corollary}\label{cor:simple}
+	Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple.
+\end{corollary}
+\begin{corollary}
+	If some connected component of $Core(G_n;r)$ is not a cycle that means
+	that either $G_n$ contains a dense hypergraph of diameter at most $4r+1$
+	or that $G_n$ contains two cycles of diameter at most $2r+1$ that are at
+	a distance at most $2r+1$. In the second case, considering the two cycles
+	and the path joining them, $G_n$ contains a dense hypergraph of diameter
+	bounded by $6r+3$. In consequence the fact that $G_n$ is $(6r+3)$-sparse
+	implies that $G_n$ is $r$-simple. Because of the previous theorem 
+	$G_n$ is a.a.s $(6r+3)$-sparse and the result follows. 
+\end{corollary}
 
@@
 
+\subsection{Convergence to Poisson variables}
+
+Our main tool for computing probabilities in the following sections
+will bethe following multivariate version of Brun's Sieve (
+Theorem 1.23, \cite{bollobas2001random}).
+
+\begin{theorem} \label{thm:BrunSieve}
+	Fix $k\in \N$. For each 
+	$n\in \N$, let $X_{n,1},\dots, X_{n,l}$ be non-negative
+	random integer variables over the same
+	probability space. Let $\lambda_1,\dots,\lambda_l$ 
+	be real numbers. Suppose that for any $r_1,\dots,r_l \in \N$
+	\[ 
+	\Ln \mathrm{E}\left[
+	\prod_{i=1}^{l} \binom{X_{n,i}}{r_i} \right]
+	= \prod_{i=1}^{l} \frac{\lambda_i}{r_i !}.	
+	\]
+	Then the $X_{n,1},\dots,X_{n,l}$ converge in distribution to
+	independent Poisson variables with means $\lambda_1,\dots,\lambda_l$ 
+	respectively. 
+\end{theorem}
+
+To make use of last theorem we will need to employ the following observation.
+
+\begin{obs} \label{obs:binomialmean} Let $X_1,\dots, X_l$ be non negative
+	random integer variables over the same space. 
+	Let $r_1,\dots,r_l\in \N$.	Suppose that
+	each $X_i$ is the sum of various indicator random variables
+	(i.e. variables that only take the values $0$ and $1$)
+	$X_i=\sum_{j=1}^{a_i} Y_{i,j}$. Define 
+	$\Omega:=\prod_{i=1}^l \binom{[a_i]}{r_i}$. That is,
+	the elements $\{S_i\}_{i\in[l]}\in \Omega$
+	represent all the possible unordered choices of 
+	$r_i$ indicator variables $Y_{i,j}$ for each $i\in [l]$.
+	Then 
+	\[
+	\mathrm{E}\left[
+	\prod_{i=1}^{l} \binom{X_i}{r_i}\right]=
+	\sum_{\{S_i\}_{i\in [l]}} \Pr\left(
+	\bigwedge_{\substack{i\in [l]\\ j\in S_i}} Y_{i,j}=1
+	\right).	
+	\]
+\end{obs}
+
 \subsection{Probabilities of trees}
@@
 We define $\Lambda$ and $M$ as the minimal families
-of expressions with arguments $\overline{\beta}$ that satisfy
- the conditions: \textbf{(1)} $1\in \Lambda$, \textbf{(2)} 
-for any $b,i\in \N$ with $1\leq i \leq c$,
-$b > 0$, and $\lambda_1,\dots, \lambda_{a_i-1}\in \Lambda$,
-the expression $(\beta_i/b) \prod_{j=1}^{a_i-1}\lambda_j$
+of expressions with arguments $\{\beta_R\}_{R\in\sigma}$
+that satisfy the conditions: \textbf{(1)}
+$1\in \Lambda$, \textbf{(2)} 
+for any $R\in \sigma$, any positive $b\in \N$,
+and $\overline{\lambda} \in \Lambda^*$,
+the expression $(\beta_R/b) \prod_{\lambda\in \overline{\lambda}}
+\lambda$
 belongs to $M$, \textbf{(3)}
@@
 as an expression with parameters
-$\overline{\beta}$, belongs to $\Lambda$ for any choice of 
+$\{\beta_R\}_{R\in\sigma}$, belongs to $\Lambda$ for any choice of 
 $r$ and $\mathcal{T}$. \par
@@
 	Let $\overline{v} \subset \N*$ be a finite set of fixed vertices and let 
-	$\sigma(\overline{x})$ be an open formula with no equality such that
+	$\pi(\overline{x})$ be an edge sentence such that
 	$length(\overline{x})=length(\overline{v})$. 
-	Define $G_n^\prime=G_n \setminus E(\overline{v})$. Fix $R\in \N$. 
+	Define $G_n^\prime=G_n \setminus E[\overline{v}]$ (i.e. $G_n$ minus all the
+	edges induced over $\overline{v}$). Fix $R\in \N$. 
 	\begin{itemize}
-		\item Let $A_n$ be the event that $G^\prime_n$ contains a path of size
-		at most	$R+1$ between any two vertices $u,w\in \overline{v}$.
+		\item Let $A_n$ be the event that $G^\prime_n$ contains a path of 
+		length	at most	$R$ between any two vertices $u,w\in \overline{v}$.
 		\item Let $B_n$ be the event
-		that $G^\prime_n$ contains a cycle of size at most $R+1$ 
-		that contains a vertex $u\in \overline{v}$.
+		that $G^\prime_n$ contains a cycle of diameter at most $R$
+		at distance at most $R$ to some vertex $u\in \overline{v}$.
 	\end{itemize}
-	Then $\Ln \mathrm{Pr}(A_n \, | \, \sigma(\overline{v}))=0$, and 
-	$\Ln \mathrm{Pr}(B_n \, | \, \sigma(\overline{v})=0$. 
+	Then $\Ln \mathrm{Pr}\big(A_n \, | \, \pi(\overline{v})\big)=0$, and 
+	$\Ln \mathrm{Pr}\big(B_n \, | \, \pi(\overline{v})\big)=0$. 
 \end{lemma}
@@
 	in our random model, 
-	$\mathrm{Pr}(A_n \, | \, \sigma(\overline{v}))
+	$\mathrm{Pr}\big(A_n \, | \, \pi(\overline{v})\big)
 	=\mathrm{Pr}(A_n)$ and 
-	$\mathrm{Pr}(B_n \, | \, \sigma(\overline{v}))
+	$\mathrm{Pr}\big(B_n \, | \, \pi(\overline{v})\big)
 	=\mathrm{Pr}(B_n)$.\par
-	The facts that $\Ln \mathrm{Pr}(A_n)=0$ and 
-	$\Ln \mathrm{Pr}(B_n)=0$ follow
-	from \cref{lem:nocopiesfixed} using that 
+	The equation $\Ln \mathrm{Pr}(A_n)=0$ follows from
+	 \cref{lem:nocopiesfixed} using that 
 	(1) the excess of any path is greater or equal than $-1$,
-	(2) the amount of paths of size at most $R+1$ is finite,
-	(3) the excess of any cycle is zero, and (4) the
-	amount of cycles of size at most $R+1$ is finite. 
+	(2) the amount of paths with length at most $R$ is finite.
+	The equation $\Ln \mathrm{Pr}(B_n)=0$ is also deduced from
+	\cref{lem:nocopiesfixed} using that
+	(1) any hypergraph $H$ consisting
+	of a path of length at most $R$ joining cycle with diameter at most 
+	$R$ satisfies that $ex(H)\geq 0$, and (2) the
+	amount of such hypergraphs is finite. 
 \end{proof}
 
-\begin{definition}
-	We call an hypergraph $G$ \textbf{saturated} if any proper 
-	sub-hypergraph $G^\prime \subset H$ satisfies $ex(G^\prime)<ex(G)$. \par
-	The \textbf{center} of a connected hypergraph $G$ is its maximal saturated
-	sub-hypergraph and it is denoted by $Center(G)$. In the general case 
-	the center of an hypergraph is the union of the
-	centers of its connected components. 
-\end{definition}
-
-\begin{definition}
-	Let $G$ be a connected hypergraph and let $\overline{v}\in V(G)^*$.
-	Then we call $Center(G, \overline{v})$ to the minimal connected hypergraph
-	that contains $Center(G)$ and the vertices $\overline{v}$. In general, if 
-	$G$ is an arbitrary hypergraph with connected components $G^1, \dots, G_k$,
-	and $\overline{v}$ are vertices $V(G)$, then we call 
-	$Center(G, \overline{v})$ to the union of $Center(G_i, V(G_i)\cap
-	\overline{v})$ for all the connected components $G_i$.
-\end{definition}
-
-\begin{definition}
-	Let $G$ be an hypergraph $G$, let $\overline{u}\in V(G)^*$
-	and let $v\in \overline{u}$.
-	Consider the graph $G^\prime= G\setminus 
-	E\big(Center(G,\overline{u})\big)$. Then the connected components of
-	$G^\prime$ are all trees. We call the \textbf{tree of $v$ in
-	$G(\overline{u})$}, denoted by $Tr\big(G(\overline{u}),v\big)$,
-	to the connected component of $G^\prime$ to which $v$ belongs
-	with $v$ as its root. \par   
-	In this same situation, let $r\in \N$ and $H:=N^G(\overline{u};r)$.
-	We call the \textbf{$r$-tree of $v$ in $G(\overline{u})$}, 
-	denoted by $Tr\big(G(\overline{u}),v;r\big)$ to 
-	$Tr\big(H(\overline{u}),v\big)$.
-\end{definition}
-
-\newpage
+\begin{corollary}\label{cor:disjointtrees}
+	Let $\overline{v}\in (\N)_*$ be a finite set of vertices 
+	and let $\pi(\overline{x})$ be an edge sentence such that
+	$len(\overline{v})=len(\overline{x})$. 
+	Define $G_n^\prime=G_n \setminus E[\overline{v}]$. 
+	Fix $r\in \N$.
+	Let $U_n$ be the event that for all $v\in \overline{v}$
+	the neighborhoods $N^{G^\prime_n}(v;r)$ are disjoint trees.
+	Then
+	\[
+	\Ln \PR{U_n \, \big| \, \pi(\overline{v})}=1.\]
+	In particular, for all $v\in \overline{v}$, a.a.s
+	\[
+	Tr\big(G_n,\overline{v};\, v;\, r)=N^{G^\prime_n}(v;r).
+	\]
+\end{corollary}
+\begin{proof}
+	As in the previous lemma, because edges are independent 
+	in our random model, \[
+	\PR{U_n \, \big| \, \pi(\overline{v})}
+	=\PR{U_n}\]
+	 for all $n$. Because of the previous lemma
+	a.a.s there is no path in $G^\prime_n$ of length at most $2r+1$ joining 
+	any two vertices in $\overline{v}$. In consequence a.a.s
+	the $N^{G^\prime_n}(v;r)$'s are disjoint.\par
+	Also, because of \cref{thm:sparse} a.a.s there are no dense
+	hypergraphs with diameter at most $r$ in $G_n$, 
+	so a.a.s the  $N^{G^\prime_n}(v;r)$'s are not dense.\par
+	Finally, because of the previous lemma, a.a.s 
+	none of the vertices in $\overbar{v}$ is at a distance
+	lesser than $r$ to a cycle of diameter at most $r$.
+	In consequence a.a.s all the $N^{G^\prime_n}(v;r)$'s are trees, 
+	as we wanted to prove. 	 
+\end{proof}
+\todo[inline]{Explicar N(v;r)=Tr(G;v;r)}.
 
@@
 		$k$-equivalence class for trees with radii at most $r$.
-		Then $\mathrm{Pr}[r,\mathcal{T}]$ exists and is an expression
+		Then 
+		\[
+		\Ln  \PR{Tr\big(G_n;\,\,v;\,\,r\big)\in \mathcal{T}}
+		=\mathrm{Pr}[r,\mathcal{T}]
+		\]
+		exists and is an expression
 		in $\Lambda$.
 		\item[(2)] Let $\overline{u}\in (\N)_*$ be a list of different fixed 
-		vertices, and let $\phi[\overline{x}]\in FO[\sigma]$ be a consistent
+		vertices, and let $\pi(\overline{x})\in FO[\sigma]$ be a consistent
 		edge sentence such that 
@@
 		\Ln \mathrm{Pr}\big( \bigwedge_{v\in \overline{v}} 
-		Tr\big(G_n, \overline{u},v;r\big)\in \mathcal{T}_v 
-		\, | \, \sigma(\overline{w})
+		Tr\big(G_n, \overline{u};\,\,v;\,\,r\big)\in \mathcal{T}_v 
+		\, | \, \pi(\overline{u})
 		\big)= \prod_{v\in \overline{v}} \mathrm{Pr}[r,\mathcal{T}_v]. \]	 	
@@
 \end{theorem}
+	We will devote the rest of this section to proving this
+	theorem. The proof will be done by induction on $r$.
+
+\begin{lemma}
+	Conditions (1) and (2) of \cref{thm:BigTrees} 
+	are satisfied for $r=0$.
+\end{lemma}
 \begin{proof}
-		We will prove (1) and (2) together by induction on $r$. \par
-		Assume $r=0$. We start by showing that (1) holds. Recall that
-		all trees with radius zero are $k$-equivalent. Thus, if
-		$\mathcal{T}$ is the unique $k$-equivalence class of trees
-		with radius zero
-		and $v\in \N$ is a fixed vertex then
-		 \[
-		 \mathrm{Pr}[0;\mathcal{T}] = \Ln \mathrm{Pr}\big( 
-		 T:=N^{G_n}(v;0) \text{ is a tree, and } (T,v)\in \mathcal{T} \big)
-		 =1, 
-		 \]
-		Indeed, $N^{G_n}(v;0)$ consists of a single vertex for all $n\geq v$,
-		and the above equation follows. The expression $1$ belongs to 
-		$\Lambda$, so (1) holds. \par
-		The case of (2) is analogous. As $r=0$, then $\mathcal{T}_1=\dots=
-		\mathcal{T}_k$ are the unique $k$-equivalence class of trees with
-		radius zero. Then, given $\sigma, \overline{u}, v_1,\dots, v_k$ as
-		in the statement,
-		\[\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^l
-		Tr\big(G_n, \overline{u},v_i;0\big)\in \mathcal{T}_i \, | \, \sigma(\overline{w})
-		\big)= \prod_{i=1}^l \mathrm{Pr}[0,\mathcal{T}_i]=1. \]	 	
-		Because of (1), $\mathrm{Pr}[0,\mathcal{T}_i]=1$ for all $i$'s, 
-		and (2) holds. \par
-		Now let $r>0$ and assume that both (1) and (2) hold for all
-
-		Via similar computations we can show that for any fixed
-		$v\in \overline{v}$.
-
-		We are going to show that the variables $X_{n,i,\epsilon}$ converge, as
-		$n$ tends to infinity, to independent Poisson variables 
-		$\mathrm{Poiss}(\mu_{r_i,\epsilon})$ whose means $\mu_{r_i,\epsilon}$ 
-		are expressions in the family $M$. Let $[\Sigma_{r_i}]$ be the set of
-		$\Sigma_{r_i}$-patterns. We want to prove: 
-		\begin{equation} \label{eqn:PoissonEdges}
-		\Ln \mathrm{Pr}\Big(
-		\bigwedge_{i=1}^k \bigwedge_{\epsilon \in [\Sigma_{r_i}]} X_{n,i,\epsilon}=a_{i,\epsilon}
-		\, | \, \sigma(\overline{w})\Big) =
-		\prod_{i=1}^k \prod_{\epsilon \in [\Sigma_{r_i}]} e^{-\mu_{r_i,\epsilon}}
-		\frac{(\mu_{r_i,\epsilon})^{a_{i,\epsilon}}}{a_{i,\epsilon}!}
-		\end{equation}
-		Furthermore, for each $i$ and $\epsilon$ we will prove that the mean 
-		$\mu_{r_i,\epsilon}$ does only depend on $r_i$ and $\epsilon$.
-		This proves both (1), and (2).\par
-		Given an $\Sigma_{r_i}$-pattern $\epsilon$ and any 
-		$(e,\chi)\in Copies(\epsilon,[n])$ we say that $(e,\chi)\in T_{n,i}$
-		if the following are satisfied: (1)	$e$ is an initial edge of $T_{n,i}$,
-		and	(2) that for any $v\in e$ such that $v\neq v_i$, it holds that
-		$\chi(v)$ is the $\simeq_k$ class of $Tr(T_{n,i},v)$.\par 
-		Given $r\in \N$ and $\epsilon\in \Sigma_{r}$
-		we define
-		$\mu_{r,\epsilon}$ as follows. Let $(e,\chi)$ be any representative of
-		$\epsilon$. Then
-		\[\mu_{r,\epsilon}=  \frac{\beta_{R(e)}}{|Aut(e,\chi)|}
-		\prod_{\substack{v\in e\\ \chi(v)\neq \tau }} \Pr[r,\chi(v)]. \]
-		For each $i\in [l]$ and $\epsilon\in [\Sigma_{r_i}]$ let 		
-		$b_{i,\epsilon}\in \N$ be fixed.
-
-		We want to prove
-		\[
-		\Ln \mathrm{E}\left[\prod_{\substack{i\in [l]\\ \epsilon \in [\Sigma_{r_i}]}} \binom{X_{n,i,\epsilon}}{b_{i,\epsilon}}
-		\right]= \prod_{\substack{i\in [l]\\ \epsilon \in [\Sigma_{r_i}]}}
-		\frac{(\mu_{r_i,\epsilon})^{b_{i,\epsilon}}}{b_{i,\epsilon}!}.
-		\]
-		Because \cref{thm:BrunSieve} this is sufficient to prove \cref{eqn:PoissonEdges}. \par
-		For each $n\in \N$ define
-		\begin{align*}
-		\Omega_n=&\Bigg\{
-		(E_{v,\epsilon})_{\substack{v\in \overline{v}\\ \epsilon
-		\in [\Sigma_{r(v)}]}} \quad \Big|\\ 
-		&  \forall v\in \overline{v},
-		\forall \epsilon \in [\Sigma_{r(v)}]\, \quad  E_{v,\epsilon}\subset
-		Copies(\epsilon,[n],\overline{w};v)\quad  \wedge \quad |E_{v,\epsilon}|=b_{v,\epsilon}\Bigg\}.
-		\end{align*}
-		Informally, the elements $(E_{v,\epsilon})_{v,\epsilon}$
-		of $\Omega_n$ are represent all choices of
-		possible initial edges for the $T_{n,v}$'s: For each $v\in \overline{v}$
-		and each $\epsilon\in [\Sigma_{r(v)}]$, $E_{n,v,\epsilon}$ selects
-		$b_{v,\epsilon}$ possible initial edges of $T_{n,v}$
-		with pattern $\epsilon$.\par
-%	 	Given an element $O\in \Omega_n$, with
-%	 	$O=\big(O_{i,\epsilon}\big)_{i\in [l], \epsilon \in [\Sigma_{r_i}]}$,
-%	 	we write $O\in G_n$ if
-		Using observation REF we obtain that
-		\[
-		\mathrm{E}\Big[\prod_{\substack{i\in [l]\\ \epsilon \in [\Sigma_{r_i}]}} \binom{X_{n,i,\epsilon}}{b_{i,\epsilon}}
-		\Big]= \sum_{(E_{v,\epsilon})_{v,\epsilon} \in \Omega_n
-		}		
-		\Pr \left( \bigwedge_{\substack{v\in \overline{v} \\ \epsilon \in
-		[\Sigma_{r(v)}]\\ (e,\chi) \in E_{v,\epsilon} }} \left( e\in E(T_{n,i}) 
-		\bigwedge_{u\in V(e), u\neq v} Tr(T_{n,v};u)\in \chi(u)
-		\right)  \right)
-		\]
-		Let $(E_{v,\epsilon})_{v,\epsilon}\in \Omega_n$. 
-		In order for $e\in E(T_{n,v})$ to be possible for all
-		$v\in \overline{v}$, $\epsilon\in [\Sigma_{r(v)}]$, 
-		$e\in E_{v,\epsilon}$ it is needed that each vertex 
-		in $[n]\setminus \overline{w}$ belongs at most to one
-		edge $(e,\chi)\in \cup_{v,\epsilon} \, E_{v,\epsilon}$.
-		This is because if for some 
-		\[
-		\bigwedge_{\substack{i\in [l]\\ \epsilon \in
-		[\Sigma_{r_i}]\\ (e,\chi) \in O_{i,\epsilon} }} \left( e\in E(T_{n,i}) 
-		\bigwedge_{v\in e, v\neq v_i} Tr(T_{n,i},v)\in \chi(v)
-		\right) 
-		\] 
-		to be possible it is needed that each $v\in $
+	Recall that	all trees with radius zero are $k$-equivalent. Thus,
+	the limits
+	appearing in conditions (1) and (2) are both equal to $1$.
 \end{proof}
 
-	\newpage
+%		Now let $r>0$ and assume that both (1) and (2) hold for all 
+%
+%		Via similar computations we can show that for any fixed
+%		$v\in \overline{v}$.
+%		
+%		We are going to show that the variables $X_{n,i,\epsilon}$ converge, as
+%		$n$ tends to infinity, to independent Poisson variables 
+%		$\mathrm{Poiss}(\mu_{r_i,\epsilon})$ whose means $\mu_{r_i,\epsilon}$ 
+%		are expressions in the family $M$. Let $[\Sigma_{r_i}]$ be the set of
+%		$\Sigma_{r_i}$-patterns. We want to prove: 
+%		\begin{equation} \label{eqn:PoissonEdges}
+%		\Ln \mathrm{Pr}\Big(
+%		\bigwedge_{i=1}^k \bigwedge_{\epsilon \in [\Sigma_{r_i}]} X_{n,i,\epsilon}=a_{i,\epsilon}
+%		\, | \, \sigma(\overline{w})\Big) =
+%		\prod_{i=1}^k \prod_{\epsilon \in [\Sigma_{r_i}]} e^{-\mu_{r_i,\epsilon}}
+%		\frac{(\mu_{r_i,\epsilon})^{a_{i,\epsilon}}}{a_{i,\epsilon}!}
+%		\end{equation}
+%		Furthermore, for each $i$ and $\epsilon$ we will prove that the mean 
+%		$\mu_{r_i,\epsilon}$ does only depend on $r_i$ and $\epsilon$.
+%		This proves both (1), and (2).\par
+%		Given an $\Sigma_{r_i}$-pattern $\epsilon$ and any 
+%		$(e,\chi)\in Copies(\epsilon,[n])$ we say that $(e,\chi)\in T_{n,i}$
+%		if the following are satisfied: (1)	$e$ is an initial edge of $T_{n,i}$,
+%		and	(2) that for any $v\in e$ such that $v\neq v_i$, it holds that
+%		$\chi(v)$ is the $\simeq_k$ class of $Tr(T_{n,i},v)$.\par 
+%		Given $r\in \N$ and $\epsilon\in \Sigma_{r}$
+%		we define
+%		$\mu_{r,\epsilon}$ as follows. Let $(e,\chi)$ be any representative of
+%		$\epsilon$. Then
+%		\[\mu_{r,\epsilon}=  \frac{\beta_{R(e)}}{|Aut(e,\chi)|}
+%		\prod_{\substack{v\in e\\ \chi(v)\neq \tau }} \Pr[r,\chi(v)]. \]
+%		For each $i\in [l]$ and $\epsilon\in [\Sigma_{r_i}]$ let 		
+%		$b_{i,\epsilon}\in \N$ be fixed. 
+%	
+%		We want to prove
+%		\[
+%		\Ln \mathrm{E}\left[\prod_{\substack{i\in [l]\\ \epsilon \in [\Sigma_{r_i}]}} \binom{X_{n,i,\epsilon}}{b_{i,\epsilon}}
+%		\right]= \prod_{\substack{i\in [l]\\ \epsilon \in [\Sigma_{r_i}]}}
+%		\frac{(\mu_{r_i,\epsilon})^{b_{i,\epsilon}}}{b_{i,\epsilon}!}.
+%		\]
+%		Because \cref{thm:BrunSieve} this is sufficient to prove \cref{eqn:PoissonEdges}. \par
+%		For each $n\in \N$ define
+%		\begin{align*}
+%		\Omega_n=&\Bigg\{
+%		(E_{v,\epsilon})_{\substack{v\in \overline{v}\\ \epsilon
+%		\in [\Sigma_{r(v)}]}} \quad \Big|\\ 
+%		&  \forall v\in \overline{v},
+%		\forall \epsilon \in [\Sigma_{r(v)}]\, \quad  E_{v,\epsilon}\subset
+%		Copies(\epsilon,[n],\overline{w};v)\quad  \wedge \quad |E_{v,\epsilon}|=b_{v,\epsilon}\Bigg\}.
+%		\end{align*}
+%		Informally, the elements $(E_{v,\epsilon})_{v,\epsilon}$
+%		of $\Omega_n$ are represent all choices of
+%		possible initial edges for the $T_{n,v}$'s: For each $v\in \overline{v}$
+%		and each $\epsilon\in [\Sigma_{r(v)}]$, $E_{n,v,\epsilon}$ selects
+%		$b_{v,\epsilon}$ possible initial edges of $T_{n,v}$
+%		with pattern $\epsilon$.\par
+%%	 	Given an element $O\in \Omega_n$, with
+%%	 	$O=\big(O_{i,\epsilon}\big)_{i\in [l], \epsilon \in [\Sigma_{r_i}]}$,
+%%	 	we write $O\in G_n$ if
+%		Using observation REF we obtain that
+%		\[
+%		\mathrm{E}\Big[\prod_{\substack{i\in [l]\\ \epsilon \in [\Sigma_{r_i}]}} \binom{X_{n,i,\epsilon}}{b_{i,\epsilon}}
+%		\Big]= \sum_{(E_{v,\epsilon})_{v,\epsilon} \in \Omega_n
+%		}		
+%		\Pr \left( \bigwedge_{\substack{v\in \overline{v} \\ \epsilon \in
+%		[\Sigma_{r(v)}]\\ (e,\chi) \in E_{v,\epsilon} }} \left( e\in E(T_{n,i}) 
+%		\bigwedge_{u\in V(e), u\neq v} Tr(T_{n,v};u)\in \chi(u)
+%		\right)  \right)
+%		\]
+%		Let $(E_{v,\epsilon})_{v,\epsilon}\in \Omega_n$. 
+%		In order for $e\in E(T_{n,v})$ to be possible for all
+%		$v\in \overline{v}$, $\epsilon\in [\Sigma_{r(v)}]$, 
+%		$e\in E_{v,\epsilon}$ it is needed that each vertex 
+%		in $[n]\setminus \overline{w}$ belongs at most to one
+%		edge $(e,\chi)\in \cup_{v,\epsilon} \, E_{v,\epsilon}$.
+%		This is because if for some 
+%		\[
+%		\bigwedge_{\substack{i\in [l]\\ \epsilon \in
+%		[\Sigma_{r_i}]\\ (e,\chi) \in O_{i,\epsilon} }} \left( e\in E(T_{n,i}) 
+%		\bigwedge_{v\in e, v\neq v_i} Tr(T_{n,i},v)\in \chi(v)
+%		\right) 
+%		\] 
+%		to be possible it is needed that each $v\in $
+
+Now, for the induction step we have to prove that 
+conditions (1) and (2) of \cref{thm:BigTrees} hold
+for any $r>0$, given that they hold for all
+$r^\prime < r$. Notice that (1) is, in fact, a particular
+case of (2). Proving only (2) would be the ``mathematically"
+reasonable way to proceed, but the proof of (2) does not contain
+any new ideas that do not appear in the proof of (1) and is, in turn,
+more convoluted notation-wise. In consequence we will offer the complete 
+proof of (1) and later give indications about what changes in the proof
+are necessary in order to show (2).
+
 	\begin{lemma}
 	Let $r\in \N$, $r>0$. Let $\mathcal{T}$ be a 
-	$\simeq_k$ class of trees with radii at most $r$.
+	$\sim_k$ class of trees with radii at most $r$.
 	Suppose that \cref{thm:BigTrees} holds
@@
 		the initial edges in $T_n$ whose $k$-pattern
-		is $\epsilon$. In other words, $X_{n,\epsilon}$ counts
+		is $\epsilon$. First we are going to show that for any
+		$(k,r)$-pattern $\epsilon$, the means $E[X_{n,\epsilon}]$
+		converge, as $n$ tends to infinity, to an expression in $M$.
+		Fix a $(k,r)$-pattern $\epsilon$. 
+		By definition $X_{n,\epsilon}$ counts
 		the colored edges $(e,\tau)\in Copies(\epsilon,[n],v)$ 
@@
 		\mathrm{E}\big[ X_{n,\epsilon} \big]
-		= \sum_{(e,\tau)\in Copies(\epsilon,[n];v)} \Pr
+		= \sum_{(e,\tau)\in Copies(\epsilon,[n];(v,\rho))} \Pr
 		\left(e\in E(T_n)
@@
 		in the RHS of last equation is the same for all 
-		$(e,\tau)\in Copies(\epsilon,[n],;v)$. Let
-		$(e,\tau)\in Copies(\epsilon,\N;v)$ be fixed. 
+		$(e,\tau)\in Copies(\epsilon,[n];(v,\rho))$. Let
+		$(e,\tau)\in Copies(\epsilon,\N;(v,\rho))$ be fixed. 
 		Using that 
-		$|Copies(\epsilon,[n],v)|=\frac{(n)_{|e|-1}}
+		$|Copies(\epsilon,[n];(v,\rho))|=\frac{(n)_{|e|-1}}
 		{|Aut(\epsilon)|}$ we obtain
@@
 		\left(e\in E(T_{n})
-		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_n, v; u)\in \tau(u) \right).
+		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } 
+		Tr(T_n, v; u)\in \tau(u) \right).
 		\]
@@
 		\left( e\in E(T_{n})
-		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_{n}, v; u)\in \tau(u) \, \Bigg| \,  e\in E(G_n) \right)
+		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } 
+		Tr(T_{n}, v; u)\in \tau(u) \, \Bigg| \,  e\in E(G_n) \right)
 		\end{align*}
-		Using REF and $\PR{e\in E(G_n)}=\frac{\beta_{R(e)}}{n^{|e|-1}}$, 
+		Because of \cref{cor:disjointtrees}, a.a.s if $e\in E(G_n)$
+		and $v\in V(e)$, then $e\in E(T_n)$. Also,
+		$\PR{e\in E(G_n)}=\frac{\beta_{R(e)}}{n^{|e|-1}}$. In consequence
 		the RHS of last equation is asymptotically equivalent
@@
 		\prod_{\substack{u\in V(e)\\ u\neq v} } \Pr\big[
-		r-1, \tau(u)\big].
-		\]
-		For each $\epsilon\in [(k,r)]$ we define $\mu_{r,\epsilon}$ 
+		r-1, \tau(u)\big],
+		\]
+		and the last expression belongs to $M$, as we wanted.\par
+
+		For each pattern $\epsilon\in P(k,r)$ we define $\mu_{r,\epsilon}$ 
 		as follows: let $(e,\tau)$ be a representative of $\epsilon$
@@
 		\]
-		Notice that $\mu_{r,\epsilon}$ depends only on $r$ and $\epsilon$
-		and it is an expression belonging to $M$. \par
+		Notice that $\mu_{r,\epsilon}$, besides belonging to $M$, 
+		depends only on $r$ and $\epsilon$. \par
 		We are going to prove that the variables $X_{n,\epsilon}$
@@
 		with mean values $\mu_{r,\epsilon}$ respectively. For
-		each $\epsilon\in [(k,r)]$ let $b_\epsilon\in \N$. We want 
+		each $\epsilon\in P(k,r)$ let $b_\epsilon\in \N$. We want 
 		to show that
@@
 		\left[
-		\prod_{\epsilon\in [(k,r)]} \binom{X_{n,\epsilon}}{b_\epsilon}	
+		\prod_{\epsilon\in P(k,r)} \binom{X_{n,\epsilon}}{b_\epsilon}	
 		\right]
-		= \prod_{\epsilon\in [(k,r)]} \frac{(\mu_{r,\epsilon})^
+		= \prod_{\epsilon\in P(k,r)} \frac{(\mu_{r,\epsilon})^
 		{b_\epsilon}}{b_\epsilon!}.	
@@
 		\Omega_n:=\left\{
-		(E_\epsilon)_{\epsilon\in [(k,r)]} \quad 
-		\Big | \quad \forall \epsilon\in [(k,r)] \quad
-		E_\epsilon\subset Copies(\epsilon,[n],v), 
+		(E_\epsilon)_{\epsilon\in P(k,r)} \quad 
+		\Big | \quad \forall \epsilon\in P(k,r) \quad
+		E_\epsilon\subset Copies(\epsilon,[n],(v,\rho)), 
 		\quad |E_\epsilon|=b_\epsilon	
@@
 		\]
+		We also define $\Omega_\N$ substituting writing $\N$
+		instead of $[n]$ in the definition of $\Omega_n$. 
 		Informally, elements of $\Omega_n$ represent choices of 
@@
 		pattern is $\epsilon$ for all $(k,r)$-patterns $\epsilon$. 	
-		Using observation REF we obtain
+		Using \cref{obs:binomialmean} we obtain
 		\[
@@
 		\left[
-		\prod_{\epsilon\in [(k,r)]} \binom{X_{n,\epsilon}}{b_\epsilon}	
+		\prod_{\epsilon\in P(k,r)} \binom{X_{n,\epsilon}}{b_\epsilon}	
 		\right]
@@
 		\sum_{
-		(E_\epsilon)_{\epsilon\in [(k,r)]}
+		(E_\epsilon)_{\epsilon\in P(k,r)}
 		\in \Omega_n}
@@
 		\bigwedge_{\substack{
-		\epsilon\in [(k,r)]\\
+		\epsilon\in P(k,r)\\
 		(e, \tau)\in E_{\epsilon}
@@
 		\]
-		We say that an element $(E_\epsilon)_{\epsilon\in [(k,r)]}$
+		We say that an element $(E_\epsilon)_{\epsilon\in P(k,r)}$
 		of $\Omega_n$ is \textbf{disjoint} each vertex 
 		$w\in [n]\setminus\{v\}$ belongs to at most one edge 
-		$(e,\tau)\in\bigcup_{\epsilon\in [(k,r)]} E_\epsilon$
+		$(e,\tau)\in\bigcup_{\epsilon\in P(k,r)} E_\epsilon$.
 		Notice that if we want the probability in the last sum to be greater 
-		than $0$ for a particular $(E_\epsilon)_{\epsilon\in [(k,r)]}
-		\in \Omega_n$ then necessarily $(E_\epsilon)_{\epsilon\in [(k,r)]}$
+		than $0$ for a particular $(E_\epsilon)_{\epsilon\in P(k,r)}
+		\in \Omega_n$ then necessarily $(E_\epsilon)_{\epsilon\in P(k,r)}$
 		is disjoint. 
 		Indeed, suppose that a vertex $w\in [n]\setminus \{v\}$ belongs to two different 
-		edges $(e_1, \tau_1),$ $(e_2,\tau_2)\in \bigcup_{\epsilon\in [(k,r)]} E_\epsilon$. 
-		In consequence $e_1$ and $e_2$ form a cycle, as they 
+		edges $(e_1, \tau_1),$ $(e_2,\tau_2)\in \bigcup_{\epsilon\in P(k,r)} E_\epsilon$. 
+		In consequence $e_1$ and $e_2$ form a cycle of diameter $1$, as they 
 		both contain $v$ and $w$. This implies that $e_1, e_2 \notin E(T_n)$.
@@
 		\sum_{
-			(E_\epsilon)_{\epsilon\in [(k,r)]}
+			(E_\epsilon)_{\epsilon\in P(k,r)}
 			\in \Omega_n^\prime}
@@
 		\bigwedge_{\substack{
-				\epsilon\in [(k,r)]\\
+				\epsilon\in P(k,r)\\
 				(e, \tau)\in E_{\epsilon}
@@
 		for all disjoint elements 
-		$(E_\epsilon)_{\epsilon\in [(k,r)]}$ the probability 
+		$(E_\epsilon)_{\epsilon\in P(k,r)}$ the probability 
 		in last sum is the same. In consequence, if we fix
-		$(E_\epsilon)_{\epsilon\in [(k,r)]}\in \Omega^\prime_\N$
+		$(E_\epsilon)_{\epsilon\in P(k,r)}\in \Omega^\prime_\N$
 		we obtain
@@
 		the vertices $u\in V(e)$ for all $e\in 
-		\bigcup_{\epsilon\in [(k,r)]} E_\epsilon$. Then, 
+		\bigcup_{\epsilon\in P(k,r)} E_\epsilon$. Then, 
 		for any $e\in 
-		\bigcup_{\epsilon\in [(k,r)]} E_\epsilon$ and any
+		\bigcup_{\epsilon\in P(k,r)} E_\epsilon$ and any
 		any $V(e)$ with $u\neq v$ it holds that
@@
 		\[
-		|\Omega_n^\prime|= (n)_{\sum_{\epsilon\in [(k,r)]} 
+		|\Omega_n^\prime|= (n)_{\sum_{\epsilon\in P(k,r)} 
 			(|\epsilon|-1)\cdot b_\epsilon}
-		\prod_{\epsilon\in [(k,r)]}
+		\prod_{\epsilon\in P(k,r)}
 		\frac{1}{b_\epsilon!} \cdot
@@
 		\]
-		Also, using REF
+		Because of \cref{cor:disjointtrees} a.a.s if $e\in E(G_n)$
+		and $v\in V(e)$, then $e\in E(T_n)$. In consequence:
 		\begin{align*}
@@
 		\bigwedge_{\substack{
-				\epsilon\in [(k,r)]\\
+				\epsilon\in P(k,r)\\
 				(e, \tau)\in E_{\epsilon}\\
@@
 		$ \bigwedge_{\substack{
-				\epsilon\in [(k,r)]\\
+				\epsilon\in P(k,r)\\
 				(e, \tau)\in E_{\epsilon}
@@
 	\[
-	\prod_{\epsilon\in [(k,r)]}
+	\prod_{\epsilon\in P(k,r)}
 	\left(\frac{\beta_{R(\epsilon)}}
 	{n^{|\epsilon|-1}}\right)^{b_\epsilon} \cdot
-	\prod_{\epsilon\in [(k,r)]} (\lambda_{r,\epsilon})^{b_\epsilon}.
+	\prod_{\epsilon\in P(k,r)} (\lambda_{r,\epsilon})^{b_\epsilon}.
 	\]
@@
 	\left[
-	\prod_{\epsilon\in [(k,r)]} \binom{X_{n,\epsilon}}{b_\epsilon}	
+	\prod_{\epsilon\in P(k,r)} \binom{X_{n,\epsilon}}{b_\epsilon}	
 	\right]
 	= \Ln  
-	\frac{(n)_{\sum_{\epsilon\in [(k,r)]}(|\epsilon|-1)\cdot b_\epsilon}}
-	{n^{\sum_{\epsilon\in [(k,r)]}(|\epsilon|-1)\cdot b_\epsilon}}
+	\frac{(n)_{\sum_{\epsilon\in P(k,r)}(|\epsilon|-1)\cdot b_\epsilon}}
+	{n^{\sum_{\epsilon\in P(k,r)}(|\epsilon|-1)\cdot b_\epsilon}}
 	\cdot
-	\prod_{\epsilon\in [(k,r)]}
+	\prod_{\epsilon\in P(k,r)}
 	\frac{1}{b_\epsilon!} \cdot
@@
 	(\lambda_{r,\epsilon})^{b_\epsilon}&\\
-	= \prod_{\epsilon\in [(k,r)]}
+	= \prod_{\epsilon\in P(k,r)}
 	\frac{\left( \mu_{r,\epsilon} \right)^
@@
 	as we wanted. In consequence, by \cref{thm:BrunSieve},
-	given $a_{\epsilon}\in \N$ for all $\epsilon\in [(k,r)]$
+	given $a_{\epsilon}\in \N$ for all $\epsilon\in P(k,r)$
 	it holds
@@
 	\Pr\left( 
-	\bigwedge_{\epsilon \in [(k,r)]} X_{n,\epsilon}=a_\epsilon
+	\bigwedge_{\epsilon \in P(k,r)} X_{n,\epsilon}=a_\epsilon
 	\right)=
-	\prod_{\epsilon\in [(k,r)]} e^{-\mu_{r,\epsilon}}
+	\prod_{\epsilon\in P(k,r)} e^{-\mu_{r,\epsilon}}
 	\frac{(\mu_{r,\epsilon})^{a_\epsilon}}{a_\epsilon!}.
 	\]
-	Notice that, because of the definition of $\simeq_k$, 
-	the event $T_n\in \mathcal{T}$ is equivalent to 
-	\[
-	\left(\bigwedge_{\epsilon \in E^1_\mathcal{T}}
-	X_{n,\epsilon}\geq k 
-	\right) \wedge \left(\bigwedge_{\epsilon \in E^2_\mathcal{T}}
-	X_{n,\epsilon}=a_\epsilon\right),
-	\]
-	for some partition $E^1_\mathcal{T}, E^2_\mathcal{T}$
-	of $[(k,r)]$ that only depends on $\mathcal{T}$ and some
-	natural numbers $a_\epsilon < k$ for each $\epsilon\in
-	E^2_\mathcal{T}$ that only depend on $\mathcal{T}$ as well. 
-	In consequence 
+%	Notice that, because of the definition of $\simeq_k$, 
+%	the event $T_n\in \mathcal{T}$ is equivalent to 
+%	\[
+%	\left(\bigwedge_{\epsilon \in E^1_\mathcal{T}}
+%	X_{n,\epsilon}\geq k 
+%	\right) \wedge \left(\bigwedge_{\epsilon \in E^2_\mathcal{T}}
+%	X_{n,\epsilon}=a_\epsilon\right),
+%	\]
+%	for some partition $E^1_\mathcal{T}, E^2_\mathcal{T}$
+%	of $P(k,r)$ that only depends on $\mathcal{T}$ and some
+%	natural numbers $a_\epsilon < k$ for each $\epsilon\in
+%	E^2_\mathcal{T}$ that only depend on $\mathcal{T}$ as well. 
+%	In consequence 
+	Finally, using \cref{obs:equivalenttrees} we get that for some
+	partition $E^1_\mathcal{T}, E^2_\mathcal{T}$ of $P(k,r)$ and 
+	some natural numbers $a_\epsilon<k$ for each 
+	$\epsilon\in E^2_\mathcal{T}$ it holds that
 	\[
@@
 	\left(
-	\prod_{\epsilon\in E^1_\mathcal{T}} \left( 1-\sum_{i=0}^{k-1}
-	e^{-\mu_{r,\epsilon}}
-	\frac{(\mu_{r,\epsilon})^i}{i!} \right)
+	\prod_{\epsilon\in E^1_\mathcal{T}} \mathrm{Poiss}_{\geq k}(\mu_{r,\epsilon}) 
 	\right)\cdot
@@
 	\prod_{\epsilon\in E^2_\mathcal{T}}
-	e^{-\mu_{r,\epsilon}}
-	\frac{(\mu_{r,\epsilon})^{a_{\epsilon}}}{a_\epsilon!} 
-	\right)
+	\mathrm{Poiss}_{a_\epsilon}(\mu_{r,\epsilon}) 
+	\right).
 	\]
@@
 
-	\section{Probabilities of cycles}
+	\subsection{Almost all graphs are (k,r)-rich}
+
+	\begin{theorem}\label{thm:rich}
+		Let $r\in \N$. Then a.a.s $G_n$ is $(k,r)$-rich.
+	\end{theorem}
+	\begin{proof}
+		Let $\Sigma$ be the set of all $\sim_k$-classes of rooted trees
+		with radii at most $r$. For each $\mathcal{T}\in \Sigma$
+		let $\overline{v}(\mathcal{T})\in (\N)_k$ be a $k$-tuple of 
+		vertices such that all the $\overline{v}(\mathcal{T})$'s are
+		disjoint. Given any $\overline{v}\in (N)_*$
+		event $\phi_n\big(\overline{v}(\mathcal{T})\big)$ as the event that
+		for any $v\in \overline{v}$, $N(v;r)\cup Core(G_n;r)\emptyset$ 
+		(thus $N(v;r)$ is a tree),
+		and that for any two $v_1,v_2\in \overline{v}$, 
+		$d^{G_n}(v_1,v_2)>2r+1$. For each $n\in \N$ let
+		\[
+		A_n:=\bigwedge_{\mathcal{T}\in \Sigma} 
+		\exists\,\, \overline{v}(\mathcal{T}) \in ([n])_k\,\,
+		 \left(
+		\phi_n(\overline{v}(\mathcal{T})) \bigwedge_{
+		v\in \overline{v}(\mathcal{T})} 
+		Tr\big(
+		G_n;\,\,v;\,\,r
+		\big)\in \mathcal{T}
+		\right).
+		\]
+		Then the event $A_n$ that $G_n$ is $(k,r)$-rich.
+		Indeed, suppose that $G_n$ satisfies
+		$A_n$. Let $\mathcal{T}\in \Sigma$ be a $\sim_k$ class and let 
+		$v_1,\dots,v_{k-1}\in [n]$ be any vertices in $G_n$. Then because of
+		$\phi_n(\overline{v}(\mathcal{T}))$ there is at least
+		one vertex $v\in \overline{v}(\mathcal{T})$ such that $d(v,v_i)\geq 2r+1$
+		for all $v_i$'s. It also holds that $T:=N(v;r)$ is a tree, and because of
+		$A_n$, $(T,v)\in \mathcal{T}$. In consequence $G_n$ is $(k,r)$-rich.\par
+		Now we show that $\Ln \PR{A_n}=1$. For that we will prove that for
+		each $\mathcal{T}\in \Sigma$, a.a.s. the following event holds:
+		\[
+		B_{n,\mathcal{T}}:=
+		\exists\,\, \overline{v}(\mathcal{T}) \in ([n])_k\,\,
+		\left(
+		\phi_n(\overline{v}(\mathcal{T})) \bigwedge_{
+			v\in \overline{v}(\mathcal{T})} 
+		Tr\big(
+		G_n;\,\,v;\,\,r
+		\big)\in \mathcal{T}
+		\right).
+		\]
+		Fix $\mathcal{T}\in \Sigma$ and fix $\epsilon>0$ an arbitrarily 
+		small real number. Let $m\in \N$,
+		and let $\overline{v}\in (\N)_m$ be a $m$-tuple of vertices. Let 
+		$X_{n,\overline{v}}$ be the random variable that counts the number of 
+		vertices $v\in \overline{v}$ such that $\mathrm{Tr}(G_n;\,\,v;\,\,r)$
+		belongs to $\mathcal{T}$. Because of \cref{thm:BigTrees}, $X_{n,\mathcal{v}}$
+		converges in distribution to a binomial variable with parameters $m$ and
+		$\Pr[r, \mathcal{T}]$. That is, for each $l\in [m]$,
+		\[
+		\Ln \PR{X_{n,\overline{v}}=l}= \binom{m}{l} \Pr[r, \mathcal{T}]^l \cdot \left(
+		1-\Pr[r,\mathcal{T}]\right)^{m-l}.
+		\]		    
+		In particular, as $\Pr[r, \mathcal{T}]$ is greater than zero, for $m$ sufficiently
+		big it holds that
+		\[
+		\Ln \PR{X_{n,\overline{v}}\geq k}> 1- \epsilon.
+		\]
+		Also, because of \cref{cor:disjointtrees} we have that $\Ln \phi_n(\overline{v})=1$,
+		and in consequence for $m$ sufficiently big
+		\[
+		\Ln \Pr\left(
+		(X_{n,\overline{v}}\geq k)
+		\wedge \phi(\overline{v})
+		\right)> 1- \epsilon.
+		\]
+		As $(X_{n,\overline{v}}\geq k)
+		\wedge \phi(\overline{v})$ implies $B_{n,\mathcal{T}}$ we have that
+		$\Ln \PR{B_{n,\mathcal{T}}}=1$. As this holds for all $\mathcal{T}\in \Sigma$
+		and $\Sigma$ is a finite set, then $\Ln \PR{A_n}=1$ as well and the result follows. 
+	\end{proof}
+
+	\subsection{Probabilities of cycles}
 
@@
 	of possible cycles over $[n]$ whose $(k,r)$-type is $O$, for each
-	$(k,r)$ type $O$. Using observation REF we obtain
+	$(k,r)$-cycle $O$. Using observation \cref{obs:binomialmean} we obtain
 	\[
@@
 \[
-G_n \text{ is $r$-simple } \wedge
+G_n \text{ is $r$-sparse } \wedge
 \left(
@@
  \Pr \left(
- G_n \text{ is $r$-simple } \wedge
+ G_n \text{ is $r$-sparse } \wedge
  \left(
@@
 \end{align*}
-Because of \cref{thm:simple}, last limit equals
+Because of \cref{thm:sparse}, last limit equals
 \begin{align*}
@@
 	\[
-	\overline{\beta}:=(\beta_R)_{R\in \sigma} \mapsto
+	\{\beta_R\}_{R\in \sigma} \mapsto
 	\Ln \Pr \left(
-	G_n(\overline{\beta}) \models \phi
+	G_n\left(\{\beta_R\}_{R\in \sigma}\right) \models \phi
 	\right)
@@
 	Let $k$ be the quantifier rank of $\phi$ and
-	let $r=3^k$. Using \cref{thm:simple} we obtain
+	let $r=3^k$. Let 
+	$G_n:=G_n\left(\{\beta_R\}_{R\in \sigma}\right)$.
+	Using \cref{cor:simple} we obtain
 	\[
 	\Ln \Pr \left(
-	G_n(\overline{\beta}) \models \phi
+	G_n \models \phi
 	\right)=
 	\Ln \Pr \left(
-	G_n(\overline{\beta}) \models \phi
+	G_n\models \phi
 	\, \Big|
-	\, G_n(\overline{\beta})
-	\text{ is $r$-simple}
+	\, G_n
+	\text{ is $r$-sparse}
 	\right).
 	\]
-	Let $S$ be the set of simple $k$-agreeability classes. 
-	Then the LHS of last equation equals
-	\[
+	Let $\Sigma$ be the set of $(k,r)$-agreeability classes of 
+	$(k,r)$-simple hypergraphs. 
+	Then
+	\begin{equation} \label{eq:aux1}
+	\Ln \Pr \left(
+	G_n \models \phi
+	\right)=
 	\Ln
-	\sum_{\mathcal{O}\in S} \Pr\left(
-	G_n(\overline{\beta})\in \mathcal{O}
+	\sum_{\mathcal{O}\in \Sigma} \Pr\left(
+	G_n\in \mathcal{O}
 	\right) \cdot 
 	\Pr\left(
-	G_n(\overline{\beta})\models \phi \,
+	G_n\models \phi \,
 	\Big| \,
-	G_n(\overline{\beta})\in \mathcal{O}
+	G_n\in \mathcal{O}
 	\right).
-	\]
-	Notice that, because the set $S$ is finite, 
-	this is the limit of a finite sum. Also, 
-	using REF, we obtain that for any $\mathcal{O}\in S$
+	\end{equation}
+	Notice that, because the set $\Sigma$ is finite, 
+	this is the limit of a finite sum and we can exchange
+	summation and limit. Also, 
+	using \cref{thm:rich}, we obtain that for any $\mathcal{O}\in \Sigma$
 	it holds
@@
 	\Ln \Pr\left(
-	G_n(\overline{\beta})\models \phi \,
+	G_n\models \phi \,
 	\Big| \,
-	G_n(\overline{\beta})\in \mathcal{O}
-	\right) = 0 \textrm{ or } 1.
+	G_n\in \mathcal{O}
+	\right) = 
+		\Ln \Pr\left(
+	G_n\models \phi \,
+	\Big| \,
+	G_n\in \mathcal{O}
+ 	\text{ and } G_n \text{ 
+	is $(k,r)$-rich} 	\right)	
 	\]

### 2020-05-03 ArticleAcortado.tex
Acortar

--- 2020-04-29 Articlebackup.tex
@@
 \newcommand{\InR}[1]{\left\{ #1_R \right\}_{R\in \sigma}}
+\newcommand{\sep}{\noindent\rule{2cm}{0.4pt}}
+\newcommand{\aut}{\mathrm{aut}}
+\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
 
@@
 
+\todo[inline]{INCOMPLETA, PENDIENTE DE SER REVISADA}
 Since the work of Erd\"os and R\`enyi on the evolution of random graphs
@@
 subsets of $S$ whose size is $k$. \par
-Given numbers, $n,m\in \N$ with $m\leq n$ we define
-$(n)_m:=n\cdot (n-1)\cdots (n-m+1)$. Given a set
+Given numbers, $n,m\in \N$ with $m\leq n$ we denote by
+$(n)_m$ the $m$-th falling factorial of $n$. \par
+Given a set
 $S$ and a number $n\in \N$ with $n\leq |S|$ we define
@@
 We also define $S^*:=\bigcup_{n=0}^\infty S^n$ and
-$(S)_*=\bigcup_{n\leq |S|} (S)_n$. Given a tuple 
+$(S)_*:=\bigcup_{n\leq |S|} (S)_n$. 
+Given two tuples $\overline{x},\overline{y}\in S^*$
+we write $\overline{x}^\smallfrown \overline{y}$ to denote their 
+concatenation. Given a tuple 
 $\overline{x}\in S^*$ and an element $x\in S$ the expression
@@
 treat the tuple $\overline{x}$
-as the set of elements $x\in \overline{x}$. \par
+as the set of elements $x\in \overline{x}$. 
 We will use the convention that over-lined variables
 , like $\overline{x}$, denote ordered tuples of arbitrary length.
-For example, given a set $S$, if we write $\overline{x}\in S^*$
-then $\overline{x}=(x_1,\dots, x_a)$ for some $a\in \N$ and 
-some $x_1,\dots, x_a\in S$. Given an ordered tuple $\overline{x}$
+Given an ordered tuple $\overline{x}$
 we define the number $len(\overline{x})$ as its length. 
@@
 $S^a$ in the following way: Given $g\in \Phi$ and
-$\overline{x}=(x_1,\dots,x_a)\in S^a$ we define 
-$g\cdot(x_1,\dots,x_a)$ and $g\cdot \overline{x}$ 
+$\overline{x}:=(x_1,\dots,x_a)\in S^a$ we define 
+$g\cdot \overline{x}$ 
 as the tuple $(x_{g(1)},\dots,x_{g(a)})$. 
@@
 and it should either be clear from context or not be relevant.\par
-\par
+
 Given two real functions over the natural numbers 
@@
 such that $f(n)\leq Cg(n)$ for $n$ sufficiently large, 
-as usual.
-If $g(n)\neq 0$ for $n$ large enough then
-we will write $f\sim g$ when $\Ln \frac{f(n)}{g(n)}=1$.\par
-
-\todo[inline]{Añadir referencias y trabajo relacionado con random SAT}
+as usual. We will write $f=\Theta(g)$ if both $f=O(g)$ and
+$g=O(f)$. If $g(n)\neq 0$ for $n$ large enough then
+we will write $f\sim g$ when $\Ln \frac{f(n)}{g(n)}=1$.
+
+%\todo[inline]{Añadir referencias y trabajo relacionado con random SAT}
 
 \subsection{Logical preliminaries}
-We will assume a certain degree of familiarity with the 
-concepts. For a more complete exposition of the topics 
-presented here one can consult \cite{ebbinghaus2013mathematical}.
-
-A relational vocabulary $\sigma$ is a collection of
-relation symbols $\{R_1,\dots, R_m,\dots\}$
-where each relation symbol $R_i$ has associated a natural
-number $ar(R_i)$ called its arity.
-A $\sigma$-structure $\mathfrak{A}$ is composed of
-a set $A$, called the universe of $\mathfrak{A}$, equipped with
-relations $R_1^{\mathfrak{A}}\subseteq A^{a_1},
-\dots, R_m^{\mathfrak{A}}\subseteq A^{a_m}$. When $\sigma$
-is understood we may refer to $\sigma$-structures as relational
-structures or simply as structures.
-A structure is called finite if its universe is a finite set. \par
-
-In the first order language $FO[\sigma]$ with signature $\sigma$ 
-formulas are formed by variables $x_1,\dots,$ $x_i,\dots$,
-the relation symbols in $\sigma$, the equal symbol $=$,
-the usual Boolean connectives $\neg, \wedge, \vee, \dots$, 
-the existential and universal quantifiers $\exists, \forall$, and
-the parentheses $),($. Then formulas in $FO[\sigma]$ are defined as 
-follows.
-\vspace*{-0.2em}
-\begin{itemize}[topsep=1pt, itemsep=1pt]
-	\item The expression $R(y_1,\dots,y_a)$, where the $y_i$'s are variables and $R$
-	is a relation symbol in $\sigma$ such that $ar(R)=a$,
-	belongs to $FO[\sigma]$.
-	\item The expression $y_1=y_2$, where $y_1, y_2$ are variables, 
-	belongs to $FO[\sigma]$.
-	\item Given formulas $\phi, \psi \in FO[\sigma]$, any Boolean combination of them
-	$\neg(\phi), (\phi \wedge \psi), (\phi \vee \psi), \dots$ belongs to $FO[\sigma]$ as well.
-	\item Given a formula $\phi \in FO[\sigma]$ and $x$ a variable that 
-	does not appear bounded
-	by a quantifier in $\phi$, the expressions $\forall x (\phi)$ and 
-	$\exists x (\phi)$ belong both to $FO[\sigma]$. 
-\end{itemize}  
-We will write $\forall y_1, y_2,\dots, y_m$ or simply $\forall \overline{y}$
-instead of  
-$\forall y_1, \forall y_2,\dots, \forall y_m$ and likewise for
-the quantifier $\exists$. Also, if $\overline{y}:=(y_1,\dots,y_a)$ is a
-tuple of variables we may write simply $R(\overline{y})$ instead
-of $R(y_1\dots,y_a)$.\par
-For the remaining of this article we will reserve the names $x,y,z$
-for the variables in our first order formulas.\par
-We define the set of free variables of a formula as usual. 
+We assume familiarity with first order logic (FO). We follow 
+the convention that first order logic contains the equality symbol. 
+Given a vocabulary $\sigma$ we will denote by $FO[\sigma]$ the set of 
+first order formulas of vocabulary $\sigma$. We define the set of 
+\textbf{free variables} of a formula as usual. 
+Given a relation symbol $R\in \sigma$ we denote by $ar(R)$ the arity of $R$. 
 Given a formula $\phi\in FO[\sigma]$ we will use the notation $\phi(\overline{y})$ 
@@
 none of its bounded variables, although it may contain variables
-which not appear in $\phi$. \par
-Formulas with no free variables are called sentences and 
-formulas with no quantifiers are called open formulas. \par
-The quantifier rank of a formula $\phi$, denoted by $qr(\phi)$, 
-is defined as the maximum number of nested quantifiers in $\phi$. \par
-Sentences in $FO[\sigma]$ are interpreted over $\sigma$-structures
-in the natural way. Given an structure $\mathcal{A}$, and a sentence
-$\phi\in FO[\sigma]$ we write $\mathcal{A} \models \phi$ to denote 
-that $\mathcal{A}$ satisfies $\phi$. If $\psi(\overline{y})$ is a
-formula, $\overline{a}$ are elements in the universe of 
-$\mathcal{A}$, and $\overline{y}$ and $\overline{a}$ are lists of the same size,
-then we write $\mathcal{A} \models 
-\psi(\overline{a})$
-to mean that $\mathcal{A}$ satisfies $\psi$ when the free variables in
-$\overline{y}$ are interpreted as the elements in $\overline{a}$ (i.e., 
-the $i$-th element of $\overline{y}$ is interpreted as the $i$-th
-element of $\overline{a}$).
-
-\subsection{Structures as multi-hypergraphs}
+which not appear in $\phi$.
+Formulas with no free variables are called \textbf{sentences} and 
+formulas with no quantifiers are called \textbf{open formulas}.
+
+\subsection{Structures as multi-hypergraphs} \label{sect:structures}
 
@@
 \begin{itemize}
-	\item A relational vocabulary $\sigma$ such that all the relations $R\in\sigma$ satisfy $ar(R)\geq 2$. 
+	\item A relational vocabulary $\sigma$ such 
+	that all the relations $R\in\sigma$ satisfy $ar(R)\geq 2$. 
 	\item 
@@
 \end{itemize}
-
-We will only consider relational structures where the relations
-are of arity at least two. This restriction is not necessary, but 
-it makes notation easier. 
-\todo[inline]{Quiz\'as deber\'ia a\~nadir un anexo dando alguna indicaci\'on sobre c\'omo tratar las relaciones unarias?}
+%
+%We will only consider relational structures where the relations
+%are of arity at least two. We claim that it is also possible to prove
+%our results for structures that include unary relations but we will refrain from
+%doing so because it would add unnecessary complexity to our proofs. \par
 
@@
 We can think any structure $G$ in $\mathcal{C}$
-as a "multi-hypergraph" whose vertices are the elements
+as a ``multi-hypergraph" whose vertices are the elements
 of the universe of $G$. Each relation $R\in \sigma$, can be 
-represented over $G$ as an "edge set" formed by tuples vertices
-of size $ar(R)$ modulo the action of $\Phi_R$. Furthermore, 
+represented over $G$ as an ``edge set" formed by tuples vertices
+of size $ar(R)$ modulo the permutations in $\Phi_R$. Furthermore, 
 repetitions of vertices in the positions given by
 $P_R$ are not allowed in these tuples.\par
-The following definitions make this ideas formal. They 
-depend on our choices of $\sigma$, $\{\phi_R\}_{R\in \sigma}$
-and $\{P_R\}_{R\in \sigma}$ but as those are fixed we can
-allow ourselves to omit those dependencies for the sake of readability.
+The following definitions make this ideas formal. Notice that they 
+depend on our fixed choice of $\sigma$, $\{\phi_R\}_{R\in \sigma}$
+and $\{P_R\}_{R\in \sigma}$.
 
@@
 in the following way: 
-given $G=(V,\{E_R\}_{R\in \sigma})$,
-we consider $V$ to be the universe of
- $G$, and for any $R\in \sigma$ we define
-$R^G\subseteq V^{ar(R)}$ as the set of tuples
+given an hypergraph $G:=(V,\{E_R\}_{R\in \sigma})$,
+we can construct a $\sigma$-structure $\mathcal{G}$ whose universe is
+$V$, and for any $R\in \sigma$ we define
+$R^\mathcal{G}\subseteq V^{ar(R)}$ as the set of tuples
 $\overline{x}\in V^{ar(R)}$ such that
-$[\overline{x}]\in E_R$. Under 
-this interpretation hypergraphs
-satisfy by definition the 
+$[\overline{x}]\in E_R$. Clearly $\mathcal{G}$
+satisfies by definition the 
 symmetry and anti-reflexivity
-axioms given at the beginning of this section. It is also easy to
-see that this interpretation induces
+axioms given at the beginning of this section. It is easy to
+see that this process induces
 a one-to-one identification between 
@@
 the $E_R(G)$'s will be called an \textbf{edge set} and its elements, 
-\textbf{edges}. Given an edge set $E_R(G)$, 
-the index $R$ will be called its \textbf{relation}.
+\textbf{edges}. Given an edge, $e\in V(G)$ we will denote by $V(e)$
+the set of all vertices that participate in $e$.
 
@@
 $V(H)=U$ and for any $R\in \sigma$ 
-each edge $e\in E_R(G)$ belongs 
-to $E_R(H)$ as well if and only if the vertices
-involved in $e$ are in $U$ (i.e. $e\in E_R[U]$).
+an edge $e\in E_R(G)$ belongs 
+to $E_R(H)$ if and only if $V(e)\subset U$.
 \par
@@
 %It is satisfied that the number
-%of labeled copies of $H$ in $G$ is $|Aut(H)|$ times the number
+%of labeled copies of $H$ in $G$ is $\aut(H)$ times the number
 %of copies of $H$ in $G$.
@@
 minus its number of vertices. \par
-
+An hypergraph $G$ is \textbf{connected} if for any two vertices $v,u\in V(G)$
+there is a sequence of edges $e_1,\dots, e_m\in E(G)$ such that
+$v\in V(e_1), u\in V(e_m)$ and for each $i\in [m-1]$, 
+$V(e_i)\cap V(e_{i+1})\neq \emptyset$. It holds that
+$ex(G)\geq -1$ for any connected hypergraph.
+\par Given a connected hypergraph $G$ 
+and vertices $v,u\in V(G)$, we say that $G$ is
+a \textbf{path} between $v$ and $u$
+if $G$ 
+does not contain any connected proper sub-hypergraph containing both $v,u$.
+\par
+A connected hypergraph $G$ is a \textbf{tree} if $ex(G)=-1$. 
+\par A connected hypergraph $G$ is called \textbf{dense} if $ex(G)>0$.\par
+A connected hypergraph $G$ with $ex(G)\geq 0$ is called \textbf{saturated} 
+if for any non-empty proper sub-hypergraph
+$H\subset G$ it holds $ex(H)<ex(G)$.
+% It is satisfied that any connected hypergraph $G$
+%with $ex(G)\geq 0$ contains a unique saturated sub-hypergraph $H$ with $ex(H)=ex(G)$.
+\par
+A connected hypergraph $G$ with $ex(G)=0$ is called \textbf{unicycle}. 
+A saturated unicycle is called a \textbf{cycle}. \par
 Given an hypergraph $G$ we define the following metric, $d$, over $V(G)$:
@@
 such that for any $R\in \sigma$, a tuple $\overline{v}\in V(H_1)^*$
-forms an edge $[\overline{v}]\in E_\sigma(H_1)$ if and only
-if $[f(\overline{v})]\in E_\sigma(H_2)$. We say that $H_1$ and
+forms an edge $[\overline{v}]\in E_R(H_1)$ if and only
+if $[f(\overline{v})]\in E_R(H_2)$. We say that $H_1$ and
 $H_2$ are isomorphic, written as $H_1\simeq H_2$, if there exists
@@
 is an isomorphism from $H$ to itself. We will denote by
-$Aut(H)$ the group of such automorphisms. \par
-
-Let $H^\simeq$ be an isomorphism class of hypergraphs. Let
-$H\in H^\simeq$ be a representative of the class. 
-Then we define $ex(H^\simeq)$ as $ex(H)$. Clearly this definition
+$\aut(H)$ the number of such automorphisms. \par
+
+Let, $\mathbb{H}$ be an isomorphism class of hypergraphs. Let
+$H\in \mathbb{H}$ be a representative of the class. 
+Then we define $ex(\mathbb{H})$ as $ex(H)$. Clearly this definition
 does not depend on the choice of $H$. The expressions
-$|Aut(H^\simeq)|$,
-$|V(H^\simeq)|$, $|E(H^\simeq)|$ or
-$|E_R(H^\simeq)|$ for $R\in \sigma$ are defined 
+$\aut(\mathbb{H})$,
+$|V(\mathbb{H})|$, $|E(\mathbb{H})|$ or
+$|E_R(\mathbb{H})|$ for $R\in \sigma$ are defined 
 in an analogous way.\par
@@
 $V(H^\prime)\subset V$ and $H\simeq H^\prime$. Analogously, if
-$H^\simeq$ is an isomorphism class of hypergraphs we define
-$Copies(H^\simeq,V)$ as the set of hypergraphs $H^\prime$ 
+$\mathbb{H}$ is an isomorphism class of hypergraphs we define
+$Copies(\mathbb{H},V)$ as the set of hypergraphs $H^\prime$ 
 that satisfy
-$V(H^\prime)\subset V$ as well as $H^\prime \in H^\simeq$.   \par
+$V(H^\prime)\subset V$ as well as $H^\prime \in \mathbb{H}$.   \par
 
@@
 
-\begin{definition}
+\begin{definition} \label{def:color}
 	Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
@@
 	We say that $(H_1,\chi_1)$ is isomorphic to $(H_2,\chi_2)$,
-	written as $(H_1, chi_1)\simeq (H_2,\chi_2)$, if there exists an
+	written as $(H_1, \chi_1)\simeq (H_2,\chi_2)$, if there exists an
 	isomorphism between them.
@@
 	isomorphism from it into itself. We will denote
-	by $Aut(H,\chi)$ the group of such automorphisms. 
+	by $\aut(H,\chi)$ the number of such automorphisms. 
 	\par
-	As with the case of hypergraphs, if $H^\simeq$ is 
+	As with the case of hypergraphs, if $\mathbb{H}$ is 
 	an isomorphism class of $\Sigma$-hypergraphs
-	then the expressions $|Aut(H^\simeq)|$ and
-	$|V(H^\simeq)|$ are defined via representatives. \par
+	then the expressions $\aut(\mathbb{H})$ and
+	$|V(\mathbb{H})|$ are defined via representatives. \par
 	Let $(H,\chi)$ be a $\Sigma$-hypergraph and let $V$ be a set.
@@
 	$(H^\prime,\chi^\prime)$ satisfying $V(H^\prime)\subset V$ and
-	$(H,\chi)\simeq (H^\prime,\chi^\prime)$. Let $H^\simeq$ be 
+	$(H,\chi)\simeq (H^\prime,\chi^\prime)$. Let $\mathbb{H}$ be 
 	an isomorphism class of $\Sigma$-hypergraphs. Then the set
-	$Copies(H^\simeq, V)$ is defined$\Sigma$-hypergraphs
+	$Copies(\mathbb{H}, V)$ is defined as the set of $\Sigma$-hypergraphs
 	$(H^\prime,\chi^\prime)$ such that 
 	$V(H^\prime)\subset V$ and
-	$(H^\prime,\chi^\prime)\in H^\simeq$. 
+	$(H^\prime,\chi^\prime)\in \mathbb{H}$. 
 	Let $v\in V$ and $s\in \Sigma$. We define the
-	set $Copies\big(H^\simeq, V;\,\, (v,s)\big)$ 
+	set $Copies\big(\mathbb{H}, V;\,\, (v,s)\big)$ 
 	as the set of $\Sigma$-hypergraphs
-	$(H^\prime,\chi^\prime)\in Copies(H^\simeq, V)$
+	$(H^\prime,\chi^\prime)\in Copies(\mathbb{H}, V)$
 	that satisfy $v\in V(H^\prime)$ as well as
@@
 
-\subsection{The random model}
+\subsection{The random model} \label{sect:random}
 
@@
 $p_R$ be a real number between zero and one.
-Let $\overline{p}:=\InR{p}$.
-The random model $G^{\mathcal{C}}(n,\overline{p})$ 
+The random model $G^{\mathcal{C}}\Big(n,\InR{p}\Big)$ 
 is the discrete probability space that
@@
 assigning to each edge $e\in E_R[n]$ probability 
-$p_R$ independently. \par
+$p_R$ independently for each $R\in \sigma$. \par
 
@@
 "sparse regime" of $G^\mathcal{C}(n,\overline{p})$, were the 
-expected number of edges each color is linear. 
+expected number of edges each sort is linear. 
 %In other words, we want that
@@
 of the form $\beta_R/n^{ar(R)-1}$ for some 
-non-negative real numbers $\InR{\beta}$.
+positive real numbers $\InR{\beta}$.
 From now on we will write $G_n\left(\InR{\beta}\right)$
@@
 Our goal is to prove the following theorem:
-%is to prove that for any sentence $\phi\in FO[\sigma]$,
-%the limit 
-%\[\Ln \mathrm{Pr}(G^\mathcal{C}(n,\overline{p}
-%(n,\overline{\beta})) \models \phi)\] 
-%is well defined and varies 
-%analytically with $\overline{\beta}$.
-% Some care is needed
-%in order to formulate this precisely, as there are some values
-%of $\overline{\beta}$ for which $\overline{p}
-%(n,\overline{\beta})$ asymptotically does not 
-%define a list of 
-%proper probabilities. 
-%Indeed, suppose that some relation
-%symbol $R_i$ in $\sigma$ is unary. 
-%Then, by definition $a_i=1$ and
-%the expression $\beta_i/n^{a_i-1}$ 
-%equals $\beta_i$. 
-%In consequence, if we assign 
-%values to $\overline{\beta}$ and let
-%$\beta_i>1$ then the random 
-%model $G^\mathcal{C}(n,\overline{p}
-%(n,\overline{\beta})$ will not be well defined. 
-%To avoid this we need to impose $\beta_i\in [0,1]$ 
-%for all the $i$'s such that $a_i=1$. \par
-%For the sake of convenience we will adopt the convention
-%that the unary relation symbols among $R_1,\dots,R_t$ 
-%are the first ones, and we will denote by $t_u$ the 
-%(possibly zero) number of such relations. 
-%Thus $a_1= a_2 =\dots= a_{t_0}=1$, and $a_i>1$ 
-%for $i>t_0$. Now we are in conditions of stating our main 
-%theorem:
 
@@
 
-Let $G^1$ and $G^2$ be hypergraphs. We define the $k$ round 
-Ehrenfeucht-Fraisse game on $G^1$ and $G^2$, denoted by
-$\ehr_k(G^1;G^2)$, as follows:
+A more complete introduction to the subject can be found in
+\cite[Section 2]{finitemodeltheory1}, for example.\par
+
+Let $H_1$ and $H_2$ be hypergraphs. We define the $k$ round 
+Ehrenfeucht-Fraisse (EF) game on $H_1$ and $H_2$, denoted by
+$\ehr_k(H_1;H_2)$, as follows:
 The game is played between two players, Spoiler and Duplicator, and
-the number of rounds, $k$, is known for both from the start.
+the number of rounds $k$ is known for both from the start.
 At the beginning of each round Spoiler chooses a vertex from either
-$V(G^1)$ or $V(G^2)$ and Duplicator responds by choosing a vertex
+$V(H_1)$ or $V(H_2)$ and Duplicator responds by choosing a vertex
 from the other set.
 Let us denote by 
-$v_i$, resp. $u_i$ the vertex from $G^1$, resp. from $G^2$, 
+$v_i$, resp. $u_i$ the vertex from $H_1$, resp. from $H_2$, 
 chosen in the $i$-th round,
@@
 	and indices $i_1,\dots, i_{ar(R)} \in [k]$, 
-	$[v_{i_1},\dots,v_{i_{ar(R)}}] \in E_R(G^1) \iff 
+	$[v_{i_1},\dots,v_{i_{ar(R)}}] \in E_R(H_1) \iff 
 	[u_{i_1},\dots,u_{i_{ar(R)}}]
-	\in E_R(G^2)$.
+	\in E_R(H_2)$.
 
 \end{itemize}
-
-We define the equivalence relation $=_k$ between hypergraphs as follows:
-We say that $G^1=_k G^2$ if for any sentence $\phi\in 
-FO[\sigma]$ with $qr(\phi)\leq k$ then ``$G^1\models\phi$ if and 
-only if $G^2\models\phi$". 
-\par
 
@@
 	[Ehrenfeut, \citealp{ehrenfeucht1961application}] Let
-	$G^1$ and $G^2$ be hypergraphs.
-	Then Duplicator wins $\ehr_k(G^1;G^2)$
-	if and only if $G^1=_k G^2$.	
+	$H_1$ and $H_2$ be hypergraphs.
+	Then Duplicator wins $\ehr_k(H_1;H_2)$
+	if and only if $H_1$ and $H_2$ satisfy the same 
+	sentences $\phi\in FO[\sigma]$ with $qr(\phi)\leq k$.		
 \end{theorem}
 
-Let $\overline{v}\in V(G^1)^*$, and 
-$\overline{u}\in V(G^2)^*$ be lists of vertices of the same length, 
+Let $\overline{v}\in V(H_1)^*$, and 
+$\overline{u}\in V(H_2)^*$ be lists of vertices of the same length, 
 $l=len(\overline{v})=len(\overline{u})$. We define the $k$ round 
-Ehrenfeucht-Fraisse game on $G^1$ and $G^2$ with initial position given
-by $\overline{v}$ and $\overline{u}$, denoted by $\ehr_k(G^1,\overline{v};G^2,\overline{u})$,
-the same way as $\ehr_k(G^1;G^2)$, but in this case the game has $l$ extra 
+Ehrenfeucht-Fraisse game on $H_1$ and $H_2$ with initial position given
+by $\overline{v}$ and $\overline{u}$, denoted by $\ehr_k(H_1,\overline{v};H_2,\overline{u})$,
+the same way as $\ehr_k(H_1;H_2)$, but in this case the game has $l$ extra 
 rounds at the beginning where the vertices in $\overline{v}$ and $\overline{u}$ are 
@@
 We also define the $k$-round distance Ehrenfeucht-Fraisse game on 
-$G^1$ and $G^2$, denoted by $d\ehr_k(G^1;G^2)$, the same way as
-$\ehr_k(G^1;G^2)$, but now, in order for Duplicator to win the
+$H_1$ and $H_2$, denoted by $d\ehr_k(H_1;H_2)$, the same way as
+$\ehr_k(H_1;H_2)$, but now, in order for Duplicator to win the
 game, the following additional condition has to be satisfied 
@@
 \begin{itemize}
-	\item For any $i,j\in [k]$, $d^{G^1}(v_i,v_j)=d^{G^2}(u_i,u_j)$.
+	\item For any $i,j\in [k]$, $d^{H_1}(v_i,v_j)=d^{H_2}(u_i,u_j)$.
 \end{itemize}
 
-Given $\overline{v}\in V(G^1)^*$, and $\overline{u}\in V(G^2)^*$
+Given $\overline{v}\in V(H_1)^*$, and $\overline{u}\in V(H_2)^*$
 lists of vertices of the same length,
 we define the game 
-$d\ehr_k(G^1,\overline{v};G^2,\overline{u})$ analogously to 
-$\ehr_k(G^1,\overline{v};G^2,\overline{u})$.
+$d\ehr_k(H_1,\overline{v};H_2,\overline{u})$ analogously to 
+$\ehr_k(H_1,\overline{v};H_2,\overline{u})$.
 
@@
 
-We show now an outline of the proof. \par 
-We show that for any quantifier rank $k$ there are some classes of
-hypergraphs 
-$C^k_1,\dots, C^k_{n_k}$ such that
-\begin{itemize}[noitemsep, topsep=0pt]
-	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
-	\item[(2)] a.a.s. any random graph belongs to some of them, and
-	\item[(3)] the limit probability of random graph belonging to 
-	any of them is an analytic expression on the parameters $\overline{\beta}$. 
+We show now an outline of the proof of \cref{thm:main}. \par 
+In essence the arguments mirror the ones in the proof of theorem 2.1
+in \cite{lynch1992probabilities}, adapted to fit our context. Fix $r\in \N$.
+The following facts hold:
+\begin{itemize}
+	\item A.a.s $G_n$ does not contain any dense hypergraph of diameter at most 
+	$2r+1$ (\cref{thm:sparse}). In consequence, all $r$-neighborhoods in $G_n$
+	a.a.s are either trees or unicycles.
+	\item Given any fixed vertices $v_1,\dots, v_m\in\N$, a.a.s 
+	$d(v_i,v_j)>2r+1$ for any two $v_i,v_j$ and a.a.s all the $N(v_i;r)$'s 
+	are trees (\cref{lem:disjointtrees}).
 \end{itemize} 
-
-After this is archived the theorem follows easily.
-
-The objective of next sections will be to define the classes 
-$C_1,\dots, C_{n_k}$ and to show that they satisfy properties (1), (2) and (3).
-
-\todo[inline]{Explicar esto mejor}
-
-\section{Some winning strategies for Duplicator}
-
-The aim of this section is to show the winning strategy
-for Duplicator that is going to be used in our proofs. \par
-
-Let $G^1$ and $G^2$ be hypergraphs, and let
-$V_1:=V(G^1), V_2:=V(G^2)$.
+For any given $k\in \N$, we define an equivalence relation $\sim_k$ for 
+hypergraphs (\cref{sect:equivtrees}, and \cref{sect:equivunicycles})
+in a way that $H_1\sim_k H_2$ implies that Duplicator wins $d\ehr_{k}(H_1;H_2)$.\par
+Given $r\in \N$, we define the \textbf{$r$-core} of an hypergraph $H$, 
+written as $Core(H;r)$, the union of the $r$-neighborhoods of
+all saturated sub-hypergraphs of $H$ whose diameter is at most $2r+1$.
+We say that $H$ is $r$-simple if all connected components of
+$Core(H;r)$ are unicycles (\cref{def:Core}) \par
+For any given $k,r\in \N$ we say that $H_1\approx_{k,r} H_2$ for two
+hypergraphs if $Core(H_1;r)$ and $Core(H_2;r)$ contain ``the same number
+up to $k$" of connected components of each $\sim_k$ class (\cref{def:agreeability}).\par
+Given $k,r\in \N$ we say that an hypergraph $H$ is $(k,r)$-rich if, informally, 
+it has enough ``$r$-neighborhoods that are trees" of each $\sim_k$ class which
+are sufficiently far from each other and sufficiently far from any small saturated
+graph (\cref{def:rich}). \par
+We prove the following facts:
+\begin{itemize}
+	\item[(1)] Let $k\in \N$ and let $r:=(3^k-1)/2$. Let $H_1$ and $H_2$
+	be $(k,r)$-rich hypergraphs satisfying $H_1\approx_{k,r} H_2$. Then
+	Duplicator wins $\ehr_{k}(H_1; H_2)$ (\cref{thm:Duplicatorwins}).
+	\item[(2)] Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple (\cref{cor:simple}).
+	\item[(3)] Let $k,r\in \N$. Then a.a.s $G_n$ is $(k,r)$-rich (\cref{thm:rich}).
+	\item[(4)] Let $k,r \in \N$. Let $\mathcal{O}$ be a $\approx_{k,r}$ class
+	of $r$-simple hypergraphs. Then 
+	\[
+	\Ln \Pr\left(G_n\left(\{\beta_R\}_{R\in \sigma}\right)\in \mathcal{O}\right)
+	\]
+	exists
+	and is an analytic expression in $\{\beta_R\}_{R\in \sigma}$ 
+	(\cref{thm:agreeabilityprobabilities}).
+\end{itemize}
+Then an sketch of the proof of the main theorem \cref{thm:main}, given in \cref{sect:main},
+ is the following:
+Let $\Phi\in FO[\sigma]$ be a sentence and let $k:=qr(\Phi)$, $r:=(3^k-1)/2$.
+Because of (1) and (3) it holds that for any $\approx_{k,r}$ class $\mathcal{O}$
+\[
+\Ln \Pr\left(G_n \models \Phi\, \big| \, G_n\in \mathcal{O} \right)= \text{ $0$ or $1$ }.
+\]
+This together with (3) and the fact that there are a finite number of
+$\approx_{k,r}$-classes of $r$-simple hypergraphs imply that $\Ln \PR{G_n \models \Phi}$
+equals a finite sum of limits of the form $\Ln \PR{G_n \in \mathcal{O}}$
+where $\mathcal{O}$ is some $\approx_{k,r}$-class of $r$-simple hypergraphs.
+Finally, using (4) we get that $\Ln \PR{G_n \models \Phi}$ exists and 
+is an analytic expression in $\{\beta_R\}_{R\in \sigma}$, as we wanted. 
+%We show that for any quantifier rank $k$ there are some classes of
+%hypergraphs 
+%$C^k_1,\dots, C^k_{n_k}$ such that
+%\begin{itemize}[noitemsep, topsep=0pt]
+%	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
+%	\item[(2)] a.a.s. any random graph belongs to some of them, and
+%	\item[(3)] the limit probability of random graph belonging to 
+%	any of them is an analytic expression on the parameters $\overline{\beta}$. 
+%\end{itemize}
+%
+%After this is archived the theorem follows easily. 
+%
+%The objective of next sections will be to define the classes 
+%$C_1,\dots, C_{n_k}$ and to show that they satisfy properties (1), (2) and (3).
+%
+%Fix a quantifier rank $k$. It is known (\cite{finitemodeltheory1}, Section 2.4)
+%that given an structure $G$, its 
+%first order logic properties definable by sentences
+%whose quantifier rank is bounded by $k$
+%depend only on the $r_k$-neighborhoods in $G$ for some 
+%constant $r_k$ that only
+%depends on $k$.
+
+\section{Model theoretic results}
+
+\subsection{Some winning strategies for Duplicator}
+
+\begin{definition} \label{def:similar}
+Let $H_1$ and $H_2$ be hypergraphs, and let
+$V_1:=V(H_1), V_2:=V(H_2)$.
 Let $\overline{v} \in V_1^*, 
@@
 $k$-\textbf{similar} $r$-neighborhoods, written as
-$(G^1,\overline{v})\simeq_{k,r}(G^2 \overline{u})$, if Duplicator wins
+$(H_1,\overline{v})\simeq_{k,r}(H_2 \overline{u})$, if Duplicator wins
 $d\ehr_k\big(N(\overline{v};r),
@@
 lists $\overline{v}$, resp. $\overline{u}$ such that 
-$(G^1,\overline{v})\simeq_{k,r}(G^2,\overline{u})$. 
+$(H_1,\overline{v})\simeq_{k,r}(H_2,\overline{u})$. 
 Given sets of vertices $X\in V_1$, $Y\in V_2$ and 
@@
 and $(Y,\overline{u})$ have $k$-similar $r$-neighborhoods,
-written as $\big(G_1, (X,\overline{v})  \big)
-\simeq_{k,r} \big(G_2, (Y,\overline{u})  \big)$, if
+written as $\big(H_1, (X,\overline{v})  \big)
+\simeq_{k,r} \big(H_2, (Y,\overline{u})  \big)$, if
 the elements of $X$ and $Y$ can be ordered in lists
 $\overline{w}$, $\overline{z}$ such that
-$(G_1,\overline{w}^\smallfrown \overline{v})
-\simeq_{k,r} (G_2,\overline{z}^\smallfrown \overline{u})$. \par
+$(H_1,\overline{w}^\smallfrown \overline{v})
+\simeq_{k,r} (H_2,\overline{z}^\smallfrown \overline{u})$. 
+\end{definition}
+
+\begin{definition} \label{def:analogous}
 Fix $r\in \N$. Suppose that $X\subseteq V_1$ and 
@@
 $Y$ have $k$-\textbf{analogous} $r$-neighborhoods,
-written as $(G^1,X)\cong_{k,r} (G^2,Y)$, 
+written as $(H_1,X)\cong_{k,r} (H_2,Y)$, 
 if for any set $Z\subset V_\delta$, with $\delta\in \{1,2\}$,
@@
 it is satisfied that ``the number of $X_i$'s  
-such that $(G^\delta, Z) \simeq_{k,r} (G^1,X_i)$ 
-and the number of $Y_i$'s such that
-$(G^\delta,Z)\simeq_{k,r} (G^2,Y_i)$
-are both equal or are both greater 
-or equal than $k$" .
-
-The main theorem of this section,which
+such that $(H_\delta, Z) \simeq_{k,r} (H_1,X_i)$" 
+and ``the number of $Y_i$'s such that
+$(H_\delta,Z)\simeq_{k,r} (H_2,Y_i)$"
+are both equal or are both greater than $k-1$.
+\end{definition}
+
+The main theorem of this section, which
 is a slight strengthening of Theorem 
@@
 
-\begin{theorem}\label{ThmDuplicator}
+\begin{theorem}\label{thm:DuplicatorAux}
 	Set $r=(3^k-1)/2$.
-	Let $G^1,G^2$ be hypergraphs and let $V_1:=V(G^1)$, $V_2:=
-	V(G^2)$.
+	Let $H_1,H_2$ be hypergraphs and let $V_1:=V(H_1)$, $V_2:=
+	V(H_2)$.
 	Suppose there exist
@@
 	\begin{enumerate}
-		\item[(1)] $(G^1,X)\cong_{k,r} (G^2,Y)$.
+		\item[(1)] $(H_1,X)\cong_{k,r} (H_2,Y)$.
 		\item[(2)]
@@
 			$d(Y,u)>2r^\prime +1$ and
-			$(G^1,v)\simeq_{k,r^\prime} (G^2,u)$.	
+			$(H_1,v)\simeq_{k,r^\prime} (H_2,u)$.	
 			\item Let $r^\prime\leq r$. Let $u\in V_2$ be
@@
 			$d(X,v)>2r^\prime +1$ and
-			$(G^1,v)\simeq_{k,r^\prime} (G^2,u)$
+			$(H_1,v)\simeq_{k,r^\prime} (H_2,u)$
 		\end{itemize}
 	\end{enumerate}
-	Then Duplicator wins $\ehr_k\big(G^1;G^2\big)$.
+	Then Duplicator wins $\ehr_k\big(H_1;H_2\big)$.
 \end{theorem}
@@
 \begin{obs} \label{obs1}
-	Let $H^1$, $H^2$ be hypergraphs and 
-	$\overline{v}\in V(H^1)^*$, $\overline{u}\in V(H^2)^*$,
+	Let $H_1$, $H_2$ be hypergraphs and 
+	$\overline{v}\in V(H_1)^*$, $\overline{u}\in V(H_2)^*$,
 	be lists of vertices. Suppose that
-	Duplicator wins $d\ehr_k(H^1,\overline{v}; \, H^2,\overline{u})$.
-	Then, for any $r\in \N$, $(H^1, \overline{v})\simeq_{k,r} 
-	(H^2,\overline{u})$. A direct consequence of this fact 
+	Duplicator wins $d\ehr_k(H_1,\overline{v}; \, H_2,\overline{u})$.
+	Then, for any $r\in \N$, $(H_1, \overline{v})\simeq_{k,r} 
+	(H_2,\overline{u})$. A direct consequence of this fact 
 	is that 
-	given hypergraphs $G^1, G^2$ and sets
-	$X\subseteq V(G^1)$, $Y\subseteq V(G^2)$ such that
-	$(G^1,X)\simeq_{k,r} (G^2,Y)$ for some $r\in \N$, 
+	given hypergraphs $H_1, H_2$ and sets
+	$X\subseteq V(H_1)$, $Y\subseteq V(H_2)$ such that
+	$(H_1,X)\simeq_{k,r} (H_2,Y)$ for some $r\in \N$, 
 	then for any $r^\prime \leq r$ it also holds 
-	$(G^1,X)\simeq_{k,r^\prime} (G^2,Y)$
+	$(H_1,X)\simeq_{k,r^\prime} (H_2,Y)$
 \end{obs}
 
-Given a set $S$ and tuples $\overline{s},\overline{t}\in S^*$
-we write $\overline{s}^\frown \overline{t}$ to denote their 
-concatenation.
-
 \begin{obs} \label{obs2}
-	Let $H_1$, $H_2$ be hypergraphs and 
-	$\overline{v}$, $\overline{u}$, be lists of vertices
-	from $V(H_1)$ and $V(H_2)$ respectively. Suppose 
+	Let $H_1$, $H_2$ be hypergraphs and let
+	$\overline{v}\in V(H_1)^*$, $\overline{u}\in V(H_2)^*$ be lists of 
+	vertices. Suppose 
 	Duplicator wins $d\ehr_k(H_1,\overline{v};\,H_2,\overline{u})$. 
@@
 	Duplicator also wins $d\ehr_{k-1}(H_1,\overline{v_2}; \,
-	H_2,\overline{u_2})$, where $\overline{v_2}:=\overline{v}^\frown v$
-	and $\overline{u_2}:=\overline{u}^\frown u$.
+	H_2,\overline{u_2})$, where $\overline{v_2}:=\overline{v}^\smallfrown v$
+	and $\overline{u_2}:=\overline{u}^\smallfrown u$.
 \end{obs}
@@
 \begin{lemma} \label{lemm:Duplicator}
-	Let $G^1$, $G^2$ be hypergraphs and let $V_1:=V(G^1),
-	V_2:=V(G^2)$. Let $\overline{v}\in V_1^*$ and
+	Let $H_1$, $H_2$ be hypergraphs and let $V_1:=V(H_1),
+	V_2:=V(H_2)$. Let $\overline{v}\in V_1^*$ and
 	$\overline{u} \in V_2^*$ be lists of vertices. Let
 	$r\in \N$ be greater than zero. Suppose that
-	$(G^1,\overline{v})\simeq_{k,3r+1} (G^2,\overline{u})$.
+	$(H_1,\overline{v})\simeq_{k,3r+1} (H_2,\overline{u})$.
 	Let $v \in V_1$ and $u\in V_2$
@@
 	$d(\overline{u},u)\leq 2r+1$ as well). 
-	Let $\overline{v_2}:=\overline{v}^\frown v$
-	and $\overline{u_2}:=\overline{u}\frown u$.
-	Then $(G^1,\overline{v_2})\simeq_{k-1,r}
-	(G^2,\overline{u_2})$.
+	Let $\overline{v_2}:=\overline{v}^\smallfrown v$
+	and $\overline{u_2}:=\overline{u}\smallfrown u$.
+	Then $(H_1,\overline{v_2})\simeq_{k-1,r}
+	(H_2,\overline{u_2})$.
 \end{lemma}
@@
 	,\overline{u_2} \, \big)\]
-	as well. Call $H_1=N(\overline{v};3r+1)$,
-	$H_2=N(\overline{u};3r+1)$. Then by \cref{obs2}
+	as well. Call $H^\prime_1=N(\overline{v};3r+1)$,
+	$H^\prime_2=N(\overline{u};3r+1)$. Then by \cref{obs2}
 	Duplicator wins
 	\[
-	d\ehr_{k-1}\big(\, N^{H_1}(
+	d\ehr_{k-1}\big(\, N^{H^\prime_1}(
 	\overline{v_2};r),\overline{v_2};\quad
-	N^{H_2}(\overline{u_2};r),\overline{u_2}\, \big).
-	\]
-	Because of this if we prove $N^{G^1}(\overline{v_2};r)
-	=N^{H_1}(\overline{v_2};r)$ and $N^{G^2}(\overline{u_2};r)
-	=N^{H_2}(\overline{u_2};r)$, then we are finished. 
-	Let $z\in N^{G^1}(v^\prime;r)$. Then
+	N^{H^\prime_2}(\overline{u_2};r),\overline{u_2}\, \big).
+	\]
+	Because of this if we prove $N^{H_1}(\overline{v_2};r)
+	=N^{H^\prime_1}(\overline{v_2};r)$ and $N^{H_2}(\overline{u_2};r)
+	=N^{H^\prime_2}(\overline{u_2};r)$, then we are finished. 
+	Let $z\in N^{H_1}(v^\prime;r)$. Then
 	$d(z,\overline{v})\leq d(z,v^\prime)+d(v^\prime,\overline{v})=3r+1$.
-	In consequence, $N^{G^1}(v;r)\subset H_1$. Thus,
-	$N^{G^1}(\overline{v_2};r)\subseteq H_1$, and $N^{G^1}(\overline{v_2};r)
-	=N^{H_1}(\overline{v_2};r)$. Analogously we obtain 
-	$N^{G^2}(\overline{u_2};r)=N^{H_2}(\overline{u_2};r)$, as we wanted. 
+	In consequence, $N^{H_1}(v;r)\subset H^\prime_1$. Thus,
+	$N^{H_1}(\overline{v_2};r)\subseteq H^\prime_1$, and $N^{H_1}(\overline{v_2};r)
+	=N^{H^\prime_1}(\overline{v_2};r)$. Analogously we obtain 
+	$N^{H_2}(\overline{u_2};r)=N^{H^\prime_2}(\overline{u_2};r)$, as we wanted. 
 \end{proof}
@@
 
-Now we are in conditions to prove \cref{ThmDuplicator}.
-
-\begin{proof}[Proof of \cref{ThmDuplicator}]
+Now we are in conditions to prove \cref{thm:DuplicatorAux}.
+
+\begin{proof}[Proof of \cref{thm:DuplicatorAux}]
 	%Set 
@@
 	%In particular this means that at the end of the $k$-th
-	%round Duplicator will have won $\ehr_k(G^1,G^2)$.	
+	%round Duplicator will have won $\ehr_k(G^1,H_2)$.	
 	Let $X_1,\dots,X_a$ and 
@@
 	Let us denote by $v^1_i$ and $v^2_i$ the vertices played
-	in $G^1$ and $G^2$ respectively during the $i$-th
-	round of $\ehr_k(G^1,G^2)$. 
+	in $H_1$ and $H_2$ respectively during the $i$-th
+	round of $\ehr_k(H_1,H_2)$. 
 	We will show a winning strategy for Duplicator
-	in $d\ehr_{k}\big(G^1;\, G^2\big)$. For each $0\leq i \leq k$,
+	in $d\ehr_{k}\big(H_1;\, H_2\big)$. For each $0\leq i \leq k$,
 	Duplicator will	keep track of some marked sets 
@@
 	of vertices $\overline{v}(T)\in V_\delta^*$ consisting
-	of the vertices played in $G_2$ so far, ordered according
-	to the rounds they where played, that were 
-	"appropriately close" to $T$ when chosen.
+	of the vertices played in $H_\delta$ so far that were 
+	"appropriately close" to $T$ when chosen,  ordered according
+	to the rounds they where played in.
 	The game will start with no sets of vertices marked and 
@@
 	\item Mark two sets $S\subset V_1$ and $T\subset V_2$ and
-	define $\overline{v}(S)=v^1_i$ and $\overline{v}(T)=v^2_i$.
+	define $\overline{v}(S):=v^1_i$ and $\overline{v}(T):=v^2_i$.
 	\item Given two sets $S\subset V_1$, $T\subset V_2$ that were 
@@
 		\[
-		\big(G^1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
-		\big(G^2, (T,\overline{v}(T))\big).	\]
+		\big(H_1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
+		\big(H_2, (T,\overline{v}(T))\big).	\]
 
@@
 	In particular, if conditions (i) to (iv) are satisfied this means
-	that if $\overline{v}^1=(v^1_1,\dots,v^1_i)$ and
-	$\overline{v}^2=(v^2_1,\dots, v^2_i)$ are the vertices played so far
+	that if $\overline{v}^1:=(v^1_1,\dots,v^1_i)$ and
+	$\overline{v}^2:=(v^2_1,\dots, v^2_i)$ are the vertices played so far
 	then Duplicator wins
@@
 	And at the end of the $k$-th round Duplicator will have won
-	$\ehr(G^1;\, G^2)$. \par
-	The game $d\ehr_k(G_1; \, G_2)$ proceeds as follows. Suppose 
-	that during the $i$-th round Spoiler chooses $v^1_i\in V_1$ 
+	$\ehr(H_1;\, H_2)$. \par
+	The game $d\ehr_k(H_1; \, H_2)$ proceeds as follows.
+	Clearly properties (i) to (iv) hold at the beginning of 
+	the game.  Suppose that
+	Duplicator can play in such a way that properties (i) to (iv) hold 
+	until the beginning of the $i$-th round. Suppose that
+	during the $i$-th round Spoiler chooses $v^1_i\in V_1$ 
 	(the case where they play in $V_2$ is symmetric). There are 
@@
 		it holds that $d(S\cup \overline{v},\quad v^1_i)\leq 2r_i +1$. 
-		In this case let $T\subset V_2$ be the set in $G_2$ marked in the 
+		In this case let $T\subset V_2$ be the set in $H_2$ marked in the 
 		same round as $T$. By hypothesis 
-		\[ \big(G^1,(S,\overline{v}(S))\big)
+		\[ \big(H_1,(S,\overline{v}(S))\big)
 		\simeq_{k-i+1,3r_i+1}
-		\big(G^2,(T,\overline{v}(T))\big). 		
+		\big(H_2,(T,\overline{v}(T))\big). 		
 		\]
@@
 		\[
-		\big(G^1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
-		\big(G^2, (T,\overline{v}(T))\big).
+		\big(H_1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
+		\big(H_2, (T,\overline{v}(T))\big).
 		\]
@@
 		\[
-		(G^1,S)\simeq_{k-i+1,3r_i+1} (G^2,T).\] 
+		(H_1,S)\simeq_{k-i+1,3r_i+1} (H_2,T).\] 
 		Thus, by definition, for some orderings $\overline{w}$, 
@@
 		$Y_1,\dots, Y_b$, and (C) 
-		$(G^1,v^1_i)\simeq_{k-i,r_i} (G^2, v^2_i)$.
+		$(H_1,v^1_i)\simeq_{k-i,r_i} (H_2, v^2_i)$.
 		After this Duplicator marks both $S=\{
@@
 
-To prove \cref{thm:main} we are going to exploit the facts that
-(1) for any fixed $r\in N$, $r$-neighborhoods in $G_n$ a.a.s 
-are either trees of unicycles, and
-(2) we can identify $k$-equivalent trees
-and unicycles sufficiently often in a simple way.
-
-\subsubsection{k-Equivalent trees}
+\subsubsection{k-Equivalent trees} \label{sect:equivtrees}
 
 \begin{definition}
-	We define a \textbf{tree} $T$ as a connected hypergraph such that
-	$ex(T)=-1$. A \textbf{rooted tree} $(T,v)$ is a tree $T$ with a 
+	 A \textbf{rooted tree} $(T,v)$ is a tree $T$ with a 
 	distinguished vertex $v\in V(T)$ called its \textbf{root}.
@@
 
-Fix a natural number $k$. We will define the
-\textbf{$k$-equivalence} relation, written as 
-$\sim_k$,  over rooted trees
-inductively over their radii as follows:
+Fix a natural number $k$. We define the
+\textbf{$k$-equivalence} relation over rooted trees, 
+written as $\sim_k$, by induction over their radii as follows:
 
@@
 
-	\item Suppose that the $k$-equivalence relation has been
-	defined for rooted trees with radius at most $r$. Let $\Sigma_r$
-	be the set consisting of the root symbol $\rho$ and
-	the $k$-equivalence classes of trees with radius at most $r$.
-	Given a rooted tree $(T,v)$ with whose radius is $r+1$
-	we define its canonical $\Sigma_r$-coloring as the map 
-	$\tau_{(T,v)}: V(T)\rightarrow \Sigma_r$ satisfying that
-	for any $u\neq v$ $\tau_{(T,v)}(u)$ is the $k$-equivalence class 
-	of $\mathrm{Tr}(T,u;\, \,v)$ and that $\tau_{(T,v)}(v)=\tau$. \par
-	Let $T_1$ and $T_2$ be rooted trees with radius $r+1$. 
+	\item Let $r>0$.
+	Suppose that the $k$-equivalence relation has been
+	defined for rooted trees with radius at most $r-1$. Let $\Sigma_{k,r-1}$
+	be the set consisting of the $k$-equivalence classes of trees
+	with radius at most $r-1$. Let $\rho$ be an special symbol called the
+	\textbf{root symbol}.
+	Given a rooted tree $(T,v)$ with whose radius is $r$
+	we define its \textbf{canonical ($\Sigma_{k,r-1}\cup \{\rho\}$)-coloring}
+	as the map 
+	$\tau_{(T,v)}: V(T)\rightarrow \Sigma_{k,r-1}\cup \{\rho\}$ satisfying that
+	 $\tau_{(T,v)}(u)$ is the
+	$\sim_k$ class of $\mathrm{Tr}(T,u;\, \,v)$
+	for any $u\neq v$, and $\tau_{(T,v)}(v)=\tau$. \par
+	Let $T_1$ and $T_2$ be rooted trees with radius $r$. 
 	We say that $(T_1,v_1)\sim_k (T_2,v_2)$ 
-	if for $\delta=1,2$, given any initial edge $e$ from $(T_\delta,v_\delta)$
-	the
+	if for any $\delta=1,2$, given any initial edge 
+	$e$ from $(T_\delta,v_\delta)$	the
 	``quantity of initial edges $e_1\in E(T_1)$ such that
@@
 \end{itemize}
+Here we are making an slight abuse of notation in the expressions of the
+type $\big(e_1,\tau_{(T_1,v_1)}\big)$. There $e$ denotes the 
+sub-hypergraph of $T_1$ whose vertices are the ones in $V(e)$ and whose
+only edge is $e$. This way $\big(e_1,\tau_{(T_1,v_1)}\big)$ is a 
+$(\Sigma_{(k,r-1)}\cup \{\rho\})$-hypergraph, as defined in \cref{def:color}.
+\end{definition}
 
@@
 	of $(\Sigma_{(k,r-1)}\cup \{\rho \})$-hypergraphs 
-	$(e,\tau)$ consisting of only one edge that satisfy 
+	$(e,\tau)$ that consist of only one edge and satisfy 
 	$\tau(v)=\rho$ for exactly one vertex $v\in V(e)$. We will
@@
 \begin{itemize}
-	\item[(1)] For any $\epsilon\in E^1_\mathcal{T}$ there are at least
+	\item[(1)] For any pattern $\epsilon\in E^1_\mathcal{T}$ there are at least
 	$k$ initial edges $e\in E(T)$ such that
 	$(e,\tau_{(T,v)})\in \epsilon$. 
-	\item[(2)] For any $\epsilon\in E^2_\mathcal{T}$ there are exactly
+	\item[(2)] For any pattern $\epsilon\in E^2_\mathcal{T}$ there are exactly
 	$a_\epsilon$ initial edges $e\in E(T)$ such that
@@
 \end{obs}
-
-\end{definition}
+\begin{obs}\label{obs:finitetrees}
+	Using last characterization of $\sim_k$ classes
+	it is easy to show that for any $r\in \N$ the quantity
+	of $\sim_k$ classes of trees with radii at most $r$ is finite. 
+	We proceed by induction. For $r=0$ there is only one $\sim_k$ class.
+	Now let $r>0$ and suppose that the statement holds for $r-1$. Then
+	the number of $(k,r)$-patterns is finite and so is the number
+	of $\sim_k$ classes of trees with radii at most $r$. 
+\end{obs}
+
 We want prove the following
 \begin{theorem} \label{thm:equivalenttrees} 
-	Let $(T_1,v_1)$ and $(T_2,v_2)$ be rooted trees.
-	Then, if they are $k$-equivalent Duplicator wins
+	Let $(T_1,v_1)$ and $(T_2,v_2)$ be rooted trees such
+	that $(T_1,v_1)\sim_k (T_2,v_2)$.
+	Then Duplicator wins
 	$d\ehr_{k}(T_1,v_1;\, \, T_2,v_2)$.
@@
 
-Before proceeding with the proof that we need an auxiliary
+Before proceeding with the proof we need an auxiliary
 result. Let $(T,v)$ be a rooted tree and $e$ an 
@@
 	Duplicator wins 
-	$d\ehr{k}(T^\prime_1, v_1; \, \, T^\prime_2,v_2)$.
+	$d\ehr_{k}(T^\prime_1, v_1; \, \, T^\prime_2,v_2)$.
 \end{lemma}
@@
 
-\subsubsection{k-Equivalent hypergraphs}
-
-\begin{definition}
-	We call a connected hypergraph $H$ \textbf{saturated} if any proper 
-	sub-hypergraph $H^\prime \subset H$ satisfies $ex(H^\prime)<ex(H)$. 
-	Notice that if $H$ is saturated, in particular $ex(H)\geq 0$ because
-	the empty hypergraph has excess zero. \par
-
-	The \textbf{center} of a connected hypergraph $H$, written as
+\subsubsection{k-Equivalent hypergraphs} \label{sect:equivunicycles}
+
+\begin{definition} \label{def:Center}
+	The \textbf{center} of an hypergraph $H$, written as
 	$Center(H)$,  
-	is its maximal saturated
-	sub-hypergraph in the case that $H$ is not a tree and 
-	is the empty hypergraph otherwise.  
-	If $H$ is an arbitrary hypergraph
-	then the center of $H$ is the union of the
-	centers of its connected components. \par
-	Let $H$ be an hypergraph and let $\overline{v}\in V(H)*$. If $H$
-	is connected then we define the graph $Center(H,\overline{v})$ 
+	is the union of all saturated sub-hypergraphs of $H$. 
+%	Given $r\in \N$, the $r$-\textbf{center} of $H$,
+%	written as $Center(H;r)$, is the union of all saturated 
+%	sub-hypergraphs of $H$ with diameter at most $2r+1$.  
+	\par
+	Let $H$ be an hypergraph, let $\overline{v}\in V(H)^*$. 
+%	and let $r\in \N$
+	If $H$
+	is connected then we define the graph
+	$Center(H,\overline{v})$
+%	, resp. $Center(H,\overline{v};\, r)$,
 	as the minimal connected sub-hypergaph of $H$ that contains
-	both $Center(H)$ and the vertices in $\overline{v}$. Otherwise,
-	if $H$ is a general hypergraph we define $Center(H,\overline{v})$ 
-	as the union for all connected components $H^\prime$ of $H$
+	both $Center(H)$
+%	, resp. $Center(H;\,r)$,
+	and the vertices in $\overline{v}$. Otherwise,
+	if $H$ is a general hypergraph we define $Center(H,\overline{v})$,
+%	, resp. $Center(H,\overline{v};\, r)$, 
+	as the union, for all connected components $H^\prime \subset H$,
 	of the minimal connected sub-hypergraph of $H^\prime$ that
-	contains both $Center(H^\prime)$ and the vertices in $\overline{v}$
+	contains both $Center(H^\prime)$
+%	, resp. $Center(H^\prime,\overline{v};\, r)$,
+	and the vertices in $\overline{v}$
 	that belong to $V(H^\prime)$.
@@
 
-\begin{definition}
-	Let $H$ be an hypergraph, let $\overline{v}\in V(H)^*$
-	and let $v\in H$. We define $\mathrm{Tr}\big(
+\begin{definition}\label{def:TrOperator}
+	Let $H$ be an hypergraph, let $\overline{v}\in V(H)^*$ and 
+	let $v\in H$. We define $\mathrm{Tr}\big(
 	H,\overline{v};\,\, v\big)$ in the following way:
@@
 	\end{itemize}
+%	Given $r\in\N$ we define  $\mathrm{Tr}\big(
+%	H,\overline{v};\,\, v;\,\, r\big)$ analogously to $\mathrm{Tr}\big(
+%	H,\overline{v};\,\, v\big)$ in the following way:
+%	\begin{itemize}
+%		\item If $d\big(\, Center(H, \overline{v};\, r)
+%		, \, \, v \big)>r$ then $T:=N(v;r)$ is a tree
+%		and	$\mathrm{Tr}\big(
+%		H,\overline{v};\,\, v;\,\, r\big)$ is the tree $T$ rooted at $v$.
+%		\item Otherwise $\mathrm{Tr}\big(
+%		H,\overline{v};\,\, v\big)$ is the tree $H[X]$ 
+%		induced on the set 
+%		\begin{align*}
+%		X:=\Big\{\, u\in V(H) \,\, \Big| \, \,
+%		d\big(\, Center(H, \overline{v};\, r)
+%		, \, \, u \big)= d\big(\, Center(H, \overline{v};\, r)
+%		, \, \, v \big) + d(v,u),&\\  \text{ and } d(v,u)\leq r
+%		\Big\},&
+%		\end{align*}
+%		to which we assign $v$ as a root. That is,
+%		$\mathrm{Tr}\big(
+%		H,\overline{v};\,\, v;\,\, r\big)$ is the tree formed of all 
+%		vertices $u$ whose distance to $v$ is at most $r$ and 
+%		whose only path to $Center(H,\overline{v};\, r)$ contains $v$. 
+%	\end{itemize}
 	In the case that $\overline{v}$ is the empty list we will write
-	simply $\mathrm{Tr}(H;\,\, v)$ instead of 
-	$\mathrm{Tr}(H,\, \, ;\,\, v)$. Notice that in the case that
+	simply $\mathrm{Tr}(H;\,\, v)$ 
+%	or $\mathrm{Tr}(H;\,\, v;\,\,r)$ 
+	instead of 
+	$\mathrm{Tr}(H,\, \, ;\,\, v)$.
+%	 or $\mathrm{Tr}(H,\,\,;\,\, v;\,\,r)$.
+	Notice that in the case that
 	$(T,u)$ is a rooted tree then the definition of 
-	$\mathrm{Tr}(T,u;\, \, v)$ given before coincides with this one,
-	so no confusion should arise. 	
+	$\mathrm{Tr}(T,u;\, \, v)$ given in \cref{sect:equivtrees}
+	coincides with the one we have
+	given now,
+	so no confusion should arise. \par
 \end{definition}
@@
 
-	\begin{theorem}
+	\begin{theorem} \label{thm:strategyaux}
 		Let $H_1$ and $H_2$ be non-tree 
@@
 
-\begin{definition}
+\begin{definition} \label{def:Core}
 	Let $H$ be an hypergraph. We define its \textbf{$r$-core}, 
@@
 	where $X$ is the set of vertices $v\in V(H)$
-	that participate in any saturated sub-hypergraph 
-	$H^\prime\subset H$ whose diameter is at most $2r+1$.\par
+	that belong to any saturated sub-hypergraph of $H$
+	whose diameter is at most $2r+1$. 
+	Equivalently, $Core(H;r)=N\big(Center(H;\, r);\, r\big)$. Given 
+	$\overline{v}\in V(G)^*$, we define $Core(H,\overline{v};r)$
+	as $N(Y;r)$, where $Y$ is the set of vertices $v\in V(H)$ that either
+	belong to $\overline{v}$ or belong to any saturated sub-hypergraph of $H$
+	whose diameter is at most $2r+1$. \par
+	We say that $H$ is $r$-\textbf{simple} if all connected components
+	of $Core(H;r)$ are unicycles.
+\end{definition}
+
+\begin{definition} \label{def:agreeability}
 	Let $H_1$ and $H_2$ be hypergraphs and let $r\in \N$.
 	Let $H^\prime_1:=Core(H_1;r)$ and $H^\prime_2:=Core(H_2;r)$. 
-	Suppose that any connected component $F$ from either 
-	$H^\prime_1$ or $H^\prime_2$ satisfies that
-	``the number of connected components $H^{\prime\prime}_1$
-	from $H^\prime_1$ such that $ H^{\prime\prime}_1 \sim_k F\, \, \,$'' 
-	and ``the number of
-	connected components $H^{\prime \prime}_2$ of $H^\prime_2$
-	such that
-	$ H^{\prime\prime}_2\sim_k F\, \, \,$" 
-	are both equal or are both greater 
-	or equal than $k$. Then we say that $H_1$ and $H_2$
-	are $(k,r)$-\textbf{agreeable}, written as $H_1\approx_{k,r} H_2$. \par
-	We say that an hypergraph $H$ is $r$-simple all connected components
-	of $Core(H;r)$ are unicycles.   
+	We say that $H_1$ and $H_2$ are $(k,r)$-agreeable, written
+	as $H_1\approx_{k,r} H_2$ if for any $\sim_k$ class $\mathcal{H}$ 
+	``the number of connected
+	components in $H^\prime_1$ that belong to $\mathcal{H}$" and
+	``the number of connected components in $H^\prime_2$ that belong to 
+	$\mathcal{H}$" are the same or are both greater than $k-1$.\par
+%	 satisfies that
+%	``the number of connected components $H^{\prime\prime}_1$
+%	from $H^\prime_1$ such that $ H^{\prime\prime}_1 \sim_k F\, \, \,$'' 
+%	and ``the number of
+%	connected components $H^{\prime \prime}_2$ of $H^\prime_2$
+%	such that
+%	$ H^{\prime\prime}_2\sim_k F\, \, \,$" 
+%	are both equal or are both greater 
+%	or equal than $k$. Then we say that $H_1$ and $H_2$
+%	are $(k,r)$-\textbf{agreeable}, written as $H_1\approx_{k,r} H_2$. \par
+
 \end{definition}
@@
 
-\begin{lemma}
+\begin{lemma} \label{lem:aux1}
 	Let $r\in \N$ and let $H_1, H_2$ be hypergraphs such that 
@@
 	belong to any saturated sub-hypergraph of diameter 
-	at most $2r+1$. Then $(H_1,X)\cong_{k,r} (H_2,Y)$.	
+	at most $2r+1$. Then $(H_1,X)\cong_{k,r} (H_2,Y)$ in the sense of
+	\cref{def:analogous}.
 \end{lemma}
@@
 	Using the definition of $H_1\approx_{k,r}H_2$ as well 
-	as the fact that $N(X_i;r)\sim_k N(Y_j;r)$ implies 
-	$(H_1,X_i)\simeq_{k,r} (H_2,Y_j)$ the result follows.	
+	as the fact that  because of \cref{thm:strategyaux}
+	$N(X_i;r)\sim_k N(Y_j;r)$ implies 
+	$(H_1,X_i)\simeq_{k,r} (H_2,Y_j)$
+	the result follows.	
 \end{proof}
-
-\begin{definition}
+\sep
+\begin{definition} \label{def:rich}
 	Let $H$ be an hypergraph and let $r\in\N$. Let
@@
 	\begin{proof}
-		We can apply \cref{ThmDuplicator} with $X\subset V(H_1)$ 
+		Because of the previous lemma we can apply 
+		\cref{thm:DuplicatorAux} with $X\subset V(H_1)$ 
 		and	$Y\subset V(H_2)$ the sets of vertices that belong
@@
 	Let $H$ be an hypergraph. Then 
-	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
-	\Theta(n^{-ex(H)})$ as $n$ tends to infinity.  
+	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]\sim
+	C\cdot(n^{-ex(H)})$ for some constant $C\in \R$ as $n$ tends to infinity.  
 \end{lemma}
@@
 \]	
-We have that $|Copies(H,[n])|=\frac{(n)_{v(H)}}{|Aut(H)|}$. Also, 
+We have that $|Copies(H,[n])|=\frac{(n)_{v(H)}}{\aut(H)}$. Also, 
 for any $H^\prime \in Copies(H,[n])$ it is satisfied
@@
 \mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
-\frac{(n)_{v(H)}}{|Aut(H)|}\cdot
+\frac{(n)_{v(H)}}{\aut(H)}\cdot
 \prod_{R\in \sigma} \left(\frac{\beta_R}{n^{ar(R)-1}}\right)^{|E_R(H)|}
@@
 n^{-ex(H)} \cdot \frac{\prod_{R\in \sigma} \beta_R^{
-|E_R{H}| }}{|Aut(H)|}.
+|E_R{H}| }}{\aut(H)}.
 \]
@@
 %$X^H_n=\sum_{f\in [n]_{V(H)}} X^H_{n,f}$. Then, by definition, the number of 
-%copies of $H$ in $G_n$ is exactly $X^H_n/|Aut(H)|$.
+%copies of $H$ in $G_n$ is exactly $X^H_n/\aut(H)$.
 %Taking into account that 
@@
 %The expected number of copies of $H$ in $G_n$ is then this last
-%expectation divided by the number of automorphisms of $H$, $|Aut(H)|$.
+%expectation divided by the number of automorphisms of $H$, $\aut(H)$.
 %In consequence,
@@
 % &\Ln \mathrm{E}\big[\# \text{copies of }H \text{ in } G_n\big] 
-%=\Ln \frac{(n)_{|V(H)|}}{|Aut(H)|} \prod_{i=1}^{t} 
+%=\Ln \frac{(n)_{|V(H)|}}{\aut(H)} \prod_{i=1}^{t} 
 %\big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
 %=\\ &\Ln \Big[(n)_{|V(H)|}\prod_{i=1}^{t}n^{(1-a_i)|E_i(H)|}\Big]
-%\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|} \simeq \Ln
-%n^{-ex(H)}\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|},
+%\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{\aut(H)} \simeq \Ln
+%n^{-ex(H)}\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{\aut(H)},
 %\end{align*}
@@
 \end{proof}
+\sep
 
@@
 \end{proof} 
+\sep
 
@@
 	in $\overline{v}$. Then
-	$\mathrm{E}\big[ X_n \big]=\Theta(n^{-ex(H)-len(\overline{v})})$.	
+	\[
+	\mathrm{E}\big[ X_n \big]=\Theta(n^{-ex(H)-len(\overline{v})}).\]
+	In particular, given any fixed $r\in \N$,
+	a.a.s the vertices $v\in \overline{v}$ satisfy that
+	the $N(v;r)$'s are disjoint trees.	
 \end{lemma}
@@
 \end{proof}
-
+\sep
 \begin{lemma}
@@
 	of it in $G_n$ tends to $1$ as $n$ goes to infinity. Using that
-	there are a finite number of dense hypergraphs of size bounded by
-	$R$ we deduce that the RHS of last inequality tends to $1$. 
+	there are a finite number of $\sim$ classes of dense hypergraphs whose
+	size bounded by	$R$ we deduce that the RHS of last inequality tends to $1$. 
 \end{proof}
-
+\sep
 \begin{corollary}\label{cor:simple}
@@
 \end{corollary}
-\begin{corollary}
+\begin{proof}
 	If some connected component of $Core(G_n;r)$ is not a cycle that means
@@
 	$G_n$ is a.a.s $(6r+3)$-sparse and the result follows. 
-\end{corollary}
-
-%\subsection{Counting colored sub-hypergraphs}
-%
-%
-%\begin{definition} 
-%	Given a set $\Sigma$, a $\Sigma$-hypergraph is a pair
-%	$(G,\chi)$ consisting of an hypergraph $G$ and a map 
-%	$\chi: V(G) \rightarrow \Sigma$.  
-%	Given two $\Sigma$-hypergraphs $(H,\rho)$ and $(G,\chi)$,
-%	an isomorphism between them is an hypergraph isomorphism 
-%	$f:V(H)\rightarrow V(G)$ satisfying $\rho(v)=\chi(f(v))$
-%	for any $v\in V(H)$. 
-%	An automorphism of a $\Sigma$-hypergraph $(G,\chi)$ is an
-%	isomorphism from $(G,\chi)$ to itself. As with the case of
-%	hypergraphs we write $Aut(G,\chi)$ to denote the group of 
-%	automorphisms of $(G,\chi)$.
-%	\par
-%	Let $(H,\rho), (G,\chi)$ be two $\Sigma$-hypergraphs. 
-%	Then a copy of $H$ in $G$ is
-%	a sub-hypergraph $H^\prime\subset G$ such that 
-%	$(H,\rho)$ is isomorphic to 
-%	$(H^\prime,\chi|_{_{H^\prime}})$.\par
-%	Given a $\Sigma$-hypergraph $(G,\chi)$ and a set $V$ we
-%	define the set $Copies(S,(G, \chi))$ as the one that contains all 
-%	possible $\Sigma$-hypergraphs $(H,\rho)$ isomorphic to $(G,\chi)$ 
-%	such that $V(H)\subset S$.	
-%\end{definition}
-%
-%\begin{definition}
-%	Given a set $\Sigma$, a random $\Sigma$-coloring of $G_n$ is 
-%	a random function $\chi_n: [n]\rightarrow \Sigma$. We say that	
-%	$\chi_n$ is symmetric if for any $s\in \Sigma$ the probability
-%	$\mathrm{Pr}\big( \chi_n(v)=s \big)$ is the same for any vertex
-%	$v\in [n]$. Notation $\mathrm{Pr}\big[\chi_n=s\big]$. \par
-%	For each $n\in \N$ let $\chi_n$ be a random $\Sigma$-coloring of $G_n$.
-%	We say that the succession $(\chi_n)_{n\in \N}$ is regular if
-%	the $\chi_n$'s are symmetric and for any $s\in \Sigma$ the limit
-%	$\Ln \mathrm{Pr}\big[ \chi_n = s \big]$ exists. 
-%\end{definition}
-%
-%
-%Remark: A random coloring $\chi$ of $G_n$ does not have to be independent from
-%$G_n$. In fact, in the cases we are going to consider $\chi$ will be determined
-%by $G_n$. 
-%
-%\begin{definition}
-%	Let $\Sigma_1,\dots,\Sigma_k$ be a sets. For each $i\in [k]$
-%	let $(\chi_{n,i})_{n \in \N}$ be a random regular sequence of
-%	$\Sigma_i$-colorings.
-%	Let $\mathcal{F}$ be a family of hypergraphs.
-%	We say that the successions $(\chi_{n,1})_{n \in \N},\dots,
-%	(\chi_{n,k})_{n \in \N}$ are $\mathcal{F}$-independent if
-%	for any given
-%	\begin{itemize}
-%		\item fixed finite number of copies of hypergraphs from 
-%		$\mathcal{F}$ in $\N$,
-%		\[
-%		S \subset \bigcup_{H\in \mathcal{F}} Copies(H,\N).
-%		\]		
-%		\item fixed disjoint sets of vertices 
-%		$V_1, \dots, V_k \subset \bigcup_{H\in S} V(H).$
-%		\item for each $i\in [k]$ and each $v\in V_i$, 
-%		a fixed label $s(v)\in \Sigma_i$
-%	\end{itemize}
-%	it is satisfied
-%	\[
-%	\Ln \mathrm{Pr}\big(
-%	\bigwedge_{i=1}^k \bigwedge_{v\in V_i} \chi_{n,i}(v)=s(v)
-%	\, \big| \, \bigwedge_{H\in S} H\subset G_n \,
-%	\big) = \prod_{i=1}^k \prod_{v\in V_i} \mathrm{Pr}\big[\chi_i=s(v)
-%	\big]		
-%	\]  
-%\end{definition}
-%
-%\begin{definition}
-%	Let $H_1,\dots, H_k$ be hypergraphs. Let $n,b_1,\dots,b_k\in \N$
-%	A $b_1,\dots,b_k$-configuration of $H_1,\dots, H_k$ over $[n]$
-%	is an ordered tuple $(O_1,\dots,O_k)$ where for each $i\in [k]$
-%	$O_i$ is an ordered $b_i$-tuple of different $H_i$-hypergraphs 
-%	over $[n]$. In other words, each $O_i$ is an element of
-%	$\big( Copies(H,[n])\big)_{b_i}$, and the set of 
-%	$b_1,\dots,b_k$-configurations of $H_1,\dots, H_k$ over $[n]$
-%	is precisely $\prod_{i=1}^{k}\big( Copies(H,[n])\big)_{b_i}$.
-%\end{definition}
-%
-%\begin{definition}
-% 	The underlying set of a configuration $\omega
-% 	=  (O_1, \dots, O_k)$ is the defined as
-% 	$S_{\omega}:=\{ H\in O_i \, | \, i\in [k]\}$.
-% 	A configuration $\omega$ is called disjoint
-%	if all the hypergraphs belonging to its underlying set
-%	$S_\omega$ have disjoint sets of vertices. 
-%\end{definition}
-%
-%\begin{theorem}
-%	Let $k\in \N$. For each $i\in [k]$ 
-%	\begin{itemize}
-%		\item Let $\Sigma_i$ be a set, let $H_i$ be a unicycle and 
-%		let $\rho^i$ be a $\Sigma_i$-coloring of $H_i$.
-%		\item Let $(\chi^i_n)_{n\in\N}$ be a succession of
-%		random $\Sigma_i$-colorings of $(G_n)_{n\in \N}$
-%		\item Let $X_{i,n}$ be the random variable that counts
-%		the number of copies of $(H_i, \rho^i)$ in
-%		$(G_n,\chi^i_n)$.				
-%	\end{itemize}
-%	Let $\mathcal{F}=\{H_1,\dots, H_n\}$. Suppose that the
-%	successions $(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
-%	are $\mathcal{F}$-independent. Then, for each $a_1,\dots,a_k\in \N$
-%	\[
-%	\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k X_{n,i}=a_i  \big)=
-%	\prod_{i=1}^{k}e^{-\lambda_i}\frac{\lambda_i^{a_i}}{a_i!},
-%	\]
-%	where for each $i\in [k]$,
-%	\[
-%	\lambda_i:= \frac{\prod_{j\in \sigma} \beta_j^{e_j(H_i)}}{|Aut(H_i,\rho^i)|} 
-%	\prod_{v\in V(H_i)} \mathrm{Pr}\big[\chi^i=\rho^i(v)\big].
-%	\]
-%\end{theorem}
-%\begin{proof}
-%	Because of \cref{thm:BrunSieve} we only need to show that for any 
-%	fixed $b_1,\dots, b_k\in \N$ it is satisfied
-%	\[
-%	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
-%	\prod_{i=1}^{k} \lambda_i^{b_i}.		
-%	\]
-%	For each $n\in \N$ let $\Omega_n$ be the set
-%	of $b_1, \dots, b_k$-configurations of $(H_1,\rho^1)
-%	,\dots, (H_k, \rho^k)$ over $[n]$. Then
-%	\[
-%	\Ln \mathrm{E}\big[ \prod_{i=1}^{k} (X_{n,i})_{b_i} \big]=
-%	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
-%	\mathrm{Pr}
-%	\big(
-%	(O_1,\dots, O_k) \subset G_n
-%	\big).	
-%	\]
-%	Let $\Omega^{\times}_n\subset \Omega_n$ be the set of 
-%	disjoint configurations in $\Omega_n$. Because of REF,
-%	\[
-%	\Ln \sum_{(O_1,\dots, O_k)\in \Omega_n}
-%	\mathrm{Pr}
-%	\big(
-%	(O_1,\dots, O_k) \subset G_n
-%	\big)=
-%	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
-%	\mathrm{Pr}\big(
-%	(O_1,\dots, O_k) \subset G_n
-%	\big).
-%	\]
-%	Because of the symmetry of the random hypergraph $G_n$ and
-%	the colorings $\chi^1_n, \dots, \chi^k_n$ the probability
-%	$\mathrm{Pr}\big(
-%	(O_1,\dots, O_k) \subset G_n
-%	\big)$ is the same for all $(U_1,\dots, U_k)\in 
-%	\Omega^\times_n$. Thus, if we fix
-%	$(O_1, \dots, O_k)$ a 
-%	disjoint $b_1,\dots,b_k$-configuration of
-%	 $(H_1,\rho^1)
-%	,\dots, (H_k, \rho^k)$ over $\N$, 
-%	\[
-%	\Ln \sum_{(O_1,\dots, O_k)\in \Omega^\times_n}
-%	\mathrm{Pr}\big(
-%	(O_1,\dots, O_k) \subset G_n
-%	\big) =
-%	\Ln |\Omega^{\times}_n|\cdot \mathrm{Pr}\big(
-%	(U_1,\dots, U_k) \subset G_n
-%	\big).
-%	\]
-%	Let $S$ be the underlying set of the configuration $(U_1,\dots,U_k)$.
-%	Let $l= \sum_{H\in S} v(S)$. Then it is satisfied 
-%	\[
-%	|\Omega^{\times}_n|= \frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}.
-%	\]
-%	Using the definition of $(U_1,\dots, U_k) \subset G_n$ and
-%	substituting $|\Omega^{\times}_n|$ we get
-%	\[
-%	\Ln |\Omega^{\times}_n|\cdot \mathrm{Pr}\big(
-%	(U_1,\dots, U_k) \subset G_n
-%	\big) = \Ln
-%	\frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot
-%	\PR{\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
-%	(H,\rho)\subset (G_n, \chi_n^i)}.
-%	\]
-%	But the event $(H,\rho)\subset (G_n, \chi_n^i)$ is equivalent to $H\subset G_n$ and
-%	$\chi_n^i(v)=\rho(v)$ for all $v\in V(H)$. Thus the LHS of last equation equals
-%	\[
-%	\Ln
-%	\frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot
-%	\Pr\Big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
-%	\big(H\subset G_n \bigwedge_{v\in V(H)} \chi_n^i(v)=\rho(v) \big) \Big).
-%	\]
-%	For each $n\in \N$ let $A_n$ the event
-%	\[
-%	A_n:=\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
-%	H\subset G_n.
-%	\]	
-%	Then,
-%	\begin{align*}
-%	&\Pr\Big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
-%	\big(H\subset G_n \bigwedge_{v\in V(H)} \chi_n^i(v)=\rho(v) \big) \Big)=\\
-%	&\Pr\big(A_n\big)\cdot \Pr\big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
-%	\bigwedge_{v\in V(H)} \chi^i_n(v)=\rho(v) \, \big| \, A \big).
-%	\end{align*}
-%	It holds that
-%	\[
-%	\PR{A_n}=\frac{1}{n^l} \prod_{i=1}^{k}\prod_{R\in \sigma} \beta_R^{e_R(H_i)\cdot b_i},
-%	\]
-%	and in consequence 
-%	\[
-%	\Ln \frac{(n)_l}{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}\cdot \PR{A_n}
-%	= \frac{\prod_{i=1}^{k}\prod_{R\in \sigma} \beta_R^{e_R(H_i)\cdot b_i}}
-%	{\prod_{i=1}^k |Aut(H_i,\rho^i)|^{b_i}}.
-%	\]
-%	Finally, using the hypothesis that 
-%	$(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
-%	are $\mathcal{F}$-independent we obtain
-%	\[
-%	\Ln \Pr\big(\bigwedge_{i=1}^k \bigwedge_{(H,\rho)\in U_i} 
-%	\bigwedge_{v\in V(H)} \chi^i_n(v)=\rho(v) \, \big| \, A \big)
-%	= \prod_{i=1}^{k} \prod_{v\in V(H_i)} \Pr\big[ \chi^i=\rho^i(v)\big]^{b_i}.
-%	\]
-%	The result follows from joining equations. 
-%\end{proof}
-%
-%\begin{definition}
-%	Let $\Sigma$ be a set containing the empty label $\emptyset$.
-%	Let $V\subset [n]$. We say that a random $\Sigma$-coloring $\chi$
-%	of $G_n$ is $V$-symmetric if $\chi(v)=\emptyset$ if and only if $v\in V$ and
-%	for any $s\in \Sigma$ the probability $\Pr(\chi(v)=s)$ is the same for all 
-%	$v\in [n]\setminus V$. \par
-%	Let $V\subset \N$ be a finite set of vertices and let $(\chi^n)_{n\in \N}$
-%	be a succession such that each $\chi^n$ is a random coloring of $G_n$. We
-%	call the succession $(\chi^n)_{n\in \N}$ $V$-regular if each $\chi^n$ is
-%	$V$-symmetric and for all $s\in \Sigma$ and $v\in \N \setminus \N$ the limit 
-%	$\Ln \PR{\chi^n(v)=s}$ exists. 
-%\end{definition}
-%
-%\begin{definition}
-%	Let $\Sigma$ be a set containing the empty label $\emptyset$. A rooted $\Sigma$-edge
-%	is a $\Sigma$-hypergraph $(e,\chi)$ where $e$ is an edge 
-%	(i.e., an hypergraph consisting of only one edge), and there is a unique vertex
-%	$v\in V(e)$ such that $\chi(v)=\emptyset$.
-%	Given a rooted $\Sigma$-edge $(e,\chi)$, a set of vertices $V$ and a vertex $v\in \N$
-%	we define the set $Copies((e,\chi),(V,v))$ as the set of copies 
-%	$(e^\prime, \chi^\prime) \in  Copies((e,\chi),V)$ such that $v$ is
-%	the root of $(e^\prime,\chi^\prime)$.
-%\end{definition}
-%
-%\begin{definition} 
-%	Let $V\subset \N$ be a finite set of vertices. 
-%	Let $\Sigma_1,\dots, \Sigma_k$ be sets containing the empty label 
-%	$\emptyset$. For each $i\in [k]$ and each $n\in \N$
-%	let $\chi_i^n$ be a random $\Sigma_i$-coloring
-%	of $G_n$ satisfying that the succession $(\chi_i^n)_{n\in \N}$ is
-%	$V$-regular. We say that the sequences $(\chi_1^n)_{n\in \N},
-%	\dots, (\chi_k^n)_{n\in \N}$ are asymptotically independent
-%	with respect to edges intersecting $V$ if for any given
-%	\begin{itemize}
-%		\item fixed finite set of edges $S\subset E(\N)$ such that any edge $e\in S$ 
-%		contains some vertex in $V$,
-%		\item fixed disjoint sets of vertices $V_1,\dots, V_k \subset \bigcup_{e\in S}e$ 
-%		satisfying $V\cup V_i=\emptyset$ for all $i\in [k]$, and
-%		\item for each $i\in [k]$ and $v\in V_i$ a fixed label $s(v)\in \Sigma_i$
-%		different from the empty label,
-%	\end{itemize}
-%	it is satisfied 
-%	\[
-%	\Ln \mathrm{Pr}\big(
-%	\bigwedge_{i=1}^k \bigwedge_{v\in V_i} \chi_{n,i}(v)=s(v)
-%	\, \big| \, \bigwedge_{e\in S} e\subset G_n \,
-%	\big) = \prod_{i=1}^k \prod_{v\in V_i} \mathrm{Pr}\big[\chi_i=s(v)
-%	\big]		
-%	\]
-%\end{definition}
-%
-%
-%\begin{theorem}
-%	\begin{theorem}
-%		Let $k\in \N$.	For each $i\in [k]$ 
-%		\begin{itemize}
-%			\item Let $v_i\in \N$ be a vertex. Define $V:=\{v_1,\dots,v_k\}$.
-%			\item Let $\Sigma_i$ be a set containing the empty label, and let $S_i$ be a set
-%			of non-isomorphic rooted $\Sigma_i$-edges. 
-%			\item For each $n\in \N$ let $\chi^i_n$ be random $\Sigma_i$-coloring
-%			$G_n$ satisfying that the succession $(\chi^i_n)_{n\in \N}$ is $V$-regular. 
-%			\item For each $(e,\rho)\in S_i$, let $X^{(e,\rho)}_{n,i}$ be the random 
-%			variable that counts the number of copies in $Copies((e,\rho),([n],v_i))$
-%			that appear in $(G_n,\chi^i_n)$.				
-%		\end{itemize}
-%		Suppose that the
-%		successions $(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
-%		are independent with respect to edges intersecting $V$.
-%		Then, for any fixed natural numbers 
-%		$(a^{(e,\rho)}_{i})_{i\in [k], (e,\rho)\in S_i}$ it holds
-%		\[
-%		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k \bigwedge_{(e,\rho)\in S_i}
-%		 X_{n,i}=a^{(e,\rho)}_i  \big)=
-%		\prod_{i=1}^{k}e^{-\lambda_i}\frac{\lambda_{(e,\rho)}^{a^{(e,\rho)}_i}}{{a^{(e,\rho)}_i}!},
-%		\]
-%		where for each $i\in [k]$,
-%		\[
-%		\lambda_{(e,\rho)}:= \frac{1}{|Aut(e,\rho)|} 
-%		\prod_{v\in V(e), \rho(v)\neq \emptyset}
-%		\mathrm{Pr}\big[\chi^i=\rho^i(v)\big].
-%		\]
-%	\end{theorem}
-%\end{theorem}
-%
+\end{proof}
+
+\begin{lemma} \label{lem:disjointtrees}
+	Let $\overline{v}\in (\N)_*$ and let $r\in \N$. Then
+	a.a.s, for all vertices $v\in \overline{v}$ the neighborhoods 
+	$N(v;r)$'s are all trees and they are all disjoint. 
+\end{lemma}
+\begin{proof}
+	An application of the first moment method together with
+	\cref{lem:nocopiesfixed} and the fact that there are a finite number
+	of $\sim$ classes of paths whose length is at most $2r+1$ implies that
+	a.a.s the $N(v;r)$'s are disjoint. \par
+	Also, because of \cref{thm:sparse} a.a.s the $N(v;r)$'s are either 
+	trees or unicycles. But if any of the $N(v;r)$'s was an unicycle then
+	that would mean that in $G_n$ there exists a path $P$ of length at most
+	$2r+1$ joining some vertex $v\in \overline{v}$
+	with a cycle $C$ of diameter at most $2r+1$. Using \cref{lem:nocopiesfixed}
+	again as well as the fact that the number of $\sim$ classes of the possible hypergraphs
+	$P\cup C$ is finite we obtain that a.a.s no such $P$ and $C$ exist. 
+	In consequence all the $N(v;r)$'s are disjoint trees as we wanted to prove. \par
+\end{proof}
 
@@
 Our main tool for computing probabilities in the following sections
-will bethe following multivariate version of Brun's Sieve (
-Theorem 1.23, \cite{bollobas2001random}).
+will be the following multivariate version of Brun's Sieve 
+(Theorem 1.23, \cite{bollobas2001random}).
 
@@
 
+\begin{definition} \label{def:treeprobabilies}
 We define $\Lambda$ and $M$ as the minimal families
@@
 product $\lambda_1\lambda_2$ belongs to $\Lambda$ as well.
-\par
+\end{definition}
+
 The goal of this section is to show 
@@
 
-\begin{lemma}
+Before we proceed it will be useful to define the following abbreviation
+\begin{definition} Let $H$ be an hypergraph, $\overline{v}\in V(H)^*$, $v\in V(H)$ and
+	$r\in \N$. Then we define $\mathrm{Tr}(H,\overline{v};\, v;\, r)$ as
+	\[
+	\mathrm{Tr}\Big( Core(H,\overline{v};\,\,r),\overline{v}; \,\, v     \Big).
+	\]
+\end{definition}
+
+\begin{lemma}\label{lem:far_away}
 	Let $\overline{v} \subset \N*$ be a finite set of fixed vertices and let 
 	$\pi(\overline{x})$ be an edge sentence such that
-	$length(\overline{x})=length(\overline{v})$. 
+	$len(\overline{x})=len(\overline{v})$. 
 	Define $G_n^\prime=G_n \setminus E[\overline{v}]$ (i.e. $G_n$ minus all the
@@
 	=\mathrm{Pr}(B_n)$.\par
-	The equation $\Ln \mathrm{Pr}(A_n)=0$ follows from
-	 \cref{lem:nocopiesfixed} using that 
-	(1) the excess of any path is greater or equal than $-1$,
-	(2) the amount of paths with length at most $R$ is finite.
-	The equation $\Ln \mathrm{Pr}(B_n)=0$ is also deduced from
-	\cref{lem:nocopiesfixed} using that
-	(1) any hypergraph $H$ consisting
-	of a path of length at most $R$ joining cycle with diameter at most 
-	$R$ satisfies that $ex(H)\geq 0$, and (2) the
-	amount of such hypergraphs is finite. 
+	Now both $\Ln \Pr(A_n)=0$ and $\Ln Pr(B_n)=0$ follow from 
+	\cref{lem:disjointtrees} using that $G^\prime_n\subset G_n$.  
 \end{proof}
 
-\begin{corollary}\label{cor:disjointtrees}
-	Let $\overline{v}\in (\N)_*$ be a finite set of vertices 
-	and let $\pi(\overline{x})$ be an edge sentence such that
-	$len(\overline{v})=len(\overline{x})$. 
-	Define $G_n^\prime=G_n \setminus E[\overline{v}]$. 
-	Fix $r\in \N$.
-	Let $U_n$ be the event that for all $v\in \overline{v}$
-	the neighborhoods $N^{G^\prime_n}(v;r)$ are disjoint trees.
-	Then
-	\[
-	\Ln \PR{U_n \, \big| \, \pi(\overline{v})}=1.\]
-	In particular, for all $v\in \overline{v}$, a.a.s
-	\[
-	Tr\big(G_n,\overline{v};\, v;\, r)=N^{G^\prime_n}(v;r).
-	\]
-\end{corollary}
-\begin{proof}
-	As in the previous lemma, because edges are independent 
-	in our random model, \[
-	\PR{U_n \, \big| \, \pi(\overline{v})}
-	=\PR{U_n}\]
-	 for all $n$. Because of the previous lemma
-	a.a.s there is no path in $G^\prime_n$ of length at most $2r+1$ joining 
-	any two vertices in $\overline{v}$. In consequence a.a.s
-	the $N^{G^\prime_n}(v;r)$'s are disjoint.\par
-	Also, because of \cref{thm:sparse} a.a.s there are no dense
-	hypergraphs with diameter at most $r$ in $G_n$, 
-	so a.a.s the  $N^{G^\prime_n}(v;r)$'s are not dense.\par
-	Finally, because of the previous lemma, a.a.s 
-	none of the vertices in $\overbar{v}$ is at a distance
-	lesser than $r$ to a cycle of diameter at most $r$.
-	In consequence a.a.s all the $N^{G^\prime_n}(v;r)$'s are trees, 
-	as we wanted to prove. 	 
-\end{proof}
-\todo[inline]{Explicar N(v;r)=Tr(G;v;r)}.
+\sep
+%\begin{corollary}\label{cor:disjointtrees}
+%	Let $\overline{v}\in (\N)_*$ be a finite set of vertices 
+%	and let $\pi(\overline{x})$ be an edge sentence such that
+%	$len(\overline{v})=len(\overline{x})$. 
+%	Define $G_n^\prime=G_n \setminus E[\overline{v}]$. 
+%	Fix $r\in \N$.
+%	Let $U_n$ be the event that for all $v\in \overline{v}$
+%	the neighborhoods $N^{G^\prime_n}(v;r)$ are disjoint trees.
+%	Then
+%	\[
+%	\Ln \PR{U_n \, \big| \, \pi(\overline{v})}=1.\]
+%	As a consequence, for all $v\in \overline{v}$,
+%	\[
+%	\Pr\Big(Tr\big(G_n,\overline{v};\, v;\, r)=N^{G^\prime_n}(v;r)\, 
+%	\Big| \, \pi(\overline{v}) \Big)=1.
+%	\]
+%\end{corollary}
+%\begin{proof}
+%	As in the previous lemma, because edges are independent 
+%	in our random model, \[
+%	\PR{U_n \, \big| \, \pi(\overline{v})}
+%	=\PR{U_n}\]
+%	 for all $n$. Because of the previous lemma
+%	a.a.s there is no path in $G^\prime_n$ of length at most $2r+1$ joining 
+%	any two vertices in $\overline{v}$. In consequence a.a.s
+%	the $N^{G^\prime_n}(v;r)$'s are disjoint.\par
+%	Also, because of \cref{thm:sparse} a.a.s there are no dense
+%	hypergraphs with diameter at most $r$ in $G_n$, 
+%	so a.a.s the  $N^{G^\prime_n}(v;r)$'s are not dense.\par
+%	Finally, because of the previous lemma, a.a.s 
+%	none of the vertices in $\overbar{v}$ is at a distance
+%	lesser than $r$ to a cycle of diameter at most $r$.
+%	In consequence a.a.s all the $N^{G^\prime_n}(v;r)$'s are trees, 
+%	as we wanted to prove. 	 \par
+%	The fact that for all $v\in \overline{v}$ a.a.s
+%	$
+%	Tr\big(G_n,\overline{v};\, v;\, r)=N^{G^\prime_n}(v;r)
+%	$
+%	is deduced from the fact that if some 
+%	$u\in V\Big(N^{G^\prime_n}(v;r) \Big)$ does not belong
+%	to $Tr\big(G_n,\overline{v};\, v;\, r)$, then 
+%	either (a) $u$ belongs to a path in $G_n^\prime$
+%	of length at most $2r+1$ 
+%	between $v$ and another vertex $w\in \overline{v}$, 
+%	(b) $u$ belongs to a cycle in $G^\prime_n$ of diameter
+%	at most $2r+1$ which contains $v$, or
+%	(c) $u$ belongs to a path in $G_n^\prime$
+%	of length at most $2r+1$ between $v$ and some cycle
+%	in $G_n^\prime$ of diameter at most $2r+1$. But as the
+%	$N^{G^\prime_n}(v;r)$'s a.a.s are disjoint trees none of 
+%	(a),(b),(c) hold with positive probability. 
+%\end{proof}
+%
+%
+%\sep
 
@@
 		\item[(1)] Let $\mathcal{T}$ be a
-		$k$-equivalence class for trees with radii at most $r$.
-		Then 
-		\[
-		\Ln  \PR{Tr\big(G_n;\,\,v;\,\,r\big)\in \mathcal{T}}
-		=\mathrm{Pr}[r,\mathcal{T}]
-		\]
-		exists and is an expression
-		in $\Lambda$.
+		$k$-equivalence class for trees with radii at most $r$. Let
+		$v\in \N$ be a vertex.	Then 
+		\[
+		\mathrm{Pr}[r,\mathcal{T}]:=\Ln  \PR{Tr\big(G_n,v;\,\,v;\,\,r\big)\in \mathcal{T}}
+		\]
+		exists,
+		is positive for all choices of 
+		$\{\beta_R\}_{R\in \epsilon}\in [0,\infty)^{|\sigma|}$,
+		and is an expression
+		in $\Lambda$ that depends only on the choice of $r$ and $\mathcal{T}$.
 		\item[(2)] Let $\overline{u}\in (\N)_*$ be a list of different fixed 
@@
 \end{proof}
-
-%		Now let $r>0$ and assume that both (1) and (2) hold for all 
-%
-%		Via similar computations we can show that for any fixed
-%		$v\in \overline{v}$.
-%		
-%		We are going to show that the variables $X_{n,i,\epsilon}$ converge, as
-%		$n$ tends to infinity, to independent Poisson variables 
-%		$\mathrm{Poiss}(\mu_{r_i,\epsilon})$ whose means $\mu_{r_i,\epsilon}$ 
-%		are expressions in the family $M$. Let $[\Sigma_{r_i}]$ be the set of
-%		$\Sigma_{r_i}$-patterns. We want to prove: 
-%		\begin{equation} \label{eqn:PoissonEdges}
-%		\Ln \mathrm{Pr}\Big(
-%		\bigwedge_{i=1}^k \bigwedge_{\epsilon \in [\Sigma_{r_i}]} X_{n,i,\epsilon}=a_{i,\epsilon}
-%		\, | \, \sigma(\overline{w})\Big) =
-%		\prod_{i=1}^k \prod_{\epsilon \in [\Sigma_{r_i}]} e^{-\mu_{r_i,\epsilon}}
-%		\frac{(\mu_{r_i,\epsilon})^{a_{i,\epsilon}}}{a_{i,\epsilon}!}
-%		\end{equation}
-%		Furthermore, for each $i$ and $\epsilon$ we will prove that the mean 
-%		$\mu_{r_i,\epsilon}$ does only depend on $r_i$ and $\epsilon$.
-%		This proves both (1), and (2).\par
-%		Given an $\Sigma_{r_i}$-pattern $\epsilon$ and any 
-%		$(e,\chi)\in Copies(\epsilon,[n])$ we say that $(e,\chi)\in T_{n,i}$
-%		if the following are satisfied: (1)	$e$ is an initial edge of $T_{n,i}$,
-%		and	(2) that for any $v\in e$ such that $v\neq v_i$, it holds that
-%		$\chi(v)$ is the $\simeq_k$ class of $Tr(T_{n,i},v)$.\par 
-%		Given $r\in \N$ and $\epsilon\in \Sigma_{r}$
-%		we define
-%		$\mu_{r,\epsilon}$ as follows. Let $(e,\chi)$ be any representative of
-%		$\epsilon$. Then
-%		\[\mu_{r,\epsilon}=  \frac{\beta_{R(e)}}{|Aut(e,\chi)|}
-%		\prod_{\substack{v\in e\\ \chi(v)\neq \tau }} \Pr[r,\chi(v)]. \]
-%		For each $i\in [l]$ and $\epsilon\in [\Sigma_{r_i}]$ let 		
-%		$b_{i,\epsilon}\in \N$ be fixed. 
-%	
-%		We want to prove
-%		\[
-%		\Ln \mathrm{E}\left[\prod_{\substack{i\in [l]\\ \epsilon \in [\Sigma_{r_i}]}} \binom{X_{n,i,\epsilon}}{b_{i,\epsilon}}
-%		\right]= \prod_{\substack{i\in [l]\\ \epsilon \in [\Sigma_{r_i}]}}
-%		\frac{(\mu_{r_i,\epsilon})^{b_{i,\epsilon}}}{b_{i,\epsilon}!}.
-%		\]
-%		Because \cref{thm:BrunSieve} this is sufficient to prove \cref{eqn:PoissonEdges}. \par
-%		For each $n\in \N$ define
-%		\begin{align*}
-%		\Omega_n=&\Bigg\{
-%		(E_{v,\epsilon})_{\substack{v\in \overline{v}\\ \epsilon
-%		\in [\Sigma_{r(v)}]}} \quad \Big|\\ 
-%		&  \forall v\in \overline{v},
-%		\forall \epsilon \in [\Sigma_{r(v)}]\, \quad  E_{v,\epsilon}\subset
-%		Copies(\epsilon,[n],\overline{w};v)\quad  \wedge \quad |E_{v,\epsilon}|=b_{v,\epsilon}\Bigg\}.
-%		\end{align*}
-%		Informally, the elements $(E_{v,\epsilon})_{v,\epsilon}$
-%		of $\Omega_n$ are represent all choices of
-%		possible initial edges for the $T_{n,v}$'s: For each $v\in \overline{v}$
-%		and each $\epsilon\in [\Sigma_{r(v)}]$, $E_{n,v,\epsilon}$ selects
-%		$b_{v,\epsilon}$ possible initial edges of $T_{n,v}$
-%		with pattern $\epsilon$.\par
-%%	 	Given an element $O\in \Omega_n$, with
-%%	 	$O=\big(O_{i,\epsilon}\big)_{i\in [l], \epsilon \in [\Sigma_{r_i}]}$,
-%%	 	we write $O\in G_n$ if
-%		Using observation REF we obtain that
-%		\[
-%		\mathrm{E}\Big[\prod_{\substack{i\in [l]\\ \epsilon \in [\Sigma_{r_i}]}} \binom{X_{n,i,\epsilon}}{b_{i,\epsilon}}
-%		\Big]= \sum_{(E_{v,\epsilon})_{v,\epsilon} \in \Omega_n
-%		}		
-%		\Pr \left( \bigwedge_{\substack{v\in \overline{v} \\ \epsilon \in
-%		[\Sigma_{r(v)}]\\ (e,\chi) \in E_{v,\epsilon} }} \left( e\in E(T_{n,i}) 
-%		\bigwedge_{u\in V(e), u\neq v} Tr(T_{n,v};u)\in \chi(u)
-%		\right)  \right)
-%		\]
-%		Let $(E_{v,\epsilon})_{v,\epsilon}\in \Omega_n$. 
-%		In order for $e\in E(T_{n,v})$ to be possible for all
-%		$v\in \overline{v}$, $\epsilon\in [\Sigma_{r(v)}]$, 
-%		$e\in E_{v,\epsilon}$ it is needed that each vertex 
-%		in $[n]\setminus \overline{w}$ belongs at most to one
-%		edge $(e,\chi)\in \cup_{v,\epsilon} \, E_{v,\epsilon}$.
-%		This is because if for some 
-%		\[
-%		\bigwedge_{\substack{i\in [l]\\ \epsilon \in
-%		[\Sigma_{r_i}]\\ (e,\chi) \in O_{i,\epsilon} }} \left( e\in E(T_{n,i}) 
-%		\bigwedge_{v\in e, v\neq v_i} Tr(T_{n,i},v)\in \chi(v)
-%		\right) 
-%		\] 
-%		to be possible it is needed that each $v\in $
+\sep
 
@@
 
-	\begin{lemma}
+	\begin{lemma} \label{lem:singletreeprob}
 	Let $r\in \N$, $r>0$. Let $\mathcal{T}$ be a 
-	$\sim_k$ class of trees with radii at most $r$.
+	$\sim_k$ class of trees with radii at most $r$ and 
+	let $v\in \N$ be any vertex. 
 	Suppose that \cref{thm:BigTrees} holds
-	for $r-1$. Then $\Pr\big[r, \mathcal{T}\big]$ 
-	exists and is and expression in $\Lambda$.   
+	for $r-1$. Then \[
+	\Pr\big[r, \mathcal{T}\big]:=
+	\Ln  \PR{Tr\big(G_n,v;\,\,v;\,\,r\big)\in \mathcal{T}}
+	\] 
+	exists, is positive for all choices of 
+	$\{\beta_R\}_{R\in \epsilon}\in [0,\infty)^{|\sigma|}$,
+	and is and expression in $\Lambda$ that depends
+	only on the choice of $r$ and $\mathcal{T}$.   
 	\end{lemma}
 	\begin{proof}
-		Fix a vertex $v\in \N$. For each $n$ let
-		$T_n:=Tr(G_n,v;r)$. We are going to show that
-		$\Ln \PR{T_n\in \mathcal{T}}$ exists and it is an 
-		expression in $\Lambda$. \par
 		For any $(k,r)$-pattern  $\epsilon$  let 
 		$X_{n,\epsilon}$ be the random variable that counts
-		the initial edges in $T_n$ whose $k$-pattern
-		is $\epsilon$. First we are going to show that for any
-		$(k,r)$-pattern $\epsilon$, the means $E[X_{n,\epsilon}]$
-		converge, as $n$ tends to infinity, to an expression in $M$.
+		the initial edges $e\in E(T_n)$ whose pattern
+		is $\epsilon$ (i.e. $(e,\tau_{(T_n,v)})\in \epsilon$). 
+		Fix a pattern $\epsilon\in P(k,r)$.
+		we define the expressions $\lambda_{r,\epsilon}$ and
+		 $\mu_{r,\epsilon}$ 
+		as follows: let $(e,\tau)$ be a representative of $\epsilon$
+		whose root is $v$. Then
+		\[
+		\lambda_{r,\epsilon}=\prod_{\substack{u\in V(e)\\ u\neq v} } \Pr\big[
+		r-1, \tau(u)\big], \quad \text{ and } \quad
+		\mu_{r,\epsilon}=\frac{\beta_{R(e)}}{\aut(\epsilon)} 
+		\cdot \lambda_{r,\epsilon}.
+		\]
+		Clearly the definitions of $\lambda_{r,\epsilon}$ and $\mu_{r,\epsilon}$
+		are independent from the representative $(e,\tau)$ and by hypothesis
+		depend only on the choice of $r$ and $\epsilon$. By hypothesis it also holds
+		that $\mu_{r,\epsilon}$ is positive for all values of
+		$\{ \beta_R \}_{R\in \sigma}\in [0,\infty)^{|\sigma|}$.
+		 Furthermore, 
+		$\mu_{r,\epsilon}$ belongs to $M$.\par
+		First we are going to show that for any
+		$(k,r)$-pattern $\epsilon$ it holds that
+	 	\[
+	 	\Ln E[X_{n,\epsilon}] = \mu_{r,\epsilon}.
+	 	\]
+	 	This step is not necessary for the proof as a whole but serves as a 
+	 	simple example that showcases the methods used.		
+		\par
 		Fix a $(k,r)$-pattern $\epsilon$. 
@@
 		$|Copies(\epsilon,[n];(v,\rho))|=\frac{(n)_{|e|-1}}
-		{|Aut(\epsilon)|}$ we obtain
+		{\aut(\epsilon)}$ we obtain
 		\[
@@
 		\end{align*}
-		Because of \cref{cor:disjointtrees}, a.a.s if $e\in E(G_n)$
+		Because of \cref{lem:far_away}, a.a.s $T_n=N(v;r)$ so a.a.s if
+		$e\in E(G_n)$
 		and $v\in V(e)$, then $e\in E(T_n)$. Also,
@@
 		Fix $\overline{u}\in (\N)_*$ a list that contains exactly the vertices
-		in $e$. Then it holds that
-		$Tr(T_{n}, v, u)=Tr(G_n(\overline{u}),u;r-1)$. 
+		in $e$. Notice that the event $e\in E(G_n)$ clearly can be described
+		by an edge sentence
+		over the vertices in $\overline{u}$.
+		Because of \cref{lem:far_away},
+		\[
+		\Ln \Pr\Big(
+		N^{G_n}(v;r) \text{ is a tree } \Big| \, \, e\in E(G_n) \Big)=1.
+		\] 
+		Set $G^\prime_n:=G_n \setminus e$.
+		In the case that $T_n= N(v;r)$ and $e\in E(G_n)$ then
+		the following chain of equalities holds for all 
+		$u\in \overline{u}$ different from $v$:
+		\[
+		Tr(T_{n}, v, u)=N^{G^\prime_n}(u;\,r-1)=Tr(G_n,\overline{u};\, u;\, r-1).
+		\] 
 		Thus,
-		\[
-		\Pr	\left(
+		\begin{align}
+		\nonumber
+		&\Pr	\left(
 		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_{n}, v; u)\in \tau(u) 
 		\, \Bigg| \,  e\in E(G_n) \right)
-		=
+		\sim\\ \label{eqn:equaltrees}
+		&
 		\Pr \left(
-		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(G_n(\overline{u}), u;
-		r-1)\in \tau(u) \, \Bigg| \,  e\in E(G_n) \right)
-		\]		
-		The event $e\in E(G_n)$ can be written as an edge sentence
-		whose variables are interpreted as vertices in $\overline{u}$.
-		Thus, by hypothesis, the RHS of last equality
+		\bigwedge_{\substack{u\in V(e)\\ u\neq v} }
+		Tr(G_n,\overline{u};\, u;\, r-1)
+		\in \tau(u) \, \Bigg| \,  e\in E(G_n) \right)
+		\end{align}
+
+		By hypothesis, the RHS of last equality
 		is asymptotically equivalent to
 		$\prod_{\substack{u\in V(e)\\ u\neq v} } \Pr\big[
-		r-1, \tau(u)\big]$.
+		r-1, \tau(u)\big]=\lambda_{r,\epsilon}$.
 		Finally, joining everything we obtain
@@
 		\mathrm{E}\big[ X_{n,\epsilon} \big]
-		= \Ln \frac{(n)_{|e|-1}}{|Aut(\epsilon)|}
+		= \Ln \frac{(n)_{|e|-1}}{\aut(\epsilon)}
 		\cdot  \frac{\beta_{R(e)}}{n^{|e|-1}}
@@
 		r-1, \tau(u)\big] =
-		\frac{\beta_{R(e)}}{|Aut(\epsilon)|} 
-		\prod_{\substack{u\in V(e)\\ u\neq v} } \Pr\big[
-		r-1, \tau(u)\big],
-		\]
-		and the last expression belongs to $M$, as we wanted.\par
-
-		For each pattern $\epsilon\in P(k,r)$ we define $\mu_{r,\epsilon}$ 
-		as follows: let $(e,\tau)$ be a representative of $\epsilon$
-		whose root is $v$. Then
-		\[
-		\mu_{r,\epsilon}=\frac{\beta_{R(e)}}{|Aut(\epsilon)|} 
-		\prod_{\substack{u\in V(e)\\ u\neq v} } \Pr\big[
-		r-1, \tau(u)\big].
-		\]
-		Notice that $\mu_{r,\epsilon}$, besides belonging to $M$, 
-		depends only on $r$ and $\epsilon$. \par
-		We are going to prove that the variables $X_{n,\epsilon}$
+		\frac{\beta_{R(e)}}{\aut(\epsilon)} 
+		\cdot \lambda_{r,\epsilon}= \mu_{r,\epsilon},
+		\]
+		as we wanted.\par
+		Now we are going to prove that the variables $X_{n,\epsilon}$
 		converge in distribution to independent Poisson variables 
@@
 		u\in V(e)\\
-		u\neq v}} Tr(T_n,v,u)\in \tau(u)		
+		u\neq v}} Tr(T_n,v;u)\in \tau(u)		
 		\right)
@@
 				u\in V(e)\\
-				u\neq v}} Tr(T_n,v,u)\in \tau(u)		
+				u\neq v}} Tr(T_n,v;u)\in \tau(u)		
 		\right)
@@
 		we obtain
-		\[
+		\begin{equation} \label{eqn:aux2}
 		\mathrm{E}
@@
 				u\in V(e)\\
-				u\neq v}} Tr(T_n,v,u)\in \tau(u)		
+				u\neq v}} Tr(T_n,v;u)\in \tau(u)		
 		\right)
 		\right). 		
-		\] 
-		Let $\overline{w}\in (\N)_*$ be a list containing exactly
-		the vertices $u\in V(e)$ for all $e\in 
-		\bigcup_{\epsilon\in P(k,r)} E_\epsilon$. Then, 
-		for any $e\in 
-		\bigcup_{\epsilon\in P(k,r)} E_\epsilon$ and any
-		any $V(e)$ with $u\neq v$ it holds that
-		if $e\in E(T_n)$ then 
-		$Tr(T_n,v,u)=Tr(G_n,\overline{w},u;r-1)$. Then
-		\[
-		\mathrm{E}
-		\left[
-		\prod_{\epsilon\in P(k,r)} \binom{X_{n,\epsilon}}{b_\epsilon}	
-		\right]
-		= 
-		|\Omega_n^\prime|\cdot
-		\Pr\left(
-		\bigwedge_{\substack{
-				\epsilon\in P(k,r)\\
-				(e, \tau)\in E_{\epsilon}
-		}} \left(
-		e\in E(T_n) \bigwedge_{\substack{
-				u\in V(e)\\
-				u\neq v}} Tr(G_n,\overline{w},u;r-1)\in \tau(u)		
-		\right)
-		\right). 		
-		\] 
+		\end{equation}
+
 		Counting vertices and automorphisms we get that
-		\[
+		\begin{equation} \label{eqn:aux3}
 		|\Omega_n^\prime|= (n)_{\sum_{\epsilon\in P(k,r)} 
@@
 		\frac{1}{b_\epsilon!} \cdot
-		\left( \frac{1}{|Aut(\epsilon)|} \right)^
+		\left( \frac{1}{\aut(\epsilon)} \right)^
 		{b_\epsilon} .
-		\]
-		Because of \cref{cor:disjointtrees} a.a.s if $e\in E(G_n)$
+		\end{equation}
+		Because of \cref{lem:far_away} a.a.s if $e\in E(G_n)$
 		and $v\in V(e)$, then $e\in E(T_n)$. In consequence:
-		\begin{align*}
+		\begin{align} \label{eqn:aux4}
 		&\Pr\left(
@@
 				u\in V(e)\\
-				u\neq v}} Tr(G_n,\overline{w},u;r-1)
+				u\neq v}} Tr(T_n;\, u)
 			\in \tau(u)		
 		\right)
-		\right)\sim\\
+		\right)\sim\\ \nonumber
 		&\Pr\left(
@@
 				u\neq v
-		}}Tr(G_n,\overline{w},u;r-1)\in \tau(u)	
+		}}Tr(T_n;\, u)\in \tau(u)	
 		\, \Bigg| \, 
@@
 		\right).
-		\end{align*}
+		\end{align}
+	Let $\overline{w}\in (\N)_*$ be a list containing exactly
+	the vertices $u\in V(e)$ for all $e\in 
+	\bigcup_{\epsilon\in P(k,r)} E_\epsilon$. 
 	The event 
@@
 	}} e\in E(G_n)$ clearly can be described via an edge sentence
-	whose variables are interpreted as vertices in $\overline{w}$. Thus,
-	by hypothesis last product of probabilities is asymptotically equivalent
+	whose variables are interpreted as vertices in $\overline{w}$.
+	Thus, analogously to \cref{eqn:equaltrees}
+	we obtain 
+	\begin{align} \label{eqn:aux5}
+	&	\Pr\left(
+	\bigwedge_{\substack{
+			\epsilon\in P(k,r)\\
+			(e, \tau)\in E_{\epsilon}
+	}} \left(
+	e\in E(T_n) \bigwedge_{\substack{
+			u\in V(e)\\
+			u\neq v}} Tr(T_n,v;u)\in \tau(u)		
+	\right) \, \, \Big| \, \,
+	\bigwedge_{\substack{
+			\epsilon\in P(k,r)\\
+			(e, \tau)\in E_{\epsilon}
+	}} e\in E(G_n)\,	
+	\right)\sim \\ \nonumber
+	&
+	\Pr\left(
+	\bigwedge_{\substack{
+			\epsilon\in P(k,r)\\
+			(e, \tau)\in E_{\epsilon}
+	}} \left(
+	e\in E(T_n) \bigwedge_{\substack{
+	u\in V(e)\\
+	u\neq v}}
+	Tr(G_n,\overline{w};\, u;\, r-1)\in \tau(u)		
+	\right)\, \, \Big| 
+	\, \,
+	\bigwedge_{\substack{
+	\epsilon\in P(k,r)\\
+	(e, \tau)\in E_{\epsilon}
+	}} e\in E(G_n)\,
+	\right)
+	\end{align}
+	By hypothesis last probability is asymptotically equivalent
 	to
 	\[
-	\prod_{\epsilon\in P(k,r)}
-	\left(\frac{\beta_{R(\epsilon)}}
-	{n^{|\epsilon|-1}}\right)^{b_\epsilon} \cdot
 	\prod_{\epsilon\in P(k,r)} (\lambda_{r,\epsilon})^{b_\epsilon}.
 	\]
-	Joining everything we obtain 
+	Joining this with \cref{eqn:aux2},
+	\cref{eqn:aux3}, \cref{eqn:aux4} and \cref{eqn:aux4} we obtain 
 	\begin{align*} 
@@
 	\frac{1}{b_\epsilon!} \cdot
-	\left( \frac{\beta_{R(\epsilon)}}{|Aut(\epsilon)|} \right)^
+	\left( \frac{\beta_{R(\epsilon)}}{\aut(\epsilon)} \right)^
 	{b_\epsilon} \cdot 
@@
 	\]
-%	Notice that, because of the definition of $\simeq_k$, 
-%	the event $T_n\in \mathcal{T}$ is equivalent to 
-%	\[
-%	\left(\bigwedge_{\epsilon \in E^1_\mathcal{T}}
-%	X_{n,\epsilon}\geq k 
-%	\right) \wedge \left(\bigwedge_{\epsilon \in E^2_\mathcal{T}}
-%	X_{n,\epsilon}=a_\epsilon\right),
-%	\]
-%	for some partition $E^1_\mathcal{T}, E^2_\mathcal{T}$
-%	of $P(k,r)$ that only depends on $\mathcal{T}$ and some
-%	natural numbers $a_\epsilon < k$ for each $\epsilon\in
-%	E^2_\mathcal{T}$ that only depend on $\mathcal{T}$ as well. 
-%	In consequence 
+
 	Finally, using \cref{obs:equivalenttrees} we get that for some
@@
 	$\epsilon\in E^2_\mathcal{T}$ it holds that
-	\[
+	\[ \PR[r,\mathcal{T}]=
 	\Ln \PR{T_n\in \mathcal{T}}= 
@@
 	\]
-	And last expression belongs to $\Lambda$ as we wanted to prove. 
+	And last expression belongs to $\Lambda$ as we wanted to prove. Furthermore,
+	as the $\mu_{r,\epsilon}$'s are positive, this expression is also 
+	positive for all values of
+	$\{ \beta_R \}_{R\in \sigma}\in [0,\infty)^{|\sigma|}$.
+ 	\end{proof}
+\sep
+
+	In order for \cref{thm:BigTrees} to be completely proven the following result is needed
+
+	\begin{lemma}
+		Let $r\in \N$ be a positive number.
+		Let $\overline{u}\in (\N)_*$ be a list of different fixed 
+		vertices, and let $\pi(\overline{x})\in FO[\sigma]$ be an
+		edge sentence such that 
+		$len(\overline{x})=len(\overline{u})$.
+		Let $\overline{v}\in (\N)_*$ be vertices contained
+		in $\overline{u}$. For each $v\in \overline{v}$
+		let $\mathcal{T}_v$ be a $k$-equivalence class
+		of trees with radii	at most $r$. Suppose that
+		\cref{thm:BigTrees} holds for $r-1$. Then
+		\[
+		\Ln \mathrm{Pr}\big( \bigwedge_{v\in \overline{v}} 
+		Tr\big(G_n, \overline{u};\,\,v;\,\,r\big)\in \mathcal{T}_v 
+		\, | \, \pi(\overline{u})
+		\big)= \prod_{v\in \overline{v}} \mathrm{Pr}[r,\mathcal{T}_v]. \]	 
+	\end{lemma}
+	\begin{proof}[Sketch of the proof.]
+		The proof is completely analogous to the one 
+		of the previous lemma but now with more 
+		random variables. For each $v\in \overline{v}$ we define
+		$T_{n,v}:=Tr\big(G_n, \overline{u};\,\,v;\,\,r\big)$.
+		Given a $(k,r)$-pattern $\epsilon\in P(k,r)$ and a vertex
+		$v\in \overline{v}$ we define the random variable 
+		$X_{n,v,\epsilon}$ as the one that counts the number of initial
+		edges $e\in E(T_{n,v})$ whose pattern is $\epsilon$. Similarly to last lemma
+		one can show that the $X_{n,v,\epsilon}$ are asymptotically distributed
+		like independent Poisson variables whose respective means are the
+		$\mu_{r,\epsilon}$ defined in the previous lemma. As before, this is done using 
+		\cref{thm:BrunSieve}, by computing the binomial moments of the $X_{n,v,\epsilon}$'s.
+		Once the asymptotic distribution of those variables is computed the identity
+		\[\Ln \mathrm{Pr}\big( \bigwedge_{v\in \overline{v}} 
+		Tr\big(G_n, \overline{u};\,\,v;\,\,r\big)\in \mathcal{T}_v 
+		\, | \, \pi(\overline{u})
+		\big)= \prod_{v\in \overline{v}} \mathrm{Pr}[r,\mathcal{T}_v]
+		\]
+		follows easily using the definition of $\mathrm{Pr}[r,\mathcal{T}_v]$ 
+		provided at the end of last proof. 
 	\end{proof}
@@
 		\]
-		Also, because of \cref{cor:disjointtrees} we have that $\Ln \phi_n(\overline{v})=1$,
+		Also, because of \cref{lem:far_away} we have that $\Ln \phi_n(\overline{v})=1$,
 		and in consequence for $m$ sufficiently big
@@
 
+\begin{definition}
+	We define $\Gamma$ and $\Upsilon$ as the minimal families of expressions with arguments
+	$\{\beta_R\}_{R\in \sigma}$ that satisfies the conditions:
+	\begin{itemize}
+	\item[(1)] For each $R\in \sigma$ let $a_R\in \N$ be any natural number. Then, given any positive number $b\in \N$
+	and any $\lambda\in \Lambda$ the expression $\frac{\lambda}{b}\cdot \prod_{R\in \sigma} \beta_R^{a_R}$
+	belongs to $\Gamma$.
+	\item[(2)] Given any $\gamma\in \Gamma$ and any $a\in \N$, the expressions $\mathrm{Poiss}_a(\gamma)$
+	and $\mathrm{Poiss}_{\geq a}(\gamma)$ both belong to $\Upsilon$.
+	\item[(3)] If $\upsilon_1, \upsilon_2\in \Upsilon$ then 
+	$\upsilon_1\cdot \upsilon_2 \in \Upsilon$ as well. 
+	\end{itemize}
+\end{definition}
+
 \begin{theorem}\label{thm:agreeabilityprobabilities}
@@
 	$\Ln \PR{G_n\in \mathcal{O}}$ exists and is an expression
-	in $\Theta$. 
+	in $\Upsilon$. 
 \end{theorem}
@@
 	that counts the number of cycles in $Core(G_n;r)$ 
-	whose $k$-type is $O$. Fix $O\in C(k,r)$. It holds
-	\[
-	\mathrm{E}\big[ X_{n,O}\big]
-	=\sum_{(H,\tau)\in Copies(0,[n])} \Pr\left(
-	H\subset G_n \bigwedge_{v\in V(H)} 
-	Tree(G_n, v;r)\in \tau(v)
-	\right)	
-	\]
-	Because of the symmetry of the random model last probability is the 
-	same for all $(H,\tau)\in Copies(O,[n])$. Fix $(H,\tau)\in
-	Copies(O,\N )$. Then
-	\begin{align*}
-	\mathrm{E}\big[ X_{n,O}\big]
-	&=\frac{(n)_{|V(H)|}}{|Aut(H,\tau)|} 
-	\cdot \Pr\left(
-	H\subset G_n \bigwedge_{v\in V(H)} 
-	Tree(G_n, v;r)\in \tau(v)
-	\right)	\\
-	&=\frac{(n)_{|V(H)|}}{|Aut(H,\tau)|}\cdot
-	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}{n^{|V(H)|}}\cdot
-	\Pr\left(\bigwedge_{v\in V(H)} 
-	Tr(G_n, v;r)\in \tau(v)
-	\quad  \Big| \quad H\subset G_n
-	\right)\\
-	&\sim 
-	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
-	{|Aut(H,\tau)|}\cdot
-	\Pr\left(\bigwedge_{v\in V(H)} 
-	Tr(G_n, v;r)\in \tau(v)
-	\quad  \Big| \quad H\subset G_n
-	\right)
-	\end{align*}
-	Let $\overline{v}\in (\N)_*$ be a list containing 
-	exactly the vertices in $V(H)$. If $H\subset G_n$
-	then $Tr(G_n, v;r)=Tr(G_n,\overline{v},v;r)$. Also,
-	the event $H\subset G_n$ clearly can be described via
-	an edge sentence concerning the vertices in $\overline{v}$.
-	In consequence, using \cref{thm:BigTrees}, last expression
-	is asymptotically equivalent to
-	\[
-	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
-	{|Aut(H,\tau)|}\cdot
-	\prod_{v\in V(H)}
-	\Pr \big[ r, \tau(v) \big].
-	\]
+	whose $k$-type is $O$. Fix $O\in C(k,r)$.
 	For any $O\in C(k,r)$ we define $\lambda_O$ and 
-	$\omega_O$ in the following way. Let $(H,\tau)$ be
+	$\gamma_O$ in the following way. Let $(H,\tau)$ be
 	a representative of $O$. Then
@@
 	\[
-	\omega_O:=
+	\gamma_O:=
 	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
-	{|Aut(H,\tau)|}\cdot\lambda_O.
-	\]
+	{\aut(H,\tau)}\cdot\lambda_O.
+	\]	
+	As in the proof of 
+	\cref{lem:singletreeprob} one can show that
+	\[
+	\Ln \mathrm{E}\big[ X_{n,O}\big]
+	= \gamma_O
+	\].
+	Notice that the expression $\gamma_O$ both belongs to $\Gamma$ and
+	does only depend on the $(k,r)$-cycle $O$. \par
+%	Because of the symmetry of the random model last probability is the 
+%	same for all $(H,\tau)\in Copies(O,[n])$. Fix $(H,\tau)\in
+%	Copies(O,\N )$. Then
+%	\begin{align*}
+%	\mathrm{E}\big[ X_{n,O}\big]
+%	&=\frac{(n)_{|V(H)|}}{\aut(H,\tau)} 
+%	\cdot \Pr\left(
+%	H\subset G_n \bigwedge_{v\in V(H)} 
+%	Tree(G_n, v;r)\in \tau(v)
+%	\right)	\\
+%	&=\frac{(n)_{|V(H)|}}{\aut(H,\tau)}\cdot
+%	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}{n^{|V(H)|}}\cdot
+%	\Pr\left(\bigwedge_{v\in V(H)} 
+%	Tr(G_n, v;r)\in \tau(v)
+%	\quad  \Big| \quad H\subset G_n
+%	\right)\\
+%	&\sim 
+%	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
+%	{\aut(H,\tau)}\cdot
+%	\Pr\left(\bigwedge_{v\in V(H)} 
+%	Tr(G_n, v;r)\in \tau(v)
+%	\quad  \Big| \quad H\subset G_n
+%	\right)
+%	\end{align*}
+%	Let $\overline{v}\in (\N)_*$ be a list containing 
+%	exactly the vertices in $V(H)$. If $H\subset G_n$
+%	then $Tr(G_n, v;r)=Tr(G_n,\overline{v},v;r)$. Also,
+%	the event $H\subset G_n$ clearly can be described via
+%	an edge sentence concerning the vertices in $\overline{v}$.
+%	In consequence, using \cref{thm:BigTrees}, last expression
+%	is asymptotically equivalent to
+%	\[
+%	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
+%	{\aut(H,\tau)}\cdot
+%	\prod_{v\in V(H)}
+%	\Pr \big[ r, \tau(v) \big].
+%	\]
+
 	We are going to prove that the variables $X_{n,O}$ converge
@@
 	independent Poisson variables whose respective means are
-	the $\omega_O$. For that we are going to use again the factorial 
+	the $\gamma_O$. For that we are going to use again the factorial 
 	moments method. For each $O\in C(k,r)$ fix a number $b_{O}\in\N$.
@@
 	\right]= \prod_{O\in C(k,r)} 
-	\frac{(\omega_O)^{b_O}}{b_O!}.
+	\frac{(\gamma_O)^{b_O}}{b_O!}.
 	\]
@@
 	\frac{(n)_{\sum_{O\in C(k,r)} |V(O)|\cdot b_O}}
-	{\prod_{O\in C(k,r)} b_O!\cdot |Aut(O)|^{b_O}}.
+	{\prod_{O\in C(k,r)} b_O!\cdot \aut(O)^{b_O}}.
 	\]
@@
 	\frac{(n)_{\sum_{O\in C(k,r)} |V(O)|\cdot b_O}}
-	{\prod_{O\in C(k,r)} b_O!\cdot |Aut(O)|^{b_O}} \cdot
+	{\prod_{O\in C(k,r)} b_O!\cdot \aut(O)^{b_O}} \cdot
 	\Pr\left(
@@
 \frac{(n)_{\sum_{O\in C(k,r)} |V(O)|\cdot b_O}}
-{\prod_{O\in C(k,r)} b_O!\cdot |Aut(O)|^{b_O}} \cdot
+{\prod_{O\in C(k,r)} b_O!\cdot \aut(O)^{b_O}} \cdot
 \prod_{O\in C(k,r)}
@@
 &\prod_{O\in C(k,r)} \frac{1}{b_O!}\left(\frac{\lambda_O  
-\cdot \prod_{R\in \sigma} \beta_R^{|E_R(O)|} }{|Aut(O)|}
+\cdot \prod_{R\in \sigma} \beta_R^{|E_R(O)|} }{\aut(O)}
 \right)^{b_O}= \prod_{O\in C(k,r)} 
-\frac{(\omega_O)^{b_O}}{b_O!},
+\frac{(\gamma_O)^{b_O}}{b_O!},
 \end{align*}
@@
 like independent
-Poisson variables with the $\omega_O$'s as their respective means.\par
-Given a simple $k$-agreeability class for hypergraphs $\mathcal{O}$ there 
-is a partition $C_1, C_2\subset C(k,r)$, $C_1\cup C_2=C(k,r)$ 
-and there are natural numbers $a_O\leq k-1$ for any $O\in C_2$ such that
+Poisson variables with the $\gamma_O$'s as their respective means.\par
+Fix a $(k,r)$-agreeability class of $r$-simple hypergraphs
+$\mathcal{O}$. 
+Because \cref{obs:agreeablecores} it holds that
+there is a partition $C_1, C_2\subset C(k,r)$, $C_1\cup C_2=C(k,r)$ 
+and natural numbers $a_O\leq k-1$ for any $O\in C_2$ such that
 $C_1, C_2, (a_O)_{O\in C_2}$ depend only on $\mathcal{O}$ and
-the event $G_n\in \mathcal{O}$ is equivalent to
-\[
-G_n \text{ is $r$-sparse } \wedge
-\left(
- \bigwedge_{O\in C_1}
- X_{n,O}\geq k
-\right)
-\wedge
-\left(
-\bigwedge_{O\in C_1}
-X_{n,O}=a_O.
-\right).
-\]
-In consequence
 \begin{align*}
@@
 \bigwedge_{O\in C_1}
-X_{n,O}=a_O.
+X_{n,O}=a_O
 \right)
@@
 \prod_{O\in C_1}
-1-\sum_{i=0}^{k-1} e^{-\omega_O}\frac{(\omega_O)^i}{i!}
+\mathrm{Poiss}_{\geq k}(\gamma_O)
 \right)
@@
 \prod_{O\in C_2}
-e^{-\omega_O}\frac{(\omega_O)^{a_O}}{a_O!}
+\mathrm{Poiss}_{a_O}(\gamma_O)
 \right)
@@
 \end{align*}
-This last expression belongs to $\Omega$, so the theorem is proven. 
+This last expression belongs to $\Upsilon$, so the theorem is proven. 
 \end{proof}
 
-\section{Proof of the main theorem}
+\section{Proof of the main theorem} \label{sect:main}
 
@@
  	\text{ and } G_n \text{ 
-	is $(k,r)$-rich} 	\right)	
-	\]
-	Let $S^\prime\subset S$ be the set of classes 
-	$\mathcal{O}$ for which last limit equals $1$. Then
+	is $(k,r)$-rich} 	\right).
+	\]
+	Because \cref{thm:Duplicatorwins} we have that given any two hypergraphs
+	$H_1$ and $H_2$ such that $H_1$ and $H_2$ are $(k,r)$-agreeable and they
+	are both $(k,r)$-rich then they both satisfy the same first order sentences
+	with quantifier rank at most $k$. Then the LHS of last equation always equals
+	either zero or one. Let $\Sigma^\prime\subset \Sigma$ be the set of classes 
+	$\mathcal{O}$ for which last limit equals one. Then
 	\[
 	\Ln \Pr \left(
-	G_n(\overline{\beta}) \models \phi
+	G_n \models \phi
 	\right)=
-	\sum_{\mathcal{O}\in S^\prime}
+	\sum_{\mathcal{O}\in \Sigma^\prime}
 	\Ln \Pr\left(
-	G_n(\overline{\beta})\in \mathcal{O}
+	G_n \in \mathcal{O}
 	\right).		
@@
 
-%During this section we will consider
-%inside of $G_n$ a set of distinguished vertices
-%$\overline{v}\in \N*$ cho
-
-%
-%expressions analytic in $\overline{\beta}$
-%
-%\begin{lemma}
-%	Let $v_1,\dots,v_l \in [n]$	
-%	
-%\end{lemma}
-
-%Let $\overline{v[s]}$, resp. $\overline{u[s]}$,
-%be the list obtained by joining the marked lists
-%in $\mathcal{X}[s]$, resp. $\mathcal{Y}[s]$, according
-%to the order of their marks. We show that during
-%this strategy, at the end of the $s$-th round
-% $\overline{v[s]}$ and $\overline{u[s]}$ have $(k-s)$-similar
-% $r_{k-s}$-neighborhoods. For $s=0$ this is trivially
-%the case, as at the beginning of the game no lists have
-%been marked and both $\overline{v[s]},\overline{u[s]}$ are empty.
-%Suppose
-
-%variables
-%
-%and , 
-%an instance of $x$ in $\phi$ is called bounded if it occurs within the 
-% scope of a quantifier bounding it (i.e. it occurs in a sub-formula of
-% $\phi$ of the form $\forall x(\psi)$ or $\exists x (\psi)$). 
-%free if $\phi$ contains an instance of $x$ that is 
-%It is specially relevant the case where $\sigma$ contains a unique
-%relation $R$ symbol with arity two. In this case two important classes
-%of relational structures are the class of posets- i.e. those structures
-%where the relation is anti-symmetric, transitive and anti-reflexive- and 
-%graphs- i.e. those where the relation is symmetric and
-%anti-reflexive. Elements of a graph's universe are called vertices
-%and pairs of related vertices are called edges. \par
-%
-%The relatively simpler structure of the binary relation in the 
-%family of graphs allows to easily enumerate (labeled) graph with
-%a given number of vertices and count how many among them have some
-%fixed number of edges. In effect, in a graph each pair of (different)
-%vertices can either form an edge or not with total independence. Thus,
-%there can be $2^{\binom{n}{2}}$ graphs with $n$ vertices and 
-% $\binom{\binom{n}{2}}{m}$ of those have exactly $m$ edges. \par
-%
-%These kind of considerations make probability spaces over graphs
-%easier to define and to deal with compared with other relational
-%structures such as posets. Among the first of such constructions 
-%to be studied are the random models of graphs $\mathrm{G}(n,m)$ 
-%and $\mathrm{G}(n,p)$ introduced by Erd\H{o}s and R\'enyi and 
-%by Gilbert respectively. \par
-%
-%Given a natural number $n$, we denote by $[n]$ the set $\{1,\dots,n\}$.
-%The model $\mathrm{G}(n,m)$, with $n$ and $m$ natural numbers,
-% is the discrete probability space
-%over the set of all graphs with $m$ edges and $[n]$ as their vertex
-%set in where the uniform probability distribution is chosen. 
-%The model $\mathrm{G}(n,p)$, with $n$ a natural number and 
-% $0\leq p \leq 1$ in the real numbers, is the discrete probability space over
-%the set of all graphs whose vertex set is $[n]$ in where each graph 
-%with $m$ edges has probability $p^m(1-p)^{\binom{n}{2}-m}$.\par
-%
-%Although early on random models of graphs were used as tools to solve 
-%other problems such as constructing graphs with large girth and large
-%chromatic number or providing lower bounds for Ramsey numbers, later 
-%they began to be studied as objects interesting in their own right.
-%A problem in this field is to determine whether the asymptotic probability
-%of a property exists or not in a given model of random graphs. For example,
-%in the model $\mathrm{G}(n,p)$, if we take $p=p(n)$ a fixed function on $n$, 
-%we want to know for which graph properties $P$ the limit of 
-%\( \mathrm{Pr}\big( \mathrm{G}(n,p(n)) \text{ satisfies } P \big) \) exists as
-% $n$ tends to infinity. \par
-%
-%A way to study this problem that has proven to be fruitful is to classify
-%graph properties according to the logical languages they can be defined 
-%in. We say that a sequence of random graphs $(G_n)_n$ obeys a
-%\textit{convergence law}
-%with respect to some logical language $\mathcal{L}$ if for any sentence
-% $\phi$ in $\mathcal{L}$ the probability that $G_n$ satisfies $\phi$ tends
-%to some limit as $n$ tends to infinity. We say that $(G_n)_n$ obeys a 
-%\textit{zero-one law} with respect to $\mathcal{L}$ if that limit is always
-%either zero or one.  \par
-%
-%The usual example of logical language is the \textit{first order (FO) language 
-%of graphs}. Here formulas are composed of variables $x,y,z, \dots$ ranging over
-%vertices, the adjacency relation symbol $R$, Boolean connectives 
-% $\wedge, \vee, \neg, \implies, \dots$, the universal $\forall$ and 
-%existential $\exists$ quantifiers and the parentheses $)$, $($. 
-%Other examples
-%of logical languages for graphs include higher order logics such as the 
-%\textit{second order (SO) language of graphs} or fragments of those such as
-%the \textit{monadic second order (MSO) language of graphs} or 
-%the \textit{existential second order (ESO) language of graphs}. \par
-%
-%Convergence laws for FO logic in the binomial model $\mathrm{G}(n,p)$
-%have been extensively studied. A classical result in this area is due to 
-%Fagin (REF) and states that $\mathrm{G}(n,p)$ obeys a zero-one law with
-%respect to FO logic when $0\leq p \leq 1$ is a fixed constant. By then
-%it was speculated that for all ``sufficiently nice" functions $p(n)$
-%tending to zero as $n$ tends to infinity the model $\mathrm{G}(n,p(n))$
-%would obey at least a convergence law with respect to FO logic. However,
-%this intuition was proven wrong in a remarkable article by Shelah and 
-%Spencer REF. Among other results, there was proven that for 
-% $\alpha\in (0,1)$ the model $\mathrm{G}(n,n^{-\alpha})$ satisfies a 
-%zero-one law with respect to FO logic if and only if $\alpha$ is irrational.
-%Furthermore, if $\alpha\in (0,1)$ is rational then 
-% $\mathrm{G}(n,n^{-\alpha})$ does not even obey a convergence law for FO
-%logic. \par
-%This strange behavior of the rational powers of $n$ is suddenly
-%interrupted at $n^{-1}$. In REF Lynch proved the following result 
-%
-%This is in fact a weaker version of theorem 2.1 in the mentioned
-%article. In there is given a characterization of the family functions
-%of the form $F_\phi$. The analyticity of the $F_\phi$'s is 
-%a consequence of this characterization. \par
-%In $\mathrm{G}(n,p)$ the regime where $p(n)=\beta n^{-1}$ is called
-%sparse. In there the number of edges in a random graph is approximately
-% $\frac{beta}{2}n$. Many interesting phenomena occur in this regime, being
-%the most notable one the sudden appearance of a unique giant connected 
-%component when $\beta$ is greater than one REF.  
-%The goal of this article is to generalize this result from Lynch to
-%other families of relational structures different form the family of 
-%graphs that still share the desirable properties that allow for a 
-%natural definition of binomial random model. \par
-%
-%A particular case of those are the families of $k$-uniform
-%(labeled) hyper-graphs for $k$ a natural number. These are formed
-%by a set of vertices and a set of edges where each edge is a set of 
-%exactly $k$ vertices. A random hyper-graph in the binomial model of 
-%random $k$-uniform hyper-graphs $\mathrm{G}_k(n,p)$ has vertex set $[n]$ 
-%and contains each possible edge with probability $p$ independently, 
-%analogously to the model $\mathrm{G}(n,p)$. In particular
-% $\mathrm{G}_2(n,p)$ is the same model as $\mathrm{G}(n,p)$. \par
-%A number of results about the binomial random model for graphs have 
-%been generalized to $\mathrm{G}_k(n,p)$. Some analogous for convergence
-%and zero-one laws for the FO language of $k$-uniform hyper-graphs have
-%been obtained REFS. The sparse regime in this model occurs when 
-% $p$ is of the form $p(n)=\beta n^{-k+1}$. This way the expected total 
-%number of edges in a random hyper-graph grows linearly with $n$, and the
-%model shares many similarities with $\mathrm{G}(n,cn^{-1})$. 
-%In REF, among other results, it is proven that
-% $\mathrm{G}_k(n,p)$ obeys a convergence law for FO logic when
-% $p=\beta n^{k-1}$.
-%
-
-%One can also consider graphs where 'loops' are allowed or directed graphs. 
-%Unlike the class of posets, these other classes of graph-like structures share 
-%the property that one can easily enumerate their elements up to a given universe 
-%size.
-
-%The first order language with signature $\sigma$ deals with strings
-%of symbols taken from the alphabet consisting of
-% variable symbols $x_1,\dots,x_m,\dots$, the symbols in $\sigma$,
-%the logical connectives $\neg, \wedge, \vee$,
-%the universal $\forall$ and existential $\exists$ quantifiers,
-%the equality symbol, and the parentheses $),($.
-%A first order formula is a string obtained after applying the
-%following set of rules a finite number of times: 
-%\begin{enumerate}[label=(\Roman*),itemsep=0pt, topsep=0pt]
-%	\item If $x_1,x_2$ are variables then $x_1=x_2$ is a formula.
-%	\item If $R_i$ is a relation symbol in $\sigma$ with arity $a_i$,
-%	and $t_1,\dots, t_{a_i}$ are terms then 
-%	$R_i(t_1,\dots,t_{a_i})$ is a formula.
-%	\item If $\varphi$ and $\psi$ are formulas, then both
-%	$(\varphi \wedge \psi)$ and $(\varphi \vee \psi)$ are formulas.
-%	\item If $\varphi$ is a formula then $\neq \varphi$ is also 
-%	a formula.
-%	\item If $\varphi$ is a formula and $x$ is a variable then both
-%	$\forall x \varphi$ and $\exists x\varphi$ are formulas. 
-%\end{enumerate} 
-%
-%Let $\varphi$ be a first order formula. An occurrence of a variable 
-%in $\varphi$ is called bounded if it is within the scope of
-%a quantifier binding it, and is called free otherwise. We
-%will assume that the occurrences of any given variable in a first
-%order sentence are either all free or all bounded. 
-%We will use the notation $\varphi(x_1,\dots, x_n)$ to indicate
-%that $x_1, \dots, x_n$ are distinct and they are the free variables
-%(i.e. the variables whose occurrences are all free) 
-%in $\varphi$. A formula with no free variables is called a sentence,
-%and a formula whose variables are all free is called open.
-%
-%Let $\mathfrak{A}$ be a $\sigma$-structure and $\varphi(x_1,\dots,x_n)$ 
-%be a first order sentence. Given a map $\alpha$ from the set
-%of free variables $\{x_1,\dots,x_n\}$ to the universe $A$ 
-%of $\mathfrak{A}$ we define the relation 
-% $\mathfrak{A} \models \varphi[\alpha]$, "$\alpha$ satisfies $\phi$ in $\mathfrak{A}$",
-%in the following way:
-%\begin{enumerate}[label=(\Roman*),itemsep=0pt, topsep=0pt]
-%	\item 
-%	\item If $R_i$ is a relation symbol in $\sigma$ with arity $a_i$,
-%	and $t_1,\dots, t_{a_i}$ are terms then 
-%	$R_i(t_1,\dots,t_{a_i})$ is a formula.
-%	\item If $\varphi$ and $\psi$ are formulas, then both
-%	$(\varphi \wedge \psi)$ and $(\varphi \vee \psi)$ are formulas.
-%	\item If $\varphi$ is a formula then $\neq \varphi$ is also 
-%	a formula.
-%	\item If $\varphi$ is a formula and $x$ is a variable then both
-%	$\forall x \varphi$ and $\exists x\varphi$ are formulas. 
-%\end{enumerate} 
-%
-%
-
-%
-%\section{Random relational structures}
-%
-%Given a natural number $n$, we will use the notation
-% $[n]:= \{1,\dots, n\}$. We will denote by $S_n$
-%the symmetric group on $[n]$, and by $\Delta_n$ the 
-%diagonal set $\{(a,a)\in [n]^2 \}$. \par
-%Given a set $X$, then $S_n$ acts on $X^n$ in an evident way. That is, 
-%given $g\in S_n$ and $(x_1, \dots, x_n)$ one can define
-%\[ g \cdot (x_1,\dots,x_n) =(y_1,\dots,y_n), \]
-%where $y_{g(i)}=x_i$ for all $1\leq i\leq n$.\par
-%Given $\Phi$ a subgroup of $S_n$ we will denote by $X^n/\Phi$
-%the orbit set associated to the action of $\Phi$ over $X^n$.\par
-%We will use the notation $[x_1,\dots,x_n]$ to refer to the 
-%equivalence class of the $n$-tuple $(x_1,\dots, x_n)$ in 
-%any sort of quotient $X^n/\Phi$. That is, while the notation
-% $(x_1,\dots, x_n)$ will be reserved to ordered $n$-tuples, 
-% $[x_1,\dots,x_n]$ will denote an ordered $n$-tuple modulo the
-%action of some arbitrary group of permutations. Which group is this 
-%will depend solely on the ambient set where $[x_1,\dots,x_n]$ is
-%considered.
-%\par
-%
-%
-%\begin{definition}
-%	Let $n,a \in \N$, let $\Phi$ be a subgroup of $S_a$, and let
-%	$A$ be a subset 
-%	\[ A\subseteq [a]^2 \setminus \delta.\]
-%	The total edge set $\mathcal{H}_{(a,\Phi, A)}(n)$ of size $a$, 
-%	symmetry group $\Phi$ and
-%	restrictions $R$ on $n$ elements is the set:
-%	\[  \mathcal{H}_{(a,\Phi, R)}(n)= ([n]^a/\Phi) \, \,
-%	\setminus \{\,  [x_1, \dots,x_a] \in [n]^a/\Phi  \, \, 
-%	| \, \, x_i=x_j \, \text{for some } (i,j)\in R \} \]
-%\end{definition}
-%
-%\begin{definition}
-%	An (hyper)-graph $([n], H_1,\dots, H_c)$ with edge colors 
-%	$1,\dots, c$, sizes $a_1,\dots,a_c$, 
-%	symmetry groups $\Phi_1,\dots,\Phi_c$ and 
-%	restrictions $A_1,\dots,A_c$ consists of 
-%	\begin{itemize}
-%		\item The set $[n]$ for some natural number $n$.
-%		\item For $i=1,\dots,c$, a colored edge set $H_i\subseteq \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ whose elements 
-%		have color $i$.
-%	\end{itemize}
-%\end{definition}
-%
-%\begin{definition} 
-%	Let $p=(p_1,\dots, p_c)$, where all $p_i$'s are real numbers
-%	between $0$ and $1$. 
-%	The random model $HG(n,p)$ with edge colors $1,\dots,c$,
-%	sizes $a_1,\dots,a_c$, 
-%	symmetry groups $\Phi_1,dots,\Phi_c$ 
-%	and restrictions $A_1,\dots,A_c$, is the one that
-%	assigns to each graph $G=([n], H_1,\dots, H_c)$
-%	probability
-%	\[ \mathrm{Pr}(G)=\prod_{i=1}^{c} p_i^{|H_i|}(1-p_i)^{|\mathcal{H}_{(a_i,\Phi_i,A_i)}(n)|-|H_i|}.	
-%	\]
-%	Equivalently, this is the probability space obtained by 
-%	assigning to each colored edge 
-%	$e\in \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ probability $p_i$ independently. 
-%\end{definition}
-%
-%For the rest of the work we will consider 
-%\begin{itemize}
-%	\item the total number of colors $c$,	
-%	\item the sizes $a_1,\dots,a_c$,
-%	\item the symmetry group $\Phi_1,\dots, \Phi_c$ and,
-%	\item the restrictions $A_1,\dots,A_l$
-%\end{itemize}
-%fixed. When we say ``graph'' from now on what
-%we will mean is ``hiper-graph with edge colors 
-% $1,\dots, c$, sizes $a_1,\dots,a_c$, 
-%symmetry groups $\Phi_1,\dots,\Phi_c$ and 
-%restrictions $R_1,\dots,R_c$''. \par
-%
-%Given a graph $G=([n], H_1,\dots, H_c)$ we will denote by
-% $H_i(G)$ the edge set $H_i$, and by $V[G]$ the vertex set
-% $[n]$. Also, we will write $H(G)$ to denote the 
-%disjoint union of colored sets $\cup_{i=1}^c H_i$.
-%This way, an edge $e\in H(G)$ with color $i$ is an element
-% $[x_1,\dots,x_{a_i}]\in H_i(G)$, and the $x_i$'s are vertices
-%belonging to $V(G)$. \par
-%Given a set of vertices, $X\subseteq V(G)$, we will denote
-%the by $G[X]$ the induced sub-graph on $X$. \par
-%As usual, we will sometimes treat edges as sets of vertices
-%rather than ``tuples modulo the action of some permutation group''. 
-%This way, expressions like $e_1\cup e_2$ for $e_1, e_2\in H(G)$
-%will make sense and mean 
-%``the set of vertices that occupy some place in $e_1$ 
-%and in $e_2$".\par
-%Some other times we will treat edges $e\in H(G)$
-%as sub-graphs of $G$ in the evident way. That is, the subgraph
-%denoted by $e$ is the one whose vertex set is $e$-i.e., the vertices in $e$-
-%and whose only edge is $e$. 
-%This way, when we have some edges $e_1,\dots, e_l\in H(G)$ 
-%it will make sense to talk
-%about the subgraph $\cup_{i=1}^l e_i$, which is the graph
-%whose vertex set is the set of vertices belonging to the $e_i$'s, 
-%and whose edges are exactly the $e_i$'s. In spite of these
-%abuses of notation the ``type'' of any ``term'' involving edges 
-%should be derivable from the context. \par
-%Another usual abuse of notation we will make is to sometimes
-%treat graphs as their underlying vertex sets. Hence,
-%expressions defined for sets of vertices will also be defined 
-%for graphs. 
-%
+We will define a binomial model of random CNF formulas, 
+in analogy with the one in \cite{chvatal1992mick},
+but clearly the generality
+in \cref{thm:main} allows for many modifications. \par
+
+\begin{definition}
+Given a variable $x$ both expressions
+$x$ and $\neg x$ are called \textbf{literals}. A \textbf{clause}
+is a set of literals. A clause $C$ is called \textbf{ordinary}
+if no variable $x$ satisfies that both $x$ and $\neg x$
+belong to $C$. An \textbf{assignment} over a set of variables $X$ is a 
+map $f$ that assigns $0$ or $1$ to each variable of $X$. A clause $C$
+is \textbf{satisfied} by an assignment $f$ if either there is some variable $x$
+such that $x\in C$ and $f(x)=1$ or there is some variable $x$ such that
+$\neg x\in C$ and $f(x)=0$. 
+Given a natural number $l\in\N$
+a $l$-\textbf{CNF formula} is a set of  ordinary clauses 
+that contain exactly $l$ literals. 
+We say that a formula $F$
+over the variables $x_1,\dots, x_n$ is \textbf{satisfiable} if there is an
+assignment $f:\{x_1,\dots, x_n\}\rightarrow \{0,1\}$ that satisfies all clauses
+for any clause $C\in F$. 
+\end{definition}
+
+Given $n, l \in \N$ and a real number $0\leq p \leq 1$ we define
+the random model $F(l,n,p)$ as the discrete probability space that
+assigns to each $l$-CNF formula $F$ formed of clauses over
+the variables $\{x_i\}_{i\in [n]}$
+ the probability
+\[
+\PR{F}= p^{|F|}\cdot (1-p)^{2^l\binom{n}{l}-|F|}.
+\] 
+Equivalently, a random formula in $F(l,n,p)$ is obtained
+by choosing each one of the $2^l\binom{n}{l}$ normal 
+clauses of size $l$ over the variables $\{x_i\}_{i\in [n]}$
+with probability $p$ independently. \par	
+We can model $l$-CNF formulas, as we have defined them, as relational 
+structures with a language $\sigma$ consisting of $l+1$ relation symbols
+$R_0,\dots, R_l$ with arity $l$. We do that in such a way that the expression
+$R_j(x_{i_1},\dots,x_{i_l})$ means that our formula contains the clause
+consisting of $\neg x_{i_1}, \dots, \neg x_{i_j}$ and $x_{i_{j+1}},\dots
+x_{i_l}$. In consequence we need $R_1,\dots, R_l$ to satisfy the 
+following additional axioms:
+\begin{itemize}
+	\item For each $0\leq j \leq l$ and 
+	for any variables $y_1,\dots,y_j$, $y_{j+1},\dots, y_l$ it holds that
+	 $R_j(y_1,\dots y_j, y_{j+1},\dots, y_l)$ if and only if it still holds after 
+	 applying any permutations on the variables $y_1,\dots,y_j$ and the variables
+	 $y_{j+1},\dots,y_l$.
+	 \item For each $0\leq j \leq l$ and 
+	 for any variables $y_1,\dots, y_l$ it holds that
+	 $R_j(y_1,\dots, y_l)$ only if all the $y_i$'s are different. 
+\end{itemize}
+Call $\mathcal{C}$ to the family of $\sigma$-structures satisfying these last two axioms.
+Then, there is a clear correspondence between $l$-CNF formulas over the variables
+$\{x_i\}_{i\in [n]}$ and the structures in $\mathcal{C}$ whose universe is 
+$\{x_i\}_{i\in [n]}$. \par
+The language $\sigma$ and the family $\mathcal{C}$ satisfy the conditions in 
+\cref{sect:structures}. The random model $F_l(n,p)$ coincides with the model
+$G(n,\{p_R\}_{R\in \sigma})$ of random $\mathcal{C}$-hypergraphs described in 
+\cref{sect:random} when all the $p_R$'s are equal. In consequence the following theorem 
+holds
+\begin{theorem} \label{thm:mainsat}
+	Let $l>1$ be a natural number.
+	For each $n\in \N$ let $F_n(\beta)$ be a random formula from
+	$F(l,n,\beta/n^{l-1})$. Then for each sentence $\Phi\in FO[\sigma]$ 
+	it is satisfied
+	that the map $f_\Phi: [0,\infty) \rightarrow \R$ given by
+	\[
+	\beta \mapsto \PR{ F_n(\beta)\models \Phi}
+	\]
+	is well defined and analytic. 
+\end{theorem}
+%As in last theorem, let $F_n(\beta)$ denote a random formula from
+%$F(l,n,\beta/n^{l-1})$.
+A different model of random CNF formulas is studied in \cite{chvatal1992mick}. There 
+formulas are viewed as families of non necessary different clauses rather than sets.
+They define a random formula with $m$ clauses of size $l$ over $n$ variables as
+a sequence of independent 
+random clauses $C_1,\dots, C_m$ where each $C_i$ is chosen uniformly at random among
+the $2^l \binom{n}{l}$ ordinary clauses of size $l$ over $n$ variables. The 
+following holds
+\begin{theorem} 
+Let $l\geq 2$ be a natural number, and let $c\in [0,\infty)$ 
+be an arbitrary real number. 
+Let $m:\N\rightarrow \N$ be a map such that
+$m(n)=(c+o(1))n$. For each $n$ let $C_{n,1},\dots, C_{n,m(n)}$
+be clauses chosen uniformly at random independently among the 
+$2^l \binom{n}{l}$ ordinary clauses of size $l$ over the
+variables $x_1,\dots, x_n$. For each $n$, let $UNSAT_n$
+denote the event that there is no assignment of the variables
+$x_1,\dots,x_n$ that satisfies all clauses $C_{n,1},\dots, C_{n,m(n)}$. 
+Then there are two real constants $0<c_1<c_2$, independent from such that 
+\[
+\Ln \Pr\big( UNSAT_n \big)=0
+\]
+if $c< c_1$, and 
+\[
+\Ln \Pr\big( UNSAT_n \big)=1
+\]
+if $c> c_2$. 
+\end{theorem}
+The existence of $c_1$ is proven in theorem 1 of \cite{chvatal1992mick}. 
+The existence of the other constant $c_2$ follows from a simple application of
+the first order method that also appears in \cite{chvatal1992mick}, as well as 
+\cite{franco1983probabilistic}, \cite{chvatal1988many}, \cite{simon1986etude}
+and possibly others. We want to show that this ``phase transition" also happens in
+our model $F(l,n,p)$ when $p\sim \beta/n^{l-1}$. We start by showing the following
+\begin{corollary}
+	Let $l\geq 2$ be a natural number. Let $c\in [0,\infty)$ be an arbitrary
+	real number and let $m:\N\rightarrow \N$ satisfy $m(n)=(c+o(1))n$. 
+	For each $n\in \N$ let $F_{n,m(n)}$ be a random formula chosen uniformly at
+	random among all the sets of $m(n)$ ordinary clauses of size $l$ over
+	the variables $x_1,\dots, x_n$. Then there
+	are two real positive constants $0<c_1<c_2$ such that
+	\[
+	\Ln \Pr \big( F_{n,m(n)} \text{ is unsatisfiable } \big)=0
+	\]
+	if $c< c_1$, and
+	\[
+	\Ln \Pr \big( F_{n,m(n)} \text{ is unsatisfiable } \big)=1
+	\]
+	if $c> c_2$.
+\end{corollary}
+\begin{proof}
+One can consider $F_{n,m(n)}$ to be the result of `selecting clauses $C_{n,1},\dots, C_{n,m(n)}$
+uniformly at random independently among all possible clauses' as in the previous theorem, but only in the case that `no two clauses $C_{n,i}, C_{n,j}$ are equal'. In consequence 
+\[
+\Pr \big( F_{n,m(n)} \text{ is unsatisfiable } \big) 
+=
+\Pr \big(UNSAT_n \, \big| \, \text{ all the $C_{n,i}$'s are different }\,\big),
+\] 
+where the event $UNSAT_n$ is defined as in the previous theorem. An application of the first
+order method yields that for $l>3$ a.a.s the number of unordered pairs $\{i,j\}$ such that
+$C_{n,i}=C_{n,j}$ is zero. For the case of $l=2$ an application of the factorial moments
+method proves that the number of such pairs $\{i,j\}$ converges in distribution to 
+a Poisson variable of positive mean. In either case we have
+\[
+\Ln \Pr \big(\, \text{ all the $C_{n,i}$'s are different }\,\big)>0.
+\]
+In consequence the constants $c_1$ and $c_2$ from the previous theorem satisfy
+the statement of this corollary. 
+\end{proof}
+\sep
+
+Let $F_{n,m(n)}$ be as in last theorem. Notice that because the symmetry in 
+the random model $F(l,n,p(n))$ one can consider $F_{n,m(n)}$ to be a random
+sample of the space $F(l,n,p(n))$ conditioned to the event that the number of clauses
+is $m(n)$. Using this observation we can prove the following result:
+
+\begin{theorem} \label{thm:phasetransition}
+	Let $l\geq 2$ be a natural number.
+	For each $n\in \N$ let $F_n(\beta)$ be a random formula from
+	$F(l,n,\beta/n^{l-1})$. Then there are real positive values 
+	$\beta_1 < \beta_2$ such that for any $0<\beta<\beta$
+	it holds
+	\[
+	\Ln \PR{F_n(\beta) \text{ is unsatisfiable }  }=0,
+	\]
+	and for any $\beta>\beta_2$
+	it holds
+	\[
+	\Ln \PR{F_n(\beta) \text{ is unsatisfiable }  }=1.
+	\]
+\end{theorem}
+\begin{proof}
+	For each $n\in \N$ let $X_{n}(\beta)$ be the random variable
+	that counts the clauses in $F_n(\beta)$. It is satisfied that
+	$\mathrm{E}[X_n(\beta)]\sim \frac{\beta\cdot 2^l}{l!}n$. Let $c_1,
+	c_2$ be as in last corollary. Define $\beta_1:= \frac{c_1\cdot l!}{2^l}$
+	and $\beta_2:= \frac{c_2 \cdot l!}{2^l}$. Fix $\beta\in \R$ satisfying
+	$0<\beta<\beta_1$. Let $\epsilon>0$ be a real number such that
+	$ \frac{\beta\cdot 2^l}{l!} +\epsilon< c_1$. For each $n\in \N$
+	set $\delta_1(n):=\floor*{ \left(\frac{\beta\cdot 2^l}{l!}-\epsilon\right)n}$
+	and $\delta_2(m):=\floor*{ \left(\frac{\beta\cdot 2^l}{l!}+\epsilon\right)n}$.
+	Because of the Central Limit
+	Theorem it holds
+	\begin{equation}\label{eqn:aux6}
+	\Ln \Pr\left( \delta_1(n) \leq X_n(\beta)  
+	\leq \delta_2(n)    \right) = 1.
+	\end{equation}
+	Denote by $dp$ the probability density function of the variable $X_n(\beta)$.
+	That is $dp(m)=\Pr(X_n(\beta)=m)$. Then, because of the previous equation it holds
+	\[
+	\Pr\left( F_n(\beta) \text{ is unsatisfiable }\right)\sim
+	\int_{\delta_1(n)}^{\delta_2(n)}
+	dp(m) \cdot \Pr \left(
+	F_n(\beta) \text{ is unsatisfiable } \Big|
+	X_n(\beta)=m	
+	\right).
+	\]
+	Notice that the property of being unsatisfiable is monotonous. That is,
+	for any two natural numbers $m_1<m_2$ it holds
+	\[
+	 \Pr \left(
+	F_n(\beta) \text{ is unsatisfiable } \Big|
+	X_n(\beta)=m_2	
+	\right) <  \Pr \left(
+	F_n(\beta) \text{ is unsatisfiable } \Big|
+	X_n(\beta)=m_2	
+	\right).
+	\]
+	In consequence,
+	\begin{align*}
+	&\int_{\delta_1(n)}^{\delta_2(n)}
+	dp(m) \cdot \Pr \left(
+	F_n(\beta) \text{ is unsatisfiable } \Big|
+	X_n(\beta)=m	
+	\right)\leq \\ & 
+	\Pr \left(
+	F_n(\beta) \text{ is unsatisfiable } \Big|
+	X_n(\beta)=\delta_2(n) \right) \cdot 
+	\Pr\big( \delta_1(n) \leq X_n(\beta)  
+	\leq \delta_2(n)  \big).   
+	\end{align*}
+	And because of \cref{eqn:aux6}, 
+	\begin{align*}
+	&\Pr \left(
+	F_n(\beta) \text{ is unsatisfiable } \Big|
+	X_n(\beta)=\delta_2(n) \right) \cdot 
+	\Pr\left( \delta_1(n) \leq X_n(\beta)  
+	\leq \delta_2(n)  \right)\sim\\&
+	\Pr \left(
+	F_n(\beta) \text{ is unsatisfiable } \Big|
+	X_n(\beta)=\delta_2(n) \right).
+	\end{align*}
+	Finally, as $\delta_2(n)< c_2n$, because of the previous
+	corollary
+	\[
+	\Ln \Pr \left(
+	F_n(\beta) \text{ is unsatisfiable } \Big|
+	X_n(\beta)=\delta_2(n) \right)= 0.
+	\]  
+	Thus, joining everything, we have proven that for any 
+	$\beta < \beta_1$, it holds that
+	$F_n(\beta)$ a.a.s is satisfiable, as we wanted.
+	Showing that for any $\beta > \beta_2$, 
+	a.a.s $F_n(\beta)$ is unsatisfiable is analogous. We
+	fix $\epsilon>0$ such that $\frac{\beta\cdot 2^l}{l!}-\epsilon>c_2$.
+	We define $\delta_1(n)$ and $\delta_2(n)$ as before. Then similarly to before 
+	using the Central Limit Theorem and the fact that
+	the property of being unsatisfiable is monotonous one can prove the bound
+	\[
+	\Ln \Pr \left(
+	F_n(\beta) \text{ is unsatisfiable } \right) \geq
+	\Ln \Pr \left(
+	F_n(\beta) \text{ is unsatisfiable } \Big|
+	X_n(\beta)=\delta_1(n) \right).
+	\]
+	And using the previous corollary we obtain that last limit equals one, 
+	and the result follows.
+
+\end{proof}
+\sep
+
+A direct consequence of last theorem, due to Albert Atserias, is the following
+
+\begin{theorem} \label{thm:satapplication}
+	Let $l>1$ be a natural number.
+	For each $n\in \N$ let $F_n(\beta)$ be a random formula from
+	$F(l,n,\beta/n^{l-1})$. Let $\Phi\in FO[\sigma]$ be a first order
+	sentence that implies unsatisfiability.  Then for all $\beta\in [0,\infty)$
+	it holds
+	\[
+	\Ln \PR{F_n(\beta)\models \Phi  }=0.
+	\]
+\end{theorem}
+\begin{proof}
+	Let $\beta_1$ and $\beta_2$ be as in \cref{thm:phasetransition}. 
+	As $\Phi$ implies unsatisfiability it holds
+	$\PR{F_n(\beta)\models \Phi  }\leq  
+	\PR{F_n(\beta) \text{ is unsatisfiable }  }$. Thus, using \cref{thm:phasetransition}
+	we get that for all $\beta\in [0,\beta_1]$
+	\[
+	\Ln \PR{F_n(\beta)\models \Phi  }=0.
+	\]
+	Because \cref{thm:mainsat} last limit varies analytically with $\beta$, so
+	if it vanishes in a proper interval $[0,\beta_1]$ then it has to vanish
+	in the whole $[0,\infty)$ by the principle of analytic continuation, and the result 
+	holds. 
+\end{proof}
+
+\section*{Conclusions}
+
+\section*{Acknowledgments}
+This work was supported by the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement ERC-2014-CoG 648276 AUTAR).\par
+\todo{Albert and Marc Noy}
+%I wish to thank Albert Atserias and Marc Noy for their help. Albert Atserias 
+%presented to me the problem of generalizing the
+%convergence law found by Lynch in \cite{lynch1992probabilities} with the application
+%to RANDOM SAT given in \cref{thm:satapplication} in mind.
 

### 2020-05-09 ArticleAcortado.tex
Acrotar más

@@
 
+\theoremstyle{definition}
 \newtheorem{proposition}{Proposition}[section]
@@
 \newtheorem{corollary}{Corollary}[section]
-\theoremstyle{definition}
 \newtheorem{definition}{Definition}[section]
@@
 \newcommand{\aut}{\mathrm{aut}}
+
 \DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
@@
 \begin{abstract}
+	We extend the convergence law for sparse random graphs proven
+	by Lynch to arbitrary relational languages.
 	We consider a finite relational vocabulary $\sigma$
@@
     $\sigma$-structures that satisfy $T$ and show that first order properties have 
-    well defined asymptotic probabilities in the sparse 
-    case. It is also shown that those limit probabilities are well-behaved with
-    respect to some parameters that represent edge densities. 
+    well defined asymptotic probabilities when the expected number of tuples satisfying
+    each relation in $\sigma$ is linear.
+    It is also shown that those limit probabilities are well-behaved with
+    respect to some parameters that represent the density of tuples satisfying $R$
+    for each relation $R$ in the vocabulary $\sigma$. 
     An application of these results to the problem of random Boolean 
     satisfiability is presented afterwards. 
-    We show that there is no first order property of $k$-CNF formulas
-    that implies unsatisfiability and holds for almost all typical 
-    unsatisfiable formulas when the number of clauses is linear.
+    We show that in a random $k$-CNF formula over $n$ variables where
+    each possible clause occurs with probability $\sim c/n^{k-1}$ independently any 
+    first order property of $k$-CNF formulas that
+    implies unsatisfiability does almost surely not hold as $n$ tends to infinity.
 
@@
 REFERENCES NEEDED.
-Suppose that $P$ is a FO graph property that implies
+Suppose $P$ is a FO graph property that implies
 non-$3$-colorability. Then, because of this implication,
@@
 $(n)_m$ the $m$-th falling factorial of $n$. \par
+We will use the convention that over-lined variables
+, like $\overline{x}$, denote ordered tuples of arbitrary length.
+Given an ordered tuple $\overline{x}$
+we define the number $len(\overline{x})$ as its length. 
+Given a tuple $\overline{x}$ and an element $x$ the expression
+$x\in \overline{x}$ means that $x$ appears as some coordinate
+in $\overline{x}$. 
+Given a map $f:X\rightarrow Y$ between two sets $X, Y$ and 
+an ordered tuple $\overline{x}:=(x_1,\dots,x_a)\in X^*$ 
+we define $f(\overline{x})\in Y^*$ as the tuple 
+$(f(x_1),\dots,f(x_a))$.
+Given two tuples $\overline{x},\overline{y}$
+we write $\overline{x}^\smallfrown \overline{y}$ to denote their 
+concatenation.
+\par
+
 Given a set
@@
 We also define $S^*:=\bigcup_{n=0}^\infty S^n$ and
-$(S)_*:=\bigcup_{n\leq |S|} (S)_n$. 
-Given two tuples $\overline{x},\overline{y}\in S^*$
-we write $\overline{x}^\smallfrown \overline{y}$ to denote their 
-concatenation. Given a tuple 
-$\overline{x}\in S^*$ and an element $x\in S$ the expression
-$x\in \overline{x}$ will mean that $x$ appears as some coordinate
-in $\overline{x}$. We will at times make an abuse of notation and
-treat the tuple $\overline{x}$
-as the set of elements $x\in \overline{x}$. 
-We will use the convention that over-lined variables
-, like $\overline{x}$, denote ordered tuples of arbitrary length.
-Given an ordered tuple $\overline{x}$
-we define the number $len(\overline{x})$ as its length. 
-Given a map $f:X\rightarrow Y$ between two sets $X, Y$ and 
-an ordered tuple $\overline{x}:=(x_1,\dots,x_a)\in X^*$ 
-we define $f(\overline{x})\in Y^*$ as the tuple 
-$(f(x_1),\dots,f(x_a))$.
-\par
+$(S)_*:=\bigcup_{n\leq |S|} (S)_n$. \par
 
@@
 $g\in \Phi$, by definition $[x_1,\dots,x_a]=[x_{g(1)}
-,\dots,x_{g(a)}]$. The notations $\overline{x}$ and
+,\dots,x_{g(a)}]$. \par
+The notations $\overline{x}$ and
 $(x_1,\dots, x_a)$ 
@@
 
-We can think any structure $G$ in $\mathcal{C}$
-as a ``multi-hypergraph" whose vertices are the elements
-of the universe of $G$. Each relation $R\in \sigma$, can be 
-represented over $G$ as an ``edge set" formed by tuples vertices
-of size $ar(R)$ modulo the permutations in $\Phi_R$. Furthermore, 
-repetitions of vertices in the positions given by
-$P_R$ are not allowed in these tuples.\par
-The following definitions make this ideas formal. Notice that they 
-depend on our fixed choice of $\sigma$, $\{\phi_R\}_{R\in \sigma}$
-and $\{P_R\}_{R\in \sigma}$.
-
+Structures in $\mathcal{C}$ generalize the usual notion of hypergraph
+in the sense that they contain multiple ``adjacency'' relations with arbitrary 
+symmetry and anti-reflexivity axioms. \par
+We will use the usual graph theory nomenclature and notation with some minor changes. 
+In the scope of this article we will call \textbf{hypergraphs}
+to structures in $\mathcal{C}$.
+Given an hypergraph $G$ we will call its \textbf{vertex set}, denoted by $V(G)$,
+to its universe.\par
+In order to define the edge sets of $G$ we need the following auxiliary definition
 \begin{definition} 
 	Let $V$ be a set, and let $R\in \sigma$.
-	We define the \textbf{total edge set over $V$
+	We define the \textbf{set of possible edges over $V$
 	given by $R$} as
@@
 	X=
-	\Big\{ [x_1,\dots,x_{ar(R)}]  
+	\Big\{ [v_1,\dots,v_{ar(R)}]  
 	\quad \Big| \quad
-	x_1,\dots,x_{ar(R)}\in V, \,
+	v_1,\dots,v_{ar(R)}\in V, \,
 	\text{ and } 
-	 \, x_i=x_j \text{ for some } 
+	 \, v_i=v_j \text{ for some } 
 	\{i,j\}\in P_R \Big\}.
 	\]
-	Also, we will say that the \textbf{sort} of the elements $e\in E_R[V]$
-	is $R$. 
+	We will call \textbf{edges} to the elements of
+	$E_R[V]$ and we will say that the \textbf{sort} of any edge $e\in E_R[V]$
+	is $R$.	In the case where $V=[n]$ we will write simply $E_R[n]$ instead
+	of $E_R[[n]]$
 \end{definition}
@@
 the positions given by $P_R$.\par
-The fact that the elements $e\in E_R(V)$ are of sort $R$ 
-is a technical detail
-introduced so that for any different relation symbols $R_1$ and
-$R_2$ it holds $E_{R_1}(V)\cap E_{R_2}(V)=\emptyset$ even in the case
-that $ar(R_1)=ar(R_2)$, $\Phi_{R_1}=\Phi_{R_2}$ and $P_{R_1}=P_{R_2}$.\par
-
-In the case where $V=[n]$ we will write simply $E_R[n]$ instead
-of $E_R[[n]]$.
-
-\begin{definition} 
-We call $\mathcal{C}$-\textbf{hypergraph}, or simply hypergraph, 
-to a pair $G=\Big(V(G),\{E_R(G)\}_{R\in\sigma}\Big)$,
-where for each $R$, $E_R(G) \subseteq E_R[V]$.
-\end{definition}
-
-Hypergraphs, as we have defined them, 
-can be naturally interpreted as
-structures from $\mathcal{C}$ 
-in the following way: 
-given an hypergraph $G:=(V,\{E_R\}_{R\in \sigma})$,
-we can construct a $\sigma$-structure $\mathcal{G}$ whose universe is
-$V$, and for any $R\in \sigma$ we define
-$R^\mathcal{G}\subseteq V^{ar(R)}$ as the set of tuples
-$\overline{x}\in V^{ar(R)}$ such that
-$[\overline{x}]\in E_R$. Clearly $\mathcal{G}$
-satisfies by definition the 
-symmetry and anti-reflexivity
-axioms given at the beginning of this section. It is easy to
-see that this process induces
-a one-to-one identification between 
-structures in $\mathcal{C}$ and hypergraphs. \par
-
-\subsection{Hypergraph notation and nomenclature}
-
-We will use standard nomenclature and notation
-from graph theory with some additions. Given an 
-hypergraph $G$ we will call its \textbf{vertex set} to $V(G)$ 
-and \textbf{vertices} 
-to the elements $v\in V(G)$. Likewise, each of 
-the $E_R(G)$'s will be called an \textbf{edge set} and its elements, 
-\textbf{edges}. Given an edge, $e\in V(G)$ we will denote by $V(e)$
+Let $G$ be an hypergraph whose set of vertices is $V$ and let $R\in \sigma$
+be a relation. 
+We define the \textbf{edge set of $G$ given by $R$}, denoted by $E_R(G)$, 
+as the set of edges $[\overline{v}]\in E_R[V]$ such that $\overline{v}\in R^G$. 
+We define \textbf{the total edge set of $G$} as the set $E(G):=\cup_{R\in \sigma} E_R(G)$.
+Given an edge, $e\in E(G)$ we will denote by $V(e)$
 the set of all vertices that participate in $e$. 
-
 \par
-Given an hypergraph $G$ we define the set $E(G)$ as the
-union $\cup_{R\in \sigma}E_R(G)$. Notice that this union 
-is disjoint because elements from different $E_R(G)$'s 
-are of different sorts. Thus, $|E(G)|=\sum_{R\in \sigma} 
-|E_R(G)|$. Analogously, given a set $V$, we define
-$E[V]:=\cup_{R\in \sigma} E_R[V]$.
-Given an edge $e\in E[V]$ we define $R(e)$
-as the sort of $e$, i.e.,
-the unique relation symbol $R(e)\in \sigma$
-such that $e\in E_{R(e)}[V]$.
+Clearly an hypergraph $G$ is completely given by its vertex set $V(G)$ and its edge 
+set $ E(G)$. Notice that edges $e\in E(G)$ are sorted according to the relation they represent.
+\par
 
@@
 $ex(G)\geq -1$ for any connected hypergraph.
-\par Given a connected hypergraph $G$ 
-and vertices $v,u\in V(G)$, we say that $G$ is
-a \textbf{path} between $v$ and $u$
-if $G$ 
+\par
+A connected hypergraph $G$ is a path between two of its 
+vertices $v,u\in V(G)$ if $G$ 
 does not contain any connected proper sub-hypergraph containing both $v,u$.
 \par
-A connected hypergraph $G$ is a \textbf{tree} if $ex(G)=-1$. 
-\par A connected hypergraph $G$ is called \textbf{dense} if $ex(G)>0$.\par
+A connected hypergraph $G$ is a \textbf{tree} if $ex(G)=-1$ and \textbf{dense} if $ex(G)>0$.
 A connected hypergraph $G$ with $ex(G)\geq 0$ is called \textbf{saturated} 
@@
 $H\subset G$ it holds $ex(H)<ex(G)$. 
-% It is satisfied that any connected hypergraph $G$
-%with $ex(G)\geq 0$ contains a unique saturated sub-hypergraph $H$ with $ex(H)=ex(G)$.
-\par
 A connected hypergraph $G$ with $ex(G)=0$ is called \textbf{unicycle}. 
@@
 		u,v\in V(H)}} |E(H)| .\]
-That is, the distance between $v$ and $u$ is the minimum number of
+That is, the \textbf{distance} between $v$ and $u$ is the minimum number of
 edges necessary to connect $v$ and $u$. 
-If such number does not exist we define $d^G(u,v)=\infty$. \par
-As usual, define $d^{G}(X,Y)$ for sets $X,Y\subset V(G)$ as the minimum
-distance $d(u,v)$ where $u\in X$ and $v\in Y$. 
-When $X=\{x\}$ we will omit the brackets and write
-$d^G(x,Y)$ instead of $d^G(\{x\},Y)$, for example.
+If such number does not exist we define $d^G(u,v)=\infty$. 
 When $G$ 
 is understood or not relevant we will usually simply denote the 
-distance by $d$ instead of $d^G$. \par
-
-Given set of vertices vertex, $X\subseteq V(G)$, 
-we denote by $N^G(X;r)$ the $r$-\textbf{neighborhood} of $X$ in 
-$G$. That is,  $N^G(X;r)= G[Y]$, where $Y\subseteq V(G)$ is 
-the set:
-\[ Y:= \{ u \in V(G) \ | \ d(X,u)\leq r   \}. \]
-In particular, when $X$ is a singleton $\{v\}$, we
-will write $N^G(v;r)$ instead of $N^G(\{v\};r)$.
-As before, we will usually drop the ``$G$'' from our 
-notation when $G$ is understood or not relevant.  \par
-
-We will often write tuples of vertices instead of sets
-inside of $d(\cdot\, , \cdot)$ and $N(\cdot\, ;r)$. In those cases
-we are treating those tuples as sets as specified in
-\cref{subsect:notation}.
-
-\subsection{Copies of Hypergraphs}
-
-Given two hypergraphs $H_1, H_2$ an \textbf{isomorphism} 
-$f$ between them is a bijection $f: V(H_1)\rightarrow V(H_2)$
-such that for any $R\in \sigma$, a tuple $\overline{v}\in V(H_1)^*$
-forms an edge $[\overline{v}]\in E_R(H_1)$ if and only
-if $[f(\overline{v})]\in E_R(H_2)$. We say that $H_1$ and
-$H_2$ are isomorphic, written as $H_1\simeq H_2$, if there exists
-some isomorphism between them.\par
-
-Let $H$ be an hypergraph. An \textbf{automorphism} of $H$
+distance by $d$ instead of $d^G$. Equivalently, the distance $d$
+coincides with the usual one defined over the Gaifman graph of the structure 
+$G$. The \textbf{diameter} of an hypergraph is the maximum distance between any 
+two of its vertices. 
+We extend naturally the distance $d$ to sets and tuples of
+vertices, as usual. Given a vertex/set/tuple $X$ and a number
+$r\in \N$ we define the \textbf{neighborhood}
+$N^G(X;r)$, or simply $N(X;r)$ when $G$ is not relevant,
+as the set of vertices $v$ such that $d^G(X,v)\leq r$.
+\par
+
+\textbf{Isomorphisms} between hypergraphs are defined the same as 
+isomorphisms between relational structures. We denote the isomorphism relation
+between hypergraphs by $\simeq$. 
+Given and hypergraph $H$, an \textbf{automorphism} of $H$
 is an isomorphism from $H$ to itself. We will denote by
@@
 
-Let, $\mathbb{H}$ be an isomorphism class of hypergraphs. Let
-$H\in \mathbb{H}$ be a representative of the class. 
-Then we define $ex(\mathbb{H})$ as $ex(H)$. Clearly this definition
-does not depend on the choice of $H$. The expressions
-$\aut(\mathbb{H})$,
-$|V(\mathbb{H})|$, $|E(\mathbb{H})|$ or
-$|E_R(\mathbb{H})|$ for $R\in \sigma$ are defined 
-in an analogous way.\par
-
 Let $H$ be an hypergraph and let $V$ be a set. We define the
-set $Copies(H,V)$ as the set of hypergraphs $H^\prime$ such that
-$V(H^\prime)\subset V$ and $H\simeq H^\prime$. Analogously, if
-$\mathbb{H}$ is an isomorphism class of hypergraphs we define
-$Copies(\mathbb{H},V)$ as the set of hypergraphs $H^\prime$ 
-that satisfy
-$V(H^\prime)\subset V$ as well as $H^\prime \in \mathbb{H}$.   \par
+set of \textbf{copies of $H$ over $V$}, denoted as $Copies(H,V)$, 
+as the set of hypergraphs 
+$H^\prime$ such that
+$V(H^\prime)\subset V$ and $H\simeq H^\prime$.   \par
 
 In our proofs it will be useful to consider colorings over 
-hypergraphs as a way to assign extra information to their 
-vertices.
-
-\begin{definition} \label{def:color}
+hypergraphs as a way to decorate their 
+vertices with extra information. 
 Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
@@
 and $\chi: V(H)\rightarrow \Sigma$ is a map 
-	called \textbf{$\Sigma$-coloring} of $H$.
-\end{definition}
-
-	Given two $\Sigma$-hypergraphs $(H_1,\chi_1)$
-	and $(H_2,\chi_2)$, an \textbf{isomorphism} between them is
-	a bijection $f:V(H_1)\rightarrow V(H_2)$ satisfying
-	that $f$ is an hypergraph isomorphism between $H_1$ and
-	$H_2$ as well as $\chi_2(f(v))=\chi_1(v)$ for all $v\in V(H_1)$.
-	We say that $(H_1,\chi_1)$ is isomorphic to $(H_2,\chi_2)$,
-	written as $(H_1, \chi_1)\simeq (H_2,\chi_2)$, if there exists an
-	isomorphism between them.
-	\par	 
-	Let $(H,\chi)$ be a $\Sigma$-hypergraph, an 
+called \textbf{$\Sigma$-coloring} of $H$. \par
+\textbf{Isomorphisms} between $\Sigma$-hypergraphs are just isomorphisms between the underlying
+hypergraphs that also preserve their colorings. We also denote the isomorphism relation between 
+$\Sigma$-hypergraphs by $\simeq$.
+Given a $\Sigma$-hypergraph $(H,\chi)$,  an 
 \textbf{automorphism} of $(H,\chi)$ is an 
-	isomorphism from it into itself. We will denote
+isomorphism from it into itself, as before. We will denote
 by $\aut(H,\chi)$ the number of such automorphisms. 
 \par
-	As with the case of hypergraphs, if $\mathbb{H}$ is 
-	an isomorphism class of $\Sigma$-hypergraphs
-	then the expressions $\aut(\mathbb{H})$ and
-	$|V(\mathbb{H})|$ are defined via representatives. \par
+
 Let $(H,\chi)$ be a $\Sigma$-hypergraph and let $V$ be a set.
-	We define the set $Copies\big(
+As before, we define the set $Copies\big(
 (H,\chi),\, \, V\big)$ as the set of $\Sigma$-hypergraphs
@@
 that satisfy $v\in V(H^\prime)$ as well as
-	$\chi^\prime(v)=s$.
+$\chi^\prime(v)=s$. \par
+
+Given $\mathbb{H}$ an isomorphism class of hypergraphs or $\Sigma$-hypergraphs
+, we define expressions
+such as $ex(\mathbb{H})$, $\aut(\mathbb{H})$,
+$|V(\mathbb{H})|$, $|E(\mathbb{H})|$ or
+$Copies(\mathbb{H},V)$ via representatives of $\mathbb{H}$.\par
 
@@
 positive real numbers $\InR{\beta}$.
-From now on we will write $G_n\left(\InR{\beta}\right)$
-to denote a random sample of 
-$G^\mathcal{C}\left(n,\left\{ \frac{
-\beta_R}{n^{ar(R)-1}}\right\}_{R\in\sigma}\right)$.
+We will denote a random sample of 
+$G^\mathcal{C}\left(n,\left\{p_R\right\}_{R\in\sigma}\right)$
+by $G_n\left(\InR{\beta}\right)$ when the probabilities $p_R$
+satisfy $p_R(n)\sim \beta_R/n^{ar(R)-1}$ for all $R\in \sigma$.
 When the choice of $\InR{\beta}$ is not relevant
@@
 
-A more complete introduction to the subject can be found in
-\cite[Section 2]{finitemodeltheory1}, for example.\par
-
-Let $H_1$ and $H_2$ be hypergraphs. We define the $k$ round 
-Ehrenfeucht-Fraisse (EF) game on $H_1$ and $H_2$, denoted by
-$\ehr_k(H_1;H_2)$, as follows:
-The game is played between two players, Spoiler and Duplicator, and
-the number of rounds $k$ is known for both from the start.
-At the beginning of each round Spoiler chooses a vertex from either
-$V(H_1)$ or $V(H_2)$ and Duplicator responds by choosing a vertex
-from the other set.
-Let us denote by 
-$v_i$, resp. $u_i$ the vertex from $H_1$, resp. from $H_2$, 
-chosen in the $i$-th round,
-for $i\in [k]$. At the end of the $k$-th round 
-Duplicator wins if the following holds:
-\begin{itemize}
-	\item For any $i,j\in [k]$, $v_i=v_j \iff u_i=u_j$.
-	\item Given a relation symbol $R\in \sigma$ 
-	and indices $i_1,\dots, i_{ar(R)} \in [k]$, 
-	$[v_{i_1},\dots,v_{i_{ar(R)}}] \in E_R(H_1) \iff 
-	[u_{i_1},\dots,u_{i_{ar(R)}}]
-	\in E_R(H_2)$.
-
-\end{itemize}
-
+We assume familiarity with Ehrenfeucht-Fraisse (EF) games.
+An introduction to the subject can be found in
+\cite[Section 2]{finitemodeltheory1}, for example. Given
+hypergraphs $H_1$ and $H_2$ we denote the $k$-round EF game played 
+on $H_1$ and
+$H_2$ by $\ehr_k(H_1;H_2)$.
 The following is satisfied:
@@
 
-Let $\overline{v}\in V(H_1)^*$, and 
-$\overline{u}\in V(H_2)^*$ be lists of vertices of the same length, 
-$l=len(\overline{v})=len(\overline{u})$. We define the $k$ round 
+Given lists $\overline{v}\in V(H_1)^*$, and 
+$\overline{u}\in V(H_2)^*$ of the same length, 
+we denote the $k$ round 
 Ehrenfeucht-Fraisse game on $H_1$ and $H_2$ with initial position given
-by $\overline{v}$ and $\overline{u}$, denoted by $\ehr_k(H_1,\overline{v};H_2,\overline{u})$,
-the same way as $\ehr_k(H_1;H_2)$, but in this case the game has $l$ extra 
-rounds at the beginning where the vertices in $\overline{v}$ and $\overline{u}$ are 
-played successively. After this, $k$ more rounds are played normally. \par
+by $\overline{v}$ and $\overline{u}$ by $\ehr_k(H_1,\overline{v};H_2,\overline{u})$.\par
 
@@
 $H_1$ and $H_2$, denoted by $d\ehr_k(H_1;H_2)$, the same way as
-$\ehr_k(H_1;H_2)$, but now, in order for Duplicator to win the
-game, the following additional condition has to be satisfied 
-at the end of the game:
-\begin{itemize}
-	\item For any $i,j\in [k]$, $d^{H_1}(v_i,v_j)=d^{H_2}(u_i,u_j)$.
-\end{itemize}
-
+$\ehr_k(H_1;H_2)$, but now in order for Duplicator to win the
+game the following additional condition has to be satisfied 
+at the end: For any $i,j\in [k]$, $d^{H_1}(v_i,v_j)=d^{H_2}(u_i,u_j)$,
+where $v_s$ and $u_s$ denote the vertex played on $H_1$, resp. $H_2$ in the 
+$s$-th round of the game. 
 Given $\overline{v}\in V(H_1)^*$, and $\overline{u}\in V(H_2)^*$
@@
 We show now an outline of the proof of \cref{thm:main}. \par 
-In essence the arguments mirror the ones in the proof of theorem 2.1
+The arguments mirror the ones in the proof of theorem 2.1
 in \cite{lynch1992probabilities}, adapted to fit our context. Fix $r\in \N$.
@@
 We say that $H$ is $r$-simple if all connected components of
-$Core(H;r)$ are unicycles (\cref{def:Core}) \par
+$Core(H;r)$ are unicycles (\cref{sec:Core}) \par
 For any given $k,r\in \N$ we say that $H_1\approx_{k,r} H_2$ for two
@@
 
+During this section $H_1$ and $H_2$ stand for
+hypergraphs and $V_1:=V(H_1)$, $V_2:=V(H_2)$.
+
 \begin{definition} \label{def:similar}
-Let $H_1$ and $H_2$ be hypergraphs, and let
-$V_1:=V(H_1), V_2:=V(H_2)$.
 Let $\overline{v} \in V_1^*, 
 \overline{u} \in V_2^*$ be tuples of the same length.
-We say that $\overline{v}$ and $\overline{u}$ have
-$k$-\textbf{similar} $r$-neighborhoods, written as
-$(H_1,\overline{v})\simeq_{k,r}(H_2 \overline{u})$, if Duplicator wins
+We write $(H_1,\overline{v})\simeq_{k,r}(H_2 \overline{u})$, if Duplicator wins
 $d\ehr_k\big(N(\overline{v};r),
 \overline{v};\, N(\overline{u};r),\overline{u}\big)$.
-Given sets of vertices $X\subseteq V_1$ and $Y\subseteq V_2$
-we say that $X$ and $Y$ have $k$-similar
-$r$-neighborhoods, written as
-$X\simeq_{k,r} Y$, if we can order their elements to form
+Given $X\subseteq V_1$ and $Y\subseteq V_2$
+we write $(H_1,X)\simeq_{k,r} (H_2,Y)$, if we can order $X$, resp $Y$ to form
 lists $\overline{v}$, resp. $\overline{u}$ such that 
 $(H_1,\overline{v})\simeq_{k,r}(H_2,\overline{u})$. 
-Given sets of vertices $X\in V_1$, $Y\in V_2$ and 
+Given $X\in V_1$, $Y\in V_2$ and 
 tuples of the same length $\overline{v}\in V_1^*$ and
-$\overline{u}\in V_2^*$ we will say that $(X,\overline{v})$ 
-and $(Y,\overline{u})$ have $k$-similar $r$-neighborhoods,
-written as $\big(H_1, (X,\overline{v})  \big)
+$\overline{u}\in V_2^*$ we write
+ $\big(H_1, (X,\overline{v})  \big)
 \simeq_{k,r} \big(H_2, (Y,\overline{u})  \big)$, if
-the elements of $X$ and $Y$ can be ordered in lists
-$\overline{w}$, $\overline{z}$ such that
+$X$ and $Y$ can be ordered to form lists
+$\overline{w}$, resp. $\overline{z}$ such that
 $(H_1,\overline{w}^\smallfrown \overline{v})
@@
 \begin{definition} \label{def:analogous}
-Fix $r\in \N$. Suppose that $X\subseteq V_1$ and 
+Fix $r\in \N$. Suppose $X\subseteq V_1$ and 
 $Y\subseteq V_2$ can
@@
 $N(Y_i;r)$'s, are connected and disjoint. 
-We say that $X$ and
-$Y$ have $k$-\textbf{analogous} $r$-neighborhoods,
-written as $(H_1,X)\cong_{k,r} (H_2,Y)$, 
+We write $(H_1,X)\cong_{k,r} (H_2,Y)$, 
 if for any set $Z\subset V_\delta$, with $\delta\in \{1,2\}$,
@@
 The main theorem of this section, which
-is a slight strengthening of Theorem 
-2.6.7 from \cite{spencer2013strange}, is the following:
+is a slight strengthening of \cite[Theorem 
+2.6.7]{spencer2013strange}, is the following:
 
@@
 	Set $r=(3^k-1)/2$.
-	Let $H_1,H_2$ be hypergraphs and let $V_1:=V(H_1)$, $V_2:=
-	V(H_2)$.
 	Suppose there exist
@@
 \begin{obs} \label{obs1}
-	Let $H_1$, $H_2$ be hypergraphs and 
-	$\overline{v}\in V(H_1)^*$, $\overline{u}\in V(H_2)^*$,
-	be lists of vertices. Suppose that
+	Let
+	$\overline{v}\in V(H_1)^*$, $\overline{u}\in V(H_2)^*$ be of equal length. Suppose
 	Duplicator wins $d\ehr_k(H_1,\overline{v}; \, H_2,\overline{u})$.
 	Then, for any $r\in \N$, $(H_1, \overline{v})\simeq_{k,r} 
-	(H_2,\overline{u})$. A direct consequence of this fact 
-	is that 
-	given hypergraphs $H_1, H_2$ and sets
-	$X\subseteq V(H_1)$, $Y\subseteq V(H_2)$ such that
-	$(H_1,X)\simeq_{k,r} (H_2,Y)$ for some $r\in \N$, 
-	then for any $r^\prime \leq r$ it also holds 
-	$(H_1,X)\simeq_{k,r^\prime} (H_2,Y)$
+	(H_2,\overline{u})$. 
 \end{obs}
@@
 \begin{obs} \label{obs2}
-	Let $H_1$, $H_2$ be hypergraphs and let
-	$\overline{v}\in V(H_1)^*$, $\overline{u}\in V(H_2)^*$ be lists of 
-	vertices. Suppose 
+	Let
+	$\overline{v}\in V(H_1)^*$, $\overline{u}\in V(H_2)^*$ be of equal length. Suppose 
 	Duplicator wins $d\ehr_k(H_1,\overline{v};\,H_2,\overline{u})$. 
@@
 \begin{lemma} \label{lemm:Duplicator}
-	Let $H_1$, $H_2$ be hypergraphs and let $V_1:=V(H_1),
-	V_2:=V(H_2)$. Let $\overline{v}\in V_1^*$ and
-	$\overline{u} \in V_2^*$ be lists of vertices. Let
-	$r\in \N$ be greater than zero. Suppose that
+	Let $\overline{v}\in V_1^*$ and
+	$\overline{u} \in V_2^*$ be of equal length. Let
+	$r\in \N$ be greater than zero. Suppose
 	$(H_1,\overline{v})\simeq_{k,3r+1} (H_2,\overline{u})$.
@@
 	$1\leq i \leq k$. 
-	Let us denote by $v^1_i$ and $v^2_i$ the vertices played
+	Let $v^1_i$ and $v^2_i$ be the vertices played
 	in $H_1$ and $H_2$ respectively during the $i$-th
 	round of $\ehr_k(H_1,H_2)$. 
-	We will show a winning strategy for Duplicator
-	in $d\ehr_{k}\big(H_1;\, H_2\big)$. For each $0\leq i \leq k$,
+	We show a winning strategy for Duplicator
+	in $\ehr_{k}\big(H_1;\, H_2\big)$. For each $0\leq i \leq k$,
 	Duplicator will	keep track of some marked sets 
@@
 	\end{itemize}
-	In particular this means that at the 
-	end of the $i$-th round the marked sets $S\subset V_1$
-	, $T\subset V_2$ and their respective lists $\overline{v}(S)$,
-	$\overline{v}(T)$ satisfy
+	We show that Duplicator can play in a way such that at the
+	end round the following are satisfied:
 	\begin{itemize}
@@
 		in $\overline{v}(T)$.
-	\end{itemize}
-	The following conditions will also be satisfied at the 
-	end of the $i$-th round
-	\begin{itemize}
 		\item[(iii)] 
@@
 	Clearly properties (i) to (iv) hold at the beginning of 
-	the game.  Suppose that
+	the game.  Suppose
 	Duplicator can play in such a way that properties (i) to (iv) hold 
-	until the beginning of the $i$-th round. Suppose that
+	until the beginning of the $i$-th round. Suppose
 	during the $i$-th round Spoiler chooses $v^1_i\in V_1$ 
@@
 	three possible cases:
-	\begin{itemize}
+	\begin{itemize}[leftmargin=*]
 		\item For some unique previously marked set $S\subset V_1$ 
@@
 
-\begin{definition}
 A \textbf{rooted tree} $(T,v)$ is a tree $T$ with a 
 distinguished vertex $v\in V(T)$ called its \textbf{root}.
-\end{definition}
 We will usually omit the root when it is not relevant and 
@@
 \textbf{initial edges} of a rooted tree $(T,v)$ are 
-the edges in $T$ that contain $v$. \par
+the edges in $T$ that contain $v$. 
+We define the radius of a rooted tree
+as the maximum distance between its root
+and any other vertex. 
+\par
 
@@
 \par
-We define the radius of a rooted tree
-as the maximum distance between its root
-and any other vertex. \par
 
@@
 
-\begin{itemize}
+\begin{itemize}[leftmargin=*]
 	\item Any two trees with radius zero are $k$-equivalent.
@@
 	\item Let $r>0$.
-	Suppose that the $k$-equivalence relation has been
+	Suppose the $k$-equivalence relation has been
 	defined for rooted trees with radius at most $r-1$. Let $\Sigma_{k,r-1}$
-	be the set consisting of the $k$-equivalence classes of trees
+	be the set consisting of the $\sim_k$ classes of trees
 	with radius at most $r-1$. Let $\rho$ be an special symbol called the
-	\textbf{root symbol}.
-	Given a rooted tree $(T,v)$ with whose radius is $r$
-	we define its \textbf{canonical ($\Sigma_{k,r-1}\cup \{\rho\}$)-coloring}
+	\textbf{root symbol}. Set $\widehat{\Sigma}_{k,r-1}:=\Sigma_{k,r-1}\cup \{\rho\}$.
+	Then we call a $(k,r)$-\textbf{pattern} to an isomorphism class
+	of $\widehat{\Sigma}_{k,r-1}$-hypergraphs 
+	$(e,\tau)$ that consist of only one edge and satisfy 
+	$\tau(v)=\rho$ for exactly one vertex $v\in V(e)$. We will
+	denote by $P(k,r)$ the set of $(k,r)$-patterns. \par
+	Given a rooted tree $(T,v)$ of radius $r$
+	we define its \textbf{canonical coloring}
 	as the map 
-	$\tau_{(T,v)}: V(T)\rightarrow \Sigma_{k,r-1}\cup \{\rho\}$ satisfying that
+	$\tau_{(T,v)}: V(T)\rightarrow \widehat{\Sigma}_{k,r-1}$ satisfying that
 	 $\tau_{(T,v)}(u)$ is the
@@
 	for any $u\neq v$, and $\tau_{(T,v)}(v)=\tau$. \par
-	Let $T_1$ and $T_2$ be rooted trees with radius $r$. 
+	Let $T_1$ and $T_2$ be rooted trees of radius $r$. 
 	We say that $(T_1,v_1)\sim_k (T_2,v_2)$ 
-	if for any $\delta=1,2$, given any initial edge 
-	$e$ from $(T_\delta,v_\delta)$	the
+	if for any pattern $\epsilon\in P(k,r)$	the
 	``quantity of initial edges $e_1\in E(T_1)$ such that
-	\[
-	\big(e,\tau_{(T_\delta,v_\delta)}\big)
-	\simeq \big(e_1,\tau_{(T_1,v_1)}\big)" 
-	\] and the
+	$\big(e,\tau_{(T_\delta,v_\delta)}\big) \in \epsilon$" 
+	and the
 	``quantity of initial edges $e_2\in E(T_2)$ such that
-	\[
-	\big(e,\tau_{(T_\delta,v_\delta)}\big)
-	\simeq \big(e_2,\tau_{(T_2,v_2)}\big)"\] are equal or
+	$\big(e,\tau_{(T_\delta,v_\delta)}\big)\in \epsilon$
+	" are equal or
 	are both greater than $k-1$.
 \end{itemize}
-Here we are making an slight abuse of notation in the expressions of the
-type $\big(e_1,\tau_{(T_1,v_1)}\big)$. There $e$ denotes the 
-sub-hypergraph of $T_1$ whose vertices are the ones in $V(e)$ and whose
-only edge is $e$. This way $\big(e_1,\tau_{(T_1,v_1)}\big)$ is a 
-$(\Sigma_{(k,r-1)}\cup \{\rho\})$-hypergraph, as defined in \cref{def:color}.
-\end{definition}
-
-\begin{definition}
-	Let $\Sigma_{(k,r-1)}$ be the set of $\sim_k$ classes
-	of rooted trees with radii at most $r-1$. Then
-	we call a $(k,r)$-\textbf{pattern} to an isomorphism class
-	of $(\Sigma_{(k,r-1)}\cup \{\rho \})$-hypergraphs 
-	$(e,\tau)$ that consist of only one edge and satisfy 
-	$\tau(v)=\rho$ for exactly one vertex $v\in V(e)$. We will
-	denote by $P(k,r)$ the set of $(k,r)$-patterns.
+
 \end{definition}
@@
 $\mathcal{T}$ such that any rooted tree $(T,v)$ belongs to
-$\mathcal{T}$ if and only if it holds that
-\begin{itemize}
-	\item[(1)] For any pattern $\epsilon\in E^1_\mathcal{T}$ there are at least
-	$k$ initial edges $e\in E(T)$ such that
-	$(e,\tau_{(T,v)})\in \epsilon$. 
-	\item[(2)] For any pattern $\epsilon\in E^2_\mathcal{T}$ there are exactly
+$\mathcal{T}$ if and only if the following hold: (1) For any pattern 
+$\epsilon\in E^1_\mathcal{T}$ there are at least $k$ initial edges $e\in E(T)$ such that
+$(e,\tau_{(T,v)})\in \epsilon$, and (2) for any pattern 
+$\epsilon\in E^2_\mathcal{T}$ there are exactly
 $a_\epsilon$ initial edges $e\in E(T)$ such that
 $(e,\tau_{(T,v)})\in \epsilon$.	
-\end{itemize}
 \end{obs}
+
 \begin{obs}\label{obs:finitetrees}
@@
 	We proceed by induction. For $r=0$ there is only one $\sim_k$ class.
-	Now let $r>0$ and suppose that the statement holds for $r-1$. Then
+	Now let $r>0$ and suppose the statement holds for $r-1$. Then
 	the number of $(k,r)$-patterns is finite and so is the number
@@
 
-Before proceeding with the proof we need an auxiliary
+Before proceeding with the proof we need the following auxiliary
 result. Let $(T,v)$ be a rooted tree and $e$ an 
@@
 in $T$ whose only path to $v$ contain $e$.
-Now we can check the following:
 
 \begin{lemma} \label{lem:equivalentedges}
-	Fix $r>0$. Suppose that theorem \ref{thm:equivalenttrees}
+	Fix $r>0$. Suppose theorem \ref{thm:equivalenttrees}
 	holds for rooted trees with radii at most $r$.
@@
 	and $(e_2,\tau_{(T_2,v_2)})$.
-	Suppose that in the $i$-th round of the game Spoiler
+	Suppose in the $i$-th round of the game Spoiler
 	plays on $T^\prime_1$. The other case is symmetric. 
 	There are two possibilities:
-	\begin{itemize}
+	\begin{itemize}[leftmargin=*]
 		\item If Spoiler plays $v_1$ 
@@
 		by assumption Duplicator has a winning 
-		strategy in \[
-		d\ehr_{k}\big(\,T^{\prime\prime}_1, u;
-		\quad T^{\prime \prime}_2, f(u)\,  \big)
-		\]
+		strategy in
+		$d\ehr_{k}\big(\,T^{\prime\prime}_1, u;
+		\quad T^{\prime \prime}_2, f(u)\,  \big)$		
 		and they can follow it considering the previous plays in
@@
 	Let $\tau_{(T_1,v_1)}$ and $\tau_{(T_2,v_2)}$ 
-	be the colorings over $T_1$ and $T_2$ defined as in 
+	be the colorings over $T_1$ and $T_2$ as in 
 	the definition of $\sim_k$. 
-	We will show that there is a winning strategy 
+	We show that there is a winning strategy 
 	for Duplicator in
@@
 	in $T_1$ and $T_2$ as non-marked. 
-	Suppose that in the $i$-th round Spoiler plays in 
+	Suppose in the $i$-th round Spoiler plays in 
 	$T_1$. The other case is symmetric. 
-	\begin{itemize}
+	\begin{itemize}[leftmargin=*]
 		\item If Spoiler plays $v_1$ then Duplicator plays $v_2$.
@@
 		There are two possibilities:
-		\begin{itemize}
+		\begin{itemize}[leftmargin=*]
 			\item If $e_1$ is not marked yet, mark it. 
@@
 			edge $e_2$ in $T_2$ satisfying 
-			\[
-			\big(e_1,\tau_{(T_1,v_1)}\big)\simeq
-			\big(e_2,\tau_{(T_2,v_2)}  \big).\]
+			$\big(e_1,\tau_{(T_1,v_1)}\big)\simeq
+			\big(e_2,\tau_{(T_2,v_2)}  \big)$.
 			Mark $e_2$ as well. 
@@
 			has a winning strategy in
-			$ d\ehr{k}(T^\prime_1, v_1; \,\, T^\prime_2,v_2)$
+			$ d\ehr{k}(T^\prime_1, v_1;$ $\,\, T^\prime_2,v_2)$
 			and can play according to it.
@@
 			marked during the same round as $e_1$ and it satisfies 
-			\[
-			\big(e_1,\tau_{(T_1,v_1)}\big)\simeq
-			\big(e_2,\tau_{(T_2,v_2)}  \big).\]	
-			Again, 
-			Because of
-			\cref{lem:equivalentedges}, Duplicator
-			has a winning strategy in
+			$\big(e_1,\tau_{(T_1,v_1)}\big)\simeq
+			\big(e_2,\tau_{(T_2,v_2)}  \big)$.	
+			Again, because of \cref{lem:equivalentedges}, 
+			Duplicator has a winning strategy in
 			$d\ehr{k}(T^\prime_1, v_1; \,\, T^\prime_2,v_2)$
@@
 
-\begin{definition} \label{def:Center}
 The \textbf{center} of an hypergraph $H$, written as
 $Center(H)$,  
-	is the union of all saturated sub-hypergraphs of $H$. 
+is the union of all saturated sub- hypergraphs of $H$. 
 %	Given $r\in \N$, the $r$-\textbf{center} of $H$,
@@
 %	sub-hypergraphs of $H$ with diameter at most $2r+1$.  
-	\par
 Let $H$ be an hypergraph, let $\overline{v}\in V(H)^*$. 
@@
 that belong to $V(H^\prime)$.
-\end{definition}
 
@@
 	H,\overline{v};\,\, v\big)$ in the following way:
-	\begin{itemize}
+	\begin{itemize}[leftmargin=*]
 		\item If $d\big(\, Center(H, \overline{v})
@@
 
+Let $H$ be a non-tree connected hypergraph. We define
+the \textbf{canonical coloring} $\tau_{H}$ over $H$
+as the one that assigns to each vertex $v\in V(H)$ the $\sim_k$ class of the tree
+$\Tr(H,v)$.\par
+
 \begin{definition}
@@
 	We say that $H_1$ and $H_2$ are $k$-equivalent,
-	written as $H_1\sim_k H_2$, if there is an hypergraph isomorphism
-	$f:V(H^\prime_1)\rightarrow V(H^\prime_2)$ such that for all vertices
-	$v\in V(H^\prime_1)$ it holds that
-	\[
-	\mathrm{Tr}\big(H_1;\,\, v\big)\sim_k 
-	\mathrm{Tr}\big(H_2;\,\, f(v)\big).
-	\] 
+	written as $H_1\sim_k H_2$, if
+	$\big( H^\prime_1,\tau_{H_1}\big) \simeq 
+	\big(H^\prime_2,\tau_{H_2}\big)$
 \end{definition}
-	Let $H$ be a non-tree connected hypergraph. We define
-	the canonical coloring $\tau_{H}$ over $Center(H)$
-	as the one that assigns to each vertex $v\in V\big(
-	Center(H)\big)$ the $\sim_k$ class of the tree
-	$\mathrm{Tr}(H,v)$.\par
-	An equivalent definition of $\sim_k$ for non tree connected
-	hypergraphs is the following: 
-	Let $H_1$ and $H_2$ be connected hypergraphs which are not trees.
-	Set $H^\prime_1:= Center(H_1)$ and $H^\prime_2:= Center(H_2)$.
-	Then we say that $H_1\sim_k H_2$ if
-	$\big( H^\prime_1,\tau_{H_1}\big) \simeq 
-	\big(H^\prime_2,\tau_{H_2}\big)$.\par
+
 The main theorem of this section is the following
@@
 		between $\big( H^\prime_1,\tau_{H_1}\big)$ and 
-		$\big(H^\prime_2,\tau_{H_2}\big)$. Let $\overline{v_1}$ 
+		$\big(H^\prime_2,\tau_{H_2}\big)$. Let $\overline{v}$ 
 		be an ordering of the vertices of $H^\prime_1$ and let
-		$\overline{v_2}:=f(\overline{v_1})$ be the corresponding
+		$\overline{u}:=f(\overline{v})$ be the corresponding
 		ordering of the vertices of $H^\prime_2$. Then
 		Duplicator wins 
-		\[	d\ehr_{k}\big(\,
-		H^\prime_1,\overline{v_1};\quad
-		H^\prime_2,\overline{v_2}\,
+		$	d\ehr_{k}\big(\,
+		H^\prime_1,\overline{v};\,\,
+		H^\prime_2,\overline{u}\,
 		\big).
-		\]
+		$
 	\end{theorem}
@@
 		The winning strategy for Duplicator is as follows. 
-		Suppose that at the beginning of the $i$-th round
+		Suppose at the beginning of the $i$-th round
 		Spoiler plays in $H_1$ (the case where they play in
@@
 		Duplicator has a winning strategy in
-		\[
+		$
 		d\ehr_{k}\big(\,
-		T_1,u; \quad T_2, f(u)\,\big),
-		\]
+		T_1,u; \, \, T_2, f(u)\,\big),
+		$
 		and they can follow it taking into account the previous
-		plays made in $T_1$ and $T_2$. In particular, 
+		plays made in $T_1$ and $T_2$, if any. In particular, 
 		if Spoiler has chosen
-		$u$ then Duplicator will necessarily choose $f(u)$.\par
+		$u$ then Duplicator will necessarily choose $f(u)$.
 		One can easily check that distances are preserved
@@
 
-\subsection{$r$-Cores}
-
-\begin{definition} \label{def:Core}
-	Let $H$ be an hypergraph. We define its \textbf{$r$-core}, 
-	written as $Core(H;r)$ as $N(X;r)$,
-	where $X$ is the set of vertices $v\in V(H)$
+\subsection{$r$-Cores} \label{sec:Core}
+
+Let $H$ be an hypergraph. Let $X$ be the set of vertices $v\in V(H)$
 that belong to any saturated sub-hypergraph of $H$
 whose diameter is at most $2r+1$. 
-	Equivalently, $Core(H;r)=N\big(Center(H;\, r);\, r\big)$. Given 
+We define the \textbf{$r$-core} of $H$, 
+written as $Core(H;r)$ as $N(X;r)$. Given 
 $\overline{v}\in V(G)^*$, we define $Core(H,\overline{v};r)$
@@
 belong to $\overline{v}$ or belong to any saturated sub-hypergraph of $H$
-	whose diameter is at most $2r+1$. \par
+whose diameter is at most $2r+1$.
 We say that $H$ is $r$-\textbf{simple} if all connected components
 of $Core(H;r)$ are unicycles.
-\end{definition}
 
@@
 	$\mathcal{O}$ such that any $r$-simple hypergraph $G$ belongs to
-	$\mathcal{O}$ if and only if it holds that
-	\begin{itemize}
-		\item[(1)] For any $\omega\in U^1_\mathcal{O}$ there are at least
-		$k$ connected components $H \subset Core(H;r)$ whose cycle 		
-		$H^\prime=Center(H)$ satisfies that
-		$(H^{\prime},\tau_{H})\in \omega$.
-		\item[(2)]For any $\omega\in U^2_\mathcal{O}$ there are exactly 
-		$a_\omega$ connected components $H \subset Core(H;r)$ whose cycle 		
-		$H^\prime=Center(H)$ satisfies that
-		$(H^{\prime},\tau_{H})\in \omega$.	
-	\end{itemize}
+	$\mathcal{O}$ if and only if it holds that (1) for any $\omega\in U^1_\mathcal{O}$ 
+	there are at least $k$ connected components $H \subset Core(G;r)$ whose cycle 		
+	$H^\prime=Center(H)$ satisfies that	$(H^{\prime},\tau_{H})\in \omega$, and
+	(2) for any $\omega\in U^2_\mathcal{O}$ there are exactly $a_\omega$ 
+	connected components $H \subset Core(G;r)$ whose cycle 
+	$H^\prime=Center(H)$ satisfies that	$(H^{\prime},\tau_{H})\in \omega$.	
 \end{obs}
@@
 %Then, because of a first moment argument the result follows.\par
-%Suppose that $v(H)\geq j$. Otherwise the statement is trivial. 
+%Suppose $v(H)\geq j$. Otherwise the statement is trivial. 
 %As before, given any $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be the random
@@
 \begin{proof}
-	Suppose that there is some edge $e\in E(G)\setminus E(H)$ with
+	Suppose there is some edge $e\in E(G)\setminus E(H)$ with
 	and $ex(e)\geq 0$. Let $P$ be a path
@@
 	probability space. Let $\lambda_1,\dots,\lambda_l$ 
-	be real numbers. Suppose that for any $r_1,\dots,r_l \in \N$
+	be real numbers. Suppose for any $r_1,\dots,r_l \in \N$
 	\[ 
@@
 	random integer variables over the same space. 
-	Let $r_1,\dots,r_l\in \N$.	Suppose that
+	Let $r_1,\dots,r_l\in \N$.	Suppose
 	each $X_i$ is the sum of various indicator random variables
@@
 	let $v\in \N$ be any vertex. 
-	Suppose that \cref{thm:BigTrees} holds
+	Suppose \cref{thm:BigTrees} holds
 	for $r-1$. Then \[
@@
 		is disjoint. 
-		Indeed, suppose that a vertex $w\in [n]\setminus \{v\}$ belongs to two different 
+		Indeed, suppose a vertex $w\in [n]\setminus \{v\}$ belongs to two different 
 		edges $(e_1, \tau_1),$ $(e_2,\tau_2)\in \bigcup_{\epsilon\in P(k,r)} E_\epsilon$. 
@@
 		let $\mathcal{T}_v$ be a $k$-equivalence class
-		of trees with radii	at most $r$. Suppose that
+		of trees with radii	at most $r$. Suppose
 		\cref{thm:BigTrees} holds for $r-1$. Then
@@
 		Then the event $A_n$ that $G_n$ is $(k,r)$-rich.
-		Indeed, suppose that $G_n$ satisfies
+		Indeed, suppose $G_n$ satisfies
 		$A_n$. Let $\mathcal{T}\in \Sigma$ be a $\sim_k$ class and let 

### 2020-05-10 ArticleAcortado.tex
Seguimos

@@
 
+Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
+is a pair $(H, \chi)$ where $H$ is an hypergraph
+and $\chi: V(H)\rightarrow \Sigma$ is a map 
+called \textbf{$\Sigma$-coloring} of $H$. \par
+
 \textbf{Isomorphisms} between hypergraphs are defined the same as 
-isomorphisms between relational structures. We denote the isomorphism relation
-between hypergraphs by $\simeq$. 
-Given and hypergraph $H$, an \textbf{automorphism} of $H$
-is an isomorphism from $H$ to itself. We will denote by
-$\aut(H)$ the number of such automorphisms. \par
+isomorphisms between relational structures. Isomorphisms between $\Sigma$-hypergraphs are just
+isomorphisms between the underlying hypergraphs that also preserve their colorings. 
+In both cases we denote the isomorphism relation by $\simeq$. 
+Given an hypergraph $H$, resp. a $\Sigma$-hypergraph $(H, \chi)$,
+an \textbf{automorphism} of $H$, resp. $(H,\chi)$,
+is an isomorphism from $H$, resp $(H,\chi)$ to itself.
+We will denote by $\aut(H)$, resp. $\aut(H,\chi)$
+ the number of such automorphisms. \par
 
@@
 $H^\prime$ such that
-$V(H^\prime)\subset V$ and $H\simeq H^\prime$.   \par
-
-In our proofs it will be useful to consider colorings over 
-hypergraphs as a way to decorate their 
-vertices with extra information. 
-Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
-is a pair $(H, \chi)$ where $H$ is an hypergraph
-and $\chi: V(H)\rightarrow \Sigma$ is a map 
-called \textbf{$\Sigma$-coloring} of $H$. \par
-\textbf{Isomorphisms} between $\Sigma$-hypergraphs are just isomorphisms between the underlying
-hypergraphs that also preserve their colorings. We also denote the isomorphism relation between 
-$\Sigma$-hypergraphs by $\simeq$.
-Given a $\Sigma$-hypergraph $(H,\chi)$,  an 
-\textbf{automorphism} of $(H,\chi)$ is an 
-isomorphism from it into itself, as before. We will denote
-by $\aut(H,\chi)$ the number of such automorphisms. 
-\par
-
-Let $(H,\chi)$ be a $\Sigma$-hypergraph and let $V$ be a set.
+$V(H^\prime)\subset V$ and $H\simeq H^\prime$. Let 
+$\chi$ be a $\Sigma$-coloring of $H$. 
 As before, we define the set $Copies\big(
@@
 $Copies(\mathbb{H},V)$ via representatives of $\mathbb{H}$.\par
+
+\subsection{Ehrenfeucht-Fraisse Games}
+
+We assume familiarity with Ehrenfeucht-Fraisse (EF) games.
+An introduction to the subject can be found in
+\cite[Section 2]{finitemodeltheory1}, for example. Given
+hypergraphs $H_1$ and $H_2$ we denote the $k$-round EF game played 
+on $H_1$ and
+$H_2$ by $\ehr_k(H_1;H_2)$.
+The following is satisfied:
+
+\begin{theorem}
+	[Ehrenfeut, \citealp{ehrenfeucht1961application}] Let
+	$H_1$ and $H_2$ be hypergraphs.
+	Then Duplicator wins $\ehr_k(H_1;H_2)$
+	if and only if $H_1$ and $H_2$ satisfy the same 
+	sentences $\phi\in FO[\sigma]$ with $qr(\phi)\leq k$.		
+\end{theorem}
+
+Given lists $\overline{v}\in V(H_1)^*$, and 
+$\overline{u}\in V(H_2)^*$ of the same length, 
+we denote the $k$ round 
+Ehrenfeucht-Fraisse game on $H_1$ and $H_2$ with initial position given
+by $\overline{v}$ and $\overline{u}$ by $\ehr_k(H_1,\overline{v};H_2,\overline{u})$.\par
+
+We also define the $k$-round distance Ehrenfeucht-Fraisse game on 
+$H_1$ and $H_2$, denoted by $d\ehr_k(H_1;H_2)$, the same way as
+$\ehr_k(H_1;H_2)$, but now in order for Duplicator to win the
+game the following additional condition has to be satisfied 
+at the end: For any $i,j\in [k]$, $d^{H_1}(v_i,v_j)=d^{H_2}(u_i,u_j)$,
+where $v_s$ and $u_s$ denote the vertex played on $H_1$, resp. $H_2$ in the 
+$s$-th round of the game. 
+Given $\overline{v}\in V(H_1)^*$, and $\overline{u}\in V(H_2)^*$
+lists of vertices of the same length,
+we define the game 
+$d\ehr_k(H_1,\overline{v};H_2,\overline{u})$ analogously to 
+$\ehr_k(H_1,\overline{v};H_2,\overline{u})$.
 
@@
 
-\subsection{Ehrenfeucht-Fraisse Games}
-
-We assume familiarity with Ehrenfeucht-Fraisse (EF) games.
-An introduction to the subject can be found in
-\cite[Section 2]{finitemodeltheory1}, for example. Given
-hypergraphs $H_1$ and $H_2$ we denote the $k$-round EF game played 
-on $H_1$ and
-$H_2$ by $\ehr_k(H_1;H_2)$.
-The following is satisfied:
-
-\begin{theorem}
-	[Ehrenfeut, \citealp{ehrenfeucht1961application}] Let
-	$H_1$ and $H_2$ be hypergraphs.
-	Then Duplicator wins $\ehr_k(H_1;H_2)$
-	if and only if $H_1$ and $H_2$ satisfy the same 
-	sentences $\phi\in FO[\sigma]$ with $qr(\phi)\leq k$.		
-\end{theorem}
-
-Given lists $\overline{v}\in V(H_1)^*$, and 
-$\overline{u}\in V(H_2)^*$ of the same length, 
-we denote the $k$ round 
-Ehrenfeucht-Fraisse game on $H_1$ and $H_2$ with initial position given
-by $\overline{v}$ and $\overline{u}$ by $\ehr_k(H_1,\overline{v};H_2,\overline{u})$.\par
-
-We also define the $k$-round distance Ehrenfeucht-Fraisse game on 
-$H_1$ and $H_2$, denoted by $d\ehr_k(H_1;H_2)$, the same way as
-$\ehr_k(H_1;H_2)$, but now in order for Duplicator to win the
-game the following additional condition has to be satisfied 
-at the end: For any $i,j\in [k]$, $d^{H_1}(v_i,v_j)=d^{H_2}(u_i,u_j)$,
-where $v_s$ and $u_s$ denote the vertex played on $H_1$, resp. $H_2$ in the 
-$s$-th round of the game. 
-Given $\overline{v}\in V(H_1)^*$, and $\overline{u}\in V(H_2)^*$
-lists of vertices of the same length,
-we define the game 
-$d\ehr_k(H_1,\overline{v};H_2,\overline{u})$ analogously to 
-$\ehr_k(H_1,\overline{v};H_2,\overline{u})$.
+\subsection{Main definitions}
+
+\begin{definition}
+Let $H$ be a connected hypergraph. If $ex(H)>0$, then it holds that
+$H$ contains a unique maximal saturated sub-hypergraph $H^\prime$. 
+Furthermore, $H^\prime$ satisfies $ex(H^\prime)=ex(H)$. If $ex(H)\leq 0$ the
+set $H^\prime$ as the empty hypergraph. Given
+$\overline{v}\in V(H)^*$ we define $Center(H,\overline{v})$ as the 
+minimal connected sub-hypergraph in $H$ that contains both $H^\prime$
+and the vertices in $\overline{v}$. 
+If $H$ is a general hypergraph, not necessarily connected, 
+we define $Center(H,\overline{v})$,
+%	, resp. $Center(H,\overline{v};\, r)$, 
+as the union, for all connected components $H^\prime \subset H$,
+of the minimal connected sub-hypergraph of $H^\prime$ that
+contains both $Center(H^\prime)$
+%	, resp. $Center(H^\prime,\overline{v};\, r)$,
+and the vertices in $\overline{v}$
+that belong to $V(H^\prime)$.
+\end{definition}
 
@@
 
-The \textbf{center} of an hypergraph $H$, written as
-$Center(H)$,  
-is the union of all saturated sub- hypergraphs of $H$. 
-%	Given $r\in \N$, the $r$-\textbf{center} of $H$,
-%	written as $Center(H;r)$, is the union of all saturated 
-%	sub-hypergraphs of $H$ with diameter at most $2r+1$.  
-Let $H$ be an hypergraph, let $\overline{v}\in V(H)^*$. 
-%	and let $r\in \N$
-If $H$
-is connected then we define the graph
-$Center(H,\overline{v})$
-%	, resp. $Center(H,\overline{v};\, r)$,
-as the minimal connected sub-hypergaph of $H$ that contains
-both $Center(H)$
-%	, resp. $Center(H;\,r)$,
-and the vertices in $\overline{v}$. Otherwise,
-if $H$ is a general hypergraph we define $Center(H,\overline{v})$,
-%	, resp. $Center(H,\overline{v};\, r)$, 
-as the union, for all connected components $H^\prime \subset H$,
-of the minimal connected sub-hypergraph of $H^\prime$ that
-contains both $Center(H^\prime)$
-%	, resp. $Center(H^\prime,\overline{v};\, r)$,
-and the vertices in $\overline{v}$
-that belong to $V(H^\prime)$.
-
 \begin{definition}\label{def:TrOperator}

### 2020-05-21 ArticleAcortado.tex
Introduccion y conclusiones

@@
 \usepackage{mathptmx}
+
+\makeatletter
+\newtheorem*{rep@theorem}{\rep@title}
+\newcommand{\newreptheorem}[2]{%
+	\newenvironment{rep#1}[1]{%
+		\def\rep@title{#2 \ref{##1}}%
+		\begin{rep@theorem}}%
+		{\end{rep@theorem}}}
+\makeatother
 
@@
 \newtheorem{remark}{Remark}[section]
-
+\newtheorem*{theorem*}{Theorem}
+\newreptheorem{theorem}{Theorem}
+\newreptheorem{corollary}{Corollary}
+
+\newenvironment{oneshot}[1]{\@begintheorem{#1}{\unskip}}{\@endtheorem}
 \newcommand{\cc}{\mathfrak{c}}
@@
 \newcommand{\ehr}{\textsc{Ehr}}
-\newcommand{\PR}[1]{\mathrm{Pr}\big(#1\big)}
+\newcommand{\PR}[1]{\mathrm{Pr}\left(#1\right)}
 \newcommand{\Tr}{\mathrm{Tr}}
@@
 
-\todo[inline]{INCOMPLETA, PENDIENTE DE SER REVISADA}
-Since the work of Erd\"os and R\`enyi on the evolution of random graphs
-\cite{erdHos1960evolution} the study of the asymptotic properties of random
-structures has played a relevant role in combinatorics and computer science.
-A central theme in this topic is, given a succession $(G_n)_n$ of random
-structures of some sort and a property $P$, to determine the limit probability
-that $G_n$ satisfies $P$ or to determine whether that limit exists. \par
-One approach that has proven to be useful is to classify the properties $P$
-according to the logical languages they can be defined in. We say that the 
-succession $(G_n)_n$ obeys a convergence law with respect to some logical language
-$\mathcal{L}$ if for any given property $P$ expressible in $\mathcal{L}$ the 
-probability that $G_n$ satisfies $P$ tends to some limit as $n$ grows to infinity.
-We say that $(G_n)_n$ obeys a zero-one law with respect to $\mathcal{L}$ if
-that limit is always either zero or one. 
+We say that a sequence of random structures $\{G_n\}_n$ satisfies a limit
+law with respect to some logical language $L$ if for any property $P$ expressible in
+$L$ the probability that $G_n$ satisfies $P$ tends to some limit as $n$ goes to $\infty$.
+If that limit takes only the values zero and one then we say that $\{G_n\}_n$ satisfies
+a zero-one law with respect to $L$.  
+Convergence and zero one laws have been extensively studied with regards to 
+random binomial graphs $G(n,p)$.
 The seminal theorem on this topic, due to Fagin \cite{fagin1976probabilities}
-and Glebskii et al. 
-\cite{glebskii1969range} independently, states that if $G_n$ denotes a labeled
-graph with $n$ vertices picked uniformly at random among all $2^{\binom{n}{2}}$ 
-possible then $(G_n)_n$ satisfies a zero-one law with respect to the first order
-(FO) language of graphs. \par
-Originally this result was proven in the broader context of relational
-structures but it was in the theory of random graphs were the study of 
-other zero-one and convergence laws became more prominent. In particular,
-the asymptotic behavior of FO logic in the binomial model of random graphs 
-$G(n,p)$ has been extensively studied. In this model, introduced by Gilbert 
-\cite{gilbert1959random}, a random graph is obtained from $n$ labeled vertices
-by adding each possible edge with probability $p$ independently. When $p=1/2$
-this distribution of random graphs coincides with the uniform one, mentioned 
-above. In general, for the case where $p$ is a constant probability a slight 
-generalization of the proofs in \cite{fagin1976probabilities} and 
-\cite{glebskii1969range} works and $G(n,p)$ satisfies a zero-one law 
-for FO logic. If we consider $p(n)$ a decreasing function of the form
-$n^{-\alpha}$ we can ask the question of what are the values of $\alpha$
-for which $G(n,p(n))$ obeys a zero-one or a convergence law for FO logic. 
-In \cite{shelah1988zero} Shelah and Spencer gave a complete answer 
-for the range $\alpha\in (0,1)$. Among other results, they proved that
-if $\alpha$ is an irrational number in this interval then
-$G(n,p(n))$ obeys a zero-one law for FO logic, while if $\alpha$
-is a rational number in the same range then $G(n,p(n))$ does not
-even satisfy a convergence law for FO logic. The case $\alpha=1$
-was later solved by Lynch in \cite{lynch1992probabilities}. A weaker
-form of the main theorem in that article states the following:
-\begin{theorem} 
-	For any FO sentence $\phi$, the function
+and Glebskii et al. \cite{glebskii1969range} independently, 
+concerns general relational structures.
+When applied to graphs it states that if $p$ is a fixed probability
+then $G(n,p)$ satisfies a zero-one law with respect to the first order
+(FO) language of graphs. This zero-one law was later extended by Shelah and Spencer
+in \cite{shelah1988zero}. There it is proven, among other results,
+that if $p:=p(n)$ was a decreasing function on
+$n$ of the form $n^{-\alpha}$, and $\alpha\in (0,1)$ is irrational
+then $G(n,p(n))$ obeys a zero-one law with respect to FO logic. Moreover, 
+it is also proven that if $\alpha\in (0,1)$ is rational then $G(n,p(n))$ 
+does not obey a convergence law. This was further extended by Lynch
+in \cite{lynch1992probabilities}, where it is shown that in the
+case where the expected number of edges is linear, when $p(n)\sim \beta/n$
+for some $\beta\in (0,\infty)$, then $G(n,p(n))$ satisfies a limit law with
+respect to FO logic. The following is a restatement of the main theorem
+in that article.
+
+\begin{theorem*}
+	Let $p(n)\sim \beta/n$. For any FO sentence $\phi$, the function
 	$F_\phi: (0,\infty)\rightarrow [0,1]$ given by 
-	\[ F_\phi(\beta) = \Ln \mathrm{Pr}\big( \mathrm{G}(n,\beta/n)
-	\text{ satisfies } \phi   \big) \]
-	is well defined and analytic. In particular, for any
-	$\beta \geq 0$ the model $\mathrm{G}(n,\beta/n)$
-	obeys a convergence law for FO logic. 
-\end{theorem}
-
-The analyticity of these asymptotic probabilities with respect to 
-the parameter $\beta$ implies that FO properties cannot "capture" sudden
-changes that occur in the random graph $\mathrm{G}(n,\beta/n)$
-as $\beta$ changes. Given $p(n)$ a probability, $P$ a property of graphs,
-and $Q$ a sufficient condition for $P$ - i.e., a property that 
-implies $P$ -, we say that $Q$ explains $P$ if $\mathrm{G}(n,p(n))$ satisfies 
-the converse implication $P \implies Q$ asymptotically almost surely
-(a.a.s.). A notable example of this phenomenon happens in the range 
-$p(n)= \log(n)/n + \beta/n$ with $\beta$ constant. Erd\"os and R\`enyi
-\cite{erdHos1960evolution} 
-showed that for probabilities of this form $\mathrm{G}(n,p(n))$ 
-a.a.s. is disconnected only if it contains an isolated vertex. 
-An observation by Albert Atserias is the following:
-
-\begin{theorem}
-Let $c$ be a real constant such that 
-$\Ln \mathrm{Pr}\big( G(n, c/n) 
-\text{ is not }	3\text{-colorable }\big)> 0$.  
-Then there is no FO graph property that explains 
-non-$3$-colorability for $G(n, c/n)$.
-\end{theorem}
-
-The short proof of this theorem is as follows: 
-It is a known fact that there are positive constants
-$c_0\leq c_1$ such that $G(n, c/n)$ is a.a.s $3$-colorable
-if $c<c_0$ and it is a.a.s non $3$-colorable if $c>c_1$ 
-REFERENCES NEEDED.
-Suppose $P$ is a FO graph property that implies
-non-$3$-colorability. Then, because of this implication,
-for all values of $c$
-\[\Ln \mathrm{Pr}\big( G(n, c/n) 
-\text{ satisfies } P \big) \leq \Ln \mathrm{Pr}\big( G(n, c/n) 
-\text{ is not }	3\text{-colorable}\big).\]
-In consequence the asymptotic probability that $G(n,c/n)$ 
-satisfies $P$ is zero when $c<c_0$. By Lynch's theorem, if 
-$P$ is definable in FO logic then this asymptotic probability
-varies analytically with $c$. Using the fact that any analytic 
-function that takes value zero in a non-empty interval must 
-equal zero everywhere, we obtain that $G(n,c/n)$ a.a.s does 
-not satisfy $P$ for any value of $c$. 
-As a consequence the theorem follows.  \par
-
-The aim of this work is to extend Lynch's result to arbitrary 
-relational structures were the relations are subject to some
-predetermined symmetry and anti-reflexivity axioms. This was 
-originally motivated by an application to the study of random
-$k$-CNF formulas. Since \cite{chvatal1992mick} it is known that 
-for each $k$ there are constants $c_0,c_1$ such that a random 
-$k$-CNF formula with $cn$ clauses over $n$ variables
-
-%Besides this 
-% 
-%This question was originally posed in \cite{atserias2005definability}
-%by Albert Atserias where the answer was given for various probability
-
-\setcounter{section}{0}
+	\[ F_\phi(\beta) = \Ln \mathrm{Pr}\left( \mathrm{G}(n,p(n))
+	\text{ satisfies } \phi   \right) \]
+	is well defined and is given by an expression with parameter $\beta$ built
+	using rational constants, addition, multiplication and exponentiation with base $e$.
+\end{theorem*}
+
+A relevant aspect of this result is that the limit probability of any FO
+property in $G(n,p(n))$ when $p(n)\sim \beta/n$ varies analytically with $\beta$.
+A consequence of this is that in this conditions no FO property can "capture" sudden changes 
+in the structure of $G(n,p(n))$. \par
+It was left open at the end of \cite{lynch1992probabilities} whether the convergence law obeyed
+by $G(n,\beta/n)$ could be generalized for other random models of relational structures
+that contain relations of degree greater than $2$.
+A result in this regard was obtained in \cite{salvadorbrasil}, 
+among other zero-one and convergence laws.
+There it is considered $G^d(n,p)$ the random model of $d$-uniform hypergraphs where
+each $d$-edge is added to a set of $n$ labeled vertices with probability $p$ independently.
+It is shown that when $p(n)\sim \beta/n^{d-1}$ -i.e., when the expected number of
+edges is linear- then $G^d(n,p(n))$ obeys a convergence law with respect of the FO
+language of $d$-uniform hypergraphs. With little additional work it can be shown that
+in this conditions the limit probability of any FO property of $G^d(n,p(n))$ varies 
+analytically with $\beta$. \par
+We aim to extend this last result to arbitrary relational structures
+to whose relations we can impose symmetry and anti-reflexivity constraints. 
+This generalization is motivated by an application to the problem of random 
+satisfiability. We continue the study started by Atserias in \cite{atserias2005definability}
+with regards to the definability in first order logic of certificates for unsatisfiability
+that hold for typical unsatisfiable formulas. There it is considered a random model for
+$3$-CNF formulas where each possible clause over $n$ variables is added with probability $p$ 
+independently. This way the expected number of clauses is $\Theta(n^3p)$ as $n$ grows.
+The main result of that article states that when the expected number of clauses is $\Theta(n^{2+\alpha})$
+for any arbitrary $\alpha>0$ then there exists some FO property of $3$-CNF formulas that implies
+unsatisfiability and asymptotically almost surely (a.a.s) holds for unsatisfiable formulas. 
+Furthermore, if the expected number of clauses is $\Theta(n^{2-\alpha})$ for any irrational
+$\alpha>0$ then no FO property that implies unsatisfiability holds a.a.s
+for unsatisfiable formulas.
 
@@
 $[n]$ to denote the set ${1,2,\dots,n}$.\par
+Given numbers, $n,m\in \N$ with $m\leq n$ we denote by
+$(n)_m$ the $m$-th falling factorial of $n$. \par
 Given a set $S$ and a natural number $k\in \N$
 we will use $\binom{S}{k}$ to denote the set of 
-subsets of $S$ whose size is $k$. \par
-Given numbers, $n,m\in \N$ with $m\leq n$ we denote by
-$(n)_m$ the $m$-th falling factorial of $n$. \par
+subsets of $S$ whose size is $k$.Given a set
+$S$ and a number $n\in \N$ with $n\leq |S|$ we define
+$(S)_n$ as the subset of $S^n$ consisting of the $n$-tuples
+whose coordinates are all different. 
+We also define $S^*:=\bigcup_{n=0}^\infty S^n$ and
+$(S)_*:=\bigcup_{n\leq |S|} (S)_n$. \par
+
 We will use the convention that over-lined variables
@@
 \par
-
-Given a set
-$S$ and a number $n\in \N$ with $n\leq |S|$ we define
-$(S)_n$ as the subset of $S^n$ consisting of the $n$-tuples
-whose coordinates are all different. 
-We also define $S^*:=\bigcup_{n=0}^\infty S^n$ and
-$(S)_*:=\bigcup_{n\leq |S|} (S)_n$. \par
 
@@
 
-%\todo[inline]{Añadir referencias y trabajo relacionado con random SAT}
+%%\todo[inline]{Añadir referencias y trabajo relacionado con random SAT}
+%
 
@@
 Given a formula $\phi\in FO[\sigma]$ we will use the notation $\phi(\overline{y})$ 
-to denote that $\overline{y}$ is a tuple of 
-(different) variables that contains all free variables in $\phi$ and
-none of its bounded variables, although it may contain variables
-which not appear in $\phi$.
+to express that $\overline{y}$ is a tuple of 
+(different) variables which contains all free variables in $\phi$ and
+none of its bounded variables, but it may contain variables
+which do not appear in $\phi$.
 Formulas with no free variables are called \textbf{sentences} and 
@@
 	each $g\in \Phi_R$:
-	\[ \forall \overline{x}:=x_1,\dots, x_{ar(R)} \big(  R(\overline{x})
-	\iff R(g\cdot\overline{x}) \big)    \]
+	\[ \forall \overline{x}:=x_1,\dots, x_{ar(R)} \left(  R(\overline{x})
+	\iff R(g\cdot\overline{x}) \right)    \]
 	\item \textit{Anti-reflexivity axioms}: For each 
@@
 	\[ \forall x_1,\dots, x_{ar(R)} 
-	\big( (x_i=x_j) \implies \neg R(x_1,\dots, x_{a_s})
-	\big)\]
+	\left( (x_i=x_j) \implies \neg R(x_1,\dots, x_{a_s})
+	\right)\]
 \end{itemize}
@@
 \par
-%
-%An homomorphism between two hypergraphs $G$ and $H$ 
-%a map $f:V(G)\rightarrow V(H)$ that sends edges 
-%from $G$ to edges in $H$ of the same color. That is,
-%if vertices $v_1,\dots, v_{a_i}$ form an edge 
-%$[v_1,\dots,v_{a_i}]\in E_i(G)$, then
-%$[f(v_1),\dots,f(v_{a_i})]\in E_i(H)$.
-%If $f$ is injective then it is called a monomorphism. 
-%If $f$ is bijective and its inverse is also an homomorphism 
-%between $H$ and $G$ then $f$ is called an isomorphism.\par
-%
-%The group of automorphisms $Aut(G)$ of an hypergraph $G$ is the group
-%of isomorphisms between $G$ and itself.
-
-%
-%Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is
-%a sub-hypergraph $H_2\subseteq G$ isomorphic to $H$. The copy
-%is called induced if $H_2$ is an induced sub-hypergraph.
-%We will call a labeled copy
-%of $H$ in $G$ to a monomorphism $f:H\rightarrow G$. 
-%It is satisfied that the number
-%of labeled copies of $H$ in $G$ is $\aut(H)$ times the number
-%of copies of $H$ in $G$.
 
@@
 \[
-ex(G):= \big(\sum_{R\in \sigma} (ar(R)-1)|E_R(G)|\big) - |V(G)|.  
+ex(G):= \left(\sum_{R\in \sigma} (ar(R)-1)|E_R(G)|\right) - |V(G)|.  
 \] 
@@
 \par
-A connected hypergraph $G$ is a path between two of its 
-vertices $v,u\in V(G)$ if $G$ 
-does not contain any connected proper sub-hypergraph containing both $v,u$.
-\par
-A connected hypergraph $G$ is a \textbf{tree} if $ex(G)=-1$ and \textbf{dense} if $ex(G)>0$.
-A connected hypergraph $G$ with $ex(G)\geq 0$ is called \textbf{saturated} 
-if for any non-empty proper sub-hypergraph
-$H\subset G$ it holds $ex(H)<ex(G)$. 
-A connected hypergraph $G$ with $ex(G)=0$ is called \textbf{unicycle}. 
-A saturated unicycle is called a \textbf{cycle}. \par
 Given an hypergraph $G$ we define the following metric, $d$, over $V(G)$:
@@
 \par
+A connected hypergraph $G$ is a path between two of its 
+vertices $v,u\in V(G)$ if $G$ 
+does not contain any connected proper sub-hypergraph containing both $v,u$.
+\par
+A connected hypergraph $G$ is a \textbf{tree} if $ex(G)=-1$ and \textbf{dense} if $ex(G)>0$.
+An hypergraph is called $r$-\textbf{sparse} if it does not contain any dense sub-hypergraph $H$
+such that $diam(H)\leq r$.
+A connected hypergraph $G$ with $ex(G)\geq 0$ is called \textbf{saturated} 
+if for any non-empty proper sub-hypergraph
+$H\subset G$ it holds $ex(H)<ex(G)$. 
+A connected hypergraph $G$ with $ex(G)=0$ is called \textbf{unicycle}. 
+A saturated unicycle is called a \textbf{cycle}. \par
+A \textbf{rooted tree} $(T,v)$ is a tree $T$ with a 
+distinguished vertex $v\in V(T)$ called its \textbf{root}.
+We will usually omit the root when it is not relevant and 
+write just $T$ instead of $(T,v)$. The
+\textbf{initial edges} of a rooted tree $(T,v)$ are 
+the edges in $T$ that contain $v$. 
+We define the radius of a rooted tree
+as the maximum distance between its root
+and any other vertex.
+\par
 
@@
 $\chi$ be a $\Sigma$-coloring of $H$. 
-As before, we define the set $Copies\big(
-(H,\chi),\, \, V\big)$ as the set of $\Sigma$-hypergraphs
+As before, we define the set $Copies\left(
+(H,\chi),\, \, V\right)$ as the set of $\Sigma$-hypergraphs
 $(H^\prime,\chi^\prime)$ satisfying $V(H^\prime)\subset V$ and
@@
 Let $v\in V$ and $s\in \Sigma$. We define the
-set $Copies\big(\mathbb{H}, V;\,\, (v,s)\big)$ 
+set $Copies\left(\mathbb{H}, V;\,\, (v,s)\right)$ 
 as the set of $\Sigma$-hypergraphs
@@
 $p_R$ be a real number between zero and one.
-The random model $G^{\mathcal{C}}\Big(n,\InR{p}\Big)$ 
+The random model $G^{\mathcal{C}}\left(n,\InR{p}\right)$ 
 is the discrete probability space that
@@
 	the function
-	%$F_\phi: [0,1]^{t_u}\times [0,\infty)^{t-t_u}
-	$F_\phi: [0,\infty)^{|\sigma|}
+	%$F_\phi: [0,1]^{t_u}\times (0,\infty)^{t-t_u}
+	$F_\phi: (0,\infty)^{|\sigma|}
 	\rightarrow \R$ given by 
 	\[
-	\InR{\beta} \mapsto \Ln Pr\big( G_n\left(
-	\InR{\beta}\right) \models \phi\big)
+	\InR{\beta} \mapsto \Ln Pr\left( G_n\left(
+	\InR{\beta}\right) \models \phi\right)
 	\]
@@
 \begin{definition} 
-Let $H$ be a connected hypergraph. If $ex(H)>0$, then it holds that
-$H$ contains a unique maximal saturated sub-hypergraph $H^\prime$. 
-Furthermore, $H^\prime$ satisfies $ex(H^\prime)=ex(H)$. If $ex(H)\leq 0$ the
-set $H^\prime$ as the empty hypergraph. Given
+Let $H$ be a connected hypergraph. Then it holds that
+$H$ contains a unique maximal saturated sub-hypergraph $H^\prime$
+and it satisfies $ex(H^\prime)=ex(H)$ if $ex(H)\geq 0$ and $H^\prime=\emptyset$ 
+if $H$ is a tree. Given
 $\overline{v}\in V(H)^*$ we define $Center(H,\overline{v})$ as the 
@@
 and the vertices in $\overline{v}$. 
-If $H$ is a general hypergraph, not necessarily connected, 
+If $H$ is not connected 
 we define $Center(H,\overline{v})$,
 %	, resp. $Center(H,\overline{v};\, r)$, 
-as the union, for all connected components $H^\prime \subset H$,
-of the minimal connected sub-hypergraph of $H^\prime$ that
-contains both $Center(H^\prime)$
-%	, resp. $Center(H^\prime,\overline{v};\, r)$,
-and the vertices in $\overline{v}$
-that belong to $V(H^\prime)$.
+as the union of $Center(H^{\prime\prime},\overline{u})$
+for all connected components $H^{\prime\prime} \subset H$,
+where $\overline{u}\in V(H)^*$ contains exactly the vertices
+in $\overline{v}$ belonging to $V(H^{\prime\prime})$. When $\overline{v}$
+is empty we simply write $Center(H)$.
 \end{definition}
 
+\begin{definition}
+Let $H$ be an hypergraph, $\overline{v}\in V(H)^*$
+and $r\in \N$. Let $X$ be the set of vertices $v\in V(H)$
+that either belong to $\overline{v}$ or belong 
+to some saturated sub-hypergraph of $H$ with
+diameter at most $2r+1$. 
+We define $Core(H, \overline{v};r)$ as $N(X;r)$. If
+$\overline{v}$ is empty we write $Core(H;r)$.
+We say that $H$ is \textbf{$r$-simple} if all connected components of 
+$Core(H;r)$ are unicycles. 	
+\end{definition}
+
+\begin{definition}\label{def:TrOperator}
+	Let $H$ be an hypergraph, let $\overline{v}\in V(H)^*$ and 
+	let $v\in H$ be such that $d(Center(H,\overline{v}),$ $ \, v)<\infty$. 
+	Let $X\subset V(H)$ be the set
+	\[
+	X:=\big\{\, u\in V(H) \,\, \big| \, 
+	d\left(\, Center(H, \overline{v})
+	, \, \, u \right)= d\left(\, Center(H, \overline{v})
+	, \, \, v \right) + d(v,u)
+	\big\}.
+	\]
+	Then we define $\mathrm{Tr}\left(
+	H,\overline{v};\,\, v\right)$ as the tree $H[X]$ 		
+	to which we assign $v$ as a root. That is,
+	$\mathrm{Tr}\left(
+	H,\overline{v};\,\, v\right)$ is the tree formed of all 
+	vertices whose only path to $Center(H,\overline{v})$ 
+	contains $v$. One can easily check that $H[X]$ is indeed a tree:
+	if it was not then it would contain some saturated sub-hypergraph, leading
+	to contradiction. 
+	Given $r\in \N$ we define $\mathrm{Tr}(H,\overline{v};\, v;\, r)$ as
+	$\mathrm{Tr}( Core(H,\overline{v};\,r),\overline{v}; \, v)$.
+	In the case that $\overline{v}$ is the empty list we will write
+	simply $\mathrm{Tr}(H;\,\, v)$ or $\Tr(H;\,\,v;\,\,r)$.
+\end{definition}
+
+\begin{definition}
+
+	Fix a natural number $k$. We define the
+	\textbf{$k$-equivalence} relation over rooted trees, 
+	written as $\sim_k$, by induction over their radii as follows:
+
+	\begin{itemize}[leftmargin=*]
+		\item Any two trees with radius zero are $k$-equivalent.
+		Notice that those trees
+		consist only of one vertex: their respective roots.
+
+		\item Let $r>0$.
+		Suppose the $k$-equivalence relation has been
+		defined for rooted trees with radius at most $r-1$. Let $\Sigma_{k,r-1}$
+		be the set consisting of the $\sim_k$ classes of trees
+		with radius at most $r-1$. Let $\rho$ be an special symbol called the
+		\textbf{root symbol}. Set $\widehat{\Sigma}_{k,r-1}:=\Sigma_{k,r-1}\cup \{\rho\}$.
+		Then we call a $(k,r)$-\textbf{pattern} to an isomorphism class
+		of $\widehat{\Sigma}_{k,r-1}$-hypergraphs 
+		$(e,\tau)$ that consist of only one loop-free edge and no isolated vertices,
+		and satisfy 
+		$\tau(v)=\rho$ for exactly one vertex $v\in V(e)$. We will
+		denote by $P(k,r)$ the set of $(k,r)$-patterns. \par
+		Given a rooted tree $(T,v)$ of radius $r$
+		we define its \textbf{canonical coloring}
+		as the map 
+		$\tau_{(T,v)}: V(T)\rightarrow \widehat{\Sigma}_{k,r-1}$ satisfying that
+		$\tau_{(T,v)}(u)$ is the
+		$\sim_k$ class of $\mathrm{Tr}(T,u;\, \,v)$
+		for any $u\neq v$, and $\tau_{(T,v)}(v)=\tau$. \par
+		Let $T_1$ and $T_2$ be rooted trees of radius $r$. 
+		We say that $(T_1,v_1)\sim_k (T_2,v_2)$ 
+		if for any pattern $\epsilon\in P(k,r)$	the
+		``quantity of initial edges $e_1\in E(T_1)$ such that
+		$\left(e,\tau_{(T_\delta,v_\delta)}\right) \in \epsilon$" 
+		and the
+		``quantity of initial edges $e_2\in E(T_2)$ such that
+		$\left(e,\tau_{(T_\delta,v_\delta)}\right)\in \epsilon$
+		" are equal or
+		are both greater than $k-1$.
+	\end{itemize}
+
+\end{definition}
+
+The following is a way of characterizing $\sim_k$ classes
+of rooted trees with radii at most $r$ that will be useful later.
+
+\begin{obs}\label{obs:equivalenttrees}
+	Let $\mathbf{T}$ be a $\sim_k$ class of rooted trees with
+	radii at most $r$. Then there is a partition $E^1_\mathbf{T},
+	E^2_\mathbf{T}$ of $P(k,r)$ and natural numbers $a_\epsilon<k$
+	for each $\epsilon\in E^2_\mathbf{T}$ that only depend on 
+	$\mathbf{T}$ such that any rooted tree $(T,v)$ belongs to
+	$\mathbf{T}$ if and only if the following hold: (1) For any pattern 
+	$\epsilon\in E^1_\mathbf{T}$ there are at least $k$ initial edges $e\in E(T)$ such that
+	$(e,\tau_{(T,v)})\in \epsilon$, and (2) for any pattern 
+	$\epsilon\in E^2_\mathbf{T}$ there are exactly
+	$a_\epsilon$ initial edges $e\in E(T)$ such that
+	$(e,\tau_{(T,v)})\in \epsilon$.	
+\end{obs}
+
+\begin{obs}\label{obs:finitetrees}
+	Using last characterization of $\sim_k$ classes
+	it is easy to show that for any $r\in \N$ the quantity
+	of $\sim_k$ classes of trees with radii at most $r$ is finite. 
+	We proceed by induction. For $r=0$ there is only one $\sim_k$ class.
+	Now let $r>0$ and suppose the statement holds for $r-1$. Then
+	the number of $(k,r)$-patterns is finite and so is the number
+	of $\sim_k$ classes of trees with radii at most $r$. 
+\end{obs}
+
+\begin{definition}
+	Given $H$ be a non-tree connected hypergraph, we define
+	its \textbf{canonical coloring} $\tau_{H}$
+	as the one that assigns to each vertex $v\in V(H)$ the $\sim_k$ 
+	class of the tree
+	$\Tr(H,v)$.
+	Let $H_1$ and $H_2$ be connected hypergraphs which are not trees.
+	Set $H^\prime_1:= Center(H_1)$ and $H^\prime_2:= Center(H_2)$.
+	We say that $H_1$ and $H_2$ are $k$-equivalent,
+	written as $H_1\sim_k H_2$, if
+	$\left( H^\prime_1,\tau_{H_1}\right) \simeq 
+	\left(H^\prime_2,\tau_{H_2}\right)$
+\end{definition}
+
+\begin{definition} \label{def:agreeability}
+	Let $H_1$ and $H_2$ be hypergraphs and let $r\in \N$.
+	Let $H^\prime_1:=Core(H_1;r)$ and $H^\prime_2:=Core(H_2;r)$. 
+	We say that $H_1$ and $H_2$ are $(k,r)$-agreeable, written
+	as $H_1\approx_{k,r} H_2$ if for any $\sim_k$ class $\mathcal{H}$ 
+	``the number of connected
+	components in $H^\prime_1$ that belong to $\mathcal{H}$" and
+	``the number of connected components in $H^\prime_2$ that belong to 
+	$\mathcal{H}$" are the same or are both greater than $k-1$.\par
+	%	 satisfies that
+	%	``the number of connected components $H^{\prime\prime}_1$
+	%	from $H^\prime_1$ such that $ H^{\prime\prime}_1 \sim_k F\, \, \,$'' 
+	%	and ``the number of
+	%	connected components $H^{\prime \prime}_2$ of $H^\prime_2$
+	%	such that
+	%	$ H^{\prime\prime}_2\sim_k F\, \, \,$" 
+	%	are both equal or are both greater 
+	%	or equal than $k$. Then we say that $H_1$ and $H_2$
+	%	are $(k,r)$-\textbf{agreeable}, written as $H_1\approx_{k,r} H_2$. \par
+
+\end{definition}
+
+\begin{definition}
+	Let $\Sigma_{(k,r-1)}$ be the set of $\sim_k$ classes
+	of rooted trees with radii at most $r-1$. Then
+	we call a $(k,r)$-\textbf{cycle} to an isomorphism class
+	of $\Sigma_{(k,r-1)}$-hypergraphs 
+	$(H,\tau)$ that are cycles of diameter at most $2r+1$.
+	We will denote by $C(k,r)$ the set of $(k,r)$-cycles.
+\end{definition}
+
+\begin{obs}\label{obs:agreeablecores}
+	Let $\mathcal{O}$ be a $\approx_{k,r}$ class
+	of $r$-simple hypergraphs. 
+	Then there is a partition $U^1_\mathcal{O},
+	U^2_\mathcal{O}$ of $C(k,r)$ and natural numbers $a_\omega<k$
+	for each $\omega\in U^2_\mathcal{O}$ that only depend on 
+	$\mathcal{O}$ such that any $r$-simple hypergraph $G$ belongs to
+	$\mathcal{O}$ if and only if it holds that (1) for any $\omega\in U^1_\mathcal{O}$ 
+	there are at least $k$ connected components $H \subset Core(G;r)$ whose cycle 		
+	$H^\prime=Center(H)$ satisfies that	$(H^{\prime},\tau_{H})\in \omega$, and
+	(2) for any $\omega\in U^2_\mathcal{O}$ there are exactly $a_\omega$ 
+	connected components $H \subset Core(G;r)$ whose cycle 
+	$H^\prime=Center(H)$ satisfies that	$(H^{\prime},\tau_{H})\in \omega$.	
+\end{obs}
+
+\begin{definition} \label{def:rich}
+	Let $H$ be an hypergraph and let $r\in\N$. Let
+	$X\subset V(H)$ be the set of vertices in $H$
+	belonging to some saturated sub-hypergraph of diameter
+	at most $2r+1$.	We say that $H$ is $(k,r)$-\textbf{rich}
+	if for any $r^\prime\leq r$, any vertices $v_1,\dots, v_k$ 
+	and any $\sim_k$ class $\mathbf{T}$ of trees with radius
+	at most $r^\prime$ it holds that there exists a vertex $v\in V(H)$
+	such that $d(v,X)> 2r^\prime+1$, $d(v,v_i)>2r^\prime+1$ for all
+	$v_i$'s and $T:=N(v;r^\prime)$ is a tree satisfying
+	$(T,v)\in \mathbf{T}$.	
+\end{definition}
+
 \subsection{Outline of the proof}
@@
 We show now an outline of the proof of \cref{thm:main}. \par 
-The arguments mirror the ones in the proof of theorem 2.1
-in \cite{lynch1992probabilities}, adapted to fit our context. Fix $r\in \N$.
-The following facts hold:
-\begin{itemize}
-	\item A.a.s $G_n$ does not contain any dense hypergraph of diameter at most 
-	$2r+1$ (\cref{thm:sparse}). In consequence, all $r$-neighborhoods in $G_n$
-	a.a.s are either trees or unicycles.
-	\item Given any fixed vertices $v_1,\dots, v_m\in\N$, a.a.s 
-	$d(v_i,v_j)>2r+1$ for any two $v_i,v_j$ and a.a.s all the $N(v_i;r)$'s 
-	are trees (\cref{lem:disjointtrees}).
-\end{itemize} 
-For any given $k\in \N$, we define an equivalence relation $\sim_k$ for 
-hypergraphs (\cref{sect:equivtrees}, and \cref{sect:equivunicycles})
-in a way that $H_1\sim_k H_2$ implies that Duplicator wins $d\ehr_{k}(H_1;H_2)$.\par
-Given $r\in \N$, we define the \textbf{$r$-core} of an hypergraph $H$, 
-written as $Core(H;r)$, the union of the $r$-neighborhoods of
-all saturated sub-hypergraphs of $H$ whose diameter is at most $2r+1$.
-We say that $H$ is $r$-simple if all connected components of
-$Core(H;r)$ are unicycles (\cref{sec:Core}) \par
-For any given $k,r\in \N$ we say that $H_1\approx_{k,r} H_2$ for two
-hypergraphs if $Core(H_1;r)$ and $Core(H_2;r)$ contain ``the same number
-up to $k$" of connected components of each $\sim_k$ class (\cref{def:agreeability}).\par
-Given $k,r\in \N$ we say that an hypergraph $H$ is $(k,r)$-rich if, informally, 
-it has enough ``$r$-neighborhoods that are trees" of each $\sim_k$ class which
-are sufficiently far from each other and sufficiently far from any small saturated
-graph (\cref{def:rich}). \par
-We prove the following facts:
-\begin{itemize}
-	\item[(1)] Let $k\in \N$ and let $r:=(3^k-1)/2$. Let $H_1$ and $H_2$
-	be $(k,r)$-rich hypergraphs satisfying $H_1\approx_{k,r} H_2$. Then
-	Duplicator wins $\ehr_{k}(H_1; H_2)$ (\cref{thm:Duplicatorwins}).
-	\item[(2)] Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple (\cref{cor:simple}).
-	\item[(3)] Let $k,r\in \N$. Then a.a.s $G_n$ is $(k,r)$-rich (\cref{thm:rich}).
-	\item[(4)] Let $k,r \in \N$. Let $\mathcal{O}$ be a $\approx_{k,r}$ class
+The arguments are similar to the ones in the proof of
+ \cite[Theorem 2.1]{lynch1992probabilities},
+adapted to fit our context. As in that
+article the proof is divided in two parts: a model theoretic part and a 
+probabilistic part. The main result of the first part is the following
+
+\begin{reptheorem}{thm:Duplicatorwins}
+	Let $H_1$, $H_2$ be hypergraphs. Let $r:=(3^k-1)/2$. Suppose
+	that both $H_1$ and $H_2$ are $(k,r)$-rich and
+	$H_1\approx_{k,r} H_2$. Then Duplicator wins $\ehr_{k}(H_1,H_2)$
+\end{reptheorem}
+
+With regards to the second part, 
+the ``landscape'' of $G_n$ can be described similarly to the one 
+of $G(n,c/n)$ as in \cite{shelah1994can}: A.a.s for any fixed radius $r$
+all neighborhoods $N(v;r)$ in $G_n$ are trees or unicycles, so cycles in 
+$G_n$ are far apart. One can find arbitrarily
+many copies of any fixed tree, while the expected number of copies 
+of any fixed cycle is finite. The main probabilistic results are the
+following:
+\begin{reptheorem}{cor:simple}
+  	Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple.
+\end{reptheorem}
+
+\begin{reptheorem}{thm:rich}
+	Let $k,r\in \N$. Then a.a.s $G_n$ is $(k,r)$-rich.
+\end{reptheorem}
+
+\begin{reptheorem}{thm:agreeabilityprobabilities}
+	Let $k,r \in \N$. Let $\mathcal{O}$ be a $\approx_{k,r}$ class
 	of $r$-simple hypergraphs. Then 
 	\[
-	\Ln \Pr\left(G_n\left(\{\beta_R\}_{R\in \sigma}\right)\in \mathcal{O}\right)
+	\Ln \mathrm{Pr}\left(G_n\left(\{\beta_R\}_{R\in \sigma}\right)\in \mathcal{O}\right)
 	\]
 	exists
-	and is an analytic expression in $\{\beta_R\}_{R\in \sigma}$ 
-	(\cref{thm:agreeabilityprobabilities}).
-\end{itemize}
-Then an sketch of the proof of the main theorem \cref{thm:main}, given in \cref{sect:main},
- is the following:
+	and is an analytic expression in $\{\beta_R\}_{R\in \sigma}$.
+\end{reptheorem}
+
+An sketch of the proof of \cref{thm:main} using these results is the following.
 Let $\Phi\in FO[\sigma]$ be a sentence and let $k:=qr(\Phi)$, $r:=(3^k-1)/2$.
-Because of (1) and (3) it holds that for any $\approx_{k,r}$ class $\mathcal{O}$
-\[
-\Ln \Pr\left(G_n \models \Phi\, \big| \, G_n\in \mathcal{O} \right)= \text{ $0$ or $1$ }.
-\]
-This together with (3) and the fact that there are a finite number of
+Because of \cref{thm:Duplicatorwins} and \cref{thm:rich}
+it holds that for any $\approx_{k,r}$ class $\mathcal{O}$
+\[
+\Ln \mathrm{Pr}\left(G_n \models \Phi\, \big| \, G_n\in \mathcal{O} \right)= \text{ $0$ or $1$ }.
+\]
+This together with \cref{cor:simple}
+and the fact that there are a finite number of
 $\approx_{k,r}$-classes of $r$-simple hypergraphs imply that $\Ln \PR{G_n \models \Phi}$
@@
 where $\mathcal{O}$ is some $\approx_{k,r}$-class of $r$-simple hypergraphs.
-Finally, using (4) we get that $\Ln \PR{G_n \models \Phi}$ exists and 
+Finally, using \cref{thm:agreeabilityprobabilities}
+ we get that $\Ln \PR{G_n \models \Phi}$ exists and 
 is an analytic expression in $\{\beta_R\}_{R\in \sigma}$, as we wanted.
-%We show that for any quantifier rank $k$ there are some classes of
-%hypergraphs 
-%$C^k_1,\dots, C^k_{n_k}$ such that
-%\begin{itemize}[noitemsep, topsep=0pt]
-%	\item[(1)] a.a.s the rank $k$ type of any two graphs in the same class coincide, 
-%	\item[(2)] a.a.s. any random graph belongs to some of them, and
-%	\item[(3)] the limit probability of random graph belonging to 
-%	any of them is an analytic expression on the parameters $\overline{\beta}$. 
-%\end{itemize}
-%
-%After this is archived the theorem follows easily. 
-%
-%The objective of next sections will be to define the classes 
-%$C_1,\dots, C_{n_k}$ and to show that they satisfy properties (1), (2) and (3).
-%
-%Fix a quantifier rank $k$. It is known (\cite{finitemodeltheory1}, Section 2.4)
-%that given an structure $G$, its 
-%first order logic properties definable by sentences
-%whose quantifier rank is bounded by $k$
-%depend only on the $r_k$-neighborhoods in $G$ for some 
-%constant $r_k$ that only
-%depends on $k$.
 
@@
 
-\subsection{Some winning strategies for Duplicator}
+\subsection{Winning strategies for Duplicator}
 
@@
 \overline{u} \in V_2^*$ be tuples of the same length.
-We write $(H_1,\overline{v})\simeq_{k,r}(H_2 \overline{u})$, if Duplicator wins
-$d\ehr_k\big(N(\overline{v};r),
-\overline{v};\, N(\overline{u};r),\overline{u}\big)$.
+We write $(H_1,\overline{v})\simeq_{k,r}(H_2, \overline{u})$, if Duplicator wins
+$d\ehr_k\left(N(\overline{v};r),
+\overline{v};\, N(\overline{u};r),\overline{u}\right)$.
 Given $X\subseteq V_1$ and $Y\subseteq V_2$
@@
 $\overline{u}\in V_2^*$ we write
- $\big(H_1, (X,\overline{v})  \big)
-\simeq_{k,r} \big(H_2, (Y,\overline{u})  \big)$, if
+ $\left(H_1, (X,\overline{v})  \right)
+\simeq_{k,r} \left(H_2, (Y,\overline{u})  \right)$, if
 $X$ and $Y$ can be ordered to form lists
@@
 is a slight strengthening of \cite[Theorem 
-2.6.7]{spencer2013strange}, is the following:
+2.6.7]{spencer2013strange}, is the following.
 
@@
 	\end{enumerate}
-	Then Duplicator wins $\ehr_k\big(H_1;H_2\big)$.
+	Then Duplicator wins $\ehr_k\left(H_1;H_2\right)$.
 \end{theorem}
@@
 	\[
-	d\ehr_k\big(\, N(\overline{v};3r+1),
-	\overline{v}; \quad N(\overline{u};3r+1),\overline{u}\, \big)
+	d\ehr_k\left(\, N(\overline{v};3r+1),
+	\overline{v}; \quad N(\overline{u};3r+1),\overline{u}\, \right)
 	\]
@@
 	\[
-	d\ehr_{k-1}\big(\, N(\overline{v};3r+1),
+	d\ehr_{k-1}\left(\, N(\overline{v};3r+1),
 	\overline{v_2}; \quad N(\overline{u};3r+1)
-	,\overline{u_2} \, \big)\]
+	,\overline{u_2} \, \right)\]
 	as well. Call $H^\prime_1=N(\overline{v};3r+1)$,
@@
 	\[
-	d\ehr_{k-1}\big(\, N^{H^\prime_1}(
+	d\ehr_{k-1}\left(\, N^{H^\prime_1}(
 	\overline{v_2};r),\overline{v_2};\quad
-	N^{H^\prime_2}(\overline{u_2};r),\overline{u_2}\, \big).
+	N^{H^\prime_2}(\overline{u_2};r),\overline{u_2}\, \right).
 	\]
@@
 \end{proof}
-\noindent\rule{2cm}{0.4pt}\par
-
-Now we are in conditions to prove \cref{thm:DuplicatorAux}.
 
@@
 	We show a winning strategy for Duplicator
-	in $\ehr_{k}\big(H_1;\, H_2\big)$. For each $0\leq i \leq k$,
+	in $\ehr_{k}\left(H_1;\, H_2\right)$. For each $0\leq i \leq k$,
 	Duplicator will	keep track of some marked sets 
@@
 		\[
-		\big(H_1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
-		\big(H_2, (T,\overline{v}(T))\big).	\]
+		\left(H_1, (S,\overline{v}(S))\right)\simeq_{k-i,r_i}
+		\left(H_2, (T,\overline{v}(T))\right).	\]
 
@@
 	\[
-	d\ehr_{k-i}\big(\,
+	d\ehr_{k-i}\left(\,
 	N(\overline{v}^1;\, r_i), \overline{v}^1; \quad
 	N(\overline{v}^2;\, r_i),\overline{v}^2 \,
-	\big),	
+	\right),	
 	\]
@@
 		same round as $T$. By hypothesis 
-		\[ \big(H_1,(S,\overline{v}(S))\big)
+		\[ \left(H_1,(S,\overline{v}(S))\right)
 		\simeq_{k-i+1,3r_i+1}
-		\big(H_2,(T,\overline{v}(T))\big). 		
+		\left(H_2,(T,\overline{v}(T))\right). 		
 		\]
@@
 		\[
-		d\ehr_{k-i+1}\big(\,
+		d\ehr_{k-i+1}\left(\,
 		N(\overline{w}^\smallfrown \overline{v}(S); \, 3r_i	+ 1)
@@
 		, \overline{z}^\smallfrown \overline{v}(T)\,	
-		\big).		
+		\right).		
 		\]
@@
 		\[
-		\big(H_1, (S,\overline{v}(S))\big)\simeq_{k-i,r_i}
-		\big(H_2, (T,\overline{v}(T))\big).
+		\left(H_1, (S,\overline{v}(S))\right)\simeq_{k-i,r_i}
+		\left(H_2, (T,\overline{v}(T))\right).
 		\]
@@
 		\[
-		d\ehr_{k-i+1}\big( \,
+		d\ehr_{k-i+1}\left( \,
 		N(\overline{w};3r_i+1), \overline{w};
@@
 		N(\overline{z};3r_i+1), \overline{z}
-		\, \big).		
+		\, \right).		
 		\]
@@
 %	
-%	\[\mathcal{X}[0]=\emptyset,
-%	\quad \mathcal{Y}[0]=\emptyset.\]
+%	\[\mathcal{X}(0,\infty]=\emptyset,
+%	\quad \mathcal{Y}(0,\infty]=\emptyset.\]
 %	At the end of the $s$-th round $\mathcal{X}[s-1]$,
@@
 
-A \textbf{rooted tree} $(T,v)$ is a tree $T$ with a 
-distinguished vertex $v\in V(T)$ called its \textbf{root}.
-We will usually omit the root when it is not relevant and 
-write just $T$ instead of $(T,v)$. The
-\textbf{initial edges} of a rooted tree $(T,v)$ are 
-the edges in $T$ that contain $v$. 
-We define the radius of a rooted tree
-as the maximum distance between its root
-and any other vertex. 
-\par
-
-%
-%Similarly, we define an edge-rooted tree $(T,e,v)$
-%as a tree $T$ with a distinguished edge $e\in E(T)$ and
-%a distinguished vertex $v\in e$. \par
-Given a rooted tree $(T, v)$, and a vertex $u\in V(T)$, 
-we define $\mathrm{Tr}(T,v;\,\, u)$ as the tree $T[X]$ induced on the
-set $X:=\{ \, w\in V(T) \, | \, d(v,w)=d(v,u)+ d(u,w) \,  \}
-$, to which we assign $u$ as the root.
-That is, $\mathrm{Tr}(T,v;\,\, u)$ is the tree consisting of those vertices
-whose only path to $v$ contains $u$.
-\par
-
-\begin{definition}
-
-Fix a natural number $k$. We define the
-\textbf{$k$-equivalence} relation over rooted trees, 
-written as $\sim_k$, by induction over their radii as follows:
-
-\begin{itemize}[leftmargin=*]
-	\item Any two trees with radius zero are $k$-equivalent.
-	Notice that those trees
-	consist only of one vertex: their respective roots.
-
-	\item Let $r>0$.
-	Suppose the $k$-equivalence relation has been
-	defined for rooted trees with radius at most $r-1$. Let $\Sigma_{k,r-1}$
-	be the set consisting of the $\sim_k$ classes of trees
-	with radius at most $r-1$. Let $\rho$ be an special symbol called the
-	\textbf{root symbol}. Set $\widehat{\Sigma}_{k,r-1}:=\Sigma_{k,r-1}\cup \{\rho\}$.
-	Then we call a $(k,r)$-\textbf{pattern} to an isomorphism class
-	of $\widehat{\Sigma}_{k,r-1}$-hypergraphs 
-	$(e,\tau)$ that consist of only one edge and satisfy 
-	$\tau(v)=\rho$ for exactly one vertex $v\in V(e)$. We will
-	denote by $P(k,r)$ the set of $(k,r)$-patterns. \par
-	Given a rooted tree $(T,v)$ of radius $r$
-	we define its \textbf{canonical coloring}
-	as the map 
-	$\tau_{(T,v)}: V(T)\rightarrow \widehat{\Sigma}_{k,r-1}$ satisfying that
-	 $\tau_{(T,v)}(u)$ is the
-	$\sim_k$ class of $\mathrm{Tr}(T,u;\, \,v)$
-	for any $u\neq v$, and $\tau_{(T,v)}(v)=\tau$. \par
-	Let $T_1$ and $T_2$ be rooted trees of radius $r$. 
-	We say that $(T_1,v_1)\sim_k (T_2,v_2)$ 
-	if for any pattern $\epsilon\in P(k,r)$	the
-	``quantity of initial edges $e_1\in E(T_1)$ such that
-	$\big(e,\tau_{(T_\delta,v_\delta)}\big) \in \epsilon$" 
-	and the
-	``quantity of initial edges $e_2\in E(T_2)$ such that
-	$\big(e,\tau_{(T_\delta,v_\delta)}\big)\in \epsilon$
-	" are equal or
-	are both greater than $k-1$.
-\end{itemize}
-
-\end{definition}
-
-The following is a way of characterizing $\sim_k$ classes
-of rooted trees with radii at most $r$ that will be useful later.
-
-\begin{obs}\label{obs:equivalenttrees}
-Let $\mathcal{T}$ be a $\sim_k$ class of rooted trees with
-radii at most $r$. Then there is a partition $E^1_\mathcal{T},
-E^2_\mathcal{T}$ of $P(k,r)$ and natural numbers $a_\epsilon<k$
-for each $\epsilon\in E^2_\mathcal{T}$ that only depend on 
-$\mathcal{T}$ such that any rooted tree $(T,v)$ belongs to
-$\mathcal{T}$ if and only if the following hold: (1) For any pattern 
-$\epsilon\in E^1_\mathcal{T}$ there are at least $k$ initial edges $e\in E(T)$ such that
-$(e,\tau_{(T,v)})\in \epsilon$, and (2) for any pattern 
-$\epsilon\in E^2_\mathcal{T}$ there are exactly
-$a_\epsilon$ initial edges $e\in E(T)$ such that
-$(e,\tau_{(T,v)})\in \epsilon$.	
-\end{obs}
-
-\begin{obs}\label{obs:finitetrees}
-	Using last characterization of $\sim_k$ classes
-	it is easy to show that for any $r\in \N$ the quantity
-	of $\sim_k$ classes of trees with radii at most $r$ is finite. 
-	We proceed by induction. For $r=0$ there is only one $\sim_k$ class.
-	Now let $r>0$ and suppose the statement holds for $r-1$. Then
-	the number of $(k,r)$-patterns is finite and so is the number
-	of $\sim_k$ classes of trees with radii at most $r$. 
-\end{obs}
-
-We want prove the following
+We want prove the following.
+
 \begin{theorem} \label{thm:equivalenttrees} 
@@
 
-Before proceeding with the proof we need the following auxiliary
+Before proceeding with the proof we need  an auxiliary
 result. Let $(T,v)$ be a rooted tree and $e$ an 
@@
 to which we assign $v$ as the root. In other words, 
-$\mathrm{Tr}\big(T,v;\, e\big)$ is the tree formed of 
+$\mathrm{Tr}\left(T,v;\, e\right)$ is the tree formed of 
 $v$ and all the vertices
@@
 	plays on $T^\prime_1$. The other case is symmetric.
-	There are two possibilities:
-	\begin{itemize}[leftmargin=*]
-		\item If Spoiler plays $v_1$ 
-		then Duplicator chooses $v_2$. 
-		\item Otherwise, Spoiler plays a vertex $v$ that belongs
+	If Spoiler plays $v_1$ then Duplicator chooses $v_2$. 
+	Otherwise, Spoiler plays a vertex $v$ that belongs
 	to some $\mathrm{Tr}(T^\prime_1,v_1;\,\, u)$ for a unique $u\in V(e_1)$
@@
 	Set $T^{\prime\prime}_1:=
-		\mathrm{Tr}\big(T^\prime_1,v_1;\,\, u\big)$
+	\mathrm{Tr}\left(T^\prime_1,v_1;\,\, u\right)$
 	and
-		$T^{\prime\prime}_2:=\mathrm{Tr}\big(T^\prime_2,v_2;\,\, f(u)\big)$
-		Then, as $\tau_{(T_1,v_1)}\big(u\big)=\tau_{(T_2,v_2)}\big(f(u)\big)$,
+	$T^{\prime\prime}_2:=\mathrm{Tr}\left(T^\prime_2,v_2;\,\, f(u)\right)$
+	Then, as $\tau_{(T_1,v_1)}\left(u\right)=\tau_{(T_2,v_2)}\left(f(u)\right)$,
 	we obtain
-		$\big(T^{\prime\prime}_1,u\big) \sim_k 
-		\big(T^{\prime \prime}_2,f(u)\big)$.
+	$\left(T^{\prime\prime}_1,u\right) \sim_k 
+	\left(T^{\prime \prime}_2,f(u)\right)$.
 	As both these trees have radii at most $r$, 
@@
 	strategy in
-		$d\ehr_{k}\big(\,T^{\prime\prime}_1, u;
-		\quad T^{\prime \prime}_2, f(u)\,  \big)$		
+	$d\ehr_{k}\left(\,T^{\prime\prime}_1, u;
+	\quad T^{\prime \prime}_2, f(u)\,  \right)$		
 	and they can follow it considering the previous plays in
 	$T^{\prime\prime}_1$ and $T^{\prime\prime}_2$.	
-	\end{itemize}
 \end{proof}
-\noindent\rule{2cm}{0.4pt}
-
-Now we can prove the main theorem of this section:
 
@@
 	If $r=0$ then both $T_1$ and $T_2$ consist
-	of only one vertex and we are done. \par
+	of only one vertex and we are done.
 	Now let $r>0$ and assume that the 
@@
 	$T_1$. The other case is symmetric. 
-	\begin{itemize}[leftmargin=*]
-		\item If Spoiler plays $v_1$ then Duplicator plays $v_2$.
-		\item Otherwise, the vertex played by Spoiler belongs to
+	If Spoiler plays $v_1$ then Duplicator plays $v_2$.
+	Otherwise, the vertex played by Spoiler belongs to
 	$\mathrm{Tr}(T_1,v_1;\,\,e_1)$
@@
 		edge $e_2$ in $T_2$ satisfying 
-			$\big(e_1,\tau_{(T_1,v_1)}\big)\simeq
-			\big(e_2,\tau_{(T_2,v_2)}  \big)$.
+		$\left(e_1,\tau_{(T_1,v_1)}\right)\simeq
+		\left(e_2,\tau_{(T_2,v_2)}  \right)$.
 		Mark $e_2$ as well. 
@@
 		marked during the same round as $e_1$ and it satisfies 
-			$\big(e_1,\tau_{(T_1,v_1)}\big)\simeq
-			\big(e_2,\tau_{(T_2,v_2)}  \big)$.	
+		$\left(e_1,\tau_{(T_1,v_1)}\right)\simeq
+		\left(e_2,\tau_{(T_2,v_2)}  \right)$.	
 		Again, because of \cref{lem:equivalentedges}, 
@@
 	\end{itemize}
-	\end{itemize}
 \end{proof}
@@
 \subsubsection{k-Equivalent hypergraphs} \label{sect:equivunicycles}
-
-\begin{definition}\label{def:TrOperator}
-	Let $H$ be an hypergraph, let $\overline{v}\in V(H)^*$ and 
-	let $v\in H$. We define $\mathrm{Tr}\big(
-	H,\overline{v};\,\, v\big)$ in the following way:
-	\begin{itemize}[leftmargin=*]
-		\item If $d\big(\, Center(H, \overline{v})
-		, \, \, v \big)=\infty$ then $v$ belongs to a connected
-		component $T$ of $H$ which is a tree and does not contain
-		any vertex in $\overline{v}$. In this case
-		$\mathrm{Tr}\big(
-		H,\overline{v};\,\, v\big)$ is the tree $T$ rooted at $v$.
-		\item Otherwise $\mathrm{Tr}\big(
-		H,\overline{v};\,\, v\big)$ is the tree $H[X]$ 
-		induced on the set 
-		\[
-		X:=\big\{\, u\in V(H) \,\, \big| \, 
-		d\big(\, Center(H, \overline{v})
-		, \, \, u \big)= d\big(\, Center(H, \overline{v})
-		, \, \, v \big) + d(v,u)
-		\big\},
-		\]
-		to which we assign $v$ as a root. That is,
-		$\mathrm{Tr}\big(
-		H,\overline{v};\,\, v\big)$ is the tree formed of all 
-		vertices whose only path to $Center(H,\overline{v})$ 
-		contains $v$. 		
-	\end{itemize}
-%	Given $r\in\N$ we define  $\mathrm{Tr}\big(
-%	H,\overline{v};\,\, v;\,\, r\big)$ analogously to $\mathrm{Tr}\big(
-%	H,\overline{v};\,\, v\big)$ in the following way:
-%	\begin{itemize}
-%		\item If $d\big(\, Center(H, \overline{v};\, r)
-%		, \, \, v \big)>r$ then $T:=N(v;r)$ is a tree
-%		and	$\mathrm{Tr}\big(
-%		H,\overline{v};\,\, v;\,\, r\big)$ is the tree $T$ rooted at $v$.
-%		\item Otherwise $\mathrm{Tr}\big(
-%		H,\overline{v};\,\, v\big)$ is the tree $H[X]$ 
-%		induced on the set 
-%		\begin{align*}
-%		X:=\Big\{\, u\in V(H) \,\, \Big| \, \,
-%		d\big(\, Center(H, \overline{v};\, r)
-%		, \, \, u \big)= d\big(\, Center(H, \overline{v};\, r)
-%		, \, \, v \big) + d(v,u),&\\  \text{ and } d(v,u)\leq r
-%		\Big\},&
-%		\end{align*}
-%		to which we assign $v$ as a root. That is,
-%		$\mathrm{Tr}\big(
-%		H,\overline{v};\,\, v;\,\, r\big)$ is the tree formed of all 
-%		vertices $u$ whose distance to $v$ is at most $r$ and 
-%		whose only path to $Center(H,\overline{v};\, r)$ contains $v$. 
-%	\end{itemize}
-	In the case that $\overline{v}$ is the empty list we will write
-	simply $\mathrm{Tr}(H;\,\, v)$ 
-%	or $\mathrm{Tr}(H;\,\, v;\,\,r)$ 
-	instead of 
-	$\mathrm{Tr}(H,\, \, ;\,\, v)$.
-%	 or $\mathrm{Tr}(H,\,\,;\,\, v;\,\,r)$.
-	Notice that in the case that
-	$(T,u)$ is a rooted tree then the definition of 
-	$\mathrm{Tr}(T,u;\, \, v)$ given in \cref{sect:equivtrees}
-	coincides with the one we have
-	given now,
-	so no confusion should arise. \par
-\end{definition}
-
-Let $H$ be a non-tree connected hypergraph. We define
-the \textbf{canonical coloring} $\tau_{H}$ over $H$
-as the one that assigns to each vertex $v\in V(H)$ the $\sim_k$ class of the tree
-$\Tr(H,v)$.\par
-
-\begin{definition}
-	Let $H_1$ and $H_2$ be connected hypergraphs which are not trees.
-	Set $H^\prime_1:= Center(H_1)$ and $H^\prime_2:= Center(H_2)$.
-	We say that $H_1$ and $H_2$ are $k$-equivalent,
-	written as $H_1\sim_k H_2$, if
-	$\big( H^\prime_1,\tau_{H_1}\big) \simeq 
-	\big(H^\prime_2,\tau_{H_2}\big)$
-\end{definition}
-
-The main theorem of this section is the following
 
@@
 		$H^\prime_2:= Center(H_2)$. Let $f$ be an isomorphism
-		between $\big( H^\prime_1,\tau_{H_1}\big)$ and 
-		$\big(H^\prime_2,\tau_{H_2}\big)$. Let $\overline{v}$ 
+		between $\left( H^\prime_1,\tau_{H_1}\right)$ and 
+		$\left(H^\prime_2,\tau_{H_2}\right)$. Let $\overline{v}$ 
 		be an ordering of the vertices of $H^\prime_1$ and let
@@
 		Duplicator wins 
-		$	d\ehr_{k}\big(\,
+		$	d\ehr_{k}\left(\,
 		H^\prime_1,\overline{v};\,\,
 		H^\prime_2,\overline{u}\,
-		\big).
+		\right).
 		$
@@
 		$u\in H^\prime_1$. 
-		Set $T_1:=\mathrm{Tr}\big(H_1;\,\,u\big)$ and
-		$T_2:=\mathrm{Tr}\big(H_2;\,\,f(u)\big)$.
+		Set $T_1:=\mathrm{Tr}\left(H_1;\,\,u\right)$ and
+		$T_2:=\mathrm{Tr}\left(H_2;\,\,f(u)\right)$.
 		By hypothesis
@@
 		$
-		d\ehr_{k}\big(\,
-		T_1,u; \, \, T_2, f(u)\,\big),
+		d\ehr_{k}\left(\,
+		T_1,u; \, \, T_2, f(u)\,\right),
 		$
@@
 \subsection{$r$-Cores} \label{sec:Core}
-
-Let $H$ be an hypergraph. Let $X$ be the set of vertices $v\in V(H)$
-that belong to any saturated sub-hypergraph of $H$
-whose diameter is at most $2r+1$. 
-We define the \textbf{$r$-core} of $H$, 
-written as $Core(H;r)$ as $N(X;r)$. Given 
-$\overline{v}\in V(G)^*$, we define $Core(H,\overline{v};r)$
-as $N(Y;r)$, where $Y$ is the set of vertices $v\in V(H)$ that either
-belong to $\overline{v}$ or belong to any saturated sub-hypergraph of $H$
-whose diameter is at most $2r+1$.
-We say that $H$ is $r$-\textbf{simple} if all connected components
-of $Core(H;r)$ are unicycles.
-
-\begin{definition} \label{def:agreeability}
-	Let $H_1$ and $H_2$ be hypergraphs and let $r\in \N$.
-	Let $H^\prime_1:=Core(H_1;r)$ and $H^\prime_2:=Core(H_2;r)$. 
-	We say that $H_1$ and $H_2$ are $(k,r)$-agreeable, written
-	as $H_1\approx_{k,r} H_2$ if for any $\sim_k$ class $\mathcal{H}$ 
-	``the number of connected
-	components in $H^\prime_1$ that belong to $\mathcal{H}$" and
-	``the number of connected components in $H^\prime_2$ that belong to 
-	$\mathcal{H}$" are the same or are both greater than $k-1$.\par
-%	 satisfies that
-%	``the number of connected components $H^{\prime\prime}_1$
-%	from $H^\prime_1$ such that $ H^{\prime\prime}_1 \sim_k F\, \, \,$'' 
-%	and ``the number of
-%	connected components $H^{\prime \prime}_2$ of $H^\prime_2$
-%	such that
-%	$ H^{\prime\prime}_2\sim_k F\, \, \,$" 
-%	are both equal or are both greater 
-%	or equal than $k$. Then we say that $H_1$ and $H_2$
-%	are $(k,r)$-\textbf{agreeable}, written as $H_1\approx_{k,r} H_2$. \par
-
-\end{definition}
-
-\begin{definition}
-	Let $\Sigma_{(k,r-1)}$ be the set of $\sim_k$ classes
-	of rooted trees with radii at most $r-1$. Then
-	we call a $(k,r)$-\textbf{cycle} to an isomorphism class
-	of $\Sigma_{(k,r-1)}$-hypergraphs 
-	$(H,\tau)$ that are cycles of diameter at most $2r+1$.
-	We will denote by $C(k,r)$ the set of $(k,r)$-cycles.
-\end{definition}
-
-The following is a way of characterizing $\approx_{k,r}$ classes
-of $r$-simple hypergraphs.
-
-\begin{obs}\label{obs:agreeablecores}
-	Let $\mathcal{O}$ be a $\approx_{k,r}$ class
-	of $r$-simple hypergraphs. 
-	Then there is a partition $U^1_\mathcal{O},
-	U^2_\mathcal{O}$ of $C(k,r)$ and natural numbers $a_\omega<k$
-	for each $\omega\in U^2_\mathcal{O}$ that only depend on 
-	$\mathcal{O}$ such that any $r$-simple hypergraph $G$ belongs to
-	$\mathcal{O}$ if and only if it holds that (1) for any $\omega\in U^1_\mathcal{O}$ 
-	there are at least $k$ connected components $H \subset Core(G;r)$ whose cycle 		
-	$H^\prime=Center(H)$ satisfies that	$(H^{\prime},\tau_{H})\in \omega$, and
-	(2) for any $\omega\in U^2_\mathcal{O}$ there are exactly $a_\omega$ 
-	connected components $H \subset Core(G;r)$ whose cycle 
-	$H^\prime=Center(H)$ satisfies that	$(H^{\prime},\tau_{H})\in \omega$.	
-\end{obs}
 
@@
 \end{proof}
-\sep
-\begin{definition} \label{def:rich}
-	Let $H$ be an hypergraph and let $r\in\N$. Let
-	$X\subset V(H)$ be the set of vertices in $H$
-	belonging to some saturated sub-hypergraph of diameter
-	at most $2r+1$.	We say that $H$ is $(k,r)$-\textbf{rich}
-	if for any $r^\prime\leq r$, any vertices $v_1,\dots, v_k$ 
-	and any $\sim_k$ class $\mathcal{T}$ of trees with radius
-	at most $r^\prime$ it holds that there exists a vertex $v\in V(H)$
-	such that $d(v,X)> 2r^\prime+1$, $d(v,v_i)>2r^\prime+1$ for all
-	$v_i$'s and that $T:=N(v;r^\prime)$ is a tree such that
-	$(T,v)\in \mathcal{T}$ (notice that $T$ is a tree necessarily. 
-	Otherwise $T$ contains a saturated sub-hypergraph with diameter 
-	lesser or equal than $2r^\prime+1$).	
-\end{definition}
+%\sep
 
@@
 
-We say that a connected hypergraph $G$ is \textbf{dense} if
-$ex(G)>0$. Given $r\in \N$, we say that $G$ is \textbf{$r$-sparse}
-if $G$ does not contain any dense subgraph $H$ such that 
-$diam(H)\leq r$. The goal of this section is to show that, for any
-fixed $r$, a.a.s $G_n$ is $r$-sparse.\par
-
 \begin{lemma}
-	Let $H$ be an hypergraph. Then 
-	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]\sim
-	C\cdot(n^{-ex(H)})$ for some constant $C\in \R$ as $n$ tends to infinity.  
+	Let $H$ be an hypergraph, and let $X_n$ be the 
+	random variable that counts the copies of $H$ in 
+	$G_n$. Then 
+	$\mathrm{E}\big[X_n\big]=\Theta(n^{-ex(H)})$.  
 \end{lemma}
@@
 \[
- \mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
+ \mathrm{E}\big[X_n\big]=
  \sum_{H^\prime \in Copies(H,[n])} \PR{H^\prime \subset G_n}.
 \]	
-We have that $|Copies(H,[n])|=\frac{(n)_{v(H)}}{\aut(H)}$. Also, 
+We have that $\Big|Copies(H,[n])\Big|=\frac{(n)_{|H|}}{\aut(H)}$. Also, 
 for any $H^\prime \in Copies(H,[n])$ it is satisfied
@@
 \[
-\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
-\frac{(n)_{v(H)}}{\aut(H)}\cdot
+\mathrm{E}\big[X_n\big]=
+\frac{(n)_{|H|}}{\aut(H)}\cdot
 \prod_{R\in \sigma} \left(\frac{\beta_R}{n^{ar(R)-1}}\right)^{|E_R(H)|}
@@
 \]	
-
-%Given any one-to-one map $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be 
-%the indicator variable
-%that takes value one when $f$ defines an monomorphism 
-%between $H$ and $G_n$ and zero otherwise. 
-%The probability that $X^H_{n,f}=1$ is exactly
-%$\prod_{i=1}^t \left(\frac{\beta_i}{n^{a_i-1}}\right)^{e_i(H)}$ which can
-%be written as $C\cdot n^{-ex(H)-v(H)}$ for some constant
-%$C$ that does not depend on $f$ nor $n$. Define 
-%$X^H_n=\sum_{f\in [n]_{V(H)}} X^H_{n,f}$. Then, by definition, the number of 
-%copies of $H$ in $G_n$ is exactly $X^H_n/\aut(H)$.
-%Taking into account that 
-%\[
-%\mathrm{E}[X^H_n]=(n)_{v(H)} \cdot C\cdot n^{-\sum_{i=1}^t (a_i-1)\cdot e_i(H)}= \Theta(n^{-ex(H)}),
-%\]
-%the result follows. 
-%Indeed, let $n\in \N$ and let $G_n$ be a random hypergraph sampled from
-% $\mathrm{G}^\mathcal{C}(n,\overline{p})$. Let
-% $\overline{h}$ be an ordering of the vertices
-%in $V(H)$. For any list 
-% $\overline{v}\in [n]_{|V(H)|}$ (recall that $[n]=V(G)$), 
-%let $X_{\overline{v}}$ be the random indicator variable
-%that takes value $1$ if the natural map 
-% $f:\overline{h}\rightarrow \overline{v}$ defines an homomorphism 
-%between $H$ and $G$. That is, $X_{\overline{v}}$ takes value $1$
-%with probability
-% $ \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|},
-% $
-%and zero otherwise. The sum of all $X_{\overline{v}}$'s for 
-%all $\overline{v}\in [n]_{|V(H)|}$ counts how many labelled 
-%copies of $H$ are in $G_n$. Thus, 
-%\[ \mathrm{E}\big[\# \text{labelled copies of }H \text{ in } G_n\big] 
-%= \sum_{\overline{v}\in [n]_{|V(G)|}} 
-%\prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
-%= (n)_{|V(H)|} \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}.
-%\]
-%The expected number of copies of $H$ in $G_n$ is then this last
-%expectation divided by the number of automorphisms of $H$, $\aut(H)$.
-%In consequence,
-%\begin{align*}
-% &\Ln \mathrm{E}\big[\# \text{copies of }H \text{ in } G_n\big] 
-%=\Ln \frac{(n)_{|V(H)|}}{\aut(H)} \prod_{i=1}^{t} 
-%\big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
-%=\\ &\Ln \Big[(n)_{|V(H)|}\prod_{i=1}^{t}n^{(1-a_i)|E_i(H)|}\Big]
-%\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{\aut(H)} \simeq \Ln
-%n^{-ex(H)}\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{\aut(H)},
-%\end{align*}
-%and last expression belongs to $\theta(n^{-ex(H)})$, as desired.\par
 \end{proof}
-\sep
-
-As a corollary of last result we get the following:  
+%\sep
+
 \begin{lemma} \label{lem:nocopiesdense}
@@
 \begin{proof}
-	Because of the previous fact, 
+	Because of the previous lemma
 	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big] 
@@
 \end{proof}
-\sep
-
-A similar result that will be useful later is the following:
-
-%\subsubsection{Rooted hypergraphs}
-%
-%A rooted hypergraph $(G,\overline{u})$ is an hypergraph $H$ together with 
-%an ordered sequence of distinguished vertices $\overline{u}\in (V(H))_*$.
-%An isomorphism between two rooted hypergraphs $(G,\overline{u})$ and
-%$(H,\overline{v})$ is a map $f: V(G)\rightarrow V(H)$ such that $f$
-%is an isomorphism between $G$ and $H$ that satisfies the additional condition
-%$f(\overline{u})=\overline{v}$. An automorphism of $(G,\overline{u})$  is 
-%an isomorphism from $(G,\overline{u})$  to itself. 
-%We write $Aut(G,\overline{u})$ to denote the group
-%of automorphisms of $(G,\overline{u})$. \par
-%
-%Given a rooted hypergraph $(G,\overline{u})$, a set of vertices
-%$V$ and a list $\overline{v}\in (V)_*$ such that $len(\overline{u})
-%= len(\overline{v})$ we define the set $Copies((G,\overline{u}),
-%(V,\overline{v}))$ as the set of rooted hypergraphs 
-%$(H,\overline{v})$ isomorphic to $(G,\overline{u})$ such that
-%$V(H)\subset V$. \par
 
@@
 	in $\overline{v}$. Then
-	\[
-	\mathrm{E}\big[ X_n \big]=\Theta(n^{-ex(H)-len(\overline{v})}).\]
-	In particular, given any fixed $r\in \N$,
-	a.a.s the vertices $v\in \overline{v}$ satisfy that
-	the $N(v;r)$'s are disjoint trees.	
+	$
+	\mathrm{E}\big[ X_n \big]=\Theta(n^{-ex(H)-len(\overline{v})})$.
 \end{lemma}
@@
 	that contain all vertices in $\overline{v}$ is
-	 $\Theta\big(n^{|V(H)|-len(\overline{v})}\big)$. Then for
+	 $\Theta\left(n^{|V(H)|-len(\overline{v})}\right)$. Then for
 	 some constant $C$,
@@
 	\mathrm{E}\big[ X_n \big]\sim 
-	C n^{|V(H)|-len(\overline{v})}
+	C \cdot n^{|V(H)|-len(\overline{v})}
 	\cdot\prod_{R\in\tau} \left( \frac{\beta_R}{n^{ar(R)-1}}\right)^{e_R(H)}=
@@
 \end{proof}
-\sep
-
-%
-%\begin{lemma}
-%	Let $\overline{v}:=(v_1,\dots,v_j)\in \N*$.
-%	Let $H$ be an hypergraph such that $ex(H)>-j$. 
-%	Then a.a.s there is no copy of $H$ in $G_n$ that
-%	contains all $v_1,\dots,v_j$. 
-%\end{lemma} 
-%\begin{proof}
-%It is sufficient to show that
-%\begin{equation}\label{eqn:aux}
-%\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
-%\overline{v} \big]\xrightarrow[]{n\to \infty} 0.
-%\end{equation}
-%Then, because of a first moment argument the result follows.\par
-%Suppose $v(H)\geq j$. Otherwise the statement is trivial. 
-%As before, given any $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be the random
-%variable that takes value one if $f$ is a monomorphism from $H$ to $G_n$
-%and zero otherwise. The probability that $X^H_{n,f}$ takes value one is
-%$C\cdot n^{-ex(H)-v(H)}$ for some constant $C$ independent from $f$ and $n$. 
-%Let 
-%\[ Y^H_{n,\overline{x}}= \sum_{\substack{f\in [n]_{V(H)}\\ 
-%\overline{x}\subset Im(f)}} X^H_{n,f}.\]
-%The number of functions $f\in [n]_{V(H)}$ such that $v_1,\dots,v_j\in Im(f)$
-%is $\Theta(n^{v(H)-j})$. In consequence 
-%$
-%\mathrm{E}\big[Y^H_{n,\overline{v}}\big]=\Theta(n^{-ex(H)-j})
-%$, and 
-%\[\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
-%\overline{v} \big]=\Theta(n^{-ex(H)-j}).
-%\]
-%This, together with $ex(H)>-j$, proves \cref{eqn:aux}. 
-%\end{proof}
-
-The main theorem of this section is the following
-\begin{theorem} \label{thm:sparse}
-	Let $r\in \N$. Then a.a.s $G_n$ is $r$-sparse. 
-\end{theorem}
-
-	The first moment method alone is not sufficient
-	to prove our claim because the amount of dense 
-	hypergraphs	$H$ such that $diam(H)\leq r$ is not finite
-	in general. Thus, we need to prove that it suffices to
-	prohibit a finite amount of dense sub-hypergraphs in order
-	to guarantee that $G_n$ is $r$-sparse.\par
+
 	Given an hypergraph $H$ and an edge $e\in E(H)$ we
@@
 	$ex(H)<ex(H^\prime)$ and that 
-	$|E(H^\prime)|\leq |E(H)|+2\cdot(r) + 1$, 
+	$|E(H^\prime)|\leq |E(H)|+2\cdot r + 1$, 
 \end{lemma}
@@
 	Then $H^\prime:=H\cup P \cup e$ satisfies the conditions of 
-	the statement. \par
-	Otherwise, all edges $e\in E(G)\setminus E(H)$ 
+	the statement. Otherwise, all edges $e\in E(G)\setminus E(H)$ 
 	satisfy $ex(e)=-1$. In this case we successively cut
@@
 \end{proof}
-\sep
+%\sep
 \begin{lemma}
@@
 \end{proof}
-\sep
+%\sep
 
@@
 diameter is at most $r$ then $G$ contains a dense sub-hypergraph
-$H$ with $|V(H)|\leq l\cdot (4r+2)$.\par
-
-Now we are in conditions to prove \cref{thm:sparse}.
-
+$H$ with $|H|\leq l\cdot (4r+2)$.\par
+
+\begin{theorem} \label{thm:sparse}
+	Let $r\in \N$. Then a.a.s $G_n$ is $r$-sparse. 
+\end{theorem}
 \begin{proof}
@@
 	that ``$G$ is $r$-sparse". Thus,
-	\[ \Ln \mathrm{Pr}\big( G_n \text{ is } r \text{-sparse}  \big)
-	\geq \Ln \mathrm{Pr} \big( G_n \text{ does not contain dense 
-	hypergraphs of size bounded by } R\big).\] 
+	\[ \Ln \mathrm{Pr}\left( G_n \text{ is } r \text{-sparse}  \right)
+	\geq \Ln \mathrm{Pr} \left( G_n \text{ does not contain dense 
+	hypergraphs of size bounded by } R\right).\] 
 	Because of	\cref{lem:nocopiesdense}, given any individual dense hypergraph,
@@
 \end{proof}
-\sep
-\begin{corollary}\label{cor:simple}
+%\sep
+As a corollary we obtain the needed result. 
+\begin{theorem}\label{cor:simple}
 	Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple.
-\end{corollary}
+\end{theorem}
 \begin{proof}
@@
 	$N(v;r)$'s are all trees and they are all disjoint.
-\end{lemma}
+
 	\begin{proof}
@@
 		\cref{lem:nocopiesfixed} and the fact that there are a finite number
-	of $\sim$ classes of paths whose length is at most $2r+1$ implies that
-	a.a.s the $N(v;r)$'s are disjoint. \par
+		of $\simeq$ classes of paths whose length is at most $2r+1$ implies that
+		a.a.s the $N(v;r)$'s are disjoint. 
 		Also, because of \cref{thm:sparse} a.a.s the $N(v;r)$'s are either 
@@
 		with a cycle $C$ of diameter at most $2r+1$. Using \cref{lem:nocopiesfixed}
-	again as well as the fact that the number of $\sim$ classes of the possible hypergraphs
-	$P\cup C$ is finite we obtain that a.a.s no such $P$ and $C$ exist. 
-	In consequence all the $N(v;r)$'s are disjoint trees as we wanted to prove. \par
+		again as well as the fact that there are a finite number of possible $\simeq$
+		classes for
+		$P\cup C$ we obtain that a.a.s no such $P$ and $C$ exist. 
+		In consequence all the $N(v;r)$'s are disjoint trees as we wanted to
+		prove. \end{proof}
+\end{lemma}
+
+\begin{lemma}\label{lem:far_away}
+	Let $\overline{v} \subset \N*$ be a finite set of fixed vertices and let 
+	$\pi(\overline{x})$ be an edge sentence such that
+	$len(\overline{x})=len(\overline{v})$. 
+	Define $G_n^\prime=G_n \setminus E[\overline{v}]$ (i.e. $G_n$ minus all the
+	edges induced over $\overline{v}$). Fix $R\in \N$. 
+	Let $A_n$ be the event that $G^\prime_n$ contains a path of 
+	length	at most	$R$ between any two vertices $u,w\in \overline{v}$.
+	Let $B_n$ be the event
+	that $G^\prime_n$ contains a cycle of diameter at most $R$
+	at distance at most $R$ to some vertex $u\in \overline{v}$.
+	Then 
+	\[
+	\Ln \mathrm{Pr}\left(A_n \, | \, \pi(\overline{v})\right)=0, \quad 
+	\text{ and } 
+	\Ln \mathrm{Pr}\left(B_n \, | \, \pi(\overline{v})\right)=0.\] 
+\end{lemma}
+\begin{proof}
+	Notice that the events $A_n$ and $B_n$ do not concern the possible edges
+	induced over $\overline{v}$. In consequence, because edges are independent
+	in our random model, 
+	$\mathrm{Pr}\left(A_n \, | \, \pi(\overline{v})\right)
+	=\mathrm{Pr}(A_n)$ and 
+	$\mathrm{Pr}\left(B_n \, | \, \pi(\overline{v})\right)
+	=\mathrm{Pr}(B_n)$. Now
+	both limits from the statement follow from 
+	\cref{lem:disjointtrees} using that $G^\prime_n\subset G_n$.  
 \end{proof}
@@
 Our main tool for computing probabilities in the following sections
-will be the following multivariate version of Brun's Sieve 
-(Theorem 1.23, \cite{bollobas2001random}).
+will be the next result, which can
+be found in \cite[Theorem 1.23]{bollobas2001random}.
 
@@
 
-To make use of last theorem we will need to employ the following observation.
+We will use the following observation in order to compute the binomial moments of 
+our random variables.
 
@@
 	\prod_{i=1}^{l} \binom{X_i}{r_i}\right]=
-	\sum_{\{S_i\}_{i\in [l]}} \Pr\left(
+	\sum_{\{S_i\}_{i\in [l]}} \mathrm{Pr}\left(
 	\bigwedge_{\substack{i\in [l]\\ j\in S_i}} Y_{i,j}=1
@@
 \subsection{Probabilities of trees}
-
-During this section we want to study
-the asymptotic probability that the 
-$r$-neighborhood of a given vertex $v\in \N$
-in $G_n$ 
-is a tree that belongs to a given $k$-equivalence
-class of trees $\mathcal{T}$ with radius at most
-$r$. That is, we want to know
-\[\Ln \mathrm{Pr}\big( 
-T:=N^{G_n}(v;r) \text{ is a tree, and } (T,v)\in \mathcal{T} \big). 
-\]
-
-Denote this limit by $\mathrm{Pr}[r,\mathcal{T}]$. Notice that the 
-definition of  $\mathrm{Pr}[r,\mathcal{T}]$ does not depend by the
-choice of $v$.\par
 
@@
 
-The goal of this section is to show 
-that $\mathrm{Pr}[r,\mathcal{T}]$,
-as an expression with parameters
-$\{\beta_R\}_{R\in\sigma}$, belongs to $\Lambda$ for any choice of 
-$r$ and $\mathcal{T}$. \par
-
-Before we proceed it will be useful to define the following abbreviation
-\begin{definition} Let $H$ be an hypergraph, $\overline{v}\in V(H)^*$, $v\in V(H)$ and
-	$r\in \N$. Then we define $\mathrm{Tr}(H,\overline{v};\, v;\, r)$ as
-	\[
-	\mathrm{Tr}\Big( Core(H,\overline{v};\,\,r),\overline{v}; \,\, v     \Big).
+\begin{definition}
+	Let $r\in \N$ and let $\mathbf{T}$ be a $\sim_k$ class
+	of trees with radius at most $r$. Let $v\in \N$ be an arbitrary 
+	vertex. We define $\mathrm{Pr}[r,\mathbf{T}]$ as the limit
+	\[
+	\Ln \mathrm{Pr}\left(
+	Tr(G_n,\,v;\,v;\,r)\in \mathbf{T}\right).
 	\]
@@
 
-\begin{lemma}\label{lem:far_away}
-	Let $\overline{v} \subset \N*$ be a finite set of fixed vertices and let 
-	$\pi(\overline{x})$ be an edge sentence such that
-	$len(\overline{x})=len(\overline{v})$. 
-	Define $G_n^\prime=G_n \setminus E[\overline{v}]$ (i.e. $G_n$ minus all the
-	edges induced over $\overline{v}$). Fix $R\in \N$. 
-	\begin{itemize}
-		\item Let $A_n$ be the event that $G^\prime_n$ contains a path of 
-		length	at most	$R$ between any two vertices $u,w\in \overline{v}$.
-		\item Let $B_n$ be the event
-		that $G^\prime_n$ contains a cycle of diameter at most $R$
-		at distance at most $R$ to some vertex $u\in \overline{v}$.
-	\end{itemize}
-	Then $\Ln \mathrm{Pr}\big(A_n \, | \, \pi(\overline{v})\big)=0$, and 
-	$\Ln \mathrm{Pr}\big(B_n \, | \, \pi(\overline{v})\big)=0$. 
-\end{lemma}
-\begin{proof}
-	Notice that the events $A_n$ and $B_n$ do not concern the possible edges
-	induced over $\overline{v}$. In consequence, because edges are independent
-	in our random model, 
-	$\mathrm{Pr}\big(A_n \, | \, \pi(\overline{v})\big)
-	=\mathrm{Pr}(A_n)$ and 
-	$\mathrm{Pr}\big(B_n \, | \, \pi(\overline{v})\big)
-	=\mathrm{Pr}(B_n)$.\par
-	Now both $\Ln \Pr(A_n)=0$ and $\Ln Pr(B_n)=0$ follow from 
-	\cref{lem:disjointtrees} using that $G^\prime_n\subset G_n$.  
-\end{proof}
-
-\sep
-%\begin{corollary}\label{cor:disjointtrees}
-%	Let $\overline{v}\in (\N)_*$ be a finite set of vertices 
-%	and let $\pi(\overline{x})$ be an edge sentence such that
-%	$len(\overline{v})=len(\overline{x})$. 
-%	Define $G_n^\prime=G_n \setminus E[\overline{v}]$. 
-%	Fix $r\in \N$.
-%	Let $U_n$ be the event that for all $v\in \overline{v}$
-%	the neighborhoods $N^{G^\prime_n}(v;r)$ are disjoint trees.
-%	Then
-%	\[
-%	\Ln \PR{U_n \, \big| \, \pi(\overline{v})}=1.\]
-%	As a consequence, for all $v\in \overline{v}$,
-%	\[
-%	\Pr\Big(Tr\big(G_n,\overline{v};\, v;\, r)=N^{G^\prime_n}(v;r)\, 
-%	\Big| \, \pi(\overline{v}) \Big)=1.
-%	\]
-%\end{corollary}
-%\begin{proof}
-%	As in the previous lemma, because edges are independent 
-%	in our random model, \[
-%	\PR{U_n \, \big| \, \pi(\overline{v})}
-%	=\PR{U_n}\]
-%	 for all $n$. Because of the previous lemma
-%	a.a.s there is no path in $G^\prime_n$ of length at most $2r+1$ joining 
-%	any two vertices in $\overline{v}$. In consequence a.a.s
-%	the $N^{G^\prime_n}(v;r)$'s are disjoint.\par
-%	Also, because of \cref{thm:sparse} a.a.s there are no dense
-%	hypergraphs with diameter at most $r$ in $G_n$, 
-%	so a.a.s the  $N^{G^\prime_n}(v;r)$'s are not dense.\par
-%	Finally, because of the previous lemma, a.a.s 
-%	none of the vertices in $\overbar{v}$ is at a distance
-%	lesser than $r$ to a cycle of diameter at most $r$.
-%	In consequence a.a.s all the $N^{G^\prime_n}(v;r)$'s are trees, 
-%	as we wanted to prove. 	 \par
-%	The fact that for all $v\in \overline{v}$ a.a.s
-%	$
-%	Tr\big(G_n,\overline{v};\, v;\, r)=N^{G^\prime_n}(v;r)
-%	$
-%	is deduced from the fact that if some 
-%	$u\in V\Big(N^{G^\prime_n}(v;r) \Big)$ does not belong
-%	to $Tr\big(G_n,\overline{v};\, v;\, r)$, then 
-%	either (a) $u$ belongs to a path in $G_n^\prime$
-%	of length at most $2r+1$ 
-%	between $v$ and another vertex $w\in \overline{v}$, 
-%	(b) $u$ belongs to a cycle in $G^\prime_n$ of diameter
-%	at most $2r+1$ which contains $v$, or
-%	(c) $u$ belongs to a path in $G_n^\prime$
-%	of length at most $2r+1$ between $v$ and some cycle
-%	in $G_n^\prime$ of diameter at most $2r+1$. But as the
-%	$N^{G^\prime_n}(v;r)$'s a.a.s are disjoint trees none of 
-%	(a),(b),(c) hold with positive probability. 
-%\end{proof}
-%
-%
-%\sep
+Notice that the 
+definition of  $\mathrm{Pr}[r,\mathbf{T}]$ does not depend on the
+choice of $v$. The goal of this section is to show 
+that $\mathrm{Pr}[r,\mathbf{T}]$ exists and is
+an expression with parameters
+$\{\beta_R\}_{R\in\sigma}$, belongs to $\Lambda$ 
+for any choice of $r$ and $\mathbf{T}$. \par
 
@@
 	\begin{itemize}
-		\item[(1)] Let $\mathcal{T}$ be a
-		$k$-equivalence class for trees with radii at most $r$. Let
-		$v\in \N$ be a vertex.	Then 
-		\[
-		\mathrm{Pr}[r,\mathcal{T}]:=\Ln  \PR{Tr\big(G_n,v;\,\,v;\,\,r\big)\in \mathcal{T}}
-		\]
+		\item[(1)] Let $\mathbf{T}$ be a
+		$k$-equivalence class for trees with radii at most $r$.	Then 
+		$
+		\mathrm{Pr}[r,\mathbf{T}]
+		$
 		exists,
 		is positive for all choices of 
-		$\{\beta_R\}_{R\in \epsilon}\in [0,\infty)^{|\sigma|}$,
+		$\{\beta_R\}_{R\in \epsilon}\in (0,\infty)^{|\sigma|}$,
 		and is an expression
-		in $\Lambda$ that depends only on the choice of $r$ and $\mathcal{T}$.
-		\item[(2)] Let $\overline{u}\in (\N)_*$ be a list of different fixed 
-		vertices, and let $\pi(\overline{x})\in FO[\sigma]$ be a consistent
+		in $\Lambda$.
+		\item[(2)] Let $\overline{u}\in (\N)_*$,
+		and let $\pi(\overline{x})\in FO[\sigma]$ be a consistent
 		edge sentence such that 
@@
 		in $\overline{u}$. For each $v\in \overline{v}$
-		let $\mathcal{T}_v$ be a $k$-equivalence class
+		let $\mathbf{T}_v$ be a $k$-equivalence class
 		of trees with radii	at most $r$. Then
 		\[
-		\Ln \mathrm{Pr}\big( \bigwedge_{v\in \overline{v}} 
-		Tr\big(G_n, \overline{u};\,\,v;\,\,r\big)\in \mathcal{T}_v 
+		\Ln \mathrm{Pr}\left( \bigwedge_{v\in \overline{v}} 
+		Tr\left(G_n, \overline{u};\,\,v;\,\,r\right)\in \mathbf{T}_v 
 		\, | \, \pi(\overline{u})
-		\big)= \prod_{v\in \overline{v}} \mathrm{Pr}[r,\mathcal{T}_v]. \]	 	
+		\right)= \prod_{v\in \overline{v}} \mathrm{Pr}[r,\mathbf{T}_v]. \]	 	
 	\end{itemize}
@@
 theorem. The proof will be done by induction on $r$. 
+Recall that	all trees with radius zero are $k$-equivalent. Thus,
+the limits appearing in conditions (1) and (2) are both equal to $1$
+in the case $r=0$. In consequence we obtain the following.
 
@@
 \end{lemma}
-\begin{proof}
-	Recall that	all trees with radius zero are $k$-equivalent. Thus,
-	the limits
-	appearing in conditions (1) and (2) are both equal to $1$.
-\end{proof}
-\sep
-
-Now, for the induction step we have to prove that 
-conditions (1) and (2) of \cref{thm:BigTrees} hold
-for any $r>0$, given that they hold for all
-$r^\prime < r$. Notice that (1) is, in fact, a particular
-case of (2). Proving only (2) would be the ``mathematically"
-reasonable way to proceed, but the proof of (2) does not contain
-any new ideas that do not appear in the proof of (1) and is, in turn,
-more convoluted notation-wise. In consequence we will offer the complete 
-proof of (1) and later give indications about what changes in the proof
-are necessary in order to show (2).
-
-	\begin{lemma} \label{lem:singletreeprob}
-	Let $r\in \N$, $r>0$. Let $\mathcal{T}$ be a 
-	$\sim_k$ class of trees with radii at most $r$ and 
-	let $v\in \N$ be any vertex. 
-	Suppose \cref{thm:BigTrees} holds
-	for $r-1$. Then \[
-	\Pr\big[r, \mathcal{T}\big]:=
-	\Ln  \PR{Tr\big(G_n,v;\,\,v;\,\,r\big)\in \mathcal{T}}
-	\] 
-	exists, is positive for all choices of 
-	$\{\beta_R\}_{R\in \epsilon}\in [0,\infty)^{|\sigma|}$,
-	and is and expression in $\Lambda$ that depends
-	only on the choice of $r$ and $\mathcal{T}$.   
-	\end{lemma}
-	\begin{proof}
-		For any $(k,r)$-pattern  $\epsilon$  let 
-		$X_{n,\epsilon}$ be the random variable that counts
-		the initial edges $e\in E(T_n)$ whose pattern
-		is $\epsilon$ (i.e. $(e,\tau_{(T_n,v)})\in \epsilon$). 
-		Fix a pattern $\epsilon\in P(k,r)$.
-		we define the expressions $\lambda_{r,\epsilon}$ and
-		 $\mu_{r,\epsilon}$ 
-		as follows: let $(e,\tau)$ be a representative of $\epsilon$
-		whose root is $v$. Then
-		\[
-		\lambda_{r,\epsilon}=\prod_{\substack{u\in V(e)\\ u\neq v} } \Pr\big[
+
+\begin{definition}
+	Let $r\in \N$ be a positive number and
+	suppose that \cref{thm:BigTrees} holds for $r-1$.
+	Given a $(k,r)$-pattern $\epsilon$ we define the expressions
+	$\lambda_{r,\epsilon}$ and $\mu_{r,\epsilon}$ in the following way.
+	Let $(e,\tau)$ be a representative of $\epsilon$
+	whose root is $v$. Then for all vertices $u\in V(e)$ such that
+	$u\neq v$ it holds that $\tau(u)$ is a $\sim_k$ class of trees with
+	radius at most $r$ and we can set  
+	\[
+	\lambda_{r,\epsilon}:=\prod_{\substack{u\in V(e)\\ u\neq v} } \mathrm{Pr}\big[
 	r-1, \tau(u)\big], \quad \text{ and } \quad
@@
 	\]
-		Clearly the definitions of $\lambda_{r,\epsilon}$ and $\mu_{r,\epsilon}$
-		are independent from the representative $(e,\tau)$ and by hypothesis
-		depend only on the choice of $r$ and $\epsilon$. By hypothesis it also holds
+\end{definition}	
+Clearly the definitions of $\lambda_{r,\epsilon}$ and
+$\mu_{r,\epsilon}$ are independent of the chosen representative.
+By hypothesis it holds
 that $\mu_{r,\epsilon}$ is positive for all values of
-		$\{ \beta_R \}_{R\in \sigma}\in [0,\infty)^{|\sigma|}$.
-		 Furthermore, 
-		$\mu_{r,\epsilon}$ belongs to $M$.\par
-		First we are going to show that for any
-		$(k,r)$-pattern $\epsilon$ it holds that
-	 	\[
-	 	\Ln E[X_{n,\epsilon}] = \mu_{r,\epsilon}.
-	 	\]
-	 	This step is not necessary for the proof as a whole but serves as a 
-	 	simple example that showcases the methods used.		
-		\par
-		Fix a $(k,r)$-pattern $\epsilon$. 
-		By definition $X_{n,\epsilon}$ counts
-		the colored edges $(e,\tau)\in Copies(\epsilon,[n],v)$ 
-		such that $e$ is an initial edge in $T_n$ satisfying that
-		for any $u\in V(e)$ with $u\neq v$, it holds
-		$Tr(T_n(v),u)\in \tau(u)$. Thus,
-		\[
-		\mathrm{E}\big[ X_{n,\epsilon} \big]
-		= \sum_{(e,\tau)\in Copies(\epsilon,[n];(v,\rho))} \Pr
-		\left(e\in E(T_n)
-		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_{n}, v; u)\in 
-		\tau(u) \right).
-		\]
-		Because of the symmetry of our random model the probability 
-		in the RHS of last equation is the same for all 
-		$(e,\tau)\in Copies(\epsilon,[n];(v,\rho))$. Let
-		$(e,\tau)\in Copies(\epsilon,\N;(v,\rho))$ be fixed. 
-		Using that 
-		$|Copies(\epsilon,[n];(v,\rho))|=\frac{(n)_{|e|-1}}
-		{\aut(\epsilon)}$ we obtain
-		\[
-		\mathrm{E}\big[ X_{n,\epsilon} \big]
-		=
-		\frac{(n)_{|e|-1}}{|
-			Aut(\epsilon)|} \Pr
-		\left(e\in E(T_{n})
-		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } 
-		Tr(T_n, v; u)\in \tau(u) \right).
-		\]
-		Also, it is satisfied
-		\begin{align*}
-		&\Pr
-		\left( e\in E(T_{n})
-		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_n, v; u)\in 
-		\tau(u) \right)=\\
-		&\PR{ e\in E(G_n)} \cdot
-		\Pr
-		\left( e\in E(T_{n})
-		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } 
-		Tr(T_{n}, v; u)\in \tau(u) \, \Bigg| \,  e\in E(G_n) \right)
-		\end{align*}
-		Because of \cref{lem:far_away}, a.a.s $T_n=N(v;r)$ so a.a.s if
-		$e\in E(G_n)$
-		and $v\in V(e)$, then $e\in E(T_n)$. Also,
-		$\PR{e\in E(G_n)}=\frac{\beta_{R(e)}}{n^{|e|-1}}$. In consequence
-		the RHS of last equation is asymptotically equivalent
-		to
-		\[
-		\frac{\beta_{R(e)}}{n^{|e|-1}} \cdot
-		\Pr	\left(
-		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_{n}, v; u)\in \tau(u) \, \Bigg| \,  e\in E(G_n) \right)
-		\]
-		Fix $\overline{u}\in (\N)_*$ a list that contains exactly the vertices
-		in $e$. Notice that the event $e\in E(G_n)$ clearly can be described
-		by an edge sentence
-		over the vertices in $\overline{u}$.
-		Because of \cref{lem:far_away},
-		\[
-		\Ln \Pr\Big(
-		N^{G_n}(v;r) \text{ is a tree } \Big| \, \, e\in E(G_n) \Big)=1.
-		\] 
-		Set $G^\prime_n:=G_n \setminus e$.
-		In the case that $T_n= N(v;r)$ and $e\in E(G_n)$ then
-		the following chain of equalities holds for all 
-		$u\in \overline{u}$ different from $v$:
-		\[
-		Tr(T_{n}, v, u)=N^{G^\prime_n}(u;\,r-1)=Tr(G_n,\overline{u};\, u;\, r-1).
-		\] 
-		Thus,
-		\begin{align}
-		\nonumber
-		&\Pr	\left(
-		\bigwedge_{\substack{u\in V(e)\\ u\neq v} } Tr(T_{n}, v; u)\in \tau(u) 
-		\, \Bigg| \,  e\in E(G_n) \right)
-		\sim\\ \label{eqn:equaltrees}
-		&
-		\Pr \left(
-		\bigwedge_{\substack{u\in V(e)\\ u\neq v} }
-		Tr(G_n,\overline{u};\, u;\, r-1)
-		\in \tau(u) \, \Bigg| \,  e\in E(G_n) \right)
-		\end{align}
-
-		By hypothesis, the RHS of last equality
-		is asymptotically equivalent to
-		$\prod_{\substack{u\in V(e)\\ u\neq v} } \Pr\big[
-		r-1, \tau(u)\big]=\lambda_{r,\epsilon}$.
-		Finally, joining everything we obtain
-		\[
-		\Ln
-		\mathrm{E}\big[ X_{n,\epsilon} \big]
-		= \Ln \frac{(n)_{|e|-1}}{\aut(\epsilon)}
-		\cdot  \frac{\beta_{R(e)}}{n^{|e|-1}}
-		\prod_{\substack{u\in V(e)\\ u\neq v} }
-		\Pr\big[
-		r-1, \tau(u)\big] =
-		\frac{\beta_{R(e)}}{\aut(\epsilon)} 
-		\cdot \lambda_{r,\epsilon}= \mu_{r,\epsilon},
-		\]
-		as we wanted.\par
-		Now we are going to prove that the variables $X_{n,\epsilon}$
-		converge in distribution to independent Poisson variables 
-		with mean values $\mu_{r,\epsilon}$ respectively. For
-		each $\epsilon\in P(k,r)$ let $b_\epsilon\in \N$. We want 
-		to show that
+$\{ \beta_R \}_{R\in \sigma}\in (0,\infty)^{|\sigma|}$
+and it is an expression belonging to $M$.
+
+\begin{lemma}\label{lem:poisedges}
+	Let $r>0$ and $\overline{u}\in (\N)_*$.
+	Let $\pi(\overline{x})\in FO[\sigma]$ be a consistent
+	edge sentence such that 
+	$len(\overline{x})=len(\overline{u})$.
+	Let $\overline{v}\in (\N)_*$ be vertices contained
+	in $\overline{u}$. For each $v\in \overline{v}$
+	set $T_{n,v}:= \Tr\left(G_n, \overline{u};\,\,v;\,\,r\right)$.
+	Given a pattern $\epsilon\in P(k,r)$ and $v\in \overline{v}$
+	we define the random variable $X_{n,v,\epsilon}$ as
+	the number of initial edges $e\in E(T_{n,v})$ such 
+	that $(e,\tau_{(T_{n,v},v)})\in \epsilon$. Suppose that
+	\cref{thm:BigTrees} holds for $r-1$. Then the conditional 
+	distributions of the variables $X_{n,v,\epsilon}$'s given
+	$\pi(\overline{u})$ converge to independent Poisson distributions
+	whose respective mean values are given by the $\mu_{r,\epsilon}$'s. 
+\end{lemma}
+\begin{proof}
+	To avoid excessively complex notation we will show only the case where
+	$\overline{v}$ consists only of one vertex $v$. The general case is proven
+	using the same arguments. Set $T_n:=T_{n,v}$ and 
+	$X_{n,\epsilon}:=X_{n,v,\epsilon}$ for all $\epsilon\in P(k,r)$.
+	By \cref{thm:BrunSieve},
+	in order to prove the result it is enough to show that 
+	for any choice of natural numbers $\{b_\epsilon\}_{\epsilon\in P(k,r)}$
+	it holds
 	\begin{equation} \label{eqn:binomexpedges}
 	\Ln
-		\mathrm{E}
+	\mathrm{E}_{\pi(\overline{u})}
 	\left[
@@
 	\end{equation}
+	Consider the numbers $\{b_\epsilon\}_{\epsilon\in P(k,r)}$
+	fixed. 
 	For each $n\in \N$ define
@@
 	\Omega_n:=\left\{
-		(E_\epsilon)_{\epsilon\in P(k,r)} \quad 
+	\{E_\epsilon\}_{\epsilon\in P(k,r)} \quad 
 	\Big | \quad \forall \epsilon\in P(k,r) \quad
@@
 	\quad |E_\epsilon|=b_\epsilon	
-		\right\}		
-		\]
-		We also define $\Omega_\N$ substituting writing $\N$
-		instead of $[n]$ in the definition of $\Omega_n$. 
+	\right\}.		
+	\]
 	Informally, elements of $\Omega_n$ represent choices of 
@@
 	\[
-		\mathrm{E}
+	\mathrm{E}_{\pi(\overline{u})}
 	\left[
@@
 	\sum_{
-		(E_\epsilon)_{\epsilon\in P(k,r)}
+		\{E_\epsilon\}_{\epsilon}
 		\in \Omega_n}
-		\Pr\left(
+	\mathrm{Pr}_{\pi(\overline{u})}\left(
 	\bigwedge_{\substack{
@@
 	\]
-		We say that an element $(E_\epsilon)_{\epsilon\in P(k,r)}$
-		of $\Omega_n$ is \textbf{disjoint} each vertex 
-		$w\in [n]\setminus\{v\}$ belongs to at most one edge 
-		$(e,\tau)\in\bigcup_{\epsilon\in P(k,r)} E_\epsilon$.
-		Notice that if we want the probability in the last sum to be greater 
-		than $0$ for a particular $(E_\epsilon)_{\epsilon\in P(k,r)}
-		\in \Omega_n$ then necessarily $(E_\epsilon)_{\epsilon\in P(k,r)}$
-		is disjoint. 
-		Indeed, suppose a vertex $w\in [n]\setminus \{v\}$ belongs to two different 
-		edges $(e_1, \tau_1),$ $(e_2,\tau_2)\in \bigcup_{\epsilon\in P(k,r)} E_\epsilon$. 
-		In consequence $e_1$ and $e_2$ form a cycle of diameter $1$, as they 
-		both contain $v$ and $w$. This implies that $e_1, e_2 \notin E(T_n)$.
-		\par
-		For each $n\in \N$ let $\Omega_n^\prime\subset \Omega_n$ be the set
-		of disjoint elements in $\Omega_n$. Then
-		\[
-		\mathrm{E}
-		\left[
-		\prod_{\epsilon\in P(k,r)} \binom{X_{n,\epsilon}}{b_\epsilon}	
-		\right]
-		= 
-		\sum_{
-			(E_\epsilon)_{\epsilon\in P(k,r)}
-			\in \Omega_n^\prime}
-		\Pr\left(
-		\bigwedge_{\substack{
-				\epsilon\in P(k,r)\\
-				(e, \tau)\in E_{\epsilon}
-		}} \left(
-		e\in E(T_n) \bigwedge_{\substack{
-				u\in V(e)\\
-				u\neq v}} Tr(T_n,v;u)\in \tau(u)		
-		\right)
-		\right). 		
-		\] 
-		Also, because of the symmetry of the random model, 
-		for all disjoint elements 
-		$(E_\epsilon)_{\epsilon\in P(k,r)}$ the probability 
-		in last sum is the same. In consequence, if we fix
-		$(E_\epsilon)_{\epsilon\in P(k,r)}\in \Omega^\prime_\N$
+	We say that a choice $\{E_\epsilon\}_{\epsilon}$
+	$\in \Omega_n$ is \textbf{disjoint} if the edges
+	$(e,\tau)\in\bigcup_{\epsilon\in P(k,r)} E_\epsilon$ satisfy
+	that no vertex $w\in \overline{u}$ other than $v$ belong to any
+	of those edges and each vertex 
+	$w\in [n]\setminus\{v\}$ belongs to at most one of those edges. 
+	For each $n\in \N$ let $\Omega_n^\prime\subset \Omega_n$ 
+	be the set	of disjoint elements in $\Omega_n$ and set
+	$\Omega^\prime_\N= \cup_{n\in \N} \Omega^\prime_n$.
+	If for some
+	$\{E_\epsilon\}_\epsilon \in \Omega_n$ 
+	it holds that $e\in E(T_n)$ for all $(e,\tau)\in
+	\bigcup_{\epsilon\in P(k,r)} E_\epsilon$ 
+	then $\{E_\epsilon\}_\epsilon$ 
+	is necessarily disjoint. 
+	This is because $T_n$ is a tree and
+	the only vertex in  $\overline{u}$ that belongs to $T_n$ 
+	is $v$ by definition.  
+	Thus, in last sum it suffices to consider only 
+	the disjoint $\{E_\epsilon\}_\epsilon$.
+	Because of the symmetry of the random model the probability
+	in that sum is the same for all disjoint choices of
+	$\{E_\epsilon\}_\epsilon$.
+	In consequence, if we fix
+	$\{E_\epsilon\}_{\epsilon}\in \Omega^\prime_\N$
 	we obtain
 	\begin{equation} \label{eqn:aux2}
-		\mathrm{E}
+	\mathrm{E}_{\pi(\overline{u})}
 	\left[
@@
 	|\Omega_n^\prime|\cdot
-		\Pr\left(
+	\mathrm{Pr}_{\pi(\overline{u})}\left(
 	\bigwedge_{\substack{
@@
 
+	Set $N:=\sum_{\epsilon\in P(k,r)} 
+	(|\epsilon|-1)\cdot b_\epsilon$.
 	Counting vertices and automorphisms we get that
 	\begin{equation} \label{eqn:aux3}
-		|\Omega_n^\prime|= (n)_{\sum_{\epsilon\in P(k,r)} 
-			(|\epsilon|-1)\cdot b_\epsilon}
+	|\Omega_n^\prime|= (n-len(\overline{u}))_{N}
 	\prod_{\epsilon\in P(k,r)}
@@
 	\end{equation}
+	Let $\overline{w}\in (\N)_*$ be a list containing exactly
+	the vertices $u\in V(e)$ for all $e\in 
+	\bigcup_{\epsilon\in P(k,r)} E_\epsilon$. 
+	Clearly, the event 
+	\[ \bigwedge_{\substack{
+			\epsilon\in P(k,r)\\
+			(e, \tau)\in E_{\epsilon}
+	}} e\in E(G_n)
+	\]  can be described via an edge sentence
+	whose variables are interpreted as vertices in $\overline{w}$.
+	Let $\psi(\overline{x})$ be one of such edge sentences.
+	This event is independent of $\pi(\overline{u})$ because edges are
+	independent in $G_n$. Thus, a simple computation yields
+	\[ 
+	\mathrm{Pr}_{\pi(\overline{u})}
+	\left(\bigwedge_{\substack{
+			\epsilon\in P(k,r)\\
+			(e, \tau)\in E_{\epsilon}
+	}} e\in E(G_n)\right) = \prod_{\epsilon\in
+	P(k,r)} \left(
+	\frac{\beta_{R(\epsilon)}}{n^{ar(R(\epsilon)-1)}}
+	\right)^{b_\epsilon}=
+	\frac{1}{n^N}
+	\prod_{\epsilon\in
+	P(k,r)} \beta_{R(\epsilon)}^{b_\epsilon}.
+	\]
+
 	Because of \cref{lem:far_away} a.a.s if $e\in E(G_n)$
@@
 	\begin{align} \label{eqn:aux4}
-		&\Pr\left(
+	&\mathrm{Pr}_{\pi(\overline{u})}\left(
 	\bigwedge_{\substack{
@@
 	\right)\sim\\ \nonumber
-		&\Pr\left(
+	&
+	\left(\frac{1}{n^N}
+	\prod_{\epsilon\in
+	P(k,r)} \beta_{R(\epsilon)}^{b_\epsilon}\right)
+	\cdot 		
+	\mathrm{Pr}_{\pi(\overline{u})\wedge \psi(\overline{w})}\left(
 	\bigwedge_{\substack{
@@
 			(e, \tau)\in E_{\epsilon}
-		}} e\in E(G_n)
-		\right)\cdot 		
-		\Pr\left(
+	}} 
 	\bigwedge_{\substack{
-				\epsilon\in P(k,r)\\
-				(e, \tau)\in E_{\epsilon}\\
 		u\in V(e)\\
@@
 	}}Tr(T_n;\, u)\in \tau(u)	
-		\, \Bigg| \, 
+	\right).
+	\end{align}
+	The trees $Tr(T_n;u)$ in last probability
+	coincide with 
+	$Tr(G_n,\overline{u}^\smallfrown\overline{w};\,u;\, r-1)$
+	for all $u$'s.
+	In consequence, using the hypothesis that \cref{thm:BigTrees}
+	holds for $r-1$ we obtain
+	\begin{align*}
+	&	\mathrm{Pr}_{\pi(\overline{u})\wedge \psi(\overline{w})}
+	\left(
 	\bigwedge_{\substack{
@@
 			(e, \tau)\in E_{\epsilon}
-		}} e\in E(G_n)
-		\right).
-		\end{align}
-	Let $\overline{w}\in (\N)_*$ be a list containing exactly
-	the vertices $u\in V(e)$ for all $e\in 
-	\bigcup_{\epsilon\in P(k,r)} E_\epsilon$. 
-	The event 
-	$ \bigwedge_{\substack{
-			\epsilon\in P(k,r)\\
-			(e, \tau)\in E_{\epsilon}
-	}} e\in E(G_n)$ clearly can be described via an edge sentence
-	whose variables are interpreted as vertices in $\overline{w}$.
-	Thus, analogously to \cref{eqn:equaltrees}
-	we obtain 
-	\begin{align} \label{eqn:aux5}
-	&	\Pr\left(
+	}} 
 	\bigwedge_{\substack{
-			\epsilon\in P(k,r)\\
-			(e, \tau)\in E_{\epsilon}
-	}} \left(
-	e\in E(T_n) \bigwedge_{\substack{
 			u\in V(e)\\
-			u\neq v}} Tr(T_n,v;u)\in \tau(u)		
-	\right) \, \, \Big| \, \,
-	\bigwedge_{\substack{
-			\epsilon\in P(k,r)\\
-			(e, \tau)\in E_{\epsilon}
-	}} e\in E(G_n)\,	
-	\right)\sim \\ \nonumber
-	&
-	\Pr\left(
-	\bigwedge_{\substack{
-			\epsilon\in P(k,r)\\
-			(e, \tau)\in E_{\epsilon}
-	}} \left(
-	e\in E(T_n) \bigwedge_{\substack{
-	u\in V(e)\\
-	u\neq v}}
-	Tr(G_n,\overline{w};\, u;\, r-1)\in \tau(u)		
-	\right)\, \, \Big| 
-	\, \,
-	\bigwedge_{\substack{
-	\epsilon\in P(k,r)\\
-	(e, \tau)\in E_{\epsilon}
-	}} e\in E(G_n)\,
-	\right)
-	\end{align}
-	By hypothesis last probability is asymptotically equivalent
-	to
-	\[
+			u\neq v
+	}}Tr(T_n;\, u)\in \tau(u)	
+	\right) \sim
 	 \prod_{\epsilon\in P(k,r)} (\lambda_{r,\epsilon})^{b_\epsilon}.
-	\]
+	\end{align*}
 	Joining this with \cref{eqn:aux2},
-	\cref{eqn:aux3}, \cref{eqn:aux4} and \cref{eqn:aux4} we obtain 
+	\cref{eqn:aux3} and \cref{eqn:aux4} we obtain 
 	\begin{align*} 
-	\Ln
-	\mathrm{E}
+	\mathrm{E}_{\pi(\overline{u})}
 	\left[
@@
 	\right]
-	= \Ln  
-	\frac{(n)_{\sum_{\epsilon\in P(k,r)}(|\epsilon|-1)\cdot b_\epsilon}}
-	{n^{\sum_{\epsilon\in P(k,r)}(|\epsilon|-1)\cdot b_\epsilon}}
+	\sim   
+	\frac{(n-len(\overline{u}))_{N}}
+	{n^{N}}
 	\cdot
@@
 	\frac{1}{b_\epsilon!} \cdot
-	\left( \frac{\beta_{R(\epsilon)}}{\aut(\epsilon)} \right)^
-	{b_\epsilon} \cdot 
-	(\lambda_{r,\epsilon})^{b_\epsilon}&\\
-	= \prod_{\epsilon\in P(k,r)}
+	\left( \frac{\beta_{R(\epsilon)}\cdot \lambda_{r,\epsilon}
+	}{\aut(\epsilon)} \right)^
+	{b_\epsilon} \sim \prod_{\epsilon\in P(k,r)}
 	\frac{\left( \mu_{r,\epsilon} \right)^
-	{b_\epsilon}}{b_\epsilon!}
-	,&
+		{b_\epsilon}}{b_\epsilon!}.
 	\end{align*}
-	as we wanted. In consequence, by \cref{thm:BrunSieve},
-	given $a_{\epsilon}\in \N$ for all $\epsilon\in P(k,r)$
-	it holds
-	\[
+	This proves \cref{eq:aux1} and the statement. 	
+\end{proof}
+
+Next lemma completes the proof of \cref{thm:BigTrees}.
+
+\begin{lemma} \label{lem:singletreeprob}
+Let $r\in \N$, $r>0$. Suppose that \cref{thm:BigTrees}
+holds for $r-1$. Then it also holds for $r$. 
+\end{lemma}
+\begin{proof}
+We start showing condition (1) of \cref{thm:BigTrees}.
+Fix $\mathbf{T}$ a $\sim_k$ class of trees with radius at most $r$. 
+Fix a vertex $v\in \N$ as well. Set $T_n:=\Tr(G_n,v;\,v;\,r)$.
+For each $\epsilon\in P(k,r)$ let
+$X_{n,\epsilon}$ be the random 
+variable that counts the number
+of initial edges in $T_n$ whose pattern is 
+$\epsilon$. Let $E^1_\mathbf{T}, E^2_\mathbf{T}, 
+\{a_\epsilon\}_\epsilon$ be as in \cref{obs:equivalenttrees}.
+Then
+\[
+\Pr[r,\mathbf{T}]=
 \Ln 
-	\Pr\left( 
-	\bigwedge_{\epsilon \in P(k,r)} X_{n,\epsilon}=a_\epsilon
-	\right)=
-	\prod_{\epsilon\in P(k,r)} e^{-\mu_{r,\epsilon}}
-	\frac{(\mu_{r,\epsilon})^{a_\epsilon}}{a_\epsilon!}.
-	\]
-
-	Finally, using \cref{obs:equivalenttrees} we get that for some
-	partition $E^1_\mathcal{T}, E^2_\mathcal{T}$ of $P(k,r)$ and 
-	some natural numbers $a_\epsilon<k$ for each 
-	$\epsilon\in E^2_\mathcal{T}$ it holds that
-	\[ \PR[r,\mathcal{T}]=
-	\Ln \PR{T_n\in \mathcal{T}}= 
+\mathrm{Pr}(T_n\in \mathbf{T})
+=
+\Ln
+\mathrm{Pr}\left(
 \left(
-	\prod_{\epsilon\in E^1_\mathcal{T}} \mathrm{Poiss}_{\geq k}(\mu_{r,\epsilon}) 
+\bigwedge_{\epsilon\in E^1_\mathbf{T}}
+X_{n,\epsilon}\geq k
+\right) \wedge
+\left(
+\bigwedge_{\epsilon\in E^2_\mathbf{T}}
+X_{n,\epsilon}= a_\epsilon
+\right)
+\right).
+\]
+And using the previous lemma we obtain that last limit
+equals the following expression.
+\[ 
+\left(
+\prod_{\epsilon\in E^1_\mathbf{T}}
+\mathrm{Poiss}_{\mu_{r,\epsilon}}(\geq k ) 
 \right)\cdot
 \left(
-	\prod_{\epsilon\in E^2_\mathcal{T}}
-	\mathrm{Poiss}_{a_\epsilon}(\mu_{r,\epsilon}) 
+\prod_{\epsilon\in E^2_\mathbf{T}}
+\mathrm{Poiss}_{\mu_{r,\epsilon}}(a_\epsilon) 
 \right).
 \]
-	And last expression belongs to $\Lambda$ as we wanted to prove. Furthermore,
+Using the definition of 
+the $\mu_{r,\epsilon}$'s we obtain that last expression
+belongs to $\Lambda$ as we wanted to prove. Furthermore,
 as the $\mu_{r,\epsilon}$'s are positive, this expression is also 
 positive for all values of
-	$\{ \beta_R \}_{R\in \sigma}\in [0,\infty)^{|\sigma|}$.
+$\{\beta_R\}_{R\in \sigma}\in (0,\infty)^{|\sigma|}$.
+Now we proceed to prove condition (2). 
+Let $\overline{u},\overline{v}, \{\mathbf{T}_v\}_{v\in \overline{v}}$
+and $\pi(\overline{x})$ be as in the statement of (2). 
+Using the previous lemma we obtain that the events
+$Tr(G_n,\overline{u};\, v;\, r)\in \mathbf{T}_v$ for all $v\in \overline{v}$
+are asymptotically independent and are also independent of $\pi(\overline{u})$. 
+In consequence the desired result follows from condition (1). 
 \end{proof}
-\sep
-
-	In order for \cref{thm:BigTrees} to be completely proven the following result is needed
-
-	\begin{lemma}
-		Let $r\in \N$ be a positive number.
-		Let $\overline{u}\in (\N)_*$ be a list of different fixed 
-		vertices, and let $\pi(\overline{x})\in FO[\sigma]$ be an
-		edge sentence such that 
-		$len(\overline{x})=len(\overline{u})$.
-		Let $\overline{v}\in (\N)_*$ be vertices contained
-		in $\overline{u}$. For each $v\in \overline{v}$
-		let $\mathcal{T}_v$ be a $k$-equivalence class
-		of trees with radii	at most $r$. Suppose
-		\cref{thm:BigTrees} holds for $r-1$. Then
-		\[
-		\Ln \mathrm{Pr}\big( \bigwedge_{v\in \overline{v}} 
-		Tr\big(G_n, \overline{u};\,\,v;\,\,r\big)\in \mathcal{T}_v 
-		\, | \, \pi(\overline{u})
-		\big)= \prod_{v\in \overline{v}} \mathrm{Pr}[r,\mathcal{T}_v]. \]	 
-	\end{lemma}
-	\begin{proof}[Sketch of the proof.]
-		The proof is completely analogous to the one 
-		of the previous lemma but now with more 
-		random variables. For each $v\in \overline{v}$ we define
-		$T_{n,v}:=Tr\big(G_n, \overline{u};\,\,v;\,\,r\big)$.
-		Given a $(k,r)$-pattern $\epsilon\in P(k,r)$ and a vertex
-		$v\in \overline{v}$ we define the random variable 
-		$X_{n,v,\epsilon}$ as the one that counts the number of initial
-		edges $e\in E(T_{n,v})$ whose pattern is $\epsilon$. Similarly to last lemma
-		one can show that the $X_{n,v,\epsilon}$ are asymptotically distributed
-		like independent Poisson variables whose respective means are the
-		$\mu_{r,\epsilon}$ defined in the previous lemma. As before, this is done using 
-		\cref{thm:BrunSieve}, by computing the binomial moments of the $X_{n,v,\epsilon}$'s.
-		Once the asymptotic distribution of those variables is computed the identity
-		\[\Ln \mathrm{Pr}\big( \bigwedge_{v\in \overline{v}} 
-		Tr\big(G_n, \overline{u};\,\,v;\,\,r\big)\in \mathcal{T}_v 
-		\, | \, \pi(\overline{u})
-		\big)= \prod_{v\in \overline{v}} \mathrm{Pr}[r,\mathcal{T}_v]
-		\]
-		follows easily using the definition of $\mathrm{Pr}[r,\mathcal{T}_v]$ 
-		provided at the end of last proof. 
-	\end{proof}
+%\sep
 
@@
 \begin{proof}
-		Let $\Sigma$ be the set of all $\sim_k$-classes of rooted trees
-		with radii at most $r$. For each $\mathcal{T}\in \Sigma$
-		let $\overline{v}(\mathcal{T})\in (\N)_k$ be a $k$-tuple of 
-		vertices such that all the $\overline{v}(\mathcal{T})$'s are
-		disjoint. Given any $\overline{v}\in (N)_*$
-		event $\phi_n\big(\overline{v}(\mathcal{T})\big)$ as the event that
-		for any $v\in \overline{v}$, $N(v;r)\cup Core(G_n;r)\emptyset$ 
-		(thus $N(v;r)$ is a tree),
-		and that for any two $v_1,v_2\in \overline{v}$, 
-		$d^{G_n}(v_1,v_2)>2r+1$. For each $n\in \N$ let
-		\[
-		A_n:=\bigwedge_{\mathcal{T}\in \Sigma} 
-		\exists\,\, \overline{v}(\mathcal{T}) \in ([n])_k\,\,
-		 \left(
-		\phi_n(\overline{v}(\mathcal{T})) \bigwedge_{
-		v\in \overline{v}(\mathcal{T})} 
-		Tr\big(
-		G_n;\,\,v;\,\,r
-		\big)\in \mathcal{T}
-		\right).
-		\]
-		Then the event $A_n$ that $G_n$ is $(k,r)$-rich.
-		Indeed, suppose $G_n$ satisfies
-		$A_n$. Let $\mathcal{T}\in \Sigma$ be a $\sim_k$ class and let 
-		$v_1,\dots,v_{k-1}\in [n]$ be any vertices in $G_n$. Then because of
-		$\phi_n(\overline{v}(\mathcal{T}))$ there is at least
-		one vertex $v\in \overline{v}(\mathcal{T})$ such that $d(v,v_i)\geq 2r+1$
-		for all $v_i$'s. It also holds that $T:=N(v;r)$ is a tree, and because of
-		$A_n$, $(T,v)\in \mathcal{T}$. In consequence $G_n$ is $(k,r)$-rich.\par
-		Now we show that $\Ln \PR{A_n}=1$. For that we will prove that for
-		each $\mathcal{T}\in \Sigma$, a.a.s. the following event holds:
-		\[
-		B_{n,\mathcal{T}}:=
-		\exists\,\, \overline{v}(\mathcal{T}) \in ([n])_k\,\,
-		\left(
-		\phi_n(\overline{v}(\mathcal{T})) \bigwedge_{
-			v\in \overline{v}(\mathcal{T})} 
-		Tr\big(
-		G_n;\,\,v;\,\,r
-		\big)\in \mathcal{T}
-		\right).
-		\]
-		Fix $\mathcal{T}\in \Sigma$ and fix $\epsilon>0$ an arbitrarily 
-		small real number. Let $m\in \N$,
-		and let $\overline{v}\in (\N)_m$ be a $m$-tuple of vertices. Let 
-		$X_{n,\overline{v}}$ be the random variable that counts the number of 
-		vertices $v\in \overline{v}$ such that $\mathrm{Tr}(G_n;\,\,v;\,\,r)$
-		belongs to $\mathcal{T}$. Because of \cref{thm:BigTrees}, $X_{n,\mathcal{v}}$
-		converges in distribution to a binomial variable with parameters $m$ and
-		$\Pr[r, \mathcal{T}]$. That is, for each $l\in [m]$,
-		\[
-		\Ln \PR{X_{n,\overline{v}}=l}= \binom{m}{l} \Pr[r, \mathcal{T}]^l \cdot \left(
-		1-\Pr[r,\mathcal{T}]\right)^{m-l}.
-		\]		    
-		In particular, as $\Pr[r, \mathcal{T}]$ is greater than zero, for $m$ sufficiently
-		big it holds that
-		\[
-		\Ln \PR{X_{n,\overline{v}}\geq k}> 1- \epsilon.
-		\]
-		Also, because of \cref{lem:far_away} we have that $\Ln \phi_n(\overline{v})=1$,
-		and in consequence for $m$ sufficiently big
-		\[
-		\Ln \Pr\left(
-		(X_{n,\overline{v}}\geq k)
-		\wedge \phi(\overline{v})
-		\right)> 1- \epsilon.
-		\]
-		As $(X_{n,\overline{v}}\geq k)
-		\wedge \phi(\overline{v})$ implies $B_{n,\mathcal{T}}$ we have that
-		$\Ln \PR{B_{n,\mathcal{T}}}=1$. As this holds for all $\mathcal{T}\in \Sigma$
-		and $\Sigma$ is a finite set, then $\Ln \PR{A_n}=1$ as well and the result follows. 
+%	$\frown_{\mathbf{T}\in\Sigma}$ 
+	Let $\Sigma$ be the set of all $\sim_k$ classes of rooted trees
+	with radii at most $r$. Let $m>k$. 
+	For each $\mathbf{T}\in \Sigma$
+	let $\overline{v}(\mathbf{T})\in (\N)_m$ be tuples
+	satisfying 
+	that all the $\overline{v}(\mathbf{T})$'s are
+	disjoint. Let $\overline{w}\in (\N)_*$ be a concatenation
+	of all the $\overline{v}(\mathbf{T})$'s. 
+	For each $\mathbf{T}\in 
+	\Sigma$ define $X_{n,\mathbf{T}}$ as the number of
+	vertices $v\in \overline{v}(\mathbf{T})$ such that 
+	$Tr(G_n,\,\overline{w};\,v;\,r)\in \mathbf{T}$. Because of \cref{thm:BigTrees}
+	the $\sim_k$ types of the trees $Tr(G_n,\,\overline{w};\,v;\,r)$ 
+	for all $v\in \overline{w}$ are asymptotically 
+	independent and given any $v\in \overline{w}$ and
+	$\mathbf{T}$ it holds that $\mathrm{Pr}(Tr(G_n,\,\overline{w};\,v;\,r)\in \mathbf{T})$
+	tends to $\Pr[r,\mathbf{T}]$ as $n$ goes to infinity. 
+	Hence,	the variables $X_{n,\mathbf{T}}$ converge in distribution to 
+	independent binomial variables whose respective parameters are
+	$m$ and $\Pr[r,\mathbf{T}]$. That is, given natural numbers
+	$0\leq l_\mathbf{T} \leq m$ for all $\mathbf{T}\in \Sigma$, it is
+	satisfied that
+
+	\[
+	\Ln
+	\mathrm{Pr}\left(
+	\bigwedge_{\mathbf{T}\in \Sigma} X_{n,\mathbf{T}}=l_\mathbf{T}
+	\right)= 
+	\prod_{\mathbf{T}\in \Sigma} \binom{m}{l_\mathbf{T}}
+	\Pr[r,\mathbf{T}]^{l_\mathbf{T}}\cdot (1-\Pr[r,\mathbf{T}] )^{m-l_\mathbf{T}}.
+	\] 
+	Fix $\delta>0$ such that $\delta< \Pr[r,\mathbf{T}]$ 
+	for all $\mathbf{T}\in \Sigma$ and fix $\epsilon>0$ arbitrarily small.
+	Because of the Law Of Large Numbers if $m$ is big enough it holds that
+	\begin{equation}\label{eq:rich1}
+	\Ln
+	\mathrm{Pr}\left(
+	\big| X_{n,\mathbf{T}}/m - \Pr[r,\mathbf{T}] \big| \geq \delta	
+	\right) \leq \epsilon \quad \text{ for all $\mathbf{T}\in \Sigma$.}
+	\end{equation}
+	Also, for $m$ big enough we have that
+	\begin{equation}\label{eq:rich2}
+		\Pr[r,\mathbf{T}] > l/m + \delta \quad \text{for all $\mathbf{T}\in \Sigma$}.
+	\end{equation}
+	Suppose that $m$ is big enough for both \cref{eq:rich1} and \cref{eq:rich2}
+	to hold. Then 
+	\[
+	\Ln
+	\mathrm{Pr}\left(
+	X_{n,\mathbf{T}} < k  \right) \leq \epsilon \quad \text{ for all $\mathbf{T}\in \Sigma$}
+	\]
+	We define the
+	event $A_n$ as the event that
+	for any $v\in \overline{w}$ we have
+	$N(v;r)\cap Core(G_n;r)=\emptyset$ 
+	(in particular this implies that $N(v;r)$ is a tree),
+	and for any two $v_1,v_2\in \overline{w}$
+	it is satisfied that	
+	$d^{G_n}(v_1,v_2)>2r+1$.
+	If $A_n$ holds then	for all	$v\in \overline{w}$ we have that
+	$N(v;r)=Tr(G_n,\,\overline{w};\,v;\,r)$ and
+	the $N(v;r)$'s are disjoint trees. 
+	Thus, if both $A_n$ holds and $X_{n,\mathbb{T}}\geq k$ for all $\mathbb{T}$ then 
+	$G_n$ is $(k,r)$-rich. Because of \cref{lem:disjointtrees} a.a.s $A_n$ holds, and we
+	obtain
+	\[
+	\Ln \mathrm{Pr}\left(
+	\text{ $G_n$ is not
+	$(k,r)$-rich }	
+	\right) \leq 
+	\Ln \mathrm{Pr}\left(
+	A_n \wedge \left(
+	\bigvee X_{n,\mathbf{T}}<k
+	\right)
+	\right) =
+	\Ln \mathrm{Pr}\left(
+	\bigvee X_{n,\mathbf{T}}<k
+	\right)	
+	\leq \epsilon^{|\Sigma|}.
+	\]
+	As $\epsilon$ can be arbitrarily small given a suitable choice of $m$ we
+	obtain that necessarily a.a.s $G_n$ is $(k,r)$-rich, as it was to be proved. 
 \end{proof}
@@
 	We define $\Gamma$ and $\Upsilon$ as the minimal families of expressions with arguments
-	$\{\beta_R\}_{R\in \sigma}$ that satisfies the conditions:
-	\begin{itemize}
-	\item[(1)] For each $R\in \sigma$ let $a_R\in \N$ be any natural number. Then, given any positive number $b\in \N$
+	$\{\beta_R\}_{R\in \sigma}$ that satisfy the following conditions:
+	(1) given natural numbers $a_R$ for each $R\in \sigma$, any positive number $b\in \N$
 	and any $\lambda\in \Lambda$ the expression $\frac{\lambda}{b}\cdot \prod_{R\in \sigma} \beta_R^{a_R}$
-	belongs to $\Gamma$.
-	\item[(2)] Given any $\gamma\in \Gamma$ and any $a\in \N$, the expressions $\mathrm{Poiss}_a(\gamma)$
-	and $\mathrm{Poiss}_{\geq a}(\gamma)$ both belong to $\Upsilon$.
-	\item[(3)] If $\upsilon_1, \upsilon_2\in \Upsilon$ then 
+	belongs to $\Gamma$, 
+	(2) given any $\gamma\in \Gamma$ and any $a\in \N$, the expressions $\mathrm{Poiss}_\gamma(a)$
+	and $\mathrm{Poiss}_{\gamma}(\geq a)$ both belong to $\Upsilon$, and
+	(3) if $\upsilon_1, \upsilon_2\in \Upsilon$ then 
 	$\upsilon_1\cdot \upsilon_2 \in \Upsilon$ as well. 
-	\end{itemize}
 \end{definition}
 
-\begin{theorem}\label{thm:agreeabilityprobabilities}
-	Let $\mathcal{O}$ be a simple $k$-agreeability class
-	of hypergraphs. Then 
-	$\Ln \PR{G_n\in \mathcal{O}}$ exists and is an expression
-	in $\Upsilon$. 
-\end{theorem}
+\begin{definition} Let $r\in \N$ and $O\in C(k,r)$.
+	Let $(H,\tau)$ be
+	a representative of $O$.
+	We define $\lambda_{r,O}$ and 
+	$\gamma_{r,O}$ in the following way:
+	\[ 
+	\lambda_{r,O}:
+	=\prod_{v\in V(H)}
+	\mathrm{Pr} \big[ r, \tau(v) \big],
+	\quad 
+	\text{ and } \quad
+	\gamma_{r,O}:=
+	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
+	{\aut(H,\tau)}\cdot\lambda_{r,O}.
+	\]	
+	Clearly the definitions of $\lambda_{r,O}$ and $\gamma_{r,O}$
+	are independent of the chosen representative and
+	the expression $\gamma_{r,O}$ belongs to $\Gamma$.
+\end{definition}
+
+\begin{lemma}
+	Let $r\in \N$. For any $O\in C(k,r)$ let $X_{n,O}$ be
+	the random variable that counts the connected components
+	$H$ of $Core(G_n;\, r)$ such that $H^\prime:=Center(H)$
+	satisfies that $(H^\prime, \tau_{H})\in O$. Then the variables
+	$X_{n,O}$'s converge in distribution to independent 
+	Poisson variables whose respective mean values are given by the 
+	$\gamma_{r,O}$'s.
+\end{lemma}
 \begin{proof}
-	Define $r:=3^k$. 
-	For each $O\in C(k,r)$ let $X_{n,O}$ be the random variable
-	that counts the number of cycles in $Core(G_n;r)$ 
-	whose $k$-type is $O$. Fix $O\in C(k,r)$.
-	For any $O\in C(k,r)$ we define $\lambda_O$ and 
-	$\gamma_O$ in the following way. Let $(H,\tau)$ be
-	a representative of $O$. Then
-	\[ 
-	\lambda_O:
-	=\prod_{v\in V(H)}
-	\Pr \big[ r, \tau(v) \big],
-	\]
-	and
-	\[
-	\gamma_O:=
-	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
-	{\aut(H,\tau)}\cdot\lambda_O.
-	\]	
-	As in the proof of 
-	\cref{lem:singletreeprob} one can show that
-	\[
-	\Ln \mathrm{E}\big[ X_{n,O}\big]
-	= \gamma_O
-	\].
-	Notice that the expression $\gamma_O$ both belongs to $\Gamma$ and
-	does only depend on the $(k,r)$-cycle $O$. \par
-%	Because of the symmetry of the random model last probability is the 
-%	same for all $(H,\tau)\in Copies(O,[n])$. Fix $(H,\tau)\in
-%	Copies(O,\N )$. Then
-%	\begin{align*}
-%	\mathrm{E}\big[ X_{n,O}\big]
-%	&=\frac{(n)_{|V(H)|}}{\aut(H,\tau)} 
-%	\cdot \Pr\left(
-%	H\subset G_n \bigwedge_{v\in V(H)} 
-%	Tree(G_n, v;r)\in \tau(v)
-%	\right)	\\
-%	&=\frac{(n)_{|V(H)|}}{\aut(H,\tau)}\cdot
-%	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}{n^{|V(H)|}}\cdot
-%	\Pr\left(\bigwedge_{v\in V(H)} 
-%	Tr(G_n, v;r)\in \tau(v)
-%	\quad  \Big| \quad H\subset G_n
-%	\right)\\
-%	&\sim 
-%	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
-%	{\aut(H,\tau)}\cdot
-%	\Pr\left(\bigwedge_{v\in V(H)} 
-%	Tr(G_n, v;r)\in \tau(v)
-%	\quad  \Big| \quad H\subset G_n
-%	\right)
-%	\end{align*}
-%	Let $\overline{v}\in (\N)_*$ be a list containing 
-%	exactly the vertices in $V(H)$. If $H\subset G_n$
-%	then $Tr(G_n, v;r)=Tr(G_n,\overline{v},v;r)$. Also,
-%	the event $H\subset G_n$ clearly can be described via
-%	an edge sentence concerning the vertices in $\overline{v}$.
-%	In consequence, using \cref{thm:BigTrees}, last expression
-%	is asymptotically equivalent to
-%	\[
-%	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
-%	{\aut(H,\tau)}\cdot
-%	\prod_{v\in V(H)}
-%	\Pr \big[ r, \tau(v) \big].
-%	\]
-
-	We are going to prove that the variables $X_{n,O}$ converge
-	in distribution as $n$ tends to infinity to 
-	independent Poisson variables whose respective means are
-	the $\gamma_O$. For that we are going to use again the factorial 
-	moments method. For each $O\in C(k,r)$ fix a number $b_{O}\in\N$.
-	We want to prove 
-	\[
+The proof is similar to the one of \cref{lem:poisedges}. 
+By \cref{thm:BrunSieve} to prove the result is enough to show
+that for any natural numbers $\{b_O\}_{O\in C(k,r)}$ it holds 
+\begin{equation} \label{eq:cycl_aux}
 \Ln 
@@
 \right]= \prod_{O\in C(k,r)} 
-	\frac{(\gamma_O)^{b_O}}{b_O!}.
-	\]
+\frac{(\gamma_{r,O})^{b_O}}{b_O!}.
+\end{equation}
 For each $n\in \N$ we define
@@
 \Omega_n:=\left\{
-	(F_O)_{O\in C(k,r)} \quad \Big|
+\{F_O\}_{O\in C(k,r)} \quad \Big|
 \quad \forall O\in C(k,r) \quad
@@
 \]
-	We also define $\Omega_\N$ by substituting $[n]$ for $\N$ in
-	the definition of $\Omega_n$. Informally, an element of $\Omega_n$ 
-	represents a choice of an unordered $b_O$-tuple
-	of possible cycles over $[n]$ whose $(k,r)$-type is $O$, for each
-	$(k,r)$-cycle $O$. Using observation \cref{obs:binomialmean} we obtain
+Given a cycle $H$ such that $V(H)\subseteq [n]$ we say 
+that $H\sqsubset G_n$ if $H=Center(H^\prime)$ for some connected 
+component $H^\prime$ of $Core(G_n;\, r)$.
+Using observation \cref{obs:binomialmean} we obtain
 \[
@@
 \right]=
-	\sum_{(F_O)_{O\in C(k,r)}\in \Omega_n}
-	\Pr\left(
+\sum_{\{F_O\}_{O}\in \Omega_n}
+\mathrm{Pr}\left(
 \bigwedge_{
@@
 \left(
-	H\subset G_n
+H\sqsubset G_n
 \bigwedge_{v\in V(H)}
@@
 \]
-	Consider the subset $\Omega_n^\prime\subset \Omega_n$ that contains
-	the elements $(F_O)_{O\in C(k,r)}\in \Omega_n$ such that there exists
-	some vertex $v\in [n]$ contained in two graphs
-	$(H_1,\tau_1),(H_2,\tau_2)\in \bigcup_{O\in C(k,r)} F_O$. We want to argue 
-	that
-	\begin{equation}\label{eqn:denseconfigurations}
-	\Ln
-	\sum_{(F_O)_{O\in C(k,r)}\in \Omega_n^\prime}
-	\Pr\left(
+We call a choice $\{F_O\}_O\in \Omega_n$ \textbf{disjoint} if no 
+vertex $v\in [n]$ belongs to two cycles $(H,\tau)\in \cup_O \, F_O$. 
+Define $\Omega_n^\prime$ as the set of disjoint elements in $\Omega_n$
+and set $\Omega_\N^\prime:=\cup_{n\in \N} \Omega^\prime_n$.
+If for some $\{F_O\}_O\in \Omega_n$ it holds that $H \sqsubset G_n$
+for all $(H,\tau)\in \cup_O F_O$ then necessarily $\{F_O\}_O$ is disjoint. 
+Indeed, suppose the opposite. Then for some $(H_1,\tau_1), (H_2,\tau_2)\in \cup_O F_O$ 
+it holds that $V(H_1)\cap V(H_2)\neq \emptyset$. Then both $H_1$ and $H_2$ belong
+to the same connected component $H$ of $Core(G_n;\,r)$ and thus $H_1\cup H_2\subset
+Center(H)$. In consequence neither $H_1\sqsubset G_n$ or $H_2\sqsubset G_n$ hold. 
+$(H_1,\tau_1),(H_2,\tau_2)\in \bigcup_{O\in C(k,r)} F_O$. Hence, 
+in the last sum it suffices to consider disjoint choices $\{F_O\}_O$. 
+Because of the symmetry of the random model the probability
+in that sum is the same for all disjoint choices of
+$\{F_O\}_O$.
+In consequence, if we fix
+$\{F_O\}_{O}\in \Omega^\prime_\N$
+we obtain
+\begin{equation}\label{eq:cycl_aux1}
+\mathrm{E}\left[
+\prod_{O\in C(k,r)}
+\binom{X_{n,O}}{b_O}
+\right]=
+|\Omega^\prime_n|\cdot
+\mathrm{Pr}\left(
 \bigwedge_{
@@
 \right)
-	\right)=0.
+\right).
 \end{equation}
-	Given an element $(F_O)_{O\in C(k,r)}\in \Omega_n$ we 
-	define the hypergraph $G\Big((F_O)_{O\in C(k,r)}\Big)$ as
-	follows:
-	\[
-	G\Big((F_O)_{O\in C(k,r)}\Big):=
-	\bigcup_{H\in F} H, 
-	\]
-	where
-	\[
-	F:=\left\{
-	H \quad \Big| \quad 
-	(H,\tau)\in \bigcup_{O\in C(k,r)} F_O	
-	\right\}.
-	\]
-	That is, $G\Big((F_O)_{O\in C(k,r)}\Big)$
-	is the union of all hypergraphs chosen in 
-	$(F_O)_{O\in C(k,r)}$. Then, for all 
-	$(F_O)_{O\in C(k,r)}\in \Omega_n$ it is 
-	satisfied
-	\begin{align*}
-	&\Pr\left(
+
+Set $N:=\sum_{O\in C(k,r)} |O|\cdot b_O$. We have that
+\begin{equation} \label{eq:cycl_aux2}
+|\Omega_n^{\prime}|=
+\frac{(n)_N}
+{\prod_{O\in C(k,r)} b_O!\cdot \aut(O)^{b_O}}.
+\end{equation}
+Let $\overline{v}\in (\N)_*$ be 
+a list that contains exactly the vertices in $G\left(
+\{F_O\}_{O\in C(k,r)}	\right)$. Then the event
+\[
+\bigwedge_{
+	\substack{
+		O\in C(k,r)\\
+		(H,\tau)\in F_O\\
+}}
+H\subset G_n
+\]
+can be written as an edge sentence concerning the vertices in $\overline{v}$.
+Let $\varphi(\overline{x})$ be one of such sentences. We have that
+\[
+\mathrm{Pr}\left(
+\bigwedge_{
+	\substack{
+		O\in C(k,r)\\
+		(H,\tau)\in F_O\\
+}}
+H\subset G_n
+\right)= \prod_{O\in C(k,r)} \left( \frac{\prod_{R\in \sigma}
+\beta_R^{|E_R(O)|}}{n^{|O|}} \right)^{b_O}=
+\frac{1}{n^N} \cdot
+\prod_{O\in C(k,r)} \left( \prod_{R\in \sigma}
+\beta_R^{|E_R(O)|} \right)^{b_O}.
+\]
+Because of \cref{cor:simple} a.a.s if some cycle $H$ of diameter at most
+$2r+1$ satisfies $H\subset G_n$ then $H\sqsubset G_n$. In consequence:
+\begin{align}
+\nonumber
+&\mathrm{Pr}\left(
 \bigwedge_{
@@
 \right)
-	\right)
-	\leq 
-	\Pr\left(
+\right) \sim \\ \label{eq:cycl_aux3}
+&\frac{1}{n^N} \cdot
+\prod_{O\in C(k,r)} \left( \prod_{R\in \sigma}
+\beta_R^{|E_R(O)|} \right)^{b_O} \cdot
+\mathrm{Pr}_{\varphi(\overline{v})}\left(
 \bigwedge_{
@@
 }}
-	H\subset G_n
-	\right) =
-	\\&
-	\Pr \left(
-	G\Big((F_O)_{O\in C(k,r)}\Big) \subset G_n
+\bigwedge_{v\in V(H)}
+Tr(G_n,v;r)\in \tau(v)
 \right).
-	\end{align*}
-	Let 
-	\[
-	t = \sum_{O\in C(k,r)} |V(O)|\cdot b_O.
-	\]
-	Then $V\Big(
-	G\Big((F_O)_{O\in C(k,r)}\Big)
-	\Big) \leq t$
-	for any $(F_O)_{O\in C(k,r)}\in \Omega_n$.\par
-	Consider the following facts
-	\begin{itemize}
-		\item[(1)] If $(F_O)_{O\in C(k,r)}\in \Omega_n^\prime$ then
-		$G\big((F_O)_{O\in C(k,r)}\big)$ is dense.
-
-		\item[(2)] Given an hypergraph $H$ with $V(H)\subset \N$,
-		the number of elements  $(F_O)_{O\in C(k,r)}\in \Omega_\N^\prime$
-		such that $H=G\big((F_O)_{O\in C(k,r)}\big)$ is finite and it is 
-		the same for all $H^\prime \simeq H$ with $V(H^\prime) \subset \N$.
-
-		\item[(3)] There is a finite amount of unlabeled dense
-		hypergraphs with size bounded by $t$.
-	\end{itemize}
-	Then it follows that
-	\begin{align*}
-	\sum_{(F_O)_{O\in C(k,r)}\in \Omega^\prime_n}
-	\Pr \Big(
-	G\Big(&(F_O)_{O\in C(k,r)}\Big) \subset G_n
-	 \Big) \\
-	& = 
-	\mathrm{O} \left(
-	\mathrm{E}\left[
-	\# \text{ of dense subgraphs in $G_n$ with size bounded by
-	 $t$}\right] \right).	
-	\end{align*}
-	And this, together with \cref{lem:nocopiesdense} proves
-	\cref{eqn:denseconfigurations}.\par
-	For all $n$ define $\Omega_n^{\prime\prime}=
-	\Omega_n\setminus \Omega_n^\prime$. That is, 
-	$\Omega_n^{\prime\prime}$ contains the elements
-	$(F_O)_{O\in C(k,r)}$ in $\Omega_n$ such that all vertices
-	$v\in [n]$ belong to at most one hypergraph
-	$(H,\tau)\in \bigcup_{O\in C(k,r)} F_O$. We also
-	define $\Omega_\N^{\prime\prime}$. Because of 
-	\cref{eqn:denseconfigurations} we have
-	\[
-	\mathrm{E}\left[
-	\prod_{O\in C(k,r)}
-	\binom{X_{n,O}}{b_O}
-	\right]=
-	\sum_{(F_O)_{O\in C(k,r)}\in \Omega_n^{\prime\prime}}
-	\Pr\left(
+\end{align}
+As all the vertices $v\in \overline{v}$ belong to $Core(G_n;\,r)$, the
+trees $Tr(G_n;\,v;\,r)$ in last probability coincide with 
+$Tr(G_n,\,\overline{v};\, v;\, r)$. Hence, by \cref{thm:BigTrees}
+we have that
+\begin{equation*}
+\mathrm{Pr}_{\varphi(\overline{v})}\left(
 \bigwedge_{
@@
 }}
-	\left(
-	H\subset G_n
 \bigwedge_{v\in V(H)}
 Tr(G_n,v;r)\in \tau(v)
-	\right)
-	\right)+o(1).
-	\]
-
-	Because of the symmetry of the model the probability inside of last sum 
-	is the same for all elements $(F_O)_{O\in C(k,r)}\in \Omega_n^{\prime\prime}$.
-	Also, counting all different vertices and automorphisms we obtain that
-	\[
-	|\Omega_n^{\prime\prime}|=
-	\frac{(n)_{\sum_{O\in C(k,r)} |V(O)|\cdot b_O}}
-	{\prod_{O\in C(k,r)} b_O!\cdot \aut(O)^{b_O}}.
-	\]
-	Fix $(F_O)_{O\in C(k,r)}\in \Omega_\N^{\prime\prime}$. Then 
-	\begin{align*}
-	&\Ln \mathrm{E}\left[
+\right) \sim 
+\prod_{O\in C(k,r)} \left(
+\lambda_{r,O}
+\right)^{b_O}.
+\end{equation*}
+Joining this with \cref{eq:cycl_aux1}, \cref{eq:cycl_aux2} and \cref{eq:cycl_aux3} we obtain
+\begin{equation*}
+\mathrm{E}\left[
 \prod_{O\in C(k,r)}
 \binom{X_{n,O}}{b_O}
-	\right]=\\
-	&
+\right]\sim
+\frac{(n)_N}{n^N}
+\cdot
+\prod_{O\in C(k,r)}
+\frac{1}{b_O!}
+\left(
+\frac{\lambda_{r,O}\cdot\prod_{R\in\sigma} \beta_R^{|E_R(O)|}}{\aut(O)}
+\right) \sim \prod_{O\in C(k,r)} \frac{(\gamma_{r,O})^{b_O}}{b_O!}.
+\end{equation*}
+This proves \cref{eq:cycl_aux} and the statement. 
+\end{proof}
+
+\begin{theorem}\label{thm:agreeabilityprobabilities}
+	Let $r\in \N$ and let $\mathcal{O}$ be a simple $(k,r)$-agreeability class
+	of hypergraphs. Then 
+	$\Ln \PR{G_n\in \mathcal{O}}$ exists and is an expression
+	in $\Upsilon$. 
+\end{theorem}
+\begin{proof}
+For each $O\in C(k,r)$ let $X_{n,O}$ be as in the previous lemma. 
+Let $U_\mathcal{O}^1, U_\mathcal{O}^2$ and $\{a_O\}_{O\in U^2_\mathcal{O}}$ 
+be as in \cref{obs:agreeablecores}. Let $A_n$ be the event that $G_n$ is $r$-simple. 
+Then
+\begin{align*}
  \Ln
-	\frac{(n)_{\sum_{O\in C(k,r)} |V(O)|\cdot b_O}}
-	{\prod_{O\in C(k,r)} b_O!\cdot \aut(O)^{b_O}} \cdot
-	\Pr\left(
-	\bigwedge_{
-		\substack{
-			O\in C(k,r)\\
-			(H,\tau)\in F_O
-	}}
+ \PR{G_n \in \mathcal{O}}=
+ \Ln
+ \mathrm{Pr} \left(
+ A_n \wedge
  \left(
-	H\subset G_n
-	\bigwedge_{v\in V(H)}
-	Tr(G_n,v;r)\in \tau(v)
-	\right)
-	\right).
-	\end{align*}
-	It holds that the probability in last expression equals
-	\[
-	\prod_{O\in C(k,r)}
-	\left( 
-	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(O)|}}{n^{|V(O)|}}
-	\right)^{b_O} \cdot
-	\Pr\left(
-	\bigwedge_{
-		\substack{
-			O\in C(k,r)\\
-			(H,\tau)\in F_O\\
-			v\in V(H)
-	}}
-	Tr(G_n,v;r)\in \tau(v) \,
-	\Bigg|  \,
-	\bigwedge_{
-		\substack{
-			O\in C(k,r)\\
-			(H,\tau)\in F_O\\
-		}}
-	H\subset G_n
-	\right).
-	\]
-	Let $\overline{v}\in (\N)_*$ be 
-	a list that contains exactly the vertices in $G\big(
-	(F_O)_{O\in C(k,r)}	\big)$. Then the event
-	\[
-	A_n:=
-		\bigwedge_{
-		\substack{
-			O\in C(k,r)\\
-			(H,\tau)\in F_O\\
-	}}
-	H\subset G_n
-	\]
-	can be written as an edge sentence concerning the vertices in $\overline{w}$.
-	Also, if $A_n$ holds then all vertices in $\overline{w}$ belong to 
-	$Core(G_n;r)$. Thus, for all $v\in \overline{v}$,
-	$Tr(G_n,v;r)=Tr(G_n,\overline{w};r)$ and using \cref{thm:BigTrees}
-	we obtain
-	\[
-	\Pr\left(
-	\bigwedge_{
-		\substack{
-			O\in C(k,r)\\
-			(H,\tau)\in F_O\\
-			v\in V(H)
-	}}
-	Tr(G_n,v;r)\in \tau(v) \,
-	\Bigg|  \,
-	\bigwedge_{
-		\substack{
-			O\in C(k,r)\\
-			(H,\tau)\in F_O\\
-	}}
-	H\subset G_n
-	\right) \sim
-	\prod_{O\in C(k,r)} (\lambda_O)^{b_O}.	
-	\]
-	Joining everything together we obtain
-	\begin{align*}
-&\Ln \mathrm{E}\left[
-\prod_{O\in C(k,r)}
-\binom{X_{n,O}}{b_O}
-\right]=\\
-&
-\Ln
-\frac{(n)_{\sum_{O\in C(k,r)} |V(O)|\cdot b_O}}
-{\prod_{O\in C(k,r)} b_O!\cdot \aut(O)^{b_O}} \cdot
-\prod_{O\in C(k,r)}
-\left( 
-\frac{\lambda_O \cdot \prod_{R\in \sigma} \beta_R^{|E_R(O)|}}{n^{|V(O)|}}
-\right)^{b_O} = \\
-&\prod_{O\in C(k,r)} \frac{1}{b_O!}\left(\frac{\lambda_O  
-\cdot \prod_{R\in \sigma} \beta_R^{|E_R(O)|} }{\aut(O)}
-\right)^{b_O}= \prod_{O\in C(k,r)} 
-\frac{(\gamma_O)^{b_O}}{b_O!},
-\end{align*}
-as we wanted. With this, because of \cref{thm:BrunSieve}, it 
-is proven that when $n$ tends to infinity
-the $X_{n,O}$'s are asymptotically distributed 
-like independent
-Poisson variables with the $\gamma_O$'s as their respective means.\par
-Fix a $(k,r)$-agreeability class of $r$-simple hypergraphs
-$\mathcal{O}$. 
-Because \cref{obs:agreeablecores} it holds that
-there is a partition $C_1, C_2\subset C(k,r)$, $C_1\cup C_2=C(k,r)$ 
-and natural numbers $a_O\leq k-1$ for any $O\in C_2$ such that
-$C_1, C_2, (a_O)_{O\in C_2}$ depend only on $\mathcal{O}$ and
-\begin{align*}
- & \Ln
- \PR{G_n \in \mathcal{O}}=\\
- &\Ln
- \Pr \left(
- G_n \text{ is $r$-sparse } \wedge
- \left(
- \bigwedge_{O\in C_1}
+ \bigwedge_{O\in U_\mathcal{O}^1}
  X_{n,O}\geq k
@@
  \left(
- \bigwedge_{O\in C_1}
+ \bigwedge_{O\in  U^2_\mathcal{O}}
  X_{n,O}=a_O.
@@
 \end{align*}
-Because of \cref{thm:sparse}, last limit equals
+Because of \cref{cor:simple}, a.a.s $A_n$ holds. Thus, using last
+lemma the previous limit equals the following expression
 \begin{align*}
-&\Ln
-\Pr \left(
-\left(
-\bigwedge_{O\in C_1}
-X_{n,O}\geq k
-\right)
-\wedge
-\left(
-\bigwedge_{O\in C_1}
-X_{n,O}=a_O
-\right)
-\right)
-=\\
-&
 \left(
 \prod_{O\in C_1}
-\mathrm{Poiss}_{\geq k}(\gamma_O)
+\mathrm{Poiss}_{\gamma_{r,O}}(\geq k)
 \right)
@@
 \prod_{O\in C_2}
-\mathrm{Poiss}_{a_O}(\gamma_O)
+\mathrm{Poiss}_{\gamma_{r,O}}(a_O)
 \right)
@@
 \end{align*}
-This last expression belongs to $\Upsilon$, so the theorem is proven. 
+As all the $\gamma_{r,O}$'s belong to $\Gamma$,
+this last expression belongs to $\Upsilon$ and the theorem is proven. 
 \end{proof}
@@
 	\{\beta_R\}_{R\in \sigma} \mapsto
-	\Ln \Pr \left(
+	\Ln \mathrm{Pr} \left(
 	G_n\left(\{\beta_R\}_{R\in \sigma}\right) \models \phi
@@
 	is well defined and it is given by a finite sum of expressions
-	in $\Theta$.
+	in $\Upsilon$.
 \end{theorem}
@@
 	$G_n:=G_n\left(\{\beta_R\}_{R\in \sigma}\right)$.
-	Using \cref{cor:simple} we obtain
-	\[
-	\Ln \Pr \left(
-	G_n \models \phi
-	\right)=
-	\Ln \Pr \left(
-	G_n\models \phi
-	\, \Big|
-	\, G_n
-	\text{ is $r$-sparse}
-	\right).
-	\]
 	Let $\Sigma$ be the set of $(k,r)$-agreeability classes of 
-	$(k,r)$-simple hypergraphs. 
-	Then
+	$r$-simple hypergraphs. Because of \cref{cor:simple} a.a.s 
+	$G_n$ is $r$-simple. In consequence
 	\begin{equation} \label{eq:aux1}
-	\Ln \Pr \left(
+	\Ln \mathrm{Pr} \left(
 	G_n \models \phi
@@
 	\Ln
-	\sum_{\mathcal{O}\in \Sigma} \Pr\left(
+	\sum_{\mathcal{O}\in \Sigma} \mathrm{Pr}\left(
 	G_n\in \mathcal{O}
 	\right) \cdot 
-	\Pr\left(
+	\mathrm{Pr}\left(
 	G_n\models \phi \,
@@
 	\end{equation}
-	Notice that, because the set $\Sigma$ is finite, 
-	this is the limit of a finite sum and we can exchange
-	summation and limit. Also, 
-	using \cref{thm:rich}, we obtain that for any $\mathcal{O}\in \Sigma$
-	it holds
-	\[
-	\Ln \Pr\left(
+	Because the set $\Sigma$ is finite, sum and we can exchange
+	last summation and limit symbols. Because \cref{thm:rich} a.a.s 
+	$G_n$ is $(k,r)$-rich. This together with \cref{thm:Duplicatorwins}
+	implies that for $\mathcal{O}\in \Sigma$
+	\[
+	\Ln \mathrm{Pr}\left(
 	G_n\models \phi \,
@@
 	\right) = 
-		\Ln \Pr\left(
-	G_n\models \phi \,
-	\Big| \,
-	G_n\in \mathcal{O}
- 	\text{ and } G_n \text{ 
-	is $(k,r)$-rich} 	\right).
-	\]
-	Because \cref{thm:Duplicatorwins} we have that given any two hypergraphs
-	$H_1$ and $H_2$ such that $H_1$ and $H_2$ are $(k,r)$-agreeable and they
-	are both $(k,r)$-rich then they both satisfy the same first order sentences
-	with quantifier rank at most $k$. Then the LHS of last equation always equals
-	either zero or one. Let $\Sigma^\prime\subset \Sigma$ be the set of classes 
+	\text{ $0$ or $1$ }.
+	\]
+	Let $\Sigma^\prime\subset \Sigma$ be the set of classes 
 	$\mathcal{O}$ for which last limit equals one. Then
 	\[
-	\Ln \Pr \left(
+	\Ln \mathrm{Pr} \left(
 	G_n \models \phi
@@
 	\sum_{\mathcal{O}\in \Sigma^\prime}
-	\Ln \Pr\left(
+	\Ln \mathrm{Pr}\left(
 	G_n \in \mathcal{O}
@@
 	each of the limits inside last sum exists and is given by
-	an expression that belongs to $\Theta$. As a consequence the
+	an expression that belongs to $\Upsilon$. As a consequence the
 	theorem follows. 	
@@
 
-We will define a binomial model of random CNF formulas, 
+We define a binomial model of random CNF formulas, 
 in analogy with the one in \cite{chvatal1992mick},
-but clearly the generality
+but the generality
 in \cref{thm:main} allows for many modifications. \par
 
-\begin{definition}
+\begin{definition}\label{def:CNF}
 Given a variable $x$ both expressions
@@
 by choosing each one of the $2^l\binom{n}{l}$ normal 
-clauses of size $l$ over the variables $\{x_i\}_{i\in [n]}$
+clauses of size $l$ over the variables $\{x_i\}_{i}$
 with probability $p$ independently. \par	
-We can model $l$-CNF formulas, as we have defined them, as relational 
+We consider $l$-CNF formulas, as defined above, as relational 
 structures with a language $\sigma$ consisting of $l+1$ relation symbols
-$R_0,\dots, R_l$ with arity $l$. We do that in such a way that the expression
+$R_0,\dots, R_l$ of arity $l$. We do that in such a way that the expression
 $R_j(x_{i_1},\dots,x_{i_l})$ means that our formula contains the clause
 consisting of $\neg x_{i_1}, \dots, \neg x_{i_j}$ and $x_{i_{j+1}},\dots
-x_{i_l}$. In consequence we need $R_1,\dots, R_l$ to satisfy the 
-following additional axioms:
-\begin{itemize}
-	\item For each $0\leq j \leq l$ and 
-	for any variables $y_1,\dots,y_j$, $y_{j+1},\dots, y_l$ it holds that
-	 $R_j(y_1,\dots y_j, y_{j+1},\dots, y_l)$ if and only if it still holds after 
-	 applying any permutations on the variables $y_1,\dots,y_j$ and the variables
-	 $y_{j+1},\dots,y_l$.
-	 \item For each $0\leq j \leq l$ and 
-	 for any variables $y_1,\dots, y_l$ it holds that
+x_{i_l}$. The relations $R_1,\dots, R_l$ satisfy the 
+following axioms: (1) for any $0\leq j \leq l$ and 
+for any variables $y_1,\dots, y_l$ the fact that
+$R_j(y_1,\dots, y_l)$ holds
+is invariant under any permutation of the variables 
+$y_1,\dots,y_j$ or $y_{j+1},\dots,y_l$, and (2) f
+or any $0\leq j \leq l$ and 
+any variables $y_1,\dots, y_l$ it holds that
 $R_j(y_1,\dots, y_l)$ only if all the $y_i$'s are different. 
-\end{itemize}
 Call $\mathcal{C}$ to the family of $\sigma$-structures satisfying these last two axioms.
-Then, there is a clear correspondence between $l$-CNF formulas over the variables
-$\{x_i\}_{i\in [n]}$ and the structures in $\mathcal{C}$ whose universe is 
-$\{x_i\}_{i\in [n]}$. \par
 The language $\sigma$ and the family $\mathcal{C}$ satisfy the conditions in 
 \cref{sect:structures}. The random model $F_l(n,p)$ coincides with the model
-$G(n,\{p_R\}_{R\in \sigma})$ of random $\mathcal{C}$-hypergraphs described in 
-\cref{sect:random} when all the $p_R$'s are equal. In consequence the following theorem 
-holds
+$G(n,\{p_R\}_{R})$ of random $\mathcal{C}$-hypergraphs described in 
+\cref{sect:random} when all the $p_R$'s are equal. As a particular
+case of \cref{thm:main} we obtain the following result. 
 \begin{theorem} \label{thm:mainsat}
@@
 	it is satisfied
-	that the map $f_\Phi: [0,\infty) \rightarrow \R$ given by
-	\[
-	\beta \mapsto \PR{ F_n(\beta)\models \Phi}
+	that the map $f_\Phi: (0,\infty) \rightarrow \R$ given by
+	\[
+	\beta \mapsto \Ln \PR{ F_n(\beta)\models \Phi}
 	\]
@@
 %$F(l,n,\beta/n^{l-1})$.
-A different model of random CNF formulas is studied in \cite{chvatal1992mick}. There 
-formulas are viewed as families of non necessary different clauses rather than sets.
-They define a random formula with $m$ clauses of size $l$ over $n$ variables as
-a sequence of independent 
-random clauses $C_1,\dots, C_m$ where each $C_i$ is chosen uniformly at random among
-the $2^l \binom{n}{l}$ ordinary clauses of size $l$ over $n$ variables. The 
-following holds
+The following is a well known result regarding random CNF formulas. 
 \begin{theorem} 
-Let $l\geq 2$ be a natural number, and let $c\in [0,\infty)$ 
+Let $l\geq 2$ be a natural number, and let $c\in (0,\infty)$ 
 be an arbitrary real number. 
@@
 $x_1,\dots,x_n$ that satisfies all clauses $C_{n,1},\dots, C_{n,m(n)}$. 
-Then there are two real constants $0<c_1<c_2$, independent from such that 
-\[
-\Ln \Pr\big( UNSAT_n \big)=0
-\]
-if $c< c_1$, and 
-\[
-\Ln \Pr\big( UNSAT_n \big)=1
-\]
+Then there are two real constants $0<c_1<c_2$, independent of such that 
+a.a.s $UNSAT_n$ does not hold if $c< c_1$, and a.a.s $UNSAT_n$ holds
 if $c> c_2$. 
 \end{theorem}
-The existence of $c_1$ is proven in theorem 1 of \cite{chvatal1992mick}. 
-The existence of the other constant $c_2$ follows from a simple application of
-the first order method that also appears in \cite{chvatal1992mick}, as well as 
+The existence of $c_1$ is proven in \cite[Theorem 1]{chvatal1992mick}.
+The fact that $c_2$ exists follows from a direct application of
+the first order method and is also shown in \cite{chvatal1992mick}, as well as 
 \cite{franco1983probabilistic}, \cite{chvatal1988many}, \cite{simon1986etude}
-and possibly others. We want to show that this ``phase transition" also happens in
-our model $F(l,n,p)$ when $p\sim \beta/n^{l-1}$. We start by showing the following
+and possibly others. We want to show that an analogous ``phase transition" also happens in
+$F(l,n,p)$ when $p\sim \beta/n^{l-1}$. We start by showing the following
 \begin{corollary}
-	Let $l\geq 2$ be a natural number. Let $c\in [0,\infty)$ be an arbitrary
+	Let $l\geq 2$ be a natural number. Let $c\in (0,\infty)$ be an arbitrary
 	real number and let $m:\N\rightarrow \N$ satisfy $m(n)=(c+o(1))n$. 
@@
 	are two real positive constants $0<c_1<c_2$ such that
-	\[
-	\Ln \Pr \big( F_{n,m(n)} \text{ is unsatisfiable } \big)=0
-	\]
-	if $c< c_1$, and
-	\[
-	\Ln \Pr \big( F_{n,m(n)} \text{ is unsatisfiable } \big)=1
-	\]
-	if $c> c_2$.
+	a.a.s $F_{n,m(n)}$ is satisfiable if $c< c_1$, and
+	a.a.s $F_{n,m(n)}$ is unsatisfiable if $c> c_2$.
 \end{corollary}
 \begin{proof}
-One can consider $F_{n,m(n)}$ to be the result of `selecting clauses $C_{n,1},\dots, C_{n,m(n)}$
-uniformly at random independently among all possible clauses' as in the previous theorem, but only in the case that `no two clauses $C_{n,i}, C_{n,j}$ are equal'. In consequence 
-\[
-\Pr \big( F_{n,m(n)} \text{ is unsatisfiable } \big) 
+For each $n\in \N$ let $C_{n,1},\dots, C_{n,m(n)}$ and $UNSAT_n$ be as in the previous theorem.
+One can consider $F_{n,m(n)}$ to be the result of selecting clauses $C_{n,1},\dots, C_{n,m(n)}$
+uniformly at random independently among all possible clauses, given the fact that
+no two clauses $C_{n,i}, C_{n,j}$ are equal. In consequence 
+\[
+\mathrm{Pr} \left( F_{n,m(n)} \text{ is unsatisfiable } \right) 
 =
-\Pr \big(UNSAT_n \, \big| \, \text{ all the $C_{n,i}$'s are different }\,\big),
-\] 
-where the event $UNSAT_n$ is defined as in the previous theorem. An application of the first
+\mathrm{Pr} \left(UNSAT_n \, \big| \, \text{ all the $C_{n,i}$'s are different }\,\right).
+\] 
+An application of the first
 order method yields that for $l>3$ a.a.s the number of unordered pairs $\{i,j\}$ such that
@@
 method proves that the number of such pairs $\{i,j\}$ converges in distribution to 
-a Poisson variable of positive mean. In either case we have
-\[
-\Ln \Pr \big(\, \text{ all the $C_{n,i}$'s are different }\,\big)>0.
-\]
+a Poisson variable. In either case all the
+$C_{n,i}$'s are different with positive asymptotic probability. 
 In consequence the constants $c_1$ and $c_2$ from the previous theorem satisfy
-the statement of this corollary. 
+our statement. 
 \end{proof}
-\sep
-
-Let $F_{n,m(n)}$ be as in last theorem. Notice that because the symmetry in 
+
+Let $F_{n,m(n)}$ be as in last result. Notice that because the symmetry in 
 the random model $F(l,n,p(n))$ one can consider $F_{n,m(n)}$ to be a random
-sample of the space $F(l,n,p(n))$ conditioned to the event that the number of clauses
-is $m(n)$. Using this observation we can prove the following result:
+sample of the space $F(l,n,p(n))$ given that the number of clauses
+is $m(n)$. Using this observation we can prove next theorem.
 
@@
 	$F(l,n,\beta/n^{l-1})$. Then there are real positive values 
-	$\beta_1 < \beta_2$ such that for any $0<\beta<\beta$
-	it holds
-	\[
-	\Ln \PR{F_n(\beta) \text{ is unsatisfiable }  }=0,
-	\]
-	and for any $\beta>\beta_2$
-	it holds
-	\[
-	\Ln \PR{F_n(\beta) \text{ is unsatisfiable }  }=1.
-	\]
+	$\beta_1 < \beta_2$ such that a.a.s $F_n(\beta)$ is satisfiable
+	for any $0<\beta<\beta_1$ and a.a.s $F_n(\beta)$ is unsatisfiable
+	and for any $\beta>\beta_2$.
 \end{theorem}
@@
 	and $\delta_2(m):=\floor*{ \left(\frac{\beta\cdot 2^l}{l!}+\epsilon\right)n}$.
-	Because of the Central Limit
-	Theorem it holds
-	\begin{equation}\label{eqn:aux6}
-	\Ln \Pr\left( \delta_1(n) \leq X_n(\beta)  
-	\leq \delta_2(n)    \right) = 1.
-	\end{equation}
-	Denote by $dp$ the probability density function of the variable $X_n(\beta)$.
-	That is $dp(m)=\Pr(X_n(\beta)=m)$. Then, because of the previous equation it holds
-	\[
-	\Pr\left( F_n(\beta) \text{ is unsatisfiable }\right)\sim
+
+	Denote by $dp_n$ the probability density function of the variable $X_n(\beta)$.
+	That is $dp_n(m)=\mathrm{Pr}(X_n(\beta)=m)$. Then, because of the previous equation it holds
+	\[
+	\mathrm{Pr}\left( F_n(\beta) \text{ is unsatisfiable }\right)\sim
 	\int_{\delta_1(n)}^{\delta_2(n)}
-	dp(m) \cdot \Pr \left(
+ \mathrm{Pr} \left(
 	F_n(\beta) \text{ is unsatisfiable } \Big|
 	X_n(\beta)=m	
-	\right).
-	\]
-	Notice that the property of being unsatisfiable is monotonous. That is,
-	for any two natural numbers $m_1<m_2$ it holds
-	\[
-	 \Pr \left(
-	F_n(\beta) \text{ is unsatisfiable } \Big|
-	X_n(\beta)=m_2	
-	\right) <  \Pr \left(
-	F_n(\beta) \text{ is unsatisfiable } \Big|
-	X_n(\beta)=m_2	
-	\right).
-	\]
+	\right)\cdot dp_n(m).
+	\]
+	Notice that the property of being unsatisfiable is monotonous.
 	In consequence,
@@
 	&\int_{\delta_1(n)}^{\delta_2(n)}
-	dp(m) \cdot \Pr \left(
+	\mathrm{Pr} \left(
 	F_n(\beta) \text{ is unsatisfiable } \Big|
 	X_n(\beta)=m	
-	\right)\leq \\ & 
-	\Pr \left(
+	\right)\cdot dp_n(m)\leq \\ & 
+	\mathrm{Pr} \left(
 	F_n(\beta) \text{ is unsatisfiable } \Big|
 	X_n(\beta)=\delta_2(n) \right) \cdot 
-	\Pr\big( \delta_1(n) \leq X_n(\beta)  
-	\leq \delta_2(n)  \big).   
+	\mathrm{Pr}\left( \delta_1(n) \leq X_n(\beta)  
+	\leq \delta_2(n)  \right).   
 	\end{align*}
-	And because of \cref{eqn:aux6}, 
-	\begin{align*}
-	&\Pr \left(
-	F_n(\beta) \text{ is unsatisfiable } \Big|
-	X_n(\beta)=\delta_2(n) \right) \cdot 
-	\Pr\left( \delta_1(n) \leq X_n(\beta)  
-	\leq \delta_2(n)  \right)\sim\\&
-	\Pr \left(
-	F_n(\beta) \text{ is unsatisfiable } \Big|
-	X_n(\beta)=\delta_2(n) \right).
-	\end{align*}
-	Finally, as $\delta_2(n)< c_2n$, because of the previous
+	Because of the Law of Large Numbers it holds
+	\begin{equation*}
+	\Ln \mathrm{Pr}\left( \delta_1(n) \leq X_n(\beta)  
+	\leq \delta_2(n) \right) = 1.
+	\end{equation*}
+	As $\delta_2(n)< c_2n$, because of the previous
 	corollary
 	\[
-	\Ln \Pr \left(
+	\Ln \mathrm{Pr} \left(
 	F_n(\beta) \text{ is unsatisfiable } \Big|
@@
 	\]  
-	Thus, joining everything, we have proven that for any 
-	$\beta < \beta_1$, it holds that
-	$F_n(\beta)$ a.a.s is satisfiable, as we wanted.
+	Joining all previous equations we obtain that for any 
+	$\beta < \beta_1$ it holds that
+	$F_n(\beta)$ a.a.s is satisfiable, as it was to be proven.
 	Showing that for any $\beta > \beta_2$, 
-	a.a.s $F_n(\beta)$ is unsatisfiable is analogous. We
-	fix $\epsilon>0$ such that $\frac{\beta\cdot 2^l}{l!}-\epsilon>c_2$.
-	We define $\delta_1(n)$ and $\delta_2(n)$ as before. Then similarly to before 
-	using the Central Limit Theorem and the fact that
-	the property of being unsatisfiable is monotonous one can prove the bound
-	\[
-	\Ln \Pr \left(
-	F_n(\beta) \text{ is unsatisfiable } \right) \geq
-	\Ln \Pr \left(
-	F_n(\beta) \text{ is unsatisfiable } \Big|
-	X_n(\beta)=\delta_1(n) \right).
-	\]
-	And using the previous corollary we obtain that last limit equals one, 
-	and the result follows.
-
+	a.a.s $F_n(\beta)$ is unsatisfiable is analogous.
 \end{proof}
-\sep
+%\sep
 
@@
 	$F(l,n,\beta/n^{l-1})$. Let $\Phi\in FO[\sigma]$ be a first order
-	sentence that implies unsatisfiability.  Then for all $\beta\in [0,\infty)$
-	it holds
-	\[
-	\Ln \PR{F_n(\beta)\models \Phi  }=0.
-	\]
+	sentence that implies unsatisfiability.  Then for all $\beta\in (0,\infty)$
+	a.a.s $F_n(\beta)$ does not satisfy $\Phi$.
 \end{theorem}
@@
 	\PR{F_n(\beta) \text{ is unsatisfiable }  }$. Thus, using \cref{thm:phasetransition}
-	we get that for all $\beta\in [0,\beta_1]$
+	we get that for all $\beta\in (0,\beta_1]$
 	\[
@@
 	Because \cref{thm:mainsat} last limit varies analytically with $\beta$, so
-	if it vanishes in a proper interval $[0,\beta_1]$ then it has to vanish
-	in the whole $[0,\infty)$ by the principle of analytic continuation, and the result 
+	if it vanishes in a proper interval $(0,\beta_1]$ then it has to vanish
+	in the whole $(0,\infty)$ by the Principle of Analytic Continuation, and the result 
 	holds. 
@@
 \section*{Acknowledgments}
-This work was supported by the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement ERC-2014-CoG 648276 AUTAR).\par
+This work was supported by the European Research Council (ERC) under the European Union's 
+Horizon 2020 research and innovation programme (grant agreement ERC-2014-CoG 648276 AUTAR).\par
 \todo{Albert and Marc Noy}
@@
 
-\pagebreak
 \bibliography{biblio}

### 2020-05-21 ArticleAcortado.tex
Menuda mierda colega

@@
 It was left open at the end of \cite{lynch1992probabilities} whether the convergence law obeyed
-by $G(n,\beta/n)$ could be generalized for other random models of relational structures
+by $G(n,p(n))$in the range $p(n)\sim \beta/n$
+could be generalized for other random models of relational structures 
 that contain relations of degree greater than $2$.
@@
 in this conditions the limit probability of any FO property of $G^d(n,p(n))$ varies 
-analytically with $\beta$. \par
-We aim to extend this last result to arbitrary relational structures
-to whose relations we can impose symmetry and anti-reflexivity constraints. 
+analytically with $\beta$. We 
+extend this result to arbitrary relational structures
+to whose relations we can impose symmetry and anti-reflexivity constraints 
+(\cref{thm:main}). \par
+
 This generalization is motivated by an application to the problem of random 
@@
 independently. This way the expected number of clauses is $\Theta(n^3p)$ as $n$ grows.
-The main result of that article states that when the expected number of clauses is $\Theta(n^{2+\alpha})$
-for any arbitrary $\alpha>0$ then there exists some FO property of $3$-CNF formulas that implies
+The main result of that article states that when the expected number of clauses is
+$\Theta(n^{2+\alpha})$ for any arbitrary $\alpha>0$ then there exists some 
+FO property of $3$-CNF formulas that implies
 unsatisfiability and asymptotically almost surely (a.a.s) holds for unsatisfiable formulas. 
@@
 $\alpha>0$ then no FO property that implies unsatisfiability holds a.a.s
-for unsatisfiable formulas.
+for unsatisfiable formulas. We complement this result by showing that 
+in a random $l$-CNF formula were each clause over $n$ variables is chosen  
+with probability $p(n)$ independently when the expected number of clauses is 
+$\Theta(n)$ there is no FO property that certifies unsatisfiability and
+holds a.a.s for unsatisfiable formulas (\cref{thm:mainsat}).
 
@@
 		is positive for all choices of 
-		$\{\beta_R\}_{R\in \epsilon}\in (0,\infty)^{|\sigma|}$,
+		$\{\beta_R\}_{R}\in (0,\infty)^{|\sigma|}$,
 		and is an expression
@@
 
-\section*{Conclusions}
-
 \section*{Acknowledgments}

### 2020-06-07 ArticleAcortado.tex
d

@@
 \usepackage{tcolorbox}
-\usepackage{natbib}
+\usepackage[square,numbers]{natbib}
 
@@
     It is also shown that those limit probabilities are well-behaved with
-    respect to some parameters that represent the density of tuples satisfying $R$
-    for each relation $R$ in the vocabulary $\sigma$. 
+    respect to some parameters that represent the density of tuples each relation $R$ 
+    in the vocabulary $\sigma$. 
     An application of these results to the problem of random Boolean 
@@
 If that limit takes only the values zero and one then we say that $\{G_n\}_n$ satisfies
-a zero-one law with respect to $L$.  
+a zero-one law with respect to $L$.  \par
 Convergence and zero one laws have been extensively studied with regards to 
@@
 then $G(n,p)$ satisfies a zero-one law with respect to the first order
-(FO) language of graphs. This zero-one law was later extended by Shelah and Spencer
+(FO) language of graphs. \par
+This zero-one law was later extended by Shelah and Spencer
 in \cite{shelah1988zero}. There it is proven, among other results,
 that if $p:=p(n)$ was a decreasing function on
-$n$ of the form $n^{-\alpha}$, and $\alpha\in (0,1)$ is irrational
+$n$ of the form $n^{-\alpha}$, and $\alpha>0$ is irrational
 then $G(n,p(n))$ obeys a zero-one law with respect to FO logic. Moreover, 
 it is also proven that if $\alpha\in (0,1)$ is rational then $G(n,p(n))$ 
-does not obey a convergence law. This was further extended by Lynch
+does not obey a convergence law. \par
+This was further extended by Lynch
 in \cite{lynch1992probabilities}, where it is shown that in the
@@
 
-\begin{theorem*}
+\begin{theorem*}[Lynch, 1992]
 	Let $p(n)\sim \beta/n$. For any FO sentence $\phi$, the function
@@
 property in $G(n,p(n))$ when $p(n)\sim \beta/n$ varies analytically with $\beta$.
-A consequence of this is that in this conditions no FO property can "capture" sudden changes 
+A consequence of this is that in these conditions no FO property can "capture" sudden changes 
 in the structure of $G(n,p(n))$. \par
@@
 could be generalized for other random models of relational structures 
-that contain relations of degree greater than $2$.
+that contain relations of arity greater than $2$.
 A result in this regard was obtained in \cite{salvadorbrasil}, 
 among other zero-one and convergence laws.
-There it is considered $G^d(n,p)$ the random model of $d$-uniform hypergraphs where
+There $G^d(n,p)$ is considered, the random model of $d$-uniform hypergraphs where
 each $d$-edge is added to a set of $n$ labeled vertices with probability $p$ independently.
@@
 language of $d$-uniform hypergraphs. With little additional work it can be shown that
-in this conditions the limit probability of any FO property of $G^d(n,p(n))$ varies 
+in these conditions the limit probability of any FO property of $G^d(n,p(n))$ varies 
 analytically with $\beta$. We 
@@
 This generalization is motivated by an application to the problem of random 
-satisfiability. We continue the study started by Atserias in \cite{atserias2005definability}
-with regards to the definability in first order logic of certificates for unsatisfiability
-that hold for typical unsatisfiable formulas. There it is considered a random model for
-$3$-CNF formulas where each possible clause over $n$ variables is added with probability $p$ 
-independently. This way the expected number of clauses is $\Theta(n^3p)$ as $n$ grows.
-The main result of that article states that when the expected number of clauses is
-$\Theta(n^{2+\alpha})$ for any arbitrary $\alpha>0$ then there exists some 
-FO property of $3$-CNF formulas that implies
-unsatisfiability and asymptotically almost surely (a.a.s) holds for unsatisfiable formulas. 
-Furthermore, if the expected number of clauses is $\Theta(n^{2-\alpha})$ for any irrational
-$\alpha>0$ then no FO property that implies unsatisfiability holds a.a.s
-for unsatisfiable formulas. We complement this result by showing that 
-in a random $l$-CNF formula were each clause over $n$ variables is chosen  
-with probability $p(n)$ independently when the expected number of clauses is 
-$\Theta(n)$ there is no FO property that certifies unsatisfiability and
-holds a.a.s for unsatisfiable formulas (\cref{thm:mainsat}).
+satisfiability. We continue the study started by Atserias in 
+\cite{atserias2005definability}
+with regards to the definability in first order
+logic of certificates for unsatisfiability
+that hold for typical unsatisfiable formulas. 
+A random model for $3$-CNF formulas where 
+each possible clause over $n$ variables 
+is added with probability $p$ independently is considered there.
+This way the expected number of clauses $m$ is $\Theta(n^3p)$ as $n$ grows.
+The main result of that article states the following:
+(1) if $m=\Theta(n^{2-\alpha})$ 
+for any irrational $\alpha>0$, then no FO property of $3$-CNF formulas
+that implies unsatisfiability holds asymptotically almost surely (a.a.s) 
+for unsatisfiable formulas, and (2) if $m=\Theta(n^{2+\alpha})$ for any $\alpha>0$,
+then there exists some FO property that implies
+unsatisfiability and  holds a.a.s for unsatisfiable formulas. \par
+The second part of the statement is the simpler one to prove:
+it can be shown that when $m=\Theta(n^{2+\alpha})$ for some 
+$\alpha>0$ then the random $3$-CNF formula
+a.a.s contains some fixed unsatisfiable subformula (which depends
+on the choice of $\alpha$). This is clearly expressible in FO logic, 
+so (2) follows. The proof of (1) is more involved and, in fact, 
+shows something stronger: if $m=\Theta(n^{2-\alpha})$
+for any $\alpha>0$ irrational, then all FO properties 
+that imply unsatisfiability
+a.a.s do not hold. This proof employs
+techniques based in the ones used by Shelah and Spencer 
+in \cite{shelah1988zero} to prove that $G(n,p)$ satisfies a 
+zero-one law with respect to FO logic when $p$ is an irrational 
+power of $n$. \par
+Since the techniques used to prove (2) rely in the fact that $\alpha$
+is irrational, the study of the range $m=\Theta(n)$
+(that is, $m=\Theta(n^{2-\alpha})$ with $\alpha=1$), was left open.
+This range is of special interest because it is where the phase 
+transition from almost sure satisfiability to almost sure unsatisfiability
+takes place. It was shown
+in \cite{chvatal1992mick} that a random $k$-CNF formula with
+$m$ clauses over $n$ variables satisfying that $m\sim c\cdot n$ 
+is a.a.s satisfiable for all sufficiently small values of $c$ and is a.a.s
+unsatisfiable for all sufficiently big values of $c$.
+\par
+The possibility of studying FO definability of certificates for unsatisfiability
+in random $l$-CNF formulas with a linear expected number of clauses 
+using a generalization of Lynch's theorem was suggested by Atserias. 
+This application is discussed in \cref{sec:SAT}. We give a brief overview
+of it here. Let $F(l,n,p)$ be a random model of $l$-CNF 
+formulas where each $l$-clause over $n$ variables is chosen with probability
+$p$ independently. Let $F_n(\beta)$ denote a random formula in
+$F(l,n,p)$ where $p:=p(n)\sim \beta/n^{l-1}$. 
+Suppose that 
+every FO property of $l$-CNF formulas 
+has a well defined asymptotic probability in $F_n(\beta)$
+for any $\beta>0$.
+Further suppose that those asymptotic probabilities vary analytically
+with $\beta$. Then any FO property that implies unsatisfiability
+a.a.s does not hold in $F_n(\beta)$ for any
+$\beta>0$. Indeed, let $P$ be one of such FO properties. One can find a
+value $\beta_0>0$ satisfying that 
+a.a.s $F_n(\beta)$ is satisfiable when $0<\beta<\beta_0$.
+In consequence $P$ a.a.s does not hold
+in $F_n(\beta)$ when $0<\beta<\beta_0$.
+Since the asymptotic probability of $P$ varies analytically
+with $\beta$ and it vanishes in the non-empty interval $(0,\beta_0)$,
+because of the Principle of Analytical Continuation
+it must be true that a.a.s $P$ does not hold in $F_n(\beta)$ for all
+$\beta>0$.
 
@@
 we write $\overline{x}^\smallfrown \overline{y}$ to denote their 
-concatenation.
+concatenation. Given a set $S$ and elements $x_s$ for each $s\in S$
+we will write $\{x_s\}_{s\in S}$, or just $\{x_s\}_s$ when $S$ is understood,
+to denote the tuple indexed by $S$ which for any $s\in S$
+contains the element $x_s$ at the position given by $s$. 
 \par
@@
 of the set $S^a$ by this action. Given an element
-$\overline{x}:=(x_1,\dots, x_a)\in S^a$ we will denote its equivalence
+$\overline{x}:=(x_1,\dots, x_a)\in S^a$ we denote its equivalence
 class in $S^a/\Phi$ by $[x_1,\dots,x_a]$ or $[\overline{x}]$.
@@
 $(x_1,\dots, x_a)$ 
-will be reserved 
-to ordered tuples while 
+represent
+ordered tuples while 
 $[\overline{x}]$ and
-$[x_1,\dots,x_a]$ will denote ordered tuples modulo the
+$[x_1,\dots,x_a]$ denote ordered tuples modulo the
 action of some arbitrary group of permutations. Which group is
@@
 
-Given two real functions over the natural numbers 
-$f,g:\N \rightarrow \R$ we will write $f=O(g)$ to 
-mean that there exists some constant $C\in \R$
-such that $f(n)\leq Cg(n)$ for $n$ sufficiently large, 
-as usual. We will write $f=\Theta(g)$ if both $f=O(g)$ and
-$g=O(f)$. If $g(n)\neq 0$ for $n$ large enough then
-we will write $f\sim g$ when $\Ln \frac{f(n)}{g(n)}=1$.
+Given real functions over the natural numbers 
+$f,g:\N \rightarrow \R$ the expressions $f=O(g)$,
+$f=o(g)$ and $f=\Theta(g)$ will have their usual meaning.
+If $g(n)\neq 0$ for $n$ large enough then
+we will write $f\sim g$ when $\Ln \frac{f(n)}{g(n)}=1$. \par
 
@@
 %
+\subsection{Probabilistic preliminaries}
+
+We assume familiarity with basic probability theory. 
+We denote by $\mathrm{Poiss}_\lambda(n)$ the discrete probability mass
+function of a random variable following a Poisson distribution with
+mean $\lambda$. That is, $\mathrm{Poiss}_\lambda(n)=e^{-\lambda}\frac{\lambda^n}{n!}$.
+We define $\mathrm{Poiss}_\lambda(\geq n)=1 - \sum_{i=0}^{n-1} \mathrm{Poiss}_\lambda(i)$. \par
+
+Our main tool for proving the convergence in distribution 
+to Poisson variables ones is the next result, which can
+be found in \cite[Theorem 1.23]{bollobas2001random}.
+
+\begin{theorem} \label{thm:BrunSieve}
+	Let $l\in \N$. For each 
+	$n\in \N$, let $X_{n,1},\dots, X_{n,l}$ be non-negative
+	random integer variables over the same
+	probability space. Let $\lambda_1,\dots,\lambda_l$ 
+	be real numbers. Suppose for any $r_1,\dots,r_l \in \N$
+	\[ 
+	\Ln \mathrm{E}\left[
+	\prod_{i=1}^{l} \binom{X_{n,i}}{r_i} \right]
+	= \prod_{i=1}^{l} \frac{\lambda_i}{r_i !}.	
+	\]
+	Then the $X_{n,1},\dots,X_{n,l}$ converge in distribution to
+	independent Poisson variables with means $\lambda_1,\dots,\lambda_l$ 
+	respectively. 
+\end{theorem}
+
+We will use the following observation in order to compute the binomial moments of 
+our random variables.
+
+\begin{obs} \label{obs:binomialmean} Let $X_1,\dots, X_l$ be non negative
+	random integer variables over the same space. 
+	Let $r_1,\dots,r_l\in \N$.	Suppose
+	each $X_i$ is the sum of various indicator random variables
+	(i.e. variables that only take the values $0$ and $1$)
+	$X_i=\sum_{j=1}^{a_i} Y_{i,j}$. Define 
+	$\Omega:=\prod_{i=1}^l \binom{[a_i]}{r_i}$. That is,
+	the elements $\{S_i\}_{i\in[l]}\in \Omega$
+	represent all the possible unordered choices of 
+	$r_i$ indicator variables $Y_{i,j}$ for each $i\in [l]$.
+	Then 
+	\[
+	\mathrm{E}\left[
+	\prod_{i=1}^{l} \binom{X_i}{r_i}\right]=
+	\sum_{\{S_i\}_{i\in [l]}} \mathrm{Pr}\left(
+	\bigwedge_{\substack{i\in [l]\\ j\in S_i}} Y_{i,j}=1
+	\right).	
+	\]
+\end{obs}
+
+If $A,B$ are events we may write the conditioned probability $\mathrm{Pr}(A\, | \, B )$ 
+as $\mathrm{Pr}_B(A)$ in some situations to shorten some expressions.
 
@@
 formulas with no quantifiers are called \textbf{open formulas}. 
+We call \textbf{edge sentence} to any consistent open formula that contains
+no occurrence of the equality symbol `$=$'.
 
@@
 \par
-A connected hypergraph $G$ is a path between two of its 
+A connected hypergraph $G$ is a \textbf{path} between two of its 
 vertices $v,u\in V(G)$ if $G$ 
@@
 an \textbf{automorphism} of $H$, resp. $(H,\chi)$,
-is an isomorphism from $H$, resp $(H,\chi)$ to itself.
-We will denote by $\aut(H)$, resp. $\aut(H,\chi)$
+is an isomorphism from $H$, resp. $(H,\chi)$, to itself.
+We will denote by $\aut(H)$, resp. $\aut(H,\chi)$,
  the number of such automorphisms. \par
@@
 $\chi$ be a $\Sigma$-coloring of $H$. 
-As before, we define the set $Copies\left(
+Analogously, we define the set $Copies\left(
 (H,\chi),\, \, V\right)$ as the set of $\Sigma$-hypergraphs
@@
 
-Given $\mathbb{H}$ an isomorphism class of hypergraphs or $\Sigma$-hypergraphs
-, we define expressions
+Given $\mathbb{H}$ an isomorphism class of hypergraphs or $\Sigma$-hypergraphs,
+we define expressions
 such as $ex(\mathbb{H})$, $\aut(\mathbb{H})$,
@@
 As in the case of Lynch's theorem, we are interested in the
-"sparse regime" of $G^\mathcal{C}(n,\overline{p})$, were the 
+"sparse regime" of $G^\mathcal{C}(n,\{p\}_R)$, were the 
 expected number of edges each sort is linear. 
-%In other words, we want that
-%$\mathrm{E}[m_i(G_n)]=\Theta(n)$ for all $i$'s.
-This is achieved when each of the $p_R$'s are 
-of the form $\beta_R/n^{ar(R)-1}$ for some 
-positive real numbers $\InR{\beta}$.
-We will denote a random sample of 
-$G^\mathcal{C}\left(n,\left\{p_R\right\}_{R\in\sigma}\right)$
-by $G_n\left(\InR{\beta}\right)$ when the probabilities $p_R$
-satisfy $p_R(n)\sim \beta_R/n^{ar(R)-1}$ for all $R\in \sigma$.
+This is achieved when for each $R\in \sigma$ 
+it holds that $p_R(n)\sim \beta_R/n^{ar(R)-1}$ for some 
+positive real number $\beta_R$.
+We will write $G_n\left(\{\beta_R\}_R\right)$
+to denote a random sample of 
+$G^\mathcal{C}\left(n,\{p_R\}_{R}\right)$
+by when for each $R\in \sigma$ holds that
+$p_R(n)\sim \beta_R/n^{ar(R)-1}$
 When the choice of $\InR{\beta}$ is not relevant
 we will write $G_n$ instead of 
-$G_n\left(\InR{\beta}\right)$.\par
-
-Our goal is to prove the following theorem:
-
-\begin{theorem} \label{thm:main}
-	Let $\phi$ be a sentence in $FO[\sigma]$. Then
-	the function
-	%$F_\phi: [0,1]^{t_u}\times (0,\infty)^{t-t_u}
-	$F_\phi: (0,\infty)^{|\sigma|}
-	\rightarrow \R$ given by 
-	\[
-	\InR{\beta} \mapsto \Ln Pr\left( G_n\left(
-	\InR{\beta}\right) \models \phi\right)
-	\]
-	is well defined and analytic. 
-\end{theorem}
+$G_n\left(\{\beta_R\}_R\right)$.\par
 
 \subsection{Main definitions}
+
+Our main definition follow closely the ones in \cite{lynch1992probabilities}
+adapted to the context of hypergraphs.
 
@@
 $H$ contains a unique maximal saturated sub-hypergraph $H^\prime$
-and it satisfies $ex(H^\prime)=ex(H)$ if $ex(H)\geq 0$ and $H^\prime=\emptyset$ 
-if $H$ is a tree. Given
+satisfying satisfies $ex(H^\prime)=ex(H)$ if $ex(H)\geq 0$, and $H^\prime=\emptyset$ 
+otherwise. Given
 $\overline{v}\in V(H)^*$ we define $Center(H,\overline{v})$ as the 
@@
 
-\begin{definition}
+For any $k\in \N$ we define an equivalence relation over rooted trees
+which generalizes both the relation of "$k$-morphism" as 
+defined in \cite{lynch1992probabilities},
+and the notion of "$(k,r)$-values" defined in \cite{salvadorbrasil}.
+
+\begin{definition}\label{def:sim_trees}
 
@@
 		Given a rooted tree $(T,v)$ of radius $r$
-		we define its \textbf{canonical coloring}
+		we define its \textbf{canonical k-coloring}
 		as the map 
-		$\tau_{(T,v)}: V(T)\rightarrow \widehat{\Sigma}_{k,r-1}$ satisfying that
-		$\tau_{(T,v)}(u)$ is the
+		$\tau^k_{(T,v)}: V(T)\rightarrow \widehat{\Sigma}_{k,r-1}$ satisfying that
+		$\tau^k_{(T,v)}(u)$ is the
 		$\sim_k$ class of $\mathrm{Tr}(T,u;\, \,v)$
-		for any $u\neq v$, and $\tau_{(T,v)}(v)=\tau$. \par
+		for any $u\neq v$, and $\tau^k_{(T,v)}(v)=\tau$. \par
 		Let $T_1$ and $T_2$ be rooted trees of radius $r$. 
@@
 		``quantity of initial edges $e_1\in E(T_1)$ such that
-		$\left(e,\tau_{(T_\delta,v_\delta)}\right) \in \epsilon$" 
+		$(e,\tau^k_{(T_\delta,v_\delta)}) \in \epsilon$" 
 		and the
 		``quantity of initial edges $e_2\in E(T_2)$ such that
-		$\left(e,\tau_{(T_\delta,v_\delta)}\right)\in \epsilon$
+		$(e,\tau^k_{(T_\delta,v_\delta)})\in \epsilon$
 		" are equal or
@@
 	$\epsilon\in E^1_\mathbf{T}$ there are at least $k$ initial edges $e\in E(T)$ such that
-	$(e,\tau_{(T,v)})\in \epsilon$, and (2) for any pattern 
+	$(e,\tau^k_{(T,v)})\in \epsilon$, and (2) for any pattern 
 	$\epsilon\in E^2_\mathbf{T}$ there are exactly
 	$a_\epsilon$ initial edges $e\in E(T)$ such that
-	$(e,\tau_{(T,v)})\in \epsilon$.	
+	$(e,\tau^k_{(T,v)})\in \epsilon$.	
 \end{obs}
 
-\begin{obs}\label{obs:finitetrees}
-	Using last characterization of $\sim_k$ classes
-	it is easy to show that for any $r\in \N$ the quantity
-	of $\sim_k$ classes of trees with radii at most $r$ is finite. 
-	We proceed by induction. For $r=0$ there is only one $\sim_k$ class.
-	Now let $r>0$ and suppose the statement holds for $r-1$. Then
-	the number of $(k,r)$-patterns is finite and so is the number
-	of $\sim_k$ classes of trees with radii at most $r$. 
-\end{obs}
-
-\begin{definition}
+From last characterization of the $\sim_k$ relation
+it follows, via an induction argument, that for any $r\in \N$ the quantity
+of $\sim_k$ classes of trees with radii at most $r$ is finite. \par
+
+\begin{definition} \label{def:sim_general}
+	Let $k\in \N$. 
 	Given $H$ be a non-tree connected hypergraph, we define
-	its \textbf{canonical coloring} $\tau_{H}$
+	its \textbf{canonical k-coloring} $\tau^k_{H}$
 	as the one that assigns to each vertex $v\in V(H)$ the $\sim_k$ 
@@
 	written as $H_1\sim_k H_2$, if
-	$\left( H^\prime_1,\tau_{H_1}\right) \simeq 
-	\left(H^\prime_2,\tau_{H_2}\right)$
+	$( H^\prime_1,\tau^k_{H_1}) \simeq 
+	(H^\prime_2,\tau^k_{H_2})$
 \end{definition}
@@
 \begin{definition} \label{def:agreeability}
-	Let $H_1$ and $H_2$ be hypergraphs and let $r\in \N$.
+	Let $k,r\in\N$ and let $H_1$ and $H_2$ be hypergraphs.
 	Let $H^\prime_1:=Core(H_1;r)$ and $H^\prime_2:=Core(H_2;r)$. 
@@
 \begin{definition}
-	Let $\Sigma_{(k,r-1)}$ be the set of $\sim_k$ classes
-	of rooted trees with radii at most $r-1$. Then
+	Let $k,r\in\N$ and let $\Sigma_{(k,r)}$ 
+	be the set of $\sim_k$ classes
+	of rooted trees with radii at most $r$. Then
 	we call a $(k,r)$-\textbf{cycle} to an isomorphism class
-	of $\Sigma_{(k,r-1)}$-hypergraphs 
+	of $\Sigma_{(k,r)}$-hypergraphs 
 	$(H,\tau)$ that are cycles of diameter at most $2r+1$.
@@
 \begin{obs}\label{obs:agreeablecores}
-	Let $\mathcal{O}$ be a $\approx_{k,r}$ class
+	Let $k,r\in\N$ and let $\mathcal{O}$ be a $\approx_{k,r}$ class
 	of $r$-simple hypergraphs. 
@@
 	there are at least $k$ connected components $H \subset Core(G;r)$ whose cycle 		
-	$H^\prime=Center(H)$ satisfies that	$(H^{\prime},\tau_{H})\in \omega$, and
+	$H^\prime=Center(H)$ satisfies that	$(H^{\prime},\tau^k_{H})\in \omega$, and
 	(2) for any $\omega\in U^2_\mathcal{O}$ there are exactly $a_\omega$ 
 	connected components $H \subset Core(G;r)$ whose cycle 
-	$H^\prime=Center(H)$ satisfies that	$(H^{\prime},\tau_{H})\in \omega$.	
+	$H^\prime=Center(H)$ satisfies that	$(H^{\prime},\tau^k_{H})\in \omega$.	
 \end{obs}
@@
 \begin{definition} \label{def:rich}
-	Let $H$ be an hypergraph and let $r\in\N$. Let
+	Let $H$ be an hypergraph and let $k,r\in\N$. Let
 	$X\subset V(H)$ be the set of vertices in $H$
@@
 
-\subsection{Outline of the proof}
-
-We show now an outline of the proof of \cref{thm:main}. \par 
-The arguments are similar to the ones in the proof of
+\subsection{Main result and outline of the proof}
+Our goal is to prove the following theorem
+
+\begin{theorem} \label{thm:main}
+	Let $\phi$ be a sentence in $FO[\sigma]$. Then
+	the function
+	%$F_\phi: [0,1]^{t_u}\times (0,\infty)^{t-t_u}
+	$F_\phi: (0,\infty)^{|\sigma|}
+	\rightarrow \R$ given by 
+	\[
+	\InR{\beta} \mapsto \Ln Pr\left( G_n\left(
+	\{\beta_R\}_R\right) \models \phi\right)
+	\]
+	is well defined and analytic. 
+\end{theorem}
+In fact we prove something stronger. We show that the limit
+in last theorem is given by an expression with parameters $\{\beta_R\}_R$
+built using rational constants, sums, products and exponentiation with base $e$.
+We do so by giving a family of expressions which contains the ones that define 
+limit probabilities of FO properties in $G_n(\{\beta\}_R)$.  \par
+
+The main arguments are similar to the ones in the proof of
  \cite[Theorem 2.1]{lynch1992probabilities},
@@
 \begin{reptheorem}{thm:Duplicatorwins}
-	Let $H_1$, $H_2$ be hypergraphs. Let $r:=(3^k-1)/2$. Suppose
+	Let $k\in \N$ and let $H_1$, $H_2$ be hypergraphs. Set $r:=(3^k-1)/2$. Suppose
 	that both $H_1$ and $H_2$ are $(k,r)$-rich and
@@
 \begin{theorem}\label{thm:DuplicatorAux}
-	Set $r=(3^k-1)/2$.
+	Let $k\in \N$.
+	Set $r:=(3^k-1)/2$.
 	Suppose there exist
@@
 \begin{obs} \label{obs1}
-	Let
+	Let $k\in \N$ and let
 	$\overline{v}\in V(H_1)^*$, $\overline{u}\in V(H_2)^*$ be of equal length. Suppose
@@
 \begin{obs} \label{obs2}
-	Let
+	Let $k\in \N$ and let
 	$\overline{v}\in V(H_1)^*$, $\overline{u}\in V(H_2)^*$ be of equal length. Suppose 
@@
 \begin{lemma} \label{lemm:Duplicator}
-	Let $\overline{v}\in V_1^*$ and
-	$\overline{u} \in V_2^*$ be of equal length. Let
-	$r\in \N$ be greater than zero. Suppose
+	Let $k,r\in \N$. Let $\overline{v}\in V_1^*$ and
+	$\overline{u} \in V_2^*$ be of equal length.
 	$(H_1,\overline{v})\simeq_{k,3r+1} (H_2,\overline{u})$.
@@
 
-	% During the game
-%	Duplicator will track of sets of lists $L^1[i]$'s
-%	and $L^2[i]$'s. At the end of the $i$-th round
-%	Duplicator will obtain $L^1[i]$, resp $L^2[i]$
-%	performing one of the following operations on 
-%	$L^1[i-1]$, resp $L^2[i-1]$:
-%	\begin{itemize}
-%		\item Adding a list $\overline{v}\in (V_1)^*$
-%		to $L^1[i-1]$ and marking it with the index $i$. 
-%		\item Appending a new vertex $v\in V_1$ to an 
-%		existing list $\overline{v}\in L^1[i-1]$.
-%	\end{itemize}	
-%	Let $r_k=1$ and for each $i\in [k-1]$ 
-%	let $r_i=3r_{i+1}+1$.
-%	We are going to show that Duplicator can 
-%	play in a way such that
-%	at the end of the $i$-th 
-%	round the following conditions
-%	are satisfied:
-%	\begin{itemize}
-%		\item[(1)] 
-%		
-%		
-%		
-%	\end{itemize}
-%	
-%	
-%	\[\mathcal{X}(0,\infty]=\emptyset,
-%	\quad \mathcal{Y}(0,\infty]=\emptyset.\]
-%	At the end of the $s$-th round $\mathcal{X}[s-1]$,
-%	resp. $\mathcal{Y}[s-1]$, will be updated into 
-%	$\mathcal{X}[s]$,
-%	resp. $\mathcal{Y}[s]$, by performing on it
-%	some of the following operations: adding a new list
-%	to it, appending one vertex to an existing list, and 
-%	marking a list with the index $s$. Duplicator will
-%	keep track of the sets $\mathcal{X}[s]$ and $\mathcal{Y}[s]$.\par
-%	
-%	We show first an strategy for Duplicator and will prove its
-%	correctness afterwards. The strategy is as follows: At the 
-%	beginning of the $s$-th round suppose Spoiler plays $w_s$ in
-%	$G^1$. The case where they play $z_s$ in $G^2$ is symmetric.
-%	Call $r=r_{k-s}$. There are three possibilities. 
-%	\begin{itemize}
-%		\item[Case 1:] The vertex $w_s$ satisfies
-%		$d(w_s,\overline{v})>2r+1$ for all 
-%		$\overline{v}\in \mathcal{X}[s-1]$. Then Duplicator 
-%		can find a vertex $z_s$ in $G^2$ such that
-%		$d(z_s,\overline{u})>2r+1$ for all 
-%		$\overline{u}\in \mathcal{Y}[s-1]$ satisfying 
-%		that $w_s$ and $z_s$ have $(k-s)$-similar
-%		$r$-neighborhoods. To form $ \mathcal{X}[s]$
-%		and $ \mathcal{Y}[s]$, add to $\mathcal{X}[s-1]$
-%		and $ \mathcal{Y}[s-1]$ the lists consisting
-%		of only $w_s$ and only $z_s$ respectively, and mark
-%		them with the number $s$.
-%		
-%		\item[Case 2:] The vertex $w_s$ satisfies
-%		$d(w_s,\overline{v})\leq 2r+1$ for a unique 
-%		$\overline{v}\in \mathcal{X}[s-1]$,and
-%		$\overline{v}$ is marked. In this case,
-%		find the list $\overline{u}\in \mathcal{Y}[s-1]$
-%		with the same mark. Duplicator 
-%		then can chose $z_s\in N(\overline{u},2r+1)$
-%		in response to $w_s$ according to a winning strategy
-%		for
-%		\[
-%		d\ehr_{k-s}(N(\overline{v},3r+1),\overline{v},
-%		N(\overline{u},3r+1),\overline{u}).
-%		\]
-%		To form $ \mathcal{X}[s]$
-%		and $ \mathcal{Y}[s]$, append $w_s$ and $z_s$
-%		to $\overline{v}$ and $\overline{u}$ respectively.
-%		
-%		\item[Case 3:] The vertex $w_s$ satisfies
-%		$d(w_s,\overline{v})\leq 2r+1$ for a unique 
-%		$\overline{v}\in \mathcal{X}[s-1]$,and
-%		$\overline{v}$ is not marked. In this case we 
-%		can	find a non-marked 
-%		list $\overline{u}\in \mathcal{Y}[s-1]$
-%		such that $\overline{v}$ and $\overline{u}$ 
-%		have $(k-s)$-similar $(3r+1)$-neighborhoods. 
-%		Duplicator then can chose $z_s\in N(\overline{u},2r+1)$
-%		in response to $w_s$ according to a winning strategy
-%		for
-%		\[
-%		d\ehr_{k-s}(N(\overline{v},3r+1),\overline{v},
-%		N(\overline{u},3r+1),\overline{u}).
-%		\]
-%		To form $ \mathcal{X}[s]$
-%		and $ \mathcal{Y}[s]$, append $w_s$ and $z_s$
-%		to $\overline{v}$ and $\overline{u}$ respectively,
-%		and mark those lists with the number $s$. 
-%	\end{itemize}
-%	
-%	All that is left now is to prove the correctness of the
-%	strategy. We show that at the end the $s$-th round, if 
-%	two lists $\overline{v} \in \mathcal{X}[s]$ and 
-%	$\overline{u} \in \mathcal{Z}[s]$ have the same mark then
-%	$\overline{v}$ and $\overline{u}$ have $(k-s)$-similar
-%	$r_{k-s}$-neighborhoods. This happens trivially at
-%	the end of the zeroth round -i.e., the beginning 
-%	of the game- as there are no marked lists. Assume the
-%	statement holds up to the end of the $(s-1)$-th round, 
-%	where $s>0$. 
-%	
-%	\begin{itemize}
-%		\item[Case 1:] Notice that the lists
-%		in $\mathcal{Y}[s-1]$ only contain the
-%		vertices previously played in $G^2$ and 
-%		the ones from $Y$. Thus, assumption $(3)$ 
-%		of the theorem, (or assumption $(2)$ in the 
-%		symmetric
-%		case where Spoiler plays in $G^2$) assures us
-%		that Duplicator can always find such $z_s$ 
-%		sufficiently far away from all the other lists. 
-%		In this case, the only new marked lists in $\mathcal{X}[s]$
-%		and $\mathcal{Y}[s]$ are the ones
-%		consisting of $w_s$ and $z_s$ respectively. By assumption
-%		$w_s$ and $z_s$ have $(k-s)$-similar $r_{k-s}$-neighborhoods.
-%		
-%		\item[Case 2:] Notice that by the induction hypothesis 
-%		$\overline{v}$ and $\overline{u}$ have $(k-s+1)$-similar
-%		$r_{s-k+1}$-neighborhoods, and in consequence a winning strategy
-%		for Duplicator exists. Using \cref{lemm:Duplicator} we obtain 
-%		that the extended lists $\overline{v},w_s$ and $\overline{u},z_s$
-%		have $(k-s)$-similar $r_{s-k}$-neighborhoods. 	
-%		
-%		\item[Case 3:] This case is analogous to the previous one.
-%		The definition of $k$-agreeability implies that there is 
-%		such an unmarked list $\overline{u}$ available. Using \cref{lemm:Duplicator} 
-%		we obtain 
-%		that the extended lists $\overline{v},w_s$ and $\overline{u},z_s$
-%		have $(k-s)$-similar $r_{s-k}$-neighborhoods.	
-%	\end{itemize} 
-%	
-%	In the three cases, if $\overline{v}$ and $\overline{v}$
-%	are lists in $\mathcal{X}[s-1]$ and $\mathcal{Y}[s-1]$
-%	respectively that share the same mark and remain unmodified
-%	in $\mathcal{X}[s]$ and $\mathcal{Y}[s]$, then by the 
-%	induction hypothesis $\overline{v}$ and $\overline{v}$
-%	have $(k-s+1)$-similar $r_{k-s+1}$-neighborhoods. This
-%	easily implies that they also have
-%	$(k-s)$-similar $r_{k-s}$-neighborhoods.\par
-%	At the end of the game, if $\overline{v}\in \mathcal{X}[k]$ and 
-%	$\overline{u}\in \mathcal{Y}[k]$ are lists with the same mark
-%	then the natural mapping between $\overline{v}$ and $\overline{u}$
-%	defines an isomorphism between $G^1[\overline{v}]$ and $G^2[\overline{u}]$.
 \end{proof}
 
-\subsection{k-Equivalence relation}
-
-\subsubsection{k-Equivalent trees} \label{sect:equivtrees}
+\subsection{k-Equivalent trees} \label{sect:equivtrees}
 
@@
 \begin{theorem} \label{thm:equivalenttrees} 
+	Let $k\in \N$. 
 	Let $(T_1,v_1)$ and $(T_2,v_2)$ be rooted trees such
@@
 \begin{lemma} \label{lem:equivalentedges}
-	Fix $r>0$. Suppose theorem \ref{thm:equivalenttrees}
+	Let $k\in \N$ and fix $r>0$. Suppose theorem \ref{thm:equivalenttrees}
 	holds for rooted trees with radii at most $r$.
 	Let $(T_1,v_1)$ and $(T_2,v_2)$ be rooted trees with radius
-	$r+1$. Let $\tau_{(T_1,v_1)}$ and $\tau_{(T_2,v_2)}$
-	be colorings over $T_1$ and $T_2$ as in the
-	definition of $k$-equivalence. 
+	$r+1$. Let $\tau^k_{(T_1,v_1)}$ and $\tau^k_{(T_2,v_2)}$
+	be colorings over $T_1$ and $T_2$ as in \cref{def:sim_trees}
 	Let $e_1$ and $e_2$ be initial edges 
 	of $T_1$ and $T_2$ respectively satisfying 
-	$(e_1,\tau_{(T_1,v_1)})\simeq (e_2,\tau_{(T_2,v_2)})$. Name 
+	$(e_1,\tau^k_{(T_1,v_1)})\simeq (e_2,\tau^k_{(T_2,v_2)})$. Name 
 	$T^\prime_1:=\mathrm{Tr}(T_1,v_1; \,\,e_1)$ and 
@@
 	$f:V(e_1)\rightarrow V(e_2)$ an isomorphism between 
-	$(e_1,\tau_{(T_1,v_1)})$
-	and $(e_2,\tau_{(T_2,v_2)})$.
+	$(e_1,\tau^k_{(T_1,v_1)})$
+	and $(e_2,\tau^k_{(T_2,v_2)})$.
 	Suppose in the $i$-th round of the game Spoiler
@@
 	$T^{\prime\prime}_2:=\mathrm{Tr}\left(T^\prime_2,v_2;\,\, f(u)\right)$
-	Then, as $\tau_{(T_1,v_1)}\left(u\right)=\tau_{(T_2,v_2)}\left(f(u)\right)$,
+	Then, as $\tau^k_{(T_1,v_1)}\left(u\right)=\tau^k_{(T_2,v_2)}\left(f(u)\right)$,
 	we obtain
@@
 	statement is true for all lesser values of $r$.
-	Let $\tau_{(T_1,v_1)}$ and $\tau_{(T_2,v_2)}$ 
+	Let $\tau^k_{(T_1,v_1)}$ and $\tau^k_{(T_2,v_2)}$ 
 	be the colorings over $T_1$ and $T_2$ as in 
-	the definition of $\sim_k$. 
+	\cref{def:sim_trees}. 
 	We show that there is a winning strategy 
@@
 		edge $e_2$ in $T_2$ satisfying 
-		$\left(e_1,\tau_{(T_1,v_1)}\right)\simeq
-		\left(e_2,\tau_{(T_2,v_2)}  \right)$.
+		$\left(e_1,\tau^k_{(T_1,v_1)}\right)\simeq
+		\left(e_2,\tau^k_{(T_2,v_2)}  \right)$.
 		Mark $e_2$ as well. 
@@
 		marked during the same round as $e_1$ and it satisfies 
-		$\left(e_1,\tau_{(T_1,v_1)}\right)\simeq
-		\left(e_2,\tau_{(T_2,v_2)}  \right)$.	
+		$\left(e_1,\tau^k_{(T_1,v_1)}\right)\simeq
+		\left(e_2,\tau^k_{(T_2,v_2)}  \right)$.	
 		Again, because of \cref{lem:equivalentedges}, 
@@
 
-\subsubsection{k-Equivalent hypergraphs} \label{sect:equivunicycles}
+\subsection{k-Equivalent hypergraphs} \label{sect:equivunicycles}
 
@@
 		Set $H^\prime_1:= Center(H_1)$ and 
-		$H^\prime_2:= Center(H_2)$. Let $f$ be an isomorphism
-		between $\left( H^\prime_1,\tau_{H_1}\right)$ and 
-		$\left(H^\prime_2,\tau_{H_2}\right)$. Let $\overline{v}$ 
+		$H^\prime_2:= Center(H_2)$. Let 
+		$\tau^k_{H_1}, \tau^k_{H_2}$ be as in
+		\cref{def:sim_general}.
+		Let $f$ be an isomorphism
+		between $( H^\prime_1,\tau^k_{H_1})$ and 
+		$(H^\prime_2,\tau^k_{H_2})$. Let $\overline{v}$ 
 		be an ordering of the vertices of $H^\prime_1$ and let
@@
 
-\subsection{$r$-Cores} \label{sec:Core}
+\subsection{Main result} \label{sec:Core}
 
 \begin{lemma} \label{lem:aux1}
-	Let $r\in \N$ and let $H_1, H_2$ be hypergraphs such that 
+	Let $k,r\in \N$ and let $H_1, H_2$ be hypergraphs such that 
 	$H_1\approx_{k,r} H_2$. Let $X$ and $Y$ be the
@@
 	a connected component of $Core(H_1;r)$, resp. $Core(H_2;r)$.
-	Using the definition of $H_1\approx_{k,r}H_2$ as well 
-	as the fact that  because of \cref{thm:strategyaux}
+	Because of \cref{thm:strategyaux}
 	$N(X_i;r)\sim_k N(Y_j;r)$ implies 
-	$(H_1,X_i)\simeq_{k,r} (H_2,Y_j)$
-	the result follows.	
+	$(H_1,X_i)\simeq_{k,r} (H_2,Y_j)$ in the sense of
+	\cref{def:similar}. The result follows now from
+	 the definition of $H_1\approx_{k,r}H_2$.	
 \end{proof}
@@
 \begin{theorem}\label{thm:Duplicatorwins}
-	Let $H_1$, $H_2$ be hypergraphs. Let $r:=(3^k-1)/2$. Suppose
+	Let $k\in \N$, and set $r:=(3^k-1)/2$.
+	Let $H_1$, $H_2$ be hypergraphs.
+	Suppose
 	that both $H_1$ and $H_2$ are $(k,r)$-rich and
@@
 		\cref{thm:DuplicatorAux} with $X\subset V(H_1)$ 
-		and	$Y\subset V(H_2)$ the sets of vertices that belong
-		to some saturated sub-hypergraph of $H_1$ or $H_2$ respectively
-		with diameter at most $2r+1$.
+		and	$Y\subset V(H_2)$ defined as before. The
+		hypothesis of $(k,r)$-richness on both $H_1, H_2$ ensures that
+		condition (2) in the statement of \cref{thm:DuplicatorAux}
+		holds. 
 	\end{proof}
@@
 \[
-\PR{H^\prime \subset G_n}= \prod_{R\in \sigma} \left(\frac{\beta_R}{n^{ar(R)-1}} 
+\PR{H^\prime \subset G_n}\sim \prod_{R\in \sigma} \left(\frac{\beta_R}{n^{ar(R)-1}} 
 \right)^{|E_R(H)|}.
@@
 \[
-\mathrm{E}\big[X_n\big]=
+\mathrm{E}\big[X_n\big]\sim 
 \frac{(n)_{|H|}}{\aut(H)}\cdot
@@
 	It holds that the number of hypergraphs $H^\prime \in Copies(H,[n])$
-	that contain all vertices in $\overline{v}$ is
-	 $\Theta\left(n^{|V(H)|-len(\overline{v})}\right)$. Then for
-	 some constant $C$,
+	that contain all vertices in $\overline{v}$ is asymptotically
+	$\sim n^{|V(H)|-len(\overline{v})}$ for
+	some constant $C$. Then,
 	\[
@@
 	Define $G_n^\prime=G_n \setminus E[\overline{v}]$ (i.e. $G_n$ minus all the
-	edges induced over $\overline{v}$). Fix $R\in \N$. 
-	Let $A_n$ be the event that $G^\prime_n$ contains a path of 
-	length	at most	$R$ between any two vertices $u,w\in \overline{v}$.
-	Let $B_n$ be the event
-	that $G^\prime_n$ contains a cycle of diameter at most $R$
-	at distance at most $R$ to some vertex $u\in \overline{v}$.
-	Then 
-	\[
-	\Ln \mathrm{Pr}\left(A_n \, | \, \pi(\overline{v})\right)=0, \quad 
-	\text{ and } 
-	\Ln \mathrm{Pr}\left(B_n \, | \, \pi(\overline{v})\right)=0.\] 
+	edges induced over $\overline{v}$). Fix $r\in \N$. 
+	Then a.a.s for all vertices $v\in \overline{v}$ the neighborhoods
+	$N^{G^\prime_n}(v;\,r)$'s are disjoint trees.  
 \end{lemma}
 \begin{proof}
-	Notice that the events $A_n$ and $B_n$ do not concern the possible edges
+	Let $A_n$ be the event that the $N^{G^\prime_n}(v;\,r)$'s are disjoint trees.  
+	Notice that $A_n$ does not concern the possible edges
 	induced over $\overline{v}$. In consequence, because edges are independent
@@
 	$\mathrm{Pr}\left(A_n \, | \, \pi(\overline{v})\right)
-	=\mathrm{Pr}(A_n)$ and 
-	$\mathrm{Pr}\left(B_n \, | \, \pi(\overline{v})\right)
-	=\mathrm{Pr}(B_n)$. Now
-	both limits from the statement follow from 
+	=\mathrm{Pr}(A_n)$. Now the result follows from 
 	\cref{lem:disjointtrees} using that $G^\prime_n\subset G_n$.  
 \end{proof}
-
-\subsection{Convergence to Poisson variables}
-
-Our main tool for computing probabilities in the following sections
-will be the next result, which can
-be found in \cite[Theorem 1.23]{bollobas2001random}.
-
-\begin{theorem} \label{thm:BrunSieve}
-	Fix $k\in \N$. For each 
-	$n\in \N$, let $X_{n,1},\dots, X_{n,l}$ be non-negative
-	random integer variables over the same
-	probability space. Let $\lambda_1,\dots,\lambda_l$ 
-	be real numbers. Suppose for any $r_1,\dots,r_l \in \N$
-	\[ 
-	\Ln \mathrm{E}\left[
-	\prod_{i=1}^{l} \binom{X_{n,i}}{r_i} \right]
-	= \prod_{i=1}^{l} \frac{\lambda_i}{r_i !}.	
-	\]
-	Then the $X_{n,1},\dots,X_{n,l}$ converge in distribution to
-	independent Poisson variables with means $\lambda_1,\dots,\lambda_l$ 
-	respectively. 
-\end{theorem}
-
-We will use the following observation in order to compute the binomial moments of 
-our random variables.
-
-\begin{obs} \label{obs:binomialmean} Let $X_1,\dots, X_l$ be non negative
-	random integer variables over the same space. 
-	Let $r_1,\dots,r_l\in \N$.	Suppose
-	each $X_i$ is the sum of various indicator random variables
-	(i.e. variables that only take the values $0$ and $1$)
-	$X_i=\sum_{j=1}^{a_i} Y_{i,j}$. Define 
-	$\Omega:=\prod_{i=1}^l \binom{[a_i]}{r_i}$. That is,
-	the elements $\{S_i\}_{i\in[l]}\in \Omega$
-	represent all the possible unordered choices of 
-	$r_i$ indicator variables $Y_{i,j}$ for each $i\in [l]$.
-	Then 
-	\[
-	\mathrm{E}\left[
-	\prod_{i=1}^{l} \binom{X_i}{r_i}\right]=
-	\sum_{\{S_i\}_{i\in [l]}} \mathrm{Pr}\left(
-	\bigwedge_{\substack{i\in [l]\\ j\in S_i}} Y_{i,j}=1
-	\right).	
-	\]
-\end{obs}
 
@@
 \begin{theorem} \label{thm:BigTrees}
-	Fix $r\in \N$. The following are satisfied:
+	Fix $r\in \N$. Let $k\in \N$ The following are satisfied:
 	\begin{itemize}
@@
 \begin{definition}
-	Let $r\in \N$ be a positive number and
-	suppose that \cref{thm:BigTrees} holds for $r-1$.
+	Let $k\in \N$ and $r>0$. 
+	Suppose that \cref{thm:BigTrees} holds for $r-1$.
 	Given a $(k,r)$-pattern $\epsilon$ we define the expressions
@@
 \begin{lemma}\label{lem:poisedges}
-	Let $r>0$ and $\overline{u}\in (\N)_*$.
+	Let $k\in \N$, $r>0$ and $\overline{u}\in (\N)_*$.
 	Let $\pi(\overline{x})\in FO[\sigma]$ be a consistent
@@
 	the number of initial edges $e\in E(T_{n,v})$ such 
-	that $(e,\tau_{(T_{n,v},v)})\in \epsilon$. Suppose that
+	that $(e,\tau^k_{(T_{n,v},v)})\in \epsilon$. Suppose that
 	\cref{thm:BigTrees} holds for $r-1$. Then the conditional 
@@
 \begin{lemma} \label{lem:singletreeprob}
-Let $r\in \N$, $r>0$. Suppose that \cref{thm:BigTrees}
+Let $r>0$. Suppose that \cref{thm:BigTrees}
 holds for $r-1$. Then it also holds for $r$. 
@@
 \begin{proof}
+Fix $k\in \N$. 
 We start showing condition (1) of \cref{thm:BigTrees}.
@@
 \begin{theorem}\label{thm:rich}
-	Let $r\in \N$. Then a.a.s $G_n$ is $(k,r)$-rich.
+	Let $k,r\in \N$. Then a.a.s $G_n$ is $(k,r)$-rich.
 \end{theorem}
@@
 
-\begin{definition} Let $r\in \N$ and $O\in C(k,r)$.
+\begin{definition} Let $k,r\in \N$ and $O\in C(k,r)$.
 	Let $(H,\tau)$ be
@@
 \begin{lemma}
-	Let $r\in \N$. For any $O\in C(k,r)$ let $X_{n,O}$ be
+	Let $k,r\in \N$. For any $O\in C(k,r)$ let $X_{n,O}$ be
 	the random variable that counts the connected components
 	$H$ of $Core(G_n;\, r)$ such that $H^\prime:=Center(H)$
-	satisfies that $(H^\prime, \tau_{H})\in O$. Then the variables
+	satisfies that $(H^\prime, \tau^k_{H})\in O$. Then the variables
 	$X_{n,O}$'s converge in distribution to independent 
@@
 \begin{theorem}\label{thm:agreeabilityprobabilities}
-	Let $r\in \N$ and let $\mathcal{O}$ be a simple $(k,r)$-agreeability class
+	Let $k,r\in \N$ and let $\mathcal{O}$ be a simple $(k,r)$-agreeability class
 	of hypergraphs. Then 
@@
 	\Ln \mathrm{Pr} \left(
-	G_n\left(\{\beta_R\}_{R\in \sigma}\right) \models \phi
+	G_n\left(\{\beta_R\}_{R}\right) \models \phi
 	\right)
@@
 
-\section{Application to random SAT}
+\section{Application to random SAT}\label{sec:SAT}
 
@@
 $x$ and $\neg x$ are called \textbf{literals}. A \textbf{clause}
-is a set of literals. A clause $C$ is called \textbf{ordinary}
+is a set of literals. A clause $C$ is called \textbf{non-tautological}
 if no variable $x$ satisfies that both $x$ and $\neg x$
@@
 Given a natural number $l\in\N$
-a $l$-\textbf{CNF formula} is a set of  ordinary clauses 
+a $l$-\textbf{CNF formula} is a set of  non-tautological clauses 
 that contain exactly $l$ literals. 
@@
 Equivalently, a random formula in $F(l,n,p)$ is obtained
-by choosing each one of the $2^l\binom{n}{l}$ normal 
+by choosing each one of the $2^l\binom{n}{l}$ non-tautological
 clauses of size $l$ over the variables $\{x_i\}_{i}$
-with probability $p$ independently. \par	
+with probability $p$ independently. When
+$p$ is a function of $n$ satisfying
+$p(n)\sim \beta/n^{l-1}$ we denote by $F_n(\beta)$ a random sample
+of $F(l,n,p(n))$.
+\par	
 We consider $l$-CNF formulas, as defined above, as relational 
@@
 	Let $l>1$ be a natural number.
-	For each $n\in \N$ let $F_n(\beta)$ be a random formula from
-	$F(l,n,\beta/n^{l-1})$. Then for each sentence $\Phi\in FO[\sigma]$ 
+	Then for each sentence $\Phi\in FO[\sigma]$ 
 	it is satisfied
@@
 be clauses chosen uniformly at random independently among the 
-$2^l \binom{n}{l}$ ordinary clauses of size $l$ over the
+$2^l \binom{n}{l}$ non-tautological clauses of size $l$ over the
 variables $x_1,\dots, x_n$. For each $n$, let $UNSAT_n$
@@
 $x_1,\dots,x_n$ that satisfies all clauses $C_{n,1},\dots, C_{n,m(n)}$. 
-Then there are two real constants $0<c_1<c_2$, independent of such that 
+Then there are two real constants $0<c_1<c_2$, such that 
 a.a.s $UNSAT_n$ does not hold if $c< c_1$, and a.a.s $UNSAT_n$ holds
@@
 The fact that $c_2$ exists follows from a direct application of
-the first order method and is also shown in \cite{chvatal1992mick}, as well as 
+the first moment method and is also shown in \cite{chvatal1992mick}, as well as 
 \cite{franco1983probabilistic}, \cite{chvatal1988many}, \cite{simon1986etude}
@@
 	For each $n\in \N$ let $F_{n,m(n)}$ be a random formula chosen uniformly at
-	random among all the sets of $m(n)$ ordinary clauses of size $l$ over
+	random among all the sets of $m(n)$ non-tautological clauses of size $l$ over
 	the variables $x_1,\dots, x_n$. Then there
@@
 \begin{theorem} \label{thm:satapplication}
-	Let $l>1$ be a natural number.
-	For each $n\in \N$ let $F_n(\beta)$ be a random formula from
-	$F(l,n,\beta/n^{l-1})$. Let $\Phi\in FO[\sigma]$ be a first order
+	Let $l>1$ be a natural number. Let $\Phi\in FO[\sigma]$ be a first order
 	sentence that implies unsatisfiability.  Then for all $\beta\in (0,\infty)$
@@
 
+\bibliographystyle{abbrvnat}
 \bibliography{biblio}
-\bibliographystyle{unsrt}	
+
 \end{document}

### 2020-06-25 ArticleAcortadobackup.tex
Final

--- 2020-06-07 ArticleAcortado.tex
@@
 \usepackage{chngcntr}
-\usepackage{cleveref}
+\usepackage[noabbrev]{cleveref}
 \usepackage{pdfpages}
@@
 \setlength{\evensidemargin}{\margen}
-\setlength{\abovedisplayskip}{3pt}
-\setlength{\belowdisplayskip}{3pt}
+\setlength{\abovedisplayskip}{2pt}
+\setlength{\belowdisplayskip}{2pt}
 %%%% Small setup %%%%
@@
 }
-\setlength{\parskip}{0.2cm}
+\setlength{\parskip}{0.1 cm}
 %%%%%%%%%%%%%%%
@@
 \newcommand{\N}{\mathbb{N}}
-\newcommand{\Hc}{\mathcal{H}}
+\newcommand{\Hc}{\mathbf{H}}
 \newcommand{\Lan}{\mathcal{L}}
 \newcommand{\Ln}{\lim\limits_{n\to \infty}}
-\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
+\newcommand{\clist}{\mathfrak{c}_{1},  s, \mathfrak{c}_m}
 \newcommand{\morph}[1]{\sim_#1}
@@
 \newcommand{\aut}{\mathrm{aut}}
-
+\newcommand{\len}{\mathrm{len}}
+\newcommand{\qr}{\mathrm{qr}}
+\newcommand{\ex}{\mathrm{ex}}
 \DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
@@
 We say that a sequence of random structures $\{G_n\}_n$ satisfies a limit
-law with respect to some logical language $L$ if for any property $P$ expressible in
-$L$ the probability that $G_n$ satisfies $P$ tends to some limit as $n$ goes to $\infty$.
+law with respect to some logical language $L$ if for every property $P$ expressible in
+$L$ the probability that $G_n$ satisfies $P$ tends to some limit as $n \to \infty$.
 If that limit takes only the values zero and one then we say that $\{G_n\}_n$ satisfies
 a zero-one law with respect to $L$.  \par
-Convergence and zero one laws have been extensively studied with regards to 
-random binomial graphs $G(n,p)$.
+Convergence and zero one laws have been extensively studied on the binomial graph $G(n,p)$.
 The seminal theorem on this topic, due to Fagin \cite{fagin1976probabilities}
@@
 concerns general relational structures.
-When applied to graphs it states that if $p$ is a fixed probability
+When applied to graphs it states that if $p$ is fixed,
 then $G(n,p)$ satisfies a zero-one law with respect to the first order
@@
 in \cite{shelah1988zero}. There it is proven, among other results,
-that if $p:=p(n)$ was a decreasing function on
-$n$ of the form $n^{-\alpha}$, and $\alpha>0$ is irrational
+that if $p:=p(n)$ is a decreasing function on
+$n$ of the form $n^{-\alpha}$ and $\alpha>0$ is irrational,
 then $G(n,p(n))$ obeys a zero-one law with respect to FO logic. Moreover, 
@@
 in \cite{lynch1992probabilities}, where it is shown that in the
-case where the expected number of edges is linear, when $p(n)\sim \beta/n$
-for some $\beta\in (0,\infty)$, then $G(n,p(n))$ satisfies a limit law with
-respect to FO logic. The following is a restatement of the main theorem
+case where the expected number of edges is linear, i.e. when $p(n)\sim \beta/n$
+for some $\beta >0$, then $G(n,p(n))$ satisfies a limit law with
+respect to FO logic. The following is a restatement of the main result
 in that article.
@@
 \begin{theorem*}[Lynch, 1992]
-	Let $p(n)\sim \beta/n$. For any FO sentence $\phi$, the function
+	Let $p(n)\sim \beta/n$. For every FO sentence $\phi$, the function
 	$F_\phi: (0,\infty)\rightarrow [0,1]$ given by 
@@
 property in $G(n,p(n))$ when $p(n)\sim \beta/n$ varies analytically with $\beta$.
-A consequence of this is that in these conditions no FO property can "capture" sudden changes 
+A consequence of this is that FO logic cannot "capture" sudden changes 
 in the structure of $G(n,p(n))$. \par
@@
 among other zero-one and convergence laws.
-There $G^d(n,p)$ is considered, the random model of $d$-uniform hypergraphs where
+There is considered the random model of $d$-uniform hypergraphs $G^d(n,p)$ where
 each $d$-edge is added to a set of $n$ labeled vertices with probability $p$ independently.
-It is shown that when $p(n)\sim \beta/n^{d-1}$ -i.e., when the expected number of
-edges is linear- then $G^d(n,p(n))$ obeys a convergence law with respect of the FO
+It is shown that when $p(n)\sim \beta/n^{d-1}$, i.e. when the expected number of
+edges is linear, then $G^d(n,p(n))$ obeys a convergence law with respect to the FO
 language of $d$-uniform hypergraphs. With little additional work it can be shown that
@@
 extend this result to arbitrary relational structures
-to whose relations we can impose symmetry and anti-reflexivity constraints 
-(\cref{thm:main}). \par
+on whose relations we can impose symmetry and anti-reflexivity constraints 
+(\Cref{thm:main}). \par
 
 This generalization is motivated by an application to the problem of random 
-satisfiability. We continue the study started by Atserias in 
+SAT. We continue the study started by Atserias in 
 \cite{atserias2005definability}
@@
 in \cite{chvatal1992mick} that a random $k$-CNF formula with
-$m$ clauses over $n$ variables satisfying that $m\sim c\cdot n$ 
+$m$ clauses over $n$ variables satisfying that $m\sim c  n$ 
 is a.a.s satisfiable for all sufficiently small values of $c$ and is a.a.s
@@
 using a generalization of Lynch's theorem was suggested by Atserias. 
-This application is discussed in \cref{sec:SAT}. We give a brief overview
+This application is discussed in \Cref{sec:SAT}. We give a brief overview
 of it here. Let $F(l,n,p)$ be a random model of $l$-CNF 
@@
 
-Given a positive natural number $n$, we will write
-$[n]$ to denote the set ${1,2,\dots,n}$.\par
+Given a positive natural number $n$, we write
+$[n]$ to denote the set ${1,2,\dots,n}$.
 Given numbers, $n,m\in \N$ with $m\leq n$ we denote by
-$(n)_m$ the $m$-th falling factorial of $n$. \par
+$(n)_m$ the $m$-th falling factorial of $n$. 
 Given a set $S$ and a natural number $k\in \N$
-we will use $\binom{S}{k}$ to denote the set of 
-subsets of $S$ whose size is $k$.Given a set
-$S$ and a number $n\in \N$ with $n\leq |S|$ we define
+we use $\binom{S}{k}$ to denote the set of 
+subsets of $S$ of size $k$.Given a set
+$S$ and $n\leq |S|$, we define
 $(S)_n$ as the subset of $S^n$ consisting of the $n$-tuples
@@
 
-We will use the convention that over-lined variables
-, like $\overline{x}$, denote ordered tuples of arbitrary length.
+We use the convention that over-lined variables, 
+like $\overline{x}$, denote ordered tuples of arbitrary length.
 Given an ordered tuple $\overline{x}$
-we define the number $len(\overline{x})$ as its length. 
+we definer $\len(\overline{x})$ as its length. 
 Given a tuple $\overline{x}$ and an element $x$ the expression
@@
 in $\overline{x}$. 
-Given a map $f:X\rightarrow Y$ between two sets $X, Y$ and 
+Given a map $f:X\rightarrow Y$ and 
 an ordered tuple $\overline{x}:=(x_1,\dots,x_a)\in X^*$ 
@@
 concatenation. Given a set $S$ and elements $x_s$ for each $s\in S$
-we will write $\{x_s\}_{s\in S}$, or just $\{x_s\}_s$ when $S$ is understood,
-to denote the tuple indexed by $S$ which for any $s\in S$
+we write $\{x_s\}_{s\in S}$, or just $\{x_s\}_s$ when $S$ is understood,
+to denote the tuple indexed by $S$ which
 contains the element $x_s$ at the position given by $s$. 
 \par
-
 Let $S$ be a set, $a$ a positive natural number, 
 and $\Phi$ a group of permutations over 
-$[a]$. Then $\Phi$ acts naturally over
+$[a]$. Then $\Phi$ acts naturally on
 $S^a$ in the following way: Given $g\in \Phi$ and
-$\overline{x}:=(x_1,\dots,x_a)\in S^a$ we define 
-$g\cdot \overline{x}$ 
-as the tuple $(x_{g(1)},\dots,x_{g(a)})$. 
-We will denote by $S^a/\Phi$ to the quotient
-of the set $S^a$ by this action. Given an element
+$\overline{x}:=(x_1,\dots,x_a)\in S^a$ let 
+$g  \overline{x}:=(x_{g(1)},\dots,x_{g(a)})$. 
+We denote by $S^a/\Phi$ the quotient
+of $S^a$ by this action. Given
 $\overline{x}:=(x_1,\dots, x_a)\in S^a$ we denote its equivalence
 class in $S^a/\Phi$ by $[x_1,\dots,x_a]$ or $[\overline{x}]$.
-Thus, for any
+Thus, for
 $g\in \Phi$, by definition $[x_1,\dots,x_a]=[x_{g(1)}
@@
 $[x_1,\dots,x_a]$ denote ordered tuples modulo the
-action of some arbitrary group of permutations. Which group is
-this will depend on the ambient set where $[x_1,\dots,x_a]$ belongs
+action of some arbitrary group of permutations. Which group it is
+will depend on the ambient set where $[x_1,\dots,x_a]$ belongs
 and it should either be clear from context or not be relevant.\par
@@
 $f,g:\N \rightarrow \R$ the expressions $f=O(g)$,
-$f=o(g)$ and $f=\Theta(g)$ will have their usual meaning.
-If $g(n)\neq 0$ for $n$ large enough then
-we will write $f\sim g$ when $\Ln \frac{f(n)}{g(n)}=1$. \par
+$f=o(g)$ and $f=\Theta(g)$ have their usual meaning.
+If $g(n)\neq 0$ for $n$ large enough 
+we write $f\sim g$ if $\Ln \frac{f(n)}{g(n)}=1$. \par
 
@@
 We define $\mathrm{Poiss}_\lambda(\geq n)=1 - \sum_{i=0}^{n-1} \mathrm{Poiss}_\lambda(i)$. \par
+Given some sequence of events $\{A_n\}_n$ we say that $A_n$ is 
+satisfied asymptotically
+almost surely (a.a.s.) if $\Pr(A_n)$ tends to $1$ as $n\to \infty$.\par
+Given a sequence of random variables $\{X_n\}_n$, the \textbf{first moment method}
+is an application of Markov's inequality that establishes that if $\mathrm{E}[X_n]$
+tends to zero as $n\to \infty$ then a.a.s $X_n=0$.\par
 
@@
 
-We will use the following observation in order to compute the binomial moments of 
+We use the following observation in order to compute the binomial moments of 
 our random variables.
@@
 \begin{obs} \label{obs:binomialmean} Let $X_1,\dots, X_l$ be non negative
-	random integer variables over the same space. 
+	random integer variables over the same probability space. 
 	Let $r_1,\dots,r_l\in \N$.	Suppose
-	each $X_i$ is the sum of various indicator random variables
+	each $X_i$ is the sum of indicator random variables
 	(i.e. variables that only take the values $0$ and $1$)
@@
 	\sum_{\{S_i\}_{i\in [l]}} \mathrm{Pr}\left(
-	\bigwedge_{\substack{i\in [l]\\ j\in S_i}} Y_{i,j}=1
+	\bigwedge_{\substack{i\in [l]\ j\in S_i}} Y_{i,j}=1
 	\right).	
@@
 If $A,B$ are events we may write the conditioned probability $\mathrm{Pr}(A\, | \, B )$ 
-as $\mathrm{Pr}_B(A)$ in some situations to shorten some expressions.
+as $\mathrm{Pr}_B(A)$ in some situations to shorten some expressions. In this situation, 
+given a random variable $X$ we put $\mathrm{E}_B[X]$ to denote conditional expectation of $X$ given the event $B$.
 
@@
 the convention that first order logic contains the equality symbol. 
-Given a vocabulary $\sigma$ we will denote by $FO[\sigma]$ the set of 
-first order formulas of vocabulary $\sigma$. We define the set of 
-\textbf{free variables} of a formula as usual. 
+Given a vocabulary $\sigma$ we denote by $FO[\sigma]$ the set of 
+first order formulas of vocabulary $\sigma$.
 Given a relation symbol $R\in \sigma$ we denote by $ar(R)$ the arity of $R$. 
-Given a formula $\phi\in FO[\sigma]$ we will use the notation $\phi(\overline{y})$ 
+Given a formula $\phi\in FO[\sigma]$ we use the notation $\phi(\overline{y})$ 
 to express that $\overline{y}$ is a tuple of 
@@
 Formulas with no free variables are called \textbf{sentences} and 
-formulas with no quantifiers are called \textbf{open formulas}. 
+formulas with no quantifiers are called \textbf{open formulas}. The \textbf{quantifier 
+rank} of a formula $\phi$, written as $\qr(\phi)$, is the maximum number of 
+nested quantifiers in $\phi$.
 We call \textbf{edge sentence} to any consistent open formula that contains
@@
 	\item 
-	Sets $\{P_R\}_{R\in \sigma}$ satisfying that for 
-	all $R\in \sigma$, 
-	$P_R\subseteq \binom{[ar(R)]}{2}$
+	Sets $\{P_R\}_{R\in \sigma}$ satisfying
+	$P_R\subseteq \binom{[ar(R)]}{2}$ for 
+	all $R\in \sigma$.
 
@@
 
-We define the class $\mathcal{C}$ as the 
+We define $\mathcal{C}$ as the 
 class of $\sigma$-structures that
@@
 	\item \textit{Symmetry axioms}: For each $R\in \sigma$ and
-	each $g\in \Phi_R$:
+	$g\in \Phi_R$:
 	\[ \forall \overline{x}:=x_1,\dots, x_{ar(R)} \left(  R(\overline{x})
-	\iff R(g\cdot\overline{x}) \right)    \]
+	\iff R(g \overline{x}) \right)    \]
 	\item \textit{Anti-reflexivity axioms}: For each 
@@
 
-Structures in $\mathcal{C}$ generalize the usual notion of hypergraph
+Structures in $\mathcal{C}$ generalize the usual notion of a hypergraph
 in the sense that they contain multiple ``adjacency'' relations with arbitrary 
 symmetry and anti-reflexivity axioms. \par
-We will use the usual graph theory nomenclature and notation with some minor changes. 
-In the scope of this article we will call \textbf{hypergraphs}
-to structures in $\mathcal{C}$.
-Given an hypergraph $G$ we will call its \textbf{vertex set}, denoted by $V(G)$,
-to its universe.\par
+We use the usual graph theory nomenclature and notation with some minor changes. 
+In the scope of this article \textbf{hypergraphs}
+are structures in $\mathcal{C}$.
+Given a hypergraph $G$ its \textbf{vertex set} $V(G)$
+is its universe.\par
 In order to define the edge sets of $G$ we need the following auxiliary definition
@@
 	given by $R$} as
-	\[ E_R[V]= (V^{ar(R)}/\Phi_R) \quad \setminus 
-	\quad X, \]
+	\[ E_R[V]= (V^{ar(R)}/\Phi_R)\, \setminus \, X, \]
 	where
@@
 	\]
-	We will call \textbf{edges} to the elements of
-	$E_R[V]$ and we will say that the \textbf{sort} of any edge $e\in E_R[V]$
-	is $R$.	In the case where $V=[n]$ we will write simply $E_R[n]$ instead
+	We call \textbf{edges} to the elements of
+	$E_R[V]$ and we say that the \textbf{sort} of an edge $e\in E_R[V]$
+	is $R$.	In the case where $V=[n]$ we write simply $E_R[n]$ instead
 	of $E_R[[n]]$
@@
 the positions given by $P_R$.\par
-Let $G$ be an hypergraph whose set of vertices is $V$ and let $R\in \sigma$
+Let $G$ be a hypergraph with vertex set is $V$ and let $R\in \sigma$
 be a relation. 
@@
 We define \textbf{the total edge set of $G$} as the set $E(G):=\cup_{R\in \sigma} E_R(G)$.
-Given an edge, $e\in E(G)$ we will denote by $V(e)$
+Given an edge, $e\in E(G)$ we denote by $V(e)$
 the set of all vertices that participate in $e$. 
 \par
-Clearly an hypergraph $G$ is completely given by its vertex set $V(G)$ and its edge 
-set $ E(G)$. Notice that edges $e\in E(G)$ are sorted according to the relation they represent.
+Clearly a hypergraph $G$ is completely given by its vertex set $V(G)$ and its edge 
+set $ E(G)$. Notice that edges $e\in E(G)$ are sorted according to the relation they represent. The \textbf{size} of $G$, written as $|G|$, is its number of vertices. 
 \par
@@
 Given two hypergraphs $H$ and $G$ we say that $H$
-is a \textbf{sub-hypergraph} of $G$, which we write as $H\subset G$,
+is a \textbf{sub-hypergraph} of $G$, written as $H\subset G$,
 if $V(H)\subset V(G)$ and $E(H)\subset E(G)$ (notice 
@@
 Given a set of vertices $U\subseteq V(G)$, 
-we will denote by $G[U]$ the \textbf{hypergraph induced
-by $G$ on $U$}. That is, $G[U]$ is an hypergraph
+we denote by $G[U]$ the \textbf{hypergraph induced
+by $G$ on $U$}. That is, $G[U]$ is a hypergraph
 $H=(V(H),\{E(H)_R\}_{R\in \sigma})$ such that 
@@
 
-We define the \textbf{excess} $ex(G)$ of an hypergraph $G$ as the number
-\[
-ex(G):= \left(\sum_{R\in \sigma} (ar(R)-1)|E_R(G)|\right) - |V(G)|.  
-\] 
-That is, the excess of $G$ is its "weighted number of edges"
+We define the \textbf{excess} $\ex(G)$ of a hypergraph $G$ as the number
+\[
+\ex(G):= \left(\sum_{R\in \sigma} (ar(R)-1)|E_R(G)|\right) - |V(G)|.  
+\] 
+That is, the excess of $G$ is the "weighted number of edges"
 minus its number of vertices. \par
@@
 $V(e_i)\cap V(e_{i+1})\neq \emptyset$. It holds that
-$ex(G)\geq -1$ for any connected hypergraph.
+$\ex(G)\geq -1$ for any connected hypergraph.
 \par
-Given an hypergraph $G$ we define the following metric, $d$, over $V(G)$:
-\[ d^G(u,v)= \min_{\substack{H \subset G\\ 
+Given a hypergraph $G$ we define the following metric, $d$, over $V(G)$:
+\[ d^G(u,v)= \min_{\substack{H \subset G\ 
 		H \text{ connected }\\
@@
 When $G$ 
-is understood or not relevant we will usually simply denote the 
-distance by $d$ instead of $d^G$. Equivalently, the distance $d$
+is understood or not relevant we simply write $d$ instead of $d^G$.
+Equivalently, the distance $d$
 coincides with the usual one defined over the Gaifman graph of the structure 
-$G$. The \textbf{diameter} of an hypergraph is the maximum distance between any 
-two of its vertices. 
+$G$. The \textbf{diameter} of a hypergraph is the maximum distance between any 
+pair of vertices. 
 We extend naturally the distance $d$ to sets and tuples of
@@
 does not contain any connected proper sub-hypergraph containing both $v,u$.
-\par
-A connected hypergraph $G$ is a \textbf{tree} if $ex(G)=-1$ and \textbf{dense} if $ex(G)>0$.
+A connected hypergraph $G$ is a \textbf{tree} if $\ex(G)=-1$ and \textbf{dense} if $\ex(G)>0$.
 An hypergraph is called $r$-\textbf{sparse} if it does not contain any dense sub-hypergraph $H$
 such that $diam(H)\leq r$.
-A connected hypergraph $G$ with $ex(G)\geq 0$ is called \textbf{saturated} 
+A connected hypergraph $G$ with $\ex(G)\geq 0$ is called \textbf{saturated} 
 if for any non-empty proper sub-hypergraph
-$H\subset G$ it holds $ex(H)<ex(G)$. 
-A connected hypergraph $G$ with $ex(G)=0$ is called \textbf{unicycle}. 
-A saturated unicycle is called a \textbf{cycle}. \par
+$H\subset G$ it holds $\ex(H)<\ex(G)$. 
+A connected hypergraph $G$ with $\ex(G)=0$ is called a \textbf{unicycle}. 
+A saturated unicycle is called a \textbf{cycle}. We say that an edge $e:=[\overline{v}]$
+contains a \textbf{loop} if some vertex $v$ appears in $\overline{v}$ more than once.\par
 A \textbf{rooted tree} $(T,v)$ is a tree $T$ with a 
 distinguished vertex $v\in V(T)$ called its \textbf{root}.
-We will usually omit the root when it is not relevant and 
+We usually omit the root when it is not relevant and 
 write just $T$ instead of $(T,v)$. The
@@
 Let $\Sigma$ be a set. A \textbf{$\Sigma$-hypergraph}
-is a pair $(H, \chi)$ where $H$ is an hypergraph
+is a pair $(H, \chi)$ where $H$ is a hypergraph
 and $\chi: V(H)\rightarrow \Sigma$ is a map 
-called \textbf{$\Sigma$-coloring} of $H$. \par
-
-\textbf{Isomorphisms} between hypergraphs are defined the same as 
+called a \textbf{$\Sigma$-coloring} of $H$. \par
+
+\textbf{Isomorphisms} between hypergraphs are defined as 
 isomorphisms between relational structures. Isomorphisms between $\Sigma$-hypergraphs are just
@@
 In both cases we denote the isomorphism relation by $\simeq$. 
-Given an hypergraph $H$, resp. a $\Sigma$-hypergraph $(H, \chi)$,
+Given a hypergraph $H$, resp. a $\Sigma$-hypergraph $(H, \chi)$,
 an \textbf{automorphism} of $H$, resp. $(H,\chi)$,
 is an isomorphism from $H$, resp. $(H,\chi)$, to itself.
-We will denote by $\aut(H)$, resp. $\aut(H,\chi)$,
+We  denote by $\aut(H)$, resp. $\aut(H,\chi)$,
 the number of such automorphisms. \par
 
-Let $H$ be an hypergraph and let $V$ be a set. We define the
+Let $H$ be a hypergraph and let $V$ be a set. We define the
 set of \textbf{copies of $H$ over $V$}, denoted as $Copies(H,V)$, 
@@
 we define expressions
-such as $ex(\mathbb{H})$, $\aut(\mathbb{H})$,
+such as $\ex(\mathbb{H})$, $\aut(\mathbb{H})$,
 $|V(\mathbb{H})|$, $|E(\mathbb{H})|$ or
@@
 We assume familiarity with Ehrenfeucht-Fraisse (EF) games.
-An introduction to the subject can be found in
+An introduction to the subject can be found for instance in
 \cite[Section 2]{finitemodeltheory1}, for example. Given
@@
 	if and only if $H_1$ and $H_2$ satisfy the same 
-	sentences $\phi\in FO[\sigma]$ with $qr(\phi)\leq k$.		
+	sentences $\phi\in FO[\sigma]$ with $\qr(\phi)\leq k$.		
 \end{theorem}
@@
 "sparse regime" of $G^\mathcal{C}(n,\{p\}_R)$, were the 
-expected number of edges each sort is linear. 
+expected number of edges of each sort is linear. 
 This is achieved when for each $R\in \sigma$ 
-it holds that $p_R(n)\sim \beta_R/n^{ar(R)-1}$ for some 
-positive real number $\beta_R$.
-We will write $G_n\left(\{\beta_R\}_R\right)$
+it holds $p_R(n)\sim \beta_R/n^{ar(R)-1}$ for some 
+$\beta_R>0$.
+We write $G_n\left(\{\beta_R\}_R\right)$
 to denote a random sample of 
 $G^\mathcal{C}\left(n,\{p_R\}_{R}\right)$
-by when for each $R\in \sigma$ holds that
-$p_R(n)\sim \beta_R/n^{ar(R)-1}$
-When the choice of $\InR{\beta}$ is not relevant
-we will write $G_n$ instead of 
+when the probabilities $p_R$ satisfy
+$p_R(n)\sim \beta_R/n^{ar(R)-1}$.
+When the choice of $\{\beta\}_R$ is not relevant
+we write $G_n$ instead of 
 $G_n\left(\{\beta_R\}_R\right)$.\par
@@
 \begin{definition} 
-Let $H$ be a connected hypergraph. Then it holds that
+Let $H$ be a connected hypergraph. Then
 $H$ contains a unique maximal saturated sub-hypergraph $H^\prime$
-satisfying satisfies $ex(H^\prime)=ex(H)$ if $ex(H)\geq 0$, and $H^\prime=\emptyset$ 
+satisfying satisfies $\ex(H^\prime)=\ex(H)$ if $\ex(H)\geq 0$, and $H^\prime=\emptyset$ 
 otherwise. Given
@@
 \begin{definition}
-Let $H$ be an hypergraph, $\overline{v}\in V(H)^*$
+Let $H$ be a hypergraph, $\overline{v}\in V(H)^*$
 and $r\in \N$. Let $X$ be the set of vertices $v\in V(H)$
@@
 \begin{definition}\label{def:TrOperator}
-	Let $H$ be an hypergraph, let $\overline{v}\in V(H)^*$ and 
+	Let $H$ be a hypergraph, let $\overline{v}\in V(H)^*$ and 
 	let $v\in H$ be such that $d(Center(H,\overline{v}),$ $ \, v)<\infty$. 
@@
 	H,\overline{v};\,\, v\right)$ as the tree $H[X]$ 		
-	to which we assign $v$ as a root. That is,
+	with $v$ as a root. That is,
 	$\mathrm{Tr}\left(
@@
 	contains $v$. One can easily check that $H[X]$ is indeed a tree:
-	if it was not then it would contain some saturated sub-hypergraph, leading
-	to contradiction. 
+	if it were not then it would contain some saturated sub-hypergraph, leading
+	to a contradiction. 
 	Given $r\in \N$ we define $\mathrm{Tr}(H,\overline{v};\, v;\, r)$ as
 	$\mathrm{Tr}( Core(H,\overline{v};\,r),\overline{v}; \, v)$.
-	In the case that $\overline{v}$ is the empty list we will write
+	In the case that $\overline{v}$ is the empty list we write
 	simply $\mathrm{Tr}(H;\,\, v)$ or $\Tr(H;\,\,v;\,\,r)$.
@@
 		\textbf{root symbol}. Set $\widehat{\Sigma}_{k,r-1}:=\Sigma_{k,r-1}\cup \{\rho\}$.
-		Then we call a $(k,r)$-\textbf{pattern} to an isomorphism class
+		Then a $(k,r)$-\textbf{pattern} is isomorphism class
 		of $\widehat{\Sigma}_{k,r-1}$-hypergraphs 
-		$(e,\tau)$ that consist of only one loop-free edge and no isolated vertices,
+		$(e,\tau)$ that consist of only one edge with no loops and no isolated vertices,
 		and satisfy 
-		$\tau(v)=\rho$ for exactly one vertex $v\in V(e)$. We will
+		$\tau(v)=\rho$ for exactly one vertex $v\in V(e)$. We
 		denote by $P(k,r)$ the set of $(k,r)$-patterns. \par
@@
 	E^2_\mathbf{T}$ of $P(k,r)$ and natural numbers $a_\epsilon<k$
-	for each $\epsilon\in E^2_\mathbf{T}$ that only depend on 
-	$\mathbf{T}$ such that any rooted tree $(T,v)$ belongs to
+	for each $\epsilon\in E^2_\mathbf{T}$ that depends only on 
+	$\mathbf{T}$ such that a rooted tree $(T,v)$ belongs to
 	$\mathbf{T}$ if and only if the following hold: (1) For any pattern 
@@
 From last characterization of the $\sim_k$ relation
-it follows, via an induction argument, that for any $r\in \N$ the quantity
+it follows using induction over $r$ that for any $r\in \N$ the quantity
 of $\sim_k$ classes of trees with radii at most $r$ is finite. \par
@@
 	Let $k\in \N$. 
-	Given $H$ be a non-tree connected hypergraph, we define
+	Given a non-tree connected hypergraph  $H$, we define
 	its \textbf{canonical k-coloring} $\tau^k_{H}$
@@
 	We say that $H_1$ and $H_2$ are $(k,r)$-agreeable, written
-	as $H_1\approx_{k,r} H_2$ if for any $\sim_k$ class $\mathcal{H}$ 
+	as $H_1\approx_{k,r} H_2$ if for any $\sim_k$ class $\mathbf{H}$ 
 	``the number of connected
-	components in $H^\prime_1$ that belong to $\mathcal{H}$" and
+	components in $H^\prime_1$ that belong to $\mathbf{H}$" and
 	``the number of connected components in $H^\prime_2$ that belong to 
-	$\mathcal{H}$" are the same or are both greater than $k-1$.\par
+	$\mathbf{H}$" are the same or are both greater than $k-1$.\par
 	%	 satisfies that
@@
 	of rooted trees with radii at most $r$. Then
-	we call a $(k,r)$-\textbf{cycle} to an isomorphism class
+	a $(k,r)$-\textbf{cycle} is an isomorphism class
 	of $\Sigma_{(k,r)}$-hypergraphs 
 	$(H,\tau)$ that are cycles of diameter at most $2r+1$.
-	We will denote by $C(k,r)$ the set of $(k,r)$-cycles.
+	We denote by $C(k,r)$ the set of $(k,r)$-cycles.
 \end{definition}
@@
 \begin{obs}\label{obs:agreeablecores}
-	Let $k,r\in\N$ and let $\mathcal{O}$ be a $\approx_{k,r}$ class
+	Let $k,r\in\N$ and let $\mathbf{O}$ be a $\approx_{k,r}$ class
 	of $r$-simple hypergraphs. 
-	Then there is a partition $U^1_\mathcal{O},
-	U^2_\mathcal{O}$ of $C(k,r)$ and natural numbers $a_\omega<k$
-	for each $\omega\in U^2_\mathcal{O}$ that only depend on 
-	$\mathcal{O}$ such that any $r$-simple hypergraph $G$ belongs to
-	$\mathcal{O}$ if and only if it holds that (1) for any $\omega\in U^1_\mathcal{O}$ 
+	Then there is a partition $U^1_\mathbf{O},
+	U^2_\mathbf{O}$ of $C(k,r)$ and natural numbers $a_\omega<k$
+	for each $\omega\in U^2_\mathbf{O}$ that depend  only on 
+	$\mathbf{O}$ such that a $r$-simple hypergraph $G$ belongs to
+	$\mathbf{O}$ if and only if it holds that (1) for any $\omega\in U^1_\mathbf{O}$ 
 	there are at least $k$ connected components $H \subset Core(G;r)$ whose cycle 		
 	$H^\prime=Center(H)$ satisfies that	$(H^{\prime},\tau^k_{H})\in \omega$, and
-	(2) for any $\omega\in U^2_\mathcal{O}$ there are exactly $a_\omega$ 
+	(2) for any $\omega\in U^2_\mathbf{O}$ there are exactly $a_\omega$ 
 	connected components $H \subset Core(G;r)$ whose cycle 
@@
 \begin{definition} \label{def:rich}
-	Let $H$ be an hypergraph and let $k,r\in\N$. Let
+	Let $H$ be a hypergraph and let $k,r\in\N$. Let
 	$X\subset V(H)$ be the set of vertices in $H$
@@
 	at most $2r+1$.	We say that $H$ is $(k,r)$-\textbf{rich}
-	if for any $r^\prime\leq r$, any vertices $v_1,\dots, v_k$ 
-	and any $\sim_k$ class $\mathbf{T}$ of trees with radius
-	at most $r^\prime$ it holds that there exists a vertex $v\in V(H)$
+	if for any $r^\prime\leq r$, vertices $v_1,\dots, v_k$ 
+	and $\sim_k$ class $\mathbf{T}$ of trees with radius
+	at most $r^\prime$ there exists a vertex $v\in V(H)$
 	such that $d(v,X)> 2r^\prime+1$, $d(v,v_i)>2r^\prime+1$ for all
@@
 adapted to fit our context. As in that
-article the proof is divided in two parts: a model theoretic part and a 
+article the proof is divided into two parts: a model theoretic part and a 
 probabilistic part. The main result of the first part is the following
@@
 \begin{reptheorem}{thm:agreeabilityprobabilities}
-	Let $k,r \in \N$. Let $\mathcal{O}$ be a $\approx_{k,r}$ class
+	Let $k,r \in \N$. Let $\mathbf{O}$ be a $\approx_{k,r}$ class
 	of $r$-simple hypergraphs. Then 
 	\[
-	\Ln \mathrm{Pr}\left(G_n\left(\{\beta_R\}_{R\in \sigma}\right)\in \mathcal{O}\right)
+	\Ln \mathrm{Pr}\left(G_n\left(\{\beta_R\}_{R\in \sigma}\right)\in \mathbf{O}\right)
 	\]
@@
 
-An sketch of the proof of \cref{thm:main} using these results is the following.
-Let $\Phi\in FO[\sigma]$ be a sentence and let $k:=qr(\Phi)$, $r:=(3^k-1)/2$.
-Because of \cref{thm:Duplicatorwins} and \cref{thm:rich}
-it holds that for any $\approx_{k,r}$ class $\mathcal{O}$
-\[
-\Ln \mathrm{Pr}\left(G_n \models \Phi\, \big| \, G_n\in \mathcal{O} \right)= \text{ $0$ or $1$ }.
-\]
-This together with \cref{cor:simple}
-and the fact that there are a finite number of
+A sketch of the proof of \Cref{thm:main} using these results as follows. 
+Let $\Phi\in FO[\sigma]$ be a sentence and let $k:=\qr(\Phi)$, $r:=(3^k-1)/2$.
+Because of \Cref{thm:Duplicatorwins,thm:rich}
+it holds that for any $\approx_{k,r}$ class $\mathbf{O}$
+\[
+\Ln \mathrm{Pr}\left(G_n \models \Phi\, \big| \, G_n\in \mathbf{O} \right)= \text{ $0$ or $1$ }.
+\]
+This together with \Cref{cor:simple}
+and the fact that there is a finite number of
 $\approx_{k,r}$-classes of $r$-simple hypergraphs imply that $\Ln \PR{G_n \models \Phi}$
-equals a finite sum of limits of the form $\Ln \PR{G_n \in \mathcal{O}}$
-where $\mathcal{O}$ is some $\approx_{k,r}$-class of $r$-simple hypergraphs.
-Finally, using \cref{thm:agreeabilityprobabilities}
+equals a finite sum of limits of the form $\Ln \PR{G_n \in \mathbf{O}}$,
+where $\mathbf{O}$ is some $\approx_{k,r}$-class of $r$-simple hypergraphs.
+Finally, using \Cref{thm:agreeabilityprobabilities}
  we get that $\Ln \PR{G_n \models \Phi}$ exists and 
-is an analytic expression in $\{\beta_R\}_{R\in \sigma}$, as we wanted.
+is an analytic expression in $\{\beta_R\}_{R}$, as we wanted.
 
@@
 Given $X\subseteq V_1$ and $Y\subseteq V_2$
-we write $(H_1,X)\simeq_{k,r} (H_2,Y)$, if we can order $X$, resp $Y$ to form
-lists $\overline{v}$, resp. $\overline{u}$ such that 
+we write $(H_1,X)\simeq_{k,r} (H_2,Y)$, if we can order $X$, resp. $Y$, to form
+lists $\overline{v}$, resp. $\overline{u}$, such that 
 $(H_1,\overline{v})\simeq_{k,r}(H_2,\overline{u})$. 
@@
 and $Y=Y_1\cup \dots \cup Y_b$ 
-such that $N(X_i;r)$'s, and the
-$N(Y_i;r)$'s, are connected and disjoint. 
+such that all $N(X_i;r)$ and $N(Y_i;r)$
+ are connected and disjoint. 
 We write $(H_1,X)\cong_{k,r} (H_2,Y)$, 
 if for any set $Z\subset V_\delta$, with $\delta\in \{1,2\}$,
-among the $X_i$'s or the $Y_i$'s
-it is satisfied that ``the number of $X_i$'s  
+among the $X_i$ or the $Y_i$
+it is satisfied that ``the number of $X_i$  
 such that $(H_\delta, Z) \simeq_{k,r} (H_1,X_i)$" 
-and ``the number of $Y_i$'s such that
+and ``the number of $Y_i$ such that
 $(H_\delta,Z)\simeq_{k,r} (H_2,Y_i)$"
@@
 The main theorem of this section, which
-is a slight strengthening of \cite[Theorem 
+is a strengthening of \cite[Theorem 
 2.6.7]{spencer2013strange}, is the following.
@@
 	Duplicator wins $d\ehr_k(H_1,\overline{v};\,H_2,\overline{u})$. 
-	Let $v\in V(H_1),u\in V(H_2)$ be vertices
+	Let $v\in V(H_1),u\in V(H_2)$ be the vertices
 	played in the first round of an instance of the game 
@@
 \begin{proof}
-	Using \cref{obs2} we get that Duplicator wins 
+	Using \Cref{obs2} we get that Duplicator wins 
 	\[
@@
 	as well. Call $H^\prime_1=N(\overline{v};3r+1)$,
-	$H^\prime_2=N(\overline{u};3r+1)$. Then by \cref{obs2}
+	$H^\prime_2=N(\overline{u};3r+1)$. Then by \Cref{obs2}
 	Duplicator wins
@@
 	$d(z,\overline{v})\leq d(z,v^\prime)+d(v^\prime,\overline{v})=3r+1$.
-	In consequence, $N^{H_1}(v;r)\subset H^\prime_1$. Thus,
+	As a consequence, $N^{H_1}(v;r)\subset H^\prime_1$. Thus,
 	$N^{H_1}(\overline{v_2};r)\subseteq H^\prime_1$, and $N^{H_1}(\overline{v_2};r)
@@
 
-\begin{proof}[Proof of \cref{thm:DuplicatorAux}]
+\begin{proof}[Proof of \Cref{thm:DuplicatorAux}]
 	%Set 
@@
 	as in the definition of $\cong_{k,r}$.
-	Define $r_0=(3^k-1)/2$ and $r_i=(r_{i-1}-1)/3$ for each
+	Let $r_0:=(3^k-1)/2$ and $r_i:=(r_{i-1}-1)/3$ for each
 	$1\leq i \leq k$. 
@@
 	\end{itemize}
-	We show that Duplicator can play in a way such that at the
+	We show that Duplicator can play in such a way that at the
 	end round the following are satisfied:
@@
 	Clearly properties (i) to (iv) hold at the beginning of 
-	the game.  Suppose
+	the game.  Suppose that
 	Duplicator can play in such a way that properties (i) to (iv) hold 
@@
 		\item For some unique previously marked set $S\subset V_1$ 
-		it holds that $d(S\cup \overline{v},\quad v^1_i)\leq 2r_i +1$. 
+		we have $d(S\cup \overline{v},\, v^1_i)\leq 2r_i +1$. 
 		In this case let $T\subset V_2$ be the set in $H_2$ marked in the 
@@
 		$\overline{v}(T):= \overline{v}(T)^\smallfrown v^2_i$. Notice
-		that because of \cref{lemm:Duplicator} now
+		that because of \Cref{lemm:Duplicator} now
 		\[
@@
 		Thus, by definition, for some orderings $\overline{w}$, 
-		$\overline{z}$ of the vertices in $S$ and $T$ respectively
-		it holds that Duplicator wins
+		$\overline{z}$ of the vertices in $S$ and $T$ respectively,
+		Duplicator wins
 		\[
@@
 		$\overline{v}(T):=v^2_i$. Notice
-		that because of \cref{lemm:Duplicator} now
+		that because of \Cref{lemm:Duplicator} now
 		\[
@@
 		\]
-		\item For all marked sets $S\subset V_1$ it holds
-		$d(S\cup \overline{v}(S), \quad v^1_i)>2r_i +1$, and
+		\item For all marked sets $S\subset V_1$ we have
+		$d(S\cup \overline{v}(S), \, v^1_i)>2r_i +1$, and
 		for all sets $S$ among $X_1,\dots, X_a$ it also holds
 		$d(S,v^1_i)> 2r_i+1$. In this case
-		from condition (2) of the statement follows that
+		from condition (2) of the statement it follows that
 		Duplicator can choose
@@
 		(A)
-		$d(T\cup \overline{v}(T),\quad v^2_i)>2r_i+1$ for all
+		$d(T\cup \overline{v}(T),\, v^2_i)>2r_i+1$ for all
 		marked sets $T\subset V_2$, (B)
@@
 	follows from comparing $r_{i-1}$ and $r_{i}$ as well 
-	as applying \cref{obs1} and \cref{obs2}.
+	as applying \Cref{obs1} and \Cref{obs2}.
 
@@
 $X:=\{v\} \cup \{\, u\in V(T) \, | \, d(v,u) = 1 + d(e,u) \,\}$,
-to which we assign $v$ as the root. In other words, 
-$\mathrm{Tr}\left(T,v;\, e\right)$ is the tree formed of 
+with $v$ as the root. In other words, 
+$\mathrm{Tr}\left(T,v;\, e\right)$ is the tree consisting of 
 $v$ and all the vertices
-in $T$ whose only path to $v$ contain $e$.
+in $T$ whose only path to $v$ contains $e$.
 
@@
 	$r+1$. Let $\tau^k_{(T_1,v_1)}$ and $\tau^k_{(T_2,v_2)}$
-	be colorings over $T_1$ and $T_2$ as in \cref{def:sim_trees}
+	be colorings over $T_1$ and $T_2$ as in \Cref{def:sim_trees}
 	Let $e_1$ and $e_2$ be initial edges 
@@
 	We show a winning strategy for Duplicator.
-	At the beginning of the game fix 
-	$f:V(e_1)\rightarrow V(e_2)$ an isomorphism between 
+	At the beginning of the game fix an isomorphism 
+	$f:V(e_1)\rightarrow V(e_2)$ between 
 	$(e_1,\tau^k_{(T_1,v_1)})$
@@
 
-\begin{proof}[Proof of \cref{thm:equivalenttrees}]~ \par
+\begin{proof}[Proof of \Cref{thm:equivalenttrees}]~ \par
 	Notice that, as $(T_1,v_1)\morph{k} (T_2,v_2)$, both $T_1$ and
@@
 	Now let $r>0$ and assume that the 
-	statement is true for all lesser values of $r$.
+	statement is true for all smaller values of $r$.
 	Let $\tau^k_{(T_1,v_1)}$ and $\tau^k_{(T_2,v_2)}$ 
 	be the colorings over $T_1$ and $T_2$ as in 
-	\cref{def:sim_trees}. 
+	\Cref{def:sim_trees}. 
 	We show that there is a winning strategy 
@@
 		Because of
-		\cref{lem:equivalentedges}, Duplicator
+		\Cref{lem:equivalentedges}, Duplicator
 		has a winning strategy in
@@
 		\left(e_2,\tau^k_{(T_2,v_2)}  \right)$.	
-		Again, because of \cref{lem:equivalentedges}, 
+		Again, because of \Cref{lem:equivalentedges}, 
 		Duplicator has a winning strategy in
@@
 	\end{itemize}
+\vspace{-2em}
 \end{proof}
@@
 		$\tau^k_{H_1}, \tau^k_{H_2}$ be as in
-		\cref{def:sim_general}.
+		\Cref{def:sim_general}.
 		Let $f$ be an isomorphism
@@
 		$(T_1,u)\sim_k (T_2,f(u))$. 
-		Then because of \cref{thm:equivalenttrees} we have that
+		Then because of \Cref{thm:equivalenttrees} we have that
 		Duplicator has a winning strategy in
@@
 		and they can follow it taking into account the previous
-		plays made in $T_1$ and $T_2$, if any. In particular, 
+		moves made in $T_1$ and $T_2$, if any. In particular, 
 		if Spoiler has chosen
@@
 	sets of vertices in $H_1$, resp. $H_2$, that
-	belong to any saturated sub-hypergraph of diameter 
+	belong to a saturated sub-hypergraph of diameter 
 	at most $2r+1$. Then $(H_1,X)\cong_{k,r} (H_2,Y)$ in the sense of
-	\cref{def:analogous}.
+	\Cref{def:analogous}.
 \end{lemma}
@@
 	a connected component of $Core(H_1;r)$, resp. $Core(H_2;r)$.
-	Because of \cref{thm:strategyaux}
+	Because of \Cref{thm:strategyaux}
 	$N(X_i;r)\sim_k N(Y_j;r)$ implies 
 	$(H_1,X_i)\simeq_{k,r} (H_2,Y_j)$ in the sense of
-	\cref{def:similar}. The result follows now from
+	\Cref{def:similar}. The result follows now from
 	 the definition of $H_1\approx_{k,r}H_2$.	
@@
 		Because of the previous lemma we can apply 
-		\cref{thm:DuplicatorAux} with $X\subset V(H_1)$ 
+		\Cref{thm:DuplicatorAux} with $X\subset V(H_1)$ 
 		and	$Y\subset V(H_2)$ defined as before. The
 		hypothesis of $(k,r)$-richness on both $H_1, H_2$ ensures that
-		condition (2) in the statement of \cref{thm:DuplicatorAux}
+		condition (2) in the statement of \Cref{thm:DuplicatorAux}
 		holds. 
@@
 \begin{lemma}
-	Let $H$ be an hypergraph, and let $X_n$ be the 
-	random variable that counts the copies of $H$ in 
+	Let $H$ be a hypergraph, and let $X_n$ be the 
+	random variable equal to the number of copies of $H$ in 
 	$G_n$. Then 
-	$\mathrm{E}\big[X_n\big]=\Theta(n^{-ex(H)})$.  
+	$\mathrm{E}\big[X_n\big]=\Theta(n^{-\ex(H)})$.  
 \end{lemma}
 \begin{proof}
-It holds
+We have
 \[
@@
 \]	
-We have that $\Big|Copies(H,[n])\Big|=\frac{(n)_{|H|}}{\aut(H)}$. Also, 
-for any $H^\prime \in Copies(H,[n])$ it is satisfied
+We also have that $\Big|Copies(H,[n])\Big|=\frac{(n)_{|H|}}{\aut(H)}$. Also, 
+for any $H^\prime \in Copies(H,[n])$ it holds that
 \[
@@
 \mathrm{E}\big[X_n\big]\sim 
-\frac{(n)_{|H|}}{\aut(H)}\cdot
+\frac{(n)_{|H|}}{\aut(H)}
 \prod_{R\in \sigma} \left(\frac{\beta_R}{n^{ar(R)-1}}\right)^{|E_R(H)|}
 \sim
-n^{-ex(H)} \cdot \frac{\prod_{R\in \sigma} \beta_R^{
+n^{-\ex(H)}  \frac{\prod_{R\in \sigma} \beta_R^{
 |E_R{H}| }}{\aut(H)}.
@@
 \begin{lemma} \label{lem:nocopiesdense}
-	Let $H$ be an hypergraph such that $ex(H)>0$. Then
+	Let $H$ be a hypergraph such that $\ex(H)>0$. Then
 	a.a.s there are no copies of $H$ in $G_n$. 
@@
 \begin{lemma}\label{lem:nocopiesfixed}
-	Let $H$ be an hypergraph. Let
+	Let $H$ be a hypergraph. Let
 	$\overline{v}\in (\N)_*$ be a list of vertices
-	with $len(\overline{v})\leq |V(H)|$.
+	with $\len(\overline{v})\leq |V(H)|$.
 	For each $n\in \N$ 
@@
 	$
-	\mathrm{E}\big[ X_n \big]=\Theta(n^{-ex(H)-len(\overline{v})})$.
+	\mathrm{E}\big[ X_n \big]=\Theta(n^{-\ex(H)-\len(\overline{v})})$.
 \end{lemma}
 \begin{proof}
-	It holds that the number of hypergraphs $H^\prime \in Copies(H,[n])$
+	The number of hypergraphs $H^\prime \in Copies(H,[n])$
 	that contain all vertices in $\overline{v}$ is asymptotically
-	$\sim n^{|V(H)|-len(\overline{v})}$ for
+	$\sim n^{|V(H)|-\len(\overline{v})}$ for
 	some constant $C$. Then,
@@
 	\mathrm{E}\big[ X_n \big]\sim 
-	C \cdot n^{|V(H)|-len(\overline{v})}
-	\cdot\prod_{R\in\tau} \left( \frac{\beta_R}{n^{ar(R)-1}}\right)^{e_R(H)}=
-	n^{-ex(H)-len(\overline{v})}\cdot C \cdot
+	C   n^{|V(H)|-\len(\overline{v})}
+	 \prod_{R\in\tau} \left( \frac{\beta_R}{n^{ar(R)-1}}\right)^{e_R(H)}=
+	n^{-\ex(H)-\len(\overline{v})}  C  
 	\prod_{R\in\tau} \left( \beta_R \right)^{e_R(H)}.
@@
 
-	Given an hypergraph $H$ and an edge $e\in E(H)$ we
+	Given a hypergraph $H$ and an edge $e\in E(H)$ we
 	define the operation of \textbf{cutting} the edge 
@@
 	Let $G$ be a
-	dense hypergraph with diameter at most $r$.
-	And let $H\subset G$ be a connected 
-	sub-hypergraph with $ex(H)<ex(G)$. Then
+	dense hypergraph with diameter at most $r$,
+	and let $H\subset G$ be a connected 
+	sub-hypergraph with $\ex(H)<\ex(G)$. Then
 	there is a connected
@@
 	satisfying $H\subset H^\prime$,
-	$ex(H)<ex(H^\prime)$ and that 
-	$|E(H^\prime)|\leq |E(H)|+2\cdot r + 1$, 
+	$\ex(H)<\ex(H^\prime)$ and that 
+	$|E(H^\prime)|\leq |E(H)|+2  r + 1$, 
 \end{lemma}
@@
 	Suppose there is some edge $e\in E(G)\setminus E(H)$ with
-	and $ex(e)\geq 0$. Let $P$ be a path
+	and $\ex(e)\geq 0$. Let $P$ be a path
 	of length at most $r$ joining $H$ and $e$ in $G$. 
@@
 	the statement. Otherwise, all edges $e\in E(G)\setminus E(H)$ 
-	satisfy $ex(e)=-1$. In this case we successively cut
+	satisfy $\ex(e)=-1$. In this case we successively cut
 	edges $e$ from $G$ such that $d(e, H)$ is the maximum possible
 	(notice that this always yields a connected hypergraph)
-	until we obtain an hypergraph $G^\prime$ with $ex(G^\prime)<ex(G)$.
+	until we obtain a hypergraph $G^\prime$ with $\ex(G^\prime)<\ex(G)$.
 	Let $e$ be the edge that was cut last. Then $V(G^\prime)\cap V(e)=
-	ex(G)-ex(G^\prime)+1 \geq 2$. Let $v_1, v_2\in V(G^\prime)\cap V(e)$,
+	\ex(G)-\ex(G^\prime)+1 \geq 2$. Let $v_1, v_2\in V(G^\prime)\cap V(e)$,
 	and let $P_1$, $P_2$ be paths of length at most $r$ that join $H$
@@
 \begin{proof}
-	Apply the previous lemma twice in a row starting with $G$ and taking
+	Apply the previous lemma twice starting with $G$ and taking
 	as $H$ a sub-hypergraph of $G$ consisting of a single vertex and 
@@
 In particular, if we define $l:=\max\limits_{R\in \sigma} \,\, ar(R)$
-then last lemma implies that if $G$ is a dense hypergraph whose
+the last lemma implies that, if $G$ is a dense hypergraph whose
 diameter is at most $r$ then $G$ contains a dense sub-hypergraph
-$H$ with $|H|\leq l\cdot (4r+2)$.\par
+$H$ with $|H|\leq l  (4r+2)$.\par
 
@@
 \begin{proof}
-	Because of last lemma there is a constant $R$ such that 
+	Because of the last lemma there is a constant $R$ such that 
 	``$G$ does not contain dense hypergraphs of size bounded by $R$" implies
@@
 	hypergraphs of size bounded by } R\right).\] 
-	Because of	\cref{lem:nocopiesdense}, given any individual dense hypergraph,
-	the probability that there are no copies
-	of it in $G_n$ tends to $1$ as $n$ goes to infinity. Using that
+	Because of	\Cref{lem:nocopiesdense}, given a fixed dense hypergraph,
+	the probability that $G_n$ contains no copies
+	of it tends to $1$ as $n$ goes to infinity. Using that
 	there are a finite number of $\sim$ classes of dense hypergraphs whose
-	size bounded by	$R$ we deduce that the RHS of last inequality tends to $1$. 
+	size bounded by	$R$, we deduce that the RHS of the last inequality tends to $1$. 
 \end{proof}
@@
 \begin{proof}
-	If some connected component of $Core(G_n;r)$ is not a cycle that means
-	that either $G_n$ contains a dense hypergraph of diameter at most $4r+1$
-	or that $G_n$ contains two cycles of diameter at most $2r+1$ that are at
-	a distance at most $2r+1$. In the second case, considering the two cycles
+	If some connected component of $Core(G_n;r)$ is not a cycle then either $G_n$ contains a dense hypergraph of diameter at most $4r+1$,
+	or $G_n$ contains two cycles of diameter at most $2r+1$ that are at
+	distance at most $2r+1$. In the second case, considering the two cycles
 	and the path joining them, $G_n$ contains a dense hypergraph of diameter
-	bounded by $6r+3$. In consequence the fact that $G_n$ is $(6r+3)$-sparse
+	bounded by $6r+3$. Hence the fact that $G_n$ is $(6r+3)$-sparse
 	implies that $G_n$ is $r$-simple. Because of the previous theorem 
@@
 	a.a.s, for all vertices $v\in \overline{v}$ the neighborhoods 
-	$N(v;r)$'s are all trees and they are all disjoint.
+	$N(v;r)$ are all trees and they are all disjoint.
 
@@
 		An application of the first moment method together with
-		\cref{lem:nocopiesfixed} and the fact that there are a finite number
-		of $\simeq$ classes of paths whose length is at most $2r+1$ implies that
-		a.a.s the $N(v;r)$'s are disjoint. 
-		Also, because of \cref{thm:sparse} a.a.s the $N(v;r)$'s are either 
+		\Cref{lem:nocopiesfixed} and the fact that there is a finite number
+		of $\simeq$ classes of paths whose length is at most $2r+1$, implies that
+		a.a.s the $N(v;r)$ are disjoint. 
+		Also, because of \Cref{thm:sparse} a.a.s the $N(v;r)$ are either 
 		trees or unicycles. But if any of the $N(v;r)$'s was an unicycle then
-		that would mean that in $G_n$ there exists a path $P$ of length at most
+		in $G_n$ there would exist a path $P$ of length at most
 		$2r+1$ joining some vertex $v\in \overline{v}$
-		with a cycle $C$ of diameter at most $2r+1$. Using \cref{lem:nocopiesfixed}
-		again as well as the fact that there are a finite number of possible $\simeq$
+		with a cycle $C$ of diameter at most $2r+1$. Using \Cref{lem:nocopiesfixed}
+		again, as well as the fact that there is a finite number of possible $\simeq$
 		classes for
-		$P\cup C$ we obtain that a.a.s no such $P$ and $C$ exist. 
+		$P\cup C$, we obtain that a.a.s no such $P$ and $C$ exist. 
 		In consequence all the $N(v;r)$'s are disjoint trees as we wanted to
@@
 	$\pi(\overline{x})$ be an edge sentence such that
-	$len(\overline{x})=len(\overline{v})$. 
+	$\len(\overline{x})=\len(\overline{v})$. 
 	Define $G_n^\prime=G_n \setminus E[\overline{v}]$ (i.e. $G_n$ minus all the
-	edges induced over $\overline{v}$). Fix $r\in \N$. 
+	edges induced on $\overline{v}$). Fix $r\in \N$. 
 	Then a.a.s for all vertices $v\in \overline{v}$ the neighborhoods
@@
 	Notice that $A_n$ does not concern the possible edges
-	induced over $\overline{v}$. In consequence, because edges are independent
-	in our random model, 
+	induced over $\overline{v}$. Because edges are independent
+	in our random model, we have that
 	$\mathrm{Pr}\left(A_n \, | \, \pi(\overline{v})\right)
 	=\mathrm{Pr}(A_n)$. Now the result follows from 
-	\cref{lem:disjointtrees} using that $G^\prime_n\subset G_n$.  
+	\Cref{lem:disjointtrees} using that $G^\prime_n\subset G_n$.  
 \end{proof}
@@
 
-Notice that the 
+Note that the 
 definition of  $\mathrm{Pr}[r,\mathbf{T}]$ does not depend on the
@@
 an expression with parameters
-$\{\beta_R\}_{R\in\sigma}$, belongs to $\Lambda$ 
+$\{\beta_R\}_{R\in\sigma}$ belonging to $\Lambda$ 
 for any choice of $r$ and $\mathbf{T}$. \par
@@
 \begin{theorem} \label{thm:BigTrees}
-	Fix $r\in \N$. Let $k\in \N$ The following are satisfied:
+	Fix $r\in \N$. Let $k\in \N$ The following hold:
 	\begin{itemize}
 		\item[(1)] Let $\mathbf{T}$ be a
-		$k$-equivalence class for trees with radii at most $r$.	Then 
+		$k$-equivalence class of trees with radii at most $r$.	Then 
 		$
@@
 		edge sentence such that 
-		$len(\overline{x})=len(\overline{u})$.
+		$\len(\overline{x})=\len(\overline{u})$.
 		Let $\overline{v}\in (\N)_*$ be vertices contained
@@
 \end{theorem}
-We will devote the rest of this section to proving this
-theorem. The proof will be done by induction on $r$. 
+We devote the rest of this section to proving this
+theorem. The proof is by induction on $r$. 
 Recall that	all trees with radius zero are $k$-equivalent. Thus,
 the limits appearing in conditions (1) and (2) are both equal to $1$
-in the case $r=0$. In consequence we obtain the following.
+in the case $r=0$.
 
 \begin{lemma}
-	Conditions (1) and (2) of \cref{thm:BigTrees} 
+	Conditions (1) and (2) of \Cref{thm:BigTrees} 
 	are satisfied for $r=0$.
@@
 	Let $k\in \N$ and $r>0$. 
-	Suppose that \cref{thm:BigTrees} holds for $r-1$.
+	Suppose that \Cref{thm:BigTrees} holds for $r-1$.
 	Given a $(k,r)$-pattern $\epsilon$ we define the expressions
-	$\lambda_{r,\epsilon}$ and $\mu_{r,\epsilon}$ in the following way.
+	$\lambda_{r,\epsilon}$ and $\mu_{r,\epsilon}$ as follows.
 	Let $(e,\tau)$ be a representative of $\epsilon$
@@
 	\[
-	\lambda_{r,\epsilon}:=\prod_{\substack{u\in V(e)\\ u\neq v} } \mathrm{Pr}\big[
+	\lambda_{r,\epsilon}:=\prod_{\substack{u\in V(e)\ u\neq v} } \mathrm{Pr}\big[
 	r-1, \tau(u)\big], \quad \text{ and } \quad
 	\mu_{r,\epsilon}=\frac{\beta_{R(e)}}{\aut(\epsilon)} 
-	\cdot \lambda_{r,\epsilon}.
+	  \lambda_{r,\epsilon}.
 	\]
@@
 	edge sentence such that 
-	$len(\overline{x})=len(\overline{u})$.
+	$\len(\overline{x})=\len(\overline{u})$.
 	Let $\overline{v}\in (\N)_*$ be vertices contained
@@
 	that $(e,\tau^k_{(T_{n,v},v)})\in \epsilon$. Suppose that
-	\cref{thm:BigTrees} holds for $r-1$. Then the conditional 
-	distributions of the variables $X_{n,v,\epsilon}$'s given
+	\Cref{thm:BigTrees} holds for $r-1$. Then the conditional 
+	distributions of the variables $X_{n,v,\epsilon}$ given
 	$\pi(\overline{u})$ converge to independent Poisson distributions
-	whose respective mean values are given by the $\mu_{r,\epsilon}$'s. 
+	whose respective mean values are given by the $\mu_{r,\epsilon}$. 
 \end{lemma}
 \begin{proof}
-	To avoid excessively complex notation we will show only the case where
-	$\overline{v}$ consists only of one vertex $v$. The general case is proven
+	To avoid excessively complex notation we prove only the case where
+	$\overline{v}$ consists of a single vertex $v$. The general case is proven
 	using the same arguments. Set $T_n:=T_{n,v}$ and 
 	$X_{n,\epsilon}:=X_{n,v,\epsilon}$ for all $\epsilon\in P(k,r)$.
-	By \cref{thm:BrunSieve},
+	By \Cref{thm:BrunSieve},
 	in order to prove the result it is enough to show that 
 	for any choice of natural numbers $\{b_\epsilon\}_{\epsilon\in P(k,r)}$
-	it holds
+	it holds that
 	\begin{equation} \label{eqn:binomexpedges}
@@
 	pattern is $\epsilon$ for all $(k,r)$-patterns $\epsilon$. 	
-	Using \cref{obs:binomialmean} we obtain
+	Using \Cref{obs:binomialmean} we obtain
 	\[
@@
 	$(e,\tau)\in\bigcup_{\epsilon\in P(k,r)} E_\epsilon$ satisfy
-	that no vertex $w\in \overline{u}$ other than $v$ belong to any
+	that no vertex $w\in \overline{u}$ other than $v$ belongs to any
 	of those edges and each vertex 
@@
 	$\{E_\epsilon\}_\epsilon \in \Omega_n$ 
-	it holds that $e\in E(T_n)$ for all $(e,\tau)\in
+	we have that $e\in E(T_n)$ for all $(e,\tau)\in
 	\bigcup_{\epsilon\in P(k,r)} E_\epsilon$ 
@@
 	is $v$ by definition.  
-	Thus, in last sum it suffices to consider only 
+	Thus, in the last sum it suffices to consider only 
 	the disjoint $\{E_\epsilon\}_\epsilon$.
-	Because of the symmetry of the random model the probability
-	in that sum is the same for all disjoint choices of
+	Because of the symmetry of the random model the probabilities
+	in that sum are the same for all disjoint choices of
 	$\{E_\epsilon\}_\epsilon$.
-	In consequence, if we fix
+	Hence, if we fix
 	$\{E_\epsilon\}_{\epsilon}\in \Omega^\prime_\N$
@@
 	= 
-	|\Omega_n^\prime|\cdot
+	|\Omega_n^\prime| 
 	\mathrm{Pr}_{\pi(\overline{u})}\left(
@@
 	Set $N:=\sum_{\epsilon\in P(k,r)} 
-	(|\epsilon|-1)\cdot b_\epsilon$.
+	(|\epsilon|-1)  b_\epsilon$.
 	Counting vertices and automorphisms we get that
 	\begin{equation} \label{eqn:aux3}
-	|\Omega_n^\prime|= (n-len(\overline{u}))_{N}
+	|\Omega_n^\prime|= (n-\len(\overline{u}))_{N}
 	\prod_{\epsilon\in P(k,r)}
-	\frac{1}{b_\epsilon!} \cdot
+	\frac{1}{b_\epsilon!}  
 	\left( \frac{1}{\aut(\epsilon)} \right)^
@@
 
-	Because of \cref{lem:far_away} a.a.s if $e\in E(G_n)$
-	and $v\in V(e)$, then $e\in E(T_n)$. In consequence:
+	Because of \Cref{lem:far_away} a.a.s if $e\in E(G_n)$
+	and $v\in V(e)$, then $e\in E(T_n)$. Thus,
 	\begin{align} \label{eqn:aux4}
@@
 	\right)
-	\right)\sim\\ \nonumber
+	\right)\sim \\ \nonumber
 	&
@@
 	P(k,r)} \beta_{R(\epsilon)}^{b_\epsilon}\right)
-	\cdot 		
 	\mathrm{Pr}_{\pi(\overline{u})\wedge \psi(\overline{w})}\left(
@@
 	\end{align}
-	The trees $Tr(T_n;u)$ in last probability
+	The trees $Tr(T_n;u)$ in the last probability
 	coincide with 
 	$Tr(G_n,\overline{u}^\smallfrown\overline{w};\,u;\, r-1)$
-	for all $u$'s.
-	In consequence, using the hypothesis that \cref{thm:BigTrees}
-	holds for $r-1$ we obtain
+	for all $u$.
+	As a consequence, using the hypothesis that \Cref{thm:BigTrees}
+	holds for $r-1$, we obtain
 	\begin{align*}
@@
 	\end{align*}
-	Joining this with \cref{eqn:aux2},
-	\cref{eqn:aux3} and \cref{eqn:aux4} we obtain 
+	Combining this this with \Cref{eqn:aux2,,eqn:aux3,,eqn:aux4} we obtain 
 	\begin{align*} 
@@
 	\right]
-	\sim   
-	\frac{(n-len(\overline{u}))_{N}}
+	\sim   \\
+	\frac{(n-\len(\overline{u}))_{N}}
 	{n^{N}}
-	\cdot
 	\prod_{\epsilon\in P(k,r)}
-	\frac{1}{b_\epsilon!} \cdot
-	\left( \frac{\beta_{R(\epsilon)}\cdot \lambda_{r,\epsilon}
+	\frac{1}{b_\epsilon!}  
+	\left( \frac{\beta_{R(\epsilon)}  \lambda_{r,\epsilon}
 	}{\aut(\epsilon)} \right)^
@@
 	\end{align*}
-	This proves \cref{eq:aux1} and the statement. 	
+	This proves \Cref{eq:aux1} and the statement. 	
 \end{proof}
 
-Next lemma completes the proof of \cref{thm:BigTrees}.
+Next lemma completes the proof of \Cref{thm:BigTrees}.
 
 \begin{lemma} \label{lem:singletreeprob}
-Let $r>0$. Suppose that \cref{thm:BigTrees}
-holds for $r-1$. Then it also holds for $r$. 
+Let $r>0$. Suppose that \Cref{thm:BigTrees}
+holds for $r-1$. Then it also holds for~$r$. 
 \end{lemma}
@@
 Fix $k\in \N$. 
-We start showing condition (1) of \cref{thm:BigTrees}.
+We start showing condition (1) of \Cref{thm:BigTrees}.
 Fix $\mathbf{T}$ a $\sim_k$ class of trees with radius at most $r$. 
@@
 $\epsilon$. Let $E^1_\mathbf{T}, E^2_\mathbf{T}, 
-\{a_\epsilon\}_\epsilon$ be as in \cref{obs:equivalenttrees}.
+\{a_\epsilon\}_\epsilon$ be as in \Cref{obs:equivalenttrees}.
 Then
@@
 \]
-And using the previous lemma we obtain that last limit
-equals the following expression.
+Using the previous lemma we obtain that the last limit
+equals the following expression:
 \[ 
@@
 \mathrm{Poiss}_{\mu_{r,\epsilon}}(\geq k ) 
-\right)\cdot
+\right) 
 \left(
@@
 Using the definition of 
-the $\mu_{r,\epsilon}$'s we obtain that last expression
+the $\mu_{r,\epsilon}$ we obtain that the last expression
 belongs to $\Lambda$ as we wanted to prove. Furthermore,
-as the $\mu_{r,\epsilon}$'s are positive, this expression is also 
+as the $\mu_{r,\epsilon}$ are positive, this expression is also 
 positive for all values of
@@
 are asymptotically independent and are also independent of $\pi(\overline{u})$. 
-In consequence the desired result follows from condition (1). 
+Then the desired result follows from condition (1). 
 \end{proof}
@@
 	satisfying 
-	that all the $\overline{v}(\mathbf{T})$'s are
+	that all the $\overline{v}(\mathbf{T})$ are
 	disjoint. Let $\overline{w}\in (\N)_*$ be a concatenation
-	of all the $\overline{v}(\mathbf{T})$'s. 
+	of all the $\overline{v}(\mathbf{T})$. 
 	For each $\mathbf{T}\in 
@@
 	vertices $v\in \overline{v}(\mathbf{T})$ such that 
-	$Tr(G_n,\,\overline{w};\,v;\,r)\in \mathbf{T}$. Because of \cref{thm:BigTrees}
+	$Tr(G_n,\,\overline{w};\,v;\,r)\in \mathbf{T}$. Because of \Cref{thm:BigTrees}
 	the $\sim_k$ types of the trees $Tr(G_n,\,\overline{w};\,v;\,r)$ 
@@
 	$m$ and $\Pr[r,\mathbf{T}]$. That is, given natural numbers
-	$0\leq l_\mathbf{T} \leq m$ for all $\mathbf{T}\in \Sigma$, it is
-	satisfied that
-
+	$0\leq l_\mathbf{T} \leq m$ for all $\mathbf{T}\in \Sigma$, 
 	\[
@@
 	\prod_{\mathbf{T}\in \Sigma} \binom{m}{l_\mathbf{T}}
-	\Pr[r,\mathbf{T}]^{l_\mathbf{T}}\cdot (1-\Pr[r,\mathbf{T}] )^{m-l_\mathbf{T}}.
+	\Pr[r,\mathbf{T}]^{l_\mathbf{T}}  (1-\Pr[r,\mathbf{T}] )^{m-l_\mathbf{T}}.
 	\] 
@@
 	for all $\mathbf{T}\in \Sigma$ and fix $\epsilon>0$ arbitrarily small.
-	Because of the Law Of Large Numbers if $m$ is big enough it holds that
+	Because of the Law of large numbers, if $m$ is large enough
 	\begin{equation}\label{eq:rich1}
@@
 	\end{equation}
-	Also, for $m$ big enough we have that
+	Also, for $m$ large enough we have 
 	\begin{equation}\label{eq:rich2}
-		\Pr[r,\mathbf{T}] > l/m + \delta \quad \text{for all $\mathbf{T}\in \Sigma$}.
+		\Pr[r,\mathbf{T}] > k/m + \delta \quad \text{for all $\mathbf{T}\in \Sigma$}.
 	\end{equation}
-	Suppose that $m$ is big enough for both \cref{eq:rich1} and \cref{eq:rich2}
+	Suppose that $m$ is large enough for both \Cref{eq:rich1,eq:rich2}
 	to hold. Then 
@@
 	\]
-	We define the
-	event $A_n$ as the event that
+	We define $A_n$ as the event that
 	for any $v\in \overline{w}$ we have
@@
 	$N(v;r)=Tr(G_n,\,\overline{w};\,v;\,r)$ and
-	the $N(v;r)$'s are disjoint trees. 
+	the $N(v;r)$ are disjoint trees. 
 	Thus, if both $A_n$ holds and $X_{n,\mathbb{T}}\geq k$ for all $\mathbb{T}$ then 
-	$G_n$ is $(k,r)$-rich. Because of \cref{lem:disjointtrees} a.a.s $A_n$ holds, and we
+	$G_n$ is $(k,r)$-rich. Because of \Cref{lem:disjointtrees} a.a.s $A_n$ holds, and we
 	obtain
@@
 	As $\epsilon$ can be arbitrarily small given a suitable choice of $m$ we
-	obtain that necessarily a.a.s $G_n$ is $(k,r)$-rich, as it was to be proved. 
+	obtain that necessarily a.a.s $G_n$ is $(k,r)$-rich, as was to be proved. 
 \end{proof}
@@
 	$\{\beta_R\}_{R\in \sigma}$ that satisfy the following conditions:
-	(1) given natural numbers $a_R$ for each $R\in \sigma$, any positive number $b\in \N$
-	and any $\lambda\in \Lambda$ the expression $\frac{\lambda}{b}\cdot \prod_{R\in \sigma} \beta_R^{a_R}$
+	(1) given natural numbers $a_R$ for each $R\in \sigma$, a positive number $b\in \N$
+	and a $\lambda\in \Lambda$, the expression $\frac{\lambda}{b}  \prod_{R\in \sigma} \beta_R^{a_R}$
 	belongs to $\Gamma$, 
-	(2) given any $\gamma\in \Gamma$ and any $a\in \N$, the expressions $\mathrm{Poiss}_\gamma(a)$
+	(2) given a $\gamma\in \Gamma$ and a $a\in \N$, the expressions $\mathrm{Poiss}_\gamma(a)$
 	and $\mathrm{Poiss}_{\gamma}(\geq a)$ both belong to $\Upsilon$, and
 	(3) if $\upsilon_1, \upsilon_2\in \Upsilon$ then 
-	$\upsilon_1\cdot \upsilon_2 \in \Upsilon$ as well. 
+	$\upsilon_1  \upsilon_2 \in \Upsilon$ as well. 
 \end{definition}
@@
 	\frac{\prod_{R\in \sigma} \beta_R^{|E_R(H)|}}
-	{\aut(H,\tau)}\cdot\lambda_{r,O}.
+	{\aut(H,\tau)} \lambda_{r,O}.
 	\]	
@@
 	Let $k,r\in \N$. For any $O\in C(k,r)$ let $X_{n,O}$ be
-	the random variable that counts the connected components
+	the random variable equal to the number of connected components
 	$H$ of $Core(G_n;\, r)$ such that $H^\prime:=Center(H)$
-	satisfies that $(H^\prime, \tau^k_{H})\in O$. Then the variables
-	$X_{n,O}$'s converge in distribution to independent 
-	Poisson variables whose respective mean values are given by the 
-	$\gamma_{r,O}$'s.
+	satisfies that $(H^\prime, \tau^k_{H})\in O$. Then the
+	$X_{n,O}$ converge in distribution to independent 
+	Poisson variables whose respective expected values are given by the 
+	$\gamma_{r,O}$.
 \end{lemma}
 \begin{proof}
-The proof is similar to the one of \cref{lem:poisedges}. 
-By \cref{thm:BrunSieve} to prove the result is enough to show
+The proof is similar to the one of \Cref{lem:poisedges}. 
+By \Cref{thm:BrunSieve}, to prove the result is enough to show
 that for any natural numbers $\{b_O\}_{O\in C(k,r)}$ it holds 
@@
 component $H^\prime$ of $Core(G_n;\, r)$.
-Using observation \cref{obs:binomialmean} we obtain
+Using observation \Cref{obs:binomialmean} we obtain
 \[
@@
 to the same connected component $H$ of $Core(G_n;\,r)$ and thus $H_1\cup H_2\subset
-Center(H)$. In consequence neither $H_1\sqsubset G_n$ or $H_2\sqsubset G_n$ hold. 
-$(H_1,\tau_1),(H_2,\tau_2)\in \bigcup_{O\in C(k,r)} F_O$. Hence, 
+Center(H)$. As a consequence neither $H_1\sqsubset G_n$ or $H_2\sqsubset G_n$ hold. 
+$(H_1,\tau_1),(H_2,\tau_2)\in \bigcup_{O\in C(k,r)} F_O$. Hence 
 in the last sum it suffices to consider disjoint choices $\{F_O\}_O$. 
@@
 \right]=
-|\Omega^\prime_n|\cdot
+|\Omega^\prime_n| 
 \mathrm{Pr}\left(
@@
 
-Set $N:=\sum_{O\in C(k,r)} |O|\cdot b_O$. We have that
+Set $N:=\sum_{O\in C(k,r)} |O|  b_O$. We have that
 \begin{equation} \label{eq:cycl_aux2}
@@
 \frac{(n)_N}
-{\prod_{O\in C(k,r)} b_O!\cdot \aut(O)^{b_O}}.
+{\prod_{O\in C(k,r)} b_O!  \aut(O)^{b_O}}.
 \end{equation}
@@
 \beta_R^{|E_R(O)|}}{n^{|O|}} \right)^{b_O}=
-\frac{1}{n^N} \cdot
+\frac{1}{n^N}  
 \prod_{O\in C(k,r)} \left( \prod_{R\in \sigma}
@@
 \]
-Because of \cref{cor:simple} a.a.s if some cycle $H$ of diameter at most
-$2r+1$ satisfies $H\subset G_n$ then $H\sqsubset G_n$. In consequence:
+Because of \Cref{cor:simple} a.a.s if some cycle $H$ of diameter at most
+$2r+1$ satisfies $H\subset G_n$ then $H\sqsubset G_n$. Hence,
 \begin{align}
@@
 \right) \sim \\ \label{eq:cycl_aux3}
-&\frac{1}{n^N} \cdot
+&\frac{1}{n^N}  
 \prod_{O\in C(k,r)} \left( \prod_{R\in \sigma}
-\beta_R^{|E_R(O)|} \right)^{b_O} \cdot
+\beta_R^{|E_R(O)|} \right)^{b_O}  
 \mathrm{Pr}_{\varphi(\overline{v})}\left(
@@
 As all the vertices $v\in \overline{v}$ belong to $Core(G_n;\,r)$, the
-trees $Tr(G_n;\,v;\,r)$ in last probability coincide with 
-$Tr(G_n,\,\overline{v};\, v;\, r)$. Hence, by \cref{thm:BigTrees}
+trees $Tr(G_n;\,v;\,r)$ in the last probability coincide with 
+$Tr(G_n,\,\overline{v};\, v;\, r)$. By \Cref{thm:BigTrees}
 we have that
@@
 \end{equation*}
-Joining this with \cref{eq:cycl_aux1}, \cref{eq:cycl_aux2} and \cref{eq:cycl_aux3} we obtain
+Combining this with \Cref{eq:cycl_aux1,eq:cycl_aux2,eq:cycl_aux3} we obtain
 \begin{equation*}
@@
 \frac{(n)_N}{n^N}
-\cdot
 \prod_{O\in C(k,r)}
@@
 \left(
-\frac{\lambda_{r,O}\cdot\prod_{R\in\sigma} \beta_R^{|E_R(O)|}}{\aut(O)}
+\frac{\lambda_{r,O} \prod_{R\in\sigma} \beta_R^{|E_R(O)|}}{\aut(O)}
 \right) \sim \prod_{O\in C(k,r)} \frac{(\gamma_{r,O})^{b_O}}{b_O!}.
 \end{equation*}
-This proves \cref{eq:cycl_aux} and the statement. 
+This proves \Cref{eq:cycl_aux} and the statement. 
 \end{proof}
@@
 \begin{theorem}\label{thm:agreeabilityprobabilities}
-	Let $k,r\in \N$ and let $\mathcal{O}$ be a simple $(k,r)$-agreeability class
+	Let $k,r\in \N$ and let $\mathbf{O}$ be a simple $(k,r)$-agreeability class
 	of hypergraphs. Then 
-	$\Ln \PR{G_n\in \mathcal{O}}$ exists and is an expression
+	$\Ln \PR{G_n\in \mathbf{O}}$ exists and is an expression
 	in $\Upsilon$. 
@@
 For each $O\in C(k,r)$ let $X_{n,O}$ be as in the previous lemma. 
-Let $U_\mathcal{O}^1, U_\mathcal{O}^2$ and $\{a_O\}_{O\in U^2_\mathcal{O}}$ 
-be as in \cref{obs:agreeablecores}. Let $A_n$ be the event that $G_n$ is $r$-simple. 
+Let $U_\mathbf{O}^1, U_\mathbf{O}^2$ and $\{a_O\}_{O\in U^2_\mathbf{O}}$ 
+be as in \Cref{obs:agreeablecores}. Let $A_n$ be the event that $G_n$ is $r$-simple. 
 Then
@@
  \Ln
- \PR{G_n \in \mathcal{O}}=
+ \PR{G_n \in \mathbf{O}}=
  \Ln
@@
  \left(
- \bigwedge_{O\in U_\mathcal{O}^1}
+ \bigwedge_{O\in U_\mathbf{O}^1}
  X_{n,O}\geq k
@@
  \left(
- \bigwedge_{O\in  U^2_\mathcal{O}}
+ \bigwedge_{O\in  U^2_\mathbf{O}}
  X_{n,O}=a_O.
@@
 \end{align*}
-Because of \cref{cor:simple}, a.a.s $A_n$ holds. Thus, using last
+Because of \Cref{cor:simple}, a.a.s $A_n$ holds. Thus, using the last
 lemma the previous limit equals the following expression
@@
 \right)
-\cdot
 \left(
@@
 \end{align*}
-As all the $\gamma_{r,O}$'s belong to $\Gamma$,
+As all the $\gamma_{r,O}$ belong to $\Gamma$,
 this last expression belongs to $\Upsilon$ and the theorem is proven. 
@@
 	let $r=3^k$. Let 
-	$G_n:=G_n\left(\{\beta_R\}_{R\in \sigma}\right)$.
-	Let $\Sigma$ be the set of $(k,r)$-agreeability classes of 
-	$r$-simple hypergraphs. Because of \cref{cor:simple} a.a.s 
-	$G_n$ is $r$-simple. In consequence
+	$G_n:=G_n\left(\{\beta_R\}_{R\in \sigma}\right)$ and 
+	let $\Sigma$ be the set of $(k,r)$-agreeability classes of 
+	$r$-simple hypergraphs. Because of \Cref{cor:simple} a.a.s 
+	$G_n$ is $r$-simple. Thus
 	\begin{equation} \label{eq:aux1}
@@
 	\Ln
-	\sum_{\mathcal{O}\in \Sigma} \mathrm{Pr}\left(
-	G_n\in \mathcal{O}
-	\right) \cdot 
+	\sum_{\mathbf{O}\in \Sigma} \mathrm{Pr}\left(
+	G_n\in \mathbf{O}
+	\right)   
 	\mathrm{Pr}\left(
@@
 	\Big| \,
-	G_n\in \mathcal{O}
+	G_n\in \mathbf{O}
 	\right).
 	\end{equation}
-	Because the set $\Sigma$ is finite, sum and we can exchange
-	last summation and limit symbols. Because \cref{thm:rich} a.a.s 
-	$G_n$ is $(k,r)$-rich. This together with \cref{thm:Duplicatorwins}
-	implies that for $\mathcal{O}\in \Sigma$
+	Because the set $\Sigma$ is finite, we can exchange the 
+	summation and the limit. By \Cref{thm:rich} a.a.s 
+	$G_n$ is $(k,r)$-rich. This together with \Cref{thm:Duplicatorwins}
+	implies that for any $\mathbf{O}\in \Sigma$
 	\[
@@
 	\Big| \,
-	G_n\in \mathcal{O}
+	G_n\in \mathbf{O}
 	\right) = 
@@
 	Let $\Sigma^\prime\subset \Sigma$ be the set of classes 
-	$\mathcal{O}$ for which last limit equals one. Then
+	$\mathbf{O}$ for which last limit equals $1$. Then
 	\[
@@
 	\right)=
-	\sum_{\mathcal{O}\in \Sigma^\prime}
+	\sum_{\mathbf{O}\in \Sigma^\prime}
 	\Ln \mathrm{Pr}\left(
-	G_n \in \mathcal{O}
+	G_n \in \mathbf{O}
 	\right).		
 	\]
-	Because of \cref{thm:agreeabilityprobabilities} we know that
-	each of the limits inside last sum exists and is given by
+	Because of \Cref{thm:agreeabilityprobabilities} we know that
+	each of the limits inside the last sum exists and is given by
 	an expression that belongs to $\Upsilon$. As a consequence the
@@
 but the generality
-in \cref{thm:main} allows for many modifications. \par
+in \Cref{thm:main} allows for many variants. \par
 
 \begin{definition}\label{def:CNF}
-Given a variable $x$ both expressions
+Given a variable $x$, both expressions
 $x$ and $\neg x$ are called \textbf{literals}. A \textbf{clause}
@@
 $\neg x\in C$ and $f(x)=0$. 
-Given a natural number $l\in\N$
+Given $l\in\N$
 a $l$-\textbf{CNF formula} is a set of  non-tautological clauses 
@@
 We say that a formula $F$
-over the variables $x_1,\dots, x_n$ is \textbf{satisfiable} if there is an
+on the variables $x_1,\dots, x_n$ is \textbf{satisfiable} if there is an
 assignment $f:\{x_1,\dots, x_n\}\rightarrow \{0,1\}$ that satisfies all clauses
-for any clause $C\in F$. 
+in $F$. 
 \end{definition}
@@
 the random model $F(l,n,p)$ as the discrete probability space that
-assigns to each $l$-CNF formula $F$ formed of clauses over
+assigns to each $l$-CNF formula $F$ on
 the variables $\{x_i\}_{i\in [n]}$
@@
 \[
-\PR{F}= p^{|F|}\cdot (1-p)^{2^l\binom{n}{l}-|F|}.
-\] 
+\PR{F}= p^{|F|}  (1-p)^{2^l\binom{n}{l}-|F|},
+\] 
+where $|F|$ is the number of clauses in $F$.
 Equivalently, a random formula in $F(l,n,p)$ is obtained
@@
 The language $\sigma$ and the family $\mathcal{C}$ satisfy the conditions in 
-\cref{sect:structures}. The random model $F_l(n,p)$ coincides with the model
+\Cref{sect:structures}. The random model $F_l(n,p)$ coincides with the model
 $G(n,\{p_R\}_{R})$ of random $\mathcal{C}$-hypergraphs described in 
-\cref{sect:random} when all the $p_R$'s are equal. As a particular
-case of \cref{thm:main} we obtain the following result. 
+\Cref{sect:random} when all the $p_R$'s are equal. As a particular
+case of \Cref{thm:main} we obtain the following result. 
 \begin{theorem} \label{thm:mainsat}
@@
 	that counts the clauses in $F_n(\beta)$. It is satisfied that
-	$\mathrm{E}[X_n(\beta)]\sim \frac{\beta\cdot 2^l}{l!}n$. Let $c_1,
-	c_2$ be as in last corollary. Define $\beta_1:= \frac{c_1\cdot l!}{2^l}$
-	and $\beta_2:= \frac{c_2 \cdot l!}{2^l}$. Fix $\beta\in \R$ satisfying
+	$\mathrm{E}[X_n(\beta)]\sim \frac{\beta  2^l}{l!}n$. Let $c_1,
+	c_2$ be as in last corollary. Define $\beta_1:= \frac{c_1  l!}{2^l}$
+	and $\beta_2:= \frac{c_2   l!}{2^l}$. Fix $\beta\in \R$ satisfying
 	$0<\beta<\beta_1$. Let $\epsilon>0$ be a real number such that
-	$ \frac{\beta\cdot 2^l}{l!} +\epsilon< c_1$. For each $n\in \N$
-	set $\delta_1(n):=\floor*{ \left(\frac{\beta\cdot 2^l}{l!}-\epsilon\right)n}$
-	and $\delta_2(m):=\floor*{ \left(\frac{\beta\cdot 2^l}{l!}+\epsilon\right)n}$.
+	$ \frac{\beta  2^l}{l!} +\epsilon< c_1$. For each $n\in \N$
+	set $\delta_1(n):=\floor*{ \left(\frac{\beta  2^l}{l!}-\epsilon\right)n}$
+	and $\delta_2(m):=\floor*{ \left(\frac{\beta  2^l}{l!}+\epsilon\right)n}$.
 
@@
 	X_n(\beta)=m	
-	\right)\cdot dp_n(m).
+	\right)  dp_n(m).
 	\]
@@
 	X_n(\beta)=m	
-	\right)\cdot dp_n(m)\leq \\ & 
+	\right)  dp_n(m)\leq \ & 
 	\mathrm{Pr} \left(
 	F_n(\beta) \text{ is unsatisfiable } \Big|
-	X_n(\beta)=\delta_2(n) \right) \cdot 
+	X_n(\beta)=\delta_2(n) \right)   
 	\mathrm{Pr}\left( \delta_1(n) \leq X_n(\beta)  
@@
 \begin{proof}
-	Let $\beta_1$ and $\beta_2$ be as in \cref{thm:phasetransition}. 
+	Let $\beta_1$ and $\beta_2$ be as in \Cref{thm:phasetransition}. 
 	As $\Phi$ implies unsatisfiability it holds
 	$\PR{F_n(\beta)\models \Phi  }\leq  
-	\PR{F_n(\beta) \text{ is unsatisfiable }  }$. Thus, using \cref{thm:phasetransition}
+	\PR{F_n(\beta) \text{ is unsatisfiable }  }$. Thus, using \Cref{thm:phasetransition}
 	we get that for all $\beta\in (0,\beta_1]$
@@
 	\]
-	Because \cref{thm:mainsat} last limit varies analytically with $\beta$, so
+	Because \Cref{thm:mainsat} last limit varies analytically with $\beta$, so
 	if it vanishes in a proper interval $(0,\beta_1]$ then it has to vanish
@@
 %convergence law found by Lynch in \cite{lynch1992probabilities} with the application
-%to RANDOM SAT given in \cref{thm:satapplication} in mind.
+%to RANDOM SAT given in \Cref{thm:satapplication} in mind.
 
